### 2020-01-14 manuscript/manuscript.Rmd
Add parameters

---
title: "parameters"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(xtable)
library(kableExtra)
# load model parameters 
source("asr-parameters.R")
```

The ASReview software knows the following parameters: 
```{r}
# configurations table 
tab <- lapply(params, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("configurations")

# combinations table
combins <- expand.grid(params)

kable(tab, format  = "pandoc")
```

\
This leads to  `r nrow(combins)` combinations of configurations:

```{r}
kable(combins, row.names = TRUE, format = "pandoc")
```

### 2020-01-14 manuscript/asr-parameters.R

@@ -1,0 +1,52 @@
+# Gerbrich Ferdinands, 14-01-2020
+# document all parameters in asreview software
+
+#path <- "~/Downloads/automated-systematic-review-unsupervised/asreview"
+
+#params <- list.files(path, recursive = TRUE, include.dirs = TRUE)
+
+# library(httr)
+# req <- GET("https://api.github.com/repos/qubixes/automated-systematic-review/tree/unsupervised")
+# stop_for_status(req)
+# filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
+# grep("/unsupervised", filelist, value = TRUE, fixed = TRUE)
+
+#params[str_detect(params, ".py", negate = TRUE)]
+
+# model parameters -------------------------------------------------------------
+
+  # categorical variables ------------------------------------------------------
+  params <- list(
+    model = c("lstm_base",
+              "lstm_pool", 
+              "nb", # naive bayes
+              "rf", # random forest 
+              "svm",
+              "dense_nn"),
+    
+    query_strategy = c("cluster",
+                       "max",
+                       "uncertainty",
+                       "random",
+                       "mixed"), # is not implemented
+    
+    balance_strategy = c("simple",
+                         "double",
+                         "triple", 
+                         "undersample"),
+    
+    feature_extraction = c("doc2vec",
+                           "tfidf", 
+                           "sbert", 
+                           "embeddingIdf",
+                           "embeddingLSTM")
+  )
+  
+  # numerical variables --------------------------------------------------------
+  n_instances <- 1 # number of papers queried each query 
+  n_prior_included <- 10 
+  n_prior_excluded <- 10 
+
+# hyperparameters --------------------------------------------------------------
+
+  

### 2020-01-15 manuscript/manuscript.Rmd
parameter table

@@
 
-The ASReview software knows the following parameters: 
 ```{r}
@@
 
+```
+
+ASReview takes the following parameters/arguments:
+
+- a model
+- a query strategy
+- a balance strategy
+- feature extraction
+
+```{r}
 kable(tab, format  = "pandoc")
@@
 
-\
 This leads to  `r nrow(combins)` combinations of configurations:

### 2020-01-16 manuscript/manuscript.Rmd
update params

@@
 
+library(tidyverse)
 library(knitr)
@@
 combins <- expand.grid(params)
+combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"
 
+combins <- combins %>%
+  filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
+  arrange(model)
 ```

### 2020-01-16 manuscript/asr-parameters.R

@@ -26,20 +26,27 @@
     
     query_strategy = c("cluster",
                        "max",
-                       "uncertainty",
-                       "random",
-                       "mixed"), # is not implemented
+                       "max * cluster",
+                       "max * uncertainty",
+                       "max * random",
+                       "cluster * uncertainty",
+                       "cluster * random"
+                       #"uncertainty",
+                       #"random",
+                       #"mixed"
+                       ), # is not implemented
     
-    balance_strategy = c("simple",
-                         "double",
-                         "triple", 
-                         "undersample"),
+    balance_strategy = c(#"simple",
+                         #"double",
+                         "triple"
+                         #"undersample"s
+                         ),
     
     feature_extraction = c("doc2vec",
                            "tfidf", 
                            "sbert", 
-                           "embeddingIdf",
-                           "embeddingLSTM")
+                           "embeddingIdf", # ?
+                           "embeddingLSTM") # only for lstm
   )
   
   # numerical variables --------------------------------------------------------

### 2020-01-16 manuscript/manuscript.Rmd
combins update

--- 2020-01-15 manuscript/manuscript.Rmd
@@
 combins <- expand.grid(params)
+#combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"
 
+combins <- combins %>%
+  #filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
+  arrange(model)
 ```

### 2020-01-16 manuscript/manuscript.Rmd
meeting 16 jan

--- 2020-01-15 manuscript/manuscript.Rmd
@@
 colnames(tab) <- c("configurations")
+```
+
+```{r}
 
@@
 
+#combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"
+
+combins <- combins %>%
+  #filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
+  arrange(model, feature_extraction )
+
+# rows to drop
+droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
+combins <- combins[droprows, ]
 ```
@@
 
+- number of training data (included/excluded)
 - a model
 - a query strategy
-- a balance strategy
+- a balance strategy (fixed)
 - feature extraction

### 2020-01-16 manuscript/asr-parameters.R

@@ -19,18 +19,19 @@
   params <- list(
     model = c("lstm_base",
               "lstm_pool", 
+              "dense_nn",
               "nb", # naive bayes
               "rf", # random forest 
               "svm",
-              "dense_nn"),
+              "lr"),
     
     query_strategy = c("cluster",
                        "max",
-                       "max * cluster",
-                       "max * uncertainty",
-                       "max * random",
-                       "cluster * uncertainty",
-                       "cluster * random"
+                       "max*cluster",
+                       "max*uncertainty",
+                       "max*random",
+                       "cluster*uncertainty",
+                       "cluster*random"
                        #"uncertainty",
                        #"random",
                        #"mixed"
@@ -49,6 +50,13 @@
                            "embeddingLSTM") # only for lstm
   )
   
+  # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
+  # and do not vary the balance strategy. 
+  params$model <- params[["model"]][4:7]
+  params$balance_strategy <- NULL
+  params$feature_extraction <- params[["feature_extraction"]][1:4]
+  params$training_data <- c("10/10", "5/5", "5/10")
+    
   # numerical variables --------------------------------------------------------
   n_instances <- 1 # number of papers queried each query 
   n_prior_included <- 10 

### 2020-01-20 definitions.Rmd
Fixed table combinations, put into latex format

---
title: "Definition list"
author: "Gerbrich Ferdinands"
date: "1/20/2020"
output: pdf_document
---
Term 1

~   Definition 1a
~   definition 1b
~ definition

Term 2 with *inline markup*

:   Definition 2

        { some code, part of Definition 2 }

    Third paragraph of definition 2.

### 2020-01-20 manuscript/manuscript.Rmd
Fixed table combinations, put into latex format

@@
 # combinations table
-combins <- expand.grid(params)
-
-#combins$model %in% c("lstm_base", "lstm_pool") & combins$feature_extraction != "embeddingLSTM"
-
-combins <- combins %>%
-  #filter(combins$model %in% c("lstm_base", "lstm_pool") & feature_extraction != "embeddingLSTM") %>%
-  arrange(model, feature_extraction )
+combins <- expand.grid(params) %>%
+  arrange(model, feature_extraction)
 
@@
 droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
-combins <- combins[droprows, ]
+combins <- combins[!droprows, ]
 ```
@@
 ```{r}
-kable(tab, format  = "pandoc")
+kable(tab, "latex", booktabs = TRUE) %>%
+  kable_styling(full_width = FALSE) %>%
+  column_spec(2, width = "30em") 
 ```
 
-This leads to  `r nrow(combins)` combinations of configurations:
+This leads to  `r nrow(combins)` combinations of configurations.
+
+- Naive bayes only goes with tfidf feature extraction.
+- For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
+- This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.
 
 ```{r}
-kable(combins, row.names = TRUE, format = "pandoc")
+combins %>%
+  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
+  kable_styling(latex_options = c("repeat_header")) %>%
+  footnote(general = "nb model only works with tfidf feature extraction strategy. " )
 ```

### 2020-01-20 manuscript/asr-parameters.R

@@ -27,11 +27,11 @@
     
     query_strategy = c("cluster",
                        "max",
-                       "max*cluster",
-                       "max*uncertainty",
-                       "max*random",
-                       "cluster*uncertainty",
-                       "cluster*random"
+                       "max * cluster",
+                       "max * uncertainty",
+                       "max * random",
+                       "cluster * uncertainty",
+                       "cluster * random"
                        #"uncertainty",
                        #"random",
                        #"mixed"

### 2020-01-23 definitions.Rmd
update definitinos

@@
 ---
-Term 1
 
-~   Definition 1a
-~   definition 1b
-~ definition
+Model.
 
-Term 2 with *inline markup*
-
-:   Definition 2
+:   The prediction model for Active learning
 
@@
     Third paragraph of definition 2.
+
+Query Strategy
+:   def
+
+        { some code, part of Definition 2 }
+
+        add paragraph here
+
+    Uncertainty sampling.
+    :  Selects the least sure instances for labelling.
+
+    Maximum sampling.
+    :  Selects the samples with the highest prediction probability.
+
+    Random and maximum sampling. 
+    :  Combination of random and maximum sampling. By default samples the 95% of the instances with max sampling, and 5% of the samples with random sampling.
+
+Feature Extraction Strategy
+:   Feature Extraction Strategy
+
+        { some code, part of Definition x }
+
+    Third paragraph of definition x.
+
+    Doc2Vec
+    :
+
+    Term frequency-inverse document frequency (tf-idf)
+    :
+
+    sbert

### 2020-01-23 manuscript/asr-parameters.R

@@ -50,6 +50,7 @@
                            "embeddingLSTM") # only for lstm
   )
   
+  
   # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
   # and do not vary the balance strategy. 
   params$model <- params[["model"]][4:7]
@@ -62,6 +63,29 @@
   n_prior_included <- 10 
   n_prior_excluded <- 10 
 
-# hyperparameters --------------------------------------------------------------
-
   
+  names(params$model) <- params$model
+  names(params$query_strategy) <- params$query_strategy
+  names(params$feature_extraction) <- params$feature_extraction
+  names(params$training_data) <- params$training_data
+  words <- params 
+
+  words$model <- c("Naive Bayes", "Random Forest", "Support Vector Machine", "Logistic Regression")
+  words$query_strategy <- c("Cluster Sampling", "Maximum Sampling",
+                            "Cluster * Maximum  Sampling", 
+                            "Maximum * Uncertainty Sampling", 
+                            "Maximum * Random Sampling", 
+                            "Cluster * Uncertainty Sampling", 
+                            "Cluster * Random Sampling")
+  
+  words$feature_extraction <- c("Doc2Vec", "tf-idf", "sbert", "embeddingIdf")
+  
+  # words$training_data <- c("10 included, 10 excluded",
+  #                          "5 included, 5 excluded",
+  #                          "5 included, 10 excluded")
+  # 
+  names(words) <- c("Models", "Query Strategies", 
+                    "Feature extraction strategies", 
+                    "Training data [included/excluded]")
+ # hyperparameters --------------------------------------------------------------
+ 

### 2020-01-28 manuscript/index/01-chap1.Rmd
- notes 23-01 - update table - add bookdown

<!--
This is for including Chapter 1.  Notice that it's also good practice to name your chunk.  This will help you debug potential issues as you knit.  The chunk above is called intro and the one below is called chapter1.  Feel free to change the name of the Rmd file as you wish, but don't forget to change it here from chap1.Rmd.
-->

<!--
The {#rmd-basics} text after the chapter declaration will allow us to link throughout the document back to the beginning of Chapter 1.  These labels will automatically be generated (if not specified) by changing the spaces to hyphens and capital letters to lowercase.  Look for the reference to this label at the beginning of Chapter 2.
-->

# R Markdown Basics {#rmd-basics}

### 2020-01-28 manuscript/index/05-appendix.Rmd
- notes 23-01 - update table - add bookdown

--- 2020-01-23 definitions.Rmd
@@
----
-title: "Definition list"
-author: "Gerbrich Ferdinands"
-date: "1/20/2020"
-output: pdf_document
----
+`r if(knitr:::is_latex_output()) '\\appendix'`
+
+`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
+
+<!--
+If you feel it necessary to include an appendix, it goes here.
+-->
+
+# The First Appendix
+
+This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup.
+
+**In the main Rmd file**
+
+```{r ref.label='include_packages', results='hide', echo = TRUE}
+```
+
+**In Chapter \@ref(ref-labels):**
+
+```{r ref.label='include_packages_2', results='hide', echo = TRUE}
+```
+
+# List of definitions
+
+Epoch
+:  A particular
 

### 2020-01-28 manuscript/index/index.Rmd
- notes 23-01 - update table - add bookdown

---
author: 'Gerbrich Ferdinands'
date: 'May 2020'
institution: 'Utrecht University'
division: 'Methodolgy and Statistics'
advisor: 'prof. dr. Rens van de Schoot'
# If you have more two advisors, un-silence line 7
#altadvisor: 'Your Other Advisor'
department: 'Faculty of Social Sciences'
degree: 'Master of Science'
title: 'My Master thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
# thesisdown::thesis_pdf: default
thesisdown::thesis_gitbook: default
#  thesisdown::thesis_word: default
# thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
acknowledgements: |
  I want to thank a few people.
#dedication: |
#  You can have a dedication here if you wish.
preface: |
  This is an example of a thesis setup to use the reed thesis document class
  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of metadata used to produce the document.  Be careful with spacing in this header!

If you'd prefer to not include a Dedication, for example, simply delete the section entirely, or silence (add #) them.

If you have other LaTeX packages you would like to include, delete the # before header-includes and list the packages after hyphens on new lines.

If you'd like to include a comment that won't be produced in your resulting file enclose it in a block like this.

If you receive a duplicate label error after knitting, make sure to delete the index.Rmd file and then knit again.
-->

```{r include_packages, include = FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
```

<!-- On ordering the chapter files:
There are two options:
1. Name your chapter files in the order in which you want them to appear (e.g., 01-Inro, 02-Data, 03-Conclusions). 
2. Otherwise, you can specify the order in which they appear in the _bookdown.yml (for PDF only).

Do not include 00(two-hyphens)prelim.Rmd and 00-abstract.Rmd in the YAML file--they are handled in the YAML above differently for the PDF version.
-->

<!-- The {.unnumbered} option here means that the introduction will be "Chapter 0." You can also use {-} for no numbers
on chapters.
-->

# Introduction {.unnumbered}

<!-- 
If you're still on the fence about using _R Markdown_, check out the resource for newbies available at <https://ismayc.github.io/rbasics-book/> or email us at <data@reed.edu>. 
-->

**Why use it?**

_R Markdown_ creates a simple and straightforward way to interface with the beauty of LaTeX.  Packages have been written in **R** to work directly with LaTeX to produce nicely formatting tables and paragraphs. In addition to creating a user friendly interface to LaTeX, _R Markdown_ also allows you to read in your data, to analyze it and to visualize it using **R** functions, and also to provide the documentation and commentary on the results of your project.  Further, it allows for **R** results to be passed inline to the commentary of your results.  You'll see more on this later.

<!-- 
Having your code and commentary all together in one place has a plethora of benefits!
-->

**Who should use it?**

Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use _R Markdown_. Of particular use should be anyone in the sciences, but the user-friendly nature of _Markdown_ and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc. should make it of great benefit to nearly anyone writing a thesis project.

**For additional help with bookdown** 
Please visit [the free online bookdown reference guide](https://bookdown.org/yihui/bookdown/).

### 2020-01-28 manuscript/index/thesis.tex
- notes 23-01 - update table - add bookdown

% This is the Reed College LaTeX thesis template. Most of the work
% for the document class was done by Sam Noble (SN), as well as this
% template. Later comments etc. by Ben Salzberg (BTS). Additional
% restructuring and APA support by Jess Youngberg (JY).
% Your comments and suggestions are more than welcome; please email
% them to cus@reed.edu
%
% See http://web.reed.edu/cis/help/latex.html for help. There are a
% great bunch of help pages there, with notes on
% getting started, bibtex, etc. Go there and read it if you're not
% already familiar with LaTeX.
%
% Any line that starts with a percent symbol is a comment.
% They won't show up in the document, and are useful for notes
% to yourself and explaining commands.
% Commenting also removes a line from the document;
% very handy for troubleshooting problems. -BTS

% As far as I know, this follows the requirements laid out in
% the 2002-2003 Senior Handbook. Ask a librarian to check the
% document before binding. -SN

%%
%% Preamble
%%
% \documentclass{<something>} must begin each LaTeX document
\documentclass[12pt,twoside]{reedthesis}
% Packages are extensions to the basic LaTeX functions. Whatever you
% want to typeset, there is probably a package out there for it.
% Chemistry (chemtex), screenplays, you name it.
% Check out CTAN to see: http://www.ctan.org/
%%
\usepackage{graphicx,latexsym}
\usepackage{amsmath}
\usepackage{amssymb,amsthm}
\usepackage{longtable,booktabs,setspace}
\usepackage{chemarr} %% Useful for one reaction arrow, useless if you're not a chem major
\usepackage[hyphens]{url}
% Added by CII
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{float}
\floatplacement{figure}{H}
% End of CII addition
\usepackage{rotating}

% Next line commented out by CII
%%% \usepackage{natbib}
% Comment out the natbib line above and uncomment the following two lines to use the new
% biblatex-chicago style, for Chicago A. Also make some changes at the end where the
% bibliography is included.
%\usepackage{biblatex-chicago}
%\bibliography{thesis}

% Added by CII (Thanks, Hadley!)
% Use ref for internal links
\renewcommand{\hyperref}[2][???]{\autoref{#1}}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Subsection}
% End of CII addition

% Added by CII
\usepackage{caption}
\captionsetup{width=5in}
% End of CII addition

% \usepackage{times} % other fonts are available like times, bookman, charter, palatino

% Syntax highlighting #22
  \usepackage{color}
  \usepackage{fancyvrb}
  \newcommand{\VerbBar}{|}
  \newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
  % Add ',fontsize=\small' for more characters per line
  \usepackage{framed}
  \definecolor{shadecolor}{RGB}{248,248,248}
  \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
  \newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
  \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
  \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\BuiltInTok}[1]{#1}
  \newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
  \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
  \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
  \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
  \newcommand{\ExtensionTok}[1]{#1}
  \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\ImportTok}[1]{#1}
  \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
  \newcommand{\NormalTok}[1]{#1}
  \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
  \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
  \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
  \newcommand{\RegionMarkerTok}[1]{#1}
  \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% To pass between YAML and LaTeX the dollar signs are added by CII
\title{My Master thesis}
\author{Gerbrich Ferdinands}
% The month and year that you submit your FINAL draft TO THE LIBRARY (May or December)
\date{May 2020}
\division{Methodolgy and Statistics}
\advisor{prof. dr. Rens van de Schoot}
\institution{Utrecht University}
\degree{Master of Science}
%If you have two advisors for some reason, you can use the following
% Uncommented out by CII
% End of CII addition

%%% Remember to use the correct department!
\department{Faculty of Social Sciences}
% if you're writing a thesis in an interdisciplinary major,
% uncomment the line below and change the text as appropriate.
% check the Senior Handbook if unsure.
%\thedivisionof{The Established Interdisciplinary Committee for}
% if you want the approval page to say "Approved for the Committee",
% uncomment the next line
%\approvedforthe{Committee}

% Added by CII
%%% Copied from knitr
%% maxwidth is the original width if it's less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\renewcommand{\contentsname}{Table of Contents}
% End of CII addition

\setlength{\parskip}{0pt}

% Added by CII

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\Acknowledgements{
I want to thank a few people.
}

\Dedication{

}

\Preface{
This is an example of a thesis setup to use the reed thesis document class
(for LaTeX) and the R bookdown package, in general.
}

\Abstract{
The preface pretty much says it all.

\par

Second paragraph of abstract starts here.
}

% End of CII addition
%%
%% End Preamble
%%
%
\begin{document}

% Everything below added by CII
  \maketitle

\frontmatter % this stuff will be roman-numbered
\pagestyle{empty} % this removes page numbers from the frontmatter
  \begin{acknowledgements}
    I want to thank a few people.
  \end{acknowledgements}
  \begin{preface}
    This is an example of a thesis setup to use the reed thesis document class
    (for LaTeX) and the R bookdown package, in general.
  \end{preface}
  \hypersetup{linkcolor=black}
  \setcounter{tocdepth}{2}
  \tableofcontents

  \listoftables

  \listoffigures
  \begin{abstract}
    The preface pretty much says it all.

    \par

    Second paragraph of abstract starts here.
  \end{abstract}

\mainmatter % here the regular arabic numbering starts
\pagestyle{fancyplain} % turns page numbering back on

\hypertarget{introduction}{%
\chapter*{Introduction}\label{introduction}}
\addcontentsline{toc}{chapter}{Introduction}

Welcome to the \emph{R Markdown} thesis template. This template is based on (and in many places copied directly from) the Reed College LaTeX template, but hopefully it will provide a nicer interface for those that have never used TeX or LaTeX before. Using \emph{R Markdown} will also allow you to easily keep track of your analyses in \textbf{R} chunks of code, with the resulting plots and output included as well. The hope is this \emph{R Markdown} template gets you in the habit of doing reproducible research, which benefits you long-term as a researcher, but also will greatly help anyone that is trying to reproduce or build onto your results down the road.

Hopefully, you won't have much of a learning period to go through and you will reap the benefits of a nicely formatted thesis. The use of LaTeX in combination with \emph{Markdown} is more consistent than the output of a word processor, much less prone to corruption or crashing, and the resulting file is smaller than a Word file. While you may have never had problems using Word in the past, your thesis is likely going to be about twice as large and complex as anything you've written before, taxing Word's capabilities. After working with \emph{Markdown} and \textbf{R} together for a few weeks, we are confident this will be your reporting style of choice going forward.

\textbf{Why use it?}

\emph{R Markdown} creates a simple and straightforward way to interface with the beauty of LaTeX. Packages have been written in \textbf{R} to work directly with LaTeX to produce nicely formatting tables and paragraphs. In addition to creating a user friendly interface to LaTeX, \emph{R Markdown} also allows you to read in your data, to analyze it and to visualize it using \textbf{R} functions, and also to provide the documentation and commentary on the results of your project. Further, it allows for \textbf{R} results to be passed inline to the commentary of your results. You'll see more on this later.

\textbf{Who should use it?}

Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use \emph{R Markdown}. Of particular use should be anyone in the sciences, but the user-friendly nature of \emph{Markdown} and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc. should make it of great benefit to nearly anyone writing a thesis project.

\textbf{For additional help with bookdown}
Please visit \href{https://bookdown.org/yihui/bookdown/}{the free online bookdown reference guide}.

\hypertarget{rmd-basics}{%
\chapter{R Markdown Basics}\label{rmd-basics}}

Here is a brief introduction into using \emph{R Markdown}. \emph{Markdown} is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. \emph{R Markdown} provides the flexibility of \emph{Markdown} with the implementation of \textbf{R} input and output. For more details on using \emph{R Markdown} see \url{http://rmarkdown.rstudio.com}.

Be careful with your spacing in \emph{Markdown} documents. While whitespace largely is ignored, it does at times give \emph{Markdown} signals as to how to proceed. As a habit, try to keep everything left aligned whenever possible, especially as you type a new paragraph. In other words, there is no need to indent basic text in the Rmd document (in fact, it might cause your text to do funny things if you do).

\hypertarget{lists}{%
\section{Lists}\label{lists}}

It's easy to create a list. It can be unordered like
\begin{itemize}
\tightlist
\item
  Item 1
\item
  Item 2
\end{itemize}
or it can be ordered like
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Item 1
\item
  Item 2
\end{enumerate}
Notice that I intentionally mislabeled Item 2 as number 4. \emph{Markdown} automatically figures this out! You can put any numbers in the list and it will create the list. Check it out below.

To create a sublist, just indent the values a bit (at least four spaces or a tab). (Here's one case where indentation is key!)
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Item 1
\item
  Item 2
\item
  Item 3
  \begin{itemize}
  \tightlist
  \item
    Item 3a
  \item
    Item 3b
  \end{itemize}
\end{enumerate}
\hypertarget{line-breaks}{%
\section{Line breaks}\label{line-breaks}}

Make sure to add white space between lines if you'd like to start a new paragraph. Look at what happens below in the outputted document if you don't:

Here is the first sentence. Here is another sentence. Here is the last sentence to end the paragraph.
This should be a new paragraph.

\emph{Now for the correct way:}

Here is the first sentence. Here is another sentence. Here is the last sentence to end the paragraph.

This should be a new paragraph.

\hypertarget{r-chunks}{%
\section{R chunks}\label{r-chunks}}

When you click the \textbf{Knit} button above a document will be generated that includes both content as well as the output of any embedded \textbf{R} code chunks within the document. You can embed an \textbf{R} code chunk like this (\texttt{cars} is a built-in \textbf{R} dataset):
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
     speed           dist       
 Min.   : 4.0   Min.   :  2.00  
 1st Qu.:12.0   1st Qu.: 26.00  
 Median :15.0   Median : 36.00  
 Mean   :15.4   Mean   : 42.98  
 3rd Qu.:19.0   3rd Qu.: 56.00  
 Max.   :25.0   Max.   :120.00  
\end{verbatim}
\hypertarget{inline-code}{%
\section{Inline code}\label{inline-code}}

If you'd like to put the results of your analysis directly into your discussion, add inline code like this:
\begin{quote}
The \texttt{cos} of \(2 \pi\) is 1.
\end{quote}
Another example would be the direct calculation of the standard deviation:
\begin{quote}
The standard deviation of \texttt{speed} in \texttt{cars} is 5.2876444.
\end{quote}
One last neat feature is the use of the \texttt{ifelse} conditional statement which can be used to output text depending on the result of an \textbf{R} calculation:
\begin{quote}
The standard deviation is less than 6.
\end{quote}
Note the use of \texttt{\textgreater{}} here, which signifies a quotation environment that will be indented.

As you see with \texttt{\$2\ \textbackslash{}pi\$} above, mathematics can be added by surrounding the mathematical text with dollar signs. More examples of this are in \protect\hyperlink{math-sci}{Mathematics and Science} if you uncomment the code in \protect\hyperlink{math}{Math}.

\hypertarget{including-plots}{%
\section{Including plots}\label{including-plots}}

You can also embed plots. For example, here is a way to use the base \textbf{R} graphics package to produce a plot using the built-in \texttt{pressure} dataset:

\includegraphics{thesis_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo=FALSE} parameter was added to the code chunk to prevent printing of the \textbf{R} code that generated the plot. There are plenty of other ways to add chunk options. More information is available at \url{http://yihui.name/knitr/options/}.

Another useful chunk option is the setting of \texttt{cache=TRUE} as you see here. If document rendering becomes time consuming due to long computations or plots that are expensive to generate you can use knitr caching to improve performance. Later in this file, you'll see a way to reference plots created in \textbf{R} or external figures.

\hypertarget{loading-and-exploring-data}{%
\section{Loading and exploring data}\label{loading-and-exploring-data}}

Included in this template is a file called \texttt{flights.csv}. This file includes a subset of the larger dataset of information about all flights that departed from Seattle and Portland in 2014. More information about this dataset and its \textbf{R} package is available at \url{http://github.com/ismayc/pnwflights14}. This subset includes only Portland flights and only rows that were complete with no missing values. Merges were also done with the \texttt{airports} and \texttt{airlines} data sets in the \texttt{pnwflights14} package to get more descriptive airport and airline names.

We can load in this data set using the following command:
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights <{-}}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data/flights.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
The data is now stored in the data frame called \texttt{flights} in \textbf{R}. To get a better feel for the variables included in this dataset we can use a variety of functions. Here we can see the dimensions (rows by columns) and also the names of the columns.
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{dim}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
[1] 52808    16
\end{verbatim}
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{names}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
 [1] "month"        "day"          "dep_time"     "dep_delay"    "arr_time"    
 [6] "arr_delay"    "carrier"      "tailnum"      "flight"       "dest"        
[11] "air_time"     "distance"     "hour"         "minute"       "carrier_name"
[16] "dest_name"   
\end{verbatim}
Another good idea is to take a look at the dataset in table form. With this dataset having more than 50,000 rows, we won't explicitly show the results of the command here. I recommend you enter the command into the Console \textbf{\emph{after}} you have run the \textbf{R} chunks above to load the data into \textbf{R}.
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{View}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
While not required, it is highly recommended you use the \texttt{dplyr} package to manipulate and summarize your data set as needed. It uses a syntax that is easy to understand using chaining operations. Below I've created a few examples of using \texttt{dplyr} to get information about the Portland flights in 2014. You will also see the use of the \texttt{ggplot2} package, which produces beautiful, high-quality academic visuals.

We begin by checking to ensure that needed packages are installed and then we load them into our current working environment:
\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# List of packages required for this analysis}
\NormalTok{pkg <{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{, }\StringTok{"ggplot2"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"bookdown"}\NormalTok{, }\StringTok{"devtools"}\NormalTok{)}
\CommentTok{\# Check if packages are not installed and assign the}
\CommentTok{\# names of the packages not installed to the variable new.pkg}
\NormalTok{new.pkg <{-}}\StringTok{ }\NormalTok{pkg[}\OperatorTok{!}\NormalTok{(pkg }\OperatorTok{\%in\%}\StringTok{ }\KeywordTok{installed.packages}\NormalTok{())]}
\CommentTok{\# If there are any packages in the list that aren\textquotesingle{}t installed,}
\CommentTok{\# install them}
\ControlFlowTok{if}\NormalTok{ (}\KeywordTok{length}\NormalTok{(new.pkg))}
  \KeywordTok{install.packages}\NormalTok{(new.pkg, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\CommentTok{\# Load packages (thesisdown will load all of the packages as well)}
\KeywordTok{library}\NormalTok{(thesisdown)}
\end{Highlighting}
\end{Shaded}
\clearpage

The example we show here does the following:
\begin{itemize}
\item
  Selects only the \texttt{carrier\_name} and \texttt{arr\_delay} from the \texttt{flights} dataset and then assigns this subset to a new variable called \texttt{flights2}.
\item
  Using \texttt{flights2}, we determine the largest arrival delay for each of the carriers.
\end{itemize}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights2 <{-}}\StringTok{ }\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(carrier\_name, arr\_delay)}
\NormalTok{max\_delays <{-}}\StringTok{ }\NormalTok{flights2 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{group\_by}\NormalTok{(carrier\_name) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{max\_arr\_delay =} \KeywordTok{max}\NormalTok{(arr\_delay, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{))}
\end{Highlighting}
\end{Shaded}
A useful function in the \texttt{knitr} package for making nice tables in \emph{R Markdown} is called \texttt{kable}. It is much easier to use than manually entering values into a table by copying and pasting values into Excel or LaTeX. This again goes to show how nice reproducible documents can be! (Note the use of \texttt{results="asis"}, which will produce the table instead of the code to create the table.) The \texttt{caption.short} argument is used to include a shorter title to appear in the List of Tables.
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{kable}\NormalTok{(max\_delays, }
      \DataTypeTok{col.names =} \KeywordTok{c}\NormalTok{(}\StringTok{"Airline"}\NormalTok{, }\StringTok{"Max Arrival Delay"}\NormalTok{),}
      \DataTypeTok{caption =} \StringTok{"Maximum Delays by Airline"}\NormalTok{,}
      \DataTypeTok{caption.short =} \StringTok{"Max Delays by Airline"}\NormalTok{,}
      \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
      \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{longtable}[t]{lr}
\caption[Max Delays by Airline]{\label{tab:maxdelays}Maximum Delays by Airline}\\
\toprule
Airline & Max Arrival Delay\\
\midrule
Alaska Airlines Inc. & 338\\
American Airlines Inc. & 1539\\
Delta Air Lines Inc. & 651\\
Frontier Airlines Inc. & 575\\
Hawaiian Airlines Inc. & 407\\
\addlinespace
JetBlue Airways & 273\\
SkyWest Airlines Inc. & 421\\
Southwest Airlines Co. & 694\\
United Air Lines Inc. & 472\\
US Airways Inc. & 347\\
\addlinespace
Virgin America & 366\\
\bottomrule
\end{longtable}
The last two options make the table a little easier-to-read.

We can further look into the properties of the largest value here for American Airlines Inc.~To do so, we can isolate the row corresponding to the arrival delay of 1539 minutes for American in our original \texttt{flights} dataset.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(arr\_delay }\OperatorTok{==}\StringTok{ }\DecValTok{1539}\NormalTok{, }
\NormalTok{                  carrier\_name }\OperatorTok{==}\StringTok{ "American Airlines Inc."}\NormalTok{) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\KeywordTok{c}\NormalTok{(month, day, carrier, dest\_name, hour, }
\NormalTok{            minute, carrier\_name, arr\_delay))}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
  dep_time dep_delay arr_time tailnum flight dest air_time distance
1     1403      1553     1934  N595AA   1568  DFW      182     1616
\end{verbatim}
We see that the flight occurred on March 3rd and departed a little after 2 PM on its way to Dallas/Fort Worth. Lastly, we show how we can visualize the arrival delay of all departing flights from Portland on March 3rd against time of departure.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(month }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{, day }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ dep\_time, }\DataTypeTok{y =}\NormalTok{ arr\_delay)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom\_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}
\includegraphics{thesis_files/figure-latex/march3plot-1.pdf}

\hypertarget{additional-resources}{%
\section{Additional resources}\label{additional-resources}}
\begin{itemize}
\item
  \emph{Markdown} Cheatsheet - \url{https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet}
\item
  \emph{R Markdown} Reference Guide - \url{https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}
\item
  Introduction to \texttt{dplyr} - \url{https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html}
\item
  \texttt{ggplot2} Documentation - \url{http://docs.ggplot2.org/current/}
\end{itemize}
\hypertarget{math-sci}{%
\chapter{Mathematics and Science}\label{math-sci}}

\hypertarget{math}{%
\section{Math}\label{math}}

\TeX~is the best way to typeset mathematics. Donald Knuth designed \TeX~when he got frustrated at how long it was taking the typesetters to finish his book, which contained a lot of mathematics. One nice feature of \emph{R Markdown} is its ability to read LaTeX code directly.

If you are doing a thesis that will involve lots of math, you will want to read the following section which has been commented out. If you're not going to use math, skip over or delete this next commented section.

\hypertarget{chemistry-101-symbols}{%
\section{Chemistry 101: Symbols}\label{chemistry-101-symbols}}

Chemical formulas will look best if they are not italicized. Get around math mode's automatic italicizing in LaTeX by using the argument \texttt{\$\textbackslash{}mathrm\{formula\ here\}\$}, with your formula inside the curly brackets. (Notice the use of the backticks here which enclose text that acts as code.)

So, \(\mathrm{Fe_2^{2+}Cr_2O_4}\) is written \texttt{\$\textbackslash{}mathrm\{Fe\_2\^{}\{2+\}Cr\_2O\_4\}\$}.

\noindent Exponent or Superscript: \(\mathrm{O^-}\)

\noindent Subscript: \(\mathrm{CH_4}\)

To stack numbers or letters as in \(\mathrm{Fe_2^{2+}}\), the subscript is defined first, and then the superscript is defined.

\noindent Bullet: CuCl \(\bullet\) \(\mathrm{7H_{2}O}\)

\noindent Delta: \(\Delta\)

\noindent Reaction Arrows: \(\longrightarrow\) or \(\xrightarrow{solution}\)

\noindent Resonance Arrows: \(\leftrightarrow\)

\noindent Reversible Reaction Arrows: \(\rightleftharpoons\)

\hypertarget{typesetting-reactions}{%
\subsection{Typesetting reactions}\label{typesetting-reactions}}

You may wish to put your reaction in an equation environment, which means that LaTeX will place the reaction where it fits and will number the equations for you.
\begin{equation}
  \mathrm{C_6H_{12}O_6  + 6O_2} \longrightarrow \mathrm{6CO_2 + 6H_2O}
  \label{eq:reaction}
\end{equation}
We can reference this combustion of glucose reaction via Equation \eqref{eq:reaction}.

\hypertarget{other-examples-of-reactions}{%
\subsection{Other examples of reactions}\label{other-examples-of-reactions}}

\(\mathrm{NH_4Cl_{(s)}}\) \(\rightleftharpoons\) \(\mathrm{NH_{3(g)}+HCl_{(g)}}\)

\noindent \(\mathrm{MeCH_2Br + Mg}\) \(\xrightarrow[below]{above}\) \(\mathrm{MeCH_2\bullet Mg \bullet Br}\)

\hypertarget{physics}{%
\section{Physics}\label{physics}}

Many of the symbols you will need can be found on the math page \url{http://web.reed.edu/cis/help/latex/math.html} and the Comprehensive LaTeX Symbol Guide (\url{http://mirror.utexas.edu/ctan/info/symbols/comprehensive/symbols-letter.pdf}).

\hypertarget{biology}{%
\section{Biology}\label{biology}}

You will probably find the resources at \url{http://www.lecb.ncifcrf.gov/~toms/latex.html} helpful, particularly the links to bsts for various journals. You may also be interested in TeXShade for nucleotide typesetting (\url{http://homepages.uni-tuebingen.de/beitz/txe.html}). Be sure to read the proceeding chapter on graphics and tables.

\hypertarget{ref-labels}{%
\chapter{Tables, Graphics, References, and Labels}\label{ref-labels}}

\hypertarget{tables}{%
\section{Tables}\label{tables}}

In addition to the tables that can be automatically generated from a data frame in \textbf{R} that you saw in \protect\hyperlink{rmd-basics}{R Markdown Basics} using the \texttt{kable} function, you can also create tables using \emph{pandoc}. (More information is available at \url{http://pandoc.org/README.html\#tables}.) This might be useful if you don't have values specifically stored in \textbf{R}, but you'd like to display them in table form. Below is an example. Pay careful attention to the alignment in the table and hyphens to create the rows and columns.
\begin{longtable}[]{@{}ccc@{}}
\caption{\label{tab:inher} Correlation of Inheritance Factors for Parents and Child}\tabularnewline
\toprule
\begin{minipage}[b]{0.29\columnwidth}\centering
Factors\strut
\end{minipage} & \begin{minipage}[b]{0.46\columnwidth}\centering
Correlation between Parents \& Child\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Inherited\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.29\columnwidth}\centering
Factors\strut
\end{minipage} & \begin{minipage}[b]{0.46\columnwidth}\centering
Correlation between Parents \& Child\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Inherited\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.29\columnwidth}\centering
Education\strut
\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
-0.49\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
Yes\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\centering
Socio-Economic Status\strut
\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
0.28\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
Slight\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\centering
Income\strut
\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
0.08\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
No\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\centering
Family Size\strut
\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
0.18\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
Slight\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\centering
Occupational Prestige\strut
\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
0.21\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
Slight\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
We can also create a link to the table by doing the following: Table \ref{tab:inher}. If you go back to \protect\hyperlink{loading-and-exploring-data}{Loading and exploring data} and look at the \texttt{kable} table, we can create a reference to this max delays table too: Table \ref{tab:maxdelays}. The addition of the \texttt{(\textbackslash{}\#tab:inher)} option to the end of the table caption allows us to then make a reference to Table \texttt{\textbackslash{}@ref(tab:label)}. Note that this reference could appear anywhere throughout the document after the table has appeared.

\clearpage

\hypertarget{figures}{%
\section{Figures}\label{figures}}

If your thesis has a lot of figures, \emph{R Markdown} might behave better for you than that other word processor. One perk is that it will automatically number the figures accordingly in each chapter. You'll also be able to create a label for each figure, add a caption, and then reference the figure in a way similar to what we saw with tables earlier. If you label your figures, you can move the figures around and \emph{R Markdown} will automatically adjust the numbering for you. No need for you to remember! So that you don't have to get too far into LaTeX to do this, a couple \textbf{R} functions have been created for you to assist. You'll see their use below.

In the \textbf{R} chunk below, we will load in a picture stored as \texttt{reed.jpg} in our main directory. We then give it the caption of ``Reed logo'', the label of ``reedlogo'', and specify that this is a figure. Make note of the different \textbf{R} chunk options that are given in the R Markdown file (not shown in the knitted document).
\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{include\_graphics}\NormalTok{(}\DataTypeTok{path =} \StringTok{"figure/reed.jpg"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{figure}
\centering
\includegraphics{figure/reed.jpg}
\caption{\label{fig:reedlogo}Reed logo}
\end{figure}
Here is a reference to the Reed logo: Figure \ref{fig:reedlogo}. Note the use of the \texttt{fig:} code here. By naming the \textbf{R} chunk that contains the figure, we can then reference that figure later as done in the first sentence here. We can also specify the caption for the figure via the R chunk option \texttt{fig.cap}.

\clearpage

Below we will investigate how to save the output of an \textbf{R} plot and label it in a way similar to that done above. Recall the \texttt{flights} dataset from Chapter \ref{rmd-basics}. (Note that we've shown a different way to reference a section or chapter here.) We will next explore a bar graph with the mean flight departure delays by airline from Portland for 2014. Note also the use of the \texttt{scale} parameter which is discussed on the next page.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{group\_by}\NormalTok{(carrier) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{mean\_dep\_delay =} \KeywordTok{mean}\NormalTok{(dep\_delay)) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ carrier, }\DataTypeTok{y =}\NormalTok{ mean\_dep\_delay)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom\_bar}\NormalTok{(}\DataTypeTok{position =} \StringTok{"identity"}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"red"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{figure}
\centering
\includegraphics{thesis_files/figure-latex/delaysboxplot-1.pdf}
\caption{\label{fig:delaysboxplot}Mean Delays by Airline}
\end{figure}
Here is a reference to this image: Figure \ref{fig:delaysboxplot}.

A table linking these carrier codes to airline names is available at \url{https://github.com/ismayc/pnwflights14/blob/master/data/airlines.csv}.

\clearpage

Next, we will explore the use of the \texttt{out.extra} chunk option, which can be used to shrink or expand an image loaded from a file by specifying \texttt{"scale=\ "}. Here we use the mathematical graph stored in the ``subdivision.pdf'' file.
\begin{figure}
\includegraphics[scale=0.75]{figure/subdivision} \caption{Subdiv. graph}\label{fig:subd}
\end{figure}
Here is a reference to this image: Figure \ref{fig:subd}. Note that \texttt{echo=FALSE} is specified so that the \textbf{R} code is hidden in the document.

\textbf{More Figure Stuff}

Lastly, we will explore how to rotate and enlarge figures using the \texttt{out.extra} chunk option. (Currently this only works in the PDF version of the book.)
\begin{figure}
\includegraphics[angle=180, scale=1.1]{figure/subdivision} \caption{A Larger Figure, Flipped Upside Down}\label{fig:subd2}
\end{figure}
As another example, here is a reference: Figure \ref{fig:subd2}.

\hypertarget{footnotes-and-endnotes}{%
\section{Footnotes and Endnotes}\label{footnotes-and-endnotes}}

You might want to footnote something.\footnote{footnote text} The footnote will be in a smaller font and placed appropriately. Endnotes work in much the same way. More information can be found about both on the CUS site or feel free to reach out to \href{mailto:data@reed.edu}{\nolinkurl{data@reed.edu}}.

\hypertarget{bibliographies}{%
\section{Bibliographies}\label{bibliographies}}

Of course you will need to cite things, and you will probably accumulate an armful of sources. There are a variety of tools available for creating a bibliography database (stored with the .bib extension). In addition to BibTeX suggested below, you may want to consider using the free and easy-to-use tool called Zotero. The Reed librarians have created Zotero documentation at \url{http://libguides.reed.edu/citation/zotero}. In addition, a tutorial is available from Middlebury College at \url{http://sites.middlebury.edu/zoteromiddlebury/}.

\emph{R Markdown} uses \emph{pandoc} (\url{http://pandoc.org/}) to build its bibliographies. One nice caveat of this is that you won't have to do a second compile to load in references as standard LaTeX requires. To cite references in your thesis (after creating your bibliography database), place the reference name inside square brackets and precede it by the ``at'' symbol. For example, here's a reference to a book about worrying: (Molina \& Borkovec, 1994). This \texttt{Molina1994} entry appears in a file called \texttt{thesis.bib} in the \texttt{bib} folder. This bibliography database file was created by a program called BibTeX. You can call this file something else if you like (look at the YAML header in the main .Rmd file) and, by default, is to placed in the \texttt{bib} folder.

For more information about BibTeX and bibliographies, see our CUS site (\url{http://web.reed.edu/cis/help/latex/index.html})\footnote{Reed~College (2007)}. There are three pages on this topic: \emph{bibtex} (which talks about using BibTeX, at \url{http://web.reed.edu/cis/help/latex/bibtex.html}), \emph{bibtexstyles} (about how to find and use the bibliography style that best suits your needs, at \url{http://web.reed.edu/cis/help/latex/bibtexstyles.html}) and \emph{bibman} (which covers how to make and maintain a bibliography by hand, without BibTeX, at \url{http://web.reed.edu/cis/help/latex/bibman.html}). The last page will not be useful unless you have only a few sources.

If you look at the YAML header at the top of the main .Rmd file you can see that we can specify the style of the bibliography by referencing the appropriate csl file. You can download a variety of different style files at \url{https://www.zotero.org/styles}. Make sure to download the file into the csl folder.

\textbf{Tips for Bibliographies}
\begin{itemize}
\tightlist
\item
  Like with thesis formatting, the sooner you start compiling your bibliography for something as large as thesis, the better. Typing in source after source is mind-numbing enough; do you really want to do it for hours on end in late April? Think of it as procrastination.
\item
  The cite key (a citation's label) needs to be unique from the other entries.
\item
  When you have more than one author or editor, you need to separate each author's name by the word ``and'' e.g.~\texttt{Author\ =\ \{Noble,\ Sam\ and\ Youngberg,\ Jessica\},}.
\item
  Bibliographies made using BibTeX (whether manually or using a manager) accept LaTeX markup, so you can italicize and add symbols as necessary.
\item
  To force capitalization in an article title or where all lowercase is generally used, bracket the capital letter in curly braces.
\item
  You can add a Reed Thesis citation\footnote{Noble (2002)} option. The best way to do this is to use the phdthesis type of citation, and use the optional ``type'' field to enter ``Reed thesis'' or ``Undergraduate thesis.''
\end{itemize}
\hypertarget{anything-else}{%
\section{Anything else?}\label{anything-else}}

If you'd like to see examples of other things in this template, please contact the Data @ Reed team (email \href{mailto:data@reed.edu}{\nolinkurl{data@reed.edu}}) with your suggestions. We love to see people using \emph{R Markdown} for their theses, and are happy to help.

\hypertarget{conclusion}{%
\chapter*{Conclusion}\label{conclusion}}
\addcontentsline{toc}{chapter}{Conclusion}

If we don't want Conclusion to have a chapter number next to it, we can add the \texttt{\{-\}} attribute.

\textbf{More info}

And here's some other random info: the first paragraph after a chapter title or section head \emph{shouldn't be} indented, because indents are to tell the reader that you're starting a new paragraph. Since that's obvious after a chapter or section title, proper typesetting doesn't add an indent there.

\appendix

\hypertarget{the-first-appendix}{%
\chapter{The First Appendix}\label{the-first-appendix}}

This first appendix includes all of the R chunks of code that were hidden throughout the document (using the \texttt{include\ =\ FALSE} chunk tag) to help with readibility and/or setup.

\textbf{In the main Rmd file}
\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# This chunk ensures that the thesisdown package is}
\CommentTok{\# installed and loaded. This thesisdown package includes}
\CommentTok{\# the template files for the thesis.}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools))}
  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(thesisdown))}
\NormalTok{  devtools}\OperatorTok{::}\KeywordTok{install\_github}\NormalTok{(}\StringTok{"ismayc/thesisdown"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(thesisdown)}
\end{Highlighting}
\end{Shaded}
\textbf{In Chapter \ref{ref-labels}:}
\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# This chunk ensures that the thesisdown package is}
\CommentTok{\# installed and loaded. This thesisdown package includes}
\CommentTok{\# the template files for the thesis and also two functions}
\CommentTok{\# used for labeling and referencing}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools))}
  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(dplyr))}
    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(ggplot2))}
    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"ggplot2"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(ggplot2))}
    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"bookdown"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(thesisdown))\{}
  \KeywordTok{library}\NormalTok{(devtools)}
\NormalTok{  devtools}\OperatorTok{::}\KeywordTok{install\_github}\NormalTok{(}\StringTok{"ismayc/thesisdown"}\NormalTok{)}
\NormalTok{  \}}
\KeywordTok{library}\NormalTok{(thesisdown)}
\NormalTok{flights <{-}}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data/flights.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\hypertarget{the-second-appendix-for-fun}{%
\chapter{The Second Appendix, for Fun}\label{the-second-appendix-for-fun}}

\backmatter

\hypertarget{references}{%
\chapter*{References}\label{references}}
\addcontentsline{toc}{chapter}{References}

\markboth{References}{References}

\noindent

\setlength{\parindent}{-0.20in}
\setlength{\leftskip}{0.20in}
\setlength{\parskip}{8pt}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-angel2000}{}%
Angel, E. (2000). \emph{Interactive computer graphics : A top-down approach with opengl}. Boston, MA: Addison Wesley Longman.

\leavevmode\hypertarget{ref-angel2001}{}%
Angel, E. (2001a). \emph{Batch-file computer graphics : A bottom-up approach with quicktime}. Boston, MA: Wesley Addison Longman.

\leavevmode\hypertarget{ref-angel2002a}{}%
Angel, E. (2001b). \emph{Test second book by angel}. Boston, MA: Wesley Addison Longman.

\leavevmode\hypertarget{ref-Molina1994}{}%
Molina, S. T., \& Borkovec, T. D. (1994). The Penn State worry questionnaire: Psychometric properties and associated characteristics. In G. C. L. Davey \& F. Tallis (Eds.), \emph{Worrying: Perspectives on theory, assessment and treatment} (pp. 265--283). New York: Wiley.

\leavevmode\hypertarget{ref-noble2002}{}%
Noble, S. G. (2002). \emph{Turning images into simple line-art} (Undergraduate thesis). Reed College.

\leavevmode\hypertarget{ref-reedweb2007}{}%
Reed~College. (2007). LaTeX your document. Retrieved from \url{http://web.reed.edu/cis/help/LaTeX/index.html}
\end{cslreferences}

% Index?

\end{document}

### 2020-02-04 manuscript/drafts/manuscript.Rmd
a lot of stuff: fix bugs add bookdown

--- 2020-01-20 manuscript/manuscript.Rmd
@@
 # configurations table 
-tab <- lapply(params, FUN = function(x) paste(x, collapse = ", "))
+tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
 tab <- do.call(rbind, tab)
-colnames(tab) <- c("configurations")
+colnames(tab) <- c("Configurations")
+
 ```
@@
 ```{r}
-
 # combinations table
@@
 ```{r}
+names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
 combins %>%
   kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
-  kable_styling(latex_options = c("repeat_header")) %>%
-  footnote(general = "nb model only works with tfidf feature extraction strategy. " )
+  kable_styling(latex_options = c("repeat_header")) 
 ```

### 2020-02-04 manuscript/index/05-appendix.Rmd
a lot of stuff: fix bugs add bookdown

--- 2020-01-23 definitions.Rmd
@@
----
-title: "Definition list"
-author: "Gerbrich Ferdinands"
-date: "1/20/2020"
-output: pdf_document
----
+`r if(knitr:::is_latex_output()) '\\appendix'`
 
+`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
+
+<!--
+If you feel it necessary to include an appendix, it goes here.
+-->
+
+# List of Definitions
 Model.
@@
 
-        { some code, part of Definition 2 }
+        some code, part of Definition 2
 
@@
 Query Strategy 
-:   def
+:   The way papers are queried to the researcher
 
-        { some code, part of Definition 2 }
+        query_strategy
 
-        add paragraph here
-
-    Uncertainty sampling.
+    Uncertainty sampling
     :  Selects the least sure instances for labelling.
 
-    Maximum sampling.
+    Maximum sampling
     :  Selects the samples with the highest prediction probability.
@@
 
-        { some code, part of Definition x }
+        feature_extraction
 
@@
     sbert
+
+<!-- # The Last Appendix -->
+
+<!-- This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup. -->
+
+<!-- **In the main Rmd file** -->
+
+<!-- ```{r ref.label='include_packages', results='hide', echo = TRUE} -->
+<!-- ``` -->
+
+<!-- **In Chapter \@ref(ref-labels):** -->
+
+<!-- ```{r ref.label='include_packages_2', results='hide', echo = TRUE} -->
+<!-- ``` -->

### 2020-02-04 manuscript/drafts/definitions.Rmd

--- 2020-01-23 definitions.Rmd
@@
 
+# List of definitions
+
 Model.

### 2020-02-04 manuscript/index/_book/thesis.tex

--- 2020-01-28 manuscript/index/thesis.tex
@@
 %\bibliography{thesis}
+
+% Gerbrich: try tro solve clsreferences. 
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
 
@@
 % To pass between YAML and LaTeX the dollar signs are added by CII
-\title{My Master thesis}
+\title{My Final College Paper}
 \author{Gerbrich Ferdinands}
@@
 \date{May 2020}
-\division{Methodolgy and Statistics}
+\division{Faculty of Social Sciences}
 \advisor{prof. dr. Rens van de Schoot}
 \institution{Utrecht University}
-\degree{Master of Science}
+\degree{Bachelor of Arts}
 %If you have two advisors for some reason, you can use the following
 % Uncommented out by CII
+\altadvisor{Jonathan de Bruin, Raoul Schram}
 % End of CII addition
@@
 %%% Remember to use the correct department!
-\department{Faculty of Social Sciences}
+\department{Mathematics}
 % if you're writing a thesis in an interdisciplinary major,
@@
 \Dedication{
-
+You can have a dedication here if you wish.
 }
@@
   \end{abstract}
-
+  \begin{dedication}
+    You can have a dedication here if you wish.
+  \end{dedication}
 \mainmatter % here the regular arabic numbering starts
@@
 
-\hypertarget{rmd-basics}{%
-\chapter{R Markdown Basics}\label{rmd-basics}}
-
-Here is a brief introduction into using \emph{R Markdown}.
-\emph{Markdown} is a simple formatting syntax for authoring HTML, PDF, and MS Word documents.
-\emph{R Markdown} provides the flexibility of \emph{Markdown} with the implementation of \textbf{R} input and output.
-For more details on using \emph{R Markdown} see \url{http://rmarkdown.rstudio.com}.
-
-Be careful with your spacing in \emph{Markdown} documents.
-While whitespace largely is ignored, it does at times give \emph{Markdown} signals as to how to proceed.
-As a habit, try to keep everything left aligned whenever possible, especially as you type a new paragraph.
-In other words, there is no need to indent basic text in the Rmd document (in fact, it might cause your text to do funny things if you do).
-
-\hypertarget{lists}{%
-\section{Lists}\label{lists}}
-
-It's easy to create a list. It can be unordered like
-\begin{itemize}
-\tightlist
-\item
-  Item 1
-\item
-  Item 2
-\end{itemize}
-or it can be ordered like
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Item 1
-\item
-  Item 2
-\end{enumerate}
-Notice that I intentionally mislabeled Item 2 as number 4. \emph{Markdown} automatically figures this out! You can put any numbers in the list and it will create the list. Check it out below.
-
-To create a sublist, just indent the values a bit (at least four spaces or a tab). (Here's one case where indentation is key!)
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Item 1
-\item
-  Item 2
-\item
-  Item 3
-  \begin{itemize}
-  \tightlist
-  \item
-    Item 3a
-  \item
-    Item 3b
-  \end{itemize}
-\end{enumerate}
-\hypertarget{line-breaks}{%
-\section{Line breaks}\label{line-breaks}}
-
-Make sure to add white space between lines if you'd like to start a new paragraph. Look at what happens below in the outputted document if you don't:
-
-Here is the first sentence. Here is another sentence. Here is the last sentence to end the paragraph.
-This should be a new paragraph.
-
-\emph{Now for the correct way:}
-
-Here is the first sentence. Here is another sentence. Here is the last sentence to end the paragraph.
-
-This should be a new paragraph.
-
-\hypertarget{r-chunks}{%
-\section{R chunks}\label{r-chunks}}
-
-When you click the \textbf{Knit} button above a document will be generated that includes both content as well as the output of any embedded \textbf{R} code chunks within the document.
-You can embed an \textbf{R} code chunk like this (\texttt{cars} is a built-in \textbf{R} dataset):
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{summary}\NormalTok{(cars)}
-\end{Highlighting}
-\end{Shaded}
-\begin{verbatim}
-     speed           dist       
- Min.   : 4.0   Min.   :  2.00  
- 1st Qu.:12.0   1st Qu.: 26.00  
- Median :15.0   Median : 36.00  
- Mean   :15.4   Mean   : 42.98  
- 3rd Qu.:19.0   3rd Qu.: 56.00  
- Max.   :25.0   Max.   :120.00  
-\end{verbatim}
-\hypertarget{inline-code}{%
-\section{Inline code}\label{inline-code}}
-
-If you'd like to put the results of your analysis directly into your discussion, add inline code like this:
-\begin{quote}
-The \texttt{cos} of \(2 \pi\) is 1.
-\end{quote}
-Another example would be the direct calculation of the standard deviation:
-\begin{quote}
-The standard deviation of \texttt{speed} in \texttt{cars} is 5.2876444.
-\end{quote}
-One last neat feature is the use of the \texttt{ifelse} conditional statement which can be used to output text depending on the result of an \textbf{R} calculation:
-\begin{quote}
-The standard deviation is less than 6.
-\end{quote}
-Note the use of \texttt{\textgreater{}} here, which signifies a quotation environment that will be indented.
-
-As you see with \texttt{\$2\ \textbackslash{}pi\$} above, mathematics can be added by surrounding the mathematical text with dollar signs.
-More examples of this are in \protect\hyperlink{math-sci}{Mathematics and Science} if you uncomment the code in \protect\hyperlink{math}{Math}.
-
-\hypertarget{including-plots}{%
-\section{Including plots}\label{including-plots}}
-
-You can also embed plots. For example, here is a way to use the base \textbf{R} graphics package to produce a plot using the built-in \texttt{pressure} dataset:
-
-\includegraphics{thesis_files/figure-latex/pressure-1.pdf}
-
-Note that the \texttt{echo=FALSE} parameter was added to the code chunk to prevent printing of the \textbf{R} code that generated the plot.
-There are plenty of other ways to add chunk options.
-More information is available at \url{http://yihui.name/knitr/options/}.
-
-Another useful chunk option is the setting of \texttt{cache=TRUE} as you see here.
-If document rendering becomes time consuming due to long computations or plots that are expensive to generate you can use knitr caching to improve performance.
-Later in this file, you'll see a way to reference plots created in \textbf{R} or external figures.
-
-\hypertarget{loading-and-exploring-data}{%
-\section{Loading and exploring data}\label{loading-and-exploring-data}}
-
-Included in this template is a file called \texttt{flights.csv}.
-This file includes a subset of the larger dataset of information about all flights that departed from Seattle and Portland in 2014.
-More information about this dataset and its \textbf{R} package is available at \url{http://github.com/ismayc/pnwflights14}.
-This subset includes only Portland flights and only rows that were complete with no missing values.
-Merges were also done with the \texttt{airports} and \texttt{airlines} data sets in the \texttt{pnwflights14} package to get more descriptive airport and airline names.
-
-We can load in this data set using the following command:
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{flights <{-}}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data/flights.csv"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-The data is now stored in the data frame called \texttt{flights} in \textbf{R}.
-To get a better feel for the variables included in this dataset we can use a variety of functions.
-Here we can see the dimensions (rows by columns) and also the names of the columns.
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{dim}\NormalTok{(flights)}
-\end{Highlighting}
-\end{Shaded}
-\begin{verbatim}
-[1] 52808    16
-\end{verbatim}
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{names}\NormalTok{(flights)}
-\end{Highlighting}
-\end{Shaded}
-\begin{verbatim}
- [1] "month"        "day"          "dep_time"     "dep_delay"    "arr_time"    
- [6] "arr_delay"    "carrier"      "tailnum"      "flight"       "dest"        
-[11] "air_time"     "distance"     "hour"         "minute"       "carrier_name"
-[16] "dest_name"   
-\end{verbatim}
-Another good idea is to take a look at the dataset in table form.
-With this dataset having more than 50,000 rows, we won't explicitly show the results of the command here.
-I recommend you enter the command into the Console \textbf{\emph{after}} you have run the \textbf{R} chunks above to load the data into \textbf{R}.
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{View}\NormalTok{(flights)}
-\end{Highlighting}
-\end{Shaded}
-While not required, it is highly recommended you use the \texttt{dplyr} package to manipulate and summarize your data set as needed.
-It uses a syntax that is easy to understand using chaining operations.
-Below I've created a few examples of using \texttt{dplyr} to get information about the Portland flights in 2014.
-You will also see the use of the \texttt{ggplot2} package, which produces beautiful, high-quality academic visuals.
-
-We begin by checking to ensure that needed packages are installed and then we load them into our current working environment:
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# List of packages required for this analysis}
-\NormalTok{pkg <{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{, }\StringTok{"ggplot2"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"bookdown"}\NormalTok{, }\StringTok{"devtools"}\NormalTok{)}
-\CommentTok{\# Check if packages are not installed and assign the}
-\CommentTok{\# names of the packages not installed to the variable new.pkg}
-\NormalTok{new.pkg <{-}}\StringTok{ }\NormalTok{pkg[}\OperatorTok{!}\NormalTok{(pkg }\OperatorTok{\%in\%}\StringTok{ }\KeywordTok{installed.packages}\NormalTok{())]}
-\CommentTok{\# If there are any packages in the list that aren\textquotesingle{}t installed,}
-\CommentTok{\# install them}
-\ControlFlowTok{if}\NormalTok{ (}\KeywordTok{length}\NormalTok{(new.pkg))}
-  \KeywordTok{install.packages}\NormalTok{(new.pkg, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\CommentTok{\# Load packages (thesisdown will load all of the packages as well)}
-\KeywordTok{library}\NormalTok{(thesisdown)}
-\end{Highlighting}
-\end{Shaded}
-\clearpage
-
-The example we show here does the following:
+\hypertarget{ASReview}{%
+\chapter{ASReview}\label{ASReview}}
 \begin{itemize}
 \item
-  Selects only the \texttt{carrier\_name} and \texttt{arr\_delay} from the \texttt{flights} dataset and then assigns this subset to a new variable called \texttt{flights2}.
+  Importance of sound systematic reviews (meta)
 \item
-  Using \texttt{flights2}, we determine the largest arrival delay for each of the carriers.
+  Why it was built
+\item
+  Advantages over other types
+\item
+  Whereas first results look promising, there hasn't been conducted a full proof of concept
 \end{itemize}
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{flights2 <{-}}\StringTok{ }\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }
-\StringTok{  }\KeywordTok{select}\NormalTok{(carrier\_name, arr\_delay)}
-\NormalTok{max\_delays <{-}}\StringTok{ }\NormalTok{flights2 }\OperatorTok{\%>\%}\StringTok{ }
-\StringTok{  }\KeywordTok{group\_by}\NormalTok{(carrier\_name) }\OperatorTok{\%>\%}
-\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{max\_arr\_delay =} \KeywordTok{max}\NormalTok{(arr\_delay, }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-A useful function in the \texttt{knitr} package for making nice tables in \emph{R Markdown} is called \texttt{kable}.
-It is much easier to use than manually entering values into a table by copying and pasting values into Excel or LaTeX.
-This again goes to show how nice reproducible documents can be!
-(Note the use of \texttt{results="asis"}, which will produce the table instead of the code to create the table.) The \texttt{caption.short} argument is used to include a shorter title to appear in the List of Tables.
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{kable}\NormalTok{(max\_delays, }
-      \DataTypeTok{col.names =} \KeywordTok{c}\NormalTok{(}\StringTok{"Airline"}\NormalTok{, }\StringTok{"Max Arrival Delay"}\NormalTok{),}
-      \DataTypeTok{caption =} \StringTok{"Maximum Delays by Airline"}\NormalTok{,}
-      \DataTypeTok{caption.short =} \StringTok{"Max Delays by Airline"}\NormalTok{,}
-      \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
-      \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-\begin{longtable}[t]{lr}
-\caption[Max Delays by Airline]{\label{tab:maxdelays}Maximum Delays by Airline}\\
-\toprule
-Airline & Max Arrival Delay\\
-\midrule
-Alaska Airlines Inc. & 338\\
-American Airlines Inc. & 1539\\
-Delta Air Lines Inc. & 651\\
-Frontier Airlines Inc. & 575\\
-Hawaiian Airlines Inc. & 407\\
-\addlinespace
-JetBlue Airways & 273\\
-SkyWest Airlines Inc. & 421\\
-Southwest Airlines Co. & 694\\
-United Air Lines Inc. & 472\\
-US Airways Inc. & 347\\
-\addlinespace
-Virgin America & 366\\
-\bottomrule
-\end{longtable}
-The last two options make the table a little easier-to-read.
+Goals:
+- Save time
+- But also more systematic..?
 
-We can further look into the properties of the largest value here for American Airlines Inc.~To do so, we can isolate the row corresponding to the arrival delay of 1539 minutes for American in our original \texttt{flights} dataset.
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(arr\_delay }\OperatorTok{==}\StringTok{ }\DecValTok{1539}\NormalTok{, }
-\NormalTok{                  carrier\_name }\OperatorTok{==}\StringTok{ "American Airlines Inc."}\NormalTok{) }\OperatorTok{\%>\%}
-\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\KeywordTok{c}\NormalTok{(month, day, carrier, dest\_name, hour, }
-\NormalTok{            minute, carrier\_name, arr\_delay))}
-\end{Highlighting}
-\end{Shaded}
-\begin{verbatim}
-  dep_time dep_delay arr_time tailnum flight dest air_time distance
-1     1403      1553     1934  N595AA   1568  DFW      182     1616
-\end{verbatim}
-We see that the flight occurred on March 3rd and departed a little after 2 PM on its way to Dallas/Fort Worth.
-Lastly, we show how we can visualize the arrival delay of all departing flights from Portland on March 3rd against time of departure.
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(month }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{, day }\OperatorTok{==}\StringTok{ }\DecValTok{3}\NormalTok{) }\OperatorTok{\%>\%}
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ dep\_time, }\DataTypeTok{y =}\NormalTok{ arr\_delay)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom\_point}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-\includegraphics{thesis_files/figure-latex/march3plot-1.pdf}
+? Misses
 
-\hypertarget{additional-resources}{%
-\section{Additional resources}\label{additional-resources}}
-\begin{itemize}
-\item
-  \emph{Markdown} Cheatsheet - \url{https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet}
-\item
-  \emph{R Markdown} Reference Guide - \url{https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}
-\item
-  Introduction to \texttt{dplyr} - \url{https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html}
-\item
-  \texttt{ggplot2} Documentation - \url{http://docs.ggplot2.org/current/}
-\end{itemize}
 \hypertarget{math-sci}{%
@@
 
-In addition to the tables that can be automatically generated from a data frame in \textbf{R} that you saw in \protect\hyperlink{rmd-basics}{R Markdown Basics} using the \texttt{kable} function, you can also create tables using \emph{pandoc}.
+In addition to the tables that can be automatically generated from a data frame in \textbf{R} that you saw in {[}R Markdown Basics{]} using the \texttt{kable} function, you can also create tables using \emph{pandoc}.
 (More information is available at \url{http://pandoc.org/README.html\#tables}.) This might be useful if you don't have values specifically stored in \textbf{R}, but you'd like to display them in table form.
@@
 We can also create a link to the table by doing the following: Table \ref{tab:inher}.
-If you go back to \protect\hyperlink{loading-and-exploring-data}{Loading and exploring data} and look at the \texttt{kable} table, we can create a reference to this max delays table too: Table \ref{tab:maxdelays}.
+If you go back to {[}Loading and exploring data{]} and look at the \texttt{kable} table, we can create a reference to this max delays table too: Table \ref{tab:maxdelays}.
 The addition of the \texttt{(\textbackslash{}\#tab:inher)} option to the end of the table caption allows us to then make a reference to Table \texttt{\textbackslash{}@ref(tab:label)}.

### 2020-02-04 manuscript/index/index.Rmd

@@
 institution: 'Utrecht University'
-division: 'Methodolgy and Statistics'
+division: 'Faculty of Social Sciences'
 advisor: 'prof. dr. Rens van de Schoot'
 # If you have more two advisors, un-silence line 7
-#altadvisor: 'Your Other Advisor'
-department: 'Faculty of Social Sciences'
+altadvisor: 'Jonathan de Bruin, Raoul Schram'
+department: 'Methodology and Statistics'
 degree: 'Master of Science'
-title: 'My Master thesis'
+title: 'My thesis'
 knit: "bookdown::render_book"
@@
 output: 
-# thesisdown::thesis_pdf: default
-thesisdown::thesis_gitbook: default
-#  thesisdown::thesis_word: default
+#  thesisdown::thesis_pdf: default # yet fails to compile 
+  thesisdown::thesis_gitbook: default # creates html book in _book folder.  
+  thesisdown::thesis_word: default
 #  thesisdown::thesis_epub: default
@@
 # needed on the line after the `|`.
-acknowledgements: |
-  I want to thank a few people.
+#acknowledgements: |
+#  I want to thank a few people.
 #dedication: |
 #  You can have a dedication here if you wish. 
-preface: |
-  This is an example of a thesis setup to use the reed thesis document class
-  (for LaTeX) and the R bookdown package, in general.
+#preface: |
+#  This is an example of a thesis setup to use the reed thesis document class
+#  (for LaTeX) and the R bookdown package, in general.
 # Specify the location of the bibliography below
-bibliography: bib/thesis.bib
+bibliography: bib/asreview.bib
 # Download your specific csl file and refer to it in the line below.
@@
 
-<!-- 
-If you're still on the fence about using _R Markdown_, check out the resource for newbies available at <https://ismayc.github.io/rbasics-book/> or email us at <data@reed.edu>. 
--->
+- Importance of sound systematic reviews (meta)
+- Why it was built
+- Advantages over other types
 
-**Why use it?**
+- Whereas first results look promising, there hasn’t been conducted a full proof of concept
 
-_R Markdown_ creates a simple and straightforward way to interface with the beauty of LaTeX.
-Packages have been written in **R** to work directly with LaTeX to produce nicely formatting tables and paragraphs.
-In addition to creating a user friendly interface to LaTeX, _R Markdown_ also allows you to read in your data, to analyze it and to visualize it using **R** functions, and also to provide the documentation and commentary on the results of your project.
-Further, it allows for **R** results to be passed inline to the commentary of your results.
-You'll see more on this later.
+Goals: 
+- Save time 
+- But also more systematic..?
 
-<!-- 
-Having your code and commentary all together in one place has a plethora of benefits!
--->
-
-**Who should use it?**
-
-Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use _R Markdown_.
-Of particular use should be anyone in the sciences, but the user-friendly nature of _Markdown_ and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc.
-should make it of great benefit to nearly anyone writing a thesis project.
-
-**For additional help with bookdown** 
-Please visit [the free online bookdown reference guide](https://bookdown.org/yihui/bookdown/).
+? Misses

### 2020-02-04 manuscript/index/05-appendix.Rmd
update gitignore

@@
 
+# Parameter Configurations
+```{r}
+# load model parameters 
+source("R/asr-parameters.R")
+```
+
+```{r}
+# configurations table 
+tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
+tab <- do.call(rbind, tab)
+colnames(tab) <- c("Configurations")
+
+```
+
+```{r}
+# combinations table
+combins <- expand.grid(params) %>%
+  arrange(model, feature_extraction)
+
+# rows to drop
+droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
+combins <- combins[!droprows, ]
+```
+
+ASReview takes the following parameters/arguments:
+
+- number of training data (included/excluded)
+- a model
+- a query strategy
+- a balance strategy (fixed)
+- feature extraction
+
+```{r}
+kable(tab, "latex", booktabs = TRUE) %>%
+  kable_styling(full_width = FALSE) %>%
+  column_spec(2, width = "30em") 
+```
+
+This leads to  `r nrow(combins)` combinations of configurations.
+
+- Naive bayes only goes with tfidf feature extraction.
+- For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
+- This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.
+
+```{r}
+names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
+combins %>%
+  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
+  kable_styling(latex_options = c("repeat_header")) 
+```
+
 # List of Definitions
+
+Balance Strategy
+
 Model.

### 2020-02-04 manuscript/index/index.Rmd
update gitignore

@@
 output: 
-#  thesisdown::thesis_pdf: default # yet fails to compile 
+  thesisdown::thesis_pdf: default # yet fails to compile 
   thesisdown::thesis_gitbook: default # creates html book in _book folder.  
-  thesisdown::thesis_word: default
+#  thesisdown::thesis_word: default
 #  thesisdown::thesis_epub: default
@@
 library(thesisdown)
+
+knitr::opts_chunk$set(echo = FALSE)
+
+source("R/packages.R")
 ```

### 2020-02-04 manuscript/index/R/asr-parameters.R

@@ -1,0 +1,91 @@
+# Gerbrich Ferdinands, 14-01-2020
+# document all parameters in asreview software
+
+#path <- "~/Downloads/automated-systematic-review-unsupervised/asreview"
+
+#params <- list.files(path, recursive = TRUE, include.dirs = TRUE)
+
+# library(httr)
+# req <- GET("https://api.github.com/repos/qubixes/automated-systematic-review/tree/unsupervised")
+# stop_for_status(req)
+# filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
+# grep("/unsupervised", filelist, value = TRUE, fixed = TRUE)
+
+#params[str_detect(params, ".py", negate = TRUE)]
+
+# model parameters -------------------------------------------------------------
+
+  # categorical variables ------------------------------------------------------
+  params <- list(
+    model = c("lstm_base",
+              "lstm_pool", 
+              "dense_nn",
+              "nb", # naive bayes
+              "rf", # random forest 
+              "svm",
+              "lr"),
+    
+    query_strategy = c("cluster",
+                       "max",
+                       "max * cluster",
+                       "max * uncertainty",
+                       "max * random",
+                       "cluster * uncertainty",
+                       "cluster * random"
+                       #"uncertainty",
+                       #"random",
+                       #"mixed"
+                       ), # is not implemented
+    
+    balance_strategy = c(#"simple",
+                         #"double",
+                         "triple"
+                         #"undersample"s
+                         ),
+    
+    feature_extraction = c("doc2vec",
+                           "tfidf", 
+                           "sbert", 
+                           "embeddingIdf", # ?
+                           "embeddingLSTM") # only for lstm
+  )
+  
+  
+  # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
+  # and do not vary the balance strategy. 
+  params$model <- params[["model"]][4:7]
+  params$balance_strategy <- NULL
+  params$feature_extraction <- params[["feature_extraction"]][1:4]
+  params$training_data <- c("10/10", "5/5", "5/10")
+    
+  # numerical variables --------------------------------------------------------
+  n_instances <- 1 # number of papers queried each query 
+  n_prior_included <- 10 
+  n_prior_excluded <- 10 
+
+  
+  names(params$model) <- params$model
+  names(params$query_strategy) <- params$query_strategy
+  names(params$feature_extraction) <- params$feature_extraction
[…]

### 2020-02-04 manuscript/index/_book/thesis.tex
ignored files

@@
 % Gerbrich: try tro solve clsreferences.
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
 
@@
 % Syntax highlighting #22
-  \usepackage{color}
-  \usepackage{fancyvrb}
-  \newcommand{\VerbBar}{|}
-  \newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-  % Add ',fontsize=\small' for more characters per line
-  \usepackage{framed}
-  \definecolor{shadecolor}{RGB}{248,248,248}
-  \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-  \newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-  \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-  \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-  \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-  \newcommand{\BuiltInTok}[1]{#1}
-  \newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-  \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-  \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-  \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-  \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-  \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-  \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-  \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-  \newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-  \newcommand{\ExtensionTok}[1]{#1}
-  \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-  \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-  \newcommand{\ImportTok}[1]{#1}
-  \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-  \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-  \newcommand{\NormalTok}[1]{#1}
-  \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-  \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-  \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-  \newcommand{\RegionMarkerTok}[1]{#1}
-  \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-  \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-  \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-  \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-  \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-  \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
 % To pass between YAML and LaTeX the dollar signs are added by CII
-\title{My Final College Paper}
+\title{My thesis}
 \author{Gerbrich Ferdinands}
@@
 \institution{Utrecht University}
-\degree{Bachelor of Arts}
+\degree{Master of Science}
 %If you have two advisors for some reason, you can use the following
@@
 %%% Remember to use the correct department!
-\department{Mathematics}
+\department{Methodology and Statistics}
 % if you're writing a thesis in an interdisciplinary major,
@@
 \Acknowledgements{
-I want to thank a few people.
+
 }
@@
 \Dedication{
-You can have a dedication here if you wish.
+
 }
@@
 \Preface{
-This is an example of a thesis setup to use the reed thesis document class
-(for LaTeX) and the R bookdown package, in general.
+
 }
@@
 
+	\usepackage{booktabs}
+ \usepackage{longtable}
+ \usepackage{array}
+ \usepackage{multirow}
+ \usepackage{wrapfig}
+ \usepackage{float}
+ \usepackage{colortbl}
+ \usepackage{pdflscape}
+ \usepackage{tabu}
+ \usepackage{threeparttable}
+ \usepackage{threeparttablex}
+ \usepackage[normalem]{ulem}
+ \usepackage{makecell}
+ \usepackage{xcolor}
 % End of CII addition
@@
 \pagestyle{empty} % this removes page numbers from the frontmatter
-  \begin{acknowledgements}
-    I want to thank a few people.
-  \end{acknowledgements}
-  \begin{preface}
-    This is an example of a thesis setup to use the reed thesis document class
-    (for LaTeX) and the R bookdown package, in general.
-  \end{preface}
+
   \hypersetup{linkcolor=black}
@@
   \end{abstract}
-  \begin{dedication}
-    You can have a dedication here if you wish.
-  \end{dedication}
+
 \mainmatter % here the regular arabic numbering starts
@@
 \addcontentsline{toc}{chapter}{Introduction}
-
-Welcome to the \emph{R Markdown} thesis template.
-This template is based on (and in many places copied directly from) the Reed College LaTeX template, but hopefully it will provide a nicer interface for those that have never used TeX or LaTeX before.
-Using \emph{R Markdown} will also allow you to easily keep track of your analyses in \textbf{R} chunks of code, with the resulting plots and output included as well.
-The hope is this \emph{R Markdown} template gets you in the habit of doing reproducible research, which benefits you long-term as a researcher, but also will greatly help anyone that is trying to reproduce or build onto your results down the road.
-
-Hopefully, you won't have much of a learning period to go through and you will reap the benefits of a nicely formatted thesis.
-The use of LaTeX in combination with \emph{Markdown} is more consistent than the output of a word processor, much less prone to corruption or crashing, and the resulting file is smaller than a Word file.
-While you may have never had problems using Word in the past, your thesis is likely going to be about twice as large and complex as anything you've written before, taxing Word's capabilities.
-After working with \emph{Markdown} and \textbf{R} together for a few weeks, we are confident this will be your reporting style of choice going forward.
-
-\textbf{Why use it?}
-
-\emph{R Markdown} creates a simple and straightforward way to interface with the beauty of LaTeX.
-Packages have been written in \textbf{R} to work directly with LaTeX to produce nicely formatting tables and paragraphs.
-In addition to creating a user friendly interface to LaTeX, \emph{R Markdown} also allows you to read in your data, to analyze it and to visualize it using \textbf{R} functions, and also to provide the documentation and commentary on the results of your project.
-Further, it allows for \textbf{R} results to be passed inline to the commentary of your results.
-You'll see more on this later.
-
-\textbf{Who should use it?}
-
-Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use \emph{R Markdown}.
-Of particular use should be anyone in the sciences, but the user-friendly nature of \emph{Markdown} and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc.
-should make it of great benefit to nearly anyone writing a thesis project.
-
-\textbf{For additional help with bookdown}
-Please visit \href{https://bookdown.org/yihui/bookdown/}{the free online bookdown reference guide}.
-
-\hypertarget{ASReview}{%
-\chapter{ASReview}\label{ASReview}}
 \begin{itemize}
@@
 
-\hypertarget{math-sci}{%
-\chapter{Mathematics and Science}\label{math-sci}}
+\appendix
 
-\hypertarget{math}{%
-\section{Math}\label{math}}
+\hypertarget{parameter-configurations}{%
+\chapter{Parameter Configurations}\label{parameter-configurations}}
 
-\TeX~is the best way to typeset mathematics.
-Donald Knuth designed \TeX~when he got frustrated at how long it was taking the typesetters to finish his book, which contained a lot of mathematics.
-One nice feature of \emph{R Markdown} is its ability to read LaTeX code directly.
-
-If you are doing a thesis that will involve lots of math, you will want to read the following section which has been commented out.
-If you're not going to use math, skip over or delete this next commented section.
-
-\hypertarget{chemistry-101-symbols}{%
-\section{Chemistry 101: Symbols}\label{chemistry-101-symbols}}
-
-Chemical formulas will look best if they are not italicized.
-Get around math mode's automatic italicizing in LaTeX by using the argument \texttt{\$\textbackslash{}mathrm\{formula\ here\}\$}, with your formula inside the curly brackets.
-(Notice the use of the backticks here which enclose text that acts as code.)
-
-So, \(\mathrm{Fe_2^{2+}Cr_2O_4}\) is written \texttt{\$\textbackslash{}mathrm\{Fe\_2\^{}\{2+\}Cr\_2O\_4\}\$}.
-
-\noindent Exponent or Superscript: \(\mathrm{O^-}\)
-
-\noindent Subscript: \(\mathrm{CH_4}\)
-
-To stack numbers or letters as in \(\mathrm{Fe_2^{2+}}\), the subscript is defined first, and then the superscript is defined.
-
-\noindent Bullet: CuCl \(\bullet\) \(\mathrm{7H_{2}O}\)
-
-\noindent Delta: \(\Delta\)
-
-\noindent Reaction Arrows: \(\longrightarrow\) or \(\xrightarrow{solution}\)
-
-\noindent Resonance Arrows: \(\leftrightarrow\)
-
-\noindent Reversible Reaction Arrows: \(\rightleftharpoons\)
-
-\hypertarget{typesetting-reactions}{%
-\subsection{Typesetting reactions}\label{typesetting-reactions}}
-
-You may wish to put your reaction in an equation environment, which means that LaTeX will place the reaction where it fits and will number the equations for you.
-\begin{equation}
-  \mathrm{C_6H_{12}O_6  + 6O_2} \longrightarrow \mathrm{6CO_2 + 6H_2O}
-  \label{eq:reaction}
-\end{equation}
-We can reference this combustion of glucose reaction via Equation \eqref{eq:reaction}.
-
-\hypertarget{other-examples-of-reactions}{%
-\subsection{Other examples of reactions}\label{other-examples-of-reactions}}
-
-\(\mathrm{NH_4Cl_{(s)}}\) \(\rightleftharpoons\) \(\mathrm{NH_{3(g)}+HCl_{(g)}}\)
-
-\noindent \(\mathrm{MeCH_2Br + Mg}\) \(\xrightarrow[below]{above}\) \(\mathrm{MeCH_2\bullet Mg \bullet Br}\)
-
-\hypertarget{physics}{%
-\section{Physics}\label{physics}}
-
-Many of the symbols you will need can be found on the math page \url{http://web.reed.edu/cis/help/latex/math.html} and the Comprehensive LaTeX Symbol Guide (\url{http://mirror.utexas.edu/ctan/info/symbols/comprehensive/symbols-letter.pdf}).
-
-\hypertarget{biology}{%
-\section{Biology}\label{biology}}
-
-You will probably find the resources at \url{http://www.lecb.ncifcrf.gov/~toms/latex.html} helpful, particularly the links to bsts for various journals.
-You may also be interested in TeXShade for nucleotide typesetting (\url{http://homepages.uni-tuebingen.de/beitz/txe.html}).
-Be sure to read the proceeding chapter on graphics and tables.
-
-\hypertarget{ref-labels}{%
-\chapter{Tables, Graphics, References, and Labels}\label{ref-labels}}
-
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
-
-In addition to the tables that can be automatically generated from a data frame in \textbf{R} that you saw in {[}R Markdown Basics{]} using the \texttt{kable} function, you can also create tables using \emph{pandoc}.
-(More information is available at \url{http://pandoc.org/README.html\#tables}.) This might be useful if you don't have values specifically stored in \textbf{R}, but you'd like to display them in table form.
-Below is an example.
-Pay careful attention to the alignment in the table and hyphens to create the rows and columns.
-\begin{longtable}[]{@{}ccc@{}}
-\caption{\label{tab:inher} Correlation of Inheritance Factors for Parents and Child}\tabularnewline
-\toprule
-\begin{minipage}[b]{0.29\columnwidth}\centering
-Factors\strut
-\end{minipage} & \begin{minipage}[b]{0.46\columnwidth}\centering
-Correlation between Parents \& Child\strut
-\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
-Inherited\strut
-\end{minipage}\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{0.29\columnwidth}\centering
-Factors\strut
-\end{minipage} & \begin{minipage}[b]{0.46\columnwidth}\centering
-Correlation between Parents \& Child\strut
-\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
-Inherited\strut
-\end{minipage}\tabularnewline
-\midrule
-\endhead
-\begin{minipage}[t]{0.29\columnwidth}\centering
-Education\strut
-\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
--0.49\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
-Yes\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.29\columnwidth}\centering
-Socio-Economic Status\strut
-\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
-0.28\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
-Slight\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.29\columnwidth}\centering
-Income\strut
-\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
-0.08\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
-No\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.29\columnwidth}\centering
-Family Size\strut
-\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
-0.18\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
-Slight\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.29\columnwidth}\centering
-Occupational Prestige\strut
-\end{minipage} & \begin{minipage}[t]{0.46\columnwidth}\centering
-0.21\strut
-\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
-Slight\strut
-\end{minipage}\tabularnewline
-\bottomrule
-\end{longtable}
-We can also create a link to the table by doing the following: Table \ref{tab:inher}.
-If you go back to {[}Loading and exploring data{]} and look at the \texttt{kable} table, we can create a reference to this max delays table too: Table \ref{tab:maxdelays}.
-The addition of the \texttt{(\textbackslash{}\#tab:inher)} option to the end of the table caption allows us to then make a reference to Table \texttt{\textbackslash{}@ref(tab:label)}.
-Note that this reference could appear anywhere throughout the document after the table has appeared.
-
-\clearpage
-
-\hypertarget{figures}{%
-\section{Figures}\label{figures}}
-
-If your thesis has a lot of figures, \emph{R Markdown} might behave better for you than that other word processor.
-One perk is that it will automatically number the figures accordingly in each chapter.
-You'll also be able to create a label for each figure, add a caption, and then reference the figure in a way similar to what we saw with tables earlier.
-If you label your figures, you can move the figures around and \emph{R Markdown} will automatically adjust the numbering for you.
-No need for you to remember!
-So that you don't have to get too far into LaTeX to do this, a couple \textbf{R} functions have been created for you to assist.
-You'll see their use below.
-
-In the \textbf{R} chunk below, we will load in a picture stored as \texttt{reed.jpg} in our main directory.
-We then give it the caption of ``Reed logo'', the label of ``reedlogo'', and specify that this is a figure.
-Make note of the different \textbf{R} chunk options that are given in the R Markdown file (not shown in the knitted document).
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{include\_graphics}\NormalTok{(}\DataTypeTok{path =} \StringTok{"figure/reed.jpg"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-\begin{figure}
-\centering
-\includegraphics{figure/reed.jpg}
-\caption{\label{fig:reedlogo}Reed logo}
-\end{figure}
-Here is a reference to the Reed logo: Figure \ref{fig:reedlogo}.
-Note the use of the \texttt{fig:} code here.
-By naming the \textbf{R} chunk that contains the figure, we can then reference that figure later as done in the first sentence here.
-We can also specify the caption for the figure via the R chunk option \texttt{fig.cap}.
-
-\clearpage
-
-Below we will investigate how to save the output of an \textbf{R} plot and label it in a way similar to that done above.
-Recall the \texttt{flights} dataset from Chapter \ref{rmd-basics}.
-(Note that we've shown a different way to reference a section or chapter here.) We will next explore a bar graph with the mean flight departure delays by airline from Portland for 2014.
-Note also the use of the \texttt{scale} parameter which is discussed on the next page.
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{flights }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{group\_by}\NormalTok{(carrier) }\OperatorTok{\%>\%}
-\StringTok{  }\KeywordTok{summarize}\NormalTok{(}\DataTypeTok{mean\_dep\_delay =} \KeywordTok{mean}\NormalTok{(dep\_delay)) }\OperatorTok{\%>\%}
-\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ carrier, }\DataTypeTok{y =}\NormalTok{ mean\_dep\_delay)) }\OperatorTok{+}
-\StringTok{  }\KeywordTok{geom\_bar}\NormalTok{(}\DataTypeTok{position =} \StringTok{"identity"}\NormalTok{, }\DataTypeTok{stat =} \StringTok{"identity"}\NormalTok{, }\DataTypeTok{fill =} \StringTok{"red"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-\begin{figure}
-\centering
-\includegraphics{thesis_files/figure-latex/delaysboxplot-1.pdf}
-\caption{\label{fig:delaysboxplot}Mean Delays by Airline}
-\end{figure}
-Here is a reference to this image: Figure \ref{fig:delaysboxplot}.
-
-A table linking these carrier codes to airline names is available at \url{https://github.com/ismayc/pnwflights14/blob/master/data/airlines.csv}.
-
-\clearpage
-
-Next, we will explore the use of the \texttt{out.extra} chunk option, which can be used to shrink or expand an image loaded from a file by specifying \texttt{"scale=\ "}.
-Here we use the mathematical graph stored in the ``subdivision.pdf'' file.
-\begin{figure}
-\includegraphics[scale=0.75]{figure/subdivision} \caption{Subdiv. graph}\label{fig:subd}
-\end{figure}
-Here is a reference to this image: Figure \ref{fig:subd}. Note that \texttt{echo=FALSE} is specified so that the \textbf{R} code is hidden in the document.
-
-\textbf{More Figure Stuff}
-
-Lastly, we will explore how to rotate and enlarge figures using the \texttt{out.extra} chunk option. (Currently this only works in the PDF version of the book.)
-\begin{figure}
-\includegraphics[angle=180, scale=1.1]{figure/subdivision} \caption{A Larger Figure, Flipped Upside Down}\label{fig:subd2}
-\end{figure}
-As another example, here is a reference: Figure \ref{fig:subd2}.
-
-\hypertarget{footnotes-and-endnotes}{%
-\section{Footnotes and Endnotes}\label{footnotes-and-endnotes}}
-
-You might want to footnote something.\footnote{footnote text} The footnote will be in a smaller font and placed appropriately.
-Endnotes work in much the same way.
-More information can be found about both on the CUS site or feel free to reach out to \href{mailto:data@reed.edu}{\nolinkurl{data@reed.edu}}.
-
-\hypertarget{bibliographies}{%
-\section{Bibliographies}\label{bibliographies}}
-
-Of course you will need to cite things, and you will probably accumulate an armful of sources.
-There are a variety of tools available for creating a bibliography database (stored with the .bib extension).
-In addition to BibTeX suggested below, you may want to consider using the free and easy-to-use tool called Zotero.
-The Reed librarians have created Zotero documentation at \url{http://libguides.reed.edu/citation/zotero}.
-In addition, a tutorial is available from Middlebury College at \url{http://sites.middlebury.edu/zoteromiddlebury/}.
-
-\emph{R Markdown} uses \emph{pandoc} (\url{http://pandoc.org/}) to build its bibliographies.
-One nice caveat of this is that you won't have to do a second compile to load in references as standard LaTeX requires.
-To cite references in your thesis (after creating your bibliography database), place the reference name inside square brackets and precede it by the ``at'' symbol.
-For example, here's a reference to a book about worrying: (Molina \& Borkovec, 1994).
-This \texttt{Molina1994} entry appears in a file called \texttt{thesis.bib} in the \texttt{bib} folder.
-This bibliography database file was created by a program called BibTeX.
-You can call this file something else if you like (look at the YAML header in the main .Rmd file) and, by default, is to placed in the \texttt{bib} folder.
-
-For more information about BibTeX and bibliographies, see our CUS site (\url{http://web.reed.edu/cis/help/latex/index.html})\footnote{Reed~College (2007)}.
-There are three pages on this topic: \emph{bibtex} (which talks about using BibTeX, at \url{http://web.reed.edu/cis/help/latex/bibtex.html}), \emph{bibtexstyles} (about how to find and use the bibliography style that best suits your needs, at \url{http://web.reed.edu/cis/help/latex/bibtexstyles.html}) and \emph{bibman} (which covers how to make and maintain a bibliography by hand, without BibTeX, at \url{http://web.reed.edu/cis/help/latex/bibman.html}).
-The last page will not be useful unless you have only a few sources.
-
-If you look at the YAML header at the top of the main .Rmd file you can see that we can specify the style of the bibliography by referencing the appropriate csl file.
-You can download a variety of different style files at \url{https://www.zotero.org/styles}.
-Make sure to download the file into the csl folder.
-
-\textbf{Tips for Bibliographies}
+ASReview takes the following parameters/arguments:
 \begin{itemize}
@@
 \item
-  Like with thesis formatting, the sooner you start compiling your bibliography for something as large as thesis, the better.
-Typing in source after source is mind-numbing enough; do you really want to do it for hours on end in late April?
-Think of it as procrastination.
+  number of training data (included/excluded)
 \item
-  The cite key (a citation's label) needs to be unique from the other entries.
+  a model
 \item
-  When you have more than one author or editor, you need to separate each author's name by the word ``and'' e.g.~\texttt{Author\ =\ \{Noble,\ Sam\ and\ Youngberg,\ Jessica\},}.
+  a query strategy
 \item
-  Bibliographies made using BibTeX (whether manually or using a manager) accept LaTeX markup, so you can italicize and add symbols as necessary.
+  a balance strategy (fixed)
 \item
-  To force capitalization in an article title or where all lowercase is generally used, bracket the capital letter in curly braces.
+  feature extraction
+\end{itemize}
+\begin{table}[H]
+\centering
+\begin{tabular}{l>{\raggedright\arraybackslash}p{30em}}
+\toprule
+  & Configurations\\
+\midrule
+Models & Naive Bayes, Random Forest, Support Vector Machine, Logistic Regression\\
+Query Strategies & Cluster Sampling, Maximum Sampling, Cluster * Maximum  Sampling, Maximum * Uncertainty Sampling, Maximum * Random Sampling, Cluster * Uncertainty Sampling, Cluster * Random Sampling\\
+Feature extraction strategies & Doc2Vec, tf-idf, sbert, embeddingIdf\\
+Training data [included/excluded] & 10/10, 5/5, 5/10\\
+\bottomrule
+\end{tabular}
+\end{table}
+This leads to 273 combinations of configurations.
+\begin{itemize}
+\tightlist
 \item
-  You can add a Reed Thesis citation\footnote{Noble (2002)} option.
-The best way to do this is to use the phdthesis type of citation, and use the optional ``type'' field to enter ``Reed thesis'' or ``Undergraduate thesis.''
+  Naive bayes only goes with tfidf feature extraction.
+\item
+  For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
+\item
+  This leads to 3 * 7 * 4 * 3 + 1 * 7 * 1 * 3 = 273 combinations.
 \end{itemize}
-\hypertarget{anything-else}{%
-\section{Anything else?}\label{anything-else}}
+\begin{longtable}{llll}
+\toprule
+Model & Query Strategy & Feature extraction strategy & Training data [included/excluded]\\
+\midrule
+\endfirsthead
+\multicolumn{4}{@{}l}{\textit{(continued)}}\\
+\toprule
+Model & Query Strategy & Feature extraction strategy & Training data [included/excluded]\\
+\midrule
+\endhead
+\
+\endfoot
+\bottomrule
+\endlastfoot
+nb & cluster & tfidf & 10/10\\
+nb & max & tfidf & 10/10\\
+nb & max * cluster & tfidf & 10/10\\
+nb & max * uncertainty & tfidf & 10/10\\
+nb & max * random & tfidf & 10/10\\
+\addlinespace
+nb & cluster * uncertainty & tfidf & 10/10\\
+nb & cluster * random & tfidf & 10/10\\
+nb & cluster & tfidf & 5/5\\
+nb & max & tfidf & 5/5\\
+nb & max * cluster & tfidf & 5/5\\
+\addlinespace
+nb & max * uncertainty & tfidf & 5/5\\
+nb & max * random & tfidf & 5/5\\
+nb & cluster * uncertainty & tfidf & 5/5\\
+nb & cluster * random & tfidf & 5/5\\
+nb & cluster & tfidf & 5/10\\
+\addlinespace
+nb & max & tfidf & 5/10\\
+nb & max * cluster & tfidf & 5/10\\
+nb & max * uncertainty & tfidf & 5/10\\
+nb & max * random & tfidf & 5/10\\
+nb & cluster * uncertainty & tfidf & 5/10\\
+\addlinespace
+nb & cluster * random & tfidf & 5/10\\
+rf & cluster & doc2vec & 10/10\\
+rf & max & doc2vec & 10/10\\
+rf & max * cluster & doc2vec & 10/10\\
+rf & max * uncertainty & doc2vec & 10/10\\
+\addlinespace
+rf & max * random & doc2vec & 10/10\\
+rf & cluster * uncertainty & doc2vec & 10/10\\
+rf & cluster * random & doc2vec & 10/10\\
+rf & cluster & doc2vec & 5/5\\
+rf & max & doc2vec & 5/5\\
+\addlinespace
+rf & max * cluster & doc2vec & 5/5\\
+rf & max * uncertainty & doc2vec & 5/5\\
+rf & max * random & doc2vec & 5/5\\
+rf & cluster * uncertainty & doc2vec & 5/5\\
+rf & cluster * random & doc2vec & 5/5\\
+\addlinespace
+rf & cluster & doc2vec & 5/10\\
+rf & max & doc2vec & 5/10\\
+rf & max * cluster & doc2vec & 5/10\\
+rf & max * uncertainty & doc2vec & 5/10\\
+rf & max * random & doc2vec & 5/10\\
+\addlinespace
+rf & cluster * uncertainty & doc2vec & 5/10\\
+rf & cluster * random & doc2vec & 5/10\\
+rf & cluster & tfidf & 10/10\\
+rf & max & tfidf & 10/10\\
+rf & max * cluster & tfidf & 10/10\\
+\addlinespace
+rf & max * uncertainty & tfidf & 10/10\\
+rf & max * random & tfidf & 10/10\\
+rf & cluster * uncertainty & tfidf & 10/10\\
+rf & cluster * random & tfidf & 10/10\\
+rf & cluster & tfidf & 5/5\\
+\addlinespace
+rf & max & tfidf & 5/5\\
+rf & max * cluster & tfidf & 5/5\\
+rf & max * uncertainty & tfidf & 5/5\\
+rf & max * random & tfidf & 5/5\\
+rf & cluster * uncertainty & tfidf & 5/5\\
+\addlinespace
+rf & cluster * random & tfidf & 5/5\\
+rf & cluster & tfidf & 5/10\\
+rf & max & tfidf & 5/10\\
+rf & max * cluster & tfidf & 5/10\\
+rf & max * uncertainty & tfidf & 5/10\\
+\addlinespace
+rf & max * random & tfidf & 5/10\\
+rf & cluster * uncertainty & tfidf & 5/10\\
+rf & cluster * random & tfidf & 5/10\\
+rf & cluster & sbert & 10/10\\
+rf & max & sbert & 10/10\\
+\addlinespace
+rf & max * cluster & sbert & 10/10\\
+rf & max * uncertainty & sbert & 10/10\\
+rf & max * random & sbert & 10/10\\
+rf & cluster * uncertainty & sbert & 10/10\\
+rf & cluster * random & sbert & 10/10\\
+\addlinespace
+rf & cluster & sbert & 5/5\\
+rf & max & sbert & 5/5\\
+rf & max * cluster & sbert & 5/5\\
+rf & max * uncertainty & sbert & 5/5\\
+rf & max * random & sbert & 5/5\\
+\addlinespace
+rf & cluster * uncertainty & sbert & 5/5\\
+rf & cluster * random & sbert & 5/5\\
+rf & cluster & sbert & 5/10\\
+rf & max & sbert & 5/10\\
+rf & max * cluster & sbert & 5/10\\
+\addlinespace
+rf & max * uncertainty & sbert & 5/10\\
+rf & max * random & sbert & 5/10\\
+rf & cluster * uncertainty & sbert & 5/10\\
+rf & cluster * random & sbert & 5/10\\
+rf & cluster & embeddingIdf & 10/10\\
+\addlinespace
+rf & max & embeddingIdf & 10/10\\
+rf & max * cluster & embeddingIdf & 10/10\\
+rf & max * uncertainty & embeddingIdf & 10/10\\
+rf & max * random & embeddingIdf & 10/10\\
+rf & cluster * uncertainty & embeddingIdf & 10/10\\
+\addlinespace
+rf & cluster * random & embeddingIdf & 10/10\\
+rf & cluster & embeddingIdf & 5/5\\
+rf & max & embeddingIdf & 5/5\\
+rf & max * cluster & embeddingIdf & 5/5\\
+rf & max * uncertainty & embeddingIdf & 5/5\\
+\addlinespace
+rf & max * random & embeddingIdf & 5/5\\
+rf & cluster * uncertainty & embeddingIdf & 5/5\\
+rf & cluster * random & embeddingIdf & 5/5\\
+rf & cluster & embeddingIdf & 5/10\\
+rf & max & embeddingIdf & 5/10\\
+\addlinespace
+rf & max * cluster & embeddingIdf & 5/10\\
+rf & max * uncertainty & embeddingIdf & 5/10\\
+rf & max * random & embeddingIdf & 5/10\\
+rf & cluster * uncertainty & embeddingIdf & 5/10\\
+rf & cluster * random & embeddingIdf & 5/10\\
+\addlinespace
+svm & cluster & doc2vec & 10/10\\
+svm & max & doc2vec & 10/10\\
+svm & max * cluster & doc2vec & 10/10\\
+svm & max * uncertainty & doc2vec & 10/10\\
+svm & max * random & doc2vec & 10/10\\
+\addlinespace
+svm & cluster * uncertainty & doc2vec & 10/10\\
+svm & cluster * random & doc2vec & 10/10\\
+svm & cluster & doc2vec & 5/5\\
+svm & max & doc2vec & 5/5\\
+svm & max * cluster & doc2vec & 5/5\\
+\addlinespace
+svm & max * uncertainty & doc2vec & 5/5\\
+svm & max * random & doc2vec & 5/5\\
+svm & cluster * uncertainty & doc2vec & 5/5\\
+svm & cluster * random & doc2vec & 5/5\\
+svm & cluster & doc2vec & 5/10\\
+\addlinespace
+svm & max & doc2vec & 5/10\\
+svm & max * cluster & doc2vec & 5/10\\
+svm & max * uncertainty & doc2vec & 5/10\\
+svm & max * random & doc2vec & 5/10\\
+svm & cluster * uncertainty & doc2vec & 5/10\\
+\addlinespace
+svm & cluster * random & doc2vec & 5/10\\
+svm & cluster & tfidf & 10/10\\
+svm & max & tfidf & 10/10\\
+svm & max * cluster & tfidf & 10/10\\
+svm & max * uncertainty & tfidf & 10/10\\
+\addlinespace
+svm & max * random & tfidf & 10/10\\
+svm & cluster * uncertainty & tfidf & 10/10\\
+svm & cluster * random & tfidf & 10/10\\
+svm & cluster & tfidf & 5/5\\
+svm & max & tfidf & 5/5\\
+\addlinespace
+svm & max * cluster & tfidf & 5/5\\
+svm & max * uncertainty & tfidf & 5/5\\
+svm & max * random & tfidf & 5/5\\
+svm & cluster * uncertainty & tfidf & 5/5\\
+svm & cluster * random & tfidf & 5/5\\
+\addlinespace
+svm & cluster & tfidf & 5/10\\
+svm & max & tfidf & 5/10\\
+svm & max * cluster & tfidf & 5/10\\
+svm & max * uncertainty & tfidf & 5/10\\
+svm & max * random & tfidf & 5/10\\
+\addlinespace
+svm & cluster * uncertainty & tfidf & 5/10\\
+svm & cluster * random & tfidf & 5/10\\
+svm & cluster & sbert & 10/10\\
+svm & max & sbert & 10/10\\
+svm & max * cluster & sbert & 10/10\\
+\addlinespace
+svm & max * uncertainty & sbert & 10/10\\
+svm & max * random & sbert & 10/10\\
+svm & cluster * uncertainty & sbert & 10/10\\
+svm & cluster * random & sbert & 10/10\\
+svm & cluster & sbert & 5/5\\
+\addlinespace
+svm & max & sbert & 5/5\\
+svm & max * cluster & sbert & 5/5\\
+svm & max * uncertainty & sbert & 5/5\\
+svm & max * random & sbert & 5/5\\
+svm & cluster * uncertainty & sbert & 5/5\\
+\addlinespace
+svm & cluster * random & sbert & 5/5\\
+svm & cluster & sbert & 5/10\\
+svm & max & sbert & 5/10\\
+svm & max * cluster & sbert & 5/10\\
+svm & max * uncertainty & sbert & 5/10\\
+\addlinespace
+svm & max * random & sbert & 5/10\\
+svm & cluster * uncertainty & sbert & 5/10\\
+svm & cluster * random & sbert & 5/10\\
+svm & cluster & embeddingIdf & 10/10\\
+svm & max & embeddingIdf & 10/10\\
+\addlinespace
+svm & max * cluster & embeddingIdf & 10/10\\
+svm & max * uncertainty & embeddingIdf & 10/10\\
+svm & max * random & embeddingIdf & 10/10\\
+svm & cluster * uncertainty & embeddingIdf & 10/10\\
+svm & cluster * random & embeddingIdf & 10/10\\
+\addlinespace
+svm & cluster & embeddingIdf & 5/5\\
+svm & max & embeddingIdf & 5/5\\
+svm & max * cluster & embeddingIdf & 5/5\\
+svm & max * uncertainty & embeddingIdf & 5/5\\
+svm & max * random & embeddingIdf & 5/5\\
+\addlinespace
+svm & cluster * uncertainty & embeddingIdf & 5/5\\
+svm & cluster * random & embeddingIdf & 5/5\\
+svm & cluster & embeddingIdf & 5/10\\
+svm & max & embeddingIdf & 5/10\\
+svm & max * cluster & embeddingIdf & 5/10\\
+\addlinespace
+svm & max * uncertainty & embeddingIdf & 5/10\\
+svm & max * random & embeddingIdf & 5/10\\
+svm & cluster * uncertainty & embeddingIdf & 5/10\\
+svm & cluster * random & embeddingIdf & 5/10\\
+lr & cluster & doc2vec & 10/10\\
+\addlinespace
+lr & max & doc2vec & 10/10\\
+lr & max * cluster & doc2vec & 10/10\\
+lr & max * uncertainty & doc2vec & 10/10\\
+lr & max * random & doc2vec & 10/10\\
+lr & cluster * uncertainty & doc2vec & 10/10\\
+\addlinespace
+lr & cluster * random & doc2vec & 10/10\\
+lr & cluster & doc2vec & 5/5\\
+lr & max & doc2vec & 5/5\\
+lr & max * cluster & doc2vec & 5/5\\
+lr & max * uncertainty & doc2vec & 5/5\\
+\addlinespace
+lr & max * random & doc2vec & 5/5\\
+lr & cluster * uncertainty & doc2vec & 5/5\\
+lr & cluster * random & doc2vec & 5/5\\
+lr & cluster & doc2vec & 5/10\\
+lr & max & doc2vec & 5/10\\
+\addlinespace
+lr & max * cluster & doc2vec & 5/10\\
+lr & max * uncertainty & doc2vec & 5/10\\
+lr & max * random & doc2vec & 5/10\\
+lr & cluster * uncertainty & doc2vec & 5/10\\
+lr & cluster * random & doc2vec & 5/10\\
+\addlinespace
+lr & cluster & tfidf & 10/10\\
+lr & max & tfidf & 10/10\\
+lr & max * cluster & tfidf & 10/10\\
+lr & max * uncertainty & tfidf & 10/10\\
+lr & max * random & tfidf & 10/10\\
+\addlinespace
+lr & cluster * uncertainty & tfidf & 10/10\\
+lr & cluster * random & tfidf & 10/10\\
+lr & cluster & tfidf & 5/5\\
+lr & max & tfidf & 5/5\\
+lr & max * cluster & tfidf & 5/5\\
+\addlinespace
+lr & max * uncertainty & tfidf & 5/5\\
+lr & max * random & tfidf & 5/5\\
+lr & cluster * uncertainty & tfidf & 5/5\\
+lr & cluster * random & tfidf & 5/5\\
+lr & cluster & tfidf & 5/10\\
+\addlinespace
+lr & max & tfidf & 5/10\\
+lr & max * cluster & tfidf & 5/10\\
+lr & max * uncertainty & tfidf & 5/10\\
+lr & max * random & tfidf & 5/10\\
+lr & cluster * uncertainty & tfidf & 5/10\\
+\addlinespace
+lr & cluster * random & tfidf & 5/10\\
+lr & cluster & sbert & 10/10\\
+lr & max & sbert & 10/10\\
+lr & max * cluster & sbert & 10/10\\
+lr & max * uncertainty & sbert & 10/10\\
+\addlinespace
+lr & max * random & sbert & 10/10\\
+lr & cluster * uncertainty & sbert & 10/10\\
+lr & cluster * random & sbert & 10/10\\
+lr & cluster & sbert & 5/5\\
+lr & max & sbert & 5/5\\
+\addlinespace
+lr & max * cluster & sbert & 5/5\\
+lr & max * uncertainty & sbert & 5/5\\
+lr & max * random & sbert & 5/5\\
+lr & cluster * uncertainty & sbert & 5/5\\
+lr & cluster * random & sbert & 5/5\\
+\addlinespace
+lr & cluster & sbert & 5/10\\
+lr & max & sbert & 5/10\\
+lr & max * cluster & sbert & 5/10\\
+lr & max * uncertainty & sbert & 5/10\\
+lr & max * random & sbert & 5/10\\
+\addlinespace
+lr & cluster * uncertainty & sbert & 5/10\\
+lr & cluster * random & sbert & 5/10\\
+lr & cluster & embeddingIdf & 10/10\\
+lr & max & embeddingIdf & 10/10\\
+lr & max * cluster & embeddingIdf & 10/10\\
+\addlinespace
+lr & max * uncertainty & embeddingIdf & 10/10\\
+lr & max * random & embeddingIdf & 10/10\\
+lr & cluster * uncertainty & embeddingIdf & 10/10\\
+lr & cluster * random & embeddingIdf & 10/10\\
+lr & cluster & embeddingIdf & 5/5\\
+\addlinespace
+lr & max & embeddingIdf & 5/5\\
+lr & max * cluster & embeddingIdf & 5/5\\
+lr & max * uncertainty & embeddingIdf & 5/5\\
+lr & max * random & embeddingIdf & 5/5\\
+lr & cluster * uncertainty & embeddingIdf & 5/5\\
+\addlinespace
+lr & cluster * random & embeddingIdf & 5/5\\
+lr & cluster & embeddingIdf & 5/10\\
+lr & max & embeddingIdf & 5/10\\
+lr & max * cluster & embeddingIdf & 5/10\\
+lr & max * uncertainty & embeddingIdf & 5/10\\
+\addlinespace
+lr & max * random & embeddingIdf & 5/10\\
+lr & cluster * uncertainty & embeddingIdf & 5/10\\
+lr & cluster * random & embeddingIdf & 5/10\\*
+\end{longtable}
+\hypertarget{list-of-definitions}{%
+\chapter{List of Definitions}\label{list-of-definitions}}
 
-If you'd like to see examples of other things in this template, please contact the Data @ Reed team (email \href{mailto:data@reed.edu}{\nolinkurl{data@reed.edu}}) with your suggestions.
-We love to see people using \emph{R Markdown} for their theses, and are happy to help.
-
-\hypertarget{conclusion}{%
-\chapter*{Conclusion}\label{conclusion}}
-\addcontentsline{toc}{chapter}{Conclusion}
-
-If we don't want Conclusion to have a chapter number next to it, we can add the \texttt{\{-\}} attribute.
-
-\textbf{More info}
-
-And here's some other random info: the first paragraph after a chapter title or section head \emph{shouldn't be} indented, because indents are to tell the reader that you're starting a new paragraph.
-Since that's obvious after a chapter or section title, proper typesetting doesn't add an indent there.
-
-\appendix
-
-\hypertarget{the-first-appendix}{%
-\chapter{The First Appendix}\label{the-first-appendix}}
-
-This first appendix includes all of the R chunks of code that were hidden throughout the document (using the \texttt{include\ =\ FALSE} chunk tag) to help with readibility and/or setup.
-
-\textbf{In the main Rmd file}
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# This chunk ensures that the thesisdown package is}
-\CommentTok{\# installed and loaded. This thesisdown package includes}
-\CommentTok{\# the template files for the thesis.}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools))}
-  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(thesisdown))}
-\NormalTok{  devtools}\OperatorTok{::}\KeywordTok{install\_github}\NormalTok{(}\StringTok{"ismayc/thesisdown"}\NormalTok{)}
-\KeywordTok{library}\NormalTok{(thesisdown)}
-\end{Highlighting}
-\end{Shaded}
-\textbf{In Chapter \ref{ref-labels}:}
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# This chunk ensures that the thesisdown package is}
-\CommentTok{\# installed and loaded. This thesisdown package includes}
-\CommentTok{\# the template files for the thesis and also two functions}
-\CommentTok{\# used for labeling and referencing}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(devtools))}
-  \KeywordTok{install.packages}\NormalTok{(}\StringTok{"devtools"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(dplyr))}
-    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(ggplot2))}
-    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"ggplot2"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(ggplot2))}
-    \KeywordTok{install.packages}\NormalTok{(}\StringTok{"bookdown"}\NormalTok{, }\DataTypeTok{repos =} \StringTok{"http://cran.rstudio.com"}\NormalTok{)}
-\ControlFlowTok{if}\NormalTok{(}\OperatorTok{!}\KeywordTok{require}\NormalTok{(thesisdown))\{}
-  \KeywordTok{library}\NormalTok{(devtools)}
-\NormalTok{  devtools}\OperatorTok{::}\KeywordTok{install\_github}\NormalTok{(}\StringTok{"ismayc/thesisdown"}\NormalTok{)}
-\NormalTok{  \}}
-\KeywordTok{library}\NormalTok{(thesisdown)}
-\NormalTok{flights <{-}}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data/flights.csv"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-\hypertarget{the-second-appendix-for-fun}{%
-\chapter{The Second Appendix, for Fun}\label{the-second-appendix-for-fun}}
-
+Balance Strategy
+\begin{description}
+\item[Model.]
+The prediction model for Active learning
+\begin{verbatim}
+some code, part of Definition 2
+\end{verbatim}
+Third paragraph of definition 2.
+\item[Query Strategy]
+The way papers are queried to the researcher
+\begin{verbatim}
+query_strategy
+\end{verbatim}
+\begin{description}
+\tightlist
+\item[Uncertainty sampling]
+Selects the least sure instances for labelling.
+\item[Maximum sampling]
+Selects the samples with the highest prediction probability.
+\item[Random and maximum sampling.]
+Combination of random and maximum sampling. By default samples the 95\% of the instances with max sampling, and 5\% of the samples with random sampling.
+\end{description}
+\item[Feature Extraction Strategy]
+Feature Extraction Strategy
+\begin{verbatim}
+feature_extraction
+\end{verbatim}
+Third paragraph of definition x.
+\begin{description}
+\tightlist
+\item[Doc2Vec]
+\item[Term frequency-inverse document frequency (tf-idf)]
+\end{description}
+sbert
+\end{description}
 \backmatter
@@
 
-\hypertarget{refs}{}
-\begin{cslreferences}
-\leavevmode\hypertarget{ref-angel2000}{}%
-Angel, E. (2000). \emph{Interactive computer graphics : A top-down approach with opengl}. Boston, MA: Addison Wesley Longman.
-
-\leavevmode\hypertarget{ref-angel2001}{}%
-Angel, E. (2001a). \emph{Batch-file computer graphics : A bottom-up approach with quicktime}. Boston, MA: Wesley Addison Longman.
-
-\leavevmode\hypertarget{ref-angel2002a}{}%
-Angel, E. (2001b). \emph{Test second book by angel}. Boston, MA: Wesley Addison Longman.
-
-\leavevmode\hypertarget{ref-Molina1994}{}%
-Molina, S.
-T., \& Borkovec, T.
-D.
-(1994).
-The Penn State worry questionnaire: Psychometric properties and associated characteristics.
-In G.
-C.
-L.
-Davey \& F.
-Tallis (Eds.), \emph{Worrying: Perspectives on theory, assessment and treatment} (pp.
-265--283).
-New York: Wiley.
-
-\leavevmode\hypertarget{ref-noble2002}{}%
-Noble, S. G. (2002). \emph{Turning images into simple line-art} (Undergraduate thesis). Reed College.
-
-\leavevmode\hypertarget{ref-reedweb2007}{}%
-Reed~College. (2007). LaTeX your document. Retrieved from \url{http://web.reed.edu/cis/help/LaTeX/index.html}
-\end{cslreferences}
-
 % Index?

### 2020-02-04 manuscript/index/05-appendix.Rmd
add model definitions

@@
 source("R/asr-parameters.R")
+source("R/packages.R")
 ```
@@
 
-ASReview takes the following parameters/arguments:
-
-- number of training data (included/excluded)
-- a model
-- a query strategy
-- a balance strategy (fixed)
-- feature extraction
+model: nb
+query_strategy: max
+balance_strategy: double
+feature_extraction: tfidf
+n_instances: 1
+n_queries: 10
+n_prior_included: 5
+n_prior_excluded: 5
+mode: simulate
+model_param: {}
+query_param: {}
+feature_param: {}
+balance_param: {}
+abstract_only: False
 
@@
 
-Balance Strategy
-
 Model.
@@
 Query Strategy 
-:   The way papers are queried to the researcher
+:   Type of active learning, determining the way papers are queried to the researcher.
 
@@
     Maximum sampling
-    :  Selects the samples with the highest prediction probability.
+    :  Selects the samples with the highest prediction probability. The references who are most likely to be included are presented first.
 
@@
 Feature Extraction Strategy
-:   Feature Extraction Strategy
+:   The way the words in the abstracts are represented in the statistical model.
 
@@
 
-    Third paragraph of definition x.
-
     Doc2Vec
     :
+
+        doc2vec
 

### 2020-02-04 manuscript/index/index.Rmd

@@
 output: 
-  thesisdown::thesis_pdf: default # yet fails to compile 
+#  thesisdown::thesis_pdf: default  
   thesisdown::thesis_gitbook: default # creates html book in _book folder.  
@@
 # Introduction {.unnumbered}
+ASReview takes the following parameters/arguments:
 
-- Importance of sound systematic reviews (meta)
-- Why it was built
-- Advantages over other types
+- a model
+- a query strategy
+- a balance strategy (fixed)
+- a feature extraction strategy
+- number of training data
 
-- Whereas first results look promising, there hasn’t been conducted a full proof of concept
+The model is typically a learning algorithm used to predict the relevance of text. The following models will be compared:
 
-Goals: 
-- Save time 
-- But also more systematic..?
-
-? Misses
+* Naive Bayes (*nb*) [@Zhang2004]. 
+*

### 2020-02-04 manuscript/drafts/manuscript.Rmd
added definitions on model parameters - model (naive bayes) - feature selection - query strategy

@@
 output: pdf_document
+bibliography: asreview.bib
 ---
@@
 
-- number of training data (included/excluded)
 - a model
@@
 - a balance strategy (fixed)
-- feature extraction
+- a feature extraction strategy
+- number of training data
+
+The goal: 
+Use these inputs to predict relevance of papers.
+
+Numerical representation of texts
+To perform a learning algorithm on the abstract, the content of the abstracts needs to be represented numerical.
+To perform learning algorithms on the abstracts, their content has to be represented in a numerical way. 
+This is done by transforming the textual content of the abstracts into numerical feature vectors. 
+A classical example representation of texts is by 'bag of words' features, where for each text the number of occurrences of each word is stored.
+This leads to n features, where n is the number of distinct words in the texts.
+[@scikit-learn]
+
+ASReview implements several feature extraction strategies. The following will be compared:
+
+* Doc2Vec [@Le2014]
+* Tfidf 
+* SBERT
+* embeddingIdf
+
+The model is typically a learning algorithm used to predict the relevance of text.
+The following models will be compared:
+
+* Naive Bayes 
+* Random Forests
+* Support Vector Machine 
+* Logistic Regression 
+* **Dense Neural Network**
+
+Active learning = 
+increasing classification performance with every query. 
+The query strategy determines the way unlabeled papers are queried to the researcher.
+
+[@modAL2018]
+
+The balance strategy
 
@@
 ```
+
+## Models 
+### Naive Bayes 
+Naive Bayes assumes all features are independent given the class value. [@Zhang2004]
+
+ASReview uses the ` MultinomialNB` from the scikit-learn package [@scikit-learn], that implements the naive Bayes algorithm for multinomially distributed data. 
+` nb`
+
+Hyperparameters
+  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations. ?
+
+### Random Forests
+
+### Support Vector Machine
+
+### Logistic Regression
+
+### *Dense Neural Network*
+
+## Query Strategies 
+* Max - Choose the most likely samples to be included according to the model
+* Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994] 
+* Random - randomly selects abstracts with no regard to model assigned probabilities. 
+* Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled
+
+The following combinations are simulated:
+
+* cluster
+* max
+* cluster * random 
+* cluster * uncertainty
+* max * cluster
+* max * random
+* max * uncertainty
+
+## Balance Strategies
+
+## Feature Extraction Strategies
+
+# Combinations
 
@@
 ```
+
+# References

### 2020-02-04 manuscript/index/index.Rmd
added definitions on model parameters - model (naive bayes) - feature selection - query strategy

@@
 # Introduction {.unnumbered}
-ASReview takes the following parameters/arguments:
-
-- a model
-- a query strategy
-- a balance strategy (fixed)
-- a feature extraction strategy
-- number of training data
-
-The model is typically a learning algorithm used to predict the relevance of text. The following models will be compared:
-
-* Naive Bayes (*nb*) [@Zhang2004]. 
-*

### 2020-02-07 manuscript/drafts/manuscript.Rmd
performed first simulation study

@@
 Hyperparameters
-  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations. ?
+
+  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations.
 
@@
 
+## amount of training data
+n_instances = number of papers queried each query
+n_queries = number of queries
+n_prior_included: 5
+n_prior_excluded:
+
 # Combinations

### 2020-02-07 manuscript/drafts/myfirstsimulation.Rmd
performed first simulation study

---
title: "My first simulation"
author: "Gerbrich Ferdinands"
date: "2/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Methods
A simulation study was performed on the Nagtegaal dataset, using a model with the following configurations:

- Model = Naive Bayes
- Query Strategy = max_random
- Balance Strategy = Double
- n_instances=10 (number of papers each query)
- n_papers=2000 (shouldn't I do all?)
- n_prior_included = 5
- n_prior_excluded = 5
- mix_ratio = 0.95 (95% max, 5% random)

| Hyperparameters |       | default | optimized |   |
|---------|-------|---------|-----------|---|
| Model   |       |         |           |   |
|         | alpha | 3.822     |3.511844   |   |
| Balance |       |         |           |   |
|         |    a  |     2.155 | 0.254892  |   |
|         | alpha |     0.94  | 1.459081  |   |
|         |  b    | 0.789  | 0.394437  |   |   
|Feature  |       |         |           |   |
|         |ngram_max|     1   |   2     |   | 
|         |split_ta|      0   |    1       |   |

For the sake of evaluating the optimized hyperparameters, two simulations of five runs each were compared: one with default hyperparameters and with optimized hyperparameters.

## Results
  Explanation of the plots come from the ` asreview-visualization` repository.
  The optimized hyperparameters do not perform better than the default ones, this is probably due to the fact that the default hyperparameters have already been optimized in the past. It is therefore to know for which models this has already been done and which not!

\pagebreak
#### Inclusions

This figure shows the number/percentage of included papers found as a function of the
number/percentage of papers reviewed. Initial included/excluded papers are subtracted so that the line
always starts at (0,0).

The quicker the line goes to a 100%, the better the performance.

![]("figs/myfirstsim/Figure_1.png")

In the beginning, the model with default parameters finds inclusions quicker than the model with optimized hyperparamters.
Only after reviewing 50% of the papers, the optimized hyperparameters outperform the default ones.

\pagebreak
#### Discovery

This figure shows the distribution of the number of papers that have to be read before discovering
each inclusion. Not every paper is equally hard to find.

The closer to the left, the better.

![]("figs/myfirstsim/Figure_2.png")

\pagebreak
#### Limits

This figure shows how many papers need to be read with a given criterion. A criterion is expressed
as "after reading _y_ % of the papers, at most an average of _z_ included papers have been not been
seen by the reviewer, if he is using max sampling.". Here, _y_ is shown on the y-axis, while
three values of _z_ are plotted as three different lines with the same color. The three values for
_z_ are 0.1, 0.5 and 2.0.

The quicker the lines touch the black (`y=x`) line, the better.

![when _z_ goes up, optimized parameters perform better.]("figs/myfirstsim/Figure_3.png")

\pagebreak
## Console output
3120 iterations ran overnight.

![]("figs/myfirstsim/computation.png")

2191 was best performing with a loss of 0.1124

![]("figs/myfirstsim/optmizationresult.png")

## Notes
- Optimizing the hyperparameters with the Nagtegaal set and then running a simulation on the Nagtegaal dataset is using the data twice. 
  This leads to overfitting. A next approach could be to perform some way of cross-validation, e.g. split the datasets in train and test datasets. 
- There are two main optimization modes: passive and active learning.
  The first is used here and is relatively fast, the second is more computationally expensive.

- Of primary interest is the comparison of different model configurations in predictive performance. 
  A simulation study can be performed with all possible configurations using the default hyperparameters. 
  The results could be used to select model configurations that could possibly benefit from hyperparameter sreening. 
- Second, we could investigate how much is to gain in predictive performance from optimizing the hyperparameters. 
  For this, some cross-validation strategy should be used. 
  Optimization can consist of two steps: 
  first, optimization through passive learning can be performed, from which the best performing models can be selected for the second step:
  optimization through passive learning.

### Possible Research Questions 
- Which model configurations have good predictive performance? 
  - for what kind of data sets and under which circumstances? 
- Does optimization of hyperparameters lead to substantial gain in predictive performance? 
  - How much and why? 
  - How do the hyperparameters relate to one another?
  - What is the optimal way to tune the hyperparameters? 
    - to determine by cross-validation 
    - for example: optimize over a large number of datasets? or a different strategy? 
- ... 
- ...

### 2020-02-12 manuscript/drafts/manuscript.Rmd
meeting notes
add doc2vec, random forest

@@
 
-Numerical representation of texts
-To perform a learning algorithm on the abstract, the content of the abstracts needs to be represented numerical.
-To perform learning algorithms on the abstracts, their content has to be represented in a numerical way. 
-This is done by transforming the textual content of the abstracts into numerical feature vectors. 
-A classical example representation of texts is by 'bag of words' features, where for each text the number of occurrences of each word is stored.
+Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
+The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
+
+A classical example of word embeddings is 'bag of words'.
+For each each text, the number of occurrences of each word is stored.
 This leads to n features, where n is the number of distinct words in the texts.
@@
 
+Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
+
+corpus = all the text:
+
 ASReview implements several feature extraction strategies. The following will be compared:
 
-* Doc2Vec [@Le2014]
-* Tfidf 
-* SBERT
-* embeddingIdf
-
 The model is typically a learning algorithm used to predict the relevance of text.
-The following models will be compared:
-
-* Naive Bayes 
-* Random Forests
-* Support Vector Machine 
-* Logistic Regression 
-* **Dense Neural Network**
 
@@
 ```
+### Feature Extraction Strategies 
+split_ta = overall hyperparameter
+
+#### TF-IDF
+The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".
+
+Term-frequency Inverse Document Frequency [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.
+
+##### hyperparameters 
+    ngram_max: int
+            Can use up to ngrams up to ngram_max. For example in the case of
+            ngram_max=2, monograms and bigrams could be used.
+
+#### Doc2Vec
+Predicts words from context. 
+Aims at capturing the relations between word (man-woman, king-queen).
+[@Le2014]. Using a neural network.
+
+using Continuous Bag-of-Words (CBOW), Skip-Gram model, ....
+Word vector _W_ and extra: document vector _D_, trained to predict words in the text.
+
+From gensim [@Rehurek2010].
+
+        Arguments
+        ---------
+        vector_size: int
+            Output size of the vector.
+        epochs: int
+            Number of epochs to train the doc2vec model.
+        min_count: int
+            Minimum number of occurences for a word in the corpus for it to
+            be included in the model.
+        workers: int
+            Number of threads to train the model with.
+        window: int
+            Maximum distance over which word vectors influence each other.
+        dm_concat: int
+            Whether to concatenate word vectors or not.
+            See paper for more detail.
+        dm: int
+            Model to use.
+            0: Use distribute bag of words (DBOW).
+            1: Use distributed memory (DM).
+            2: Use both of the above with half the vector size and concatenate
+            them.
+        dbow_words: int
+            Whether to train the word vectors using the skipgram metho
+
+#### SBERT
+
+BERT-base model with mean-tokens pooling [@Reimers2019]
+
+#### embeddingIdf 
+This model averages the weighted word vectors of all the words in the text,
+in order to get a single feature vector for each text. The weights are provided by the inverse document frequencies
 
@@
 ### Random Forests
+A number of decision trees are fit on bootstrapped samples of the original data, 
+[@Breiman2001]
+RandomForestClassifier from sklearn
+
+Arguments
+        ---------
+        n_estimators: int
+            Number of estimators.
+        max_features: int
+            Number of features in the model.
+        class_weight: float
+            Class weight of the inclusions.
+        random_state: int, RandomState
+            Set the random state of the RNG.
+        """
 
@@
 
-### *Dense Neural Network*
+### __Dense Neural Network__
 
@@
 
-## Feature Extraction Strategies
+## amount of training data
 
-## amount of training data
-n_instances = number of papers queried each query
-n_queries = number of queries
-n_prior_included: 5
-n_prior_excluded:
+* n_instances = number of papers queried each query
+* n_queries = number of queries
+* n_prior_included: 5
+* n_prior_excluded:
 

### 2020-02-12 manuscript/drafts/asr-parameters.R

@@ -78,7 +78,7 @@
                             "Cluster * Uncertainty Sampling", 
                             "Cluster * Random Sampling")
   
-  words$feature_extraction <- c("Doc2Vec", "tf-idf", "sbert", "embeddingIdf")
+  words$feature_extraction <- c("Doc2Vec", "TF-IDF", "sbert", "embeddingIdf")
   
   # words$training_data <- c("10 included, 10 excluded",
   #                          "5 included, 5 excluded",

### 2020-02-12 manuscript/drafts/manuscript.Rmd
added a few metrics

@@
 ``` 
+# Introduction
 
+## The problem
+## Current solutions
+Workload savings 30-70 percent, at a loss of 5% of relevant studies [@Omara-Eves2015].
+
+# The software 
 ASReview takes the following parameters/arguments:
@@
 
-## Models 
-### Naive Bayes 
+### Models 
+#### Naive Bayes 
 Naive Bayes assumes all features are independent given the class value. [@Zhang2004]
@@
 
-### Random Forests
+#### Random Forests
 A number of decision trees are fit on bootstrapped samples of the original data, 
@@
 
-### Support Vector Machine
+#### Support Vector Machine
 
-### Logistic Regression
+#### Logistic Regression
 
-### __Dense Neural Network__
+#### __Dense Neural Network__
 
-## Query Strategies 
+### Query Strategies 
 * Max - Choose the most likely samples to be included according to the model
@@
 
-## Balance Strategies
+### Balance Strategies
 
-## amount of training data
+### amount of training data
 
@@
 
+See appendix A for a table containing all 273 combinations.
+
+# Performance metrics
+Tradeoff: identifying all relevant papers and reducing workload.
+
+What is more important: recall or precision?
+
+Recall more highly valued than precision.
+
+What about class imbalance?
+
+#### RRF
+Amount of relevant references found after having screened a certain percentage of the total number of abstracts.
+
+#### Work saved over sampling (WSS)
+Indicates how much time can be saved, at a given level of recall.
+WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
+Typically, WSS is measured at a recall of 0.95.
+
+$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall ) $$
+
+#### Raoul
+#### Utility? 
+#### F-measure 
+#### ROC/AUC
+
+# Appendix A - combinations
+
 ```{r}

### 2020-02-13 manuscript/test/04-simulation.Rmd
remove thesisdown files, update notes

--- 2020-02-07 manuscript/drafts/myfirstsimulation.Rmd
@@
----
-title: "My first simulation"
-author: "Gerbrich Ferdinands"
-date: "2/7/2020"
-output: pdf_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+# My first simulation
+```{r, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 
-![]("figs/myfirstsim/Figure_1.png")
+```{r}
+knitr::include_graphics("figs/myfirstsim/Figure_1.png")
+```
 
@@
 
-![]("figs/myfirstsim/Figure_2.png")
+```{r}
+knitr::include_graphics("figs/myfirstsim/Figure_2.png")
+```
 
@@
 
-![when _z_ goes up, optimized parameters perform better.]("figs/myfirstsim/Figure_3.png")
+```{r}
+knitr::include_graphics("figs/myfirstsim/Figure_3.png")
+```
 
@@
 
-![]("figs/myfirstsim/computation.png")
-
+```{r}
+knitr::include_graphics("figs/myfirstsim/computation.png")
+```
 2191 was best performing with a loss of 0.1124
 
-![]("figs/myfirstsim/optmizationresult.png")
+```{r}
+knitr::include_graphics("figs/myfirstsim/optmizationresult.png")
+```
 

### 2020-02-13 manuscript/test/_book/bookdown-demo.tex
remove thesisdown files, update notes

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Minimal Book Example},
  pdfauthor={Yihui Xie},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{A Minimal Book Example}
\author{Yihui Xie}
\date{2020-02-12}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{frontpage}{%
\chapter{Frontpage}\label{frontpage}}

This is my thesis project.

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

You can label chapter and section titles using \texttt{\{\#label\}} after them, e.g., we can reference Chapter \ref{intro}. If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \ref{methods}.

Figures and tables with captions will be placed in \texttt{figure} and \texttt{table} environments, respectively.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mar =} \KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{4}\NormalTok{, }\FloatTok{.1}\NormalTok{, }\FloatTok{.1}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(pressure, }\DataTypeTok{type =} \StringTok{\textquotesingle{}b\textquotesingle{}}\NormalTok{, }\DataTypeTok{pch =} \DecValTok{19}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{bookdown-demo_files/figure-latex/nice-fig-1}

}

\caption{Here is a nice figure!}\label{fig:nice-fig}
\end{figure}

Reference a figure by its code chunk label with the \texttt{fig:} prefix, e.g., see Figure \ref{fig:nice-fig}. Similarly, you can reference tables generated from \texttt{knitr::kable()}, e.g., see Table \ref{tab:nice-tab}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{kable}\NormalTok{(}
  \KeywordTok{head}\NormalTok{(iris, }\DecValTok{20}\NormalTok{), }\DataTypeTok{caption =} \StringTok{\textquotesingle{}Here is a nice table!\textquotesingle{}}\NormalTok{,}
  \DataTypeTok{booktabs =} \OtherTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:nice-tab}Here is a nice table!}
\centering
\begin{tabular}[t]{rrrrl}
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species\\
\midrule
5.1 & 3.5 & 1.4 & 0.2 & setosa\\
4.9 & 3.0 & 1.4 & 0.2 & setosa\\
4.7 & 3.2 & 1.3 & 0.2 & setosa\\
4.6 & 3.1 & 1.5 & 0.2 & setosa\\
5.0 & 3.6 & 1.4 & 0.2 & setosa\\
\addlinespace
5.4 & 3.9 & 1.7 & 0.4 & setosa\\
4.6 & 3.4 & 1.4 & 0.3 & setosa\\
5.0 & 3.4 & 1.5 & 0.2 & setosa\\
4.4 & 2.9 & 1.4 & 0.2 & setosa\\
4.9 & 3.1 & 1.5 & 0.1 & setosa\\
\addlinespace
5.4 & 3.7 & 1.5 & 0.2 & setosa\\
4.8 & 3.4 & 1.6 & 0.2 & setosa\\
4.8 & 3.0 & 1.4 & 0.1 & setosa\\
4.3 & 3.0 & 1.1 & 0.1 & setosa\\
5.8 & 4.0 & 1.2 & 0.2 & setosa\\
\addlinespace
5.7 & 4.4 & 1.5 & 0.4 & setosa\\
5.4 & 3.9 & 1.3 & 0.4 & setosa\\
5.1 & 3.5 & 1.4 & 0.3 & setosa\\
5.7 & 3.8 & 1.7 & 0.3 & setosa\\
5.1 & 3.8 & 1.5 & 0.3 & setosa\\
\bottomrule
\end{tabular}
\end{table}

You can write citations, too. For example, we are using the \textbf{bookdown} package (Xie \protect\hyperlink{ref-R-bookdown}{2020}) in this sample book, which was built on top of R Markdown and \textbf{knitr} (Xie \protect\hyperlink{ref-xie2015}{2015}).

\hypertarget{literature}{%
\chapter{Literature}\label{literature}}

Here is a review of existing methods.

\hypertarget{methods}{%
\chapter{Methods}\label{methods}}

We describe our methods in this chapter.

\hypertarget{my-first-simulation}{%
\chapter{My first simulation}\label{my-first-simulation}}

\hypertarget{methods-1}{%
\section{Methods}\label{methods-1}}

A simulation study was performed on the Nagtegaal dataset, using a model with the following configurations:

\begin{itemize}
\tightlist
\item
  Model = Naive Bayes
\item
  Query Strategy = max\_random
\item
  Balance Strategy = Double
\item
  n\_instances=10 (number of papers each query)
\item
  n\_papers=2000 (shouldn't I do all?)
\item
  n\_prior\_included = 5
\item
  n\_prior\_excluded = 5
\item
  mix\_ratio = 0.95 (95\% max, 5\% random)
\end{itemize}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Hyperparameters & & default & optimized &\tabularnewline
\midrule
\endhead
Model & & & &\tabularnewline
& alpha & 3.822 & 3.511844 &\tabularnewline
Balance & & & &\tabularnewline
& a & 2.155 & 0.254892 &\tabularnewline
& alpha & 0.94 & 1.459081 &\tabularnewline
& b & 0.789 & 0.394437 &\tabularnewline
Feature & & & &\tabularnewline
& ngram\_max & 1 & 2 &\tabularnewline
& split\_ta & 0 & 1 &\tabularnewline
\bottomrule
\end{longtable}

For the sake of evaluating the optimized hyperparameters, two simulations of five runs each were compared: one with default hyperparameters and with optimized hyperparameters.

\hypertarget{results}{%
\section{Results}\label{results}}

Explanation of the plots come from the \texttt{asreview-visualization} repository.
The optimized hyperparameters do not perform better than the default ones, this is probably due to the fact that the default hyperparameters have already been optimized in the past. It is therefore to know for which models this has already been done and which not!

\pagebreak

\hypertarget{inclusions}{%
\subsubsection{Inclusions}\label{inclusions}}

This figure shows the number/percentage of included papers found as a function of the
number/percentage of papers reviewed. Initial included/excluded papers are subtracted so that the line
always starts at (0,0).

The quicker the line goes to a 100\%, the better the performance.

\includegraphics{figs/myfirstsim/Figure_1.png}

In the beginning, the model with default parameters finds inclusions quicker than the model with optimized hyperparamters.
Only after reviewing 50\% of the papers, the optimized hyperparameters outperform the default ones.

\pagebreak

\hypertarget{discovery}{%
\subsubsection{Discovery}\label{discovery}}

This figure shows the distribution of the number of papers that have to be read before discovering
each inclusion. Not every paper is equally hard to find.

The closer to the left, the better.

\includegraphics{figs/myfirstsim/Figure_2.png}

\pagebreak

\hypertarget{limits}{%
\subsubsection{Limits}\label{limits}}

This figure shows how many papers need to be read with a given criterion. A criterion is expressed
as ``after reading \emph{y} \% of the papers, at most an average of \emph{z} included papers have been not been
seen by the reviewer, if he is using max sampling.''. Here, \emph{y} is shown on the y-axis, while
three values of \emph{z} are plotted as three different lines with the same color. The three values for
\emph{z} are 0.1, 0.5 and 2.0.

The quicker the lines touch the black (\texttt{y=x}) line, the better.

\includegraphics{figs/myfirstsim/Figure_3.png}

\pagebreak

\hypertarget{console-output}{%
\section{Console output}\label{console-output}}

3120 iterations ran overnight.

\includegraphics{figs/myfirstsim/computation.png}
2191 was best performing with a loss of 0.1124

\includegraphics{figs/myfirstsim/optmizationresult.png}

\hypertarget{notes}{%
\section{Notes}\label{notes}}

\begin{itemize}
\item
  Optimizing the hyperparameters with the Nagtegaal set and then running a simulation on the Nagtegaal dataset is using the data twice.
  This leads to overfitting. A next approach could be to perform some way of cross-validation, e.g.~split the datasets in train and test datasets.
\item
  There are two main optimization modes: passive and active learning.
  The first is used here and is relatively fast, the second is more computationally expensive.
\item
  Of primary interest is the comparison of different model configurations in predictive performance.
  A simulation study can be performed with all possible configurations using the default hyperparameters.
  The results could be used to select model configurations that could possibly benefit from hyperparameter sreening.
\item
  Second, we could investigate how much is to gain in predictive performance from optimizing the hyperparameters.
  For this, some cross-validation strategy should be used.
  Optimization can consist of two steps:
  first, optimization through passive learning can be performed, from which the best performing models can be selected for the second step:
  optimization through passive learning.
\end{itemize}

\hypertarget{possible-research-questions}{%
\subsection{Possible Research Questions}\label{possible-research-questions}}

\begin{itemize}
\tightlist
\item
  Which model configurations have good predictive performance?

  \begin{itemize}
  \tightlist
  \item
    for what kind of data sets and under which circumstances?
  \end{itemize}
\item
  Does optimization of hyperparameters lead to substantial gain in predictive performance?

  \begin{itemize}
  \tightlist
  \item
    How much and why?
  \item
    How do the hyperparameters relate to one another?
  \item
    What is the optimal way to tune the hyperparameters?

    \begin{itemize}
    \tightlist
    \item
      to determine by cross-validation
    \item
      for example: optimize over a large number of datasets? or a different strategy?
    \end{itemize}
  \end{itemize}
\item
  \ldots{}
\item
  \ldots{}
\end{itemize}

\hypertarget{appendix-appendix}{%
\appendix}

\hypertarget{appendix-a}{%
\chapter{Appendix A}\label{appendix-a}}

We have finished a nice book.

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-xie2015}{}%
Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{http://yihui.name/knitr/}.

\leavevmode\hypertarget{ref-R-bookdown}{}%
---------. 2020. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. \url{https://github.com/rstudio/bookdown}.
\end{cslreferences}

\end{document}

### 2020-02-13 manuscript/test/index.Rmd
remove thesisdown files, update notes

--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Frontpage
This is my thesis project.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

### 2020-02-13 manuscript/index/R/asr-parameters.R

@@ -1,91 +1,0 @@
-# Gerbrich Ferdinands, 14-01-2020
-# document all parameters in asreview software
-
-#path <- "~/Downloads/automated-systematic-review-unsupervised/asreview"
-
-#params <- list.files(path, recursive = TRUE, include.dirs = TRUE)
-
-# library(httr)
-# req <- GET("https://api.github.com/repos/qubixes/automated-systematic-review/tree/unsupervised")
-# stop_for_status(req)
-# filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
-# grep("/unsupervised", filelist, value = TRUE, fixed = TRUE)
-
-#params[str_detect(params, ".py", negate = TRUE)]
-
-# model parameters -------------------------------------------------------------
-
-  # categorical variables ------------------------------------------------------
-  params <- list(
-    model = c("lstm_base",
-              "lstm_pool", 
-              "dense_nn",
-              "nb", # naive bayes
-              "rf", # random forest 
-              "svm",
-              "lr"),
-    
-    query_strategy = c("cluster",
-                       "max",
-                       "max * cluster",
-                       "max * uncertainty",
-                       "max * random",
-                       "cluster * uncertainty",
-                       "cluster * random"
-                       #"uncertainty",
-                       #"random",
-                       #"mixed"
-                       ), # is not implemented
-    
-    balance_strategy = c(#"simple",
-                         #"double",
-                         "triple"
-                         #"undersample"s
-                         ),
-    
-    feature_extraction = c("doc2vec",
-                           "tfidf", 
-                           "sbert", 
-                           "embeddingIdf", # ?
-                           "embeddingLSTM") # only for lstm
-  )
-  
-  
-  # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
-  # and do not vary the balance strategy. 
-  params$model <- params[["model"]][4:7]
-  params$balance_strategy <- NULL
-  params$feature_extraction <- params[["feature_extraction"]][1:4]
-  params$training_data <- c("10/10", "5/5", "5/10")
-    
-  # numerical variables --------------------------------------------------------
-  n_instances <- 1 # number of papers queried each query 
-  n_prior_included <- 10 
-  n_prior_excluded <- 10 
-
-  
-  names(params$model) <- params$model
-  names(params$query_strategy) <- params$query_strategy
-  names(params$feature_extraction) <- params$feature_extraction
[…]

### 2020-02-18 manuscript/drafts/analyseplan.Rmd
updated analysis plan

---
title: "analyseplan"
author: "Gerbrich Ferdinands"
date: "2/13/2020"
output: pdf_document
---
Goal: evaluate performance of different models of the ASReview tool.

### Stage 1: hyperparameter optimization
We are testing 5 models on 5 different datasets.

Every model has its own set of hyperparameters.
The hyperparameters are optimized on the 5 datasets in three different ways:

- 1 on 1: maximum performance 
- 4 on 1: cross-validation 
- 5 on 1: more data = more better?

This results $(5+5+1)*5$ sets of hyperparameters.

### Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

### Datasets

#### ptsd
#### ace
#### hall

#### nagtegaal - van PhD van Lars
#### medische van Jan

### Models
(input table here?)

- Naive Bayes 
- Random Forests
- Support Vecor Machine (doc2vec)
- Logistic Regression
- Dense Neural Network (doc2vec)

The other parameters remain fixed over the 5 models:

- Feature extraction = tf-idf
- Query Strategy = max
- Balance Strategy = triple
- n_instances=10 (number of papers each query)
- n_prior_included = 5
- n_prior_excluded = 5
- mix_ratio = 0.95 (95% max, 5% random)

## Hyperparameters

## Scripts 
  - simulatie:
- [ ] script die optimalisatie genereert (config files.)
- [ ] script die `.ini`'s voor simulatie genereert.

```{bash}
output/
├── active_learning
│   ├── nb_max_double_tfidf
│   │   └── depression_hall_ace_ptsd_nagtegaal
│   │       ├── best
│   │       │   ├── ace
│   │       │   ├── depression
│   │       │   ├── hall
│   │       │   ├── nagtegaal
│   │       │   └── ptsd
│   │       ├── current
│   │       │   ├── ace
│   │       │   ├── depression
│   │       │   ├── hall
│   │       │   ├── nagtegaal
│   │       │   └── ptsd
│   │       └── trials.pkl
```

### 2020-02-18 manuscript/drafts/manuscript.Rmd
updated analysis plan

@@
 ---
-title: "parameters"
+title: "Manuscxript drafts"
 author: "Gerbrich Ferdinands"
@@
 tab <- do.call(rbind, tab)
+# remove row training data (28.02)
 colnames(tab) <- c("Configurations")
-
+tab <- tab[-4,]
 ```
@@
 # combinations table
+params[[4]] <- NULL # remove training data
 combins <- expand.grid(params) %>%
@@
 ``` 
-# Introduction
-
-## The problem
-## Current solutions
-Workload savings 30-70 percent, at a loss of 5% of relevant studies [@Omara-Eves2015].
+# Analysis strategy
+Goal: evaluate performance of different models of the ASReview tool.
 
@@
 
-- a model
-- a query strategy
-- a balance strategy (fixed)
-- a feature extraction strategy
-- number of training data
+<!-- - a model -->
+<!-- - a query strategy -->
+<!-- - a balance strategy -->
+<!-- - a feature extraction strategy -->
 
-The goal: 
+```{r}
+kable(tab, "latex", booktabs = TRUE, col.names = "Configurations") %>%
+  kable_styling(full_width = FALSE) %>%
+  column_spec(2, width = "30em") 
+```
+
 Use these inputs to predict relevance of papers.
 
+## Stage 1: hyperparameter optimization
+We are going to test 5 models on 5 different datasets.
+
+### Datasets
+
+#### ptsd
+#### ace
+#### hall 
+#### nagtegaal - van PhD van Lars
+#### medische van Jan
+
+### Models
+- Naive Bayes 
+- Random Forests
+- Support Vecor Machine 
+- Logistic Regression
+- Dense Neural Network
+
+Or, more specific:
+
+```{r}
+tabbie <-
+  combins %>%
+  filter(query_strategy == "max",
+         feature_extraction %in% c("doc2vec", "tfidf") & model %in% c("dense_nn","svm", "nb", "rf", "lr")) %>%
+  select(-query_strategy)
+
+tabbie <- tabbie[c(1,3,5,6,9),]
+row.names(tabbie) <- NULL
+tabbie %>%
+  kable(col.names = names(words)[1:3], format = "latex")
+```
+
+The other parameters remain fixed over the 5 models:
+
+- Query Strategy = max
+- Balance Strategy = triple
+- n_instances=10 (number of papers each query)
+- n_prior_included = 5
+- n_prior_excluded = 5
+
+### Hyperparameters
+Every model has its own set of hyperparameters:
+
+### Optimization
+The hyperparameters are optimized on the 5 datasets in three different ways:
+
+- 1 on 1: maximum performance 
+- 4 on 1: cross-validation 
+- 5 on 1: more data = more better?
+
+This results $(5+5+1)*5$ sets of hyperparameters.
+
+## Stage 2: simulation
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed.
+From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
+
+### Outcomes 
+Several metrics are used to compare performance of different models over datasets,
+
+| Dataset   |   | Naive Bayes | Random Forests | Support Vector Machine | Logistic Regression | Dense Neural Network |  
+| --------- | - | --- | --- | --- | --- | ---|
+| ptsd      |   | ?   |     |     |    |     | 
+| ace       |   | ?   |     |     |    |     | 
+| hall      |   | ?   |     |     |    |     | 
+| nagtegaal |   | ?   |     |     |    |     | 
+| ....      |   | ?   |     |     |    |     |
+
+? How to compare outcomes of 3 different optimization strategies?
+
+# Appendix A - list of definitions
 Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
@@
 
-The balance strategy
-
-```{r}
-kable(tab, "latex", booktabs = TRUE) %>%
-  kable_styling(full_width = FALSE) %>%
-  column_spec(2, width = "30em") 
-```
 ### Feature Extraction Strategies 
@@
 
-# Appendix A - combinations
+# Appendix B - combinations
 
 ```{r}
-names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
+names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy") #, "Training data [included/excluded]")
 combins %>%

### 2020-02-18 manuscript/test/_book/bookdown-demo.tex
updated analysis plan

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs}
@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
 
@@
 \author{Yihui Xie}
-\date{2020-02-12}
+\date{2020-02-18}
 
@@
 }
-\hypertarget{frontpage}{%
-\chapter{Frontpage}\label{frontpage}}
+\hypertarget{thesis-ferdinands}{%
+\chapter{thesis Ferdinands}\label{thesis-ferdinands}}
 
-This is my thesis project.
+Goal: evaluate performance of different models of the ASReview tool.
 
-\hypertarget{intro}{%
-\chapter{Introduction}\label{intro}}
+\hypertarget{stage-1-hyperparameter-optimization}{%
+\subsection{Stage 1: hyperparameter optimization}\label{stage-1-hyperparameter-optimization}}
 
-You can label chapter and section titles using \texttt{\{\#label\}} after them, e.g., we can reference Chapter \ref{intro}.
-If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \ref{methods}.
+We are testing 5 models on 5 different datasets.
 
-Figures and tables with captions will be placed in \texttt{figure} and \texttt{table} environments, respectively.
+Every model has its own set of hyperparameters.
+The hyperparameters are optimized on the 5 datasets in three different ways:
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{par}\NormalTok{(}\DataTypeTok{mar =} \KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{4}\NormalTok{, }\FloatTok{.1}\NormalTok{, }\FloatTok{.1}\NormalTok{))}
-\KeywordTok{plot}\NormalTok{(pressure, }\DataTypeTok{type =} \StringTok{\textquotesingle{}b\textquotesingle{}}\NormalTok{, }\DataTypeTok{pch =} \DecValTok{19}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
+\begin{itemize}
+\tightlist
+\item
+  1 on 1: maximum performance
+\item
+  4 on 1: cross-validation
+\item
+  5 on 1: more data = more better?
+\end{itemize}
 
-\begin{figure}
+This results \((5+5+1)*5\) sets of hyperparameters.
 
-{\centering \includegraphics[width=0.8\linewidth]{bookdown-demo_files/figure-latex/nice-fig-1}
+\hypertarget{stage-2-simulation}{%
+\subsection{Stage 2: simulation}\label{stage-2-simulation}}
 
-}
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed.
+From these \(5*5*3=75\) simulation studies, performance of the different models is evaluated.
 
-\caption{Here is a nice figure!}\label{fig:nice-fig}
-\end{figure}
+\hypertarget{scripts}{%
+\section{Scripts}\label{scripts}}
 
-Reference a figure by its code chunk label with the \texttt{fig:} prefix, e.g., see Figure \ref{fig:nice-fig}.
-Similarly, you can reference tables generated from \texttt{knitr::kable()}, e.g., see Table \ref{tab:nice-tab}.
+\begin{itemize}
+\tightlist
+\item
+  simulatie:
+\item[$\square$]
+  script die optimalisatie genereert (config files.)
+\item[$\square$]
+  script die \texttt{.ini}'s voor simulatie genereert.
+\end{itemize}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{knitr}\OperatorTok{::}\KeywordTok{kable}\NormalTok{(}
-  \KeywordTok{head}\NormalTok{(iris, }\DecValTok{20}\NormalTok{), }\DataTypeTok{caption =} \StringTok{\textquotesingle{}Here is a nice table!\textquotesingle{}}\NormalTok{,}
-  \DataTypeTok{booktabs =} \OtherTok{TRUE}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
+\hypertarget{strategy}{%
+\chapter{Analysis strategy}\label{strategy}}
 
-\begin{table}
+\hypertarget{datasets}{%
+\section{Datasets}\label{datasets}}
 
-\caption{\label{tab:nice-tab}Here is a nice table!}
-\centering
-\begin{tabular}[t]{rrrrl}
-\toprule
-Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species\\
-\midrule
-5.1 & 3.5 & 1.4 & 0.2 & setosa\\
-4.9 & 3.0 & 1.4 & 0.2 & setosa\\
-4.7 & 3.2 & 1.3 & 0.2 & setosa\\
-4.6 & 3.1 & 1.5 & 0.2 & setosa\\
-5.0 & 3.6 & 1.4 & 0.2 & setosa\\
-\addlinespace
-5.4 & 3.9 & 1.7 & 0.4 & setosa\\
-4.6 & 3.4 & 1.4 & 0.3 & setosa\\
-5.0 & 3.4 & 1.5 & 0.2 & setosa\\
-4.4 & 2.9 & 1.4 & 0.2 & setosa\\
-4.9 & 3.1 & 1.5 & 0.1 & setosa\\
-\addlinespace
-5.4 & 3.7 & 1.5 & 0.2 & setosa\\
-4.8 & 3.4 & 1.6 & 0.2 & setosa\\
-4.8 & 3.0 & 1.4 & 0.1 & setosa\\
-4.3 & 3.0 & 1.1 & 0.1 & setosa\\
-5.8 & 4.0 & 1.2 & 0.2 & setosa\\
-\addlinespace
-5.7 & 4.4 & 1.5 & 0.4 & setosa\\
-5.4 & 3.9 & 1.3 & 0.4 & setosa\\
-5.1 & 3.5 & 1.4 & 0.3 & setosa\\
-5.7 & 3.8 & 1.7 & 0.3 & setosa\\
-5.1 & 3.8 & 1.5 & 0.3 & setosa\\
-\bottomrule
-\end{tabular}
-\end{table}
+\begin{itemize}
+\tightlist
+\item
+  ptsd
+\item
+  ace
+\item
+  hall
+\item
+  nagtegaal - van PhD van Lars
+\item
+  medische van Jan
+\end{itemize}
 
-You can write citations, too.
-For example, we are using the \textbf{bookdown} package (Xie \protect\hyperlink{ref-R-bookdown}{2020}) in this sample book, which was built on top of R Markdown and \textbf{knitr} (Xie \protect\hyperlink{ref-xie2015}{2015}).
+\hypertarget{models}{%
+\section{Models}\label{models}}
 
-\hypertarget{literature}{%
-\chapter{Literature}\label{literature}}
+(input table here?)
 
-Here is a review of existing methods.
+\begin{itemize}
+\tightlist
+\item
+  Naive Bayes
+\item
+  Random Forests
+\item
+  Support Vecor Machine (doc2vec)
+\item
+  Logistic Regression
+\item
+  Dense Neural Network (doc2vec)
+\end{itemize}
 
-\hypertarget{methods}{%
-\chapter{Methods}\label{methods}}
+The other parameters remain fixed over the 5 models:
 
-We describe our methods in this chapter.
+\begin{itemize}
+\tightlist
+\item
+  Feature extraction = tf-idf
+\item
+  Query Strategy = max
+\item
+  Balance Strategy = triple
+\item
+  n\_instances=10 (number of papers each query)
+\item
+  n\_prior\_included = 5
+\item
+  n\_prior\_excluded = 5
+\item
+  mix\_ratio = 0.95 (95\% max, 5\% random)
+\end{itemize}
+
+\hypertarget{hyperparameters}{%
+\section{Hyperparameters}\label{hyperparameters}}
 
@@
 
-\hypertarget{methods-1}{%
-\section{Methods}\label{methods-1}}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
-\hypertarget{appendix-a}{%
-\chapter{Appendix A}\label{appendix-a}}
-
-We have finished a nice book.
-
-\hypertarget{refs}{}
-\begin{cslreferences}
-\leavevmode\hypertarget{ref-xie2015}{}%
-Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{http://yihui.name/knitr/}.
-
-\leavevmode\hypertarget{ref-R-bookdown}{}%
----------. 2020. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. \url{https://github.com/rstudio/bookdown}.
-\end{cslreferences}
+\hypertarget{list-of-definitions}{%
+\chapter{List of definitions}\label{list-of-definitions}}
 

### 2020-02-18 manuscript/test/index.Rmd
updated analysis plan

@@
 
-# Frontpage
-This is my thesis project.
+# thesis Ferdinands
+Goal: evaluate performance of different models of the ASReview tool.
+
+### Stage 1: hyperparameter optimization
+We are testing 5 models on 5 different datasets.
+
+Every model has its own set of hyperparameters.
+The hyperparameters are optimized on the 5 datasets in three different ways:
+
+- 1 on 1: maximum performance 
+- 4 on 1: cross-validation 
+- 5 on 1: more data = more better?
+
+This results $(5+5+1)*5$ sets of hyperparameters.
+
+### Stage 2: simulation
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed.
+From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
+
+## Scripts 
+  - simulatie:
+- [ ] script die optimalisatie genereert (config files.)
+- [ ] script die `.ini`'s voor simulatie genereert.
 

### 2020-02-18 manuscript/test/R/asr-parameters.R

@@ -53,7 +53,7 @@
   
   # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
   # and do not vary the balance strategy. 
-  params$model <- params[["model"]][3:7]
+  params$model <- params[["model"]][4:7]
   params$balance_strategy <- NULL
   params$feature_extraction <- params[["feature_extraction"]][1:4]
   params$training_data <- c("10/10", "5/5", "5/10")
@@ -70,7 +70,7 @@
   names(params$training_data) <- params$training_data
   words <- params 
 
-  words$model <- c("2-Layer Neural Network", "Naive Bayes", "Random Forest", "Support Vector Machine", "Logistic Regression")
+  words$model <- c("Naive Bayes", "Random Forest", "Support Vector Machine", "Logistic Regression")
   words$query_strategy <- c("Cluster Sampling", "Maximum Sampling",
                             "Cluster * Maximum  Sampling", 
                             "Maximum * Uncertainty Sampling", 

### 2020-02-25 manuscript/drafts/manuscript.Rmd
knit
update notes, add manuscript texts on data, update references

@@
 ---
-title: "Manuscxript drafts"
+title: "Manuscript drafts"
 author: "Gerbrich Ferdinands"
@@
 library(kableExtra)
+library(captioner)
+library(glue)
+
 # load model parameters 
 source("asr-parameters.R")
+
+# path to all R folder
+pathRdata <- "../../R/data/"
 ```
@@
 ```
-# Analysis strategy
+
+```{r all tables, results = 'hide'}
+table_nums <- captioner(prefix = "Table")
+table_nums(name = "datasets", caption = "Descriptive statistics on articles and resulting datasets for each original systematic review.")
+```
+
+# Introduction
+SR are booming
+ML tools as well
+
+[@PRISMA-PGroup2015]
+
+What must be the objective of our tool?
+
+Selecting papers is a two-step process: abstract & fulltext screening
+
+# Methods
 Goal: evaluate performance of different models of the ASReview tool. 
+The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
+annotated include/exclude
+
+## Datasets
+The data consists of five open datasets on systematic reviews from various research areas. 
+All datasets are openly available.
+The raw files were preprocessed. Duplicate entries were removed.
+Entries with missing abstracts were removed. 
+Preprocessing scripts can be found on the GitHub repository
+
+Descriptive statistics on the five systematic reviews can be found in Table `r table_nums("datasets", display = "cite")`.
+
+```{r}
+# datasets table
+load(paste0(pathRdata, "datasets_table.Rdata"))
+
+tibble(Dataset = names(all), 
+       #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
+       `No. studies` = sapply(all, function(x) x[1,1]), 
+       `No. selected for fulltext screening` = sapply(all, function(x) x[1,2]),
+       `No. final inclusions` = sapply(all, function(x) x[1,3]),
+       `Inclusion rate (%)` = sapply(all, function(x) round(x[1,3]/x[1,1]*100,2)),
+       `No. studies in test collection` = sapply(all, function(x) x[3,1]),
+       `No. selected for fulltext screening test collection` = sapply(all, function(x) x[3,2]),
+       `No. final inclusions in test collection` = sapply(all, function(x) x[3,3]),
+       `Inclusion rate in test collection (%)` = sapply(all, function(x) round(x[3,3]/x[3,1]*100,2))
+       ) %>%
+  # knitr kable
+  kable(format = "latex",
+        booktabs = TRUE,
+        caption = table_nums("datasets")) %>%
+  kable_styling(full_width = TRUE) %>%
+  add_header_above(c("", "Original study" = 4, "Test collection" = 4))
+
+  # add citations
+```
+
+The inclusion rate is ... data is imbalanced. 
+what is the philosophy
+False negatives must be avoided ... 
+The cost of a false negative outweighs the cost of a false positive. 
+Note that we assume the oracle/original user to hold the truth. 
+This is of course not always the case.
+
+## Models 
+Five different models were applied on the data.
+
+### Optimizing Hyperparameters 
+Every model has its own hyperparameters. 
+For every model, the hyperparameters are optimized three times, arriving at three versions of the model:
 
@@
 ```{r}
-kable(tab, "latex", booktabs = TRUE, col.names = "Configurations") %>%
-  kable_styling(full_width = FALSE) %>%
-  column_spec(2, width = "30em") 
+tab %>%
+kable(format = "latex", 
+      booktabs = TRUE, 
+      col.names = "Configurations") %>%
+  kable_styling(full_width = TRUE)
 ```
@@
 
-## Stage 1: hyperparameter optimization
+### Stage 1: hyperparameter optimization
 We are going to test 5 models on 5 different datasets.
 
-### Datasets
+#### ACE
+The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.
+
+WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
 
 #### ptsd
-#### ace
+The review  
+The data
+
 #### hall 
-#### nagtegaal - van PhD van Lars
-#### medische van Jan
+The review [@Hall2012], is reviewed in [@Yu2016].
+
+#### nudging
+The review [@Nagtegaal2019]
+The data [@Nagtegaal2019a]
+
+Paper says: 
+- systematic search n = 2006
+- full text screening n = 377
+- included in synthesis n = 100
+
+Open data online says:
+
+- systematic search n = 
+- full text screening n = 
+- included in synthesis n = 101 (18?)
+
+abstract excel sheet private says: 
+- systematic search n = 2018
+- full text screening n = 
+- included in synthesis n = 118
+
+Difference in 18 inclusions = systematic reviews. to exclude/include?
+
+#### Wilson
+The review [@Appenzeller-Herzog2019]
+The dataset [@Appenzeller-Herzog2020]
+
+- systematic search n = 3453
+- full text screening n = 174
+- included in synthesis n = 26
 
@@
 row.names(tabbie) <- NULL
+
 tabbie %>%
-  kable(col.names = names(words)[1:3], format = "latex")
+  kable(col.names = names(words)[c(1,3)], 
+        format = "latex",
+        booktabs = TRUE)
 ```
@@
 - 1 on 1: maximum performance
+
+$$ d = D $$
 - 4 on 1: cross-validation 
+$$ d \notin D$$
+
+$$ D = {1, 2, 3, 4}$$
+
 - 5 on 1: more data = more better?
+
+$$ d \in D $$
 
@@
 ? How to compare outcomes of 3 different optimization strategies?
+
+## Evaluation
 
@@
 WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
-Typically, WSS is measured at a recall of 0.95.
+Typically, WSS is measured at a recall of 0.95. Reasonable because..
 
-$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall ) $$
+$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$
 
@@
 #### ROC/AUC
+
+Is performance related to some characteristic (n, inclusion rate, ...)
+
+## Cross-validation
+Should give an accurate estimate of maximum performance / future systematic reviews to be performed.
 

### 2020-02-25 R/datasets.R

@@ -1,0 +1,115 @@
+# this script is for checking all the raw vs preprocessed data, that are on datasets GH repo. 
+library(tidyverse)
+template <- data.frame(search = rep(0,3),
+                       ftext = rep(0, 3), 
+                       incl = rep(0,3),
+                       row.names = c("paper", "raw", "asreview"))
+
+################################################################################
+## Nagtegaal dataset ###########################################################
+################################################################################ 
+# original ---------------------------------------------------------------------
+nagtegaal <- data.frame(paper = c(2006, 377, 100), 
+                        raw = rep(0, 3), 
+                        asreview = rep(0,3),
+                        row.names = c("search", "ftext", "incl"))
+nagtegaal <- t(nagtegaal)
+
+# raw --------------------------------------------------------------------------
+# see nagtegaal.R file
+# asreview ---------------------------------------------------------------------
+abstracts <- readxl::read_xlsx("data/nagtegaal.xlsx")
+table(abstracts$included)
+# duplicated abstracts ?? 
+anyDuplicated(abstracts$abstract)
+abstracts[duplicated(abstracts$abstract),]
+
+nagtegaal["asreview",] <- c(length(abstracts$included),
+                            NA,
+                            sum(abstracts$included)
+                            )
+
+################################################################################
+## Wilson dataset ##############################################################
+################################################################################
+wilson <- template
+wilson["paper", ] <- c(3453, 174, 26)
+
+# raw --------------------------------------------------------------------------
+w_ftext <- read.csv("../datasets/raw/DOKU_All FT-Screening_20200116_cap.csv")
+w_incl <- read.csv("../datasets/raw/DOKU_All Included_20200116_cap.csv")
+w_all <- read.csv("../datasets/raw/DOKU_All TiAb-Screening_20200116_cap.csv")
+wilson["raw", ] <- c(nrow(w_all), nrow(w_ftext), nrow(w_incl))
+
+# asreview ---------------------------------------------------------------------
+w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv",
+                  header=T)
+
+wilson ["asreview",] <- c(nrow(w_asr), 
+                          sum(w_asr$label_abstract_screening, na.rm = TRUE),
+                          sum(w_asr$label_included))
+wilson
+# difference in asreview and raw data is because of 16 duplicates. 
+wilson[2,1] - wilson[3,1]
+
+################################################################################
[…]

### 2020-02-25 manuscript/drafts/manuscript.Rmd
update manuscript   - update notes   - update bookdown files

@@
 
-# path to all R folder
 pathRdata <- "../../R/data/"
+
 ```
@@
 
-Descriptive statistics on the five systematic reviews can be found in Table `r table_nums("datasets", display = "cite")`.
+Descriptive statistics on the five systematic reviews can be found in `r table_nums("datasets", display = "cite")`.
 
@@
 Five different models were applied on the data.
+
+Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
+The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
+
+A classical example of word embeddings is 'bag of words'.
+For each each text, the number of occurrences of each word is stored.
+This leads to n features, where n is the number of distinct words in the texts.
+[@scikit-learn]
+
+Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
+
+corpus = all the text:
+
+ASReview implements several feature extraction strategies. The following will be compared:
+
+The model is typically a learning algorithm used to predict the relevance of text.
+
+Active learning = 
+increasing classification performance with every query. 
+The query strategy determines the way unlabeled papers are queried to the researcher.
+
+[@modAL2018]
+
+####
 
@@
 #### hall 
-The review [@Hall2012], is reviewed in [@Yu2016].
+The review [@Hall2012], is reviewed in [@Yu2018a].
 
@@
 # Appendix A - list of definitions
-Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
-The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
-
-A classical example of word embeddings is 'bag of words'.
-For each each text, the number of occurrences of each word is stored.
-This leads to n features, where n is the number of distinct words in the texts.
-[@scikit-learn]
-
-Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
-
-corpus = all the text:
-
-ASReview implements several feature extraction strategies. The following will be compared:
-
-The model is typically a learning algorithm used to predict the relevance of text.
-
-Active learning = 
-increasing classification performance with every query. 
-The query strategy determines the way unlabeled papers are queried to the researcher.
-
-[@modAL2018]
 

### 2020-02-25 manuscript/test/index.Rmd
update manuscript   - update notes   - update bookdown files

@@
 ), 'packages.bib')
+
+# load all necessary packages
+source("R/packages.R")
+
+# path to all R folder
+pathRdata <- "../../R/data/"
+
+# set chunk default options knitr
+knitr::opts_chunk$set(echo = FALSE)
+
 ```

### 2020-02-25 manuscript/test/R/packages.R

@@ -1,0 +1,6 @@
+library(tidyverse)
+library(knitr)
+library(xtable)
+library(kableExtra)
+library(captioner)
+library(glue)

### 2020-03-02 manuscript/drafts/manuscript.Rmd
update manuscript and meeting notes

@@
 
+#### Introduction 
+#### Methods
+A convenience sample of 5 existing systematic reviews on varying topics was collected.
+
+#### Results
+#### Discussion
+
+\newpage
 # Introduction
@@
 ML tools as well
+Literature reviews 
+machine learning algorithms have been proposed to reduce workload in abstract screening.
+
+- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
+- justification - 
+- background 
+- guidance to reader 
+- summary/conclusion
 
@@
 
+\newpage
 # Methods
@@
 The screening process is simulated using ASReview, seeing if the original inclusions replicate.
-annotated include/exclude
 
 ## Datasets
-The data consists of five open datasets on systematic reviews from various research areas. 
-All datasets are openly available.
-The raw files were preprocessed. Duplicate entries were removed.
+The algorithm will be tested on five systematic reviews from various research areas. 
+test datasets serve as systematic search results, then perform active learning to detect inclusions.
+
+#### software 
+A review on fault prediction in software engineering by [@Hall2012]. 
+The dataset is reviewed from [@Yu2018a] who collected datasets on literature reviews from the software engineering field.
+
+#### nudging
+review [@Nagtegaal2019]
+The data [@Nagtegaal2019a]
+
+Difference in 18 inclusions = systematic reviews. to exclude/include?
+
+#### ptsd
+The review [@vandeSchoot2018]
+The data [@Winter2020]
+
+#### Wilson
+The review [@Appenzeller-Herzog2019]
+The dataset [@Appenzeller-Herzog2020]
+
+- systematic search n = 3453
+- full text screening n = 174
+- included in synthesis n = 26
+
+... dataset is ...
+
+Descriptive statistics on the reviews can be found in `r table_nums("datasets", display = "cite")`. 
+All datasets accompanying the systematic reviews are openly published. 
+The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.
+
+For every SR, the raw datafiles were preprocessed into a test dataset.
+
+These test datasets contain authors, title, abstract and annotation of whether the entry was included in the final review or not (0/1).
+
 Entries with missing abstracts were removed. 
+Duplicate entries were removed. 
 Preprocessing scripts can be found on the GitHub repository
-
-Descriptive statistics on the five systematic reviews can be found in `r table_nums("datasets", display = "cite")`.
 
@@
 We are going to test 5 models on 5 different datasets. 
-
 #### ACE
@@
 The data
-
-#### ptsd
-The review  
-The data
-
-#### hall 
-The review [@Hall2012], is reviewed in [@Yu2018a].
-
-#### nudging
-The review [@Nagtegaal2019]
-The data [@Nagtegaal2019a]
-
-Paper says: 
-- systematic search n = 2006
-- full text screening n = 377
-- included in synthesis n = 100
-
-Open data online says:
-
-- systematic search n = 
-- full text screening n = 
-- included in synthesis n = 101 (18?)
-
-abstract excel sheet private says: 
-- systematic search n = 2018
-- full text screening n = 
-- included in synthesis n = 118
-
-Difference in 18 inclusions = systematic reviews. to exclude/include?
-
-#### Wilson
-The review [@Appenzeller-Herzog2019]
-The dataset [@Appenzeller-Herzog2020]
-
-- systematic search n = 3453
-- full text screening n = 174
-- included in synthesis n = 26
 
@@
 ## Stage 2: simulation
-for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed.
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
 From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
 
+Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
 ### Outcomes 
+For each model, 
 Several metrics are used to compare performance of different models over datasets,
@@
 
+\newpage
+
+# Results
+
+\newpage
+# Discussion
+
+\newpage
 # Appendix A - list of definitions

### 2020-03-02 manuscript/test/bookdown-demo.tex
update manuscript and meeting notes

--- 2020-02-18 manuscript/test/_book/bookdown-demo.tex
@@
 \setcounter{secnumdepth}{5}
+\usepackage{booktabs}
+\usepackage{amsthm}
+\makeatletter
+\def\thm@space@setup{%
+  \thm@preskip=8pt plus 2pt minus 4pt
+  \thm@postskip=\thm@preskip
+}
+\makeatother
+\usepackage[]{natbib}
+\bibliographystyle{apalike}
 
@@
 \author{Yihui Xie}
-\date{2020-02-18}
+\date{2020-02-25}
 
@@
 
-\hypertarget{strategy}{%
-\chapter{Analysis strategy}\label{strategy}}
+\hypertarget{introduction-intro}{%
+\chapter{Introduction (\#intro)}\label{introduction-intro}}
+
+SR are booming
+ML tools as well
+
+\citep{PRISMA-PGroup2015}
+
+What must be the objective of our tool?
+
+Selecting papers is a two-step process: abstract \& fulltext screening
+
+\hypertarget{current-solutions}{%
+\section{Current solutions}\label{current-solutions}}
+
+Workload savings 30-70 percent, at a loss of 5\% of relevant studies \citep{Omara-Eves2015}.
+
+\hypertarget{methods-methods}{%
+\chapter{Methods (\#methods)}\label{methods-methods}}
+
+Goal: evaluate performance of different models of the ASReview tool.
+The screening process is simulated using ASReview, seeing if the original inclusions replicate.
+annotated include/exclude
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  ptsd
-\item
-  ace
-\item
-  hall
-\item
-  nagtegaal - van PhD van Lars
-\item
-  medische van Jan
-\end{itemize}
+The data consists of five open datasets on systematic reviews from various research areas.
+All datasets are openly available.
+The raw files were preprocessed. Duplicate entries were removed.
+Entries with missing abstracts were removed.
+Preprocessing scripts can be found on the GitHub repository
+
+Descriptive statistics on the five systematic reviews can be found in Table Table 1.
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}Table  1: Descriptive statistics on articles and resulting datasets for each original systematic review.}
+\centering
+\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{4}{c}{Original study} & \multicolumn{4}{c}{Test collection} \\
+\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
+Dataset & No.
+studies & No.
+selected for fulltext screening & No.
+final inclusions & Inclusion rate (\%) & No.
+studies in test collection & No.
+selected for fulltext screening test collection & No.
+final inclusions in test collection & Inclusion rate in test collection (\%)\\
+\midrule
+nudging & 2006 & 377 & 100 & 4.99 & 2018 & NA & 118 & 5.85\\
+wilson & 3453 & 174 & 26 & 0.75 & 3437 & 174 & 26 & 0.76\\
+ptsd & 6185 & 363 & 34 & 0.55 & 5782 & 356 & 38 & 0.66\\
+software & 8911 & NA & 106 & 1.19 & 8911 & NA & 104 & 1.17\\
+ace & 2544 & NA & 41 & 1.61 & 2544 & NA & 41 & 1.61\\
+\bottomrule
+\end{tabu}
+\end{table}
+
+The inclusion rate is \ldots{} data is imbalanced.
+what is the philosophy
+False negatives must be avoided \ldots{}
+The cost of a false negative outweighs the cost of a false positive.
+Note that we assume the oracle/original user to hold the truth.
+This is of course not always the case.
 
@@
 
-(input table here?)
+Five different models were applied on the data.
+
+\hypertarget{optimizing-hyperparameters}{%
+\subsection{Optimizing Hyperparameters}\label{optimizing-hyperparameters}}
+
+Every model has its own hyperparameters.
+For every model, the hyperparameters are optimized three times, arriving at three versions of the model:
+
+\hypertarget{the-software}{%
+\chapter{The software}\label{the-software}}
+
+ASReview takes the following parameters/arguments:
+
+\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X}
+\toprule
+  & Configurations\\
+\midrule
+Models & Naive Bayes, Random Forest, Support Vector Machine, Logistic Regression\\
+Query Strategies & Cluster Sampling, Maximum Sampling, Cluster * Maximum  Sampling, Maximum * Uncertainty Sampling, Maximum * Random Sampling, Cluster * Uncertainty Sampling, Cluster * Random Sampling\\
+Feature extraction strategies & Doc2Vec, TF-IDF, sbert, embeddingIdf\\
+\bottomrule
+\end{tabu}
+
+Use these inputs to predict relevance of papers.
+
+\hypertarget{stage-1-hyperparameter-optimization-1}{%
+\subsection{Stage 1: hyperparameter optimization}\label{stage-1-hyperparameter-optimization-1}}
+
+We are going to test 5 models on 5 different datasets.
+
+\hypertarget{ace}{%
+\subsubsection{ACE}\label{ace}}
+
+The ACEInhibitors dataset from the study by \citep{Cohen2006}. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.
+
+\href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in \citep{Cohen2006}. (5x2 crossvalidation). Can we beat this?
+The data
+
+\hypertarget{ptsd}{%
+\subsubsection{ptsd}\label{ptsd}}
+
+The review\\
+The data
+
+\hypertarget{hall}{%
+\subsubsection{hall}\label{hall}}
+
+The review \citep{Hall2012}, is reviewed in \citep{Yu2016}.
+
+\hypertarget{nudging}{%
+\subsubsection{nudging}\label{nudging}}
+
+The review \citep{Nagtegaal2019}
+The data \citep{Nagtegaal2019a}
+
+Paper says:
+- systematic search n = 2006
+- full text screening n = 377
+- included in synthesis n = 100
+
+Open data online says:
+
+\begin{itemize}
+\tightlist
+\item
+  systematic search n =
+\item
+  full text screening n =
+\item
+  included in synthesis n = 101 (18?)
+\end{itemize}
+
+abstract excel sheet private says:
+- systematic search n = 2018
+- full text screening n =
+- included in synthesis n = 118
+
+Difference in 18 inclusions = systematic reviews. to exclude/include?
+
+\hypertarget{wilson}{%
+\subsubsection{Wilson}\label{wilson}}
+
+The review \citep{Appenzeller-Herzog2019}
+The dataset \citep{Appenzeller-Herzog2020}
+
+\begin{itemize}
+\tightlist
+\item
+  systematic search n = 3453
+\item
+  full text screening n = 174
+\item
+  included in synthesis n = 26
+\end{itemize}
+
+\hypertarget{models-1}{%
+\subsection{Models}\label{models-1}}
 
@@
 \item
-  Support Vecor Machine (doc2vec)
+  Support Vecor Machine
 \item
@@
 \item
-  Dense Neural Network (doc2vec)
+  Dense Neural Network
 \end{itemize}
+
+Or, more specific:
+
+\begin{tabular}{ll}
+\toprule
+Models & Feature extraction strategies\\
+\midrule
+nb & tfidf\\
+rf & tfidf\\
+svm & tfidf\\
+lr & doc2vec\\
+NA & NA\\
+\bottomrule
+\end{tabular}
 
@@
 \tightlist
-\item
-  Feature extraction = tf-idf
 \item
@@
   n\_prior\_excluded = 5
-\item
-  mix\_ratio = 0.95 (95\% max, 5\% random)
 \end{itemize}
@@
 \hypertarget{hyperparameters}{%
-\section{Hyperparameters}\label{hyperparameters}}
+\subsection{Hyperparameters}\label{hyperparameters}}
+
+Every model has its own set of hyperparameters:
+
+\hypertarget{optimization}{%
+\subsection{Optimization}\label{optimization}}
+
+The hyperparameters are optimized on the 5 datasets in three different ways:
+
+\begin{itemize}
+\tightlist
+\item
+  1 on 1: maximum performance
+\end{itemize}
+
+\[ d = D \]
+- 4 on 1: cross-validation
+\[ d \notin D\]
+
+\[ D = {1, 2, 3, 4}\]
+
+\begin{itemize}
+\tightlist
+\item
+  5 on 1: more data = more better?
+\end{itemize}
+
+\[ d \in D \]
+
+This results \((5+5+1)*5\) sets of hyperparameters.
+
+\hypertarget{stage-2-simulation-1}{%
+\section{Stage 2: simulation}\label{stage-2-simulation-1}}
+
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed.
+From these \(5*5*3=75\) simulation studies, performance of the different models is evaluated.
+
+\hypertarget{outcomes}{%
+\subsection{Outcomes}\label{outcomes}}
+
+Several metrics are used to compare performance of different models over datasets,
+
+\begin{longtable}[]{@{}lllllll@{}}
+\toprule
+\begin{minipage}[b]{0.29\columnwidth}\raggedright
+Dataset\strut
+\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
+Naive Bayes\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
+Random Forests\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
+Support Vector Machine\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
+Logistic Regression\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
+Dense Neural Network\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.29\columnwidth}\raggedright
+ptsd\strut
+\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+?\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.29\columnwidth}\raggedright
+ace\strut
+\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+?\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.29\columnwidth}\raggedright
+hall\strut
+\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+?\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.29\columnwidth}\raggedright
+nagtegaal\strut
+\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+?\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.29\columnwidth}\raggedright
+\ldots.\strut
+\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+?\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
+\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
+
+? How to compare outcomes of 3 different optimization strategies?
+
+\hypertarget{evaluation}{%
+\section{Evaluation}\label{evaluation}}
 
@@
 
-\includegraphics{figs/myfirstsim/Figure_1.png}
+\includegraphics[width=17.78in]{figs/myfirstsim/Figure_1}
 
@@
 
-\includegraphics{figs/myfirstsim/Figure_2.png}
+\includegraphics[width=17.78in]{figs/myfirstsim/Figure_2}
 
@@
 
-\includegraphics{figs/myfirstsim/Figure_3.png}
+\includegraphics[width=17.78in]{figs/myfirstsim/Figure_3}
 
@@
 
-\includegraphics{figs/myfirstsim/computation.png}
+\includegraphics[width=26.42in]{figs/myfirstsim/computation}
 2191 was best performing with a loss of 0.1124
 
-\includegraphics{figs/myfirstsim/optmizationresult.png}
+\includegraphics[width=23in]{figs/myfirstsim/optmizationresult}
 
@@
 
+  \bibliography{book.bib,packages.bib}
+
 \end{document}

### 2020-03-02 datasets/data_preprocessing.Rmd
Notebook on preprocessing systematic review datasets
- add directory with test datasets
- add descriptives on inclusions for every (version of) the dataset .

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
template <- data.frame(search = rep(0,4), # papers obtained in systematic search
                       ftext = rep(0, 4), # number of abstract inclusions
                       incl = rep(0,4), # papers included in systematic review
                       row.names = c("paper", # numbers reported in the publication
                                     "raw", # numbers published on raw dataset
                                     "asreview",
                                     "test")) # numbers in test dataset asreview

# function to compute descriptives from dataset
data_descr <- function(data){
  return(c(nrow(data), # all papers obtained in the systematic search
           sum(data$inclusion_code > 0), # number of abstract inclusions
           sum(data$included))) # papers included in systematic review
}
```

This notebook processes all five systematic review datasets into datasets that can be used for testing asreview.

## nudging dataset 
```{r}
# by Rosanna Nagtegaal
nudging <- template
nudging["paper", ] <- c(2006, 377, 100) 
```

## PTSD dataset
```{r}
ptsd <- template 
ptsd["paper", ] <- c(6185, 363, 34) # from flowchart

# raw --------------------------------------------------------------------------
ptsd["raw", ]

```

```{r}
# asreview ---------------------------------------------------------------------
ptsd_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Van_de_Schoot_PTSD/output/PTSD_VandeSchoot_18.csv",
                     header=T)

ptsd["asreview", ] <- data_descr(ptsd_asr)
```

Now, remove duplicate entries and empty abstracts to arrive at test set. 
```{r}
ptsd_test <- ptsd_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
```

There are 38 inclusions in this dataset, should be 34. 
Een vraag! De 'bayesian PTSD-trajectory analysis' kent 34 final inclusions. 
Voor (het quALITS paper dan, denk ik?) 38 inclusies waren. 
```{r}
# get rid of 4 extra inclusions (see log book)
drop_id <- 
  ptsd_test %>%
  filter(included == 1, 
         str_detect(authors, "Sterling, M., Hendrikz, J., Kenardy, J.") |
         str_detect(authors, "Hou") |
         str_detect(authors, "Mason") |
         str_detect(authors, "Pérez")) %>%
  select(id)
drop_id <- drop_id$id

ptsd_test <- ptsd_test[!(ptsd_test$id %in% drop_id), ]

```

Save the test dataset.
```{r}
# save test file
write.csv(ptsd_test %>%
            select(authors, title, abstract, included, inclusion_code), # select relevant columns
          "test_datasets/ptsd.csv")
```

Derive statistics in final test set.
```{r}
ptsd["test", ] <- data_descr(ptsd_test)
```

## software

### 2020-03-03 datasets/data_preprocessing.Rmd
Methods
- add information on simulation

@@
 
+## ace dataset 
 ## nudging dataset 
@@
 ## software
+
+## wilson
+
+# Save descriptive statistics
+
+```{r eval = FALSE}
+# put everything together in list. 
+all <- list(ace = ace,
+            nudging = nudging,
+            ptsd = ptsd,
+            software = software,
+            wilson = wilson)
+
+# save datafile, to serve as data for descriptive table in manuscript
+save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
+```

### 2020-03-03 manuscript/drafts/manuscript.Rmd
Methods
- add information on simulation

@@
 
-pathRdata <- "../../R/data/"
+#pathRdata <- "../../R/data/"
+pathRdata <- "data/"
 
@@
 
+## active learning for systematic reviews 
+achine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
+The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
+
+A classical example of word embeddings is 'bag of words'.
+For each each text, the number of occurrences of each word is stored.
+This leads to n features, where n is the number of distinct words in the texts.
+[@scikit-learn]
+
+Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
+
+corpus = all the text:
+
+ASReview implements several feature extraction strategies. The following will be compared:
+
+The model is typically a learning algorithm used to predict the relevance of text.
+
+Active learning = 
+increasing classification performance with every query. 
+The query strategy determines the way unlabeled papers are queried to the researcher.
+
+[@modAL2018]
+
 \newpage
@@
 The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
+What would happen if the citation screening would have been performed using asreview?
 
@@
 test datasets serve as systematic search results, then perform active learning to detect inclusions.
+
+#### ace
+The ACEInhibitors dataset from the study by [@Cohen2006].
+The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.
+
+a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.
+
+WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
 
@@
 #### ptsd
-The review [@vandeSchoot2018]
-The data [@Winter2020]
+A review [@vandeSchoot2018] on longitudinal studies on posttraumatic stress symptoms assessed after exposure to trauma. 
+The corresponding dataset [@Winter2020].
 
@@
 
-## Models 
-Five different models were applied on the data.
+## Simulations
+The original systematic review is reproduced using five different models.
 
-Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
-The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
+A simulation consists of the following elements:
+we have a model $M$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
+The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$.
 
-A classical example of word embeddings is 'bag of words'.
-For each each text, the number of occurrences of each word is stored.
-This leads to n features, where n is the number of distinct words in the texts.
-[@scikit-learn]
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
+From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
 
-Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
-
-corpus = all the text:
-
-ASReview implements several feature extraction strategies. The following will be compared:
-
-The model is typically a learning algorithm used to predict the relevance of text.
-
-Active learning = 
-increasing classification performance with every query. 
-The query strategy determines the way unlabeled papers are queried to the researcher.
-
-[@modAL2018]
-
-####
+Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
 
@@
 We are going to test 5 models on 5 different datasets.
-#### ACE
-The ACEInhibitors dataset from the study by [@Cohen2006]. a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.
-
-WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
 
@@
 
-## Stage 2: simulation
-for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
-From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
-
-Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
 ### Outcomes 

### 2020-03-03 manuscript/drafts/manuscript.Rmd
update introduction

@@
 # Introduction
-SR are booming
-ML tools as well
-Literature reviews 
-machine learning algorithms have been proposed to reduce workload in abstract screening.
+Systematic Reviews (SR's) are booming - but they are a lot of work
+Various machien learning tools have been proposed to reduce workload in abstract screening.
 
@@
 
+A SR can be divided into phases. 
+Everything starts with a **systematic search**, leading to
+then citation screening is performed, then full-text screening
 [@PRISMA-PGroup2015]
 
-What must be the objective of our tool?
+What must be the objective of our tool?:
+It is the tedious task citation screening part where loads of time can be saved.
+
+models are designed in a 'realistic' way (you have some inclusions)
 
@@
 [@modAL2018]
+
+## Background
+[@Yu2018a, @Yu2019] simulated 32 svm classifiers, on software engineering.
+
+In terms of Yu et al, we adopt .CT.
+
+Our extensions is that we try different classifiers, on more datasets.
 
@@
 
-A simulation consists of the following elements:
-we have a model $M$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
+A simulation is of one model on one dataset. 
+we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
 The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
-
+We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
 for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
@@
 Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
+
+assumptions
+
+ - decisions of the original SR are **ground truth** (benchmark) (oracle)
+
+ - binary classifications: relevant/irrelevant
 

### 2020-03-04 datasets/data_preprocessing.Rmd
Adding cleaned up datasets
- preprocessing dataset scripts ace, software, and wilson.
- add meeting notes for march 5th

--- 2020-03-02 datasets/data_preprocessing.Rmd
@@
 
+## ace dataset 
+```{r}
+ace <- template
+ace["paper", ] <- c(2544, NA, round(2544*0.0160))
+
+# raw --------------------------------------------------------------------------
+# original paper not to linked directly. cannot be retrieved? 
+# checked dataset online by cohen et al. 
+#https://dmice.ohsu.edu/cohenaa/systematic-drug-class-review-data.html
+ace["raw", ] <- c(2544, NA, 41)
+
+# asreview ---------------------------------------------------------------------
+ace_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Cohen_EBM/output/ACEInhibitors.csv",
+                     header=T)
+
+ace["asreview", ] <- c(nrow(ace_asr),
+                       NA,
+                       sum(ace_asr$label_included))
+```
+
+Create test dataset
+```{r}
+ace_test <- ace_asr %>%
+  drop_na(abstract) %>% # drop entries with missing abstracts
+  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
+
+ace["test", ] <- c(nrow(ace_test),
+                   NA,
+                   sum(ace_test$label_included))
+```
+
+```{r}
+# select columns
+ace_test <- ace_test %>%
+       select(authors, title, abstract, label_included) # select relevant columns
+
+# save test file
+write.csv(ace_test,
+          "test_datasets/ace.csv")
+```
+
 ## nudging dataset 
@@
 nudging["paper", ] <- c(2006, 377, 100) 
+```
+
+```{r}
+# data is not public yet
+# raw
+# asreview
 ```
@@
 
+# get rid of 4 papers
 ptsd_test <- ptsd_test[!(ptsd_test$id %in% drop_id), ] 
-
 ```
@@
 ```{r}
+# finalize dataset and save 
+ptsd_test <- ptsd_test %>%
+            select(authors, title, abstract, included, inclusion_code) # select relevant columns
 # save test file
-write.csv(ptsd_test %>%
-            select(authors, title, abstract, included, inclusion_code), # select relevant columns
+write.csv(ptsd_test,
           "test_datasets/ptsd.csv")
@@
 ## software
+```{r}
+hall <- template
+# or do it in the paper from the Yu et al study? yes. 
+hall["paper", ] <- c(8911, NA, 104)
+
+# raw --------------------------------------------------------------------------
+h_raw <- read.csv("https://zenodo.org/record/1162952/files/Hall.csv",
+                  header=T)
+
+hall["raw", ] <- c(length(h_raw$Document.Title),
+                   NA,
+                   sum(h_raw$label == "yes"))
+
+# asreview ---------------------------------------------------------------------
+hall_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Four%20Software%20Engineer%20Data%20Sets/Software%20Engineering%201%20Hall.csv",
+                     header=T)
+
+hall["asreview", ] <- data_descr(hall_asr)
+
+```
+
+creating test dataset
+```{r}
+hall_test <- hall_asr %>%
+   drop_na(abstract) %>% # drop entries with missing abstracts
+   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+hall["test", ] <- data_descr(hall_test)
+
+write.csv(hall_test , # select relevant columns
+          "test_datasets/software.csv")
+```
+
+## wilson
+
+```{r}
+wilson <- template
+wilson["paper", ] <- c(3453, 174, 26)
+
+# raw --------------------------------------------------------------------------
+# w_ftext <- read.delim("../datasets/raw/DOKU_All FT-Screening_20200116_cap.txt")
+# w_incl <- read.csv("../datasets/raw/DOKU_All Included_20200116_cap.csv")
+# w_all <- read.csv("../datasets/raw/DOKU_All TiAb-Screening_20200116_cap.csv")
+# wilson["raw", ] <- c(nrow(w_all), nrow(w_ftext), nrow(w_incl))
+wilson["raw", ] <- c(3453, 174, 26) # looked it up
+
+w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv",
+                     header=T)
+
+# inclusion_code label is not in there 
+w_asr$inclusion_code <- w_asr$label_abstract_screening + w_asr$label_included
+w_asr$included <- w_asr$label_included
+wilson["asreview", ] <- data_descr(w_asr)
+
+```
+
+```{r}
+# create test dataset
+w_test <- w_asr %>%
+  drop_na(abstract) %>% # drop entries with missing abstracts
+  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+
+# select relevant columns
+w_test <- w_test %>%
+            select(authors, title, abstract, included, inclusion_code)
+
+wilson["test",] <- data_descr(w_test)
+```
+
+Save the test dataset.
+```{r}
+# save test file
+write.csv(w_test , # select relevant columns
+          "test_datasets/wilson.csv")
+```
+```
+
+# Save descriptive statistics
+
+```{r eval = TRUE}
+# put everything together in list. 
+all <- list(ace = ace,
+            nudging = nudging,
+            ptsd = ptsd,
+            software = hall,
+            wilson = wilson)
+
+# save datafile, to serve as data for descriptive table in manuscript
+save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
+```

### 2020-03-09 datasets/data_preprocessing.nb.Rmd
Dataset preprocessing - updated noteobook on preprocessing for 4/5 datasets - updated meeting notes - renamed meeting notes

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
This notebook processes all five systematic review datasets into datasets that can be used for testing asreview.

```{r, results = "hide"}
library(tidyverse)
library(knitr)
library(kableExtra)
```

### Set-up
```{r}
# create storage for statistics
template <- data.frame(search = rep(0,4), # papers obtained in systematic search
                       ftext = rep(0, 4), # number of abstract inclusions
                       incl = rep(0,4), # papers included in final systematic review

                       row.names = c("paper", # numbers reported in the publication
                                     "raw", # numbers published on raw dataset (by author,  mostly on OSF)
                                     "asreview", # numbers on asreview repository 
                                     "test")) # numbers in test dataset

# statistics on duplicates and dropping in ASReview dataset
drops <- data.frame(n = rep(0,5), # candidates
                    na = rep(0,5),# number of missing abstracts
                    narate = rep(0,5), # percenta of missing abstracts
                    dup = rep(0,5),  # number of duplicate abstracts 
                    duprate = rep(0,5), # percentage of missing abstracts
                    row.names = c("ace", "nudging", "ptsd", "software", "wilson"))

# some functions to extract statistics
data_descr <- function(data){
  return(c(nrow(data), # all papers obtained in the systematic search
           ifelse(sum(data$inclusion_code > 0), sum(data$inclusion_code > 0), NA), # number of abstract inclusions
           sum(data$included))) # papers included in systematic review
}

nostudies <- function(all, set, stage){ # number of studies
  sapply(all, function(x) x[set, stage])
}

inclrate <- function(all, set){ # inclusion rate
  sapply(all, function(x) round(x[set,"incl"]/x[set,"search"]*100,2))
}
```

## Ace dataset 
```{r}
ace <- template
# paper ------------------------------------------------------------------------
ace["paper", ] <- c(2544, NA, round(2544*0.0160))

# raw --------------------------------------------------------------------------
# original paper not to linked directly. cannot be retrieved? 
# checked dataset online by cohen et al. 
#https://dmice.ohsu.edu/cohenaa/systematic-drug-class-review-data.html
ace["raw", ] <- c(2544, NA, 41)

# asreview ---------------------------------------------------------------------
ace_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Cohen_EBM/output/ACEInhibitors.csv",
                     header=T)

ace["asreview", ] <- c(nrow(ace_asr),
                       NA,
                       sum(ace_asr$label_included))
```

### Create test dataset
```{r}
# replace empty abstracts by NA values. 
ace_asr[ace_asr$abstract == "", "abstract"] <- NA

# drop missings and duplicates. 
ace_test <- ace_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts

# select columns
ace_test <- ace_test %>%
       select(authors, title, abstract, label_included) # select relevant columns

# data on 
ace["test", ] <- c(nrow(ace_test),
                   NA,
                   sum(ace_test$label_included))
```

### Some statistics 
```{r}
# missingness and duplicates in raw data on ASReview
drops["ace",] <- ace_asr %>%
          summarise(n = length(abstract),
                    na = sum(is.na(abstract)),
                    na_rate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    dup_rate = sum(duplicated(abstract, incomparables = NA))/length(abstract))
drops["ace",]
ace
```

## nudging dataset 
```{r}
# by Rosanna Nagtegaal
nudging <- template
nudging["paper", ] <- c(2006, 377, 100) 
```

```{r}
# data is not public yet

# raw

# asreview
```

### Create test dataset

## PTSD dataset
```{r}
ptsd <- template 
ptsd["paper", ] <- c(6185, 363, 34) # from flowchart

# raw --------------------------------------------------------------------------
ptsd["raw", ]

# asreview ---------------------------------------------------------------------
ptsd_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Van_de_Schoot_PTSD/output/PTSD_VandeSchoot_18.csv", 
                     header=T)

ptsd["asreview", ] <- data_descr(ptsd_asr)

```

### Create test dataset
Now, remove duplicate entries and empty abstracts to arrive at test set. 
```{r}
ptsd_test <- ptsd_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
```

There are 38 inclusions in this dataset, should be 34. 
```{r}
# get rid of 4 extra inclusions (see log book)
excl <- 
  ptsd_test %>%
  filter(included == 1, 
         str_detect(authors, "Sterling, M., Hendrikz, J., Kenardy, J.") |
         str_detect(authors, "Hou") |
         str_detect(authors, "Mason") |
         str_detect(authors, "Pérez")) %>%
  select(id)

indices <- ptsd_test$id %in% excl

# get rid of 4 papers
ptsd_test[indices, "included"] <- 0
```

```{r}
# finalize dataset  
ptsd_test <- ptsd_test %>%
  select(authors, title, abstract, included, inclusion_code) # select relevant columns
```

Derive statistics in final test set.
```{r}
ptsd["test", ] <- data_descr(ptsd_test)

# statistics on duplicates from asr data to test
drops["ptsd", ] <- ptsd_asr %>%
  summarise(n = length(abstract),
                    na = sum(is.na(abstract)),
                    narate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))

ptsd
```

## software dataset
```{r}
hall <- template

# paper ------------------------------------------------------------------------
hall["paper", ] <- c(8911, NA, 104)

# raw --------------------------------------------------------------------------
h_raw <- read.csv("https://zenodo.org/record/1162952/files/Hall.csv",
                  header=T)

hall["raw", ] <- c(length(h_raw$Document.Title),
                   NA,
                   sum(h_raw$label == "yes"))

# asreview ---------------------------------------------------------------------
hall_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Four%20Software%20Engineer%20Data%20Sets/Software%20Engineering%201%20Hall.csv",
                     header=T)

hall["asreview", ] <- data_descr(hall_asr)
```

### Creating test dataset
```{r}
hall_test <- hall_asr %>%
   drop_na(abstract) %>% # drop entries with missing abstracts
   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

hall["test", ] <- data_descr(hall_test)
```

### Statistics 
```{r}
drops["software", ] <- 
  hall_asr %>%
   summarise(n = length(abstract),
                    na = sum(is.na(abstract)),
                    narate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))

hall
```

## Wilson dataset

```{r}
wilson <- template
# paper ------------------------------------------------------------------------
wilson["paper", ] <- c(3453, 174, 26)

# raw --------------------------------------------------------------------------
# w_ftext <- read.delim("../datasets/raw/DOKU_All FT-Screening_20200116_cap.txt")
# w_incl <- read.csv("../datasets/raw/DOKU_All Included_20200116_cap.csv")
# w_all <- read.csv("../datasets/raw/DOKU_All TiAb-Screening_20200116_cap.csv")
# wilson["raw", ] <- c(nrow(w_all), nrow(w_ftext), nrow(w_incl))
wilson["raw", ] <- c(3453, 174, 26) # looked it up

# asreview ---------------------------------------------------------------------
w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv",
                     header=T)

# add inclusion_code label 
w_asr$inclusion_code <- w_asr$label_abstract_screening + w_asr$label_included
w_asr$included <- w_asr$label_included
wilson["asreview", ] <- data_descr(w_asr)

```

```{r}
# create test dataset
w_test <- w_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

# select relevant columns
w_test <- w_test %>%
            select(authors, title, abstract, included, inclusion_code)

wilson["test",] <- data_descr(w_test)
```

Statistics
```{r}
drops["wilson",] <- 
  w_asr %>%
   summarise(n = length(abstract),
                    na = sum(is.na(abstract)),
                    narate = sum(is.na(abstract))/length(abstract),
                    dup = sum(duplicated(abstract, incomparables = NA)),
                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))

wilson
```

# Save descriptive statistics on all datasets

```{r eval = TRUE}
# put everything together in list. 
all <- list(ace = ace,
            nudging = nudging,
            ptsd = ptsd,
            software = hall,
            wilson = wilson)

# save datafile, to serve as data for descriptive table in manuscript
save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
```

# Statistics
All candidate papers, paper selected for full text screening, papers included in final review and inclusion rate, over various versions of the dataset.  
```{r, echo = FALSE}
tibble(Dataset = names(all), 
       # paper 
       `candidates_paper` = nostudies(all, "paper", "search"), 
       `fulltext_paper` = nostudies(all, "paper", "ftext"),
       `incl_paper` = nostudies(all, "paper", "incl"),
       `inclrate_paper` = inclrate(all, "paper"),

       # raw data 
       `candidates_raw` = nostudies(all, "raw", "search"), 
       `fulltext_raw` = nostudies(all, "raw", "ftext"),
       `incl_raw` = nostudies(all, "raw", "incl"),
       `inclrate_paper` = inclrate(all, "raw"),

       # asreview repository 
       `candidates_asr` = nostudies(all, "asreview", "search"), 
       `fulltext_asr` = nostudies(all, "asreview", "ftext"),
       `incl_asr` = nostudies(all, "asreview", "incl"),
       `inclrate_asr` = inclrate(all, "asreview"),

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")
       ) %>% 
  t() %>%
  kable("html") %>%
  kable_styling(full_width = "TRUE") %>%
  #scroll_box(width = "100%", height = "200px") %>%
  pack_rows("Paper", 2, 5) %>%
  pack_rows("Raw data", 6, 9) %>%
  pack_rows("ASReview data", 10, 13) %>%
  pack_rows("Test data set", 14, 17) 
```

Descriptives on missingness and duplicate abstracts in the ASReview test data set. 
```{r, echo = FALSE}
drops %>%
  kable("html",
        col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
        digits = 2) %>%
  kable_styling(full_width = TRUE)
```

# Write all test dataset files 
```{r}
# ace
write.csv(ace_test, "test_datasets/ace.csv")

# nagtegaal

# ptsd
write.csv(ptsd_test, "test_datasets/ptsd.csv")

# hall
write.csv(hall_test, "test_datasets/software.csv")
# wilson
write.csv(w_test, "test_datasets/wilson.csv")

```

### 2020-03-09 manuscript/drafts/manuscript.Rmd
Dataset preprocessing - updated noteobook on preprocessing for 4/5 datasets - updated meeting notes - renamed meeting notes

@@
 date: "1/14/2020"
-output: pdf_document
+output: 
+  pdf_document:
+    citation_package: biblatex
 bibliography: asreview.bib
+
 ---
@@
 library(glue)
+library(rbbt)
 
@@
 table_nums <- captioner(prefix = "Table")
-table_nums(name = "datasets", caption = "Descriptive statistics on articles and resulting datasets for each original systematic review.")
+# table  on datasets statistics
+table_nums(name = "datasets", caption = "Statistics on datasets from original systematic reviews.")
 ```
@@
 
+RQ1
+
 ## active learning for systematic reviews 
@@
 
+- pool unlabeled abstracts $\mathcal{U}$ 
+- labeled data set $\mathcal{L}$, 
+- instance $x$, label $y$
+
+- utility measure $\phi_A(\cdot)$
+- $x^*_A$ best query instance according to $\phi_A(\cdot)$
+
+```{}
+while
+
+```
+
 ## Background
-[@Yu2018a, @Yu2019] simulated 32 svm classifiers, on software engineering.
-
+[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
+A popular classifier is SVM 
 In terms of Yu et al, we adopt .CT.
@@
 ## Datasets
+
 The algorithm will be tested on five systematic reviews from various research areas. 
@@
 #### ace 
+A dataset from a collection of systematic reviews on drug efficacy from the medical sciences [@Cohen2006]. 
+This dataset is on a systematic review
+
+efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
+The ace dataset comes from a study on reducing workload in systematic reviews  [@Cohen2006].
+The ace dataset is on the efficacy of
+
+drug class 
 The ACEInhibitors dataset from the study by [@Cohen2006].
@@
 
-- systematic search n = 3453
-- full text screening n = 174
-- included in synthesis n = 26
-
-... dataset is ...
-
-Descriptive statistics on the reviews can be found in `r table_nums("datasets", display = "cite")`. 
+Statistics on the SRs can be found in `r table_nums("datasets", display = "cite")`. 
 All datasets accompanying the systematic reviews are openly published. 
@@
 Duplicate entries were removed. 
-Preprocessing scripts can be found on the GitHub repository
+Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
 
@@
 
+nstudies <- function(all, datastage, col){
+}
+
+nostudies <- function(all, set, stage){
+  sapply(all, function(x) x[set, stage])
+}
+inclrate <- function(all, set){
+  sapply(all, function(x) round(x[set,"incl"]/x[set,"search"]*100,2))
+}
+
+datastats <- 
   tibble(Dataset = names(all), 
        #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
-       `No. studies` = sapply(all, function(x) x[1,1]), 
-       `No. selected for fulltext screening` = sapply(all, function(x) x[1,2]),
-       `No. final inclusions` = sapply(all, function(x) x[1,3]),
-       `Inclusion rate (%)` = sapply(all, function(x) round(x[1,3]/x[1,1]*100,2)),
-       `No. studies in test collection` = sapply(all, function(x) x[3,1]),
-       `No. selected for fulltext screening test collection` = sapply(all, function(x) x[3,2]),
-       `No. final inclusions in test collection` = sapply(all, function(x) x[3,3]),
-       `Inclusion rate in test collection (%)` = sapply(all, function(x) round(x[3,3]/x[3,1]*100,2))
-       ) %>%
-  # knitr kable
+       # paper 
+       `candidates_paper` = nostudies(all, "paper", "search"), 
+       #`fulltext_paper` = nostudies(all, "paper", "ftext"),
+       `incl_paper` = nostudies(all, "paper", "incl"),
+       `inclrate_paper` = inclrate(all, "paper"),
+       # test set 
+       `candidates_test` =  nostudies(all, "test", "search"), 
+       #`fulltext_test` =  nostudies(all, "test", "ftext"), 
+       `incl_test` =  nostudies(all, "test", "incl"), 
+       `inclrate_test` = inclrate(all, "test")
+       ) 
+```
+
+`r table_nums("datasets")`
+```{r}
+datastats %>%
   kable(format = "latex",
         booktabs = TRUE,
-        caption = table_nums("datasets")) %>%
+        col.names = c("Dataset", rep(c("Candidate studies", 
+                                       #"Studies selected for fulltext screening", 
+                                       "Final inclusions", 
+                                       "Inclusion rate (%)"),2))) %>%
   kable_styling(full_width = TRUE) %>%
-  add_header_above(c("", "Original study" = 4, "Test collection" = 4))
-
-  # add citations
+  add_header_above(c("", "Original study" = 3, "Test collection" = 3))
 ```
@@
 
+## Models 
+Now, we build five different active learning models.
+
+we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$.
+
+We are going to test 5 models on 5 different datasets.
+
+classifier - feature extraction - query strategy - balance strategy
+
+BTMD -
+
+#### Classifiers
+- Naive Bayes (B)
+- Random Forests (R)
+- Support Vecor Machine (S)
+- Logistic Regression (L)
+- Dense Neural Network (N)
+
+#### Feature extraction strategies
+To compute relevancy of a paper, we use the title and abstract 
+- baseline model:
+
+### Balance strategies
+triple = 
+The other parameters remain fixed over the 5 models:
+
+- Query Strategy = max
+- Balance Strategy = triple
+- n_instances=10 (number of papers each query)
+- n_prior_included = 5
+- n_prior_excluded = 5
+
 ## Simulations
@@
 A simulation is of one model on one dataset.
-we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
+
 The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
 We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
+The researcher has some prior knowledge about the pool, some papers ought to be included in the SR
 for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
@@
  - decisions of the original SR are **ground truth** (benchmark) (oracle)
-
  - binary classifications: relevant/irrelevant
@@
 ### Stage 1: hyperparameter optimization
-We are going to test 5 models on 5 different datasets.
-
-### Models
-- Naive Bayes 
-- Random Forests
-- Support Vecor Machine 
-- Logistic Regression
-- Dense Neural Network
 
@@
 ```
-
-The other parameters remain fixed over the 5 models:
-
-- Query Strategy = max
-- Balance Strategy = triple
-- n_instances=10 (number of papers each query)
-- n_prior_included = 5
-- n_prior_excluded = 5
 

### 2020-03-10 manuscript/drafts/manuscript.Rmd
- add condition grid - add background on other strategies - add starting point, retraining, querying

@@
 
-RQ1
-
 ## active learning for systematic reviews 
-achine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
-The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.
-
-A classical example of word embeddings is 'bag of words'.
-For each each text, the number of occurrences of each word is stored.
-This leads to n features, where n is the number of distinct words in the texts.
-[@scikit-learn]
-
-Word embeddings allows ASReview to predict relevance of abstracts from the features of abstracts of which relevance is known.
-
 corpus = all the text:
-
-ASReview implements several feature extraction strategies. The following will be compared:
-
-The model is typically a learning algorithm used to predict the relevance of text.
 
@@
 
+RQ1 - what are good classifiers 
+RQ2 - what are good optimization strategies
+
 ## Background
+[@OMara-Eves2015] literature review
+
 [@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
-A popular classifier is SVM 
+A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
 In terms of Yu et al, we adopt .CT.
+
+SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
+
+abstrackr
+
+SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
+Also include social sciences data besides medical data.
+
+[@Cohen2006] perceptron-based classifier (neural network)
+
+SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
+in limitations section mentions that LR yields about same results, nb inferior results.
+
+[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
+  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas Naïve Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+The AUC results are mixed, although boosting has a slight edge overall.
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, Naïve Bayes for sensitivity, and boosting for balance between the two, for example)."
 
@@
 ## Datasets
-
 The algorithm will be tested on five systematic reviews from various research areas. 
@@
 
+There are two classes in the data: exlusions and inclusions.
+The inclusions are clearly the minority class.
+
 ## Models 
-Now, we build five different active learning models.
-
-we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$.
-
-We are going to test 5 models on 5 different datasets.
-
-classifier - feature extraction - query strategy - balance strategy
-
-BTMD -
+Five different active learning models were build. 
+Every model $m$ was used to perform an automated systematic review on SR dataset $d$. 
+The models all apply a different classifier $c$ with its own set of (hyper)parameters $h$.
 
 #### Classifiers
+The classifier predicts the class of all papers. 
+To predict whether a paper should be an exclusion or an inclusion, different classifiers
+
 - Naive Bayes (B)
@@
 
-#### Feature extraction strategies
-To compute relevancy of a paper, we use the title and abstract 
-- baseline model:
+Besides $c$, components of $m$ are fea
 
-### Balance strategies
-triple = 
-The other parameters remain fixed over the 5 models:
+To summarize, every model $m$ consists of the following key components: 
+classifier, feature extraction strategy, query strategy, balance strategy.
 
-- Query Strategy = max
-- Balance Strategy = triple
+For example $M_1$ BTMD (naive bayes, tfidf, certainty sampling, double balance)
+STMD
+
+#### Word representation 
+To be able to predict whether a paper needs to be included or excluded (e.g. to predict class), 
+the classifier needs some features from the papers.  
+As features we use the title and abstract from every paper - this is what is prescribed by prisma, (check!) 
+The classifier cannot predict the paper class from the raw titles and abstracts as they are.
+Therefore, the content of the texts needs to be transformed into numerical representations called feature vectors.
+
+A classical example is a 'bag of words' representation. 
+For each each text, the number of occurrences of each word is stored. 
+This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
+
+We use the following feature extraction methods
+- TF-IDF
+
+#### The next abstract to be queried  
+The model has various ways of deciding which instance should be queried next.
+
+#### Rebalancing the training set
+To account for class imbalance in the data, the model can apply several strategies to rebalance the training set.
+
+A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.
+
+#### Starting point
+The initial training set consists of 5 inclusions and 5 exclusions, randomly sampled from the dataset. 
+We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
+The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
+
+```
+c = naivebayes
+f = tfidf
+q = max
+n_prior_included = 5
+n_prior_excluded = 5
+```
+
+#### Retraining
+We can choose to retrain the model after labeling $n$ instances. 
 - n_instances=10 (number of papers each query)
-- n_prior_included = 5
-- n_prior_excluded = 5
 
 ## Simulations
-The original systematic review is reproduced using five different models.
+To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews.
 
-A simulation is of one model on one dataset.
+### Optimizing hyperparameters
+For every model*data combination, 3 sets of hyperparameters are generated to ... 
+parallel
+Every model has its own hyperparameters. 
+For every model, the hyperparameters are optimized three times, arriving at three versions of the model:
 
-The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
-We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
-The researcher has some prior knowledge about the pool, some papers ought to be included in the SR
+We nog have 75 combinations. 
 for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
@@
 
-Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions. Results are aggregated (?)
+A simulation is of one model on one dataset. 
+The simulation is repeated for 10 trials $t$.
 
-assumptions
+Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions.
+So every trial the prior inclusions and exclusions are randomly selected. 
+Results are aggregated (?)
+
+#### Assumptions
 
@@
  - binary classifications: relevant/irrelevant
-
-### Optimizing Hyperparameters 
-Every model has its own hyperparameters. 
-For every model, the hyperparameters are optimized three times, arriving at three versions of the model:
 
@@
 # Performance metrics
+The goal is twofold: we want to identify all relevant papers, as fast as we can. 
 Tradeoff: identifying all relevant papers and reducing workload. 
+A good metric to evaluate this is..
 

### 2020-03-10 01_simulation.R

@@ -1,0 +1,6 @@
+
+conditiongrid <- readRDS("manuscript/drafts/simulation/00_conditiongrid.RDS")
+
+# dataset
+
+# hyperparameters 

### 2020-03-10 manuscript/drafts/simulation/00_condition_grid.R

@@ -1,0 +1,33 @@
+# condition grid
+
+# classifier
+c <- c("B", 
+       "R", 
+       "S", 
+       "L", 
+       "N")
+
+# query strategy
+q <- c("C" # certainty
+       #"U" # uncertainty
+)
+
+# feature extraction method
+f <- c("T", # tf-idf
+       "D" # Doc2Vec
+       #"S", # sbert 
+       #"E" # embeddingIdf
+) 
+
+# balance strategy
+b <- c(#"N",# no reblancing 
+       "W", # weighting
+       "U" # undersampling (as a bonus!)
+)
+
+conditiongrid <- tibble(condition = do.call(paste0, expand.grid(c, q, f, b)))
+
+conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec", "AU"))
+# stage 1 = all classifiers + tfidf, stage 2 is repeat with doc2vec, stage 3 is repeat with agressive undersampling. 
+
+saveRDS(conditiongrid, file = "manuscript/drafts/simulation/00_conditiongrid.RDS")

### 2020-03-11 manuscript/drafts/manuscript.Rmd
- add classification problem - add datsets info - add classifiers - update meeting notes

@@
 
+Binary classification problem. 
+predict whether a paper in the pool is an inclusion or exclusion, 
+based on labeled instances from $\mathcal{L}$ and use training data to understand how input variables are related to class.
+
+We're building active learning model who takes X as an input an predicts class using labels from training set. 
+Model improves by deciding asking more information from the reviewer (oracle), 
+accounting for imbalance.
+
+#### Assumptions 
+1) decisions of the original SR are **ground truth** (benchmark) (oracle)
+
+The inclusion rate is ... data is imbalanced. 
+what is the philosophy
+False negatives must be avoided ... 
+The cost of a false negative outweighs the cost of a false positive. 
+Note that we assume the oracle/original user to hold the truth. 
+This is of course not always the case.
+
+There are two classes in the data: exlusions and inclusions.
+The inclusions are clearly the minority class.
+
+Datasets from the medical and social sciences, software engineering and public administration. 
+Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.
+
 ## active learning for systematic reviews 
@@
 [@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
-  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas Naïve Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
 The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, Naïve Bayes for sensitivity, and boosting for balance between the two, for example)."
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
 
 Our extensions is that we try different classifiers, on more datasets.
+
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104, ASReview - Smart software for Systematic Reviews.
+
+All simulations were run using through caartesius EINF-156
 
@@
 What would happen if the citation screening would have been performed using asreview? 
+All datasets accompanying the systematic reviews are openly published.
 
@@
 #### ace 
-A dataset from a collection of systematic reviews on drug efficacy from the medical sciences [@Cohen2006]. 
-This dataset is on a systematic review
-
-efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
-The ace dataset comes from a study on reducing workload in systematic reviews  [@Cohen2006].
-The ace dataset is on the efficacy of
-
-drug class 
-The ACEInhibitors dataset from the study by [@Cohen2006].
-The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.
+Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
+All systematic reviews in this database are on drug efficacy. 
+The ace dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
 
 a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-
-WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
 The data
@@
 #### software 
-A review on fault prediction in software engineering by [@Hall2012]. 
-The dataset is reviewed from [@Yu2018a] who collected datasets on literature reviews from the software engineering field.
+The dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
+This dataset is on fault prediction in software engineering by [@Hall2012].
 
 #### nudging
-review [@Nagtegaal2019]
-The data [@Nagtegaal2019a]
-
-Difference in 18 inclusions = systematic reviews. to exclude/include?
+A review from the behavioural public administration area. 
+The SR includes studies on nudging healthcare professionals [@Nagtegaal2019]. 
+The data was stored on the Harvard Dataverse [@Nagtegaal2019a].
 
 #### ptsd
-A review [@vandeSchoot2018] on longitudinal studies on posttraumatic stress symptoms assessed after exposure to trauma. 
-The corresponding dataset [@Winter2020].
+A literature review from field of psychology. The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
+The corresponding dataset can be found on the Open Science Framework [...].
 
 #### Wilson
-The review [@Appenzeller-Herzog2019]
-The dataset [@Appenzeller-Herzog2020]
+A dataset from the medical sciences [@Appenzeller-Herzog2020]. 
+TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].
 
-Statistics on the SRs can be found in `r table_nums("datasets", display = "cite")`. 
-All datasets accompanying the systematic reviews are openly published. 
-The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.
+All datasets started with an initial pool of thousands of papers. 
+A fraction of these papers where deemed relevant for the SR, with inclusion rates varying from .. to .. (`r table_nums("datasets", display = "cite")`).
 
-For every SR, the raw datafiles were preprocessed into a test dataset.
-
-These test datasets contain authors, title, abstract and annotation of whether the entry was included in the final review or not (0/1).
-
-Entries with missing abstracts were removed. 
-Duplicate entries were removed. 
+The raw datafiles published with the SRs were preprocessed into a test dataset.
+The test datasets contain title information on all citations obtained in the search strategy. 
+The instances in the data consist of a title, an abstract and were labeled to indicate which citations were included in the systematic review. 
+Instances with missing abstracts were removed. 
+Duplicate instances were removed. 
 Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
@@
 
-The inclusion rate is ... data is imbalanced. 
-what is the philosophy
-False negatives must be avoided ... 
-The cost of a false negative outweighs the cost of a false positive. 
-Note that we assume the oracle/original user to hold the truth. 
-This is of course not always the case.
-
-There are two classes in the data: exlusions and inclusions.
-The inclusions are clearly the minority class.
-
 ## Models 
@@
 #### Classifiers
-The classifier predicts the class of all papers. 
+The classifier predicts the class of all papers, given the training dataset/labeled data set $\mathcal{L}$.
+
+Given the labels and some features from all abstracts in the pool, the classifier 
 To predict whether a paper should be an exclusion or an inclusion, different classifiers
 
-- Naive Bayes (B)
-- Random Forests (R)
-- Support Vecor Machine (S)
-- Logistic Regression (L)
-- Dense Neural Network (N)
+Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$.
+Naive Bayes assumes all features are independent given the class value.
+This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
+Especially at ...
+tasks.
+
+Random Forests (R) is where a large number of decision trees are fit on bootstrapped samples of the original data.
+All trees cast a vote on the class, which are aggregated into a class prediciton for each input $\mathbf{X}$ [@Breiman2001].
+
+Support Vecor Machine (S) - finds a multidimensional hyperplane to separate classes.
+[@Tong2001]
+
+Logistic Regression (L) -
+
+Dense Neural Network (N) -
 
@@
 This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
+The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
+Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.
 
-We use the following feature extraction methods
-- TF-IDF
+(T) (D)
 
@@
 A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.
+
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
 
@@
 Results are aggregated (?)
-
-#### Assumptions
-
- - decisions of the original SR are **ground truth** (benchmark) (oracle)
- - binary classifications: relevant/irrelevant
 
@@
 #### TF-IDF
-The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".
-
-Term-frequency Inverse Document Frequency [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.
 
@@
 #### Support Vector Machine
+
+ Arguments
+        ---------
+        gamma: str
+            Gamma parameter of the SVM model.
+        class_weight:
+            class_weight of the inclusions.
+        C:
+            C parameter of the SVM model.
+        kernel:
+            SVM kernel type.
+        random_state:
+            State of the RNG.
 

### 2020-03-11 01_simulation.R

@@ -1,6 +1,26 @@
-
 conditiongrid <- readRDS("manuscript/drafts/simulation/00_conditiongrid.RDS")
 
-# dataset
+# datasets (5)
+D <- c("ace", "nudging", "ptsd", "software", "wilson")
 
-# hyperparameters 
+conditiongrid %>% add_column(ace = 0L,
+                             nudging = 0L,
+                             ptsd = 0L,
+                             software = 0L,
+                             wilson = 0L)
+
+# optimize hyperparameters (11 sets (1+2*5)) 
+opt <- c("all", "four", "one")
+
+# 300 sets of hyperparameters
+expand.grid(conditiongrid$condition, D, opt)
+
+# pick hyperparameter sets for every model 
+
+
+# simulate 
+
+conditiongrid
+
+conditiongrid$pathString <- paste("tree", 
+                                  conditiongrid$condition,)

### 2020-03-11 manuscript/drafts/manuscript.Rmd
add introduction draft

@@
 - summary/conclusion
+---
+This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.
+
+Systematic reviews are top of the bill in research.
+As more and more papers are published and reproducibility crisis has emerged, science calls for more meta.
+It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
+Performing a systematic review is a tedious and time-consuming task.
+To review a specific research area, one starts out with an initial search of thousands of academic papers.
+All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
+With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
+This whole processes costs this and this much time [shelmilt].
+
+The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
+This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
+Together with the reviewer /human machine interaction.
+The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
+It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
+
+The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
+To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
+This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
+Also reviewing is now much more fun.
+As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
+
+So you might wonder, how does such an algorithm actually work?
+Active learning strategy, starting with a pool of unlabeled abstracts (U).
+The reviewer starts labeling some instances in U, creating L.
+The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method).
+Now, it made an initial classification.
+The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next.
+By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.
+
+Now there are a few technical details.
+Many different versions of such algorithms exist.
+Many of such algorithms have been described in the active learning literature and have been applied in the systematic reviewing process.
+Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strategy.
+
+Most often the SVM classifier is used, popular and very good results.
+Also lots of other configurations.
+However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
+Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
+
+In the current study, we aim at exploring the performance of several classifiers on reducing workload while maintaining performance in abstract screening process.
+This is done by performing simulations on existing systematic reviews.
+Performance is evaluated by how much time can be saved … while maintaining accuracy.
+
+Present research questions. 
+RQ1 – which classifiers perform best? 
+-	RQ1a – does classifier performance vary over different research areas? 
+(in what terms does it perform best)
+
+RQ2 different hyperparameter optimizations?
+Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.
+
+The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. So not only medical sciences.
+
+To perform all these computations the research was carried out using the ASReview software by Utrecht University, which has a simulation mode that you can just input your labelled review file into and perform a simulation study with it.
+To be found on GitHub.
+It has many adjustable components/is very versatile.
+
+Then if we still have time left we explore the effect of another feature extraction method, namely doc2vec.
+This might possibly increase performance as it performs better at grasping structure/hidden relations/hierarchy between words in the texts.
+So, it could be interesting in more ‘fuzzy’ research areas.
+A downside is that it takes more computing time.
+
+Then if there’s even more time we might want to compare a different balance strategy.
+
+----
 

### 2020-03-11 manuscript/drafts/manuscript.Rmd
- update meeting notes

@@
 - objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
-- justification - 
+- justification 
 - background 
@@
 - summary/conclusion
----
+
+-----
+
 This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.

### 2020-03-11 datasets/data_preprocessing.nb.Rmd
fix notebook error

@@
        `incl_raw` = nostudies(all, "raw", "incl"),
-       `inclrate_paper` = inclrate(all, "raw"),
+       `inclrate_raw` = inclrate(all, "raw"),
 
@@
   kable("html") %>%
-  kable_styling(full_width = "TRUE") %>%
+  kable_styling(full_width = TRUE) %>%
   #scroll_box(width = "100%", height = "200px") %>%

### 2020-03-13 datasets/data_preprocessing.nb.Rmd
- update meeting notes - add nagtegaal to preprocessing
introduce bug

@@
 
-```{r}
+```{r eval = FALSE}
 # data is not public yet
 
-# raw
+# raw --------------------------------------------------------------------------
 
-# asreview
+# asreview ---------------------------------------------------------------------
+
+# remove missing abstracts 
+final <- final[final$title != "NA", ]
+
+# remove duplicates (171 duplicates)
+final <- final %>%
+  distinct(abstract, .keep_all = TRUE)
+table(final$inclusion_code)
+
+nrow(final)
+final$abstract_included %>% table()
+final$included %>% table()
+
+# 
+write.csv(final, "data/nagtegaal.csv")
+
 ```
@@
 
+```{r}
+nudging["test", ] <- c(1848, 382, 100)
+```
+
 ## PTSD dataset
@@
 ptsd <- template 
-ptsd["paper", ] <- c(6185, 363, 34) # from flowchart
+ptsd["paper", ] <- c(6185, 363, 38) # from flowchart
 

### 2020-03-13 manuscript/drafts/manuscript.Rmd
introduce bug

@@
   pdf_document:
+    keep_tex: yes
     citation_package: biblatex
 bibliography: asreview.bib
+---
 
----
 ```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
+
+options(tinytex.verbose = TRUE)
 
@@
 Systematic Reviews (SR's) are booming - but they are a lot of work
-Various machien learning tools have been proposed to reduce workload in abstract screening.
+Various machine learning tools have been proposed to reduce workload in abstract screening.
 
 - objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
-- justification 
+- justification - 
 - background 
@@
 
------
+---
 
@@
 
+We approach asr as a classification problem: 
+All papers obtained in the systematic search form a pool of instances x. 
+All instances x need to be classified, e.g. we want to give them a label y. 
+all x are now part of U,.
+Binary classification, either inclusion or exclusion. 
+We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.
+
+By starting of with L, the algorithm utilizes characteristics of X to predict labels in U.
+
+We want to classify the papers in 
+Where the whole collection of papers in the systematic search form a pool of instances x, with unknown label y. 
+<x,y>. 
+```
+input: a pool of unlabeled abstracts $\mathcal{U}$ 
+oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
+
+  M = train($\mathcal{L}$)
+  query x \isin
+
+```
+- pool unlabeled abstracts $\mathcal{U}$ 
+- labeled data set $\mathcal{L}$, 
+- instance $x$, label $y$
+
+- utility measure $\phi_A(\cdot)$
+- $x^*_A$ best query instance according to $\phi_A(\cdot)$
+
 Now there are a few technical details.
@@
 
-The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. So not only medical sciences.
+The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
+So not only medical sciences.
 
@@
 
-- pool unlabeled abstracts $\mathcal{U}$ 
-- labeled data set $\mathcal{L}$, 
-- instance $x$, label $y$
-
-- utility measure $\phi_A(\cdot)$
-- $x^*_A$ best query instance according to $\phi_A(\cdot)$
-
-```{}
-while
-
-```
-
 RQ1 - what are good classifiers 
@@
 
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104, ASReview - Smart software for Systematic Reviews.
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
 
-All simulations were run using through caartesius EINF-156
+All simulations were run using through cartesius EINF-156
 
@@
 
-#### ace 
 Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
 All systematic reviews in this database are on drug efficacy. 
-The ace dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
+The _ace_ dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
 
@@
 
-#### software 
-The dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
+The _software_ dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
 This dataset is on fault prediction in software engineering by [@Hall2012].
 
-#### nudging
-A review from the behavioural public administration area. 
+The _nudging_ dataset comes from a review from the behavioural public administration area. 
 The SR includes studies on nudging healthcare professionals [@Nagtegaal2019]. 
@@
 
-#### ptsd
-A literature review from field of psychology. The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
-The corresponding dataset can be found on the Open Science Framework [...].
+A literature review from field of psychology, _ptsd_. 
+The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
+The corresponding data can be found on the Open Science Framework [...].
 
-#### Wilson
-A dataset from the medical sciences [@Appenzeller-Herzog2020]. 
+_wilson_, a dataset from the medical sciences [@Appenzeller-Herzog2020]. 
 TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].
@@
 All datasets started with an initial pool of thousands of papers. 
-A fraction of these papers where deemed relevant for the SR, with inclusion rates varying from .. to .. (`r table_nums("datasets", display = "cite")`).
+A fraction of these papers where deemed relevant for the SR, with inclusion rates around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).
 
@@
 
+Logistic Regression (L) -
+
 Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$.
@@
 [@Tong2001]
-
-Logistic Regression (L) -
 
@@
 
-We nog have 75 combinations. 
+We now have 75 combinations. 
 for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
@@
 
+### Statistical analysis 
+#### measures
+#### comparison over conditions
+
 # The software 
 ASReview takes the following parameters/arguments:
-
-<!-- - a model -->
-<!-- - a query strategy -->
-<!-- - a balance strategy -->
-<!-- - a feature extraction strategy -->
 
@@
 
-### Outcomes 
+#### Performance metrics 
 For each model, 
@@
 
+The goal is twofold: we want to identify all relevant papers, as fast as we can. 
+Tradeoff: identifying all relevant papers and reducing workload. 
+A good metric to evaluate this is..
+
+What is more important: recall or precision?
+
+Recall more highly valued than precision.
+
+What about class imbalance?
+
+#### RRF
+Amount of relevant references found after having screened a certain percentage of the total number of abstracts.
+
+#### Work saved over sampling (WSS)
+Indicates how much time can be saved, at a given level of recall.
+WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
+Typically, WSS is measured at a recall of 0.95. Reasonable because..
+
+$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$
+
+#### Raoul
+#### Utility? 
+#### F-measure 
+#### ROC/AUC
+
+Is performance related to some characteristic (n, inclusion rate, ...)
+
 ? How to compare outcomes of 3 different optimization strategies?
-
-## Evaluation
 
@@
 
-# Performance metrics
-The goal is twofold: we want to identify all relevant papers, as fast as we can. 
-Tradeoff: identifying all relevant papers and reducing workload. 
-A good metric to evaluate this is..
-
-What is more important: recall or precision?
-
-Recall more highly valued than precision.
-
-What about class imbalance?
-
-#### RRF
-Amount of relevant references found after having screened a certain percentage of the total number of abstracts.
-
-#### Work saved over sampling (WSS)
-Indicates how much time can be saved, at a given level of recall.
-WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
-Typically, WSS is measured at a recall of 0.95. Reasonable because..
-
-$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$
-
-#### Raoul
-#### Utility? 
-#### F-measure 
-#### ROC/AUC
-
-Is performance related to some characteristic (n, inclusion rate, ...)
-
 ## Cross-validation
@@
 
+# Appendix C - supercomputer Cartesius
+
+500,000 SBU
+
+Running on Cartesius is charged in System Billing Units (SBUs), and charging is based on the wall clock time of a job.
+On fat and thin nodes, an SBU is equal to using 1 core for 1 hour (a core hour), or 1 core for 20 minutes on a GPU node.
+Since compute nodes are allocated exclusively to a single job at a time, you will be charged for all cores on that node - even if you are using less.
+
 # References

### 2020-03-13 manuscript/drafts/manuscript.tex
introduce bug

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Manuscript drafts},
  pdfauthor={Gerbrich Ferdinands},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage[]{biblatex}
\addbibresource{asreview.bib}

\title{Manuscript drafts}
\author{Gerbrich Ferdinands}
\date{1/14/2020}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\paragraph{Introduction}\label{introduction}}

\hypertarget{methods}{%
\paragraph{Methods}\label{methods}}

A convenience sample of 5 existing systematic reviews on varying topics
was collected.

\hypertarget{results}{%
\paragraph{Results}\label{results}}

\hypertarget{discussion}{%
\paragraph{Discussion}\label{discussion}}

\newpage

\hypertarget{introduction-1}{%
\section{Introduction}\label{introduction-1}}

Systematic Reviews (SR's) are booming - but they are a lot of work
Various machine learning tools have been proposed to reduce workload in
abstract screening.

\begin{itemize}
\tightlist
\item
  objectives - to demonstrate effectiveness of ml algorithm in reducing
  abstract classification for systematic reviews
\item
  justification -
\item
  background
\item
  guidance to reader
\item
  summary/conclusion
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

This study is about how machine learning algorithms can increase
efficiency in systematic reviews. I will write about what SRs are, and
how workload can be reduced.

Systematic reviews are top of the bill in research. As more and more
papers are published and reproducibility crisis has emerged, science
calls for more meta. It is important reflect on research by giving an
overview of research areas which is typically done by a systematic
review {[}\ldots{]}. Performing a systematic review is a tedious and
time-consuming task. To review a specific research area, one starts out
with an initial search of thousands of academic papers. All these papers
abstracts need to be screened to find an initial batch of possibly
relevant papers. With now hopefully only a couple of hundred papers
left, the researcher needs to read these papers full-text to arrive at a
final selection of papers that are relevant for the final systematic
review {[}this is prisma process?{]}. This whole processes costs this
and this much time {[}shelmilt{]}.

The stage of abstract screening where abstracts are systematically
screened is where a lot is to be gained. This stage is the target of
possible learning algorithms that can assist the reviewer in selecting
the relevant papers. Together with the reviewer /human machine
interaction. The algorithm aims to compute which papers in the pool need
to be excluded and which need to be included, based on the reviewers
decisions. It learns from the reviewers decisions and asks the reviewer
to provide more labels, incrementally improving its class predictions.

The goal of the algorithm defined in the current study is to reduce to
number of abstracts needed to screen (maybe not right term, bit
biomedical). To be more specific, the algorithm aims to present the
reader with the primary studies as soon as possible. This means that at
some point you probably have seen all relevant abstracts and are only
viewing excluded papers, which means you can stop reviewing much earlier
(theoretically spoken). Also reviewing is now much more fun. As compared
to when you have to review all abstracts and you perhaps see only one
relevant abstract every other week/day.

So you might wonder, how does such an algorithm actually work? Active
learning strategy, starting with a pool of unlabeled abstracts (U). The
reviewer starts labeling some instances in U, creating L. The algorithm
utilizes L to predict labels for all abstracts (classifier), by using a
set of features from the papers called X, for example the text in the
abstract (feature extraction method). Now, it made an initial
classification. The algorithm now aims to improve its classification by
which paper from U will be presented to the reviewer next. By labeling
the next paper, the reviewer provides the algorithm with new information
which the algorithm uses to update its prediction.

We approach asr as a classification problem: All papers obtained in the
systematic search form a pool of instances x. All instances x need to be
classified, e.g.~we want to give them a label y. all x are now part of
U,. Binary classification, either inclusion or exclusion. We want to
classify based on some features from the instances \(x\), feature vector
\(\mathbf{X}\).

By starting of with L, the algorithm utilizes characteristics of X to
predict labels in U.

We want to classify the papers in Where the whole collection of papers
in the systematic search form a pool of instances x, with unknown label
y. \textless x,y\textgreater.

\begin{verbatim}
input: a pool of unlabeled abstracts $\mathcal{U}$ 
oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,

  M = train($\mathcal{L}$)
  query x \isin

\end{verbatim}

\begin{itemize}
\item
  pool unlabeled abstracts \(\mathcal{U}\)
\item
  labeled data set \(\mathcal{L}\),
\item
  instance \(x\), label \(y\)
\item
  utility measure \(\phi_A(\cdot)\)
\item
  \(x^*_A\) best query instance according to \(\phi_A(\cdot)\)
\end{itemize}

Now there are a few technical details. Many different versions of such
algorithms exist. Many of such algorithms have been described in the
active learning literature and have been applied in the systematic
reviewing process. Not exhaustive, but the algorithm can apply many
different strategies to arrive at its predictions, which can be divided
in following parameters: classifier, feature extraction strategy,
balancing, query strategy.

Most often the SVM classifier is used, popular and very good results.
Also lots of other configurations. However, other classifiers have not
been tested a lot (polygon thing by cohe, naïve bayes and random forest
by \ldots), but mostly SVM still. Also, most research in the medical
sciences (well there are some exceptions of course {[}conversation
between cohen and matwill{]}

In the current study, we aim at exploring the performance of several
classifiers on reducing workload while maintaining performance in
abstract screening process. This is done by performing simulations on
existing systematic reviews. Performance is evaluated by how much time
can be saved \ldots{} while maintaining accuracy.

Present research questions. RQ1 -- which classifiers perform best? -
RQ1a -- does classifier performance vary over different research areas?
(in what terms does it perform best)

RQ2 different hyperparameter optimizations? Classifiers come with
hyperparameters. We have to make a choice on how to set these
hyperparameters. What we do is create 3 sets, optimizing in three ways,
aggregate results obtained.

The goal is to gain insight in classifiers other than the widely applied
SVM, overall various research areas. So not only medical sciences.

To perform all these computations the research was carried out using the
ASReview software by Utrecht University, which has a simulation mode
that you can just input your labelled review file into and perform a
simulation study with it. To be found on GitHub. It has many adjustable
components/is very versatile.

Then if we still have time left we explore the effect of another feature
extraction method, namely doc2vec. This might possibly increase
performance as it performs better at grasping structure/hidden
relations/hierarchy between words in the texts. So, it could be
interesting in more `fuzzy' research areas. A downside is that it takes
more computing time.

Then if there's even more time we might want to compare a different
balance strategy.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

A SR can be divided into phases. Everything starts with a
\textbf{systematic search}, leading to then citation screening is
performed, then full-text screening \autocite{PRISMA-PGroup2015}

What must be the objective of our tool?: It is the tedious task citation
screening part where loads of time can be saved.

models are designed in a `realistic' way (you have some inclusions)

Selecting papers is a two-step process: abstract \& fulltext screening

Binary classification problem. predict whether a paper in the pool is an
inclusion or exclusion, based on labeled instances from \(\mathcal{L}\)
and use training data to understand how input variables are related to
class.

We're building active learning model who takes X as an input an predicts
class using labels from training set. Model improves by deciding asking
more information from the reviewer (oracle), accounting for imbalance.

\hypertarget{assumptions}{%
\paragraph{Assumptions}\label{assumptions}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  decisions of the original SR are \textbf{ground truth} (benchmark)
  (oracle)
\end{enumerate}

The inclusion rate is \ldots{} data is imbalanced. what is the
philosophy False negatives must be avoided \ldots{} The cost of a false
negative outweighs the cost of a false positive. Note that we assume the
oracle/original user to hold the truth. This is of course not always the
case.

There are two classes in the data: exlusions and inclusions. The
inclusions are clearly the minority class.

Datasets from the medical and social sciences, software engineering and
public administration. Medical sciences SRs are viewed as more
`strict'/`structured' and social sciences more messy.

\hypertarget{active-learning-for-systematic-reviews}{%
\subsection{active learning for systematic
reviews}\label{active-learning-for-systematic-reviews}}

corpus = all the text:

Active learning = increasing classification performance with every
query. The query strategy determines the way unlabeled papers are
queried to the researcher.

\autocite{modAL2018}

RQ1 - what are good classifiers RQ2 - what are good optimization
strategies

\hypertarget{background}{%
\subsection{Background}\label{background}}

\autocite{OMara-Eves2015} literature review

\autocite{Yu2018a}, \autocite{Yu2019} simulated 32 svm classifiers, on
software engineering. A popular classifier is SVM. succes with HUTM
(fastread), uncertainty, mix of weighting and agressive undersampling,
In terms of Yu et al, we adopt .CT.

SVM - tf-idf on medical data, uncertainty sampling, agressive
undersampling. \autocite{Wallace2010}

abstrackr

SVM + Weighting + uncertainty (bow) produced good methods
\autocite{Miwa2014} Also include social sciences data besides medical
data.

\autocite{Cohen2006} perceptron-based classifier (neural network)

SVM on legal documents (no balancing, certainty ) \autocite{Cormack2014}
in limitations section mentions that LR yields about same results, nb
inferior results.

\autocite{Kilicoglu2009} - SVM, naive bayes, boosting and combinations.
future work should optimize parameters. ``Regarding the base classifiers
used in identifying method- ologically rigorous studies, boosting
consistently strikes the best balance between precision and recall,
whereas naive Bayes in general performs well on recall (demonstrating a
tradeoff between recall and precision), as does polynomial SVM on
precision. The AUC results are mixed, although boosting has a slight
edge overall. These results demonstrate that different classifiers can
be used to satisfy different information needs (SVM for specificity,
naive Bayes for sensitivity, and boosting for balance between the two,
for example).''

Our extensions is that we try different classifiers, on more datasets.

This study was approved by the Ethics Committee of the Faculty of Social
and Behavioural Sciences of Utrecht University, filed as an amendement
under study 20-104.

All simulations were run using through cartesius EINF-156

\newpage

\hypertarget{methods-1}{%
\section{Methods}\label{methods-1}}

Goal: evaluate performance of different models of the ASReview tool. The
screening process is simulated using ASReview, seeing if the original
inclusions replicate. What would happen if the citation screening would
have been performed using asreview? All datasets accompanying the
systematic reviews are openly published.

\hypertarget{datasets}{%
\subsection{Datasets}\label{datasets}}

The algorithm will be tested on five systematic reviews from various
research areas. test datasets serve as systematic search results, then
perform active learning to detect inclusions.

Cohen et al.~collected systematic review datasets from the medical
sciences \autocite{Cohen2006}. All systematic reviews in this database
are on drug efficacy. The \emph{ace} dataset used in the current study
comes from a systematic review on the efficacy of Angiotensin-converting
enzyme (ACE) inhibitors.

a machine learning-based citation classification tool to reduce workload
in systematic reviews of drug class efficacy. Using a perceptron
classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in
\autocite{Cohen2006}. (5x2 crossvalidation). Can we beat this? The data

The \emph{software} dataset is retrieved from \autocite{Yu2018a}, who
collected datasets on literature reviews from the software engineering
field. This dataset is on fault prediction in software engineering by
\autocite{Hall2012}.

The \emph{nudging} dataset comes from a review from the behavioural
public administration area. The SR includes studies on nudging
healthcare professionals \autocite{Nagtegaal2019}. The data was stored
on the Harvard Dataverse \autocite{Nagtegaal2019a}.

A literature review from field of psychology, \emph{ptsd}. The SR is on
studies applying latent trajectory analyses on posttraumatic stress
after exposure to trauma \autocite{vandeSchoot2017}. The corresponding
data can be found on the Open Science Framework {[}\ldots{]}.

\emph{wilson}, a dataset from the medical sciences
\autocite{Appenzeller-Herzog2020}. TA review on effectiveness treatments
of Wilson disease \autocite{Appenzeller-Herzog2019}.

All datasets started with an initial pool of thousands of papers. A
fraction of these papers where deemed relevant for the SR, with
inclusion rates around 1-2 percent with one outlier of about 5 percent
(Table 1).

The raw datafiles published with the SRs were preprocessed into a test
dataset. The test datasets contain title information on all citations
obtained in the search strategy. The instances in the data consist of a
title, an abstract and were labeled to indicate which citations were
included in the systematic review. Instances with missing abstracts were
removed. Duplicate instances were removed. Preprocessing scripts can be
found on the GitHub\footnote{\url{https://github.com/GerbrichFerdinands/asreview-thesis}}

Table 1: Statistics on datasets from original systematic reviews.

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Original study} & \multicolumn{3}{c}{Test collection} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Dataset & Candidate studies & Final inclusions & Inclusion rate (\%) & Candidate studies & Final inclusions & Inclusion rate (\%)\\
\midrule
ace & 2544 & 41 & 1.61 & 2235 & 41 & 1.83\\
nudging & 2006 & 100 & 4.99 & 1848 & 100 & 5.41\\
ptsd & 6185 & 38 & 0.61 & 5031 & 38 & 0.76\\
software & 8911 & 104 & 1.17 & 8896 & 104 & 1.17\\
wilson & 3453 & 26 & 0.75 & 2334 & 24 & 1.03\\
\bottomrule
\end{tabu}

\hypertarget{models}{%
\subsection{Models}\label{models}}

Five different active learning models were build. Every model \(m\) was
used to perform an automated systematic review on SR dataset \(d\). The
models all apply a different classifier \(c\) with its own set of
(hyper)parameters \(h\).

\hypertarget{classifiers}{%
\paragraph{Classifiers}\label{classifiers}}

The classifier predicts the class of all papers, given the training
dataset/labeled data set \(\mathcal{L}\).

Given the labels and some features from all abstracts in the pool, the
classifier To predict whether a paper should be an exclusion or an
inclusion, different classifiers

Logistic Regression (L) -

Naive Bayes (B) - predicts the class of an instance given input features
\(\mathbf{X}\). Naive Bayes assumes all features are independent given
the class value. This is obviously not the case but still the algorithm
performs impressively \autocite{Zhang2004}. Especially at \ldots{}
tasks.

Random Forests (R) is where a large number of decision trees are fit on
bootstrapped samples of the original data. All trees cast a vote on the
class, which are aggregated into a class prediciton for each input
\(\mathbf{X}\) \autocite{Breiman2001}.

Support Vecor Machine (S) - finds a multidimensional hyperplane to
separate classes. \autocite{Tong2001}

Dense Neural Network (N) -

Besides \(c\), components of \(m\) are fea

To summarize, every model \(m\) consists of the following key
components: classifier, feature extraction strategy, query strategy,
balance strategy.

For example \(M_1\) BTMD (naive bayes, tfidf, certainty sampling, double
balance) STMD

\hypertarget{word-representation}{%
\paragraph{Word representation}\label{word-representation}}

To be able to predict whether a paper needs to be included or excluded
(e.g.~to predict class), the classifier needs some features from the
papers.\\
As features we use the title and abstract from every paper - this is
what is prescribed by prisma, (check!) The classifier cannot predict the
paper class from the raw titles and abstracts as they are. Therefore,
the content of the texts needs to be transformed into numerical
representations called feature vectors.

A classical example is a `bag of words' representation. For each each
text, the number of occurrences of each word is stored. This leads to n
features, where n is the number of distinct words in the texts
\autocite{scikit-learn}. The bag-of-words method is simplistic and will
highly value often occuring but otherwise meaningless words such as
``and''. Term-frequency Inverse Document Frequency (TF-IDF)
\autocite{Ramos2003} circumvents this problem by adjusting a term
frequency in a text with the inverse docuement frequency, the frequency
of a given word in the entire corpus.

\begin{enumerate}
\def\labelenumi{(\Alph{enumi})}
\setcounter{enumi}{19}
\item
  \begin{enumerate}
  \def\labelenumii{(\Alph{enumii})}
  \setcounter{enumii}{3}
  \tightlist
  \item
  \end{enumerate}
\end{enumerate}

\hypertarget{the-next-abstract-to-be-queried}{%
\paragraph{The next abstract to be
queried}\label{the-next-abstract-to-be-queried}}

The model has various ways of deciding which instance should be queried
next.

\hypertarget{rebalancing-the-training-set}{%
\paragraph{Rebalancing the training
set}\label{rebalancing-the-training-set}}

To account for class imbalance in the data, the model can apply several
strategies to rebalance the training set.

A reweighting strategy is applied where inclusions (the minority class)
are weighted more heavily than the exclusions.

When no balancing is applied, the training data set = labeled data set
\(\mathcal{L}\)

\hypertarget{starting-point}{%
\paragraph{Starting point}\label{starting-point}}

The initial training set consists of 5 inclusions and 5 exclusions,
randomly sampled from the dataset. We use 5 inclusions and exclusions as
we assume the researcher has some prior knowledge on this. The
researcher has some prior knowledge about the pool, some papers ought to
be included in the SR.

\begin{verbatim}
c = naivebayes
f = tfidf
q = max
n_prior_included = 5
n_prior_excluded = 5
\end{verbatim}

\hypertarget{retraining}{%
\paragraph{Retraining}\label{retraining}}

We can choose to retrain the model after labeling \(n\) instances. -
n\_instances=10 (number of papers each query)

\hypertarget{simulations}{%
\subsection{Simulations}\label{simulations}}

To evaluate performance of the five models described above, the model is
used to simulate five existing systematic reviews.

\hypertarget{optimizing-hyperparameters}{%
\subsubsection{Optimizing
hyperparameters}\label{optimizing-hyperparameters}}

For every model*data combination, 3 sets of hyperparameters are
generated to \ldots{} parallel Every model has its own hyperparameters.
For every model, the hyperparameters are optimized three times, arriving
at three versions of the model:

We now have 75 combinations. for every for every model (5), for every
dataset (5) and for every set of optimized hyperparameters (3), a
simulation study consisting trials is performed. From these \(5*5*3=75\)
simulation studies, performance of the different models is evaluated.

A simulation is of one model on one dataset. The simulation is repeated
for 10 trials \(t\).

Every simulation study consists of 10 trials, to account for the
randomness of prior inclusions and exclusions. So every trial the prior
inclusions and exclusions are randomly selected. Results are aggregated
(?)

\hypertarget{statistical-analysis}{%
\subsubsection{Statistical analysis}\label{statistical-analysis}}

\hypertarget{measures}{%
\paragraph{measures}\label{measures}}

\hypertarget{comparison-over-conditions}{%
\paragraph{comparison over
conditions}\label{comparison-over-conditions}}

\hypertarget{the-software}{%
\section{The software}\label{the-software}}

ASReview takes the following parameters/arguments:

\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X}
\toprule
  & Configurations\\
\midrule
Models & 2-Layer Neural Network, Naive Bayes, Random Forest, Support Vector Machine, Logistic Regression\\
Query Strategies & Cluster Sampling, Maximum Sampling, Cluster * Maximum  Sampling, Maximum * Uncertainty Sampling, Maximum * Random Sampling, Cluster * Uncertainty Sampling, Cluster * Random Sampling\\
Feature extraction strategies & Doc2Vec, TF-IDF, sbert, embeddingIdf\\
\bottomrule
\end{tabu}

Use these inputs to predict relevance of papers.

\hypertarget{stage-1-hyperparameter-optimization}{%
\subsubsection{Stage 1: hyperparameter
optimization}\label{stage-1-hyperparameter-optimization}}

Or, more specific:

\begin{tabular}{ll}
\toprule
Models & Feature extraction strategies\\
\midrule
dense\_nn & doc2vec\\
nb & tfidf\\
rf & tfidf\\
svm & doc2vec\\
lr & tfidf\\
\bottomrule
\end{tabular}

\hypertarget{hyperparameters}{%
\subsubsection{Hyperparameters}\label{hyperparameters}}

Every model has its own set of hyperparameters:

\hypertarget{optimization}{%
\subsubsection{Optimization}\label{optimization}}

The hyperparameters are optimized on the 5 datasets in three different
ways:

\begin{itemize}
\tightlist
\item
  1 on 1: maximum performance
\end{itemize}

\[ d = D \] - 4 on 1: cross-validation \[ d \notin D\]

\[ D = {1, 2, 3, 4}\]

\begin{itemize}
\tightlist
\item
  5 on 1: more data = more better?
\end{itemize}

\[ d \in D \]

This results \((5+5+1)*5\) sets of hyperparameters.

\hypertarget{performance-metrics}{%
\paragraph{Performance metrics}\label{performance-metrics}}

For each model, Several metrics are used to compare performance of
different models over datasets,

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\begin{minipage}[b]{0.29\columnwidth}\raggedright
Dataset\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Naive Bayes\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Random Forests\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Support Vector Machine\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Logistic Regression\strut
\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright
Dense Neural Network\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.29\columnwidth}\raggedright
ptsd\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
ace\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
hall\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
nagtegaal\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.29\columnwidth}\raggedright
\ldots.\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
?\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

The goal is twofold: we want to identify all relevant papers, as fast as
we can. Tradeoff: identifying all relevant papers and reducing workload.
A good metric to evaluate this is..

What is more important: recall or precision?

Recall more highly valued than precision.

What about class imbalance?

\hypertarget{rrf}{%
\paragraph{RRF}\label{rrf}}

Amount of relevant references found after having screened a certain
percentage of the total number of abstracts.

\hypertarget{work-saved-over-sampling-wss}{%
\paragraph{Work saved over sampling
(WSS)}\label{work-saved-over-sampling-wss}}

Indicates how much time can be saved, at a given level of recall. WSS is
in terms of the percentage of abstracts that don't have to be screened
by the researcher. Typically, WSS is measured at a recall of 0.95.
Reasonable because..

\[\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) \]

\hypertarget{raoul}{%
\paragraph{Raoul}\label{raoul}}

\hypertarget{utility}{%
\paragraph{Utility?}\label{utility}}

\hypertarget{f-measure}{%
\paragraph{F-measure}\label{f-measure}}

\hypertarget{rocauc}{%
\paragraph{ROC/AUC}\label{rocauc}}

Is performance related to some characteristic (n, inclusion rate,
\ldots)

? How to compare outcomes of 3 different optimization strategies?

\newpage

\hypertarget{results-1}{%
\section{Results}\label{results-1}}

\newpage

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

\newpage

\hypertarget{appendix-a---list-of-definitions}{%
\section{Appendix A - list of
definitions}\label{appendix-a---list-of-definitions}}

\hypertarget{feature-extraction-strategies}{%
\subsubsection{Feature Extraction
Strategies}\label{feature-extraction-strategies}}

split\_ta = overall hyperparameter

\hypertarget{tf-idf}{%
\paragraph{TF-IDF}\label{tf-idf}}

\hypertarget{hyperparameters-1}{%
\subparagraph{hyperparameters}\label{hyperparameters-1}}

\begin{verbatim}
ngram_max: int
        Can use up to ngrams up to ngram_max. For example in the case of
        ngram_max=2, monograms and bigrams could be used.
\end{verbatim}

\hypertarget{doc2vec}{%
\paragraph{Doc2Vec}\label{doc2vec}}

Predicts words from context. Aims at capturing the relations between
word (man-woman, king-queen). \autocite{Le2014}. Using a neural network.

using Continuous Bag-of-Words (CBOW), Skip-Gram model, \ldots. Word
vector \emph{W} and extra: document vector \emph{D}, trained to predict
words in the text.

From gensim \autocite{Rehurek2010}.

\begin{verbatim}
    Arguments
    ---------
    vector_size: int
        Output size of the vector.
    epochs: int
        Number of epochs to train the doc2vec model.
    min_count: int
        Minimum number of occurences for a word in the corpus for it to
        be included in the model.
    workers: int
        Number of threads to train the model with.
    window: int
        Maximum distance over which word vectors influence each other.
    dm_concat: int
        Whether to concatenate word vectors or not.
        See paper for more detail.
    dm: int
        Model to use.
        0: Use distribute bag of words (DBOW).
        1: Use distributed memory (DM).
        2: Use both of the above with half the vector size and concatenate
        them.
    dbow_words: int
        Whether to train the word vectors using the skipgram metho

\end{verbatim}

\hypertarget{sbert}{%
\paragraph{SBERT}\label{sbert}}

BERT-base model with mean-tokens pooling \autocite{Reimers2019}

\hypertarget{embeddingidf}{%
\paragraph{embeddingIdf}\label{embeddingidf}}

This model averages the weighted word vectors of all the words in the
text, in order to get a single feature vector for each text. The weights
are provided by the inverse document frequencies

\hypertarget{models-1}{%
\subsubsection{Models}\label{models-1}}

\hypertarget{naive-bayes}{%
\paragraph{Naive Bayes}\label{naive-bayes}}

Naive Bayes assumes all features are independent given the class value.
\autocite{Zhang2004}

ASReview uses the \texttt{MultinomialNB} from the scikit-learn package
\autocite{scikit-learn}, that implements the naive Bayes algorithm for
multinomially distributed data. \texttt{nb}

Hyperparameters

\begin{itemize}
\tightlist
\item
  alpha - accounts for features not present in learning samples and
  prevents zero probabilities in further computations.
\end{itemize}

\hypertarget{random-forests}{%
\paragraph{Random Forests}\label{random-forests}}

A number of decision trees are fit on bootstrapped samples of the
original data, \autocite{Breiman2001} RandomForestClassifier from
sklearn

Arguments --------- n\_estimators: int Number of estimators.
max\_features: int Number of features in the model. class\_weight: float
Class weight of the inclusions. random\_state: int, RandomState Set the
random state of the RNG. """

\hypertarget{support-vector-machine}{%
\paragraph{Support Vector Machine}\label{support-vector-machine}}

Arguments --------- gamma: str Gamma parameter of the SVM model.
class\_weight: class\_weight of the inclusions. C: C parameter of the
SVM model. kernel: SVM kernel type. random\_state: State of the RNG.

\hypertarget{logistic-regression}{%
\paragraph{Logistic Regression}\label{logistic-regression}}

\hypertarget{dense-neural-network}{%
\paragraph{\texorpdfstring{\textbf{Dense Neural
Network}}{Dense Neural Network}}\label{dense-neural-network}}

\hypertarget{query-strategies}{%
\subsubsection{Query Strategies}\label{query-strategies}}

\begin{itemize}
\tightlist
\item
  Max - Choose the most likely samples to be included according to the
  model
\item
  Uncertainty - choose the most uncertain samples according to the model
  (i.e.~closest to 0.5 probability) \autocite{Lewis1994}
\item
  Random - randomly selects abstracts with no regard to model assigned
  probabilities.
\item
  Cluster - Use clustering after feature extraction on the dataset. Then
  the highest probabilities within random clusters are sampled
\end{itemize}

The following combinations are simulated:

\begin{itemize}
\tightlist
\item
  cluster
\item
  max
\item
  cluster * random
\item
  cluster * uncertainty
\item
  max * cluster
\item
  max * random
\item
  max * uncertainty
\end{itemize}

\hypertarget{balance-strategies}{%
\subsubsection{Balance Strategies}\label{balance-strategies}}

\hypertarget{amount-of-training-data}{%
\subsubsection{amount of training data}\label{amount-of-training-data}}

\begin{itemize}
\tightlist
\item
  n\_instances = number of papers queried each query
\item
  n\_queries = number of queries
\item
  n\_prior\_included: 5
\item
  n\_prior\_excluded:
\end{itemize}

\hypertarget{combinations}{%
\section{Combinations}\label{combinations}}

This leads to 119 combinations of configurations.

\begin{itemize}
\tightlist
\item
  Naive bayes only goes with tfidf feature extraction.
\item
  For the feature extraction strategies we will focus on doc2vec and
  tfidf. (but will compute all 4)
\item
  This leads to 3 * 7 * 4 * 3 + 1 * 7 * 1 * 3 = 273 combinations.
\end{itemize}

See appendix A for a table containing all 273 combinations.

\hypertarget{cross-validation}{%
\subsection{Cross-validation}\label{cross-validation}}

Should give an accurate estimate of maximum performance / future
systematic reviews to be performed.

\hypertarget{appendix-b---combinations}{%
\section{Appendix B - combinations}\label{appendix-b---combinations}}

\begin{longtable}{lll}
\toprule
Model & Query Strategy & Feature extraction strategy\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
Model & Query Strategy & Feature extraction strategy\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
dense\_nn & cluster & doc2vec\\
dense\_nn & max & doc2vec\\
dense\_nn & max * cluster & doc2vec\\
dense\_nn & max * uncertainty & doc2vec\\
dense\_nn & max * random & doc2vec\\
\addlinespace
dense\_nn & cluster * uncertainty & doc2vec\\
dense\_nn & cluster * random & doc2vec\\
dense\_nn & cluster & tfidf\\
dense\_nn & max & tfidf\\
dense\_nn & max * cluster & tfidf\\
\addlinespace
dense\_nn & max * uncertainty & tfidf\\
dense\_nn & max * random & tfidf\\
dense\_nn & cluster * uncertainty & tfidf\\
dense\_nn & cluster * random & tfidf\\
dense\_nn & cluster & sbert\\
\addlinespace
dense\_nn & max & sbert\\
dense\_nn & max * cluster & sbert\\
dense\_nn & max * uncertainty & sbert\\
dense\_nn & max * random & sbert\\
dense\_nn & cluster * uncertainty & sbert\\
\addlinespace
dense\_nn & cluster * random & sbert\\
dense\_nn & cluster & embeddingIdf\\
dense\_nn & max & embeddingIdf\\
dense\_nn & max * cluster & embeddingIdf\\
dense\_nn & max * uncertainty & embeddingIdf\\
\addlinespace
dense\_nn & max * random & embeddingIdf\\
dense\_nn & cluster * uncertainty & embeddingIdf\\
dense\_nn & cluster * random & embeddingIdf\\
nb & cluster & tfidf\\
nb & max & tfidf\\
\addlinespace
nb & max * cluster & tfidf\\
nb & max * uncertainty & tfidf\\
nb & max * random & tfidf\\
nb & cluster * uncertainty & tfidf\\
nb & cluster * random & tfidf\\
\addlinespace
rf & cluster & doc2vec\\
rf & max & doc2vec\\
rf & max * cluster & doc2vec\\
rf & max * uncertainty & doc2vec\\
rf & max * random & doc2vec\\
\addlinespace
rf & cluster * uncertainty & doc2vec\\
rf & cluster * random & doc2vec\\
rf & cluster & tfidf\\
rf & max & tfidf\\
rf & max * cluster & tfidf\\
\addlinespace
rf & max * uncertainty & tfidf\\
rf & max * random & tfidf\\
rf & cluster * uncertainty & tfidf\\
rf & cluster * random & tfidf\\
rf & cluster & sbert\\
\addlinespace
rf & max & sbert\\
rf & max * cluster & sbert\\
rf & max * uncertainty & sbert\\
rf & max * random & sbert\\
rf & cluster * uncertainty & sbert\\
\addlinespace
rf & cluster * random & sbert\\
rf & cluster & embeddingIdf\\
rf & max & embeddingIdf\\
rf & max * cluster & embeddingIdf\\
rf & max * uncertainty & embeddingIdf\\
\addlinespace
rf & max * random & embeddingIdf\\
rf & cluster * uncertainty & embeddingIdf\\
rf & cluster * random & embeddingIdf\\
svm & cluster & doc2vec\\
svm & max & doc2vec\\
\addlinespace
svm & max * cluster & doc2vec\\
svm & max * uncertainty & doc2vec\\
svm & max * random & doc2vec\\
svm & cluster * uncertainty & doc2vec\\
svm & cluster * random & doc2vec\\
\addlinespace
svm & cluster & tfidf\\
svm & max & tfidf\\
svm & max * cluster & tfidf\\
svm & max * uncertainty & tfidf\\
svm & max * random & tfidf\\
\addlinespace
svm & cluster * uncertainty & tfidf\\
svm & cluster * random & tfidf\\
svm & cluster & sbert\\
svm & max & sbert\\
svm & max * cluster & sbert\\
\addlinespace
svm & max * uncertainty & sbert\\
svm & max * random & sbert\\
svm & cluster * uncertainty & sbert\\
svm & cluster * random & sbert\\
svm & cluster & embeddingIdf\\
\addlinespace
svm & max & embeddingIdf\\
svm & max * cluster & embeddingIdf\\
svm & max * uncertainty & embeddingIdf\\
svm & max * random & embeddingIdf\\
svm & cluster * uncertainty & embeddingIdf\\
\addlinespace
svm & cluster * random & embeddingIdf\\
lr & cluster & doc2vec\\
lr & max & doc2vec\\
lr & max * cluster & doc2vec\\
lr & max * uncertainty & doc2vec\\
\addlinespace
lr & max * random & doc2vec\\
lr & cluster * uncertainty & doc2vec\\
lr & cluster * random & doc2vec\\
lr & cluster & tfidf\\
lr & max & tfidf\\
\addlinespace
lr & max * cluster & tfidf\\
lr & max * uncertainty & tfidf\\
lr & max * random & tfidf\\
lr & cluster * uncertainty & tfidf\\
lr & cluster * random & tfidf\\
\addlinespace
lr & cluster & sbert\\
lr & max & sbert\\
lr & max * cluster & sbert\\
lr & max * uncertainty & sbert\\
lr & max * random & sbert\\
\addlinespace
lr & cluster * uncertainty & sbert\\
lr & cluster * random & sbert\\
lr & cluster & embeddingIdf\\
lr & max & embeddingIdf\\
lr & max * cluster & embeddingIdf\\
\addlinespace
lr & max * uncertainty & embeddingIdf\\
lr & max * random & embeddingIdf\\
lr & cluster * uncertainty & embeddingIdf\\
lr & cluster * random & embeddingIdf\\*
\end{longtable}

\hypertarget{appendix-c---supercomputer-cartesius}{%
\section{Appendix C - supercomputer
Cartesius}\label{appendix-c---supercomputer-cartesius}}

500,000 SBU

Running on Cartesius is charged in System Billing Units (SBUs), and
charging is based on the wall clock time of a job. On fat and thin
nodes, an SBU is equal to using 1 core for 1 hour (a core hour), or 1
core for 20 minutes on a GPU node. Since compute nodes are allocated
exclusively to a single job at a time, you will be charged for all cores
on that node - even if you are using less.

\printbibliography[title=References]

\end{document}

### 2020-03-13 manuscript/drafts/simulation/01_simulation.R

@@ -1,5 +1,12 @@
 conditiongrid <- readRDS("manuscript/drafts/simulation/00_conditiongrid.RDS")
 
+# which trials to take? 
+st <- "classifier"
+# only select conditions from stage. 
+conditiongrid <- 
+  conditiongrid %>% 
+  filter(stage == st)
+
 # datasets (5)
 D <- c("ace", "nudging", "ptsd", "software", "wilson")
 
@@ -13,7 +20,7 @@ conditiongrid %>% add_column(ace = 0L,
 opt <- c("all", "four", "one")
 
 # 300 sets of hyperparameters
-expand.grid(conditiongrid$condition, D, opt)
+expand.grid(conditiongrid$condition, data = D, hyperopt = opt)
 
 # pick hyperparameter sets for every model 
 

### 2020-03-17 datasets/data_preprocessing.nb.Rmd
- try fixing .tex bug (still not working) - add logbook on hyperparameter optimization

@@
   drop_na(abstract) %>% # drop entries with missing abstracts
+  filter(abstract != "") %>%
   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
@@
   drop_na(abstract) %>% # drop entries with missing abstracts
+  filter(abstract != "") %>%
   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
@@
    drop_na(abstract) %>% # drop entries with missing abstracts
+   filter(abstract != "") %>%
    distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
@@
    summarise(n = length(abstract),
-                    na = sum(is.na(abstract)),
+                    na = sum(is.na(abstract)), # todo correct this, "NA", or ""
                     narate = sum(is.na(abstract))/length(abstract),

### 2020-03-17 manuscript/drafts/manuscript.Rmd
- try fixing .tex bug (still not working) - add logbook on hyperparameter optimization

@@
    pdf_document:
-    keep_tex: yes
-    citation_package: biblatex
+  #   citation_package: biblatex
 bibliography: asreview.bib

### 2020-03-17 simulation/README.Rmd
- try fixing .tex bug (still not working) - add logbook on hyperparameter optimization

---
title: "logbook simulations"
output:   
  md_document:
    variant: markdown_github
---

This is the log of simulations. 
There are three stages, we start with the first where we are comparing different classifiers.

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r, echo = FALSE}
conditiongrid <- readRDS("00_conditiongrid.RDS")

conditiongrid$condition %>%
  kable(format = "markdown") %>%
  pack_rows("Classifier", 1, 5) %>%
  pack_rows("Feature Extraction", 6, 10) %>%
  pack_rows("Balance Strategy", 11, 20)
```

### Version information
Personal device

Cartesius supercomputer

-----

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")

hyperparametersets %>%
  kable(format = "markdown")
```

R - 275 secs 119% - 5 datasets 
```{r}
275 / 5 * 1000 / 60 # 916 minutes
```

## 1.1 Optimizing (hyper)parameters per model, per dataset (1-1)

### 1.1.1 Ace
```{r}
lubridate::date("2020-03-17")
```

Optimization run on own device 
```{bash, eval = FALSE}
# RCTW
mpirun -n 2 asreview hyper-active -m nb -b double -e tfidf -q max -d ace -n 10000 -r 8 --mpi 
```

Optimization run on Cartesius
```{bash, eval = FALSE}
# RCTW
./cart_hyper_run.py hyper-active -t 10 -m rf -b double -e tfidf -q max -d ace

# SCTW

# LCTW

# NCTW
```

### 1.1.2 Nudging
### 1.1.3 PTSD
### 1.1.4 Software
### 1.1.5 Wilson

# Stage 2 - Feature exraction 
Comparing tfidf with doc2vec

# Stage 3 - Balance strategy
Redo all the analyses with a different balance strategy (aggressive undersampling?)
Probably won't have time for this.

### 2020-03-17 manuscript/drafts/simulation/01_simulation.R

@@ -1,33 +1,0 @@
-conditiongrid <- readRDS("manuscript/drafts/simulation/00_conditiongrid.RDS")
-
-# which trials to take? 
-st <- "classifier"
-# only select conditions from stage. 
-conditiongrid <- 
-  conditiongrid %>% 
-  filter(stage == st)
-
-# datasets (5)
-D <- c("ace", "nudging", "ptsd", "software", "wilson")
-
-conditiongrid %>% add_column(ace = 0L,
-                             nudging = 0L,
-                             ptsd = 0L,
-                             software = 0L,
-                             wilson = 0L)
-
-# optimize hyperparameters (11 sets (1+2*5)) 
-opt <- c("all", "four", "one")
-
-# 300 sets of hyperparameters
-expand.grid(conditiongrid$condition, data = D, hyperopt = opt)
-
-# pick hyperparameter sets for every model 
-
-
-# simulate 
-
-conditiongrid
-
-conditiongrid$pathString <- paste("tree", 
-                                  conditiongrid$condition,)

### 2020-03-17 simulation/00_condition_grid.R

@@ -1,0 +1,33 @@
+# condition grid
+
+# classifier
+c <- c("B", 
+       "R", 
+       "S", 
+       "L", 
+       "N")
+
+# query strategy
+q <- c("C" # certainty
+       #"U" # uncertainty
+)
+
+# feature extraction method
+f <- c("T", # tf-idf
+       "D" # Doc2Vec
+       #"S", # sbert 
+       #"E" # embeddingIdf
+) 
+
+# balance strategy
+b <- c(#"N",# no reblancing 
+       "W", # weighting
+       "U" # undersampling (as a bonus!)
+)
+
+conditiongrid <- tibble(condition = do.call(paste0, expand.grid(c, q, f, b)))
+
+conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec", "AU"))
+# stage 1 = all classifiers + tfidf, stage 2 is repeat with doc2vec, stage 3 is repeat with agressive undersampling. 
+
+saveRDS(conditiongrid, file = "simulation/00_conditiongrid.RDS")

### 2020-03-17 simulation/01_hyperparameter_sets.R

@@ -1,0 +1,34 @@
+conditiongrid <- readRDS("simulation/00_conditiongrid.RDS")
+
+# stage - which trials to take? (1, 2, 3)
+st <- "classifier"
+
+# only select conditions from stage. 
+conditiongrid <- 
+  conditiongrid %>% 
+  filter(stage == st)
+
+# datasets (D)
+D <- c("ace", "nudging", "ptsd", "software", "wilson")
+
+# add datsets? 
+conditiongrid %>% add_column(ace = 0L,
+                             nudging = 0L,
+                             ptsd = 0L,
+                             software = 0L,
+                             wilson = 0L) 
+
+# optimize hyperparameters (11 sets (1+2*5)) 
+opt <- c("one", "four", "all")
+
+# 300 sets of hyperparameters in total 
+# 75 for stage 1
+hyperparametersets <- expand.grid(model = conditiongrid$condition, hyperopt = opt) 
+hyperparametersets <- hyperparametersets %>% 
+  add_column(ace = 0L,
+             nudging = 0L,
+             ptsd = 0L,
+             software = 0L,
+             wilson = 0L)
+# save 
+saveRDS(hyperparametersets, file = "simulation/01_hyperparameter_sets.RDS")

### 2020-03-17 datasets/data_preprocessing.nb.Rmd
udpate simulation

@@
   drop_na(abstract) %>% # drop entries with missing abstracts
-  filter(abstract != "") %>%
+  filter(abstract != "",
+         abstract!= " ") %>
   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

### 2020-03-17 simulation/README.Rmd
udpate simulation

@@
 library(kableExtra)
+
+knitr::opts_chunk$set(echo = FALSE)
 ```
 
-```{r, echo = FALSE}
+```{r}
 conditiongrid <- readRDS("00_conditiongrid.RDS")
 
-conditiongrid$condition %>%
-  kable(format = "markdown") %>%
-  pack_rows("Classifier", 1, 5) %>%
-  pack_rows("Feature Extraction", 6, 10) %>%
-  pack_rows("Balance Strategy", 11, 20)
+conditiongrid %>%
+  kable(format = "markdown")
 ```
@@
 
+asreview
+
 -----
@@
 hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")
-
-hyperparametersets %>%
-  kable(format = "markdown")
 ```
@@
 ### 1.1.1 Ace
+
 ```{r}
@@
 # RCTW
-./cart_hyper_run.py hyper-active -t 10 -m rf -b double -e tfidf -q max -d ace
+./cart_hyper_run.py hyper-active -t 5 -m rf -b double -e tfidf -q max -d ace -r 23
 
@@
 
+```{r}
+# to-do grid 
+todo <- hyperparametersets
+
+# set emojis for grid 
+c <- emo::ji("check")
+
+todo$ace[1] <- c
+```
+
+```{r}
+# save the to-do grid in markdown style
+todo <- todo %>%
+  kable(format = "markdown")
+saveRDS(todo, file = "02_todo_hp.RDS")
+
+todo 
+```
+
 # Stage 2 - Feature exraction 

### 2020-03-17 datasets/data_preprocessing.nb.Rmd
- add nagtegaal dataset

--- 2020-03-17 datasets/data_preprocessing.nb.Rmd
@@
 # raw --------------------------------------------------------------------------
-
+n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
 # asreview ---------------------------------------------------------------------
@@
 # remove missing abstracts 
-final <- final[final$title != "NA", ]
-
-# remove duplicates (171 duplicates)
-final <- final %>%
-  distinct(abstract, .keep_all = TRUE)
-table(final$inclusion_code)
-
-nrow(final)
-final$abstract_included %>% table()
-final$included %>% table()
-
-# 
-write.csv(final, "data/nagtegaal.csv")
+nudging_test <- n_raw %>%
+  drop_na(abstract) %>% # drop entries with missing abstracts
+  filter(abstract != "", abstract != "NA") %>%
+  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
+# missing statistics
 
@@
 ```{r}
-nudging["test", ] <- c(1848, 382, 100)
+nudging["test", ] <- data_descr(nudging_test)
 ```
@@
 # asreview ---------------------------------------------------------------------
-w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv",
-                     header=T)
+w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv", header=T)
 
@@
 wilson["asreview", ] <- data_descr(w_asr)
-
 ```
@@
   drop_na(abstract) %>% # drop entries with missing abstracts
-  filter(abstract != "") %>%
-  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+  filter(abstract != "",
+         abstract!= " ") %>%
+  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
 
@@
 ```{r}
-drops["wilson",] <- 
-  w_asr %>%
+drops["wilson", ] <- w_asr %>%
    summarise(n = length(abstract),
@@
        `incl_test` =  nostudies(all, "test", "incl"), 
-       `inclrate_test` = inclrate(all, "test")
-       ) %>% 
+       `inclrate_test` = inclrate(all, "test")) %>% 
   t() %>% 
@@
 
-# nagtegaal
+# nudging 
+write.csv(nudging_test, "test_datasets/nudging.csv")
 

### 2020-03-23 manuscript/drafts/manuscript.Rmd
- add workflow optimization hyperparameters - add log hyperparameter optimization - add first simulation results BCTW model

@@
 Many of such algorithms have been described in the active learning literature and have been applied in the systematic reviewing process.
-Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strategy.
+Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.
 
@@
 #### Word representation 
-To be able to predict whether a paper needs to be included or excluded (e.g. to predict class), 
-the classifier needs some features from the papers.  
-As features we use the title and abstract from every paper - this is what is prescribed by prisma, (check!) 
-The classifier cannot predict the paper class from the raw titles and abstracts as they are.
-Therefore, the content of the texts needs to be transformed into numerical representations called feature vectors.
+To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
+Examples of such information are titles and abstracts. 
+However, the classifier cannot predict the publication class from titles and abstracts as they are. 
+Their textual content to needs to be mapped to feature vectors. 
+This process of numerically representing textual content is called 'word embeddings'.
 
-A classical example is a 'bag of words' representation. 
-For each each text, the number of occurrences of each word is stored. 
+A classical example of word embeddings a 'bag of words' representation. 
+For each text in the data set, the number of occurrences of each word is stored. 
 This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
 The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
-Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.
+Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
+
+The model expedits features of previously labeled publications and 
+Based on features of the previously labeled inclusions and exclusions, the model
+
+The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
 

### 2020-03-23 simulation/README.Rmd
- add workflow optimization hyperparameters - add log hyperparameter optimization - add first simulation results BCTW model

--- 2020-03-17 simulation/README.Rmd
@@
 This is the log of simulations.
+
+# Simulations
+
+## Hyperparameter optimization
 There are three stages, we start with the first where we are comparing different classifiers.
@@
 library(kableExtra)
+datasets <- c("ace", "ptsd", "nudging", "software", "wilson")
+knitr::opts_chunk$set(echo = FALSE)
 ```
 
-```{r, echo = FALSE}
+```{r}
 conditiongrid <- readRDS("00_conditiongrid.RDS")
 
-conditiongrid$condition %>%
-  kable(format = "markdown") %>%
-  pack_rows("Classifier", 1, 5) %>%
-  pack_rows("Feature Extraction", 6, 10) %>%
-  pack_rows("Balance Strategy", 11, 20)
+conditiongrid %>%
+  kable(format = "markdown")
 ```
@@
 ### Version information
-Personal device
+Personal device: macos catalina 10.15.2
 
 Cartesius supercomputer 
+asreview 0.7.2
+asreview simulation branch reorganization.
 
@@
 
-hyperparametersets %>%
-  kable(format = "markdown")
+# to-do grid 
+todo <- hyperparametersets
+
+# set emojis for grid 
+check <- function(todo, m, ho, d){
+  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("check") 
+  return(todo)
+}
+
+busy <- function(todo, m, ho, d){
+  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("timer") 
+  return(todo)
+}
+
+huh <- function(todo, m, ho, d){
+  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("question") 
+  return(todo)
+}
+
+not <- function(todo, m, ho, d){
+  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("x") 
+  return(todo)
+}
+
 ```
@@
 ## 1.1 Optimizing (hyper)parameters per model, per dataset (1-1)
-
-### 1.1.1 Ace
 ```{r}
 lubridate::date("2020-03-17")
-```
-
-Optimization run on own device 
-```{bash, eval = FALSE}
-# RCTW
-mpirun -n 2 asreview hyper-active -m nb -b double -e tfidf -q max -d ace -n 10000 -r 8 --mpi 
+# i am working on svm model for all datasets 
+todo <- busy(todo, "SCTW", "one", "ace")
 ```
@@
 ```{bash, eval = FALSE}
+# BCTW
+
 # RCTW
-./cart_hyper_run.py hyper-active -t 10 -m rf -b double -e tfidf -q max -d ace
+
+# SCTW 
+./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
+
+# LCTW
+
+# NCTW
+```
+
+***
+
+```{r}
+lubridate::date("2020-03-18")
+todo <- check(todo, "BCTW", "one", datasets)
+todo <- check(todo, "SCTW", "one", "ace")
+```
+
+Store config files from job 7768402, SCTW model.
+
+```{bash, eval = FALSE}
+asreview create-config output/active/svm_max_double_tfidf/ace/trials.pkl -o config/SCTW_ace.ini
+```
+
+Transfer config files to my computer home directory 
+```{bash, eval = FALSE}
+# in own device. 
+scp gerbrich@cartesius.surfsara.nl:asreview/config/SCTW_ace.ini ~
+```
+
+```{bash, eval = FALSE}
+# BCTW
+./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ace -r 23 # 7772446
+./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d nudging -r 23 # 7772450
+./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ptsd -r 23 # 7772452
+./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d software -r 23 # 7772454
+./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d wilson -r 23 # 7772456
+# extract all trials.pkl files 
+scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ace/trials.pkl ~/hyperopt/trials/BCTW_ace.pkl 
+scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/nudging/trials.pkl ~/hyperopt/trials/BCTW_nudging.pkl 
+scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ptsd/trials.pkl ~/hyperopt/trials/BCTW_ptsd.pkl
+scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/software/trials.pkl ~/hyperopt/trials/BCTW_software.pkl 
+scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/wilson/trials.pkl ~/hyperopt/trials/BCTW_wilson.pkl 
+# create config files
+asreview create-config trials/BCTW_ace.pkl -o config/BCTW_ace.ini
+asreview create-config trials/BCTW_nudging.pkl -o config/BCTW_nudging.ini
+asreview create-config trials/BCTW_ptsd.pkl -o config/BCTW_ptsd.ini
+asreview create-config trials/BCTW_software.pkl -o config/BCTW_software.ini
+asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini
+
+# RCTW
 
@@
 # NCTW
+
 ```
 
-### 1.1.2 Nudging
-### 1.1.3 PTSD
-### 1.1.4 Software
-### 1.1.5 Wilson
+***
 
-# Stage 2 - Feature exraction 
+```{r}
+lubridate::date("2020-03-19")
+
+#todo <- check(todo, "BCTW", "one", datasets)
+```
+
+### simulations with nb 
+```{bash, eval = FALSE}
+# create config files within cartesius (scripts folder)
+asreview create-config output/active/nb_max_double_tfidf/ace/trials.pkl -o config/BCTW_ace.ini
+asreview create-config output/active/nb_max_double_tfidf/nudging/trials.pkl  -o config/BCTW_nudging.ini
+asreview create-config output/active/nb_max_double_tfidf/ptsd/trials.pkl  -o config/BCTW_ptsd.ini
+asreview create-config output/active/nb_max_double_tfidf/software/trials.pkl  -o config/BCTW_software.ini
+asreview create-config output/active/nb_max_double_tfidf/wilson/trials.pkl  -o config/BCTW_wilson.ini
+```
+
+```{bash, eval = FALSE}
+# run simulations within cartesius
+./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23
+
+./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23
+
+./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23
+
+./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23
+
+./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
+```
+
+### extract simulation results nb 
+```{bash}
+# transfer files to device 
+scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
+```
+
+```{bash}
+# on own device
+asreview plot asreview-thesis/simulation_output
+```
+
+***
+```{r}
+lubridate::date("2020-03-22")
+todo <- busy(todo, "SCTW", "one", datasets[2:5])
+todo <- busy(todo, c("LCTW", "RCTW", "NCDW"), "one", "ace")
+todo <- not(todo, "NCTW", "one", datasets)
+# do the remaining datasets of svm, and one test run for L and one for R. 
+```
+
+Sent hyperparameters for optimization
+```{bash, eval = FALSE}
+# SCTW
+./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d nudging -r 23 # 7805983
+./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ptsd -r 23 # 7805984
+./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d software -r 23 # 7805985
+./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986
+
+# LCTW 
+./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987
+
+# RCTW 
+./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989
+
+# NCTW does not work well with tfidf, save for second round with doc2vec: 
+# NCDW
+./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021
+
+```
+
+***
+```{r}
+lubridate::date("2020-03-23")
+todo <- check(todo, "SCTW", "one", datasets[3:5])
+```
+
+Resimulate BCTW models.
+ - create-config file from trials.pkl: n_instances 20, 1/1
+ - how to overrule this parameters? (not possible through cli)
+
+```{bash, eval = FALSE}
+./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 
+./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 
+./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 
+./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 
+./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 
+```
+
+Process BCTW models into table
+ - python script to extract statistics
+ -
+
+Checkout hyperopt SCTW
+Nudging dataset doesn't optimize well? 
+```{r}
+todo <- huh(todo, "SCTW", "one", "nudging")
+```
+
+Checkout results first hyperopt: 
+LCTW - no output?? 
+RCTW - only 'current'
+```{r}
+todo <- huh(todo, c("LCTW", "RCTW"), "one", "ace")
+```
+
+NCDW - loss still going down, sent in for another 12 hours. 
+```{bash, eval = FALSE}
+./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
+```
+
+(re)Simulate BCTW models
+Simulate SCTW models
+
+***
+
+```{r}
+lubridate::date("2020-03-24")
+# todo <- busy(todo, "SCTW", "one", datasets[2:5])
+```
+
+Process SCTW models into table
+
+Simulate LCTW, RCTW and NCTW models
+
+Create a nice plot
+
+Send first version of table
+
+***
+
+```{r}
+# save the to-do grid in markdown style
+todo[todo==0] <- emo::ji("white square button")
+todo %>% kable(format = "markdown")
+
+saveRDS(todo %>% kable(format = "markdown"), 
+        file = "02_todo_hp.RDS")
+```
+
+## Stage 2 - Feature extraction 
 Comparing tfidf with doc2vec
 
-# Stage 3 - Balance strategy
+## Stage 3 - Balance strategy
 Redo all the analyses with a different balance strategy (aggressive undersampling?)
 Probably won't have time for this.
+
+# The data 
+On 17 march 2020:
+
+```
+************  ace.csv  ************
+
+Number of papers:            2235
+Number of inclusions:        41 (1.83%)
+Number of exclusions:        2194 (98.17%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        123
+Average abstract length:     1623
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  nudging.csv  ************
+
+Number of papers:            1847
+Number of inclusions:        100 (5.41%)
+Number of exclusions:        1747 (94.59%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        109
+Average abstract length:     1831
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  ptsd.csv  ************
+
+Number of papers:            5031
+Number of inclusions:        38 (0.76%)
+Number of exclusions:        4993 (99.24%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        104
+Average abstract length:     1537
+Number of missing titles:    1 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  software.csv  ************
+
+Number of papers:            8896
+Number of inclusions:        104 (1.17%)
+Number of exclusions:        8792 (98.83%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        81
+Average abstract length:     896
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  wilson.csv  ************
+
+Number of papers:            2333
+Number of inclusions:        23 (0.99%)
+Number of exclusions:        2310 (99.01%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        83
+Average abstract length:     1325
+Number of missing titles:    1 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+```

### 2020-03-23 03_simulate_settings.R

@@ -1,0 +1,5 @@
+# every hyperparameter set gets a config-file 
+
+# now we run x simulations 
+
+# every dataset * model * hyperparameter set a simulation is run 

### 2020-03-23 simulation/00_condition_grid.R

@@ -31,3 +31,6 @@ conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("clas
 # stage 1 = all classifiers + tfidf, stage 2 is repeat with doc2vec, stage 3 is repeat with agressive undersampling. 
 
 saveRDS(conditiongrid, file = "simulation/00_conditiongrid.RDS")
+saveRDS(c("ace", "nudging", "ptsd", "software", "wilson"), file = "simulation/00_datasets.RDS")
+
+        

### 2020-03-23 simulation/01_hyperparameter_sets.R

@@ -1,12 +1,12 @@
 conditiongrid <- readRDS("simulation/00_conditiongrid.RDS")
 
 # stage - which trials to take? (1, 2, 3)
-st <- "classifier"
+st <- c("classifier", "doc2vec")
 
 # only select conditions from stage. 
 conditiongrid <- 
   conditiongrid %>% 
-  filter(stage == st)
+  filter(stage %in% st)
 
 # datasets (D)
 D <- c("ace", "nudging", "ptsd", "software", "wilson")

### 2020-03-23 simulation_output/extractstat.py

@@ -1,0 +1,45 @@
+#!/usr/bin/env python
+# coding: utf-8
+import json
+import numpy as np
+from asreviewcontrib.statistics import StateStatistics
+
+import argparse
+import os
+
+def parse_arguments():
+  parser = argparse.ArgumentParser(description="testing argparser")
+  parser.add_argument("-path", type=dir_path)
+  parser.add_argument("-output", type=dir_path)
+  return parser.parse_args()
+
+def dir_path(path):
+     if os.path.isdir(path):
+         return path
+     else:
+         raise argparse.ArgumentTypeError(f"readable_dir:{path} is not a valid path")
+
+args=parse_arguments()
+
+#print(dir_path(args.path))
+
+# state
+state_dict = StateStatistics.from_path(args.path, wss_vals=[95], rrf_vals=[10]).to_dict()
+
+# settings
+state_dict["settings"] = vars(state_dict["settings"])
+
+# define function to convert numpy int64 to integers
+def convert_int64(mydict):
+    for key, value in mydict.items():
+        if isinstance(value, np.int64):
+            #print(key, value)
+            mydict[key] = int(value)
+        elif isinstance(value, dict):
+            convert_int64(value)
+
+convert_int64(state_dict)
+
+# save as json file
+with open(args.output, "w") as f:
+    json.dump(state_dict, f)

### 2020-03-23 simulation_output/read_statistics.R

@@ -1,0 +1,4 @@
+# 03_
+library(rjson)
+result <- fromJSON(file = "simulation_output/statistics/testoutput.json")
+result

### 2020-03-23 simulation_output/testap.py

@@ -1,0 +1,19 @@
+#!/usr/bin/env python
+import argparse
+import os
+
+def parse_arguments():
+  parser = argparse.ArgumentParser(description="testing argparser")
+  parser.add_argument("-path", type=dir_path)
+  #parser.add_argument("--output", type=dir_path)
+  return parser.parse_args()
+
+def dir_path(path):
+    if os.path.isdir(path):
+        return path
+    else:
+        raise argparse.ArgumentTypeError(f"readable_dir:{path} is not a valid path")
+
+args=parse_arguments()
+
+print(dir_path(args.path))

### 2020-03-23 simulation/01_hyperparameter_sets.R
- add r-scripts to read statistics from json file

@@ -9,7 +9,7 @@ conditiongrid <-
   filter(stage %in% st)
 
 # datasets (D)
-D <- c("ace", "nudging", "ptsd", "software", "wilson")
+D <- readRDS("simulation/00_datasets.RDS")
 
 # add datsets? 
 conditiongrid %>% add_column(ace = 0L,

### 2020-03-23 simulation_output/read_statistics.R

@@ -1,4 +1,15 @@
 # 03_
 library(rjson)
+
+# load datasets
+D <- readRDS("simulation/00_datasets.RDS")
+conditiongrid <- readRDS("simulation/00_conditiongrid.RDS")
+
+# list for hyperopt condition one 
+one <- vector('list', length(D))
+names(one) <- D
+
+# fill dataset elements with conditions 
+
+# load results
 result <- fromJSON(file = "simulation_output/statistics/testoutput.json")
-result

### 2020-03-23 simulation/README.Rmd
Update simulations log

@@
 
-Checkout results first hyperopt: 
-LCTW - no output?? 
+### Checkout results first hyperopt 
+LCTW - no output? 
 RCTW - only 'current'
@@
 
+```{bash, eval = FALSE}
+# LCTW 
+# made a mistake in command, "logistic" instead of "lr", run again 
+./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
+
+# RCTW, fixed a parameter bug in simulation package. 
+./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
+```
+
+```{r}
+todo <- busy(todo, c("LCTW", "RCTW"), "one", "ace")
+```
+
 NCDW - loss still going down, sent in for another 12 hours. 
 ```{bash, eval = FALSE}
+# NCDW
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926

### 2020-03-23 datasets/data_preprocessing.nb.Rmd
- add virus dataset - update simulation log

@@
 
+## Virus dataset
+```{r}
+v_raw <- read.csv("../../sims/data/virus.csv")
+
+sum(v_raw$abstract == "")
+
+v_test <- v_raw %>%
+  drop_na(abstract) %>%
+  filter(abstract != "", abstract != "NA")
+
+v_test <- v_test[v_test$record_id != 1732,]
+
+```
+
 ## Wilson dataset
@@
 write.csv(hall_test, "test_datasets/software.csv")
+
+# virus 
+write.csv(v_test, "test_datasets/virus.csv")
+
 # wilson

### 2020-03-23 simulation/README.Rmd
- add virus dataset - update simulation log

@@
 scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
+
+scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
 ```
@@
 
-Resimulate BCTW models.
- - create-config file from trials.pkl: n_instances 20, 1/1
- - how to overrule this parameters? (not possible through cli)
-
-```{bash, eval = FALSE}
-./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 
-./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 
-./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 
-./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 
-./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 
-```
-
-Process BCTW models into table
- - python script to extract statistics
- -
-
 Checkout hyperopt SCTW
@@
 (re)Simulate BCTW models
-Simulate SCTW models
+
+Resimulate BCTW models.
+ - create-config file from trials.pkl: n_instances 20, 1/1
+ - how to overrule this parameters? (not possible through cli)
+
+```{bash, eval = FALSE}
+./cart_simulate.py data/ace.csv --config_file config/one/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 # 7814382
+./cart_simulate.py data/nudging.csv --config_file config/one/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 # 7814384
+./cart_simulate.py data/ptsd.csv --config_file config/one/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 # 7814391
+./cart_simulate.py data/software.csv --config_file config/one/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 # 7814392 
+./cart_simulate.py data/wilson.csv --config_file config/one/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 # 7814395
+```
 
@@
 ```
+
+Process BCTW models into table
+ - python script to extract statistics
+
+Checkout what happened with NCDW and other errors in hpcbatch
+
+Simulate SCTW models
 

### 2020-03-23 simulation_output/extractstat.py
- remove simulation output from repo to save space, moved elsewhere on device.

@@ -1,45 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-import json
-import numpy as np
-from asreviewcontrib.statistics import StateStatistics
-
-import argparse
-import os
-
-def parse_arguments():
-  parser = argparse.ArgumentParser(description="testing argparser")
-  parser.add_argument("-path", type=dir_path)
-  parser.add_argument("-output", type=dir_path)
-  return parser.parse_args()
-
-def dir_path(path):
-     if os.path.isdir(path):
-         return path
-     else:
-         raise argparse.ArgumentTypeError(f"readable_dir:{path} is not a valid path")
-
-args=parse_arguments()
-
-#print(dir_path(args.path))
-
-# state
-state_dict = StateStatistics.from_path(args.path, wss_vals=[95], rrf_vals=[10]).to_dict()
-
-# settings
-state_dict["settings"] = vars(state_dict["settings"])
-
-# define function to convert numpy int64 to integers
-def convert_int64(mydict):
-    for key, value in mydict.items():
-        if isinstance(value, np.int64):
-            #print(key, value)
-            mydict[key] = int(value)
-        elif isinstance(value, dict):
-            convert_int64(value)
-
-convert_int64(state_dict)
-
-# save as json file
-with open(args.output, "w") as f:
-    json.dump(state_dict, f)

### 2020-03-23 simulation_output/read_statistics.R

@@ -1,15 +1,0 @@
-# 03_
-library(rjson)
-
-# load datasets
-D <- readRDS("simulation/00_datasets.RDS")
-conditiongrid <- readRDS("simulation/00_conditiongrid.RDS")
-
-# list for hyperopt condition one 
-one <- vector('list', length(D))
-names(one) <- D
-
-# fill dataset elements with conditions 
-
-# load results
-result <- fromJSON(file = "simulation_output/statistics/testoutput.json")

### 2020-03-23 simulation_output/testap.py

@@ -1,19 +1,0 @@
-#!/usr/bin/env python
-import argparse
-import os
-
-def parse_arguments():
-  parser = argparse.ArgumentParser(description="testing argparser")
-  parser.add_argument("-path", type=dir_path)
-  #parser.add_argument("--output", type=dir_path)
-  return parser.parse_args()
-
-def dir_path(path):
-    if os.path.isdir(path):
-        return path
-    else:
-        raise argparse.ArgumentTypeError(f"readable_dir:{path} is not a valid path")
-
-args=parse_arguments()
-
-print(dir_path(args.path))

### 2020-03-28 simulation_study/README.Rmd
clean up repository remove unneccesary files

--- 2020-03-23 simulation/README.Rmd
@@
 
-This is the log of simulations.
+The log of the simulation study.
 
-# Simulations
+- hpoptimization. 
+  - Sripts for hyperparameter optimization
+  - 
+- simulation 
+  - scripts for simulation studies
 
@@
 library(kableExtra)
-datasets <- c("ace", "ptsd", "nudging", "software", "wilson")
+datasets <- c("ace", "nudging","ptsd",  "software", "wilson")
 knitr::opts_chunk$set(echo = FALSE)
@@
 ### extract simulation results nb 
-```{bash}
+```{bash, eval = FALSE}
 # transfer files to device 
@@
 
-```{bash}
+```{bash, eval = FALSE}
 # on own device
@@
 todo <- huh(todo, "SCTW", "one", "nudging")
+todo <- check(todo, "SCTW", "one", "nudging")
 ```
@@
 ./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
+# evaluated run, now other datasets
+./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
+./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
+./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
+./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
+./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157
 
@@
 ./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
+# evaluated run, now other datasets
+./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
+./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
+./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
+./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
+./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
 ```
@@
 ```{r}
-todo <- busy(todo, c("LCTW", "RCTW"), "one", "ace")
+todo <- busy(todo, c("LCTW", "RCTW"), "one", datasets)
 ```
@@
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
+# error 
+# accidentally got killed while downgrading tensorflow at the same time. 
+# run again, 7815147
+
+# NCDW for remaining datasets
+
 ```
-
-(re)Simulate BCTW models
 
@@
 
+Optimize BCTW model 6 datasets (for paper)
+```{bash, eval = FALSE}
+./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
+./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
+# create config file (BMTW (M=mixed)) 
+asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
+# move config to device
+scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/
+
+# run simulations (on own device)
+
+# see script
+
+```
+
 ***
@@
 ```{r}
-lubridate::date("2020-03-24")
+lubridate::date("2020-03-27")
 # todo <- busy(todo, "SCTW", "one", datasets[2:5])
+
 ```
 
-Process BCTW models into table
+Process BCTW models simulations into table
  - python script to extract statistics
 
+Create checklist table for simulations
+
 Checkout what happened with NCDW and other errors in hpcbatch 
+```{bash, eval = FALSE}
+# retest with hall dataset 
+./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d hall -r 23 # 7843185
+```
 
@@
 Simulate LCTW, RCTW and NCTW models 
+   - create config files
+   - run simulation
 
@@
 Send first version of table
+
+Move all hyperopt results to harddrive
+
+scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active /Volumes/Gerbrich/asreview/archive/output
+
+scp -r gerbrich@cartesius.surfsara.nl:/output/active/nb_max_random_triple_tfidf ~
+
+scp -r gerbrich@cartesius.surfsara.nl:/asreview/output/active/nb_max_random_triple_tfidf/ /Volumes/Gerbrich/asreview/archive/output
 

### 2020-03-28 03_simulate_settings.R

@@ -1,5 +1,0 @@
-# every hyperparameter set gets a config-file 
-
-# now we run x simulations 
-
-# every dataset * model * hyperparameter set a simulation is run 

### 2020-03-28 manuscript/test/R/asr-parameters.R

@@ -1,91 +1,0 @@
-# Gerbrich Ferdinands, 14-01-2020
-# document all parameters in asreview software
-
-#path <- "~/Downloads/automated-systematic-review-unsupervised/asreview"
-
-#params <- list.files(path, recursive = TRUE, include.dirs = TRUE)
-
-# library(httr)
-# req <- GET("https://api.github.com/repos/qubixes/automated-systematic-review/tree/unsupervised")
-# stop_for_status(req)
-# filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
-# grep("/unsupervised", filelist, value = TRUE, fixed = TRUE)
-
-#params[str_detect(params, ".py", negate = TRUE)]
-
-# model parameters -------------------------------------------------------------
-
-  # categorical variables ------------------------------------------------------
-  params <- list(
-    model = c("lstm_base",
-              "lstm_pool", 
-              "dense_nn",
-              "nb", # naive bayes
-              "rf", # random forest 
-              "svm",
-              "lr"),
-    
-    query_strategy = c("cluster",
-                       "max",
-                       "max * cluster",
-                       "max * uncertainty",
-                       "max * random",
-                       "cluster * uncertainty",
-                       "cluster * random"
-                       #"uncertainty",
-                       #"random",
-                       #"mixed"
-                       ), # is not implemented
-    
-    balance_strategy = c(#"simple",
-                         #"double",
-                         "triple"
-                         #"undersample"s
-                         ),
-    
-    feature_extraction = c("doc2vec",
-                           "tfidf", 
-                           "sbert", 
-                           "embeddingIdf", # ?
-                           "embeddingLSTM") # only for lstm
-  )
-  
-  
-  # but for the current simulation study we only use nb, svm, and rf, and logistic regression.
-  # and do not vary the balance strategy. 
-  params$model <- params[["model"]][4:7]
-  params$balance_strategy <- NULL
-  params$feature_extraction <- params[["feature_extraction"]][1:4]
-  params$training_data <- c("10/10", "5/5", "5/10")
-    
-  # numerical variables --------------------------------------------------------
-  n_instances <- 1 # number of papers queried each query 
-  n_prior_included <- 10 
-  n_prior_excluded <- 10 
-
-  
-  names(params$model) <- params$model
-  names(params$query_strategy) <- params$query_strategy
-  names(params$feature_extraction) <- params$feature_extraction
[…]

### 2020-03-28 manuscript/test/R/packages.R

@@ -1,6 +1,0 @@
-library(tidyverse)
-library(knitr)
-library(xtable)
-library(kableExtra)
-library(captioner)
-library(glue)

### 2020-03-28 simulation_study/00_condition_grid.R

@@ -1,5 +1,4 @@
 # condition grid
-
 # classifier
 c <- c("B", 
        "R", 
@@ -21,13 +20,13 @@ f <- c("T", # tf-idf
 
 # balance strategy
 b <- c(#"N",# no reblancing 
-       "W", # weighting
-       "U" # undersampling (as a bonus!)
+       "D", # dynamic undersampling
+       #"U" # undersampling (as a bonus!)
 )
 
 conditiongrid <- tibble(condition = do.call(paste0, expand.grid(c, q, f, b)))
 
-conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec", "AU"))
+conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec")) #, "AU"))
 # stage 1 = all classifiers + tfidf, stage 2 is repeat with doc2vec, stage 3 is repeat with agressive undersampling. 
 
 saveRDS(conditiongrid, file = "simulation/00_conditiongrid.RDS")

### 2020-03-28 datasets/data_preprocessing.nb.Rmd
update datasets - add virus dataset - add keywords for hyperparameter optimization - add datasets without keywords for simulation

--- 2020-03-17 datasets/data_preprocessing.nb.Rmd
@@
 ---
-This notebook processes all five systematic review datasets into datasets that can be used for testing asreview.
+This notebook processes all systematic review datasets into datasets suitable testing asreview.
 
-```{r, results = "hide"}
+Every dataset is a .csv file with the following columns: 
+  - title
+  - abstract
+  - label_included
+  - keywords? (?)
+
+Entries with missing abstracts are removed
+
+```{r, include = FALSE}
 library(tidyverse)
@@
 ### Set-up
-```{r}
+```{r, echo = FALSE}
+datasets <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
+nd <- length(datasets)
 # create storage for statistics
@@
 # statistics on duplicates and dropping in ASReview dataset
-drops <- data.frame(n = rep(0,5), # candidates
-                    na = rep(0,5),# number of missing abstracts
-                    narate = rep(0,5), # percenta of missing abstracts
-                    dup = rep(0,5),  # number of duplicate abstracts 
-                    duprate = rep(0,5), # percentage of missing abstracts
-                    row.names = c("ace", "nudging", "ptsd", "software", "wilson"))
+drops <- data.frame(n = rep(0,nd), # candidates
+                    na = rep(0,nd),# number of missing abstracts
+                    narate = rep(0,nd), # percentage of missing abstracts
+                    dup = rep(0,nd),  # number of duplicate abstracts 
+                    duprate = rep(0,nd), # percentage of missing abstracts
+                    row.names = datasets)
 
@@
 
-## Ace dataset 
+## ACE
 ```{r}
@@
                      header=T)
+# replace empty abstracts by NA values.
+
+ace_asr[ace_asr$abstract == "", "abstract"] <- NA
+# stats on missingness in this data
+drops["ace",] <- ace_asr %>%
+           summarise(n = length(abstract),
+                    na = sum(is.na(abstract)),
+                    na_rate = sum(is.na(abstract))/length(abstract)*100,
+                    dup = sum(duplicated(abstract, incomparables = NA)),
+                    dup_rate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
 
@@
 ```{r}
-# replace empty abstracts by NA values. 
-ace_asr[ace_asr$abstract == "", "abstract"] <- NA
-
 # drop missings and duplicates. 
@@
   drop_na(abstract) %>% # drop entries with missing abstracts
-  filter(abstract != "") %>%
   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
-
-# select columns
-ace_test <- ace_test %>%
-       select(authors, title, abstract, label_included) # select relevant columns
 
@@
 # missingness and duplicates in raw data on ASReview
-drops["ace",] <- ace_asr %>%
-          summarise(n = length(abstract),
-                    na = sum(is.na(abstract)),
-                    na_rate = sum(is.na(abstract))/length(abstract),
-                    dup = sum(duplicated(abstract, incomparables = NA)),
-                    dup_rate = sum(duplicated(abstract, incomparables = NA))/length(abstract))
 drops["ace",]
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 # data is not public yet
@@
 n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
+
+# missing statistics 
+drops["nudging",] <- n_raw %>%
+          summarise(n = length(abstract),
+                    na = sum(is.na(abstract)),
+                    na_rate = sum(is.na(abstract))/length(abstract)*100,
+                    dup = sum(duplicated(abstract, incomparables = NA)),
+                    dup_rate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
 # asreview ---------------------------------------------------------------------
@@
   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
-# missing statistics
+
+nudging["test", ] <- data_descr(nudging_test)
 
@@
 
+### Some statistics
 ```{r}
-nudging["test", ] <- data_descr(nudging_test)
+
+drops["nudging",]
+nudging
 ```
@@
 
+# statistics on duplicates from asr data to test
+drops["ptsd", ] <- ptsd_asr %>%
+  summarise(n = length(abstract),
+                    na = sum(is.na(abstract)),
+                    narate = sum(is.na(abstract))/length(abstract)*100,
+                    dup = sum(duplicated(abstract, incomparables = NA)),
+                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
 ```
@@
   drop_na(abstract) %>% # drop entries with missing abstracts
-  filter(abstract != "") %>%
+  filter(abstract != "", abstract != "NA") %>%
   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+
 ```
@@
 ptsd_test <- ptsd_test %>%
-  select(authors, title, abstract, included, inclusion_code) # select relevant columns
+  select(authors, title, abstract, keywords, included, inclusion_code) # select relevant columns
+
+ptsd["test", ] <- data_descr(ptsd_test)
 ```
@@
 ```{r}
-ptsd["test", ] <- data_descr(ptsd_test)
-
-# statistics on duplicates from asr data to test
-drops["ptsd", ] <- ptsd_asr %>%
-  summarise(n = length(abstract),
-                    na = sum(is.na(abstract)),
-                    narate = sum(is.na(abstract))/length(abstract),
-                    dup = sum(duplicated(abstract, incomparables = NA)),
-                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))
-
+drops["ptsd", ]
 ptsd
@@
                     na = sum(is.na(abstract)),
-                    narate = sum(is.na(abstract))/length(abstract),
+                    narate = sum(is.na(abstract))/length(abstract)*100,
                     dup = sum(duplicated(abstract, incomparables = NA)),
-                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))
+                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
 
 hall
+```
+
+## Virus dataset
+```{r}
+virus <- template
+virus["paper",] <- c(2481, 132, 120)
+v_raw <- read.csv("../../sims/data/virus.csv")
+v_raw$abstract[v_raw$abstract == ""] <- NA
+
+virus["raw", ] <- data_descr(v_raw)
+
+drops["virus", ] <- 
+  v_raw %>%
+  summarise(n = length(abstract),
+                    na = sum(is.na(abstract)),
+                    narate = sum(is.na(abstract))/length(abstract)*100,
+                    dup = sum(duplicated(abstract, incomparables = NA)),
+                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
+
+v_test <- v_raw %>%
+  drop_na(abstract) %>% # drop entries with missing abstracts
+   filter(abstract != "") %>%
+   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+
+virus["test",] <- data_descr(v_test)
 ```
@@
 
+w_asr[w_asr$abstract == "", "abstract"] <- NA
+drops["wilson", ] <- w_asr %>%
+   summarise(n = length(abstract),
+                    na = sum(is.na(abstract)),
+                    narate = sum(is.na(abstract))/length(abstract)*100,
+                    dup = sum(duplicated(abstract, incomparables = NA)),
+                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract)*100)
 # add inclusion_code label 
@@
   drop_na(abstract) %>% # drop entries with missing abstracts
-  filter(abstract != "",
-         abstract!= " ") %>%
   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
-
-# select relevant columns
-w_test <- w_test %>%
-  select(authors, title, abstract, included, inclusion_code)
 
@@
 ```{r}
-drops["wilson", ] <- w_asr %>%
-   summarise(n = length(abstract),
-                    na = sum(is.na(abstract)), # todo correct this, "NA", or ""
-                    narate = sum(is.na(abstract))/length(abstract),
-                    dup = sum(duplicated(abstract, incomparables = NA)),
-                    duprate = sum(duplicated(abstract, incomparables = NA))/length(abstract))
+drops["wilson",]
 
@@
 save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
+
+saveRDS(drops, file = "data_statistics/drops.RDS")
 ```
@@
   kable_styling(full_width = TRUE)
+
 ```
@@
 # ace
-write.csv(ace_test, "test_datasets/ace.csv")
+write.csv(ace_test %>%  select(authors, title, abstract, keywords, label_included), "test_datasets/ace.csv")
 
-# nudging 
-write.csv(nudging_test, "test_datasets/nudging.csv")
+# nudging (no keywords available)
+write.csv(nudging_test %>% select(title, abstract, included), "test_datasets/nudging.csv")
 
 # ptsd
-write.csv(ptsd_test, "test_datasets/ptsd.csv")
+write.csv(ptsd_test %>% select(authors, title, abstract, keywords, included), "test_datasets/ptsd.csv")
 
-# hall
+# hall (no keywords available )
 write.csv(hall_test, "test_datasets/software.csv")
+
+# virus 
+write.csv(v_test %>% select(authors, title, abstract, keywords, included), "test_datasets/virus.csv")
+
 # wilson
-write.csv(w_test, "test_datasets/wilson.csv")
+write.csv(w_test %>% select(authors, title, abstract, keywords, included), "test_datasets/wilson.csv")
+```
 
+# write test dataset files for simulation (removing keywords)
+```{r}
+# ace
+write.csv(ace_test %>%  select(authors, title, abstract, label_included), "sim_datasets/ace.csv")
+# nudging (no keywords available)
+write.csv(nudging_test %>% select(title, abstract, included), "sim_datasets/nudging.csv")
+# ptsd
+write.csv(ptsd_test %>% select(authors, title, abstract, included), "sim_datasets/ptsd.csv")
+# hall (no keywords available )
+write.csv(hall_test, "sim_datasets/software.csv")
+# virus 
+write.csv(v_test %>% select(authors, title, abstract, included), "sim_datasets/virus.csv")
+# wilson
+write.csv(w_test %>% select(authors, title, abstract, included), "sim_datasets/wilson.csv")
 ```

### 2020-03-28 datasets/data_preprocessing.nb.Rmd
test hyperopt through shell script

@@
 # Write all test dataset files 
-```{r}
+```{r, eval = FALSE}
 # ace
@@
 # write test dataset files for simulation (removing keywords)
-```{r}
+```{r, eval = FALSE}
 # ace
@@
 ```
+
+To check:
+```{bash , eval = FALSE}
+asreview stat test_datasets/*
+```
+
+returns 
+```
+************  ace.csv  ************
+
+Number of papers:            2235
+Number of inclusions:        41 (1.83%)
+Number of exclusions:        2194 (98.17%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        123
+Average abstract length:     1623
+Average number of keywords:  15.0
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  nudging.csv  ************
+
+Number of papers:            1847
+Number of inclusions:        100 (5.41%)
+Number of exclusions:        1747 (94.59%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        109
+Average abstract length:     1831
+Average number of keywords:  None
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  ptsd.csv  ************
+
+Number of papers:            5031
+Number of inclusions:        38 (0.76%)
+Number of exclusions:        4993 (99.24%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        104
+Average abstract length:     1537
+Average number of keywords:  9.9
+Number of missing titles:    1 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  software.csv  ************
+
+Number of papers:            8896
+Number of inclusions:        104 (1.17%)
+Number of exclusions:        8792 (98.83%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        81
+Average abstract length:     896
+Average number of keywords:  None
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  virus.csv  ************
+
+Number of papers:            2304
+Number of inclusions:        114 (4.95%)
+Number of exclusions:        2190 (95.05%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        103
+Average abstract length:     1345
+Average number of keywords:  20.3
+Number of missing titles:    0 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+************  wilson.csv  ************
+
+Number of papers:            2333
+Number of inclusions:        23 (0.99%)
+Number of exclusions:        2310 (99.01%)
+Number of unlabeled:         0 (0.00%)
+Average title length:        83
+Average abstract length:     1325
+Average number of keywords:  31.3
+Number of missing titles:    1 (of which 0 included)
+Number of missing abstracts: 0 (of which 0 included)
+
+```

### 2020-03-28 simulation_study/README.Rmd
test hyperopt through shell script

@@
 
-scp -r gerbrich@cartesius.surfsara.nl:/asreview/output/active/nb_max_random_triple_tfidf/ /Volumes/Gerbrich/asreview/archive/output
+scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf ~
 
+scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/best ~
 ***

### 2020-03-28 simulation_study/hpoptimization/input.sh

@@ -1,0 +1,2 @@
+!#/bin/bash
+./cart_hyper_run.py hyper-active -t 5 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402

### 2020-03-30 simulation_study/01_hyperparameter_sets.R
update hp optimization checklists

@@ -1,34 +1,0 @@
-conditiongrid <- readRDS("simulation/00_conditiongrid.RDS")
-
-# stage - which trials to take? (1, 2, 3)
-st <- c("classifier", "doc2vec")
-
-# only select conditions from stage. 
-conditiongrid <- 
-  conditiongrid %>% 
-  filter(stage %in% st)
-
-# datasets (D)
-D <- readRDS("simulation/00_datasets.RDS")
-
-# add datsets? 
-conditiongrid %>% add_column(ace = 0L,
-                             nudging = 0L,
-                             ptsd = 0L,
-                             software = 0L,
-                             wilson = 0L) 
-
-# optimize hyperparameters (11 sets (1+2*5)) 
-opt <- c("one", "four", "all")
-
-# 300 sets of hyperparameters in total 
-# 75 for stage 1
-hyperparametersets <- expand.grid(model = conditiongrid$condition, hyperopt = opt) 
-hyperparametersets <- hyperparametersets %>% 
-  add_column(ace = 0L,
-             nudging = 0L,
-             ptsd = 0L,
-             software = 0L,
-             wilson = 0L)
-# save 
-saveRDS(hyperparametersets, file = "simulation/01_hyperparameter_sets.RDS")

### 2020-03-30 simulation_study/R/00_condition_grid.R

@@ -19,17 +19,17 @@ f <- c("T", # tf-idf
 ) 
 
 # balance strategy
-b <- c(#"N",# no reblancing 
-       "D", # dynamic undersampling
+b <- c(#"S",# simple, no reblancing 
+       "D" # double (dynamic supersampling)
        #"U" # undersampling (as a bonus!)
 )
 
 conditiongrid <- tibble(condition = do.call(paste0, expand.grid(c, q, f, b)))
 
-conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec")) #, "AU"))
+#conditiongrid$stage <- factor(c(rep(1:2, each = 5), rep(3,10)), labels = c("classifier", "doc2vec")) #, "AU"))
 # stage 1 = all classifiers + tfidf, stage 2 is repeat with doc2vec, stage 3 is repeat with agressive undersampling. 
 
-saveRDS(conditiongrid, file = "simulation/00_conditiongrid.RDS")
-saveRDS(c("ace", "nudging", "ptsd", "software", "wilson"), file = "simulation/00_datasets.RDS")
+saveRDS(conditiongrid, file = "R/00_conditiongrid.RDS")
+saveRDS(c("ace", "nudging", "ptsd", "software", "virus", "wilson"), file = "R/00_datasets.RDS")
 
         

### 2020-03-30 simulation_study/hpoptimization/input.sh

@@ -1,2 +1,4 @@
 !#/bin/bash
-./cart_hyper_run.py hyper-active -t 5 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
+./cart_hyper_run.py hyper-active -t 5 -m svm -b double -q max -e tfidf -q max -d ace -r 23 # job id 7768402
+
+./cart

### 2020-03-30 manuscript/drafts/manuscript.tex

@@
 \usepackage{xcolor}
-\usepackage[]{biblatex}
-\addbibresource{asreview.bib}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
 
@@
 \textbf{systematic search}, leading to then citation screening is
-performed, then full-text screening \autocite{PRISMA-PGroup2015}
+performed, then full-text screening (PRISMA-P Group et al. 2015)
 
@@
 
-\autocite{modAL2018}
+(Danka and Horvath, n.d.)
 
@@
 
-\autocite{OMara-Eves2015} literature review
-
-\autocite{Yu2018a}, \autocite{Yu2019} simulated 32 svm classifiers, on
-software engineering. A popular classifier is SVM. succes with HUTM
-(fastread), uncertainty, mix of weighting and agressive undersampling,
-In terms of Yu et al, we adopt .CT.
+(O'Mara-Eves et al. 2015) literature review
+
+(Yu, Kraft, and Menzies 2018), (Yu and Menzies 2019) simulated 32 svm
+classifiers, on software engineering. A popular classifier is SVM.
+succes with HUTM (fastread), uncertainty, mix of weighting and agressive
+undersampling, In terms of Yu et al, we adopt .CT.
 
 SVM - tf-idf on medical data, uncertainty sampling, agressive
-undersampling. \autocite{Wallace2010}
+undersampling. (Wallace et al. 2010)
 
@@
 
-SVM + Weighting + uncertainty (bow) produced good methods
-\autocite{Miwa2014} Also include social sciences data besides medical
-data.
-
-\autocite{Cohen2006} perceptron-based classifier (neural network)
-
-SVM on legal documents (no balancing, certainty ) \autocite{Cormack2014}
-in limitations section mentions that LR yields about same results, nb
-inferior results.
-
-\autocite{Kilicoglu2009} - SVM, naive bayes, boosting and combinations.
+SVM + Weighting + uncertainty (bow) produced good methods (Miwa et al.
+2014) Also include social sciences data besides medical data.
+
+(Cohen et al. 2006) perceptron-based classifier (neural network)
+
+SVM on legal documents (no balancing, certainty ) (Cormack and Grossman
+2014) in limitations section mentions that LR yields about same results,
+nb inferior results.
+
+(Kilicoglu et al. 2009) - SVM, naive bayes, boosting and combinations.
 future work should optimize parameters. ``Regarding the base classifiers
@@
 Cohen et al.~collected systematic review datasets from the medical
-sciences \autocite{Cohen2006}. All systematic reviews in this database
+sciences (Cohen et al. 2006). All systematic reviews in this database
 are on drug efficacy. The \emph{ace} dataset used in the current study
@@
 in systematic reviews of drug class efficacy. Using a perceptron
-classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in
-\autocite{Cohen2006}. (5x2 crossvalidation). Can we beat this? The data
-
-The \emph{software} dataset is retrieved from \autocite{Yu2018a}, who
-collected datasets on literature reviews from the software engineering
-field. This dataset is on fault prediction in software engineering by
-\autocite{Hall2012}.
+classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in (Cohen
+et al. 2006). (5x2 crossvalidation). Can we beat this? The data
+
+The \emph{software} dataset is retrieved from (Yu, Kraft, and Menzies
+2018), who collected datasets on literature reviews from the software
+engineering field. This dataset is on fault prediction in software
+engineering by (Hall et al. 2012).
 
@@
 public administration area. The SR includes studies on nudging
-healthcare professionals \autocite{Nagtegaal2019}. The data was stored
-on the Harvard Dataverse \autocite{Nagtegaal2019a}.
+healthcare professionals (Nagtegaal et al. 2019a). The data was stored
+on the Harvard Dataverse (Nagtegaal et al. 2019b).
 
@@
 studies applying latent trajectory analyses on posttraumatic stress
-after exposure to trauma \autocite{vandeSchoot2017}. The corresponding
-data can be found on the Open Science Framework {[}\ldots{]}.
-
-\emph{wilson}, a dataset from the medical sciences
-\autocite{Appenzeller-Herzog2020}. TA review on effectiveness treatments
-of Wilson disease \autocite{Appenzeller-Herzog2019}.
+after exposure to trauma (\noopsort{schoot}van de Schoot et al. 2017).
+The corresponding data can be found on the Open Science Framework
+{[}\ldots{]}.
+
+\emph{wilson}, a dataset from the medical sciences (Appenzeller-Herzog
+2020). TA review on effectiveness treatments of Wilson disease
+(Appenzeller-Herzog et al. 2019).
 
@@
 the class value. This is obviously not the case but still the algorithm
-performs impressively \autocite{Zhang2004}. Especially at \ldots{}
-tasks.
+performs impressively (Zhang 2004). Especially at \ldots{} tasks.
 
@@
 class, which are aggregated into a class prediciton for each input
-\(\mathbf{X}\) \autocite{Breiman2001}.
+\(\mathbf{X}\) (Breiman 2001).
 
 Support Vecor Machine (S) - finds a multidimensional hyperplane to
-separate classes. \autocite{Tong2001}
+separate classes. (Tong and Koller 2001)
 
@@
 features, where n is the number of distinct words in the texts
-\autocite{scikit-learn}. The bag-of-words method is simplistic and will
+(Pedregosa et al. 2011). The bag-of-words method is simplistic and will
 highly value often occuring but otherwise meaningless words such as
-``and''. Term-frequency Inverse Document Frequency (TF-IDF)
-\autocite{Ramos2003} circumvents this problem by adjusting a term
-frequency in a text with the inverse docuement frequency, the frequency
-of a given word in the entire corpus.
+``and''. Term-frequency Inverse Document Frequency (TF-IDF) (Ramos and
+others 2003) circumvents this problem by adjusting a term frequency in a
+text with the inverse docuement frequency, the frequency of a given word
+in the entire corpus.
 
@@
 Predicts words from context. Aims at capturing the relations between
-word (man-woman, king-queen). \autocite{Le2014}. Using a neural network.
+word (man-woman, king-queen). (Le and Mikolov 2014). Using a neural
+network.
 
@@
 
-From gensim \autocite{Rehurek2010}.
+From gensim (Řehůřek and Sojka 2010).
 
@@
 
-BERT-base model with mean-tokens pooling \autocite{Reimers2019}
+BERT-base model with mean-tokens pooling (Reimers and Gurevych 2019)
 
@@
 Naive Bayes assumes all features are independent given the class value.
-\autocite{Zhang2004}
+(Zhang 2004)
 
 ASReview uses the \texttt{MultinomialNB} from the scikit-learn package
-\autocite{scikit-learn}, that implements the naive Bayes algorithm for
+(Pedregosa et al. 2011), that implements the naive Bayes algorithm for
 multinomially distributed data. \texttt{nb}
@@
 A number of decision trees are fit on bootstrapped samples of the
-original data, \autocite{Breiman2001} RandomForestClassifier from
-sklearn
+original data, (Breiman 2001) RandomForestClassifier from sklearn
 
@@
   Uncertainty - choose the most uncertain samples according to the model
-  (i.e.~closest to 0.5 probability) \autocite{Lewis1994}
+  (i.e.~closest to 0.5 probability) (Lewis and Catlett 1994)
 \item
@@
 
-\printbibliography[title=References]
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{cslreferences}
+\leavevmode\hypertarget{ref-Appenzeller-Herzog2020}{}%
+Appenzeller-Herzog, Christian. 2020. ``Data from Comparative
+Effectiveness of Common Therapies for Wilson Disease: A Systematic
+Review and Meta-Analysis of Controlled Studies.'' Zenodo.
+
+\leavevmode\hypertarget{ref-Appenzeller-Herzog2019}{}%
+Appenzeller-Herzog, Christian, Tim Mathes, Marlies L. S. Heeres, Karl
+Heinz Weiss, Roderick H. J. Houwen, and Hannah Ewald. 2019.
+``Comparative Effectiveness of Common Therapies for Wilson Disease: A
+Systematic Review and Meta-Analysis of Controlled Studies.'' \emph{Liver
+International} 39 (11): 2136--52.
+\url{https://doi.org/10.1111/liv.14179}.
+
+\leavevmode\hypertarget{ref-Breiman2001}{}%
+Breiman, Leo. 2001. ``Random Forests.'' \emph{Machine Learning} 45 (1):
+5--32. \url{https://doi.org/10.1023/A:1010933404324}.
+
+\leavevmode\hypertarget{ref-Cohen2006}{}%
+Cohen, A. M., W. R. Hersh, K. Peterson, and Po-Yin Yen. 2006. ``Reducing
+Workload in Systematic Review Preparation Using Automated Citation
+Classification.'' \emph{Journal of the American Medical Informatics
+Association : JAMIA} 13 (2): 206--19.
+\url{https://doi.org/10.1197/jamia.M1929}.
+
+\leavevmode\hypertarget{ref-Cormack2014}{}%
+Cormack, Gordon V., and Maura R. Grossman. 2014. ``Evaluation of
+Machine-Learning Protocols for Technology-Assisted Review in Electronic
+Discovery.'' In \emph{Proceedings of the 37th International ACM SIGIR
+Conference on Research \& Development in Information Retrieval},
+153--62. SIGIR '14. Gold Coast, Queensland, Australia: Association for
+Computing Machinery. \url{https://doi.org/10.1145/2600428.2609601}.
+
+\leavevmode\hypertarget{ref-modAL2018}{}%
+Danka, Tivadar, and Peter Horvath. n.d. ``modAL: A Modular Active
+Learning Framework for Python.''
+
+\leavevmode\hypertarget{ref-Hall2012}{}%
+Hall, Tracy, Sarah Beecham, David Bowes, David Gray, and Steve Counsell.
+2012. ``A Systematic Literature Review on Fault Prediction Performance
+in Software Engineering.'' \emph{IEEE Transactions on Software
+Engineering} 38 (6): 1276--1304.
+\url{https://doi.org/10.1109/TSE.2011.103}.
+
+\leavevmode\hypertarget{ref-Kilicoglu2009}{}%
+Kilicoglu, H., D. Demner-Fushman, T. C. Rindflesch, N. L. Wilczynski,
+and R. B. Haynes. 2009. ``Towards Automatic Recognition of
+Scientifically Rigorous Clinical Research Evidence.'' \emph{Journal of
+the American Medical Informatics Association} 16 (1): 25--31.
+\url{https://doi.org/10/bjkhh9}.
+
+\leavevmode\hypertarget{ref-Le2014}{}%
+Le, Quoc V., and Tomas Mikolov. 2014. ``Distributed Representations of
+Sentences and Documents.'' \emph{arXiv:1405.4053 {[}Cs{]}}, May.
+\url{http://arxiv.org/abs/1405.4053}.
+
+\leavevmode\hypertarget{ref-Lewis1994}{}%
+Lewis, David D., and Jason Catlett. 1994. ``Heterogeneous Uncertainty
+Sampling for Supervised Learning.'' In \emph{Machine Learning
+Proceedings 1994}, edited by William W. Cohen and Haym Hirsh, 148--56.
+San Francisco (CA): Morgan Kaufmann.
+\url{https://doi.org/10.1016/B978-1-55860-335-6.50026-X}.
+
+\leavevmode\hypertarget{ref-Miwa2014}{}%
+Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
+2014. ``Reducing Systematic Review Workload Through Certainty-Based
+Screening.'' \emph{Journal of Biomedical Informatics} 51 (October):
+242--53. \url{https://doi.org/10.1016/j.jbi.2014.06.005}.
+
+\leavevmode\hypertarget{ref-Nagtegaal2019}{}%
+Nagtegaal, Rosanna, Lars Tummers, Mirko Noordegraaf, and Victor Bekkers.
+2019a. ``Nudging Healthcare Professionals Towards Evidence-Based
+Medicine: A Systematic Scoping Review.'' \emph{Journal of Behavioral
+Public Administration} 2 (2).
+\url{https://doi.org/doi.org/10.30636/jbpa.22.71}.
+
+\leavevmode\hypertarget{ref-Nagtegaal2019a}{}%
+---------. 2019b. ``Nudging Healthcare Professionals Towards
+Evidence-Based Medicine: A Systematic Scoping Review.'' Harvard
+Dataverse.
+
+\leavevmode\hypertarget{ref-OMara-Eves2015}{}%
+O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
+Sophia Ananiadou. 2015. ``Using Text Mining for Study Identification in
+Systematic Reviews: A Systematic Review of Current Approaches.''
+\emph{Systematic Reviews} 4 (1): 5.
+\url{https://doi.org/10.1186/2046-4053-4-5}.
+
+\leavevmode\hypertarget{ref-scikit-learn}{}%
+Pedregosa, F., G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O.
+Grisel, M. Blondel, et al. 2011. ``Scikit-Learn: Machine Learning in
+Python.'' \emph{Journal of Machine Learning Research} 12: 2825--30.
+
+\leavevmode\hypertarget{ref-PRISMA-PGroup2015}{}%
+PRISMA-P Group, David Moher, Larissa Shamseer, Mike Clarke, Davina
+Ghersi, Alessandro Liberati, Mark Petticrew, Paul Shekelle, and Lesley A
+Stewart. 2015. ``Preferred Reporting Items for Systematic Review and
+Meta-Analysis Protocols (PRISMA-P) 2015 Statement.'' \emph{Systematic
+Reviews} 4 (1): 1. \url{https://doi.org/10.1186/2046-4053-4-1}.
+
+\leavevmode\hypertarget{ref-Ramos2003}{}%
+Ramos, Juan, and others. 2003. ``Using Tf-Idf to Determine Word
+Relevance in Document Queries.'' In \emph{Proceedings of the First
+Instructional Conference on Machine Learning}, 242:133--42. Piscataway,
+NJ.
+
+\leavevmode\hypertarget{ref-Reimers2019}{}%
+Reimers, Nils, and Iryna Gurevych. 2019. ``Sentence-BERT: Sentence
+Embeddings Using Siamese BERT-Networks.'' \emph{arXiv:1908.10084
+{[}Cs{]}}, August. \url{http://arxiv.org/abs/1908.10084}.
+
+\leavevmode\hypertarget{ref-Rehurek2010}{}%
+Řehůřek, Radim, and Petr Sojka. 2010. ``Software Framework for Topic
+Modelling with Large Corpora.'' In \emph{Proceedings of the LREC 2010
+Workshop on New Challenges for NLP Frameworks}, 45--50. Valletta, Malta:
+ELRA.
+
+\leavevmode\hypertarget{ref-Tong2001}{}%
+Tong, Simon, and Daphne Koller. 2001. ``Support Vector Machine Active
+Learning with Applications to Text Classification.'' \emph{Journal of
+Machine Learning Research} 2 (Nov): 45--66.
+
+\leavevmode\hypertarget{ref-vandeSchoot2017}{}%
+\noopsort{schoot}van de Schoot, Rens, Marit Sijbrandij, Sonja D. Winter,
+Sarah Depaoli, and Jeroen K. Vermunt. 2017. ``The GRoLTS-Checklist:
+Guidelines for Reporting on Latent Trajectory Studies.''
+\emph{Structural Equation Modeling: A Multidisciplinary Journal} 24 (3):
+451--67. \url{https://doi.org/10/gdpcw9}.
+
+\leavevmode\hypertarget{ref-Wallace2010}{}%
+Wallace, Byron C., Thomas A. Trikalinos, Joseph Lau, Carla Brodley, and
+Christopher H. Schmid. 2010. ``Semi-Automated Screening of Biomedical
+Citations for Systematic Reviews.'' \emph{BMC Bioinformatics} 11 (1):
+55. \url{https://doi.org/10.1186/1471-2105-11-55}.
+
+\leavevmode\hypertarget{ref-Yu2018a}{}%
+Yu, Zhe, Nicholas A. Kraft, and Tim Menzies. 2018. ``Finding Better
+Active Learners for Faster Literature Reviews.'' \emph{Empirical
+Software Engineering} 23 (6): 3161--86.
+\url{https://doi.org/10.1007/s10664-017-9587-0}.
+
+\leavevmode\hypertarget{ref-Yu2019}{}%
+Yu, Zhe, and Tim Menzies. 2019. ``FAST2: An Intelligent Assistant for
+Finding Relevant Papers.'' \emph{Expert Systems with Applications} 120
+(April): 57--71. \url{https://doi.org/10.1016/j.eswa.2018.11.021}.
+
+\leavevmode\hypertarget{ref-Zhang2004}{}%
+Zhang, Harry. 2004. ``The Optimality of Naive Bayes.'' In
+\emph{Proceedings of the Seventeenth International Florida Artificial
+Intelligence Research Society Conference, FLAIRS 2004}. Vol. 2.
+\end{cslreferences}
 

### 2020-03-30 simulation_study/README.Rmd

@@
 ---
-title: "logbook simulations"
+title: "log"
 output:   
@@
 
-## Hyperparameter optimization
-There are three stages, we start with the first where we are comparing different classifiers.
-
 ```{r include = FALSE}
@@
 library(kableExtra)
-datasets <- c("ace", "nudging","ptsd",  "software", "wilson")
+source("R/functions.R")
 knitr::opts_chunk$set(echo = FALSE)
 ```
+
+```{r eval = FALSE}
+# 
+source("R/00_condition_grid.R")
+source("R/01_hyperparameter_sets.R")
+```
+
+## Hyperparameter optimization
+There are three stages, we start with the first 5 where we are comparing different classifiers.
 
@@
 ```{r}
-hyperparametersets <- readRDS("01_hyperparameter_sets.RDS")
-
-# to-do grid 
-todo <- hyperparametersets
-
-# set emojis for grid 
-check <- function(todo, m, ho, d){
-  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("check") 
-  return(todo)
-}
-
-busy <- function(todo, m, ho, d){
-  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("timer") 
-  return(todo)
-}
-
-huh <- function(todo, m, ho, d){
-  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("question") 
-  return(todo)
-}
-
-not <- function(todo, m, ho, d){
-  todo[todo$model %in% m & todo$hyperopt == ho, d] <- emo::ji("x") 
-  return(todo)
-}
+emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
 

### 2020-03-30 simulation_study/hpoptimization/README.Rmd

---
title: "log hyperparameter optimization"
output: html_notebook
---

Per day, all commands sent to surfsara

After a command is sent, save that todo checklist file!

```{r}
hpsets <- readRDS("../R/01_hyperparameter_sets.RDS")

d <- colnames(hpsets)
condition <- rownames(hpsets)
classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
names(classifier) <- c("B", "R", "S", "L", "N")
```

# one on one optimization

## classifiers 
BCTD on all datasets
```{r}
# BCTD
script <- noquote(sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d %s -r 23", d))
write.table(script, file = "scripts/one/nb_classifier.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
# job names
names(script) <- c("7846991", "7846993", "7846994", "7846997", "7846998", "7846999")
```

```{r}
# check off to do list. 
hpsets["NCTD", , ] <- 9 # impossible model
hpsets["BCTD", , "one"] <- 1 # finish nb one-one-one simulations
```

The other 3 classifiers 
```{r}
cons <- expand.grid(c = classifier[2:4], d = d, stringsAsFactors = FALSE)
# all models
class1 <- sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$c, cons$d)
write.table(class1, file = "scripts/one/three_classifiers.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# job names
names(class1) <- c(7847065,7847066,7847067,7847068,7847069, 7847070, 7847071,7847072, 7847074,7847075, 7847076, 7847077,7847078,7847079,7847080,7847081, 7847082,7847084)

hpsets[condition[2:4], , "one"] <- 1
```

## now with doc2vec feature extraction 
```{r}
cons <- expand.grid(c = classifier[2:5], d = d, stringsAsFactors = FALSE)

# a test run first maybe
# NCDD
noquote("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e doc2vec -q max -d ace -r 23") # 7847109
# todo list
hpsets[condition[6], , ] <- 9 # multinomial nb cannot deal with doc2vec (negative values!!)
```

```{r}
# then all classifier * dataset combinations. 
t <- rep(c("12", "42", "42", "5-00"), length(d))
d2v1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", t, cons$c, cons$d)
# one test of doc2vec 
write.table(d2v1, file = "scripts/one/doc2vec.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2v1) <- c("7854137", "7854187", "7854188", "7854208", 
                 "7854189", "7854190", "7854191", "7854209", 
                 "7854192", "7854193", "7854194", "7854210", 
                 "7854195", "7854196", "7854197", "7854211", 
                 "7854198", "7854199", "7854200", "7854212", 
                 "7854201", "7854202", "7854203", "7854213")

hpsets[condition[7:10], ,"one"] <- 1
```

# n
```{r}
t <- c("12:00:00", "24:00:00", "48:00:00", "24:00:00")
# optimize hyperparams over all datasets
allc <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e tfidf -q max -r 23", t, classifier[1:4])
write.table(allc, file = "scripts/n/fourclassifiers.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)

# later for more than 12 hours. 
names(allc) <- c("7848203", "7848204", "7848205", "7848206")

hpsets[condition[1:4], , "all"] <- 1
```

## doc2vec models 
```{r}
t <- rep(c("42", "42", "42", "5-00"))
cons <- expand.grid(c = classifier[2:5], stringsAsFactors = FALSE)

d2vall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -r 23", t, cons$c)

write.table(d2vall, file = "scripts/n/doc2vec.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(d2vall) <- c("7854227", "7854228", "7854229", "7854230")

hpsets[condition[7:10], ,"all"] <- 1
```

# n-1

### 2020-04-01 simulation_study/hpoptimization/README.Rmd
test ini file

@@
 hpsets[condition[7:10], ,"all"] <- 1
+
 ```
@@
 # n-1
+
+--- 
+# Visual inspection 30-03-2020
+
+## classifiers
+```{bash, eval = FALSE}
+# script to show all lisa.err files to see if processes done yes/no
+.catlisaerr.sh
+```
+- svm 
+  - ace (3x) 3 times the time. 
+  - nudging 7x
+  - ptsd 7x 
+  - software 3x (of 4)
+  - virus 5x
+  - wilson 3x
+    - all 10x
+- rf 
+  - software 2x 
+  - all 3x
+- rest is fine, over 1000 runs and seems not to improve much. 
+```{r}
+hpsets[condition[c(1,4)], , c("one", "all")] <- 2
+hpsets[condition[c(2,3)],  d[c(1:2, 5:6)], "one"] <- 2
+```
+
+Sent in around 13 pm (30.03.2020)
+```{r}
+# svm extra time 
+cons <- expand.grid(c = classifier[3], stringsAsFactors = FALSE, d= d)
+cons$t <- c("36", rep("84", 2), "48", "60", "36")
+extrasvm1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
+names(extrasvm1) <- c("7867379","7867380", "7867382", "7867383", "7867384", "7867387")
+
+cons <- expand.grid(c=classifier[2], stringsAsFactors = FALSE, d=d[3:4])
+
+cons$t <- c("06", "24")
+
+extrarf1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
+names(extrarf1) <- c("7867388", "7867389")
+
+# later check rf - ptsd - one
+hpsets[condition[2], d[3], "one"] <- 2
+
+cons <- data.frame(c = classifier[2:3], t = c("5-00", "5-00"))
+extraall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -r 23", cons$t, cons$c)
+names(extraall) <- c("7867412", "7873506")
+
+# save scripts for reproducibility 
+write.table(c(extrasvm1, extrarf1), file = "scripts/one/extratime_classifier.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+write.table(extraall, file = "scripts/n/extratime_classifier.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+```
+
+## doc2vec 
+```{bash, eval = FALSE}
+# bash script to print all hyperopt results. 
+./show.sh
+```
+
+- nn-2-layer - try again with -r 11.  (for all datasets still doesn't work )
+
+```{r}
+# redo nn-2-layer with doc2vec. 
+#./cart_hyper_run.py hyper-active -t 01:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 11 7867616 test for an hour 
+hpsets[condition[10], , "one"] <- 8 # error
+cons <- expand.grid(c = classifier[5], stringsAsFactors = FALSE, d=d)
+cons$t <- "5-00:00:00"
+nn2dv1 <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e doc2vec -q max -d %s -r 11", cons$t, cons$c, cons$d)
+write.table(nn2dv1, file = "scripts/one/nn2d2v.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(nn2dv1) <- c("7872280", "7872281", "7872282", "7872283", "7872284", "7872285")
+hpsets[condition[10], , "one"] <- 1 # sent in again
+# this can be turnt of afer 52 hours. (thursday morning) 02.04
+
+nn2d2vall <- c("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m nn-2-layer -b double -e doc2vec -q max -r 4")
+write.table(nn2d2vall, file = "scripts/n/nn2d2v.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(nn2d2vall) <- "7873511"
+```
+
+- rf is done 
+  - ace 3x? 
+  - nudging 2x 
+  - ptsd 6x
+  - software 10 x
+  - virus 1.5 x 
+  - wilson 1x
+
+```{r}
+# redo random forest d2v
+t <- rep(c("36", "24", "72", "5-00", "18", "12"))
+x_d2v_rf <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m rf -b double -e doc2vec -q max -d %s -r 23", t, d)
+# one test of doc2vec 
+write.table(x_d2v_rf, file = "scripts/one/x_d3v_rf.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(x_d2v_rf) <- c("7867607", "7867608", "7867609", "7867610", "7867611", "7867612")
+```
+
+# asreview create-config
+
+# export config files 
+(from all files in output :) )
+
+```{r}
+d4 <- c(paste(d[1:5], collapse=","), 
+        paste(d[2:6], collapse=","), 
+        paste(d[c(3:6,1)], collapse = ","), 
+        paste(d[c(4:6, 1:2)], collapse=","),
+        paste(d[c(5:6, 1:3)], collapse = ","),
+        paste(d[c(6, 1:4)], collapse = ","))
+cons <- expand.grid(c = classifier, d = d4, f=c("tfidf", "doc2vec"), stringsAsFactors = FALSE)
+cons <- cons[!(cons$c == "nb" & cons$f == "doc2vec"), ]
+cons$r <- ifelse(cons$c == "nn-2-layer", "11", "23")
+cons$t <- ifelse(cons$c == "nb", "12", "5-00")
+# all models
+n_1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e %s -q max -d %s -r %s", cons$t, cons$c, cons$f, cons$d, cons$r)
+write.table(n_1, file = "scripts/n-1/all_models.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+
+# job names
+names(n_1) <- c("7873344", "7873345", "7873346", "7873347", "7873348",
+                "7873360", "7873361", "7873363", "7873364", "7873365",
+                "7873378", "7873379", "7873381", "7873382", "7873383",
+                "7873392", "7873393", "7873394", "7873396",
+                "7873396",
+                "7873397", "7873398", "7873399", "7873400", "7873401",
+                "7873407", "7873408", "7873409", "7873411", "7873413",
+                "7873425", "7873427", "7873429", "7873431", "7873433",
+                "7873446", "7873448", "7873450", "7873453", 
+                "7873455",
+                "7873460", "7873461", "7873462", "7873463",
+                "7873464",
+                "7873466", "7873467", "7873468", "7873469", "7873470", 
+                "7873471", "7873472", "7873473", "7873474")
+
+hpsets[c(1:5, 6:10),,"four"] <- 1
+```
+
+31.03.2020
+### all 
+all SCDD, LCDD RCDD, resend for 5 days 
+```{r}
+# more time for doc2vec all datasets - svm + logistic 
+d2vall
+cons <- expand.grid(c = classifier[2:4], stringsAsFactors = FALSE)
+d2vall_x <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e doc2vec -q max -r 23", cons$c)
+write.table(d2vall_x, file = "scripts/n/d2v_all_x.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(d2vall_x) <- c("7873497", "7873499","7873500")
+```
+
+try nn2 with tfidf -r 11
+
+checkout nn 2 layer tfidf
+
+### one
+one LCDD, for 2x the time 
+one SCDD for 1x the time 
+```{r}
+cons <- expand.grid(c = classifier[3:4], d = d, stringsAsFactors = FALSE)
+cons$t <- ifelse(cons$c=="logistic", "96", "48")
+d2v1_x <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", cons$t, cons$c, cons$d)
+write.table(d2v1_x, file = "scripts/one/d2vone_x.txt", sep="\t", quote = FALSE, row.names = FALSE)
+
+names(d2v1_x) <- c("7877706", "7877707", "7877708", "7877709", "7877710",
+                   "7877711", "7877712", "7877713", "7877714", "7877715", "7877716", 
+                   "7877717")
+```
+
+```{r}
+hpsets[condition[2], d[4] , "one"] <- 2
+```

### 2020-04-01 simulation_study/hpoptimization/config/configfiles.Rmd
test ini file

---
title: "create_config_files"
author: "Gerbrich Ferdinands"
date: "4/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hpsets <- readRDS("../R/01_hyperparameter_sets.RDS")

```

## R Markdown

```{bash, eval = FALSE}
# get config files from surfsara to hard drive 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
```

Manually update config files to simulation 
Push finished ones to GH repository
Fetch github repo on surfsara

make link in surfsara 
ln -s /home/gerbrich/asreview/manuscript/asreview-thesis/simulation_study/simulation/config simconfig

```{r}
scp -r 
gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/siminput
```

### 2020-04-03 simulation_study/hpoptimization/README.Rmd
config files SCDD

@@
 ```
+
+01.04
+nn-2-layer retry r-1 
+```{r}
+cons <- expand.grid(c = classifier[5], fe = c("tfidf", "doc2vec"), d = d, stringsAsFactors = FALSE)
+
+nn_test <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 2", cons$c, cons$fe, cons$d)
+write.table(nn_test, file = "scripts/one/nn_test.txt", sep="\t", quote = FALSE, row.names = FALSE)
+
+names(nn_test) <- c("7891389", "7891390", "7891391", "7891392", "7891393", "7891394", "7891395", "7891396", "7891402", "7891407", "7891408", "7891411")
+# ./cart_hyper_run_asrnn.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d wilson -r 2 # 7886988, 
+#./cart_hyper_run.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 2 # 7883466
+# ssh tcn560
+# top 
+```
+
+```{r}
+# cancel all logistic 4-1 sets 
+#  7873347, 7873448, 7873460, 7873464, 7873469, 7873473
+hpsets["LCTD", , "four"] <- 2
+```
+
+03.04.2020
+```{r}
+# svm d2v one are done! 
+hpsets["SCDD",, "one"] <- 2
+```

### 2020-04-03 simulation_study/simulation/README.Rmd
config files SCDD

---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

createLines <- function(cond, d, hp){
  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
  files <- data.frame(c = condition, 
                    f = c("nb_max_double_tfidf",
                    "rf_max_double_tfidf",
                    "svm_max_double_tfidf",
                    "logistic_max_double_tfidf",
                    "nn-2-layer_max_double_tfidf",
                    "nb_max_double_doc2vec",
                    "rf_max_double_doc2vec",
                    "svm_max_double_doc2vec",
                    "logistic_max_double_doc2vec",
                    "nn-2-layer_max_double_doc2vec"))

  # create condition grid
  cons <- expand.grid(d = d, hp = hp, c = cond, stringsAsFactors = FALSE)
  cons <- left_join(cons, files)

  # write 
  script <- sprintf(comm, 
        # input data
        cons$d, 
        # config file details
        cons$hp, cons$c, cons$f, cons$d,
        # output file details
        cons$hp, cons$c, cons$d)
return(script)
}
transfer <- function(hp, c){
    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)
    txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"

    sprintf(txt, hp, c, hp, c)
}

```

```{r, include=FALSE}
sims <- readRDS("../R/01_hyperparameter_sets.RDS")
d <- colnames(sims)
condition <- rownames(sims)
classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
names(classifier) <- c("B", "R", "S", "L", "N")
```

# create config files 
#### 01.04.2020
```{bash, eval = FALSE}
# get config files from surfsara to hard drive 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
```

Manually update config files to simulation 
Push finished ones to GH repository
Fetch github repo on surfsara

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 1 # simulation configs are up
```

# Run simulations

## hp = one

#### BCTD
```{r}
bctd <- createLines(condition[1], d=d, hp = "one")
write.table(bctd, file = "scripts/one/bctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(bctd) <- c("7883184", "7883202", "7883207", "7883209", "7883213", "7883214")
```

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lcdt.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c("7883218", "7883219", "7883220", "7883221", "7883223", "7883224",
                     "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")
```

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 2 # simulations are running 
```

# transfer simulation files to harddrive

```{bash, eval = FALSE}
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

./cart_simulate.py simdata/wilson.csv --config_file simconfig/one/LCTD/logistic_max_double_tfidf-wilson.ini --state_file simoutput/one/LCTD/wilson/results.h5 -r 15
```

```{r}
transfer("one", condition[c(1,2,4)])
```

```{r}
# output is on harddrive
sims[condition[1], , "one"] <- 3
```

#### 02.04.2020
get config files 'all' BCTD, LCTD.

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

```{r}
# output is on harddrive
sims[condition[2], , "one"] <- 3
```

#### 03.04.2020
SCDD model

```{r}
# get config files
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
# manually transform
# push to github

sims[condition[8], d, "one"] <- 1 # simulation configs are up
# run simulations

scdd <- createLines(condition[8], d, "one")

sims[condition[8], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[8], , "one"] <- 3 # output is on harddrive
```

---

```{r template, eval = FALSE}
# get config files
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
# manually transform
# push to github 
sims[condition[1], d, "one"] <- 1 # simulation configs are up
# run simulations 
createLines()
sims[condition[1], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[1], , "one"] <- 3 # output is on harddrive
```

### 2020-04-03 simulation_study/plot/saveplot.py

@@ -1,0 +1,7 @@
+with Plot.from_paths(["PATH_1", "PATH_2"]) as plot:
+	inc_plot = plot.new("inclusion")
+	inc_plot.set_grid()
+	inc_plot.set_xlim(0, 30)
+	inc_plot.set_ylim(0, 101)
+	inc_plot.set_legend()
+	inc_plot.save("SOME_FILE.png")

### 2020-04-03 simulation_study/simulation/README.Rmd
add config file LCTD all

@@
 # get config files
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
 # manually transform
 # push to github 
+sims[condition[8], d, "one"] <- 1 # simulation configs are up
 
-sims[condition[8], d, "one"] <- 1 # simulation configs are up
 # run simulations 
+scdd <- createLines(condition[8], d, "one")
+write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(scdd) <- c("7893237", "7893241", "7893243", "7893244", "7893246", "7893247")
+sims[condition[8], d, "one"] <- 2 # simulations are running
 
-scdd <- createLines(condition[8], d, "one")
+# transfer to harddrive 
+transfer("hp", condition[8])
+#sims[condition[8], , "one"] <- 3 # output is on harddrive
+```
 
-sims[condition[8], d, "one"] <- 2 # simulations are running 
-# transfer to harddrive 
-transfer()
-sims[condition[8], , "one"] <- 3 # output is on harddrive
+all - LCTD hyperparameters 
+```{r}
+# manually transform
+# push to github 
+sims[condition[4], , "all"] <- 1 # configs are on github 
 ```
@@
 # get config files
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
 # manually transform

### 2020-04-04 manuscript/drafts/manuscript.Rmd
update datasets in manuscript

@@
    pdf_document:
-  #   citation_package: biblatex
+     citation_package: biblatex
 bibliography: asreview.bib
@@
 
-#pathRdata <- "../../R/data/"
-pathRdata <- "data/"
-
+#pathRdata <- "data/"
+pathRdata <- "../../datasets/data_statistics/"
 ```
@@
 # datasets table
-load(paste0(pathRdata, "datasets_table.Rdata"))
+drops <- readRDS(paste0(pathRdata, "drops.RDS"))
+all <- readRDS(paste0(pathRdata, "all.RDS"))
 
@@
 To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews. 
+A simulation is of one model on one dataset. 
+The simulation is repeated for 15 trials $t$.
+
+The starting point of the active learning model in the simulation is one prior included publication and one prior excluded publication. 
+The training set is randomly sampled from the data. 
+Every simulation study consists of 15 trials, to account for the randomness of prior inclusions and exclusions.
+So every trial the prior inclusions and exclusions are randomly selected. 
+Results are aggregated (?)
 
@@
 From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
-
-A simulation is of one model on one dataset. 
-The simulation is repeated for 10 trials $t$.
-
-Every simulation study consists of 10 trials, to account for the randomness of prior inclusions and exclusions.
-So every trial the prior inclusions and exclusions are randomly selected. 
-Results are aggregated (?)
 

### 2020-04-04 simulation_study/hpoptimization/README.Rmd
add config file LCTD all
update datasets in manuscript

@@
 ---
-title: "log hyperparameter optimization"
-output: html_notebook
+title: "Hyperparameter optimization log"
+output: github_document
 ---
@@
 ```
+
+```{r}
+# all - BCTD gets a few extra
+hpsets["BCTD",, "all"] <- 1 # 7893274 (12 hours)
+# all - LCTD is done
+```
+
+04.04.2020
+```{r}
+# rf all is done 
+hpsets["RCTD",,"all"] <- 2 
+hpsets["BCTD",, "all"] <- 2 
+```

### 2020-04-04 simulation_study/simulation/README.Rmd
update datasets in manuscript

@@
 ---
-title: "README"
+title: "Simulations log"
 output: github_document
@@
 # transfer to harddrive 
-transfer("hp", condition[8])
+transfer("one", condition[8])
 #sims[condition[8], , "one"] <- 3 # output is on harddrive
@@
 sims[condition[4], , "all"] <- 1 # configs are on github
+
+# run simulations 
+lctd_n <- createLines(condition[4], d, "all")
+write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(lctd_n) <- c()
+#sims[condition[4], d, "all"] <- 2 # simulations are running
+
+# transfer to harddrive 
+transfer("n", condition[4])
+#sims[condition[8], , "one"] <- 3 # output is on harddrive
 ```

### 2020-04-04 datasets/data_preprocessing.nb.Rmd
add id to datadd id to datasets

@@
 ---
-title: "R Notebook"
-output:
-  html_document:
-    df_print: paged
+title: "Dataset preprocessing"
+output: github_document
 ---
-This notebook processes all systematic review datasets into datasets suitable testing asreview.
+This notebook processes all systematic review datasets into datasets suitable testing ASReview.
 
@@
   - label_included
-  - keywords? (?)
+  - keywords? (only for hyperparameter optimization, not for simulation).
 
@@
   filter(abstract != "", abstract != "NA") %>%
-  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
+  distinct(abstract, .keep_all = TRUE) %>% # remove entries with duplicate abstracts
+  mutate(id = X)
 
@@
 ptsd_test <- ptsd_test %>%
-  select(authors, title, abstract, keywords, included, inclusion_code) # select relevant columns
+  select(id, authors, title, abstract, keywords, included, inclusion_code) # select relevant columns
 
@@
    filter(abstract != "") %>%
-   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
+   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts
+
+hall_test <- hall_test %>% # add id
+  mutate(id = 1:nrow(hall_test))
 
@@
 # save datafile, to serve as data for descriptive table in manuscript
-save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
+saveRDS(all, file = "data_statistics/all.RDS")
 
@@
   t() %>% 
-  kable("html") %>%
-  kable_styling(full_width = TRUE) %>%
-  #scroll_box(width = "100%", height = "200px") %>%
-  pack_rows("Paper", 2, 5) %>%
-  pack_rows("Raw data", 6, 9) %>%
-  pack_rows("ASReview data", 10, 13) %>%
-  pack_rows("Test data set", 14, 17)  
+  kable("markdown") 
+# %>%
+#   kable_styling(full_width = TRUE) %>%
+#   #scroll_box(width = "100%", height = "200px") %>%
+#   pack_rows("Paper", 2, 5) %>%
+#   pack_rows("Raw data", 6, 9) %>%
+#   pack_rows("ASReview data", 10, 13) %>%
+#   pack_rows("Test data set", 14, 17)  
 ```
@@
 drops %>%
-  kable("html",
+  kable("markdown",
         col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
-        digits = 2) %>%
-  kable_styling(full_width = TRUE)
+        digits = 2) 
+# %>%
+#   kable_styling(full_width = TRUE)
 
@@
 # Write all test dataset files 
-```{r, eval = FALSE}
+```{r, eval = TRUE}
 # ace
-write.csv(ace_test %>%  select(authors, title, abstract, keywords, label_included), "test_datasets/ace.csv")
+write.csv(ace_test %>%  select(pubmedID, authors, title, abstract, keywords, label_included), "test_datasets/ace.csv", row.names = FALSE)
 
 # nudging (no keywords available)
-write.csv(nudging_test %>% select(title, abstract, included), "test_datasets/nudging.csv")
+write.csv(nudging_test %>% select(id, title, abstract, included), "test_datasets/nudging.csv", row.names = FALSE)
 
 # ptsd
-write.csv(ptsd_test %>% select(authors, title, abstract, keywords, included), "test_datasets/ptsd.csv")
+write.csv(ptsd_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/ptsd.csv", row.names = FALSE)
 
 # hall (no keywords available )
-write.csv(hall_test, "test_datasets/software.csv")
+write.csv(hall_test, "test_datasets/software.csv", row.names = FALSE)
 
 # virus 
-write.csv(v_test %>% select(authors, title, abstract, keywords, included), "test_datasets/virus.csv")
+write.csv(v_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/virus.csv", row.names = FALSE)
 
 # wilson
-write.csv(w_test %>% select(authors, title, abstract, keywords, included), "test_datasets/wilson.csv")
+write.csv(w_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/wilson.csv", row.names = FALSE)
 ```
@@
 # write test dataset files for simulation (removing keywords)
-```{r, eval = FALSE}
+```{r, eval = TRUE}
 # ace
-write.csv(ace_test %>%  select(authors, title, abstract, label_included), "sim_datasets/ace.csv")
+write.csv(ace_test %>%  select(pubmedID, title, abstract, label_included), "sim_datasets/ace.csv", row.names = FALSE)
 # nudging (no keywords available)
-write.csv(nudging_test %>% select(title, abstract, included), "sim_datasets/nudging.csv")
+write.csv(nudging_test %>% select(id, title, abstract, included), "sim_datasets/nudging.csv", row.names = FALSE)
 # ptsd
-write.csv(ptsd_test %>% select(authors, title, abstract, included), "sim_datasets/ptsd.csv")
+write.csv(ptsd_test %>% select(id, title, abstract, included), "sim_datasets/ptsd.csv", row.names = FALSE)
 # hall (no keywords available )
-write.csv(hall_test, "sim_datasets/software.csv")
+write.csv(hall_test, "sim_datasets/software.csv", row.names = FALSE)
 # virus 
-write.csv(v_test %>% select(authors, title, abstract, included), "sim_datasets/virus.csv")
+write.csv(v_test %>% select(id, title, abstract, included), "sim_datasets/virus.csv", row.names = FALSE)
 # wilson
-write.csv(w_test %>% select(authors, title, abstract, included), "sim_datasets/wilson.csv")
+write.csv(w_test %>% select(id, title, abstract, included), "sim_datasets/wilson.csv", row.names = FALSE)
 ```

### 2020-04-04 manuscript/drafts/manuscript.Rmd
add id to datadd id to datasets

@@
 ```
-input: a pool of unlabeled abstracts $\mathcal{U}$ 
+input:  
+    a pool of unlabeled abstracts $\mathcal{U}$ 
     oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
@@
   M = train($\mathcal{L}$)
-  query x \isin
+  Query x \isin \mathcal{U} (<x, y=?)
+  oracle <x, y>
 
@@
 
+## Models 
+Five different active learning models were build. 
+Every model $m$ was used to perform an automated systematic review on SR dataset $d$. 
+The models all apply a different classifier $c$ with its own set of (hyper)parameters $h$.
+
+#### Classifiers
+The classifier predicts the class of all papers, given the training dataset/labeled data set $\mathcal{L}$.
+
+Given the labels and some features from all abstracts in the pool, the classifier 
+To predict whether a paper should be an exclusion or an inclusion, different classifiers
+
+Logistic Regression (L) -
+
+Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$.
+Naive Bayes assumes all features are independent given the class value.
+This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
+Especially at ...
+tasks.
+
+Random Forests (R) is where a large number of decision trees are fit on bootstrapped samples of the original data.
+All trees cast a vote on the class, which are aggregated into a class prediciton for each input $\mathbf{X}$ [@Breiman2001].
+
+Support Vecor Machine (S) - finds a multidimensional hyperplane to separate classes.
+[@Tong2001]
+
+Dense Neural Network (N) -
+
+Besides $c$, components of $m$ are fea
+
+To summarize, every model $m$ consists of the following key components: 
+classifier, feature extraction strategy, query strategy, balance strategy.
+
+For example $M_1$ BCTD (naive bayes, certainty sampling, tf-idf, dynamic supersampling)
+STMD
+
+#### Word representation 
+To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
+Examples of such information are titles and abstracts. 
+However, the classifier cannot predict the publication class from titles and abstracts as they are. 
+Their textual content to needs to be mapped to feature vectors. 
+This process of numerically representing textual content is called 'word embeddings'.
+
+A classical example of word embeddings a 'bag of words' representation. 
+For each text in the data set, the number of occurrences of each word is stored. 
+This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
+The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
+Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
+
+The model expedits features of previously labeled publications and 
+Based on features of the previously labeled inclusions and exclusions, the model
+
+The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
+
+(T) (D)
+
+#### The next abstract to be queried  
+The model has various ways of deciding which instance should be queried next. 
+(C) but other methods, here only C
+
+#### Rebalancing the training set
+To account for class imbalance in the data, the model can apply several strategies to rebalance the training set.
+
+A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.
+
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
+
+Dynamic Supersampling (D)
+
+## Simulations
+A simulation is of one model on one dataset. 
+The simulation is repeated for 15 trials $t$.
+
+The starting point of the active learning model in the simulation is one prior included publication and one prior excluded publication. 
+The training set is randomly sampled from the data. 
+Every simulation study consists of 15 trials, to account for the randomness of prior inclusions and exclusions.
+So every trial the prior inclusions and exclusions are randomly selected. 
+Results are aggregated (?)
+
+#### Controlled Variables
+Starting point
+The initial training set consists of 1 inclusion and 1 exclusion, randomly sampled from the dataset. 
+Demonstrate 'worst case scenario' where reviewer has minimal prior knowledge on publications in the data. 
+The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
+
+Retraining
+We can choose to retrain the model after labeling $n$ instances. 
+- n_instances=1 (number of papers each query)
+
 ## Datasets
+Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
+The data from the original source were preprocessed into a test dataset, containing all publications obtained in the systematic search, with labels indicating the publications included in the systematic review.
 
-The algorithm will be tested on five systematic reviews from various research areas. 
+The test datasets contain title information on all publications obtained in the search strategy. 
+The instances in the data consist of a title, an abstract and were labeled to indicate which publications were included in the systematic review. 
+Instances with missing abstracts were removed. 
+Duplicate instances were removed. 
+Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
+
 test datasets serve as systematic search results, then perform active learning to detect inclusions.
@@
 A fraction of these papers where deemed relevant for the SR, with inclusion rates around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).
-
-The raw datafiles published with the SRs were preprocessed into a test dataset.
-The test datasets contain title information on all citations obtained in the search strategy. 
-The instances in the data consist of a title, an abstract and were labeled to indicate which citations were included in the systematic review. 
-Instances with missing abstracts were removed. 
-Duplicate instances were removed. 
-Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
 
@@
 ```
-
-## Models 
-Five different active learning models were build. 
-Every model $m$ was used to perform an automated systematic review on SR dataset $d$. 
-The models all apply a different classifier $c$ with its own set of (hyper)parameters $h$.
-
-#### Classifiers
-The classifier predicts the class of all papers, given the training dataset/labeled data set $\mathcal{L}$.
-
-Given the labels and some features from all abstracts in the pool, the classifier 
-To predict whether a paper should be an exclusion or an inclusion, different classifiers
-
-Logistic Regression (L) -
-
-Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$.
-Naive Bayes assumes all features are independent given the class value.
-This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
-Especially at ...
-tasks.
-
-Random Forests (R) is where a large number of decision trees are fit on bootstrapped samples of the original data.
-All trees cast a vote on the class, which are aggregated into a class prediciton for each input $\mathbf{X}$ [@Breiman2001].
-
-Support Vecor Machine (S) - finds a multidimensional hyperplane to separate classes.
-[@Tong2001]
-
-Dense Neural Network (N) -
-
-Besides $c$, components of $m$ are fea
-
-To summarize, every model $m$ consists of the following key components: 
-classifier, feature extraction strategy, query strategy, balance strategy.
-
-For example $M_1$ BTMD (naive bayes, tfidf, certainty sampling, double balance)
-STMD
-
-#### Word representation 
-To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
-Examples of such information are titles and abstracts. 
-However, the classifier cannot predict the publication class from titles and abstracts as they are. 
-Their textual content to needs to be mapped to feature vectors. 
-This process of numerically representing textual content is called 'word embeddings'.
-
-A classical example of word embeddings a 'bag of words' representation. 
-For each text in the data set, the number of occurrences of each word is stored. 
-This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
-The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
-Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
-
-The model expedits features of previously labeled publications and 
-Based on features of the previously labeled inclusions and exclusions, the model
-
-The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
-
-(T) (D)
-
-#### The next abstract to be queried  
-The model has various ways of deciding which instance should be queried next.
-
-#### Rebalancing the training set
-To account for class imbalance in the data, the model can apply several strategies to rebalance the training set.
-
-A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.
-
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-
-#### Starting point
-The initial training set consists of 5 inclusions and 5 exclusions, randomly sampled from the dataset. 
-We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
-The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
-
-```
-c = naivebayes
-f = tfidf
-q = max
-n_prior_included = 5
-n_prior_excluded = 5
-```
-
-#### Retraining
-We can choose to retrain the model after labeling $n$ instances. 
-- n_instances=10 (number of papers each query)
-
-## Simulations
-To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews. 
-A simulation is of one model on one dataset. 
-The simulation is repeated for 15 trials $t$.
-
-The starting point of the active learning model in the simulation is one prior included publication and one prior excluded publication. 
-The training set is randomly sampled from the data. 
-Every simulation study consists of 15 trials, to account for the randomness of prior inclusions and exclusions.
-So every trial the prior inclusions and exclusions are randomly selected. 
-Results are aggregated (?)
 

### 2020-04-06 datasets/data_preprocessing.nb.Rmd
update hyperopt, update meeting notes

@@
 n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
-
+n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
+n_rr <- read.csv2("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/WMGPGZ/HY6N2S",
+                  sep = ",")
+n_rr <- fread("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/WMGPGZ/HY6N2S",
+                  sep = ",", encoding = "UTF-8")
 # missing statistics

### 2020-04-06 manuscript/drafts/manuscript.Rmd
update hyperopt, update meeting notes

@@
 output:
+  word_document: default
   pdf_document:
@@
 
+The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
+
 #### Assumptions 
@@
 All datasets accompanying the systematic reviews are openly published. 
+We built several machine learning models to perform aautomated systematic reviews, 
+who are then applied on existing systematic reviews.
 
 ## Models 
-Five different active learning models were build. 
-Every model $m$ was used to perform an automated systematic review on SR dataset $d$. 
-The models all apply a different classifier $c$ with its own set of (hyper)parameters $h$.
+To perform automated systematic reviews, x machine learning models ($M$) were built. 
+The machine learning models consists of four main components.
 
 #### Classifiers
-The classifier predicts the class of all papers, given the training dataset/labeled data set $\mathcal{L}$.
+Every model applies a classifier $c$ to predict the relevance of publications in the data. 
+The classfiier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
+predicts the class of an instance given input features $\mathbf{X}$
 
-Given the labels and some features from all abstracts in the pool, the classifier 
-To predict whether a paper should be an exclusion or an inclusion, different classifiers
-
-Logistic Regression (L) -
-
-Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$.
-Naive Bayes assumes all features are independent given the class value.
+Logistic Regression (L) - L2-regularized logistic regression. 
+Logistic models the posterior directly, naive bayes has higher bias but lower variance, 
+logistic might perform better when trainign set increases. [@Ng2002]
+Naive Bayes (B) - Naive Bayes assumes all features are independent given the class value.
 This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
@@
 Besides $c$, components of $m$ are fea
-
-To summarize, every model $m$ consists of the following key components: 
-classifier, feature extraction strategy, query strategy, balance strategy.
-
-For example $M_1$ BCTD (naive bayes, certainty sampling, tf-idf, dynamic supersampling)
-STMD
 
@@
 
-Dynamic Supersampling (D)
+Dynamic Supersampling (D) - Dynamic supersampling is similar to undersampling in the sense that it decreases the imbalance of de training data.
+In the case of dynamic supersampling, the number of exclusions is decreased, whereas the number of inclusions are increased (by copy) such that the total number of samples remains the same.
+The ratio between inclusions and exclusions is not fixed, but dynamically updated and depends on the number of training samples, the total number of papers and the ratio between inclusions and exclusions.
+(by Raoul)
 
-## Simulations
-A simulation is of one model on one dataset. 
-The simulation is repeated for 15 trials $t$.
-
-The starting point of the active learning model in the simulation is one prior included publication and one prior excluded publication. 
-The training set is randomly sampled from the data. 
-Every simulation study consists of 15 trials, to account for the randomness of prior inclusions and exclusions.
-So every trial the prior inclusions and exclusions are randomly selected. 
-Results are aggregated (?)
-
-#### Controlled Variables
-Starting point
-The initial training set consists of 1 inclusion and 1 exclusion, randomly sampled from the dataset. 
-Demonstrate 'worst case scenario' where reviewer has minimal prior knowledge on publications in the data. 
-The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
-
-Retraining
-We can choose to retrain the model after labeling $n$ instances. 
-- n_instances=1 (number of papers each query)
+To summarize, every model $m$ consists of four components. 
+In the current study, the classifier and the feature extraction strategy are varied, whereas the query and balance strategy remain fixed. 
+In the current study only a fraction of all possible configurations are tested for the sake of brevity. 
+There are many more options available and open to exploration.
 
@@
 Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
-The data from the original source were preprocessed into a test dataset, containing all publications obtained in the systematic search, with labels indicating the publications included in the systematic review.
+Data from the original source were preprocessed into a test dataset, containing all publications obtained in the systematic search.
+with labels indicating the publications included in the systematic review.
 
@@
 
+## Simulations
+To demonstrate the models, simulations are performed of the models on six original systematic reviews.  
+With the labeled datasets, the systematic review can be reproduced but with now using a machine learning model to optimize the reviewing process.
+
+The initial training set of the active learning model in the simulation is one prior included publication and one prior excluded publication, randomly sampled from the data. 
+This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data.
+
+For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
+The oracle is not the reviewer but the labels in the data. 
+The model retrains every time after a label is provided by the oracle. 
+The simulation ends when all publications in the dataset have been queried.
+
+To account for variance, every simulation is repeated for 15 trials $t$.
+
 ### Optimizing hyperparameters
+with its own set of (hyper)parameters $h$. 
 For every model*data combination, 3 sets of hyperparameters are generated to ... 
@@
 ### Statistical analysis 
+Results are aggregated over 15 runs of every simulation.
+
 #### measures
@@
 Every model has its own set of hyperparameters:
+Model hyperparameters were optimized for every dataset. 
+Optimization was done through … (what kind of statistic is optimized on?) 
+by the asreview-hyperopt extension. 
+Optimization was visually inspected.
 
@@
 # Results
+
+```{r}
+simulations <- readRDS("../../simulation_study/R/01_hyperparameter_sets.RDS")[,,1]
+
+kable(simulations)
+```
 

### 2020-04-06 meetings/11_notes_7apr.Rmd
update hyperopt, update meeting notes

---
title: "11_notes_7apr"
output: github_document
---

# Notes - core team meeting - core team meeting

Questions:

How to make simulations faster?

- plot making in lc

- logistic regression 
  - [use saga as solver instead of liblinear?](https://stackoverflow.com/questions/38640109/logistic-regression-python-solvers-defintions/52388406#52388406)
  - l2 regularization --> why? why nog l1? 
  - [](https://towardsdatascience.com/dont-sweat-the-solver-stuff-aea7cddc3451)

# recap/decisions last week

# Meeting

# To do

### 2020-04-09 manuscript/drafts/manuscript.Rmd
add hyperparaemter optimization

@@
 All simulations were run using through cartesius EINF-156 
-
-\newpage
-# Methods
 Goal: evaluate performance of different models of the ASReview tool. 
@@
 All datasets accompanying the systematic reviews are openly published. 
-We built several machine learning models to perform aautomated systematic reviews, 
+We built several machine learning models to perform automated systematic reviews, 
 who are then applied on existing systematic reviews.
 
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
+The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
+
+a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
+Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
+
+\newpage
+# Methods
+Performance of several machine learning models was demonstrated on six systematic review datasets.
+
 ## Models 
-To perform automated systematic reviews, x machine learning models ($M$) were built. 
-The machine learning models consists of four main components.
+_x_ machine learning models ($M$) were built. 
+The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.
 
@@
 
-Logistic Regression (L) - L2-regularized logistic regression. 
+Logistic Regression (LR) - L2-regularized logistic regression. 
 Logistic models the posterior directly, naive bayes has higher bias but lower variance, 
 logistic might perform better when trainign set increases. [@Ng2002]
-Naive Bayes (B) - Naive Bayes assumes all features are independent given the class value.
+Naive Bayes (NB) - Naive Bayes assumes all features are independent given the class value.
 This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
@@
 
-Random Forests (R) is where a large number of decision trees are fit on bootstrapped samples of the original data.
-All trees cast a vote on the class, which are aggregated into a class prediciton for each input $\mathbf{X}$ [@Breiman2001].
+Random Forests (RF) is where a large number of decision trees are fit on bootstrapped samples of the original data.
+All trees cast a vote on the class, which are aggregated into a class prediction for each input $\mathbf{X}$ [@Breiman2001].
 
-Support Vecor Machine (S) - finds a multidimensional hyperplane to separate classes.
+Support Vecor Machine (SVM) - finds a multidimensional hyperplane to separate classes.
 [@Tong2001]
-
-Dense Neural Network (N) -
-
-Besides $c$, components of $m$ are fea
 
@@
 
-(T) (D)
+(TF-IDF) (Doc2Vec)
 
-#### The next abstract to be queried  
-The model has various ways of deciding which instance should be queried next. 
-(C) but other methods, here only C
+#### Fixed components  
+All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.
 
-#### Rebalancing the training set
-To account for class imbalance in the data, the model can apply several strategies to rebalance the training set.
-
-A reweighting strategy is applied where inclusions (the minority class) are weighted more heavily than the exclusions.
-
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-
-Dynamic Supersampling (D) - Dynamic supersampling is similar to undersampling in the sense that it decreases the imbalance of de training data.
-In the case of dynamic supersampling, the number of exclusions is decreased, whereas the number of inclusions are increased (by copy) such that the total number of samples remains the same.
-The ratio between inclusions and exclusions is not fixed, but dynamically updated and depends on the number of training samples, the total number of papers and the ratio between inclusions and exclusions.
-(by Raoul)
-
-To summarize, every model $m$ consists of four components. 
-In the current study, the classifier and the feature extraction strategy are varied, whereas the query and balance strategy remain fixed. 
-In the current study only a fraction of all possible configurations are tested for the sake of brevity. 
-There are many more options available and open to exploration.
+To decrease the class imbalance in the training data, the model rebalances the training set by Dynamic Supersampling (DS).
+DS decreases the number of irrelevant papers in the training data, whereas the number of relevant papers are increased (by copy) such that the total number of samples remains the same.
+The ratio between relevant and irrelevant papers is not fixed, but dynamically updated and depends on the number of training samples, the total number of publications and the ratio between relevant and irrelevant publications.
 
@@
 Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
-Data from the original source were preprocessed into a test dataset, containing all publications obtained in the systematic search.
-with labels indicating the publications included in the systematic review.
+Data were preprocessed from the original source into a test dataset, containing all publications obtained in the systematic search.
+The test datasets are labelled indicating the relevant and irrelevant publications.
+Using these labels, a computer simulation of an automated systematic review can be performed on the systematic review data.
 
 The test datasets contain title information on all publications obtained in the search strategy. 
-The instances in the data consist of a title, an abstract and were labeled to indicate which publications were included in the systematic review. 
-Instances with missing abstracts were removed. 
-Duplicate instances were removed. 
-Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
-
-test datasets serve as systematic search results, then perform active learning to detect inclusions.
+The instances in the data consist of a title and an abstract and were labeled to indicate which publications were included in the systematic review.
+Instances with missing abstracts and duplicate instances were removed from the data.
+The data preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
 
@@
 The _ace_ dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
-
-a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
 
@@
 
+### Optimizing hyperparameters
+Every model component contains hyperparameters, leading to a unique set of hyperparameters for each model. To maximize model performance, we need to find optimal values for the hyperparameters. 
+For every model the optimal hyperparameter values are determined by optimizing on the data $d$.
+The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space.
+A description of all hyperparameters and their sample space can be found in the appendix.
+
+Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g.
+the area above the curve in the inclusion plot).
+
+The optimization data $d$ consists of (a subset from) the six systematic review datasets $D$ mentioned above. 
+Three different approaches in composing $d$ are explored:
+
+- __one__, where hyperparameters are optimized on only one of the six datasets, $d \in D$. Such hyperparameters are expected to lead to maximum performance in the same dataset $d$.
+- __n__, where hyperparameters are optimized on all six data sets, $d = D$. This optimization approach intends to serve in producing the most optimal hyperparameters overall. 
+- __n-1__, where hyperparameters are optimized on all six datasets but one, $d \subset D$.
+Serving as a sensitivity analysis for the former condition, e.g.
+how sensitive are the hyperparamters.
+also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before.
+where d are all datasets but the one where we want to simulate later on. 
+This results in $6+6+1=13$ sets of hyperparameters for every model.
+
+Results were visually inspected to check if an optimum (minimal loss) has been reached. 
+More trials were run if the loss still seemed to go down at a quick pace.
+
+The hyperparameter values that were found to lead to a minimum loss value were visually inspected.
+
+### Optimization results
+For every model, 13 sets of hyperparameters were optimized.
+
+*to include: plotting the loss reduction over trials*
+
+Optimal values of the hyperparameters were visually inspected.
+
+As an example, the hyperparameters of the RF_TF-IDF model are presented in Figure 1. 
+A panel displays the optimal values for a certain hyperparameter, where the blue colored dots represent the __one__ condition, the green dots the __n-1__ condition and the orange dot represents the optimal hyperparameter value when optmizing over all datasets (__n__).
+The x-axis represents the possible parameter space where the vertical grey lines mark the boundaries of the hyperparameter space (if possible).
+Note that the feature parameters ngram_max, split_ta, use_keywords and model parameters max_features and n_estimators are categorical.
+
+Overall, the optimal values are distributed over the parameter space.
+Outlying values all belong to the __one__ condition where optimization was dependent on one dataset only.
+Fore example, the class_weight parameter has an outlying value of 11.3 that belongs to the nudging dataset.
+(Why this is the case I can only speculate, but it is worth mentioning that this dataset has a relatively high inclusion rate  of 5.41%, compared to the other datasets).
+
+```{r}
+include_graphics(
+  "figs/rf_tfidf.eps",
+)
+```
+
+## Appendix x - Hyperparameters and their sample space
+
+Classifier hyperparameters
+
+    class_weight: normal(0,1) constrained to be > 0
+    class weight of the inclusions.
+
+  Logistic Regression
+
+    c: float. normal(0,1), constrained to be > 0
+
+  Support Vector Machine
+
+    gamma: ["auto", "scale"],
+    Gamma parameter of the SVM model.
+
+    C: 
+    C parameter of the SVM model.
+
+    kernel:
+    SVM kernel type.["linear", "rbf", "poly", "sigmoid"]
+
+  Naive Bayes
+
+    "model_param.alpha", # exp(normal(0,1))
+
+  Random Forest
+
+    max_features: int (between 6 and 10)
+        Number of features in the model.
+
+    n_estimators: int between 10 and 100 
+        Number of estimators.
+
+    model_param.n_estimators" #quniform(10,100,1)
+
+Balance strategy hyperparameters:
+    Dynamic supersampling:
+
+    a: float
+        Governs the weight of the 1's. Higher values mean linearly more 1's
+        in your training sample.
+    alpha: float
+        Governs the scaling the weight of the 1's, as a function of the
+        ratio of ones to zeros. A positive value means that the lower the
+        ratio of zeros to ones, the higher the weight of the ones.
+    b: float
+        Governs how strongly we want to sample depending on the total
+        number of samples. A value of 1 means no dependence on the total
+        number of samples, while lower values mean increasingly stronger
+        dependence on the number of samples.
+
+Feature extraction strategy hyperparameters
+
+    split_ta: 0 or 1
+       whether titles and abstracts are split
+
+    use_keywords: 0 or 1
+        whether keywords should be used
+
+  TF-IDF
+
+    ngram_max: 1, 2 or 3
+        Can use up to ngrams up to ngram_max. For example in the case of 
+        ngram_max=2, monograms and bigrams could be used.
+
+  Doc2Vec
+
+    vector_size: int (between 32 and 127)
+        Output size of the vector.
+
+    epochs: int (between 20 and 50)
+        Number of epochs to train the doc2vec model.
+
+    min_count: int (between 1 and 3)
+        Minimum number of occurences for a word in the corpus for it to be 
+        included in the model.
+
+    window: int (between 5 and 9)
+        Maximum distance over which word vectors influence each other.
+
+    dm_concat: int 0 or 1
+        Whether to concatenate word vectors or not.
+
+    dm: int 
+        Model to use.
+        0: Use distribute bag of words (DBOW).
+        1: Use distributed memory (DM).
+        2: Use both of the above with half the vector size and concatenate them.
+
+    dbow_words: int 0 or 1
+        Whether to train the word vectors using the skipgram method.
+
 ## Simulations
@@
 This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data. 
-
 For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
@@
 To account for variance, every simulation is repeated for 15 trials $t$.
-
-### Optimizing hyperparameters
-with its own set of (hyper)parameters $h$. 
-For every model*data combination, 3 sets of hyperparameters are generated to ... 
-parallel
-Every model has its own hyperparameters. 
-For every model, the hyperparameters are optimized three times, arriving at three versions of the model:
-
-We now have 75 combinations. 
-for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
-From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
 
@@
 ASReview takes the following parameters/arguments: 
+ We now have 75 combinations. 
+for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
+From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
 
@@
 ```
-
-### Hyperparameters
-Every model has its own set of hyperparameters:
-Model hyperparameters were optimized for every dataset. 
-Optimization was done through … (what kind of statistic is optimized on?) 
-by the asreview-hyperopt extension. 
-Optimization was visually inspected.
-
-### Optimization
-The hyperparameters are optimized on the 5 datasets in three different ways:
-
-- 1 on 1: maximum performance
-
-$$ d = D $$
-- 4 on 1: cross-validation 
-$$ d \notin D$$
-
-$$ D = {1, 2, 3, 4}$$
-
-- 5 on 1: more data = more better?
-
-$$ d \in D $$
-
-This results $(5+5+1)*5$ sets of hyperparameters.
 
@@
 
+In the current study, the classifier and the feature extraction strategy are varied, whereas the query and balance strategy remain fixed. 
+In the current study only a fraction of all possible configurations are tested for the sake of brevity. 
+There are many more options available and open to exploration.
+
 # References

### 2020-04-09 results/README.Rmd
add hyperparaemter optimization

---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
```

Script for reading simulation files
```{python}

```

Script for reading results 
```{r}
data <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
statspath <- paste0("statistics/one/RCTD/", "testoutput_RCTD_one_", data, ".json")

ace <- fromJSON(file = statspath[1])

```

### 2020-04-09 simulation_study/hpoptimization/README.Rmd
add hyperparaemter optimization

@@
 
-Per day, all commands sent to surfsara
+```{r setup, echo = FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+library(knitr)
+```
 
-After a command is sent, save that todo checklist file!
-
-```{r}
+```{r, echo = FALSE}
 hpsets <- readRDS("../R/01_hyperparameter_sets.RDS")
-
 d <- colnames(hpsets)
@@
 ```
+
+```{r, echo = FALSE}
+log <- readRDS("log.RDS")
+kable(log[,,1], format = "markdown")
+
+kable(log[,,2], format = "markdown")
+
+kable(log[,,3], format = "markdown")
+```
+
+### hyperparameter optimization results
+
+---
 
@@
 
-## now with doc2vec feature extraction 
+now with doc2vec feature extraction 
 ```{r}
@@
 # top
+
+# send again on fat nodes on 04.04
+nn_test2 <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 31", cons$c, cons$fe, cons$d)
+write.table(nn_test2, file = "scripts/one/nn_test2.txt", sep="\t", quote = FALSE, row.names = FALSE)
+
+names(nn_test2) <- c("7904508", "7904509", "7904510", "7904511", "7904512", "7904513", "7904514", "7904515", "7904516",
+                    "7904518", "7904519", "7904520")
 ```
@@
 ```
+
+05.05.2020
+```{r}
+# all 
+# LCDD 24 more hours
+# ./cart_hyper_run.py hyper-active -t 24:00:00 -m logistic -b double -e doc2vec -q max -r 23 
+# 7904435
+```
+
+send in 'one' nn-2-layer models again (see above)
+send in 'all' for nn-2-layer models.
+```{r}
+cons <- expand.grid(c = classifier[5], fe = c("tfidf", "doc2vec"), stringsAsFactors = FALSE)
+nn_test_all <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -r 31", cons$c, cons$fe)
+write.table(nn_test_all, file = "scripts/n/nn_test_all.txt", sep="\t", quote = FALSE, row.names = FALSE)
+names(nn_test_all) <- c("7904535", "7904536")
+
+hpsets[condition[c(5,10)], , "all"] <- 1
+```
+
+06.05.2020
+```{r}
+# SCTD optimization
+hpsets[condition[3], c("ptsd", "software"), "one"] <- 2
+hpsets[condition[3], , "all" ] <- 2
+hpsets[condition[3], , "four"] <- 2
+```
+
+```{r}
+# RCDD 
+hpsets[condition[7], "wilson","one"] <- 2
+
+# other sent for a bit more 
+x_d2v_rf_3 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m rf -b double -e doc2vec -q max -d %s -r 23", rep("24",5), d[1:5])
+
+write.table(x_d2v_rf_3, file = "scripts/one/d2v_rf_3.txt", sep="\t", quote = FALSE, row.names = FALSE)
+
+names(x_d2v_rf_3) <- c("7911083", "7911084", "7911085", "7911086", "7911087")
+```
+
+```{r}
+#SCDD
+hpsets[condition[8],,] 
+# all again: 7911104
+# n_1 again 
+cons <- expand.grid(c = "svm", d = d4, f=c("doc2vec"), stringsAsFactors = FALSE)
+
+# all models
+n_1_svmdx <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 23", cons$c, cons$f, cons$d)
+write.table(n_1_svmdx, file = "scripts/n-1/n_1_xsvmd2v.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(n_1_svmdx) <- c("7911112", "7911113", "7911114", "7911115", "7911116", "7911117")
+```
+
+```{r}
+#LCDD
+hpsets[condition[9], , c("one", "all")] <- 2
+
+# n-1 send in again
+cons <- expand.grid(c = "logistic", d = d4, f=c("doc2vec"), stringsAsFactors = FALSE)
+
+n_1x_ld <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 23", cons$c, cons$f, cons$d)
+write.table(n_1x_ld, file = "scripts/n-1/n_1x_ld.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(n_1x_ld) <- c("7911092", "7911093", "7911094", "7911095", "7911096", "7911097")
+```
+
+```{r}
+# n-2
+#RCTD
+hpsets[condition[2], , "four"] <- 2
+
+# BCTD 
+n_1_nbx <- sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d %s -r 23", d4)
+write.table(n_1_nbx, file = "scripts/n-1/n_1_nbx.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(n_1_nbx) <- c("7911126", "7911127", "7911128", "7911129", "7911130", "7911131")
+
+# all doc2vec models 
+# cons <- expand.grid(c = classifier[2:4], d = d4, stringsAsFactors = FALSE)
+# n_1_d2vx <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", cons$c, cons$d)
+# write.table(n_1_d2vx, file = "scripts/n-1/d2vx.txt", sep = "\t", quote = FALSE,
+#             row.names = FALSE)
+# names(n_1_d2vx)
+```
+
+```{r}
+saveRDS(hpsets, file = "log.RDS")
+```

### 2020-04-09 simulation_study/hpoptimization/config/README.Rmd
add hyperparaemter optimization

---
title: "Results hyperparameter optimization"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(ggplot2)
library(knitr)

php <- function(data){
  data %>%
    ggplot(aes(x = value, y = "", color = group)) +
    geom_jitter(height = 0.2) +
    facet_wrap(vars(param), nrow = 8, scales = "free_x") +
    geom_vline(aes(xintercept = lb), color = "grey") +
    geom_vline(aes(xintercept = ub), color = "grey") 
}

```

```{r, figure.heigth = 12}
hpsets <- readRDS("hpresults.RDS")
```

```{r}
php(hpsets$lr_tfidf) + 
  labs(title = "Hyperparameters Logistic Regression + TF-IDF")
```

```{r, eval = FALSE}
php(hpsets$lr_doc2vec) + 
  labs(title = "Hyperparameters Logistic Regression + Doc2Vec")
```

```{r}
php(hpsets$rf_tfidf) + 
  labs(title = "Hyperparameters Random Forest + TF-IDF")
```

statistics for random forest + tf-idf
```{r}

hpsets$rf_tfidf %>%
   group_by(param, group) %>%
    summarise(variance = var(value), 
              sd = sd(value),
              min = min(value), 
              mean = mean(value),
              median = median(value),
              max = max(value)) %>%
  kable("markdown")

```

```{r}
php(hpsets$rf_d2v) + 
  labs(title = "Hyperparameters Random Forest + Doc2Vec")
```

### 2020-04-09 simulation_study/hpoptimization/config/load_results.R

@@ -1,0 +1,143 @@
+# script to load results from ini folder. 
+library(ini)
+library(tidyverse)
+  
+files <- list.files("simulation_study/hpoptimization/config/config")
+
+gethps <- function(files){
+  # Function extracting all hyperparametersets for a certain model in files. 
+  for(f in files){
+    ini <- read.ini(paste0("simulation_study/hpoptimization/config/config/", f))
+    
+    # first file creates a template 
+    if (f == files[1]){
+      res <- unlist(ini) 
+      # add other files to the list 
+    } else {
+      res <- do.call(Map, list(c, res, unlist(ini)))
+    }
+  }
+  # create a dataframe
+  res <- as.data.frame(res)
+  res <- res %>% select(!starts_with("global_settings"))
+  rownames(res) <- substring(files, regexpr("-", files) + 1)
+  res <- res %>% rownames_to_column("datasets")
+  return(res)
+}
+# different models 
+
+sctd <- files[str_detect(files, "svm") & str_detect(files, "tfidf")] %>%
+  gethps()
+
+scdd <- files[str_detect(files, "svm") & str_detect(files, "doc2vec")] %>%
+  gethps() 
+
+bctd <- files[str_detect(files, "nb") & str_detect(files, "tfidf")] %>%
+  gethps() 
+bctd <- bctd %>% mutate_at(vars(-datasets), function(x) as.numeric(as.character(x)))
+
+
+lctd <- files[str_detect(files, "logistic") & str_detect(files, "tfidf")] %>%
+  gethps() 
+#lctd <- lctd %>% rownames_to_column("datasets")
+lctd <- lctd %>% mutate_at(vars(-datasets), function(x) as.numeric(as.character(x)))
+
+lcdd <- files[str_detect(files, "logistic") & str_detect(files, "doc2vec")] %>%
+  gethps() 
+lcdd <- lcdd %>% mutate_at(vars(-datasets), function(x) as.numeric(as.character(x)))
+
+
+rctd <- files[str_detect(files, "rf") & str_detect(files, "tfidf")] %>%
+  gethps() 
+rctd <- rctd %>% mutate_at(vars(-datasets), function(x) as.numeric(as.character(x)))
+
+rcdd <- files[str_detect(files, "rf") & str_detect(files, "doc2vec")] %>%
+  gethps() 
[…]

### 2020-04-09 simulation_study/hpoptimization/config/README.Rmd
update plots hyperopt

@@
 
-```{r, eval = FALSE}
-php(hpsets$lr_doc2vec) + 
+```{r, eval}
+php(hpsets$lr_d2v) + 
   labs(title = "Hyperparameters Logistic Regression + Doc2Vec")
@@
 
+```{r}
+php(hpsets$rf_d2v) + 
+  labs(title = "Hyperparameters Random Forest + Doc2Vec")
+```
+
 statistics for random forest + tf-idf
 ```{r}
-
 hpsets$rf_tfidf %>%
@@
   kable("markdown")
-
 ```
-
-```{r}
-php(hpsets$rf_d2v) + 
-  labs(title = "Hyperparameters Random Forest + Doc2Vec")
-```

### 2020-04-09 simulation_study/hpoptimization/config/load_results.R

@@ -117,7 +117,7 @@ lctd <- prepData(lctd)
 lcdd <- prepData(lcdd)
 
 # bctd
-#bctd <- prepData(bctd)
+bctd <- prepData(bctd)
 
 # rctd
 rctd <- prepData(rctd)
@@ -126,10 +126,12 @@ rctd <- prepData(rctd)
 rcdd <- prepData(rcdd)
 
 # sctd
-
+sctd <- prepData(sctd)
 # scdd
-
+scdd <- prepData(scdd)
 # inspect 
+
+#
 
 
 # put al results in a list 

### 2020-04-10 simulation_study/simulation/README.Rmd
update hyperopt, update meeting notes
Fix bug c parameter logistic config files

--- 2020-04-03 simulation_study/simulation/README.Rmd
@@
 
-# transfer to harddrive 
-transfer("hp", condition[8])
-#sims[condition[8], , "one"] <- 3 # output is on harddrive
 ```
 
-all - LCTD hyperparameters 
+```{r}
+sctd <- createLines(condition[3], d, "one")
+write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(sctd) <- c("7945897", "7945899", "7945902", "7945903", "7945910", "7945912")
+sims[condition[3], d, "one"] <- 2 # simulations are running
+
+rcdd <- createLines(condition[7], d, "one")
+write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(rctd) <- c("")
+sims[condition[7], d, "one"] <- 2 # simulations are running
+
+lcdd <- createLines(condition[8], d, "one")
+
+```
+
+10.04.2020
+
+```{r}
+# transfer to harddrive 
+transfer("one", condition[8])
+#sims[condition[8], , "one"] <- 3 # output is on harddrive
+transfer("one", condition[4])
+
+# simulations both failed? 
+```
+
+### all 
+RCTD all
+BCTD all 
+LCTD all
+
 ```{r}
@@
 sims[condition[4], , "all"] <- 1 # configs are on github
+
+```
+
+```{r}
+# run simulations 
+lctd_n <- createLines(condition[4], d, "all")
+write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(lctd_n) <- c()
+#sims[condition[4], d, "all"] <- 2 # simulations are running
+
+# transfer to harddrive 
+transfer("n", condition[4])
+#sims[condition[8], , "one"] <- 3 # output is on harddrive
 ```

### 2020-04-10 simulation_study/simulation/README.Rmd
Fix bug C-parameter SCTD config files

@@
 rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
-write.table(rctd_lctd, file = "scripts/one/rctd_lcdt.txt", sep = "\t", quote = FALSE,
+write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
             row.names = FALSE)
 #one_rctd_virus etc 
-names(rctd_lctd) <- c("7883218", "7883219", "7883220", "7883221", "7883223", "7883224",
+names(rctd_lctd) <- c("7949940", "7949952", "7949953", "7949954", "7949956", "7949959",
                      "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")

### 2020-04-13 simulation_study/README.Rmd
test ini file
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

@@
 
-```{r include = FALSE}
+```{r, include = FALSE}
 library(tidyverse)
@@
 
-```{r eval = FALSE}
+```{r, eval = FALSE}
 # 
@@
 ```{r}
-conditiongrid <- readRDS("00_conditiongrid.RDS")
-
+conditiongrid <- readRDS("R/00_conditiongrid.RDS")
 conditiongrid %>%
@@
 emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
-
+todo <- emptytodo
 ```
@@
 # BCTW
-
 # RCTW
-
 # SCTW 
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
-
 # LCTW
-
 # NCTW
@@
 asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini
-
 # RCTW
-
 # SCTW 
-
 # LCTW
-
 # NCTW
-
 ```
@@
 lubridate::date("2020-03-19")
-
 #todo <- check(todo, "BCTW", "one", datasets)
@@
 ./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23 
-
 ./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23 
-
 ./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23 
-
 ./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23 
-
 ./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
@@
 scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
-
 scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
@@
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986
-
 # LCTW 
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987
-
 # RCTW 
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989
-
 # NCTW does not work well with tfidf, save for second round with doc2vec: 
@@
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021
-
 ```
@@
 ./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157
-
 # RCTW, fixed a parameter bug in simulation package. 
@@
 # run again, 7815147
-
 # NCDW for remaining datasets 
-
 ```
@@
 scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/
-
 # run simulations (on own device)
-
 # see script
-
 ```
@@
 # todo <- busy(todo, "SCTW", "one", datasets[2:5])
-
 ```
@@
 todo %>% kable(format = "markdown")
-
 saveRDS(todo %>% kable(format = "markdown"), 
@@
 ************  ace.csv  ************
-
 Number of papers:            2235
@@
 Number of missing abstracts: 0 (of which 0 included)
-
 ************  nudging.csv  ************
-
 Number of papers:            1847
@@
 Number of missing abstracts: 0 (of which 0 included)
-
 ************  ptsd.csv  ************
-
 Number of papers:            5031
@@
 Number of missing abstracts: 0 (of which 0 included)
-
 ************  software.csv  ************
-
 Number of papers:            8896
@@
 Number of missing abstracts: 0 (of which 0 included)
-
 ************  wilson.csv  ************
-
 Number of papers:            2333

### 2020-04-13 simulation_study/hpoptimization/README.Rmd
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

--- 2020-04-03 simulation_study/hpoptimization/README.Rmd
@@
 ---
-title: "log hyperparameter optimization"
-output: html_notebook
+title: "Hyperparamter optimization"
+output:   
+  md_document:
+    variant: markdown_github
 ---
 
-Per day, all commands sent to surfsara
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
+library(tidyverse)
+library(ggplot2)
+library(knitr)
 
-After a command is sent, save that todo checklist file!
+php <- function(data){
+  data %>%
+    filter(param %in% numericalvars) %>%
+    mutate(value = as.numeric(value)) %>% 
+    ggplot(aes(x = value, y = "", color = group)) +
+    geom_jitter(height = 0.2) +
+    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
+    geom_vline(aes(xintercept = lb), color = "grey") +
+    geom_vline(aes(xintercept = ub), color = "grey") 
+}
 
-```{r}
-hpsets <- readRDS("../R/01_hyperparameter_sets.RDS")
-
-d <- colnames(hpsets)
-condition <- rownames(hpsets)
-classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
-names(classifier) <- c("B", "R", "S", "L", "N")
+php_c <- function(data){
+  data %>%
+    filter(param %in% categoricalvars) %>%
+    mutate(value = as.factor(value)) %>% 
+    ggplot(aes(x = value, color = group, fill = group, group = group)) +
+    geom_bar(position="dodge") +
+    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
+    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")
+}
 ```
 
-# one on one optimization
-
-## classifiers 
-BCTD on all datasets
-```{r}
-# BCTD
-script <- noquote(sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d %s -r 23", d))
-write.table(script, file = "scripts/one/nb_classifier.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-# job names
-names(script) <- c("7846991", "7846993", "7846994", "7846997", "7846998", "7846999")
+```{r, figure.heigth = 12}
+hpsets <- readRDS("config/hpresults.RDS")
+numericalvars <- c("balance_param.a", "balance_param.alpha", "balance_param.b", "model_param.alpha", "model_param.c", "model_param.class_weight", "feature_param.vector_size", "feature_param.epochs", "model_param.n_estimators")
+categoricalvars <-c("feature_param.ngram_max", "feature_param.split_ta", "feature_param.use_keywords", "model_param.gamma", "feature_param.dbow_words", "feature_param.dm", "feature_param.dm_concat", "feature_param.min_count", "feature_param.window", "model_param.max_features")
 ```
@@
 ```{r}
-# check off to do list. 
-hpsets["NCTD", , ] <- 9 # impossible model
-hpsets["BCTD", , "one"] <- 1 # finish nb one-one-one simulations
-```
-
-The other 3 classifiers 
-```{r}
-cons <- expand.grid(c = classifier[2:4], d = d, stringsAsFactors = FALSE)
-# all models
-class1 <- sprintf("./cart_hyper_run.py hyper-active -t 12:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$c, cons$d)
-write.table(class1, file = "scripts/one/three_classifiers.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-
-# job names
-names(class1) <- c(7847065,7847066,7847067,7847068,7847069, 7847070, 7847071,7847072, 7847074,7847075, 7847076, 7847077,7847078,7847079,7847080,7847081, 7847082,7847084)
-
-hpsets[condition[2:4], , "one"] <- 1
-```
-
-## now with doc2vec feature extraction 
-```{r}
-cons <- expand.grid(c = classifier[2:5], d = d, stringsAsFactors = FALSE)
-
-# a test run first maybe
-# NCDD
-noquote("./cart_hyper_run.py hyper-active -t 12:00:00 -m nb -b double -e doc2vec -q max -d ace -r 23") # 7847109
-# todo list
-hpsets[condition[6], , ] <- 9 # multinomial nb cannot deal with doc2vec (negative values!!)
+library(tidyverse)
+trials <- read_csv("trials/trials.csv")
 ```
@@
 ```{r}
-# then all classifier * dataset combinations. 
-t <- rep(c("12", "42", "42", "5-00"), length(d))
-d2v1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", t, cons$c, cons$d)
-# one test of doc2vec 
-write.table(d2v1, file = "scripts/one/doc2vec.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(d2v1) <- c("7854137", "7854187", "7854188", "7854208", 
-                 "7854189", "7854190", "7854191", "7854209", 
-                 "7854192", "7854193", "7854194", "7854210", 
-                 "7854195", "7854196", "7854197", "7854211", 
-                 "7854198", "7854199", "7854200", "7854212", 
-                 "7854201", "7854202", "7854203", "7854213")
+lossp <- function(trials, sort = TRUE){
+  if(sort){
+  p <-  trials %>%
+    ggplot(aes(x = nrow(trials):1, y = loss))
+  } else {
+  p <- trials %>%
+    ggplot(aes(x = trial, y = loss))
+  }
+  p + geom_line()
 
-hpsets[condition[7:10], ,"one"] <- 1
+}
 ```
 
-# n
+# Naive Bayes + TF-IDF
+
+## Loss plots
 ```{r}
-t <- c("12:00:00", "24:00:00", "48:00:00", "24:00:00")
-# optimize hyperparams over all datasets
-allc <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e tfidf -q max -r 23", t, classifier[1:4])
-write.table(allc, file = "scripts/n/fourclassifiers.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-
-# later for more than 12 hours. 
-names(allc) <- c("7848203", "7848204", "7848205", "7848206")
-
-hpsets[condition[1:4], , "all"] <- 1
-```
-
-## doc2vec models 
-```{r}
-t <- rep(c("42", "42", "42", "5-00"))
-cons <- expand.grid(c = classifier[2:5], stringsAsFactors = FALSE)
-
-d2vall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -r 23", t, cons$c)
-
-write.table(d2vall, file = "scripts/n/doc2vec.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(d2vall) <- c("7854227",  "7854228", "7854229", "7854230")
-
-hpsets[condition[7:10], ,"all"] <- 1
 
@@
 
-# n-1
+## Hyperparameter values
+```{r NB_TFIDF}
+php(hpsets$nb_tfidf) + 
+  labs(title = "Hyperparameters Naive Bayes + TF-IDF")
 
---- 
-# Visual inspection 30-03-2020
+# plot feature_param.ngram_max
+hpsets$nb_tfidf %>%
+  php_c()
 
-## classifiers
-```{bash, eval = FALSE}
-# script to show all lisa.err files to see if processes done yes/no
-.catlisaerr.sh
-```
-- svm 
-  - ace (3x) 3 times the time. 
-  - nudging 7x
-  - ptsd 7x 
-  - software 3x (of 4)
-  - virus 5x
-  - wilson 3x
-    - all 10x
-- rf 
-  - software 2x 
-  - all 3x
-- rest is fine, over 1000 runs and seems not to improve much. 
-```{r}
-hpsets[condition[c(1,4)], , c("one", "all")] <- 2
-hpsets[condition[c(2,3)],  d[c(1:2, 5:6)], "one"] <- 2
 ```
 
-Sent in around 13 pm (30.03.2020)
-```{r}
-# svm extra time 
-cons <- expand.grid(c = classifier[3], stringsAsFactors = FALSE, d= d)
-cons$t <- c("36", rep("84", 2), "48", "60", "36")
-extrasvm1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
-names(extrasvm1) <- c("7867379","7867380", "7867382", "7867383", "7867384", "7867387")
+# SVM + TF-IDF 
+```{r SVM_TFIDF, eval = FALSE}
+hpsets$svm_tfidf %>%
+  php() +
+  labs(title = "Hyperparameters SVM + TF-IDF")
 
-cons <- expand.grid(c=classifier[2], stringsAsFactors = FALSE, d=d[3:4])
-
-cons$t <- c("06", "24")
-
-extrarf1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -d %s -r 23", cons$t, cons$c, cons$d)
-names(extrarf1) <- c("7867388", "7867389")
-
-# later check rf - ptsd - one
-hpsets[condition[2], d[3], "one"] <- 2
-
-cons <- data.frame(c = classifier[2:3], t = c("5-00", "5-00"))
-extraall <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e tfidf -q max -r 23", cons$t, cons$c)
-names(extraall) <- c("7867412", "7873506")
-
-# save scripts for reproducibility 
-write.table(c(extrasvm1, extrarf1), file = "scripts/one/extratime_classifier.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-write.table(extraall, file = "scripts/n/extratime_classifier.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
+hpsets$svm_tfidf %>%
+  php_c() 
 ```
 
-## doc2vec 
-```{bash, eval = FALSE}
-# bash script to print all hyperopt results. 
-./show.sh
+```{r LR_TFIDF}
+php(hpsets$lr_tfidf) + 
+  labs(title = "Hyperparameters Logistic Regression + TF-IDF")
+
+hpsets$lr_tfidf %>%
+  php_c()
 ```
 
-- nn-2-layer - try again with -r 11.  (for all datasets still doesn't work )
+```{r LR_D2V, eval}
+php(hpsets$lr_d2v) + 
+  labs(title = "Hyperparameters Logistic Regression + Doc2Vec")
 
-```{r}
-# redo nn-2-layer with doc2vec. 
-#./cart_hyper_run.py hyper-active -t 01:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 11 7867616 test for an hour 
-hpsets[condition[10], , "one"] <- 8 # error
-cons <- expand.grid(c = classifier[5], stringsAsFactors = FALSE, d=d)
-cons$t <- "5-00:00:00"
-nn2dv1 <- sprintf("./cart_hyper_run.py hyper-active -t %s -m %s -b double -e doc2vec -q max -d %s -r 11", cons$t, cons$c, cons$d)
-write.table(nn2dv1, file = "scripts/one/nn2d2v.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(nn2dv1) <- c("7872280", "7872281", "7872282", "7872283", "7872284", "7872285")
-hpsets[condition[10], , "one"] <- 1 # sent in again
-# this can be turnt of afer 52 hours. (thursday morning) 02.04
-
-nn2d2vall <- c("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m nn-2-layer -b double -e doc2vec -q max -r 4")
-write.table(nn2d2vall, file = "scripts/n/nn2d2v.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(nn2d2vall) <- "7873511"
-```
-
-- rf is done 
-  - ace 3x? 
-  - nudging 2x 
-  - ptsd 6x
-  - software 10 x
-  - virus 1.5 x 
-  - wilson 1x
-
-```{r}
-# redo random forest d2v
-t <- rep(c("36", "24", "72", "5-00", "18", "12"))
-x_d2v_rf <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m rf -b double -e doc2vec -q max -d %s -r 23", t, d)
-# one test of doc2vec 
-write.table(x_d2v_rf, file = "scripts/one/x_d3v_rf.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(x_d2v_rf) <- c("7867607", "7867608", "7867609", "7867610", "7867611", "7867612")
-```
-
-# asreview create-config
-
-# export config files 
-(from all files in output :) )
-
-```{r}
-d4 <- c(paste(d[1:5], collapse=","), 
-        paste(d[2:6], collapse=","), 
-        paste(d[c(3:6,1)], collapse = ","), 
-        paste(d[c(4:6, 1:2)], collapse=","),
-        paste(d[c(5:6, 1:3)], collapse = ","),
-        paste(d[c(6, 1:4)], collapse = ","))
-cons <- expand.grid(c = classifier, d = d4, f=c("tfidf", "doc2vec"), stringsAsFactors = FALSE)
-cons <- cons[!(cons$c == "nb" & cons$f == "doc2vec"), ]
-cons$r <- ifelse(cons$c == "nn-2-layer", "11", "23")
-cons$t <- ifelse(cons$c == "nb", "12", "5-00")
-# all models
-n_1 <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e %s -q max -d %s -r %s", cons$t, cons$c, cons$f, cons$d, cons$r)
-write.table(n_1, file = "scripts/n-1/all_models.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-
-# job names
-names(n_1) <- c("7873344", "7873345", "7873346", "7873347", "7873348",
-                "7873360", "7873361", "7873363", "7873364", "7873365",
-                "7873378", "7873379", "7873381", "7873382", "7873383",
-                "7873392", "7873393", "7873394", "7873396",
-                "7873396",
-                "7873397", "7873398", "7873399", "7873400", "7873401",
-                "7873407", "7873408", "7873409", "7873411", "7873413",
-                "7873425", "7873427", "7873429", "7873431", "7873433",
-                "7873446", "7873448", "7873450", "7873453", 
-                "7873455",
-                "7873460", "7873461", "7873462", "7873463",
-                "7873464",
-                "7873466", "7873467", "7873468", "7873469", "7873470", 
-                "7873471", "7873472", "7873473", "7873474")
-
-hpsets[c(1:5, 6:10),,"four"] <- 1
-```
-
-31.03.2020
-### all 
-all SCDD, LCDD RCDD, resend for 5 days 
-```{r}
-# more time for doc2vec all datasets - svm + logistic 
-d2vall
-cons <- expand.grid(c = classifier[2:4], stringsAsFactors = FALSE)
-d2vall_x <- sprintf("./cart_hyper_run.py hyper-active -t 5-00:00:00 -m %s -b double -e doc2vec -q max -r 23", cons$c)
-write.table(d2vall_x, file = "scripts/n/d2v_all_x.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(d2vall_x) <- c("7873497", "7873499","7873500")
-```
-
-try nn2 with tfidf -r 11
-
-checkout nn 2 layer tfidf
-
-### one
-one LCDD, for 2x the time 
-one SCDD for 1x the time 
-```{r}
-cons <- expand.grid(c = classifier[3:4], d = d, stringsAsFactors = FALSE)
-cons$t <- ifelse(cons$c=="logistic", "96", "48")
-d2v1_x <- sprintf("./cart_hyper_run.py hyper-active -t %s:00:00 -m %s -b double -e doc2vec -q max -d %s -r 23", cons$t, cons$c, cons$d)
-write.table(d2v1_x, file = "scripts/one/d2vone_x.txt", sep="\t", quote = FALSE, row.names = FALSE)
-
-names(d2v1_x) <- c("7877706", "7877707", "7877708", "7877709", "7877710",
-                   "7877711", "7877712", "7877713", "7877714", "7877715", "7877716", 
-                   "7877717")
+hpsets$lr_d2v %>%
+  php_c()
 ```
@@
 ```{r}
-hpsets[condition[2], d[4] , "one"] <- 2
-```
+php(hpsets$rf_tfidf) + 
+  labs(title = "Hyperparameters Random Forest + TF-IDF")
 
-01.04
-nn-2-layer retry r-1 
-```{r}
-cons <- expand.grid(c = classifier[5], fe = c("tfidf", "doc2vec"), d = d, stringsAsFactors = FALSE)
-
-nn_test <- sprintf("./cart_hyper_run_asrnn.py hyper-active -t 5-00:00:00 -m %s -b double -e %s -q max -d %s -r 2", cons$c, cons$fe, cons$d)
-write.table(nn_test, file = "scripts/one/nn_test.txt", sep="\t", quote = FALSE, row.names = FALSE)
-
-names(nn_test) <- c("7891389", "7891390", "7891391", "7891392", "7891393", "7891394", "7891395", "7891396", "7891402", "7891407", "7891408", "7891411")
-# ./cart_hyper_run_asrnn.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d wilson -r 2 # 7886988, 
-#./cart_hyper_run.py hyper-active -t 55 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 2 # 7883466
-# ssh tcn560
-# top 
+hpsets$rf_tfidf %>%
+  php_c()
 ```
@@
 ```{r}
-# cancel all logistic 4-1 sets 
-#  7873347, 7873448, 7873460, 7873464, 7873469, 7873473
-hpsets["LCTD", , "four"] <- 2
+php(hpsets$rf_d2v) + 
+  labs(title = "Hyperparameters Random Forest + Doc2Vec")
+
+hpsets$rf_d2v %>%
+  php_c()
 ```
 
-03.04.2020
+statistics for random forest + tf-idf
 ```{r}
-# svm d2v one are done! 
-hpsets["SCDD",, "one"] <- 2
+hpsets$rf_tfidf %>%
+   group_by(param, group) %>%
+    summarise(variance = var(value), 
+              sd = sd(value),
+              min = min(value), 
+              mean = mean(value),
+              median = median(value),
+              max = max(value)) %>%
+  kable("markdown")
 ```

### 2020-04-13 simulation_study/simulation/README.Rmd
fix bugC-parameter LCDD config files
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

--- 2020-04-04 simulation_study/simulation/README.Rmd
@@
 rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
-write.table(rctd_lctd, file = "scripts/one/rctd_lcdt.txt", sep = "\t", quote = FALSE,
+write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
             row.names = FALSE)
 #one_rctd_virus etc 
-names(rctd_lctd) <- c("7883218", "7883219", "7883220", "7883221", "7883223", "7883224",
-                     "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")
+names(rctd_lctd) <- c(rep("0", 6), "7949940", "7949952", "7949953", "7949954", "7949956", "7949959")
 ```
@@
            row.names = FALSE)
-names(scdd) <- c("7893237", "7893241", "7893243", "7893244", "7893246", "7893247")
+ names(scdd) <- c("7950186", "7950187", "7950188", "7950189", "7950190", "7950191")
  sims[condition[8], d, "one"] <- 2 # simulations are running 
+```
 
+```{r}
+ sctd <- createLines(condition[3], d, "one")
+ write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(sctd) <- c("7950483", "7950484", "7950485", "7950487", "7950489", "7950490")
+sims[condition[3], d, "one"] <- 2 # simulations are running
+```
+
+```{r}
+rcdd <- createLines(condition[7], d, "one")
+write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
+            row.names = FALSE)
+names(rcdd) <- c("7950491", "7950493", "7950495", "7950496", "7950497", "7950499")
+sims[condition[7], d, "one"] <- 2 # simulations are running
+```
+
+```{r}
+lcdd <- createLines(condition[9], d, "one")
+write.table(lcdd, file = "scripts/one/lcdd.txt", sep = "\t", quote = FALSE, row.names = FALSE)
+names(lcdd) <- c("7965136", "7965141", "7965143", "7965145", "7965146", "7965147")
+sims[condition[9], d, "one"] <- 2 # simulations are running
+```
+
+10.04.2020
+
+```{r}
+# LCTD and SCDD both failedsimulations both failed? 
+# ran again 
+# transfer to harddrive
+transfer("one", condition[c(4,7:9)])
+# sctd is not finished yet! 
+sims[condition[4],,"one"] <- 3 # output is on harddrive
+
+# sims[condition[7],,"one"] <- 3 # output is on harddrive 
+# sims[condition[8],,"one"] <- 3 # output is on harddrive 
+# too little space for 9, so run again
+
+sims[condition[9],,"one"] <- 3 # output is on harddrive 
+# but ace wasn't finished yet!
+
+```
+
+Repeat all failed simulations
+
+```{r}
+# run again 
 # transfer to harddrive 
 transfer("one", condition[8])
+
 #sims[condition[8], , "one"] <- 3 # output is on harddrive
@@
 
-all - LCTD hyperparameters 
+### all 
 ```{r}
@@
 
+```
+
+```{r}
 # run simulations 
-lctd_n <- createLines(condition[4], d, "all")
-write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(lctd_n) <- c()
-#sims[condition[4], d, "all"] <- 2 # simulations are running
-
-# transfer to harddrive 
-transfer("n", condition[4])
+# lctd_n <- createLines(condition[4], d, "all")
+# write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
+#             row.names = FALSE)
+# names(lctd_n) <- c()
+# #sims[condition[4], d, "all"] <- 2 # simulations are running 
+# 
+# # transfer to harddrive 
+# transfer("n", condition[4])
 #sims[condition[8], , "one"] <- 3 # output is on harddrive

### 2020-04-13 simulation_study/R/functions.R

@@ -33,8 +33,8 @@ check <- function(x){switch(x,
 # 8 = not going to do 
 # 9 = problems
  
-apply(hpsets[,1,1], check)
-
-check(hpsets[1,1,1])
-
-sapply(hpsets, check, FUN.VALUE = hpsets)
+# apply(hpsets[,1,1], check)
+# 
+# check(hpsets[1,1,1])
+# 
+# sapply(hpsets, check, FUN.VALUE = hpsets)

### 2020-04-13 simulation_study/hpoptimization/config/load_results.R

@@ -90,15 +90,6 @@ prepData <- function(data){
   return(data)
 }
 
-php <- function(data){
-  data %>%
-    ggplot(aes(x = value, y = "", color = group)) +
-    geom_jitter(height = 0.2) +
-    facet_wrap(vars(param), nrow = 8, scales = "free_x") +
-    geom_vline(aes(xintercept = lb), color = "grey") +
-    geom_vline(aes(xintercept = ub), color = "grey") 
-}
-
 # compute variance of hyperparameters 
 paramstats <- function(data){
   data %>% 
@@ -110,14 +101,14 @@ paramstats <- function(data){
 }
 
 
-## plot for lctd 
+# bctd
+bctd <- prepData(bctd)
+
+# plot for lctd 
 lctd <- prepData(lctd)
 
 # lcdd 
 lcdd <- prepData(lcdd)
-
-# bctd
-bctd <- prepData(bctd)
 
 # rctd
 rctd <- prepData(rctd)
@@ -131,15 +122,12 @@ sctd <- prepData(sctd)
 scdd <- prepData(scdd)
 # inspect 
 
-#
-
-
 # put al results in a list 
-hps <- list(svm_tfidf = sctd, svm_d2v = scdd,
+hps <- list(svm_tfidf = sctd, 
+            svm_d2v = scdd,
             nb_tfidf = bctd, 
             lr_tfidf = lctd, 
             lr_d2v = lcdd, 
             rf_tfidf = rctd, 
-            rf_d2v = rcdd, all.names = TRUE)
-
+            rf_d2v = rcdd)
 saveRDS(hps, file = "simulation_study/hpoptimization/config/hpresults.RDS")

### 2020-04-13 simulation_study/hpoptimization/trials/load_trials.R

@@ -1,0 +1,18 @@
+# load data from trials.csv files and process into dataframe
+losspath <- "/Volumes/Gerbrich/asreview/output/active/"
+models <- list.files(losspath)
+mpaths <- paste0(losspath, models)
+conditions <- list.files(mpaths[1])
+paste0(mpaths, "/",conditions, "/trials.csv")
+
+
+for(m in mpaths) {
+  
+}
+
+test <- do.call(read_csv, file = paste0(mpaths, "/",conditions, "/trials.csv"))
+
+# get loss column, get model name column, condition column
+
+# save losses
+saveRDS(test, file = "simulation_study/hpoptimization/trials/trials.RDS")

### 2020-04-13 simulation_study/hpoptimization/README.Rmd
add extra loss plots hpoptimization

@@
 ---
-title: "Hyperparamter optimization"
+title: "Hyperparamter Optimization"
 output:   
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+```
+
+```{r packages}
 library(tidyverse)
@@
 library(knitr)
+library(directlabels)
+```
 
+To every model belongs a unique set of hyperparameters.
+To maximize model performance, we need to find optimal values for the hyperparameters.
+For every model the optimal hyperparameter values are determined by optimizing on data $d$.
+The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space.
+
+Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (eg the area above the curve in the inclusion plot).
+
+The optimization data d consists of (a subset from) the six systematic review datasets D mentioned above. Three different approaches in composing d are explored:
+
+- __one__, where hyperparameters are optimized on only one of the six datasets. Such hyperparameters are expected to lead to maximum performance in the same dataset d.
+- __n__, where hyperparameters are optimized on all six data sets. This optimization approach intends to serve in producing the most optimal hyperparameters overall. 
+- __n-1__, where hyperparameters are optimized on all six datasets but one.
+Serving as a sensitivity analysis for the former condition, eg how sensitive are the hyperparamters.
+also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before.
+where d are all datasets but the one where we want to simulate later on.
+
+This results in 6+6+1=13 sets of hyperparameters for every model.
+Optimization trials were visually inspected to check if an optimum (minimal loss) has been reached.
+More trials were run if the loss still seemed to go down at a quick pace.
+The hyperparameter sets that were found to lead to a minimum loss value were visually inspected.
+
+```{r functions}
 php <- function(data){
@@
     geom_vline(aes(xintercept = lb), color = "grey") +
-    geom_vline(aes(xintercept = ub), color = "grey") 
+    geom_vline(aes(xintercept = ub), color = "grey") +
+    theme_minimal()
 }
@@
     facet_wrap(vars(param), nrow = 2, scales = "free_x") +
-    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")
+    labs(title = "(optimal) categorical hyperparameters", y = "", x = "Parameter values")+
+    theme_minimal()
 }
@@
 
-```{r, figure.heigth = 12}
+```{r}
 hpsets <- readRDS("config/hpresults.RDS")
@@
 
-```{r}
-library(tidyverse)
-trials <- read_csv("trials/trials.csv")
-```
+```{r loss_function}
 
-```{r}
-lossp <- function(trials, sort = TRUE){
-  if(sort){
-  p <-  trials %>%
-    ggplot(aes(x = nrow(trials):1, y = loss))
-  } else {
-  p <- trials %>%
-    ggplot(aes(x = trial, y = loss))
+# loss i where x is index, a.k.a. loss plot sorted from high to low loss.
+loss_i <- function(trials){
+  trials %>%
+  ggplot(aes(x = index, y = loss)) +
+  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
+  labs(title = "Loss plot", x = "Trials sorted from high to low loss") +
+    theme_minimal()
 }
-  p + geom_line()
 
+# loss t where x is trials, loss plot is sorted over time
+loss_t <- function(trials){
+  trials %>%
+    ggplot(aes(x = trial, y = loss)) +
+    geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+    geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
+    labs(title = "Loss plot", x = "Over trials") +
+    theme_minimal()
 }
@@
 ## Loss plots
+Two times the same data, first plot is over trials, second sorted from highest to lowest loss.
 ```{r}
+nbtfidftrials <- readRDS("trials/nb_tfidf_trials.RDS")
 
+nbtfidftrials <- nbtfidftrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+nbtfidftrials %>% loss_i
+
+# loss plot sorted by trial numbers 
+nbtfidftrials %>%
+  loss_t()
 ```
@@
   php_c() 
-
 ```
@@
 
+# Logistic Regression + TF-IDF 
 ```{r LR_TFIDF}
@@
 
-```{r LR_D2V, eval}
+# Logistic Regression + Doc2Vec
+```{r LR_D2V}
 php(hpsets$lr_d2v) + 
@@
 
-```{r}
+# Random Forest + TF-IDF
+```{r rf_tfidf}
 php(hpsets$rf_tfidf) + 
@@
 
-```{r}
+# Random Forest + Doc2Vec
+## Loss plot
+```{r rf_d2v_loss}
+rfd2vtrials <- readRDS("trials/rf_d2v_trials.RDS")
+
+rfd2vtrials <- rfd2vtrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+rfd2vtrials %>%
+  ggplot(aes(x = index, y = loss)) +
+  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
+  labs(title = "Loss plot", x = "Trials sorted from high to low loss")
+
+rfd2vtrials %>%
+  ggplot(aes(x = index, y = loss)) +
+  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
+  labs(title = "Loss plot", x = "Over trials")
+```
+
+## Hyperparameter Values
+```{r rf_d2v}
 php(hpsets$rf_d2v) + 
@@
 ```
-
-statistics for random forest + tf-idf
-```{r}
-hpsets$rf_tfidf %>%
-   group_by(param, group) %>%
-    summarise(variance = var(value), 
-              sd = sd(value),
-              min = min(value), 
-              mean = mean(value),
-              median = median(value),
-              max = max(value)) %>%
-  kable("markdown")
-```

### 2020-04-13 simulation_study/hpoptimization/trials/load_trials.R

@@ -2,17 +2,47 @@
 losspath <- "/Volumes/Gerbrich/asreview/output/active/"
 models <- list.files(losspath)
 mpaths <- paste0(losspath, models)
-conditions <- list.files(mpaths[1])
-paste0(mpaths, "/",conditions, "/trials.csv")
+conditions <- list.files(mpaths[3])
 
-
-for(m in mpaths) {
+addGroup <- function(data){
+  one <- data$datasets %in% c("ace", "nudging", "ptsd", "software", "virus", "wilson")
+  n <- data$datasets == "ptsd_virus_ace_software_wilson_nudging"
+  n_1 <- !(one | n)
   
+  data$group <- rep("0", length(one))
+  
+  data[one, "group"] <- "one"
+  data[n, "group"] <- "n"
+  data[n_1, "group"] <- "n-1"
+  return(data)
 }
 
-test <- do.call(read_csv, file = paste0(mpaths, "/",conditions, "/trials.csv"))
+trialsdf <- function(files){
+  tdf <- lapply(files, read_csv)
+  tdf <- map(tdf, `[`, c("loss", "trial"))
+  tdf <- tdf %>% map(~ mutate(.x, index = 1:nrow(.x)))
+  tdf <- bind_rows(tdf, .id = "model")
+  tdf <- separate(tdf, model, sep = "-", into = c("model", "datasets"))
+  tdf <- addGroup(tdf)
+  tdf$group <- as.factor(tdf$group)
+  return(tdf)
+}
+
+files <- paste0(mpaths[3], "/",conditions, "/trials.csv")
+names(files) <- paste0(models[3], "-", conditions)
+nb_tfidf <- trialsdf(files)
+
+
+saveRDS(nb_tfidf, file = "simulation_study/hpoptimization/trials/nb_tfidf_trials.RDS")
+
+
+
+files <- paste0(mpaths[5], "/",conditions, "/trials.csv")
+names(files) <- paste0(models[5], "-", conditions)
+rf_d2v <- trialsdf(files)
+saveRDS(rf_d2v, file = "simulation_study/hpoptimization/trials/rf_d2v_trials.RDS")
+
 
 # get loss column, get model name column, condition column
 
 # save losses
-saveRDS(test, file = "simulation_study/hpoptimization/trials/trials.RDS")

### 2020-04-13 simulation_study/hpoptimization/README.Rmd
update RF loss plots

@@
 ---
-
+# Optimizing Hyperparameters
 ```{r setup, include=FALSE}
@@
 - __n__, where hyperparameters are optimized on all six data sets. This optimization approach intends to serve in producing the most optimal hyperparameters overall. 
-- __n-1__, where hyperparameters are optimized on all six datasets but one.
-Serving as a sensitivity analysis for the former condition, eg how sensitive are the hyperparamters.
-also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before.
-where d are all datasets but the one where we want to simulate later on.
+- __n-1__, where hyperparameters are optimized on all six datasets but one. Serving as a sensitivity analysis for the former condition, eg how sensitive are the hyperparamters to different data sets.
 
@@
 rfd2vtrials %>%
-  ggplot(aes(x = index, y = loss)) +
-  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
-  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
-  labs(title = "Loss plot", x = "Trials sorted from high to low loss")
+  loss_t()
 
 rfd2vtrials %>%
-  ggplot(aes(x = index, y = loss)) +
-  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
-  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
-  labs(title = "Loss plot", x = "Over trials")
+  loss_i()
 ```

### 2020-04-15 simulation_study/hpoptimization/README.Rmd
add remaining loss plots hpoptimization

@@
     geom_jitter(height = 0.2) +
-    facet_wrap(vars(param), nrow = 2, scales = "free_x") +
+    facet_wrap(vars(param), ncol = 3, scales = "free_x") +
     geom_vline(aes(xintercept = lb), color = "grey") +
@@
 ```{r loss_function}
-
 # loss i where x is index, a.k.a. loss plot sorted from high to low loss.
@@
 ```{r}
-nbtfidftrials <- readRDS("trials/nb_tfidf_trials.RDS")
+nbtfidftrials <- readRDS("trials/nb_tfidf-trials.RDS")
 
@@
 # loss plot by index 
-nbtfidftrials %>% loss_i
+nbtfidftrials %>% 
+  loss_i()
 
@@
 
+Inspect outliers: 
+```{r}
+# inspect outliers
+hpsets$nb_tfidf %>% filter(param %in% c("balance_param.a", "model_param.alpha")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
+```
+
 # SVM + TF-IDF
-```{r SVM_TFIDF, eval = FALSE}
+
+```{r SVM_TFIDF}
+svmtfidftrials <- readRDS("trials/svm_tfidf-trials.RDS")
+
+svmtfidftrials <- svmtfidftrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+svmtfidftrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
+svmtfidftrials %>%
+  loss_t()
+
+# parameter values numerical 
 hpsets$svm_tfidf %>%
@@
 ```{r LR_TFIDF}
+lrtfidftrials <- readRDS("trials/lr_tfidf-trials.RDS")
+
+lrtfidftrials <- lrtfidftrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+lrtfidftrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
+lrtfidftrials %>%
+  loss_t()
+
 php(hpsets$lr_tfidf) + 
@@
 
+Inspect outliers
+```{r}
+hpsets$lr_tfidf %>% filter(param %in% c("balance_param.a", "model_param.c")) %>% group_by(param) %>% filter(value > 40) %>% select(-ub, -lb)
+hpsets$lr_tfidf %>% filter(param %in% c("model_param.class_weight")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
+```
+
 # Logistic Regression + Doc2Vec
 ```{r LR_D2V}
+lrd2vtrials <- readRDS("trials/lr_d2v-trials.RDS")
+
+lrd2vtrials <- lrd2vtrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+lrd2vtrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
+lrd2vtrials %>%
+  loss_t()
+
 php(hpsets$lr_d2v) + 
@@
 ```{r rf_tfidf}
+rftfidftrials <- readRDS("trials/rf_tfidf-trials.RDS")
+
+rftfidftrials <- rftfidftrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+rftfidftrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
+rftfidftrials %>%
+  loss_t()
+
 php(hpsets$rf_tfidf) + 
@@
 ```{r rf_d2v_loss}
-rfd2vtrials <- readRDS("trials/rf_d2v_trials.RDS")
+rfd2vtrials <- readRDS("trials/rf_d2v-trials.RDS")
 
@@
 
+# loss plot by index 
+rfd2vtrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
 rfd2vtrials %>%
@@
 
-rfd2vtrials %>%
-  loss_i()
 ```

### 2020-04-15 simulation_study/hpoptimization/trials/load_trials.R

@@ -1,9 +1,13 @@
+library(tidyverse)
 # load data from trials.csv files and process into dataframe
+
 losspath <- "/Volumes/Gerbrich/asreview/output/active/"
 models <- list.files(losspath)
+# get rid of neural network 2-layer models s
+models <- models[c(-4, -5)]
 mpaths <- paste0(losspath, models)
-conditions <- list.files(mpaths[3])
 
+# add group (n-1, n, one) to dataset. 
 addGroup <- function(data){
   one <- data$datasets %in% c("ace", "nudging", "ptsd", "software", "virus", "wilson")
   n <- data$datasets == "ptsd_virus_ace_software_wilson_nudging"
@@ -17,10 +21,12 @@ addGroup <- function(data){
   return(data)
 }
 
+# extract hyperparameter data from trials.csv files 
 trialsdf <- function(files){
   tdf <- lapply(files, read_csv)
   tdf <- map(tdf, `[`, c("loss", "trial"))
   tdf <- tdf %>% map(~ mutate(.x, index = 1:nrow(.x)))
+  
   tdf <- bind_rows(tdf, .id = "model")
   tdf <- separate(tdf, model, sep = "-", into = c("model", "datasets"))
   tdf <- addGroup(tdf)
@@ -28,21 +34,14 @@ trialsdf <- function(files){
   return(tdf)
 }
 
-files <- paste0(mpaths[3], "/",conditions, "/trials.csv")
-names(files) <- paste0(models[3], "-", conditions)
-nb_tfidf <- trialsdf(files)
+# more readable names for differnet models 
+names <- c("lr_d2v", "lr_tfidf", "nb_tfidf", "rf_d2v", "rf_tfidf", "svm_d2v", "svm_tfidf")
 
+for(m in mpaths){
+  conditions <- list.files(m)
+  files <- paste0(m, "/",conditions, "/trials.csv")
+  names(files) <- paste0(models[m==mpaths], "-", conditions)
+  trials <- trialsdf(files)
+  saveRDS(trials, file = paste0("simulation_study/hpoptimization/trials/", names[m==mpaths], "-trials.RDS"))
+}
 
-saveRDS(nb_tfidf, file = "simulation_study/hpoptimization/trials/nb_tfidf_trials.RDS")
-
-
-
-files <- paste0(mpaths[5], "/",conditions, "/trials.csv")
-names(files) <- paste0(models[5], "-", conditions)
-rf_d2v <- trialsdf(files)
[…]

### 2020-04-24 manuscript/drafts/manuscript.Rmd
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters
- update introduction section,

@@
 author: "Gerbrich Ferdinands"
-date: "1/14/2020"
+date: "22/04/2020"
 output:
-  word_document: default
   pdf_document:
     citation_package: biblatex
+#  word_document: default
 bibliography: asreview.bib
@@
 
+Keywords: Human-Machine interaction, active learning, systematic reviews, text classification
+
 #### Introduction 
+<!-- This study aims to contribute to this growing area of research by exploring  -->
+
 #### Methods
-A convenience sample of 5 existing systematic reviews on varying topics was collected.
+<!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->
 
@@
 # Introduction
-Systematic Reviews (SR's) are booming - but they are a lot of work
-Various machine learning tools have been proposed to reduce workload in abstract screening.
+Systematic reviews are top of the bill in building evidence in research.
+A systematic review attempts to bring together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
+Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007].
+<!-- PRISMA definition:  -->
+<!-- > "A systematic review attempts to collate all relevant evidences that fits pre-specified eligibility criteria to answer a specific research -->
+<!-- question.
 
-- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
-- justification - 
-- background 
-- guidance to reader 
-- summary/conclusion
+add that htis is a systematic/rigorous process?-->
+
+Systematic reviews are costly.
+Conducting a systematic review involves the manual screening of thousands of titles and abstracts, identifying publications relevant to asnwering the research question.
+This process typically requires over a year of work from a team of researchers [@Borah2017].
+Besides time-consuming, the process of title and abstract screening is also prone to human error [@Wang2020].
+<!-- (14 to 77,910, trimmed mean 1,286).  -->
+<!-- Need to be screened by multiple researchers.  -->
+
+<!-- As the number of scientific publications is growing at an increasing rate [source], the workload in SR is getting heavier.  -->
+
+As time and resources are limited, it is often impossible to meet the strict criteria of a systematic review. 
+Currently, the demand for systematic reviews exceeds the available capacity by far [@Lau2019].
+Moreover, the required resources for a systematic review is making it difficult to timely respond to urgent matters.
+An example of this is the need for clinical guidelines in the current covid-19 crisis. 
+To ensure a timely review, reducing workload in systematic reviews is imperative.
+
+With advances in Artificial Intelligence (AI), a plethora of methods have been proposed to reduce workload in systematic reviews [@Harrison2020].
+More specifically, the field of AI-aided title and abstract screening is rapidly evolving [@OMara-Eves2015].
+Machine Learning (ML) models have been proposed, aiming to assist the reviewer by detecting whether a given publication is relevant or irrelevant to the systematic review.
+Findings suggest such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
+Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Yu2018] [moresources].
+The publications to be screened are ordered by their likeliness of relevance, seeing all relevant publicatoins much earlier on in the screening process when they would have been read in a random order.
+
+Screening prioritization reorders   
+Their objective is to assist the reviewer in the screening process by prioritizing publications most likely to be relevant.
+
+recent research/promising Active Learning.
+
+The current study focus is on reducing workload by prioritizing the most relevant abstracts.
+Presenting the abstracts orders the abstracts by likelihood of relevance, e.g.
+th The reviewer sees the most relevant abstracts first, If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.
+
+The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
+It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
+
+In most recent studies, 
+The latest state-of-the-art methods implement active learning, where the model improves its prediction of relevance based on the reviewers latest decisions in the screening process [@Yu2018; @Miwa2014].
+The ML-model, where the ML-model orders the most
+
+In most recent studies, X has been measured in four different ways.
+The use of qualitative case studies is a well-established approach in …
+
+Their objective is
+
+"Screening is performed in two steps, first preliminarily based on title and abstract,
+then based on full-text." 
+Screening a title + abstracts takes 30 seconds on average, for an experienced reviewer, and longer for inexperienced ones [@Wallace2010].
+
+<!-- add: current consensus active learning are state of the art: how do they woroK; by prioritizatio (put in a picture)  -->
+
+<!-- #### identifying the niche  -->
+Although considerable research has been devoted to the effectiveness of ML-models in reducing workload in title and abstract screening, the complex nature of the field makes it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
+The lack of replication on data outside the biomedical sciences makes it impossible to draw conclusions about the general effectiveness of such technologies [@OMara-Eves2015].
+Taken together, these issues prohibit the adoptation of AI-aided title and abstract screening by systematic reviewers.
+
+[@Marshall2020]
+
+<!-- By evaluating different configurations of an active learning model on different review contexts.  -->
+<!-- status quo: prioritization + active learning? + certainty [@Miwa2014], but classifier  -->
+<!-- Although several studies attempt to evaluate such methods,  -->
+<!-- It makes  -->
+<!-- although  tackle issues in the (complex) area,  -->
+<!-- Furthermore, few studies have investigated the use of different classifiers in any systematic way -->
+<!-- AI-aided title and abstract screening has been proven succesful in reducing workload, but a lack of replication and  -->
+
+<!-- Furthermore, a comparison mode in public health and clinicial medicing [@Miwa2014] compared different classifier on different datasets and found differential performance on 'messier' social sciences datasets.
+-->
+
+<!-- #### Occupying -->
+<!-- ##### (listing purpose of new research,  -->
+The current study aims to address these concerns in the following ways:
+
+1) Combining latest insights from the field of AI-aided title and abstract screening, various ML-models for screening prioritization are built.
+2) To evaluate model performance across different review contexts, the models are simulated on multiple datasets from various research areas, of which the data is openly accessible.
+3) To ensure replication and transparency, the simulations are implemented in an open source pipeline called `ASReview`. 
+<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
+
+This study set out to increase the evidence base of ML-models aiming to reduce workload in title and abstract screening in systematic reviews.
+Working towards a general consensus in this emerging field, performance of state-of-the art ML-models is evaluated over various research contexts.
+To further increase usability and acceptability of such models amongst systematic reviewers, the study presents a reproducible workflow.
+
+ <!-- [@OConnor2019] -->
+
+<!-- ##### listing questions,  -->
+<!-- This study .  -->
+<!-- research questions:  -->
+<!-- RQ1 – how -->
+<!-- -	RQ1a – does classifier performance vary over different research areas? -->
+<!-- (in what terms does it perform best)  -->
+
+<!-- ASReview aims to reduce workload in the citation screening process by prioritizing the most relevant abstracts.  -->
+<!-- ASReview combines in text classification  -->
+
+<!-- Furthermore, this study makes a contribution to ...  by demonstrating a reproducible and flexible tool,  -->
+<!-- Furthermore, a generic and reproducible workflow is presented to facilitate, hopefully to increase acceptability and usability by researchers performing systematic reviews.  -->
+
+The remaining part of this paper is organized as follows: first, a short review of state-of-the art methods is given.
+Second, the proposed ML-models will be explained on a conceptual level.
+Third, the methods section gives a detailed description of the study design.
+The results section ...
+and last, the results will be discussed.
 
@@
 
-This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.
+Active learning is the approach where   [@Settles2002]
 
-Systematic reviews are top of the bill in research.
-As more and more papers are published and reproducibility crisis has emerged, science calls for more meta.
-It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
-Performing a systematic review is a tedious and time-consuming task.
-To review a specific research area, one starts out with an initial search of thousands of academic papers.
-All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
-With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
-This whole processes costs this and this much time [shelmilt].
+Study selection in systematic review process
+
+#### summarise models used
+#### propose pipeline 
+##### and specific components?
+
+#### summarise datasets tested
+\
+\
+
+## Background
+[@OMara-Eves2015] literature review
+
+[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
+A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
+In terms of Yu et al, we adopt .CT.
+
+SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
+
+abstrackr
+
+SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
+Also include social sciences data besides medical data.
+
+[@Cohen2006] perceptron-based classifier (neural network)
+
+SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
+in limitations section mentions that LR yields about same results, nb inferior results.
+
+[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
+  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+The AUC results are mixed, although boosting has a slight edge overall.
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
+
+Our extensions is that we try different classifiers, on more datasets.
+
+Goal: evaluate performance of different models of the ASReview tool. 
+The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
+What would happen if the citation screening would have been performed using asreview? 
+All datasets accompanying the systematic reviews are openly published. 
+We built several machine learning models to perform automated systematic reviews, 
+who are then applied on existing systematic reviews.
+
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
+The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
+
+a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
+Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
+
+Openness, reproducible,
+
+Benefits:
+
+Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
+meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
+
+paper organization:
+
+The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
+So not only medical sciences.
+
+Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
+Few studies have evaluated different classifiers in any systematic way
+different models to use haven't been investigated in a systematic way (only in software engineering)
+
+1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
+2) screening prioritization is appealing to systematic reviewers because ...
+3) 
+4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
+
+lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
+There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
+
+However, there is a need for consensus () and transparancy?
+
+So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
+
+Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
+
+##### indicating the structure of the writing)
+principle findings:
+
+<!-- RQ2 different hyperparameter optimizations? -->
+<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
+
+For truly evaluate the effectiveness of such methods,
+
+automatically (by machine learning techniques)
+In the current study we focus on the effectiveness of different machine learning models in reducing workload in the citation screening process. 
+Assisting the reviewer. Combining various machine learning techniques. 
+Combining recent insights on, we propose ASReview.
+Approaching the citation screening phase as a classfication task,
+The benefit is that ASReview is dynamic, user can decide
+open source, multiple classifiers and other settings,
+
+The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th
+The reviewer sees the most relevant abstracts first, 
+If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.
+
+Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
+
+#### Proposed solution
+This study is about how machine learning models can increase efficiency in systematic reviews.
+Their main objective is to identify ..
+
+The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
+As the relevant publications are screened first, the reviewing process can be quit earlier.
 
@@
 
+### Background
+... starts with a search for potentially relevant publications. 
+This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
+Because the initial set often consists of thousands of papers and the
+
+To gather the findings relevant to answering the research question, a systematic search is performed.
+A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
+From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
+Of all candidate studies only a fraction is relevant [...].
+
+As more and more papers are published and reproducibility crisis has emerged, 
+A systematic search often results in thousands of candidate studies.
+Relevant publications are then identified by screening title and abstract of all candidate studies. 
+This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
+This is a time consuming process that weighs heavily on resources.
+
+Most often the SVM classifier is used, popular and very good results.
+Also lots of other configurations.
+However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
+Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
+
+A solution is ...
+
+It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
+
+To review a specific research area, one starts out with an initial search of thousands of academic papers.
+All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
+With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
+This whole processes costs this and this much time [shelmilt].
+
+#### Technical details
 So you might wonder, how does such an algorithm actually work?
@@
   M = train($\mathcal{L}$)
-  Query x \isin \mathcal{U} (<x, y=?)
+  Query x isin mathcal{U} (<x, y=?)
   oracle <x, y>
@@
 Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.
-
-Most often the SVM classifier is used, popular and very good results.
-Also lots of other configurations.
-However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
-Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
-
-In the current study, we aim at exploring the performance of several classifiers on reducing workload while maintaining performance in abstract screening process.
-This is done by performing simulations on existing systematic reviews.
-Performance is evaluated by how much time can be saved … while maintaining accuracy.
-
-Present research questions. 
-RQ1 – which classifiers perform best? 
--	RQ1a – does classifier performance vary over different research areas? 
-(in what terms does it perform best)
-
-RQ2 different hyperparameter optimizations?
-Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.
-
-The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
-So not only medical sciences.
 
@@
 
-## Background
-[@OMara-Eves2015] literature review
-
-[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
-A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
-In terms of Yu et al, we adopt .CT.
-
-SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
-
-abstrackr
-
-SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
-Also include social sciences data besides medical data.
-
-[@Cohen2006] perceptron-based classifier (neural network)
-
-SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
-in limitations section mentions that LR yields about same results, nb inferior results.
-
-[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
-  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
-The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
-
-Our extensions is that we try different classifiers, on more datasets.
-
+\newpage
+# Methods
 This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
@@
 All simulations were run using through cartesius EINF-156
-Goal: evaluate performance of different models of the ASReview tool. 
-The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
-What would happen if the citation screening would have been performed using asreview? 
-All datasets accompanying the systematic reviews are openly published. 
-We built several machine learning models to perform automated systematic reviews, 
-who are then applied on existing systematic reviews.
 
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
-
-a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
-
-\newpage
-# Methods
 Performance of several machine learning models was demonstrated on six systematic review datasets.  
+study design: retrospective
 
@@
 
+- we look for final inclusions but we screen only the abstracts (do they satisfy the imformation need  (blake (page 19 omara et evs)))
+
+future research: 
+- stopping rule is not discussed
+- computation/retraining time
+
+strengths:
+
+- open data
+- different research areas
+- different models on same dataset
+- different datasets on same model
+
+limitations
+
+future research
+- all models save time, difficult to distinguish performance over datasets, especially when applied on a dataset of which no prior information is known (e.g.
+inclusions isn't known in practice).
+Perhaps go for other criteria like the fastest model, replicate study with computation time?
+
+Simulating the title and abstract screening process, models are evaluted on their capability/speed of detecting the final inclusions. 
+However, in a manual SR these final inclusions are selected after reading the fulltext. Information the text mining tool does not have. 
+To truly assess the added value of such a tool, models should be evaluated on their capability of detecting the abstract inclusions. 
+Call for systematic reviewers to openly publish need for open data containing abstract inclusions, not only final inclusions!
+
 \newpage

### 2020-04-24 simulation_study/hpoptimization/README.Rmd
- update introduction section,

@@
     ggplot(aes(x = value, color = group, fill = group, group = group)) +
-    geom_bar(position="dodge") +
+    geom_bar(position="stack") +
     facet_wrap(vars(param), nrow = 2, scales = "free_x") +
@@
 
+## Results
+Loss plots: Two times the same data, first plot is over trials, second sorted from highest to lowest loss.
+
+Hyperparameters on a continuous scale are plotted as dots in a scatterplot. 
+Discrete hyperparameters are displayed in a barplot
+
+Conclusions: 
+- loss is going down over trials 
+- some datasets go down faster
+- some datasets go down more
+
 # Naive Bayes + TF-IDF
@@
 ## Loss plots
-Two times the same data, first plot is over trials, second sorted from highest to lowest loss.
+
 ```{r}
@@
 # inspect outliers
-hpsets$nb_tfidf %>% filter(param %in% c("balance_param.a", "model_param.alpha")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
+hpsets$nb_tfidf %>% filter(param %in% c("balance_param.a", "model_param.alpha")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb) %>%
+  kable(format = "markdown")
 ```
@@
 svmtfidftrials %>%
+  loss_t()
+
+# parameter values numerical 
+hpsets$svm_tfidf %>%
+  php() +
+  labs(title = "Hyperparameters SVM + TF-IDF")
+
+hpsets$svm_tfidf %>%
+  php_c() 
+```
+# SVM + Doc2Vec
+
+```{r SVM_D2V}
+svmd2vtrials <- readRDS("trials/svm_d2v-trials.RDS")
+
+svmd2vtrials <- svmd2vtrials %>%
+  group_by(datasets) %>%
+  mutate(index = rev(index))
+
+# loss plot by index 
+svmd2vtrials %>% 
+  loss_i()
+
+# loss plot sorted by trial numbers 
+svmd2vtrials %>%
   loss_t()
@@
 ```{r}
-hpsets$lr_tfidf %>% filter(param %in% c("balance_param.a", "model_param.c")) %>% group_by(param) %>% filter(value > 40) %>% select(-ub, -lb)
-hpsets$lr_tfidf %>% filter(param %in% c("model_param.class_weight")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb)
+hpsets$lr_tfidf %>% filter(param %in% c("balance_param.a", "model_param.c")) %>% group_by(param) %>% filter(value > 40) %>% select(-ub, -lb) %>%
+  kable(format = "markdown")
+hpsets$lr_tfidf %>% filter(param %in% c("model_param.class_weight")) %>% group_by(param) %>% filter(value > 1000) %>% select(-ub, -lb) %>%
+  kable(format = "markdown")
 ```

### 2020-04-24 simulation_study/simulation/README.Rmd
- update introduction section,

@@
 
-createLines <- function(cond, d, hp){
+createLines <- function(cond, d, hp, seed = FALSE){
   comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
@@
         cons$hp, cons$c, cons$d)
+
+  if(seed){
+    script <- paste0(script, " --init_seed 42")
+  }
 return(script)
 }
-transfer <- function(hp, c){
+transfer <- function(hp, c, seed = FALSE){
     cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)
+
+    if(seed){
+      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s_seed/%s"
+    } else {
       txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"
-
-    sprintf(txt, hp, c, hp, c)
+    }
+    result <- sprintf(txt, hp, c, hp, c)
+    return(result)
 }
@@
 Fetch github repo on surfsara
+
+ASReview version 0.8.1
 
@@
 transfer("one", condition[c(4,7:9)])
+
 # sctd is not finished yet! 
@@
 # but ace wasn't finished yet! 
-
 ```
@@
 transfer("one", condition[8])
-
-#sims[condition[8], , "one"] <- 3 # output is on harddrive
 ```
 
-### all 
+15.04.2020 
 ```{r}
-# manually transform
-# push to github 
-sims[condition[4], , "all"] <- 1 # configs are on github
+transfer("one", condition[3]) # SCTD 
+sims[condition[8], , "one"] <- 3 # output is on harddrive
 
-```
+# BCTD run ace dataset again 
+createLines(condition[1], "ace", "one") # 8018165
+#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/BCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/BCTD
+sims[condition[1], "ace", "one"] <- 3 # output is on harddrive
 
-```{r}
-# run simulations 
-# lctd_n <- createLines(condition[4], d, "all")
-# write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
-#             row.names = FALSE)
-# names(lctd_n) <- c()
-# #sims[condition[4], d, "all"] <- 2 # simulations are running 
-# 
-# # transfer to harddrive 
-# transfer("n", condition[4])
-#sims[condition[8], , "one"] <- 3 # output is on harddrive
+# RCDD needs to go all over again
+names(rcdd) <- c("8018262", "8018263", "8018264", "8018265", "8018267", "8018268")
+transfer("one", "RCDD")
+
+# SCDD need ace ptsd software virus again
+# ace 8019246
+# ptsd 8019247
+# software 8019250
+# virus 8019251
+transfer("one", "SCDD")
+
+# LCDD only ace 
+createLines(condition[9], "ace", "one") # 8019423
+#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCDD/ace /Volumes/Gerbrich/asreview/simoutput/one/LCDD
+
+# LCTD
+# software 
+createLines("LCTD", "software", "one") # 8020733
+# scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCTD/software /Volumes/Gerbrich/asreview/simoutput/one/LCTD
+
+# SCTD 
+# ace ptsd software
+sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
+names(sctd) <- c("8025808", "8025809", "8025810")
+#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
+createLines("SCTD", "ptsd", "one") # 8066095
+createLines("SCTD", "software", "one")
 ```
@@
 ---
+
+23.04.2020
+Simulations for ace dataset again but now with seed. 
+```{r, message = FALSE}
+seed_ace <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ace", "one", seed = TRUE) %>%
+  noquote()
+names(seed_ace) <- c(".", "8119459", "8119460", "8119461", "8119462", "8119463", "8119464")
+
+seed_nudging <- createLines(condition[c(1, 2, 3,4,7,8,9)], "nudging", "one", seed = TRUE) %>%
+  noquote()
+names(seed_nudging) <- c("8119472", "8119472", "sctd", "")
+
+# transfer sctd's later!(3)
+noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
+# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD
+
+```
 

### 2020-04-25 manuscript/drafts/manuscript.Rmd
First draft introduction section

@@
 output:
+  word_document: default
   pdf_document:
     citation_package: biblatex
-#  word_document: default
 bibliography: asreview.bib
@@
 <!-- question. 
-
-add that htis is a systematic/rigorous process?-->
+add that this is a systematic/rigorous process?-->
 
 Systematic reviews are costly.
-Conducting a systematic review involves the manual screening of thousands of titles and abstracts, identifying publications relevant to asnwering the research question.
-This process typically requires over a year of work from a team of researchers [@Borah2017].
-Besides time-consuming, the process of title and abstract screening is also prone to human error [@Wang2020].
+Conducting a systematic review involves the manual screening of thousands of titles and abstracts, identifying publications relevant to answering the research question.
+An experienced reviewer takes on average 30 seconds to screen one title and abstract, whereas an inexperienced reviewer takes even longer [@Wallace2010].
+Conducting a systematic review typically requires over a year of work from a team of researchers [@Borah2017].
+<!-- Besides time-consuming, the process of title and abstract screening is prone to human error [@Wang2020]. -->
 <!-- (14 to 77,910, trimmed mean 1,286).  -->
@@
 
+Systematic reviewers face competing demands. The production of a systematic review is a time-consuming process, but is often bound to a limited budget and timeframe. 
+Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
+Especially when the need for guidelines is urgent - such as in the context of the current COVID-19 crisis - it is almost impossible to provide a review that is both timely and comprehensive.
+To ensure a timely review, reducing workload in systematic reviews is imperative.
+
 <!-- As the number of scientific publications is growing at an increasing rate [source], the workload in SR is getting heavier.  -->
 
-As time and resources are limited, it is often impossible to meet the strict criteria of a systematic review. 
-Currently, the demand for systematic reviews exceeds the available capacity by far [@Lau2019].
-Moreover, the required resources for a systematic review is making it difficult to timely respond to urgent matters.
-An example of this is the need for clinical guidelines in the current covid-19 crisis. 
-To ensure a timely review, reducing workload in systematic reviews is imperative.
-
-With advances in Artificial Intelligence (AI), a plethora of methods have been proposed to reduce workload in systematic reviews [@Harrison2020].
-More specifically, the field of AI-aided title and abstract screening is rapidly evolving [@OMara-Eves2015].
-Machine Learning (ML) models have been proposed, aiming to assist the reviewer by detecting whether a given publication is relevant or irrelevant to the systematic review.
-Findings suggest such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
-Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Yu2018] [moresources].
-The publications to be screened are ordered by their likeliness of relevance, seeing all relevant publicatoins much earlier on in the screening process when they would have been read in a random order.
-
-Screening prioritization reorders   
-Their objective is to assist the reviewer in the screening process by prioritizing publications most likely to be relevant.
-
-recent research/promising Active Learning.
-
-The current study focus is on reducing workload by prioritizing the most relevant abstracts.
-Presenting the abstracts orders the abstracts by likelihood of relevance, e.g.
-th The reviewer sees the most relevant abstracts first, If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.
-
-The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
-It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
-
-In most recent studies, 
-The latest state-of-the-art methods implement active learning, where the model improves its prediction of relevance based on the reviewers latest decisions in the screening process [@Yu2018; @Miwa2014].
-The ML-model, where the ML-model orders the most
-
-In most recent studies, X has been measured in four different ways.
-The use of qualitative case studies is a well-established approach in …
-
-Their objective is
-
-"Screening is performed in two steps, first preliminarily based on title and abstract,
-then based on full-text." 
-Screening a title + abstracts takes 30 seconds on average, for an experienced reviewer, and longer for inexperienced ones [@Wallace2010].
+With advances in Artificial Intelligence (AI), there has been wide interest in tools to reduce workload in systematic reviews [@Harrison2020].
+More specifically, the field of AI-aided title and abstract screening is rapidly evolving.
+Various learning models have been proposed, aiming to detect whether a given publication is relevant or irrelevant to the systematic review.
+Findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
+<!-- To date, several studies have begun to examine the use of learning algorithms for screening prioritization. -->
+
+Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Cohen2009; @Shemilt2014]. 
+In screening prioritization, the learning model reorders publications to be screened by their likeliness to be relevant, aiming to present the reviewer with the most relevant publications first.
+Such an approach allows for substantial time-savings in the screening process:
+Reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].  
+Moreover, when combined with a stopping criterion, screening prioritization can be used to reduce the number of publications needed to screen. 
+Additionally, several studies report increasing efficiency beyond reducing workload [@OMara-Eves2015].
+
+<!-- assist the reviewer in the screening process -->
+<!-- Several studies have proposed active learning models for screening prioritization -->
+Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2019; @Yu2018; @Miwa2014].
+Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012].
+Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.  
+When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
+The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
+In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
+Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.
+
+<!-- The latest state-of-the-art methods implement active learning, where the model improves  -->
+<!-- The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.  -->
+
+<!-- The algorithm aims to detect whether a given publication is relevant or irrelevant to the systematic review and reorders the publications by their likeliness of relevance; the reviewer sees most relevant papers first!
+-->
+<!-- thereby its predictions can be  is allowed to choose the data points it would like to learn from, thus allowing it to learn more efficiently.  -->
+<!-- Active learning systems attempt to overcome the labeling bottleneck by asking -->
+<!-- queries in the form of unlabeled instances to be labeled by an oracle (e.g., a human -->
+<!-- annotator). -->
+<!--  that a machine learning algorithm can perform better with less training if it is allowed to choose the data from which it learns.
+An active learner may pose "queries," usually in the form of unlabeled data instances to be labeled by an "oracle" (e.g., a human annotator) that already understands the nature of the problem -->
+<!-- in which a model can choose the data points it would like to learn from, thus allowing it to learn more efficiently -->
+<!-- its predictions by interactively querying the user to provide labels to unlabeled data .  -->
+<!-- In title and abstract screening this means that the active learning -->
+<!-- is allowed to improve its predictions by choosing the data it wants to learn from.  -->
+
+<!-- Although the effectiveness of active learning models in reducing workload in title and abstract screening has been extensively studied,  -->
+Although the application of learning models in reducing workload of systematic reviews has been extensively studied, the complex nature of the field is making it difficult to draw overarching conclusions about best practice.
+Moreover, the lack of replication on data outside the biomedical sciences makes it impossible to draw conclusions about the general effectiveness of such technologies [@OMara-Eves2015; @Marshall2020].
+Up to now only few studies have investigated active learning models for screening prioritization, with promising results.
+The question remains how different active learning models for screening prioritization perform across different review contexts.
+Hence, additional evaluations of active learning models are required.
+
+The purpose of this paper is to increase the evidence base of active learning models for reducing workload in title and abstract screening in systematic reviews. 
+Combining latest insights from this area, we present a pipeline of active learning for prioritization screening, called `ASReview`.
+`ASReview` is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies. 
+Working towards a general consensus in this emerging field, this study implements various active learning models (in `ASReview`).
+Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas.
+All data presented in this study are openly published, hoping to facilitate usability and acceptability of AI-assisted title and abstract screening in the field of systematic review.
+
+The remaining part of this paper is organized as follows.
+The Technical Details section will cover the workings of active learning models for study selection in systematic reviews on a conceptual level.
+The method section describes ... The results section reports ... The discusssion section summarises the findings, comments on them and  summarises the main findings, discusses 
+discuss limitations, draw conclusion and
+
+<!-- We demonstrate effectiveness of a generic/flexible tool for assisting researchers in the screening phase..? -->
+<!-- To allow comparison of different models they need to be applied on the same dataset.  -->
+
+<!-- "Screening is performed in two steps, first preliminarily based on title and abstract, -->
+<!-- then based on full-text."  -->
 
@@
 <!-- #### identifying the niche  -->
-Although considerable research has been devoted to the effectiveness of ML-models in reducing workload in title and abstract screening, the complex nature of the field makes it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
-The lack of replication on data outside the biomedical sciences makes it impossible to draw conclusions about the general effectiveness of such technologies [@OMara-Eves2015].
-Taken together, these issues prohibit the adoptation of AI-aided title and abstract screening by systematic reviewers.
-
-[@Marshall2020]
 
@@
 <!-- ##### (listing purpose of new research,  -->
-The current study aims to address these concerns in the following ways:
-
-1) Combining latest insights from the field of AI-aided title and abstract screening, various ML-models for screening prioritization are built.
-2) To evaluate model performance across different review contexts, the models are simulated on multiple datasets from various research areas, of which the data is openly accessible.
-3) To ensure replication and transparency, the simulations are implemented in an open source pipeline called `ASReview`. 
+
 <!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
-
-This study set out to increase the evidence base of ML-models aiming to reduce workload in title and abstract screening in systematic reviews.
-Working towards a general consensus in this emerging field, performance of state-of-the art ML-models is evaluated over various research contexts.
-To further increase usability and acceptability of such models amongst systematic reviewers, the study presents a reproducible workflow.
 
@@
 
-The remaining part of this paper is organized as follows: first, a short review of state-of-the art methods is given.
-Second, the proposed ML-models will be explained on a conceptual level.
-Third, the methods section gives a detailed description of the study design.
-The results section ...
-and last, the results will be discussed.
-
 ---
-
-Active learning is the approach where   [@Settles2002]
-
-Study selection in systematic review process
 

### 2020-04-25 manuscript/drafts/manuscript.tex
First draft introduction section

--- 2020-03-13 manuscript/drafts/manuscript.tex
@@
 \author{Gerbrich Ferdinands}
-\date{1/14/2020}
+\date{22/04/2020}
 
@@
 
+Keywords: Human-Machine interaction, active learning, systematic
+reviews, text classification
+
 \hypertarget{introduction}{%
@@
 
-A convenience sample of 5 existing systematic reviews on varying topics
-was collected.
-
 \hypertarget{results}{%
@@
 
-Systematic Reviews (SR's) are booming - but they are a lot of work
-Various machine learning tools have been proposed to reduce workload in
-abstract screening.
-
-\begin{itemize}
-\tightlist
-\item
-  objectives - to demonstrate effectiveness of ml algorithm in reducing
-  abstract classification for systematic reviews
-\item
-  justification -
-\item
-  background
-\item
-  guidance to reader
-\item
-  summary/conclusion
-\end{itemize}
+Systematic reviews are top of the bill in building evidence in research.
+A systematic review attempts to bring together all studies relevant to
+answer a specific research question \autocite{PRISMA-PGroup2015}.
+Systematic reviews inform practice and policy \autocite{Gough2002} and
+are key in developing clinical guidelines \autocite{Chalmers2007}.
+
+Systematic reviews are costly. Conducting a systematic review involves
+the manual screening of thousands of titles and abstracts, identifying
+publications relevant to answering the research question. An experienced
+reviewer takes on average 30 seconds to screen one title and abstract,
+whereas an inexperienced reviewer takes even longer
+\autocite{Wallace2010}. Conducting a systematic review typically
+requires over a year of work from a team of researchers
+\autocite{Borah2017}.
+
+Systematic reviewers face competing demands. The production of a
+systematic review is a time-consuming process, but is often bound to a
+limited budget and timeframe. Currently, the demand for systematic
+reviews exceeds the available time and resources by far
+\autocite{Lau2019}. Especially when the need for guidelines is urgent -
+such as in the context of the current COVID-19 crisis - it is almost
+impossible to provide a review that is both timely and comprehensive. To
+ensure a timely review, reducing workload in systematic reviews is
+imperative.
+
+With advances in Artificial Intelligence (AI), there has been wide
+interest in tools to reduce workload in systematic reviews
+\autocite{Harrison2020}. More specifically, the field of AI-aided title
+and abstract screening is rapidly evolving. Various learning models have
+been proposed, aiming to detect whether a given publication is relevant
+or irrelevant to the systematic review. Findings suggest that such
+models potentially reduce workload with 30-70\% at the cost of losing
+5\% of relevant publications (95\% recall) \autocite{OMara-Eves2015}.
+
+Screening prioritization is a well-established approach in increasing
+efficiency in title and abstract screening
+\autocite{Cohen2009,Shemilt2014}. In screening prioritization, the
+learning model reorders publications to be screened by their likeliness
+to be relevant, aiming to present the reviewer with the most relevant
+publications first. Such an approach allows for substantial time-savings
+in the screening process: Reviewing relevant publications early
+facilitates a faster transition of those publications to the next steps
+in the review process \autocite{Cohen2009}.\\
+Moreover, when combined with a stopping criterion, screening
+prioritization can be used to reduce the number of publications needed
+to screen. Additionally, several studies report increasing efficiency
+beyond reducing workload \autocite{OMara-Eves2015}.
+
+Recent studies have demonstrated the effectiveness of screening
+prioritization by means of active learning models
+\autocite{Yu2019,Yu2018,Miwa2014}. Active learning is when the model can
+iteratively improve its predictions by allowing the model to choose the
+data from which it can learn \autocite{Settles2012}. Active learning has
+proven to be an efficient strategy in large datasets where labels are
+scarce, which makes identifying relevant publications an ideal candidate
+for such models.\\
+When applied in the screening process, an active learning model can
+iteratively improve its relevancy predictions by interacting with the
+reviewer. The model decides which publication it wants the reviewer to
+screen next, who then provides the model with a label (`relevant',
+`irrelevant'). In this active learning cycle, the model can
+incrementally improve its predictions on the relevancy of the remaining
+unlabeled publications. Based on previous labelling decisions by the
+reviewer, the model constantly reorders the remaining publications in
+the dataset.
+
+Although the application of (active) learning models in reducing
+workload of systematic reviews has been extensively studied, the complex
+nature of the field is making it difficult to draw overarching
+conclusions about best practice. Moreover, the lack of replication on
+data outside the biomedical sciences makes it impossible to draw
+conclusions about the general effectiveness of such technologies
+\autocite{OMara-Eves2015}. The question remains how different active
+learning models for screening prioritization perform across different
+review contexts. Hence, additional evaluations of active learning models
+are required.
+
+The purpose of this paper is to increase the evidence base of active
+learning models for reducing workload in title and abstract screening in
+systematic reviews. Combining latest insights from this area, we present
+a pipeline of active learning for prioritization screening, called
+\texttt{ASReview}. \texttt{ASReview} is an open source and generic tool
+such that users can adapt and add modules as they like, encouraging
+fellow researchers to replicate findings from previous studies. Working
+towards a general consensus in this emerging field, this study
+implements various active learning models (in \texttt{ASReview}). Models
+are evaluated by performing a simulation on data from six existing
+systematic reviews from various research areas. All data presented in
+this study are openly published, hoping to facilitate usability and
+acceptability of AI-assisted title and abstract screening in the field
+of systematic review.
+
+The remaining part of this paper is organized as follows. The Technical
+Details section will cover the workings of active learning models for
+study selection in systematic reviews on a conceptual level. The method
+section describes \ldots{} The results section reports \ldots{} The
+discusssion section summarises the findings, comments on them and
+summarises the main findings, discusses discuss limitations, draw
+conclusion and
+
+\autocite{Marshall2020}
 
@@
 
-This study is about how machine learning algorithms can increase
-efficiency in systematic reviews. I will write about what SRs are, and
-how workload can be reduced.
-
-Systematic reviews are top of the bill in research. As more and more
-papers are published and reproducibility crisis has emerged, science
-calls for more meta. It is important reflect on research by giving an
-overview of research areas which is typically done by a systematic
-review {[}\ldots{]}. Performing a systematic review is a tedious and
-time-consuming task. To review a specific research area, one starts out
-with an initial search of thousands of academic papers. All these papers
-abstracts need to be screened to find an initial batch of possibly
-relevant papers. With now hopefully only a couple of hundred papers
-left, the researcher needs to read these papers full-text to arrive at a
-final selection of papers that are relevant for the final systematic
-review {[}this is prisma process?{]}. This whole processes costs this
-and this much time {[}shelmilt{]}.
-
-The stage of abstract screening where abstracts are systematically
-screened is where a lot is to be gained. This stage is the target of
-possible learning algorithms that can assist the reviewer in selecting
-the relevant papers. Together with the reviewer /human machine
-interaction. The algorithm aims to compute which papers in the pool need
-to be excluded and which need to be included, based on the reviewers
-decisions. It learns from the reviewers decisions and asks the reviewer
-to provide more labels, incrementally improving its class predictions.
-
-The goal of the algorithm defined in the current study is to reduce to
-number of abstracts needed to screen (maybe not right term, bit
-biomedical). To be more specific, the algorithm aims to present the
-reader with the primary studies as soon as possible. This means that at
-some point you probably have seen all relevant abstracts and are only
-viewing excluded papers, which means you can stop reviewing much earlier
-(theoretically spoken). Also reviewing is now much more fun. As compared
-to when you have to review all abstracts and you perhaps see only one
-relevant abstract every other week/day.
-
-So you might wonder, how does such an algorithm actually work? Active
-learning strategy, starting with a pool of unlabeled abstracts (U). The
-reviewer starts labeling some instances in U, creating L. The algorithm
-utilizes L to predict labels for all abstracts (classifier), by using a
-set of features from the papers called X, for example the text in the
-abstract (feature extraction method). Now, it made an initial
-classification. The algorithm now aims to improve its classification by
-which paper from U will be presented to the reviewer next. By labeling
-the next paper, the reviewer provides the algorithm with new information
-which the algorithm uses to update its prediction.
-
-We approach asr as a classification problem: All papers obtained in the
-systematic search form a pool of instances x. All instances x need to be
-classified, e.g.~we want to give them a label y. all x are now part of
-U,. Binary classification, either inclusion or exclusion. We want to
-classify based on some features from the instances \(x\), feature vector
-\(\mathbf{X}\).
-
-By starting of with L, the algorithm utilizes characteristics of X to
-predict labels in U.
-
-We want to classify the papers in Where the whole collection of papers
-in the systematic search form a pool of instances x, with unknown label
-y. \textless x,y\textgreater.
-
-\begin{verbatim}
-input: a pool of unlabeled abstracts $\mathcal{U}$ 
-oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
-
-  M = train($\mathcal{L}$)
-  query x \isin
-
-\end{verbatim}
-
-\begin{itemize}
-\item
-  pool unlabeled abstracts \(\mathcal{U}\)
-\item
-  labeled data set \(\mathcal{L}\),
-\item
-  instance \(x\), label \(y\)
-\item
-  utility measure \(\phi_A(\cdot)\)
-\item
-  \(x^*_A\) best query instance according to \(\phi_A(\cdot)\)
-\end{itemize}
-
-Now there are a few technical details. Many different versions of such
-algorithms exist. Many of such algorithms have been described in the
-active learning literature and have been applied in the systematic
-reviewing process. Not exhaustive, but the algorithm can apply many
-different strategies to arrive at its predictions, which can be divided
-in following parameters: classifier, feature extraction strategy,
-balancing, query strategy.
-
-Most often the SVM classifier is used, popular and very good results.
-Also lots of other configurations. However, other classifiers have not
-been tested a lot (polygon thing by cohe, naïve bayes and random forest
-by \ldots), but mostly SVM still. Also, most research in the medical
-sciences (well there are some exceptions of course {[}conversation
-between cohen and matwill{]}
-
-In the current study, we aim at exploring the performance of several
-classifiers on reducing workload while maintaining performance in
-abstract screening process. This is done by performing simulations on
-existing systematic reviews. Performance is evaluated by how much time
-can be saved \ldots{} while maintaining accuracy.
-
-Present research questions. RQ1 -- which classifiers perform best? -
-RQ1a -- does classifier performance vary over different research areas?
-(in what terms does it perform best)
-
-RQ2 different hyperparameter optimizations? Classifiers come with
-hyperparameters. We have to make a choice on how to set these
-hyperparameters. What we do is create 3 sets, optimizing in three ways,
-aggregate results obtained.
-
-The goal is to gain insight in classifiers other than the widely applied
-SVM, overall various research areas. So not only medical sciences.
-
-To perform all these computations the research was carried out using the
-ASReview software by Utrecht University, which has a simulation mode
-that you can just input your labelled review file into and perform a
-simulation study with it. To be found on GitHub. It has many adjustable
-components/is very versatile.
-
-Then if we still have time left we explore the effect of another feature
-extraction method, namely doc2vec. This might possibly increase
-performance as it performs better at grasping structure/hidden
-relations/hierarchy between words in the texts. So, it could be
-interesting in more `fuzzy' research areas. A downside is that it takes
-more computing time.
-
-Then if there's even more time we might want to compare a different
-balance strategy.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-A SR can be divided into phases. Everything starts with a
-\textbf{systematic search}, leading to then citation screening is
-performed, then full-text screening \autocite{PRISMA-PGroup2015}
-
-What must be the objective of our tool?: It is the tedious task citation
-screening part where loads of time can be saved.
-
-models are designed in a `realistic' way (you have some inclusions)
-
-Selecting papers is a two-step process: abstract \& fulltext screening
-
-Binary classification problem. predict whether a paper in the pool is an
-inclusion or exclusion, based on labeled instances from \(\mathcal{L}\)
-and use training data to understand how input variables are related to
-class.
-
-We're building active learning model who takes X as an input an predicts
-class using labels from training set. Model improves by deciding asking
-more information from the reviewer (oracle), accounting for imbalance.
-
-\hypertarget{assumptions}{%
-\paragraph{Assumptions}\label{assumptions}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
-  decisions of the original SR are \textbf{ground truth} (benchmark)
-  (oracle)
-\end{enumerate}
-
-The inclusion rate is \ldots{} data is imbalanced. what is the
-philosophy False negatives must be avoided \ldots{} The cost of a false
-negative outweighs the cost of a false positive. Note that we assume the
-oracle/original user to hold the truth. This is of course not always the
-case.
-
-There are two classes in the data: exlusions and inclusions. The
-inclusions are clearly the minority class.
-
-Datasets from the medical and social sciences, software engineering and
-public administration. Medical sciences SRs are viewed as more
-`strict'/`structured' and social sciences more messy.
-
-\hypertarget{active-learning-for-systematic-reviews}{%
-\subsection{active learning for systematic
-reviews}\label{active-learning-for-systematic-reviews}}
-
-corpus = all the text:
-
-Active learning = increasing classification performance with every
-query. The query strategy determines the way unlabeled papers are
-queried to the researcher.
-
-\autocite{modAL2018}
-
-RQ1 - what are good classifiers RQ2 - what are good optimization
-strategies
+\hypertarget{summarise-models-used}{%
+\paragraph{summarise models used}\label{summarise-models-used}}
+
+\hypertarget{propose-pipeline}{%
+\paragraph{propose pipeline}\label{propose-pipeline}}
+
+\hypertarget{and-specific-components}{%
+\subparagraph{and specific components?}\label{and-specific-components}}
+
+\hypertarget{summarise-datasets-tested}{%
+\paragraph{summarise datasets tested}\label{summarise-datasets-tested}}
+
+\hfill\break
+\hfill\break
 
@@
 
-This study was approved by the Ethics Committee of the Faculty of Social
-and Behavioural Sciences of Utrecht University, filed as an amendement
-under study 20-104.
-
-All simulations were run using through cartesius EINF-156
-
-\newpage
-
-\hypertarget{methods-1}{%
-\section{Methods}\label{methods-1}}
-
 Goal: evaluate performance of different models of the ASReview tool. The
@@
 have been performed using asreview? All datasets accompanying the
-systematic reviews are openly published.
+systematic reviews are openly published. We built several machine
+learning models to perform automated systematic reviews, who are then
+applied on existing systematic reviews.
+
+When no balancing is applied, the training data set = labeled data set
+\(\mathcal{L}\) The model can query the labels, who serve as the
+reviewer, active learning then perform active learning to detect
+inclusions.
+
+a machine learning-based citation classification tool to reduce workload
+in systematic reviews of drug class efficacy. Using a perceptron
+classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in
+\autocite{Cohen2006}. (5x2 crossvalidation). Can we beat this? The data
+
+Openness, reproducible,
+
+Benefits:
+
+Adopting some sort of stopping criterion (outside scope of the current
+thesis) the reviewer can quit reviewing after having read only a
+fraction of candidate studies. meaning the screening process can be
+finished after reading a fraction of all candidate studies. Saving hours
+of time and resources.
+
+paper organization:
+
+The goal is to gain insight in classifiers other than the widely applied
+SVM, overall various research areas. So not only medical sciences.
+
+Although considerable research has been devoted to \ldots, less
+attention has been paid to the comparison of different classifiers. Few
+studies have evaluated different classifiers in any systematic way
+different models to use haven't been investigated in a systematic way
+(only in software engineering)
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  the lack of replication of methods is making it impossible to draw any
+  overall conclusions about best practice/ best approaches of the
+  problem of reducing workload in screening.
+\item
+  screening prioritization is appealing to systematic reviewers because
+  \ldots{}
+\item
+\item
+  implemantation: usabliity and acceptability of such tools amongst
+  researchers conducting a systematic review.
+\end{enumerate}
+
+lack of studies investigating the effect of different methods over
+different research areas. (yu but only software engineering, miwa
+perhaps?) There is also a significant lack of examples outside of
+healthcare with the exception of one example in software engingeering
+
+However, there is a need for consensus () and transparancy?
+
+So far, however, there has been little discussion about the different
+classifiers to be used. Support Vector Machine has been the default in
+almost all studies.
+
+Several algorithms to assist the reviewer in the abstract screening
+process have been proposed. (they are available in many shapes/sorts).
+
+\hypertarget{indicating-the-structure-of-the-writing}{%
+\subparagraph{indicating the structure of the
+writing)}\label{indicating-the-structure-of-the-writing}}
+
+principle findings:
+
+For truly evaluate the effectiveness of such methods,
+
+automatically (by machine learning techniques) In the current study we
+focus on the effectiveness of different machine learning models in
+reducing workload in the citation screening process. Assisting the
+reviewer. Combining various machine learning techniques. Combining
+recent insights on, we propose ASReview. Approaching the citation
+screening phase as a classfication task, The benefit is that ASReview is
+dynamic, user can decide open source, multiple classifiers and other
+settings,
+
+The current study focus is on reducing workload by prioritizing the most
+relevant abstracts. Presenting the abstracts orders the abstracts by
+likelihood of relevance, e.g.~th The reviewer sees the most relevant
+abstracts first, If the model performs well all relevent abstracts will
+be seen much earlier than when abstracts are read at a random order.
+
+Such a solution can save time and resources. Time saving is not the only
+benefit: and help to minimize bias..
+
+\hypertarget{proposed-solution}{%
+\paragraph{Proposed solution}\label{proposed-solution}}
+
+This study is about how machine learning models can increase efficiency
+in systematic reviews. Their main objective is to identify ..
+
+The strategy to reduce workload proposed in the current study is by
+prioritizing publications that are deemed most relevant to the
+systematic review. As the relevant publications are screened first, the
+reviewing process can be quit earlier.
+
+The stage of abstract screening where abstracts are systematically
+screened is where a lot is to be gained. This stage is the target of
+possible learning algorithms that can assist the reviewer in selecting
+the relevant papers. Together with the reviewer /human machine
+interaction. The algorithm aims to compute which papers in the pool need
+to be excluded and which need to be included, based on the reviewers
+decisions. It learns from the reviewers decisions and asks the reviewer
+to provide more labels, incrementally improving its class predictions.
+
+The goal of the algorithm defined in the current study is to reduce to
+number of abstracts needed to screen (maybe not right term, bit
+biomedical). To be more specific, the algorithm aims to present the
+reader with the primary studies as soon as possible. This means that at
+some point you probably have seen all relevant abstracts and are only
+viewing excluded papers, which means you can stop reviewing much earlier
+(theoretically spoken). Also reviewing is now much more fun. As compared
+to when you have to review all abstracts and you perhaps see only one
+relevant abstract every other week/day.
+
+\hypertarget{background-1}{%
+\subsubsection{Background}\label{background-1}}
+
+\ldots{} starts with a search for potentially relevant publications.
+This initial set of candidate studies need to be manually screened to
+identify the publications relevant for answering the research question.
+Because the initial set often consists of thousands of papers and the
+
+To gather the findings relevant to answering the research question, a
+systematic search is performed. A systematic search starts with
+collecting all publications that meet pre-specified eligibility
+criteria. From this collection of candidate studies the researcher has
+to identify the publications relevant for answering the research
+question. Of all candidate studies only a fraction is relevant
+{[}\ldots{]}.
+
+As more and more papers are published and reproducibility crisis has
+emerged, A systematic search often results in thousands of candidate
+studies. Relevant publications are then identified by screening title
+and abstract of all candidate studies. This screening process is a
+manual task often executed by multiple reviewers to ensure reliability.
+This is a time consuming process that weighs heavily on resources.
+
+Most often the SVM classifier is used, popular and very good results.
+Also lots of other configurations. However, other classifiers have not
+been tested a lot (polygon thing by cohe, naïve bayes and random forest
+by \ldots), but mostly SVM still. Also, most research in the medical
+sciences (well there are some exceptions of course {[}conversation
+between cohen and matwill{]}
+
+A solution is \ldots{}
+
+It is important reflect on research by giving an overview of research
+areas which is typically done by a systematic review {[}\ldots{]}.
+
+To review a specific research area, one starts out with an initial
+search of thousands of academic papers. All these papers abstracts need
+to be screened to find an initial batch of possibly relevant papers.
+With now hopefully only a couple of hundred papers left, the researcher
+needs to read these papers full-text to arrive at a final selection of
+papers that are relevant for the final systematic review {[}this is
+prisma process?{]}. This whole processes costs this and this much time
+{[}shelmilt{]}.
+
+\hypertarget{technical-details}{%
+\paragraph{Technical details}\label{technical-details}}
+
+So you might wonder, how does such an algorithm actually work? Active
+learning strategy, starting with a pool of unlabeled abstracts (U). The
+reviewer starts labeling some instances in U, creating L. The algorithm
+utilizes L to predict labels for all abstracts (classifier), by using a
+set of features from the papers called X, for example the text in the
+abstract (feature extraction method). Now, it made an initial
+classification. The algorithm now aims to improve its classification by
+which paper from U will be presented to the reviewer next. By labeling
+the next paper, the reviewer provides the algorithm with new information
+which the algorithm uses to update its prediction.
+
+We approach asr as a classification problem: All papers obtained in the
+systematic search form a pool of instances x. All instances x need to be
+classified, e.g.~we want to give them a label y. all x are now part of
+U,. Binary classification, either inclusion or exclusion. We want to
+classify based on some features from the instances \(x\), feature vector
+\(\mathbf{X}\).
+
+By starting of with L, the algorithm utilizes characteristics of X to
+predict labels in U.
+
+We want to classify the papers in Where the whole collection of papers
+in the systematic search form a pool of instances x, with unknown label
+y. \textless x,y\textgreater.
+
+\begin{verbatim}
+input:  
+    a pool of unlabeled abstracts $\mathcal{U}$ 
+    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
+
+  M = train($\mathcal{L}$)
+  Query x isin mathcal{U} (<x, y=?)
+  oracle <x, y>
+
+\end{verbatim}
+
+\begin{itemize}
+\item
+  pool unlabeled abstracts \(\mathcal{U}\)
+\item
+  labeled data set \(\mathcal{L}\),
+\item
+  instance \(x\), label \(y\)
+\item
+  utility measure \(\phi_A(\cdot)\)
+\item
+  \(x^*_A\) best query instance according to \(\phi_A(\cdot)\)
+\end{itemize}
+
+Now there are a few technical details. Many different versions of such
+algorithms exist. Many of such algorithms have been described in the
+active learning literature and have been applied in the systematic
+reviewing process. Not exhaustive, but the algorithm can apply many
+different strategies to arrive at its predictions, which can be divided
+in following parameters: classifier, feature extraction strategy,
+balancing, query strateg y.
+
+To perform all these computations the research was carried out using the
+ASReview software by Utrecht University, which has a simulation mode
+that you can just input your labelled review file into and perform a
+simulation study with it. To be found on GitHub. It has many adjustable
+components/is very versatile.
+
+Then if we still have time left we explore the effect of another feature
+extraction method, namely doc2vec. This might possibly increase
+performance as it performs better at grasping structure/hidden
+relations/hierarchy between words in the texts. So, it could be
+interesting in more `fuzzy' research areas. A downside is that it takes
+more computing time.
+
+Then if there's even more time we might want to compare a different
+balance strategy.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+A SR can be divided into phases. Everything starts with a
+\textbf{systematic search}, leading to then citation screening is
+performed, then full-text screening \autocite{PRISMA-PGroup2015}
+
+What must be the objective of our tool?: It is the tedious task citation
+screening part where loads of time can be saved.
+
+models are designed in a `realistic' way (you have some inclusions)
+
+Selecting papers is a two-step process: abstract \& fulltext screening
+
+Binary classification problem. predict whether a paper in the pool is an
+inclusion or exclusion, based on labeled instances from \(\mathcal{L}\)
+and use training data to understand how input variables are related to
+class.
+
+We're building active learning model who takes X as an input an predicts
+class using labels from training set. Model improves by deciding asking
+more information from the reviewer (oracle), accounting for imbalance.
+
+The researcher has some prior knowledge about the pool, some papers
+ought to be included in the SR.
+
+\hypertarget{assumptions}{%
+\paragraph{Assumptions}\label{assumptions}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  decisions of the original SR are \textbf{ground truth} (benchmark)
+  (oracle)
+\end{enumerate}
+
+The inclusion rate is \ldots{} data is imbalanced. what is the
+philosophy False negatives must be avoided \ldots{} The cost of a false
+negative outweighs the cost of a false positive. Note that we assume the
+oracle/original user to hold the truth. This is of course not always the
+case.
+
+There are two classes in the data: exlusions and inclusions. The
+inclusions are clearly the minority class.
+
+Datasets from the medical and social sciences, software engineering and
+public administration. Medical sciences SRs are viewed as more
+`strict'/`structured' and social sciences more messy.
+
+\hypertarget{active-learning-for-systematic-reviews}{%
+\subsection{active learning for systematic
+reviews}\label{active-learning-for-systematic-reviews}}
+
+corpus = all the text:
+
+Active learning = increasing classification performance with every
+query. The query strategy determines the way unlabeled papers are
+queried to the researcher.
+
+\autocite{modAL2018}
+
+RQ1 - what are good classifiers RQ2 - what are good optimization
+strategies
+
+\newpage
+
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
+
+This study was approved by the Ethics Committee of the Faculty of Social
+and Behavioural Sciences of Utrecht University, filed as an amendement
+under study 20-104.
+
+All simulations were run using through cartesius EINF-156
+
+Performance of several machine learning models was demonstrated on six
+systematic review datasets.\\
+study design: retrospective
+
+\hypertarget{models}{%
+\subsection{Models}\label{models}}
+
+\emph{x} machine learning models (\(M\)) were built. The models consist
+of multiple components, of which the classifier and the feature
+extraction strategy varied over the models.
+
+\hypertarget{classifiers}{%
+\paragraph{Classifiers}\label{classifiers}}
+
+Every model applies a classifier \(c\) to predict the relevance of
+publications in the data. The classfiier predicts the class of a
+publication in the dataset expediting a training dataset
+\(\mathcal{L}\), predicts the class of an instance given input features
+\(\mathbf{X}\)
+
+Logistic Regression (LR) - L2-regularized logistic regression. Logistic
+models the posterior directly, naive bayes has higher bias but lower
+variance, logistic might perform better when trainign set increases.
+\autocite{Ng2002} Naive Bayes (NB) - Naive Bayes assumes all features
+are independent given the class value. This is obviously not the case
+but still the algorithm performs impressively \autocite{Zhang2004}.
+Especially at \ldots{} tasks.
+
+Random Forests (RF) is where a large number of decision trees are fit on
+bootstrapped samples of the original data. All trees cast a vote on the
+class, which are aggregated into a class prediction for each input
+\(\mathbf{X}\) \autocite{Breiman2001}.
+
+Support Vecor Machine (SVM) - finds a multidimensional hyperplane to
+separate classes. \autocite{Tong2001}
+
+\hypertarget{word-representation}{%
+\paragraph{Word representation}\label{word-representation}}
+
+To predict the class of a publication class (e.g.~whether a publication
+should be included or excluded), the classifier uses information from
+the publications in the dataset. Examples of such information are titles
+and abstracts. However, the classifier cannot predict the publication
+class from titles and abstracts as they are. Their textual content to
+needs to be mapped to feature vectors. This process of numerically
+representing textual content is called `word embeddings'.
+
+A classical example of word embeddings a `bag of words' representation.
+For each text in the data set, the number of occurrences of each word is
+stored. This leads to n features, where n is the number of distinct
+words in the texts \autocite{scikit-learn}. The bag-of-words method is
+simplistic and will highly value often occuring but otherwise
+meaningless words such as ``and''. Term-frequency Inverse Document
+Frequency (TF-IDF) \autocite{Ramos2003} circumvents this problem by
+adjusting a term frequency in a text with the inverse docuement
+frequency, the frequency of a given word in the entire data set.
+
+The model expedits features of previously labeled publications and Based
+on features of the previously labeled inclusions and exclusions, the
+model
+
+The features used are title and abstract from every publication. - this
+is what is prescribed by prisma, (check!)
+
+(TF-IDF) (Doc2Vec)
+
+\hypertarget{fixed-components}{%
+\paragraph{Fixed components}\label{fixed-components}}
+
+All models \(M\) apply the same query strategy of certainty sampling, in
+which the presented publication is always the one of which the model is
+most certain for it to be relevant.
+
+To decrease the class imbalance in the training data, the model
+rebalances the training set by Dynamic Supersampling (DS). DS decreases
+the number of irrelevant papers in the training data, whereas the number
+of relevant papers are increased (by copy) such that the total number of
+samples remains the same. The ratio between relevant and irrelevant
+papers is not fixed, but dynamically updated and depends on the number
+of training samples, the total number of publications and the ratio
+between relevant and irrelevant publications.
 
@@
 
-The algorithm will be tested on five systematic reviews from various
-research areas. test datasets serve as systematic search results, then
-perform active learning to detect inclusions.
+Six Systematic Reviews from various research areas were used to simulate
+the automated systematic review process. Data were preprocessed from the
+original source into a test dataset, containing all publications
+obtained in the systematic search. The test datasets are labelled
+indicating the relevant and irrelevant publications. Using these labels,
+a computer simulation of an automated systematic review can be performed
+on the systematic review data.
+
+The test datasets contain title information on all publications obtained
+in the search strategy. The instances in the data consist of a title and
+an abstract and were labeled to indicate which publications were
+included in the systematic review. Instances with missing abstracts and
+duplicate instances were removed from the data. The data preprocessing
+scripts can be found on the GitHub\footnote{\url{https://github.com/GerbrichFerdinands/asreview-thesis}}
 
@@
 
-a machine learning-based citation classification tool to reduce workload
-in systematic reviews of drug class efficacy. Using a perceptron
-classifier, \href{mailto:WSS@95}{\nolinkurl{WSS@95}}\% = 56.61 in
-\autocite{Cohen2006}. (5x2 crossvalidation). Can we beat this? The data
-
 The \emph{software} dataset is retrieved from \autocite{Yu2018a}, who
@@
 (Table 1).
-
-The raw datafiles published with the SRs were preprocessed into a test
-dataset. The test datasets contain title information on all citations
-obtained in the search strategy. The instances in the data consist of a
-title, an abstract and were labeled to indicate which citations were
-included in the systematic review. Instances with missing abstracts were
-removed. Duplicate instances were removed. Preprocessing scripts can be
-found on the GitHub\footnote{\url{https://github.com/GerbrichFerdinands/asreview-thesis}}
 
@@
 ace & 2544 & 41 & 1.61 & 2235 & 41 & 1.83\\
-nudging & 2006 & 100 & 4.99 & 1848 & 100 & 5.41\\
+nudging & 2006 & 100 & 4.99 & 1847 & 100 & 5.41\\
 ptsd & 6185 & 38 & 0.61 & 5031 & 38 & 0.76\\
 software & 8911 & 104 & 1.17 & 8896 & 104 & 1.17\\
-wilson & 3453 & 26 & 0.75 & 2334 & 24 & 1.03\\
+wilson & 3453 & 26 & 0.75 & 2333 & 23 & 0.99\\
 \bottomrule
 \end{tabu}
-
-\hypertarget{models}{%
-\subsection{Models}\label{models}}
-
-Five different active learning models were build. Every model \(m\) was
-used to perform an automated systematic review on SR dataset \(d\). The
-models all apply a different classifier \(c\) with its own set of
-(hyper)parameters \(h\).
-
-\hypertarget{classifiers}{%
-\paragraph{Classifiers}\label{classifiers}}
-
-The classifier predicts the class of all papers, given the training
-dataset/labeled data set \(\mathcal{L}\).
-
-Given the labels and some features from all abstracts in the pool, the
-classifier To predict whether a paper should be an exclusion or an
-inclusion, different classifiers
-
-Logistic Regression (L) -
-
-Naive Bayes (B) - predicts the class of an instance given input features
-\(\mathbf{X}\). Naive Bayes assumes all features are independent given
-the class value. This is obviously not the case but still the algorithm
-performs impressively \autocite{Zhang2004}. Especially at \ldots{}
-tasks.
-
-Random Forests (R) is where a large number of decision trees are fit on
-bootstrapped samples of the original data. All trees cast a vote on the
-class, which are aggregated into a class prediciton for each input
-\(\mathbf{X}\) \autocite{Breiman2001}.
-
-Support Vecor Machine (S) - finds a multidimensional hyperplane to
-separate classes. \autocite{Tong2001}
-
-Dense Neural Network (N) -
-
-Besides \(c\), components of \(m\) are fea
-
-To summarize, every model \(m\) consists of the following key
-components: classifier, feature extraction strategy, query strategy,
-balance strategy.
-
-For example \(M_1\) BTMD (naive bayes, tfidf, certainty sampling, double
-balance) STMD
-
-\hypertarget{word-representation}{%
-\paragraph{Word representation}\label{word-representation}}
-
-To be able to predict whether a paper needs to be included or excluded
-(e.g.~to predict class), the classifier needs some features from the
-papers.\\
-As features we use the title and abstract from every paper - this is
-what is prescribed by prisma, (check!) The classifier cannot predict the
-paper class from the raw titles and abstracts as they are. Therefore,
-the content of the texts needs to be transformed into numerical
-representations called feature vectors.
-
-A classical example is a `bag of words' representation. For each each
-text, the number of occurrences of each word is stored. This leads to n
-features, where n is the number of distinct words in the texts
-\autocite{scikit-learn}. The bag-of-words method is simplistic and will
-highly value often occuring but otherwise meaningless words such as
-``and''. Term-frequency Inverse Document Frequency (TF-IDF)
-\autocite{Ramos2003} circumvents this problem by adjusting a term
-frequency in a text with the inverse docuement frequency, the frequency
-of a given word in the entire corpus.
-
-\begin{enumerate}
-\def\labelenumi{(\Alph{enumi})}
-\setcounter{enumi}{19}
-\item
-  \begin{enumerate}
-  \def\labelenumii{(\Alph{enumii})}
-  \setcounter{enumii}{3}
-  \tightlist
-  \item
-  \end{enumerate}
-\end{enumerate}
-
-\hypertarget{the-next-abstract-to-be-queried}{%
-\paragraph{The next abstract to be
-queried}\label{the-next-abstract-to-be-queried}}
-
-The model has various ways of deciding which instance should be queried
-next.
-
-\hypertarget{rebalancing-the-training-set}{%
-\paragraph{Rebalancing the training
-set}\label{rebalancing-the-training-set}}
-
-To account for class imbalance in the data, the model can apply several
-strategies to rebalance the training set.
-
-A reweighting strategy is applied where inclusions (the minority class)
-are weighted more heavily than the exclusions.
-
-When no balancing is applied, the training data set = labeled data set
-\(\mathcal{L}\)
-
-\hypertarget{starting-point}{%
-\paragraph{Starting point}\label{starting-point}}
-
-The initial training set consists of 5 inclusions and 5 exclusions,
-randomly sampled from the dataset. We use 5 inclusions and exclusions as
-we assume the researcher has some prior knowledge on this. The
-researcher has some prior knowledge about the pool, some papers ought to
-be included in the SR.
-
-\begin{verbatim}
-c = naivebayes
-f = tfidf
-q = max
-n_prior_included = 5
-n_prior_excluded = 5
-\end{verbatim}
-
-\hypertarget{retraining}{%
-\paragraph{Retraining}\label{retraining}}
-
-We can choose to retrain the model after labeling \(n\) instances. -
-n\_instances=10 (number of papers each query)
-
-\hypertarget{simulations}{%
-\subsection{Simulations}\label{simulations}}
-
-To evaluate performance of the five models described above, the model is
-used to simulate five existing systematic reviews.
 
@@
 
-For every model*data combination, 3 sets of hyperparameters are
-generated to \ldots{} parallel Every model has its own hyperparameters.
-For every model, the hyperparameters are optimized three times, arriving
-at three versions of the model:
-
-We now have 75 combinations. for every for every model (5), for every
-dataset (5) and for every set of optimized hyperparameters (3), a
-simulation study consisting trials is performed. From these \(5*5*3=75\)
-simulation studies, performance of the different models is evaluated.
-
-A simulation is of one model on one dataset. The simulation is repeated
-for 10 trials \(t\).
-
-Every simulation study consists of 10 trials, to account for the
-randomness of prior inclusions and exclusions. So every trial the prior
-inclusions and exclusions are randomly selected. Results are aggregated
-(?)
+Every model component contains hyperparameters, leading to a unique set
+of hyperparameters for each model. To maximize model performance, we
+need to find optimal values for the hyperparameters. For every model the
+optimal hyperparameter values are determined by optimizing on the data
+\(d\). The hyperparameters are optimized by running several hundreds of
+optimization trials, in which hyperparameter values are sampled from
+their possible parameter space. A description of all hyperparameters and
+their sample space can be found in the appendix.
+
+Maximum model performance is defined as the average time it takes to
+find an inclusion in the data, or more specific: the loss function
+minimizes the average number of papers needed to screen to find an
+inclusion (e.g.~the area above the curve in the inclusion plot).
+
+The optimization data \(d\) consists of (a subset from) the six
+systematic review datasets \(D\) mentioned above. Three different
+approaches in composing \(d\) are explored:
+
+\begin{itemize}
+\tightlist
+\item
+  \textbf{one}, where hyperparameters are optimized on only one of the
+  six datasets, \(d \in D\). Such hyperparameters are expected to lead
+  to maximum performance in the same dataset \(d\).
+\item
+  \textbf{n}, where hyperparameters are optimized on all six data sets,
+  \(d = D\). This optimization approach intends to serve in producing
+  the most optimal hyperparameters overall.
+\item
+  \textbf{n-1}, where hyperparameters are optimized on all six datasets
+  but one, \(d \subset D\). Serving as a sensitivity analysis for the
+  former condition, e.g.~how sensitive are the hyperparamters. also as a
+  cross-validation later on: hyperparameters obtained by training data,
+  test data is never seen before. where d are all datasets but the one
+  where we want to simulate later on. This results in \(6+6+1=13\) sets
+  of hyperparameters for every model.
+\end{itemize}
+
+Results were visually inspected to check if an optimum (minimal loss)
+has been reached. More trials were run if the loss still seemed to go
+down at a quick pace.
+
+The hyperparameter values that were found to lead to a minimum loss
+value were visually inspected.
+
+\hypertarget{optimization-results}{%
+\subsubsection{Optimization results}\label{optimization-results}}
+
+For every model, 13 sets of hyperparameters were optimized.
+
+\emph{to include: plotting the loss reduction over trials}
+
+Optimal values of the hyperparameters were visually inspected.
+
+As an example, the hyperparameters of the RF\_TF-IDF model are presented
+in Figure 1. A panel displays the optimal values for a certain
+hyperparameter, where the blue colored dots represent the \textbf{one}
+condition, the green dots the \textbf{n-1} condition and the orange dot
+represents the optimal hyperparameter value when optmizing over all
+datasets (\textbf{n}). The x-axis represents the possible parameter
+space where the vertical grey lines mark the boundaries of the
+hyperparameter space (if possible). Note that the feature parameters
+ngram\_max, split\_ta, use\_keywords and model parameters max\_features
+and n\_estimators are categorical.
+
+Overall, the optimal values are distributed over the parameter space.
+Outlying values all belong to the \textbf{one} condition where
+optimization was dependent on one dataset only. Fore example, the
+class\_weight parameter has an outlying value of 11.3 that belongs to
+the nudging dataset. (Why this is the case I can only speculate, but it
+is worth mentioning that this dataset has a relatively high inclusion
+rate of 5.41\%, compared to the other datasets).
+
+\includegraphics{figs/rf_tfidf.eps}
+
+\hypertarget{appendix-x---hyperparameters-and-their-sample-space}{%
+\subsection{Appendix x - Hyperparameters and their sample
+space}\label{appendix-x---hyperparameters-and-their-sample-space}}
+
+Classifier hyperparameters
+
+\begin{verbatim}
+class_weight: normal(0,1) constrained to be > 0
+class weight of the inclusions.
+
+\end{verbatim}
+
+Logistic Regression
+
+\begin{verbatim}
+c: float. normal(0,1), constrained to be > 0
+\end{verbatim}
+
+Support Vector Machine
+
+\begin{verbatim}
+gamma: ["auto", "scale"],
+Gamma parameter of the SVM model.
+
+C: 
+C parameter of the SVM model.
+
+kernel:
+SVM kernel type.["linear", "rbf", "poly", "sigmoid"]
+\end{verbatim}
+
+Naive Bayes
+
+\begin{verbatim}
+"model_param.alpha", # exp(normal(0,1))
+
+\end{verbatim}
+
+Random Forest
+
+\begin{verbatim}
+max_features: int (between 6 and 10)
+    Number of features in the model.
+
+n_estimators: int between 10 and 100 
+    Number of estimators.
+
+model_param.n_estimators" #quniform(10,100,1)
+\end{verbatim}
+
+Balance strategy hyperparameters: Dynamic supersampling:
+
+\begin{verbatim}
+a: float
+    Governs the weight of the 1's. Higher values mean linearly more 1's
+    in your training sample.
+alpha: float
+    Governs the scaling the weight of the 1's, as a function of the
+    ratio of ones to zeros. A positive value means that the lower the
+    ratio of zeros to ones, the higher the weight of the ones.
+b: float
+    Governs how strongly we want to sample depending on the total
+    number of samples. A value of 1 means no dependence on the total
+    number of samples, while lower values mean increasingly stronger
+    dependence on the number of samples.
+
+\end{verbatim}
+
+Feature extraction strategy hyperparameters
+
+\begin{verbatim}
+split_ta: 0 or 1
+   whether titles and abstracts are split
+
+use_keywords: 0 or 1
+    whether keywords should be used
+
+\end{verbatim}
+
+TF-IDF
+
+\begin{verbatim}
+ngram_max: 1, 2 or 3
+    Can use up to ngrams up to ngram_max. For example in the case of 
+    ngram_max=2, monograms and bigrams could be used.
+\end{verbatim}
+
+Doc2Vec
+
+\begin{verbatim}
+vector_size: int (between 32 and 127)
+    Output size of the vector.
+
+epochs: int (between 20 and 50)
+    Number of epochs to train the doc2vec model.
+
+min_count: int (between 1 and 3)
+    Minimum number of occurences for a word in the corpus for it to be 
+    included in the model.
+
+window: int (between 5 and 9)
+    Maximum distance over which word vectors influence each other.
+
+dm_concat: int 0 or 1
+    Whether to concatenate word vectors or not.
+
+dm: int 
+    Model to use.
+    0: Use distribute bag of words (DBOW).
+    1: Use distributed memory (DM).
+    2: Use both of the above with half the vector size and concatenate them.
+
+dbow_words: int 0 or 1
+    Whether to train the word vectors using the skipgram method.
+\end{verbatim}
+
+\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}}
+
+To demonstrate the models, simulations are performed of the models on
+six original systematic reviews.\\
+With the labeled datasets, the systematic review can be reproduced but
+with now using a machine learning model to optimize the reviewing
+process.
+
+The initial training set of the active learning model in the simulation
+is one prior included publication and one prior excluded publication,
+randomly sampled from the data. This demonstrates a `worst case
+scenario' where the reviewer has minimal prior knowledge on publications
+in the data. For this simulations there is no need for a human reviewer
+since the labels in the data can be queried. The oracle is not the
+reviewer but the labels in the data. The model retrains every time after
+a label is provided by the oracle. The simulation ends when all
+publications in the dataset have been queried.
+
+To account for variance, every simulation is repeated for 15 trials
+\(t\).
 
@@
 \subsubsection{Statistical analysis}\label{statistical-analysis}}
+
+Results are aggregated over 15 runs of every simulation.
 
@@
 
-ASReview takes the following parameters/arguments:
+ASReview takes the following parameters/arguments: We now have 75
+combinations. for every for every model (5), for every dataset (5) and
+for every set of optimized hyperparameters (3), a simulation study
+consisting trials is performed. From these \(5*5*3=75\) simulation
+studies, performance of the different models is evaluated.
 
@@
 \end{tabular}
-
-\hypertarget{hyperparameters}{%
-\subsubsection{Hyperparameters}\label{hyperparameters}}
-
-Every model has its own set of hyperparameters:
-
-\hypertarget{optimization}{%
-\subsubsection{Optimization}\label{optimization}}
-
-The hyperparameters are optimized on the 5 datasets in three different
-ways:
-
-\begin{itemize}
-\tightlist
-\item
-  1 on 1: maximum performance
-\end{itemize}
-
-\[ d = D \] - 4 on 1: cross-validation \[ d \notin D\]
-
-\[ D = {1, 2, 3, 4}\]
-
-\begin{itemize}
-\tightlist
-\item
-  5 on 1: more data = more better?
-\end{itemize}
-
-\[ d \in D \]
-
-This results \((5+5+1)*5\) sets of hyperparameters.
 
@@
 
+\begin{tabular}{l|r|r|r|r|r|r}
+\hline
+  & ace & nudging & ptsd & software & virus & wilson\\
+\hline
+BCTD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+RCTD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+SCTD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+LCTD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+NCTD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+BCDD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+RCDD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+SCDD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+LCDD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+NCDD & 0 & 0 & 0 & 0 & 0 & 0\\
+\hline
+\end{tabular}
+
 \newpage
@@
 \section{Discussion}\label{discussion-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  we look for final inclusions but we screen only the abstracts (do they
+  satisfy the imformation need (blake (page 19 omara et evs)))
+\end{itemize}
+
+future research: - stopping rule is not discussed -
+computation/retraining time
+
+strengths:
+
+\begin{itemize}
+\tightlist
+\item
+  open data
+\item
+  different research areas
+\item
+  different models on same dataset
+\item
+  different datasets on same model
+\end{itemize}
+
+limitations
+
+future research - all models save time, difficult to distinguish
+performance over datasets, especially when applied on a dataset of which
+no prior information is known (e.g.~inclusions isn't known in practice).
+Perhaps go for other criteria like the fastest model, replicate study
+with computation time?
+
+Simulating the title and abstract screening process, models are evaluted
+on their capability/speed of detecting the final inclusions. However, in
+a manual SR these final inclusions are selected after reading the
+fulltext. Information the text mining tool does not have. To truly
+assess the added value of such a tool, models should be evaluated on
+their capability of detecting the abstract inclusions. Call for
+systematic reviewers to openly publish need for open data containing
+abstract inclusions, not only final inclusions!
 
@@
 
-\hypertarget{hyperparameters-1}{%
-\subparagraph{hyperparameters}\label{hyperparameters-1}}
+\hypertarget{hyperparameters}{%
+\subparagraph{hyperparameters}\label{hyperparameters}}
 
@@
 
+In the current study, the classifier and the feature extraction strategy
+are varied, whereas the query and balance strategy remain fixed. In the
+current study only a fraction of all possible configurations are tested
+for the sake of brevity. There are many more options available and open
+to exploration.
+
 \printbibliography[title=References]

### 2020-04-25 simulation_study/simulation/README.Rmd
First draft introduction section

@@
   noquote()
-names(seed_nudging) <- c("8119472", "8119472", "sctd", "")
+names(seed_nudging) <- c("8119472", "8119472", "8121720", "8121721", "8121722", "8121723", "8121725")
 

### 2020-04-26 manuscript/drafts/manuscript.Rmd
update methods section

@@
 output:
-  word_document: default
   pdf_document:
     citation_package: biblatex
+  word_document: default
 bibliography: asreview.bib
@@
 Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.
-When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
-The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
-In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
-Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.
+When applied in screening prioritization, an active learning model can decide which publication it wants the reviewer to screen next.
+Based on the reviewers screening decision ('relevant', 'irrelevant'), the model can incrementally improve its relevancy predictions on the remaining publications, and again select the next publication to be screened.
 
@@
 <!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
-
  <!-- [@OConnor2019] -->
@@
 --- 
-
-#### summarise models used
-#### propose pipeline 
-##### and specific components?
-
-#### summarise datasets tested
-\
-\
-
-## Background
-[@OMara-Eves2015] literature review
-
-[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
-A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
-In terms of Yu et al, we adopt .CT.
-
-SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
-
-abstrackr
-
-SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
-Also include social sciences data besides medical data.
-
-[@Cohen2006] perceptron-based classifier (neural network)
-
-SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
-in limitations section mentions that LR yields about same results, nb inferior results.
-
-[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
-  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
-The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
-
-Our extensions is that we try different classifiers, on more datasets.
-
-Goal: evaluate performance of different models of the ASReview tool. 
-The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
-What would happen if the citation screening would have been performed using asreview? 
-All datasets accompanying the systematic reviews are openly published. 
-We built several machine learning models to perform automated systematic reviews, 
-who are then applied on existing systematic reviews.
-
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
-
-a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
-
-Openness, reproducible,
-
-Benefits:
-
-Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
-meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
-
-paper organization:
-
-The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
-So not only medical sciences.
-
-Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
-Few studies have evaluated different classifiers in any systematic way
-different models to use haven't been investigated in a systematic way (only in software engineering)
-
-1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
-2) screening prioritization is appealing to systematic reviewers because ...
-3) 
-4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
-
-lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
-There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
-
-However, there is a need for consensus () and transparancy?
-
-So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
-
-Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
-
-##### indicating the structure of the writing)
-principle findings:
-
-<!-- RQ2 different hyperparameter optimizations? -->
-<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
-
-For truly evaluate the effectiveness of such methods,
-
-automatically (by machine learning techniques)
-In the current study we focus on the effectiveness of different machine learning models in reducing workload in the citation screening process. 
-Assisting the reviewer. Combining various machine learning techniques. 
-Combining recent insights on, we propose ASReview.
-Approaching the citation screening phase as a classfication task,
-The benefit is that ASReview is dynamic, user can decide
-open source, multiple classifiers and other settings,
-
-The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th
-The reviewer sees the most relevant abstracts first, 
-If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.
-
-Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
-
-#### Proposed solution
-This study is about how machine learning models can increase efficiency in systematic reviews.
-Their main objective is to identify ..
-
-The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
-As the relevant publications are screened first, the reviewing process can be quit earlier.
-
-The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
-This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
-Together with the reviewer /human machine interaction.
-The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
-It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
-
-The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
-To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
-This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
-Also reviewing is now much more fun.
-As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
-
-### Background
-... starts with a search for potentially relevant publications. 
-This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
-Because the initial set often consists of thousands of papers and the
-
-To gather the findings relevant to answering the research question, a systematic search is performed.
-A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
-From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
-Of all candidate studies only a fraction is relevant [...].
-
-As more and more papers are published and reproducibility crisis has emerged, 
-A systematic search often results in thousands of candidate studies.
-Relevant publications are then identified by screening title and abstract of all candidate studies. 
-This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
-This is a time consuming process that weighs heavily on resources.
-
-Most often the SVM classifier is used, popular and very good results.
-Also lots of other configurations.
-However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
-Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
-
-A solution is ...
-
-It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
-
-To review a specific research area, one starts out with an initial search of thousands of academic papers.
-All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
-With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
-This whole processes costs this and this much time [shelmilt].
-
-#### Technical details
-So you might wonder, how does such an algorithm actually work?
-Active learning strategy, starting with a pool of unlabeled abstracts (U).
-The reviewer starts labeling some instances in U, creating L.
-The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method).
+## Technical details
+In this section, the workings of an active learning model for screening prioritization will be explained in more detail.
+
+### Active learning cycle
+Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.  
+The goal of the technique is to identify the sparse relevant publications as early as possible / present for labelling.
+There is a lot of data, but not a lot of labels.
+
+When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
+The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
+In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
+Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.
+
+All publications obtained in the search $x$ form a pool of unlabelled instances $\mathcal{U}$. 
+To conduct a systematic review the reviewer needs to identify which publications are relevant, 
+The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$.
+This is the starting point for the active learning model.
+The model trains a model who predicts
+
+- instance $x$, label $y$
+- utility measure $\phi_A(\cdot)$
+- $x^*_A$ best query instance according to $\phi_A(\cdot)$
+
+```
+input:  
+    a pool of unlabeled abstracts $\mathcal{U}$ 
+    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
+
+  M = train($\mathcal{L}$)
+  Query x isin mathcal{U} (<x, y=?)
+  oracle <x, y>
+
+```
+
+All instances x need to be classified, e.g. we want to give them a label y. 
+Binary classification, either inclusion or exclusion. 
+we start out with a pool of unlabelled abstracts U.
+
+The model utilizes L to predict labels for all abstracts (classifier). (training)
+a new paper is selected (query) the one that is most likely to be relevant. & queried 
+The reviewer is asked to label the query (relevant, irrelevant), which is then added to the training set. 
+Now the model can update in (retraining) its predictions based on the new training dataset. This is caled retraining. 
+The cycle starts over again.. 
+As the cycle repeats itselfs, labeled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s
+
+This is done by using a set of features from the papers called X, for example the text in the abstract (feature extraction method).
 Now, it made an initial classification.
@@
 
-We approach asr as a classification problem: 
-All papers obtained in the systematic search form a pool of instances x. 
-All instances x need to be classified, e.g. we want to give them a label y. 
-all x are now part of U,.
-Binary classification, either inclusion or exclusion. 
 We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.
@@
 By starting of with L, the algorithm utilizes characteristics of X to predict labels in U. 
-
 We want to classify the papers in 
@@
 <x,y>.
-```
-input:  
-    a pool of unlabeled abstracts $\mathcal{U}$ 
-    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
-
-  M = train($\mathcal{L}$)
-  Query x isin mathcal{U} (<x, y=?)
-  oracle <x, y>
-
-```
-- pool unlabeled abstracts $\mathcal{U}$ 
-- labeled data set $\mathcal{L}$, 
-- instance $x$, label $y$
-
-- utility measure $\phi_A(\cdot)$
-- $x^*_A$ best query instance according to $\phi_A(\cdot)$
-
+
+#### details: features, balance, ... / known issues. 
 Now there are a few technical details.
@@
 
-To perform all these computations the research was carried out using the ASReview software by Utrecht University, which has a simulation mode that you can just input your labelled review file into and perform a simulation study with it.
-To be found on GitHub.
-It has many adjustable components/is very versatile.
-
-Then if we still have time left we explore the effect of another feature extraction method, namely doc2vec.
+## Models 
+_x_ active learning models ($M$) were built. 
+The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.
+
+#### Classifiers
+
+Every model applies a classifier $c$ to predict the relevance of publications in the data. 
+The classifier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
+predicts the class of an instance given input features $\mathbf{X}$
+
+#### Word representation 
+For a model to be able to predict relevancies, the title and abstract of the publications need to be represented numerically. 
+To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
+Examples of such information are titles and abstracts. 
+However, the classifier cannot predict the publication class from titles and abstracts as they are. 
+Their textual content to needs to be mapped to feature vectors. 
+This process of numerically representing textual content is called 'word embeddings'.
+
+A classical example of word embeddings a 'bag of words' representation. 
+For each text in the data set, the number of occurrences of each word is stored. 
+This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
+The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
+Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
+
+The model expedits features of previously labeled publications and 
+Based on features of the previously labeled inclusions and exclusions, the model
+
+The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
+
+(TF-IDF) (Doc2Vec)
+
+#### Fixed components  
+Utility measure / query strategy 
+All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.
+
+we explore the effect of another feature extraction method, namely doc2vec.
 This might possibly increase performance as it performs better at grasping structure/hidden relations/hierarchy between words in the texts.
@@
 
-Then if there’s even more time we might want to compare a different balance strategy.
-
-----
-
-A SR can be divided into phases. 
-Everything starts with a **systematic search**, leading to
-then citation screening is performed, then full-text screening
-[@PRISMA-PGroup2015]
-
-What must be the objective of our tool?:
-It is the tedious task citation screening part where loads of time can be saved.
-
-models are designed in a 'realistic' way (you have some inclusions)
-
-Selecting papers is a two-step process: abstract & fulltext screening
-
-Binary classification problem. 
-predict whether a paper in the pool is an inclusion or exclusion, 
-based on labeled instances from $\mathcal{L}$ and use training data to understand how input variables are related to class.
-
-We're building active learning model who takes X as an input an predicts class using labels from training set. 
-Model improves by deciding asking more information from the reviewer (oracle), 
-accounting for imbalance.
-
-The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
-
-#### Assumptions 
-1) decisions of the original SR are **ground truth** (benchmark) (oracle)
-
-The inclusion rate is ... data is imbalanced. 
-what is the philosophy
-False negatives must be avoided ... 
-The cost of a false negative outweighs the cost of a false positive. 
-Note that we assume the oracle/original user to hold the truth. 
-This is of course not always the case.
-
-There are two classes in the data: exlusions and inclusions.
-The inclusions are clearly the minority class.
-
-Datasets from the medical and social sciences, software engineering and public administration. 
-Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.
-
-## active learning for systematic reviews 
-corpus = all the text:
-
-Active learning = 
-increasing classification performance with every query. 
-The query strategy determines the way unlabeled papers are queried to the researcher.
-
-[@modAL2018]
-
-RQ1 - what are good classifiers 
-RQ2 - what are good optimization strategies
+---
 
 \newpage
+
 # Methods
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
-
-All simulations were run using through cartesius EINF-156
-
-Performance of several machine learning models was demonstrated on six systematic review datasets.  
-study design: retrospective
-
-## Models 
-_x_ machine learning models ($M$) were built. 
-The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.
-
-#### Classifiers
-Every model applies a classifier $c$ to predict the relevance of publications in the data. 
-The classfiier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
-predicts the class of an instance given input features $\mathbf{X}$
+Several active learning models where developed with the goal of identifying the sparse relevant publications early as possible.
+The aim of this study was to assess performance of screening prioritization by several active learning models on increasing efficiency in title and abstract screening in six systematic reviews, compared to screening at random order/in the conventional process.
+Model performance was demonstrated by performing a simulation on six systematic review datasets from various research areas.
+
+To evaluate  retrospective analysis / simulation
+various areas for generalizability
+
+## Active Learning Models 
+The 7 active learning models tested differ on the classifier and feature extraction they use. 
+Four classifiers and two feature extraction strategies were tested, leading to 7 models* *(nb doesn't do d2v)
+The performance
+ - Naive Bayes + TF-IDF
+ - Random Forest + TF-IDF 
+ - Support Vector Machine + TF-IDF
+ - ...
 
@@
 tasks.
-
 Random Forests (RF) is where a large number of decision trees are fit on bootstrapped samples of the original data.
 All trees cast a vote on the class, which are aggregated into a class prediction for each input $\mathbf{X}$ [@Breiman2001].
-
 Support Vecor Machine (SVM) - finds a multidimensional hyperplane to separate classes.
@@
 
-#### Word representation 
-To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
-Examples of such information are titles and abstracts. 
-However, the classifier cannot predict the publication class from titles and abstracts as they are. 
-Their textual content to needs to be mapped to feature vectors. 
-This process of numerically representing textual content is called 'word embeddings'.
-
-A classical example of word embeddings a 'bag of words' representation. 
-For each text in the data set, the number of occurrences of each word is stored. 
-This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
-The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
-Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
-
-The model expedits features of previously labeled publications and 
-Based on features of the previously labeled inclusions and exclusions, the model
-
-The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
-
-(TF-IDF) (Doc2Vec)
-
-#### Fixed components  
-All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.
+The following were fixed over models:
 
@@
 
-## Datasets
-Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
+## Simulation study
+To demonstrate the models, simulations are performed of the models on six original systematic reviews. ** asreview has a nice simulation mode. 
+The models were applied on data from existing systematic reviews.
+
+The screening process was simulated by
+
+For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
+the label column acts as the oracle.
+The oracle is not the reviewer but the labels in the data.
+
+The model retrains every time after a label is provided by the oracle. 
+The simulation ends when all publications in the dataset have been queried.
+
+The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
+
+#### Assumptions 
+1) decisions of the original SR are **ground truth** (benchmark) (oracle)
+The initial training set of the active learning model in the simulation is one prior included publication and one prior excluded publication, randomly sampled from the data. 
+This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data. this is realistic / lower bound.
+
+We're building active learning model who takes X as an input an predicts class using labels from training set. 
+Model improves by deciding asking more information from the reviewer (oracle), 
+accounting for imbalance.
+
+To account for variance, every simulation is repeated for 15 trials $t$. 
+study assumptions:
+
+- simulation mode 
+- assumptions (prior knowledge etc, oracle = reviewer).
+
+A SR can be divided into phases. 
+Everything starts with a **systematic search**, leading to
+then citation screening is performed, then full-text screening
+[@PRISMA-PGroup2015]
+
+What must be the objective of our tool?:
+It is the tedious task citation screening part where loads of time can be saved.
+
+Selecting papers is a two-step process: abstract & fulltext screening
+
+Binary classification problem. 
+predict whether a paper in the pool is an inclusion or exclusion, 
+based on labeled instances from $\mathcal{L}$ and use training data to understand how input variables are related to class.
+
+### Statistical analysis 
+Results are aggregated over 15 runs of every simulation.
+
+#### measures
+#### comparison over conditions 
+The inclusion rate is ... data is imbalanced. 
+what is the philosophy
+False negatives must be avoided ... 
+The cost of a false negative outweighs the cost of a false positive. 
+Note that we assume the oracle/original user to hold the truth. 
+This is of course not always the case.
+
+There are two classes in the data: exlusions and inclusions.
+The inclusions are clearly the minority class.
+
+Datasets from the medical and social sciences, software engineering and public administration. 
+Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.
+
+#### Data selection & preprocessing
+various datasets is necessary cause it is difficult to compare models accross datasets but also model performance is very data dependent!
+
+Six systematic reviews from various research areas were used to simulate the automated systematic review process.
 Data were preprocessed from the original source into a test dataset, containing all publications obtained in the systematic search.
@@
 
+### How will results be analysed/performance will be evaluated? 
+how is 'good' performance defined/quantified?
+
+metrics used: 
+#### Performance metrics 
+For each model, 
+Several metrics are used to compare performance of different models over datasets,
+
+| Dataset   |   | Naive Bayes | Random Forests | Support Vector Machine | Logistic Regression | Dense Neural Network |  
+| --------- | - | --- | --- | --- | --- | ---|
+| ptsd      |   | ?   |     |     |    |     | 
+| ace       |   | ?   |     |     |    |     | 
+| hall      |   | ?   |     |     |    |     | 
+| nagtegaal |   | ?   |     |     |    |     | 
+| ....      |   | ?   |     |     |    |     |
+
+The goal is twofold: we want to identify all relevant papers, as fast as we can. 
+Tradeoff: identifying all relevant papers and reducing workload. 
+A good metric to evaluate this is..
+
+What is more important: recall or precision?
+
+Recall more highly valued than precision.
+
+What about class imbalance?
+
+#### RRF
+Amount of relevant references found after having screened a certain percentage of the total number of abstracts.
+
+#### Work saved over sampling (WSS)
+Indicates how much time can be saved, at a given level of recall.
+WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
+Typically, WSS is measured at a recall of 0.95. Reasonable because..
+
+$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$
+
+#### Raoul
+#### Utility? 
+#### F-measure 
+#### ROC/AUC
+
+Is performance related to some characteristic (n, inclusion rate, ...)
+
+? How to compare outcomes of 3 different optimization strategies? 
+---
+
+All datasets accompanying the systematic reviews are openly published. 
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
+Simulations were carried out using ASReview ...,
+Statistical analyses were performed using R version ... 
+All simulations were run using through cartesius EINF-156
+
+To perform all these computations the research was carried out using the ASReview software by Utrecht University, which has a simulation mode that you can just input your labelled review file into and perform a simulation study with it.
+To be found on GitHub.
+It has many adjustable components/is very versatile.
+
 ### Optimizing hyperparameters
@@
 The hyperparameter values that were found to lead to a minimum loss value were visually inspected.
+
+\newpage
+## Background
+[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
+A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
+In terms of Yu et al, we adopt .CT.
+
+SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
+
+abstrackr
+
+SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
+Also include social sciences data besides medical data.
+
+[@Cohen2006] perceptron-based classifier (neural network)
+
+SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
+in limitations section mentions that LR yields about same results, nb inferior results.
+
+[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
+  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+The AUC results are mixed, although boosting has a slight edge overall.
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
+
+Our extensions is that we try different classifiers, on more datasets.
+
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
+The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
+
+a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
+Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
+
+Openness, reproducible,
+
+Benefits:
+
+Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
+meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
+
+paper organization:
+
+The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
+So not only medical sciences.
+
+Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
+Few studies have evaluated different classifiers in any systematic way
+different models to use haven't been investigated in a systematic way (only in software engineering)
+
+1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
+2) screening prioritization is appealing to systematic reviewers because ...
+3) 
+4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
+
+lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
+There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
+
+However, there is a need for consensus () and transparancy?
+
+So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
+
+Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
+
+<!-- RQ2 different hyperparameter optimizations? -->
+<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
+
+For truly evaluate the effectiveness of such methods,
+
+Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
+
+#### Proposed solution
+This study is about how machine learning models can increase efficiency in systematic reviews.
+Their main objective is to identify ..
+
+The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
+As the relevant publications are screened first, the reviewing process can be quit earlier.
+
+The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
+This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
+Together with the reviewer /human machine interaction.
+The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
+It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
+
+The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
+To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
+This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
+Also reviewing is now much more fun.
+As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
+
+### Background
+... starts with a search for potentially relevant publications. 
+This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
+Because the initial set often consists of thousands of papers and the
+
+To gather the findings relevant to answering the research question, a systematic search is performed.
+A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
+From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
+Of all candidate studies only a fraction is relevant [...].
+
+As more and more papers are published and reproducibility crisis has emerged, 
+A systematic search often results in thousands of candidate studies.
+Relevant publications are then identified by screening title and abstract of all candidate studies. 
+This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
+This is a time consuming process that weighs heavily on resources.
+
+Most often the SVM classifier is used, popular and very good results.
+Also lots of other configurations.
+However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
+Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
+
+A solution is ...
+
+It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
+
+To review a specific research area, one starts out with an initial search of thousands of academic papers.
+All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
+With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
+This whole processes costs this and this much time [shelmilt].
+
+----
+
+## active learning for systematic reviews 
+corpus = all the text:
+
+Active learning = 
+increasing classification performance with every query. 
+The query strategy determines the way unlabeled papers are queried to the researcher.
+
+[@modAL2018]
+
+\newpage
 
@@
 
-## Simulations
-To demonstrate the models, simulations are performed of the models on six original systematic reviews.  
-With the labeled datasets, the systematic review can be reproduced but with now using a machine learning model to optimize the reviewing process.
-
-The initial training set of the active learning model in the simulation is one prior included publication and one prior excluded publication, randomly sampled from the data. 
-This demonstrates a 'worst case scenario' where the reviewer has minimal prior knowledge on publications in the data. 
-For this simulations there is no need for a human reviewer since the labels in the data can be queried. 
-The oracle is not the reviewer but the labels in the data. 
-The model retrains every time after a label is provided by the oracle. 
-The simulation ends when all publications in the dataset have been queried.
-
-To account for variance, every simulation is repeated for 15 trials $t$.
-
-### Statistical analysis 
-Results are aggregated over 15 runs of every simulation.
-
-#### measures
-#### comparison over conditions
-
 # The software 
@@
 ```
-
-#### Performance metrics 
-For each model, 
-Several metrics are used to compare performance of different models over datasets,
-
-| Dataset   |   | Naive Bayes | Random Forests | Support Vector Machine | Logistic Regression | Dense Neural Network |  
-| --------- | - | --- | --- | --- | --- | ---|
-| ptsd      |   | ?   |     |     |    |     | 
-| ace       |   | ?   |     |     |    |     | 
-| hall      |   | ?   |     |     |    |     | 
-| nagtegaal |   | ?   |     |     |    |     | 
-| ....      |   | ?   |     |     |    |     |
-
-The goal is twofold: we want to identify all relevant papers, as fast as we can. 
-Tradeoff: identifying all relevant papers and reducing workload. 
-A good metric to evaluate this is..
-
-What is more important: recall or precision?
-
-Recall more highly valued than precision.
-
-What about class imbalance?
-
-#### RRF
-Amount of relevant references found after having screened a certain percentage of the total number of abstracts.
-
-#### Work saved over sampling (WSS)
-Indicates how much time can be saved, at a given level of recall.
-WSS is in terms of the percentage of abstracts that don't have to be screened by the researcher. 
-Typically, WSS is measured at a recall of 0.95. Reasonable because..
-
-$$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$
-
-#### Raoul
-#### Utility? 
-#### F-measure 
-#### ROC/AUC
-
-Is performance related to some characteristic (n, inclusion rate, ...)
-
-? How to compare outcomes of 3 different optimization strategies?
 

### 2020-04-26 simulation_study/simulation/README.Rmd
update methods section

@@
 # transfer sctd's later!(3)
-noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
+noquote(transfer("one", condition[c(1,2,3,4,7,8,9)], seed = TRUE))
 # ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD
+
+```
+
+```{r}
+seed_virus <- createLines(condition[c(1, 2, 3,4,7,8,9)], "virus", "one", seed = TRUE) %>%
+  noquote()
+names(seed_virus) <- c("8125572", "8125573", "8125574", "8125575", "8125581", "8125582", "8125583")
+
+seed_wilson <- createLines(condition[c(1, 2, 3,4,7,8,9)], "wilson", "one", seed = TRUE) %>%
+  noquote()
+names(seed_wilson) <- c("8125584", "8125585", "8125586", "8125587", "8125588", "8125589", "8125590")
+```
+
+```{r}
+seed_ptsd <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ptsd", "one", seed = TRUE) %>%
+  noquote()
+
+# sctd later
+
+seed_software <- createLines(condition[c(1, 2, 3,4,7,8,9)], "software", "one", seed = TRUE) %>%
+  noquote()
+# sctd later
+names(seed_software) <- c("8129589", "8129732", "8129588", ".", ".", ".", ".")
+
+# ptsd sctd
 

### 2020-05-01 manuscript/drafts/manuscript.Rmd
Update manuscript and dataset table

--- 2020-04-25 manuscript/drafts/manuscript.Rmd
@@
   word_document: default
+  citation_package: biblatex
   pdf_document:
-    citation_package: biblatex
 bibliography: asreview.bib
+csl: systematic-reviews.csl
 ---
@@
 \newpage
+
 # Introduction
 Systematic reviews are top of the bill in building evidence in research.
-A systematic review attempts to bring together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
+A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
 Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007].
@@
 add that this is a systematic/rigorous process?-->
-
-Systematic reviews are costly.
-Conducting a systematic review involves the manual screening of thousands of titles and abstracts, identifying publications relevant to answering the research question.
+However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts, identifying publications relevant to answering the research question.
 An experienced reviewer takes on average 30 seconds to screen one title and abstract, whereas an inexperienced reviewer takes even longer [@Wallace2010].
-Conducting a systematic review typically requires over a year of work from a team of researchers [@Borah2017].
+Conducting a systematic review typically requires over a year of work by a team of researchers [@Borah2017].
 <!-- Besides time-consuming, the process of title and abstract screening is prone to human error [@Wang2020]. -->
@@
 
-Systematic reviewers face competing demands. The production of a systematic review is a time-consuming process, but is often bound to a limited budget and timeframe. 
+Moreover, systematic reviewers are often bound to a limited budget and timeframe.
 Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
@@
 
-<!-- As the number of scientific publications is growing at an increasing rate [source], the workload in SR is getting heavier.  -->
-
 With advances in Artificial Intelligence (AI), there has been wide interest in tools to reduce workload in systematic reviews [@Harrison2020].
-More specifically, the field of AI-aided title and abstract screening is rapidly evolving.
-Various learning models have been proposed, aiming to detect whether a given publication is relevant or irrelevant to the systematic review.
+Various learning models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
 Findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
@@
 Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Cohen2009; @Shemilt2014].
-In screening prioritization, the learning model reorders publications to be screened by their likeliness to be relevant, aiming to present the reviewer with the most relevant publications first.
-Such an approach allows for substantial time-savings in the screening process:
+In screening prioritization, the learning model reorders publications to be screened by their likeliness to be relevant.
+The model presents the reviewer with the publications which are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
+Such an approach allows for substantial time-savings in the screening process.
 Reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
-Moreover, when combined with a stopping criterion, screening prioritization can be used to reduce the number of publications needed to screen. 
-Additionally, several studies report increasing efficiency beyond reducing workload [@OMara-Eves2015].
+Additionally, several studies report increasing efficiency beyond saving time [@OMara-Eves2015].
 
@@
 <!-- Several studies have proposed active learning models for screening prioritization -->
-Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2019; @Yu2018; @Miwa2014].
+Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2018; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010].
 Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012].
-Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes identifying relevant publications an ideal candidate for such models.  
-When applied in the screening process, an active learning model can iteratively improve its relevancy predictions by interacting with the reviewer.
-The model decides which publication it wants the reviewer to screen next, who then provides the model with a label ('relevant', 'irrelevant'). 
-In this active learning cycle, the model can incrementally improve its predictions on the relevancy of the remaining unlabeled publications. 
-Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset.
+Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes title and abstract screening an ideal candidate for such models.
+When applied in screening prioritization, the reviewer screens publications that are presented by an active learning model.
+Subsequently, the active learning model learns from the reviewers' decision ('relevant', 'irrelevant') and uses this knowledge in selecting the next publication to be screened by the reviewer.
+
+Although prior studies on the application of active learning models in title and abstract screening have addressed important issues [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], the complex nature of the field is making it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
+First, whilst there exists a scala of classification techniques, research to date has not yet evaluated techniques other than Support Vector Machines (SVM) [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010].
+Second, Miwa et al.
+[@Miwa2014] were the only study so far to make a direct comparison of model performance across research areass and found that active learning was more difficult on data from the social sciences compared to data from the medical sciences.
+The lack of replication on data from varying research contexts makes it impossible to draw conclusions about the general effectiveness of such techniques [@OMara-Eves2015; @Marshall2020].
+The question remains how active learning models for screening prioritization perform across different (1) classification techniques and (2) review contexts.
+Hence, additional evaluations of active learning models are required.
+
+<!-- on the reviewers screening decision ('relevant', 'irrelevant'), the model can incrementally improve its relevancy predictions on the remaining publications, and again select the next publication to be screened.
+-->
 
@@
 <!-- Although the effectiveness of active learning models in reducing workload in title and abstract screening has been extensively studied,  -->
-Although the application of learning models in reducing workload of systematic reviews has been extensively studied, the complex nature of the field is making it difficult to draw overarching conclusions about best practice.
-Moreover, the lack of replication on data outside the biomedical sciences makes it impossible to draw conclusions about the general effectiveness of such technologies [@OMara-Eves2015; @Marshall2020].
-Up to now only few studies have investigated active learning models for screening prioritization, with promising results.
-The question remains how different active learning models for screening prioritization perform across different review contexts.
-Hence, additional evaluations of active learning models are required.
-
-The purpose of this paper is to increase the evidence base of active learning models for reducing workload in title and abstract screening in systematic reviews. 
-Combining latest insights from this area, we present a pipeline of active learning for prioritization screening, called `ASReview`.
-`ASReview` is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies. 
-Working towards a general consensus in this emerging field, this study implements various active learning models (in `ASReview`).
-Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas.
-All data presented in this study are openly published, hoping to facilitate usability and acceptability of AI-assisted title and abstract screening in the field of systematic review.
+
+The purpose of the current paper is to increase the evidence base of active learning models for reducing workload in title and abstract screening in systematic reviews.
+Combining latest insights from this area, we propose seven different active learning models for the purpose of identifying relevant publications in systematic review datasets.
+The models were chosen to maximize the number of identified relevant publications, while minimizing the number of publications needed to screen.
+Working towards a general consensus in this emerging field, model performance was asessed by conducting a retrospective simulation on six systematic review datasets.
+Datasets were collected from the fields of medicine, software engineering, psychology, behavioural public administration, and virology to assess generalizability of the models across research contexts.
+The models, datasets and simulations are implemented in a pipeline of active learning for prioritization screening, called $\texttt{ASReview}$ [@ASReview2020].
+$\texttt{ASReview}$ is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
+All scripts and data used are openly published to facilitate usability and acceptability of AI-assisted title and abstract screening in the field of systematic review.
 
@@
 
----
-
-#### summarise models used
-#### propose pipeline 
-##### and specific components?
-
-#### summarise datasets tested
-\
-\
-
-## Background
-[@OMara-Eves2015] literature review
-
-[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
-A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
-In terms of Yu et al, we adopt .CT.
-
-SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
-
-abstrackr
-
-SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
-Also include social sciences data besides medical data.
-
-[@Cohen2006] perceptron-based classifier (neural network)
-
-SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
-in limitations section mentions that LR yields about same results, nb inferior results.
-
-[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
-  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
-The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
-
-Our extensions is that we try different classifiers, on more datasets.
-
-Goal: evaluate performance of different models of the ASReview tool. 
-The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
-What would happen if the citation screening would have been performed using asreview? 
-All datasets accompanying the systematic reviews are openly published. 
-We built several machine learning models to perform automated systematic reviews, 
-who are then applied on existing systematic reviews.
-
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
-
-a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
-
-Openness, reproducible,
-
-Benefits:
-
-Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
-meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
-
-paper organization:
-
-The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
-So not only medical sciences.
-
-Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
-Few studies have evaluated different classifiers in any systematic way
-different models to use haven't been investigated in a systematic way (only in software engineering)
-
-1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
-2) screening prioritization is appealing to systematic reviewers because ...
-3) 
-4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
-
-lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
-There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
-
-However, there is a need for consensus () and transparancy?
-
-So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
-
-Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
-
-##### indicating the structure of the writing)
-principle findings:
-
-<!-- RQ2 different hyperparameter optimizations? -->
-<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
-
-For truly evaluate the effectiveness of such methods,
-
-automatically (by machine learning techniques)
-In the current study we focus on the effectiveness of different machine learning models in reducing workload in the citation screening process. 
-Assisting the reviewer. Combining various machine learning techniques. 
-Combining recent insights on, we propose ASReview.
-Approaching the citation screening phase as a classfication task,
-The benefit is that ASReview is dynamic, user can decide
-open source, multiple classifiers and other settings,
-
-The current study focus is on reducing workload by prioritizing the most relevant abstracts. Presenting the abstracts orders the abstracts by likelihood of relevance, e.g. th
-The reviewer sees the most relevant abstracts first, 
-If the model performs well all relevent abstracts will be seen much earlier than when abstracts are read at a random order.
-
-Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
-
-#### Proposed solution
-This study is about how machine learning models can increase efficiency in systematic reviews.
-Their main objective is to identify ..
-
-The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
-As the relevant publications are screened first, the reviewing process can be quit earlier.
-
-The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
-This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
-Together with the reviewer /human machine interaction.
-The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
-It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
-
-The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
-To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
-This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
-Also reviewing is now much more fun.
-As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
-
-### Background
-... starts with a search for potentially relevant publications. 
-This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
-Because the initial set often consists of thousands of papers and the
-
-To gather the findings relevant to answering the research question, a systematic search is performed.
-A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
-From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
-Of all candidate studies only a fraction is relevant [...].
-
-As more and more papers are published and reproducibility crisis has emerged, 
-A systematic search often results in thousands of candidate studies.
-Relevant publications are then identified by screening title and abstract of all candidate studies. 
-This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
-This is a time consuming process that weighs heavily on resources.
-
-Most often the SVM classifier is used, popular and very good results.
-Also lots of other configurations.
-However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
-Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
-
-A solution is ...
-
-It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
-
-To review a specific research area, one starts out with an initial search of thousands of academic papers.
-All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
-With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
-This whole processes costs this and this much time [shelmilt].
-
-#### Technical details
-So you might wonder, how does such an algorithm actually work?
-Active learning strategy, starting with a pool of unlabeled abstracts (U).
-The reviewer starts labeling some instances in U, creating L.
-The algorithm utilizes L to predict labels for all abstracts (classifier), by using a set of features from the papers called X, for example the text in the abstract (feature extraction method).
-Now, it made an initial classification.
-The algorithm now aims to improve its classification by which paper from U will be presented to the reviewer next.
-By labeling the next paper, the reviewer provides the algorithm with new information which the algorithm uses to update its prediction.
-
-We approach asr as a classification problem: 
-All papers obtained in the systematic search form a pool of instances x. 
-All instances x need to be classified, e.g. we want to give them a label y. 
-all x are now part of U,.
-Binary classification, either inclusion or exclusion. 
-We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.
-
-By starting of with L, the algorithm utilizes characteristics of X to predict labels in U.
-
-We want to classify the papers in 
-Where the whole collection of papers in the systematic search form a pool of instances x, with unknown label y. 
-<x,y>. 
-```
-input:  
-    a pool of unlabeled abstracts $\mathcal{U}$ 
-    oracle labels a few initial papers, from $\mathcal{U}$, $\mathcal{L}$,
-
-  M = train($\mathcal{L}$)
-  Query x isin mathcal{U} (<x, y=?)
-  oracle <x, y>
-
-```
-- pool unlabeled abstracts $\mathcal{U}$ 
-- labeled data set $\mathcal{L}$, 
-- instance $x$, label $y$
-
-- utility measure $\phi_A(\cdot)$
-- $x^*_A$ best query instance according to $\phi_A(\cdot)$
-
-Now there are a few technical details.
+# Methods 
+## Task Description
+The screening process of a systematic review starts with all publications obtained in the search.
+The task is to identify which of these publications are relevant, by screening the publications at the title and abstract level.
+In active learning for screening prioritiztaion, the screening process proceeds as follows:
+
+- Start with the set of all publications $x$ with an unknown label, $\mathcal{U}$.
+- The reviewer provides a label for a few publications $x \in \mathcal{U}$, creating an set of labeled publications $\mathcal{L}$.
+The publications can be labeled as relevant $x_R$ or irrelevant $x_I$.
+- The active learning cycle starts:
+
+  1. A classifier is trained on the labeled publications, $C = \texttt{train}(\mathcal{L})$
+
+  2. The classifier predicts labels for all unlabelled publications, $C(\mathcal{U})$
+
+  3. Based on the predictions by $C$, the model selects the most relevant publication $x \in \mathcal{U}$
+
+  4. The model asks the reviewer to screen this publication, $x_?$
+
+  5. The reviewer screens the publication and provides a label, $x_R$ or $x_I$
+
+  6. The labeled publication is added to the training data, $\mathcal{L}$
+
+  7. Back to step 1.
+
+- In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled publications.
+The relevant publications are identified as early in the process as possible.
+The reviewer and the model keep interacting until the reviewer decides to stop or until all publications in $\mathbf{U}$ have been labelled.
+
+<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
+The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
+-->
+
+<!-- - then active learning cycle starts in which the user makes a decision after each iteration of the model which is then used to re-train the model. -->
+
+<!-- - instance $x$, label $y$ -->
+<!-- - utility measure $\phi_A(\cdot)$ -->
+<!-- - $x^*_A$ best query instance according to $\phi_A(\cdot)$ -->
+
+<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$. -->
+<!-- This is the starting point for the active learning model. -->
+<!-- The model trains a classifier who predicts ...  -->
+<!-- The reviewer and the are interacting in the active learning cycle. -->
+<!-- Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset. -->
+
+<!-- # Algorithm 1 -->
+<!-- Just a sample algorithmn -->
+<!-- \begin{algorithm}[H] -->
+<!-- \DontPrintSemicolon -->
+<!-- \SetAlgoLined -->
+<!-- \KwResult{Write here the result} -->
+<!-- \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output} -->
+<!-- \Input{Write here the input} -->
+<!-- \Output{Write here the output} -->
+<!-- \BlankLine -->
+<!-- \While{While condition}{ -->
+<!--     instructions\; -->
+<!--     \eIf{condition}{ -->
+<!--         instructions1\; -->
+<!--         instructions2\; -->
+<!--     }{ -->
+<!--         instructions3\; -->
+<!--     } -->
+<!-- } -->
+<!-- \caption{While loop with If/Else condition} -->
+<!-- \end{algorithm}  -->
+
+<!-- meaning the reviewer the reviewer screens as little as possible while inclusion rate = high (not true but is nice statistic?) -->
+<!-- The model is balancing two goals: obtain all relevant publications with as little as reviewing possible. -->
+<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
+The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
+-->
+
+<!-- #### Assumptions  -->
+<!-- 1) decisions of the original SR are **ground truth** (benchmark) (oracle) -->
+<!-- study assumptions: -->
+<!-- - simulation mode  -->
+<!-- - assumptions (prior knowledge etc, oracle = reviewer). -->
+
+<!-- A SR can be divided into phases.  -->
+<!-- Everything starts with a **systematic search**, leading to -->
+<!-- then citation screening is performed, then full-text screening -->
+<!-- [@PRISMA-PGroup2015] -->
+
+<!-- Selecting papers is a two-step process: abstract & fulltext screening -->
+
+<!-- x -->
+
+<!-- Now there are a few technical details.
 Many different versions of such algorithms exist.
@@
 Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.
-
-To perform all these computations the research was carried out using the ASReview software by Utrecht University, which has a simulation mode that you can just input your labelled review file into and perform a simulation study with it.
-To be found on GitHub.
-It has many adjustable components/is very versatile.
-
-Then if we still have time left we explore the effect of another feature extraction method, namely doc2vec.
-This might possibly increase performance as it performs better at grasping structure/hidden relations/hierarchy between words in the texts.
-So, it could be interesting in more ‘fuzzy’ research areas.
-A downside is that it takes more computing time.
-
-Then if there’s even more time we might want to compare a different balance strategy.
-
-----
-
-A SR can be divided into phases. 
-Everything starts with a **systematic search**, leading to
-then citation screening is performed, then full-text screening
-[@PRISMA-PGroup2015]
-
-What must be the objective of our tool?:
-It is the tedious task citation screening part where loads of time can be saved.
-
-models are designed in a 'realistic' way (you have some inclusions)
-
-Selecting papers is a two-step process: abstract & fulltext screening
-
-Binary classification problem. 
-predict whether a paper in the pool is an inclusion or exclusion, 
-based on labeled instances from $\mathcal{L}$ and use training data to understand how input variables are related to class.
-
-We're building active learning model who takes X as an input an predicts class using labels from training set. 
-Model improves by deciding asking more information from the reviewer (oracle), 
-accounting for imbalance.
-
-The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.
-
-#### Assumptions 
-1) decisions of the original SR are **ground truth** (benchmark) (oracle)
-
-The inclusion rate is ... data is imbalanced. 
-what is the philosophy
-False negatives must be avoided ... 
-The cost of a false negative outweighs the cost of a false positive. 
-Note that we assume the oracle/original user to hold the truth. 
-This is of course not always the case.
-
-There are two classes in the data: exlusions and inclusions.
-The inclusions are clearly the minority class.
-
-Datasets from the medical and social sciences, software engineering and public administration. 
-Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.
-
-## active learning for systematic reviews 
-corpus = all the text:
-
-Active learning = 
-increasing classification performance with every query. 
-The query strategy determines the way unlabeled papers are queried to the researcher.
-
-[@modAL2018]
-
-RQ1 - what are good classifiers 
-RQ2 - what are good optimization strategies
-
-\newpage
-# Methods
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
-
-All simulations were run using through cartesius EINF-156
-
-Performance of several machine learning models was demonstrated on six systematic review datasets.  
-study design: retrospective
+-->
+
+<!-- The current section describes how common issues in identifying relevant publication can be dealt with.  -->
+<!-- key components  -->
+
+## Technical details
+A more detailed account of the active learning models is given in the following section.
+The structure and functions of the key components of the models will be introduced to clarify the choices made in the design of the current study.
+
+#### Classification
+To make predictions on the unlabeled publications, a classifier is trained on features from the set of previously labeled publications. 
+<!-- The classifier predicts class of a given unlabeled publication.  -->
+A technique widely used in classification tasks is the Support Vector Machine (SVM).
+SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
+SVMs have been proven to be effective in active learning models for screening prioritization [@Yu2018; Miwa2014].
+Moreover, SVMs are the currently the only classifier implemented in ready-to-use software tools implementing active learning for screening prioritization (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]).
+
+Whilst performance several classification techniques have been investigated in the AI-aided title and abstract screening field in general [SOURCE], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
+<!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
+<!-- In fact, research in this area to date has not yet determined the performance of classifiers other than SVMs. -->
+The current study aims to address this gap by exploring performance of three classifiers besides SVM:
+
+ - L2-regularized Logistic Regression (LR)  models the probabilities describing the possible outcomes by a logistic function.
+The L2 penalty is imposed on the coefficients to reduce the number of features upon which the given solution is dependent [@scikit-learn].
+ - Naive Bayes (NB) is a supervised learning algorithm often used in text classification.
+Based on Bayes' Theorem, with the 'naive' assumption that all features are independent given the class value [@Zhang2004].
+- Random Forests (RF) is a supervised learning algorithm where a large number of decision trees are fit on bootstrapped samples of the original data.
+All trees cast a vote on the class, which are aggregated into a class prediction for each instance [@Breiman2001].
+
+These three classification techniques were selected because they are all widely adopted in previous studies on text classifcation [source].
+Moreover, the amount of processing power is relatively low.
+They can run on a personal computer.
+
+ <!-- Logistic models the posterior directly, naive bayes has higher bias but lower variance,  -->
+ <!-- logistic might perform better when trainign set increases. [@Ng2002] -->
+<!-- To carry out classification of publications, a classifier takes given input features $\mathbf{X}$ -->
+<!-- The model utilizes features of previously labeled publications and  -->
+<!-- The model utilizes L to predict labels for all abstracts (classifier). (training) -->
+<!-- a new paper is selected (query) the one that is most likely to be relevant. & queried  -->
+<!-- The reviewer is asked to label the query (relevant, irrelevant), which is then added to the training set.  -->
+<!-- Now the model can update in (retraining) its predictions based on the new training dataset. This is caled retraining.  -->
+<!-- The cycle starts over again..  -->
+<!-- As the cycle repeats itselfs, labeled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s -->
+<!-- We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.  -->
+
+#### Class imbalance problem
+There are two classes in the dataset: relevant and irrelevant publications.
+Typically, only a fraction of the publications in the data belong to the relevant class.
+This poses a problem for training a classifier as there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
+Moreover, classifiers are well-suited to separate data into classes, but not to correctly identifying one class [@Wallace2010].
+This is evident in the case of a dataset where only one percent of publications are relevant.
+A model would achieve 99% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been identified.
+Therefore, the class imbalance problem causes the classifier to miss relevant publications.
+
+Previous studies have addressed the class imbalance problem by rebalancing the training data in different ways [@OMara-Eves2015].
+To decrease the class imbalance in the training data, the models in the current study rebalance the training set by Dynamic Supersampling (DS).
+DS decreases the number of irrelevant publications in the training data, whereas the number of relevant publications are increased (by copy) such that the size of the training data remains the same.
+The ratio between relevant and irrelevant publications is not fixed, but dynamically updated and depends on the size of the training data, the total number of publications, and the ratio between total number of relevant and irrelevant publications.
+
+#### Word embeddings 
+To predict publication class, the classifier uses information from the publications in the dataset. 
+Examples of such information are titles and abstracts.
+However, a model cannot predict class from the titles and abstracts as they are; their textual content needs to be repressented numerically.
+The textual information needs to be mapped to feature vectors.
+This process of numerically representing textual content is called 'word embeddings'.
+
+A classical example of word embeddings is a 'bag of words' (bow) representation.
+For each text in the data set, the number of occurrences of each word is stored.
+This leads to $n$ features, where $n$ is the number of distinct words in the texts [@scikit-learn].
+The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".
+A more sophisticated approach is Term-frequency Inverse Document Frequency (TF-IDF).
+TF-IDF circumvents this problem by adjusting the term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set [@Ramos2003].
+A downside of TF-IDF and other bow methods is that they do not take into account the ordering of the words, thereby ignoring semantics.
+An example of an approach that aims to overcome this weakness is Doc2Vec (D2V), capable of grasping the relations between words by learning to predict the words in the texts [@Le2014].
+
+Miwa et al.
+found that active learning was more difficult on data from the social sciences compared to data the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014].
+As the study by Miwa et al.
+adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated word embeddings strategy has the potential to bridge the performance gap between these research areas.
+
+#### Query strategy
+The active learning model can adopt different strategies in selecting the next publication to be screened by the reviewer. 
+A strategy mentioned before is selecting the publication with the highest probability of being relevant.
+In the active learning literature this is referred to as certainty-based active learning [@Settles2012].
+Another well-known strategy is uncertainty-based active learning, where the instances that will be presented next will be those instances on which on which the model's classifications are the least certain, i.e.
+close to 0.5 probability [@Settles2012].
+Traditionally, this strategy trains the most accurate model because the model can learn the most from instances it is uncertain about.
+
+Even though uncertainty-based active learning generally leads to a more accurate model in the end, certainty-based active learning is the preferred strategy for the task at hand.
+The main reason is that this strategy is far better suited to the goal of prioritizing the relevant publications.
+Moreover, a study comparing performance of both strategies in found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
+Furthermore, uncertainty-based active learning is far better equipped at dealing with imbalanced data in active learning [@Fu2011].
+Therefore, certainty-based sampling is most equipped to the current scenario in which we are dealing with highly imbalanced datasets and where the goal is to identify all relevant publications as soon as possible.
 
 ## Models 
-_x_ machine learning models ($M$) were built. 
-The models consist of multiple components, of which the classifier and the feature extraction strategy varied over the models.
-
-#### Classifiers
-Every model applies a classifier $c$ to predict the relevance of publications in the data. 
-The classfiier predicts the class of a publication in the dataset expediting a training dataset $\mathcal{L}$,
-predicts the class of an instance given input features $\mathbf{X}$
-
-Logistic Regression (LR) - L2-regularized logistic regression. 
-Logistic models the posterior directly, naive bayes has higher bias but lower variance, 
-logistic might perform better when trainign set increases. [@Ng2002]
-Naive Bayes (NB) - Naive Bayes assumes all features are independent given the class value.
-This is obviously not the case but still the algorithm performs impressively [@Zhang2004].
-Especially at ...
-tasks.
-
-Random Forests (RF) is where a large number of decision trees are fit on bootstrapped samples of the original data.
-All trees cast a vote on the class, which are aggregated into a class prediction for each input $\mathbf{X}$ [@Breiman2001].
-
-Support Vecor Machine (SVM) - finds a multidimensional hyperplane to separate classes.
-[@Tong2001]
-
-#### Word representation 
-To predict the class of a publication class (e.g. whether a publication should be included or excluded), the classifier uses information from the publications in the dataset. 
-Examples of such information are titles and abstracts. 
-However, the classifier cannot predict the publication class from titles and abstracts as they are. 
-Their textual content to needs to be mapped to feature vectors. 
-This process of numerically representing textual content is called 'word embeddings'.
-
-A classical example of word embeddings a 'bag of words' representation. 
-For each text in the data set, the number of occurrences of each word is stored. 
-This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
-The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
-Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set.
-
-The model expedits features of previously labeled publications and 
-Based on features of the previously labeled inclusions and exclusions, the model
-
-The features used are title and abstract from every publication. - this is what is prescribed by prisma, (check!)
-
-(TF-IDF) (Doc2Vec)
-
-#### Fixed components  
-All models $M$ apply the same query strategy of certainty sampling, in which the presented publication is always the one of which the model is most certain for it to be relevant.
-
-To decrease the class imbalance in the training data, the model rebalances the training set by Dynamic Supersampling (DS).
-DS decreases the number of irrelevant papers in the training data, whereas the number of relevant papers are increased (by copy) such that the total number of samples remains the same.
-The ratio between relevant and irrelevant papers is not fixed, but dynamically updated and depends on the number of training samples, the total number of publications and the ratio between relevant and irrelevant publications.
+The seven models consist of the components described in the Technical Details section, adopting four different classification techniques and two different word embeddings approaches:
+
+First, four models combining every classifier with TF-IDF word embeddings were investigated: 
+ - SVM + TF-IDF
+ - NB + TF-IDF
+ - RF + TF-IDF 
+ - SVM + TF-IDF
+
+Second, the classifiers were combined with Doc2Vec word embeddings, leading to the following three models:^[The combination NB + D2V is impossible because NB can only process positive input features, whereas D2V]
+
+ - SVM + Doc2Vec
+ - RF + Doc2Vec
+ - SVM + Doc2Vec
+
+## Simulation study
+For each of the seven models, performance was evaluated by simulating the model on the screening process of six systematic reviews. 
+Performance of the seven models was evaluated by simulating their behaviour in the screening process of six systematic review datasets.
+Put differently, 42 simulations were carried out.
+For every model - dataset combination, hyperparameters were optimized^[see the Appendix for more information].
+To account for variance, every simulation was repeated for 15 trials.
+Simulations were run using ASReview's simulation mode [@ASReview2020]. There was no need for a human reviewer as the model could query the labels in the data instead.
+
+Every simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
+To account for bias, the initial training set was randomly sampled from the dataset for every of the 15 runs.
+Although varying over runs, the initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
+A seed value was set to ensure reproducability.
+The classifier was retrained every time after a publication had been labeled. 
+The simulation ended after all publications in the dataset had been labeled.
+
+<!-- can retrieve the labels from the annotated dataset instead -->
+<!-- The oracle is not the reviewer but the labels in the data.  -->
+<!-- The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.  -->
 
 ## Datasets 
-Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
-Data were preprocessed from the original source into a test dataset, containing all publications obtained in the systematic search.
-The test datasets are labelled indicating the relevant and irrelevant publications.
-Using these labels, a computer simulation of an automated systematic review can be performed on the systematic review data.
-
-The test datasets contain title information on all publications obtained in the search strategy. 
-The instances in the data consist of a title and an abstract and were labeled to indicate which publications were included in the systematic review.
-Instances with missing abstracts and duplicate instances were removed from the data.
-The data preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]
-
-Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
-All systematic reviews in this database are on drug efficacy.
-The _ace_ dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
-
-The _software_ dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field.
-This dataset is on fault prediction in software engineering by [@Hall2012].
-
-The _nudging_ dataset comes from a review from the behavioural public administration area.
-The SR includes studies on nudging healthcare professionals [@Nagtegaal2019].
-The data was stored on the Harvard Dataverse [@Nagtegaal2019a].
-
-A literature review from field of psychology, _ptsd_.
-The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017].
-The corresponding data can be found on the Open Science Framework [...].
-
-_wilson_, a dataset from the medical sciences [@Appenzeller-Herzog2020]. 
-TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].
-
-All datasets started with an initial pool of thousands of papers. 
-A fraction of these papers where deemed relevant for the SR, with inclusion rates around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).
+The models were simulated on a convenience sample of six systematic review datasets.
+The data selection process was driven by two factors.
+Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas.
+Secondly, datasets were selected by their availability, given the limited timespan of the current project.
+The datasets were retrieved from a collection of open systematic review datasets to be used for text mining purposes^[https://github.com/asreview/systematic-review-datasets, [@ASReview2020]].
+
+Three out of six datasets originated from the _medical sciences_: Ace, Wilson, and Virus.
+The Wilson dataset [@Appenzeller-Herzog2020] is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
+The Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
+The Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
+From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012].
+The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_,
+The PTSD dataset contains publications from the field of _psychology_.
+The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017].
+Of these six datasets, Ace, and Software have been used for model simulations in previous studies on AI-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].
+
+Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search.
+Candidate studies with missing abstracts and duplicate instances were removed from the data.
+Test datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
+All test datasets consisted of thousands of candidate studies, of which only only a fraction was deemed relevant to the systematic review.
+Inclusion rates were centered around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).
+<!-- The data preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis] -->
 
@@
 }
-
 datastats <- 
@@
                                        #"Studies selected for fulltext screening", 
-                                       "Final inclusions", 
+                                       "Relevant studies", 
                                        "Inclusion rate (%)"),2))) %>%
@@
 ```
+
+## Evaluating performance
+Model performance was visualized by plotting recall curves and further assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD).
+Results were averaged over 15 trials for every simulation.
+
+Plotting recall as a function of the number of screened publications offers insight in model performance throughout the screening process [@Cormack2014; @Yu2018].
+The curves give informations in two directions.
+On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
+
+WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006]. 
+When measured at the typical recall level of 0.95 [@Cohen2006], WSS yields an estimate of the amount of work that can have be saved at the cost of failing to identify 5% of relevant publications.
+In the current study, WSS is computed at 0.95 and 1.00 recall level.
+RRF statistics are computed at 10%, representing the proportion of relevant studies that were identified after screening 10% of all publications.
+
+Both RRF and WSS are sensitive to random effects as these statistics are strongly dependent on the position of the cutoff value. 
+Moreover, WSS makes assumptions about acceptable recall levels whereas this might depend on the research question at hand [@OMara-Eves2015]. 
+A statistic that is not dependent on some arbitrary cutoff value is the ATD, which is the average number of publications that are screened to find a relevant publication, divided by the total number of publications in the data.
+The ATD is proportional to the area above the recall curve.
+
+<!-- FN are far more problematic/unwanted/detrimental than FP: a researcher can label the FP as irrelevant whereas the FN are possibly never seen thereby missing relevant studies running the risk of an invalid systematic review.
+-->
+<!-- The goal is twofold: we want to identify all relevant papers, as fast as we can.  -->
+<!-- Tradeoff: identifying all relevant papers and reducing workload.  -->
+<!-- what about class imbalance.  -->
+
+Analyses were carried out using R [@RCoreTeam2019], version 3.6.1. 
+All datasets accompanying the systematic reviews are openly published. 
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
+All simulations were run using through Cartesius (EINF-156).
+
+<!-- $$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$  -->
+
+<!-- $$\texttt{ATD} = \frac{L}{N}$$ -->
+<!-- $$\texttt{ATD} = \frac{L(relevant) }{N}$$ -->
+
+<!-- Is performance related to some characteristic (n, inclusion rate, ...) -->
+
+<!-- ? How to compare outcomes of 3 different optimization strategies?  -->
+
+<!-- The cost of a false negative outweighs the cost of a false positive.  -->
+<!-- Note that we assume the oracle/original user to hold the truth.  -->
+<!-- This is of course not always the case.  -->
+<!-- There are two classes in the data: exlusions and inclusions. -->
+
+<!-- Datasets from the medical and social sciences, software engineering and public administration.  -->
+<!-- Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.  -->
+<!-- Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas. -->
+
+---
 
@@
 The hyperparameter values that were found to lead to a minimum loss value were visually inspected.
+
+\newpage
+## Background
+[@Yu2018], [@Yu2018] simulated 32 svm classifiers, on software engineering. 
+A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
+In terms of Yu et al, we adopt .CT.
+
+SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
+
+abstrackr svm certainty
+
+SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
+Also include social sciences data besides medical data.
+
+[@Cohen2006] perceptron-based classifier (neural network)
+
+SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
+in limitations section mentions that LR yields about same results, nb inferior results.
+
+[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
+  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+The AUC results are mixed, although boosting has a slight edge overall.
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
+
+Our extensions is that we try different classifiers, on more datasets.
+
+When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
+The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
+
+a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
+Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
+The data
+
+Openness, reproducible,
+
+Benefits:
+
+Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
+meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
+
+paper organization:
+
+The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
+So not only medical sciences.
+
+Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
+Few studies have evaluated different classifiers in any systematic way
+different models to use haven't been investigated in a systematic way (only in software engineering)
+
+1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
+2) screening prioritization is appealing to systematic reviewers because ...
+3) 
+4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
+
+lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
+There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
+
+However, there is a need for consensus () and transparancy?
+
+So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
+
+Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
+
+<!-- RQ2 different hyperparameter optimizations? -->
+<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
+
+For truly evaluate the effectiveness of such methods,
+
+Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
+
+#### Proposed solution
+This study is about how machine learning models can increase efficiency in systematic reviews.
+Their main objective is to identify ..
+
+The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
+As the relevant publications are screened first, the reviewing process can be quit earlier.
+
+The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
+This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
+Together with the reviewer /human machine interaction.
+The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
+It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
+
+The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
+To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
+This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
+Also reviewing is now much more fun.
+As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
+
+### Background
+... starts with a search for potentially relevant publications. 
+This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
+Because the initial set often consists of thousands of papers and the
+
+To gather the findings relevant to answering the research question, a systematic search is performed.
+A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
+From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
+Of all candidate studies only a fraction is relevant [...]. 
+As more and more papers are published and reproducibility crisis has emerged, 
+A systematic search often results in thousands of candidate studies.
+Relevant publications are then identified by screening title and abstract of all candidate studies. 
+This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
+This is a time consuming process that weighs heavily on resources.
+
+Most often the SVM classifier is used, popular and very good results.
+Also lots of other configurations.
+However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
+Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
+
+A solution is ...
+
+It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
+
+To review a specific research area, one starts out with an initial search of thousands of academic papers.
+All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
+With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
+This whole processes costs this and this much time [shelmilt].
+
+----
+
+## active learning for systematic reviews 
+corpus = all the text:
+
+Active learning = 
+increasing classification performance with every query. 
+The query strategy determines the way unlabeled papers are queried to the researcher.
+
+[@modAL2018]
+
+\newpage
 

### 2020-05-01 results/README.Rmd
Update manuscript and dataset table

@@
 library(rjson)
+library(tidyverse)
+library(knitr)
 ```
@@
 ```{python}
-
+# to be found on harddrive results folder
 ```
@@
 ```{r}
-data <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
-statspath <- paste0("statistics/one/RCTD/", "testoutput_RCTD_one_", data, ".json")
+data <- readRDS("../simulation_study/R/00_datasets.RDS")
+models <- list.files("/Volumes/Gerbrich/asreview/results/one/statistics/")
+names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )
 
-ace <- fromJSON(file = statspath[1])
+# function that reads results for a model M 
+read_results <- function(m){
+   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m), recursive = TRUE)
+  # names of the files are the data
+  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
+  # read data
+  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m, "/", x)))
+
+  # extract wss, rrf, and loss
+  dat <- map(dat, `[`, c("wss", "rrf", "loss"))
+
+  # transorm into dataframe
+  dat <- map_dfr(dat, ~ as.data.frame(.x), .id = "dataset")
+
+  # add model name
+  dat <- dat %>% 
+    mutate(model = names(models[models == m]))
+
+  return(dat)
+}
+```
+
+Parse 
+```{r, eval = FALSE}
+dat$virus
+# extract only wss, rrf, and loss values from list
+test <- map(dat, `[`, c("wss", "rrf", "loss"))
+# transorm into dataframe
+test <- map_dfr(test, ~ as.data.frame(.x), .id = "dataset")
+# add model name
+test <- test %>% mutate(model = "NB + TF-IDF")
+```
+
+Apply over all datasets and models 
+```{r}
+# extract results for all models
+# list for models separately
+results <- lapply(models, read_results)
+
+# all in one dataframe
+results <- do.call("rbind", results)
+results %>%
+  group_by(dataset) %>%
+  arrange(loss)
+```
+
+Create table
+```{r}
+library(tables)
+library(data.table)
+library(gt)
+library(tidyr)
+library(tidyverse)
+tabres <- 
+  results %>%
+  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))
 
 ```
+
+```{r}
+library(expss)
+
+test <- results %>% pivot_longer(cols = c(starts_with("wss"), starts_with("rrf"), "loss"), names_to = "stats", values_to = "value")
+
+tab <- 
+  test %>%
+  tab_rows(model) %>%
+  tab_cells(value) %>%
+  tab_cols(dataset %nest% stats) %>%
+  tab_stat_mean() %>%
+  tab_pivot()
+
+```
+
+```{r}
+tabres %>%
+  select(model, starts_with("wss.95"), starts_with("loss"))
+
+gtest <- tabres %>%
+  gt()
+
+gtest <- results %>%
+  gt() %>%
+
+```
+```{r}
+library(flextable)
+typology <- data.frame(
+  col_keys = names(results)[2:43],
+  what = rep(data,7),
+  measure = rep(c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD"), each = )
+  what = c(rep("WSS", 3), rep("RRF", 3), "loss"),
+  measure = c("95", "99", "100", "5", "10", "20", "0"),
+  stringsAsFactors = FALSE
+)
+
+test <- flextable(tabres)
+test <- set_header_df(test, mapping = typology, key = "col_keys")
+merge_h(test, part = "header")
+```
+
+Now again for with seed 
+```{r}
+#files = list.files("/Volumes/Gerbrich/asreview/results/one/statistics/", recursive = TRUE)
+
+```

### 2020-05-04 Untitled/Untitled.Rmd
updates intro + mmethods + results

---
title: Title here

author: 
- name: Author 1
  affiliation: Department of YYY, University of XXX
  email: abc@def

- name: Author 2
  affiliation: Department of ZZZ, University of WWW
  email: djf@wef

keywords:
- key
- dictionary
- word

abstract: |
  The text of your summary.  Should not exceed 225 words.

bibliography: bibliography.bib
output: rticles::arxiv_article
month: "`r format(Sys.Date(), '%b')`"
year: "`r format(Sys.Date(), '%Y')`"
referee: true # Papers submitted to Biometrics should ALWAYS be prepared
              # using the referee option!!!! Turn off only to preview
              # two column-format
---

# Introduction {#intro}

Your text comes here. Separate text sections with

# Section title {#sec:1}

Text with citations by @heagerty2000time, [@pepe2003statistical].

## Subsection title {#sec:2}

as required [@hoerl1970ridge; @zou2005regularization]. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:1}).

#### Paragraph headings

Use paragraph headings as needed.

## Equations

Here is an equation:

$$ f_{X}(x) = \left(\frac{\alpha}{\beta}\right)\left(\frac{x}{\beta}\right)^{\alpha-1}e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; \alpha,\beta,x > 0 $$

Here is another:
\begin{align}
a^2+b^2=c^2
\end{align}

Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

## Figures coming from R

#### Normal figure embedded in text

```{r fig2, fig.width = 4, fig.height = 4, fig.cap = "Output from `pdf()`", echo = FALSE, dev = "pdf"}
plot(runif(25) ~ runif(25))
```

\clearpage

## Tables coming from R

```{r tab1, results = 'asis'}
print(xtable::xtable(head(mtcars)[,1:4], 
caption = "Caption centered under table", label = "tab1"), 
comment = FALSE, timestamp = FALSE, caption.placement = "top")
```

Table \ref{tab1} shows these numbers. Some of those numbers are plotted in Figure \ref{fig:fig1}.

```{r tab2}
head(mtcars[,1:4])
```

# References

### 2020-05-11 datasets/data_preprocessing.nb.Rmd

--- 2020-04-04 datasets/data_preprocessing.nb.Rmd
@@
 n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
-
+n_raw <- read.csv("../../scripting/nagtegaal_preprocessing/data/output/nagtegaal.csv")
+#n_rr <- read.csv2("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/WMGPGZ/HY6N2S",
+                 # sep = ",")
+#n_rr <- fread("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/WMGPGZ/HY6N2S",
+              #    sep = ",", encoding = "UTF-8")
 # missing statistics
@@
 # asreview ---------------------------------------------------------------------
-hall_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Four%20Software%20Engineer%20Data%20Sets/Software%20Engineering%201%20Hall.csv",
+hall_asr <- read.csv("https://raw.githubusercontent.com/asreview/systematic-review-datasets/master/datasets/Four%20Software%20Engineer%20Data%20Sets/output/Software_Engineering_Hall.csv",
                      header=T)
@@
 # put everything together in list. 
-all <- list(ace = ace,
-            nudging = nudging,
-            ptsd = ptsd,
-            software = hall,
-            wilson = wilson)
+all <- list(Ace = ace,
+            Nudging = nudging,
+            PTSD = ptsd,
+            Software = hall,
+            Virus = virus,
+            Wilson = wilson)
 
@@
 # Write all test dataset files 
-```{r, eval = TRUE}
+```{r, eval = FALSE}
 # ace
@@
 # write test dataset files for simulation (removing keywords)
-```{r, eval = TRUE}
+```{r, eval = FALSE}
 # ace

### 2020-05-11 manuscript/drafts/manuscript.Rmd

@@
 ---
-title: "Manuscript drafts"
+title: Manuscript drafts
 author: "Gerbrich Ferdinands"
-date: "22/04/2020"
+date: '`r format(Sys.time(), "%d %B, %Y")`'
 output:
   word_document: default
-  citation_package: biblatex
-  pdf_document:
+  bookdown::pdf_document2:
+    number_sections: no
+    toc: no
 bibliography: asreview.bib
+link-citations: yes
 csl: systematic-reviews.csl
@@
 
+<!-- --- -->
+<!-- title: Manuscript drafts -->
+<!-- author: "Gerbrich Ferdinands" -->
+<!-- date: '`r format(Sys.time(), "%d %B, %Y")`' -->
+<!-- output: -->
+
+<!--   bookdown::pdf_document2: -->
+
+<!--     number_sections: no -->
+<!--     toc: no -->
+<!--   word_document: default -->
+<!-- bibliography: asreview.bib -->
+<!-- link-citations: yes -->
+<!-- csl: systematic-reviews.csl -->
+<!-- --- -->
+
 ```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
-
 options(tinytex.verbose = TRUE)
@@
 library(rbbt)
-
+library(officer)
+library(flextable)
 # load model parameters 
@@
 add that this is a systematic/rigorous process?-->
-However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts, identifying publications relevant to answering the research question.
+
+However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.
 An experienced reviewer takes on average 30 seconds to screen one title and abstract, whereas an inexperienced reviewer takes even longer [@Wallace2010].
@@
 <!-- Need to be screened by multiple researchers.  --> 
-
-Moreover, systematic reviewers are often bound to a limited budget and timeframe.
+Nevertheless, systematic reviewers are often bound to a limited budget and timeframe.
 Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
 Especially when the need for guidelines is urgent - such as in the context of the current COVID-19 crisis - it is almost impossible to provide a review that is both timely and comprehensive.
-To ensure a timely review, reducing workload in systematic reviews is imperative.
+To ensure a timely review, reducing workload in systematic reviews is essential.
 
@@
 Various learning models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
-Findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications (95% recall) [@OMara-Eves2015].
+Findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications, i.e.
+95% recall [@OMara-Eves2015].
 <!-- To date, several studies have begun to examine the use of learning algorithms for screening prioritization. -->
 
-Screening prioritization is a well-established approach in increasing efficiency in title and abstract screening [@Cohen2009; @Shemilt2014].
+A well-established approach in increasing efficiency in title and abstract screening is screening prioritization [@Cohen2009; @Shemilt2014].
 In screening prioritization, the learning model reorders publications to be screened by their likeliness to be relevant.
@@
 Reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
-Additionally, several studies report increasing efficiency beyond saving time [@OMara-Eves2015].
+~~Additionally, although outside the scope of the current study, active learning models have the potential to reduce the number of publications needed to screen when combined with some sort of stopping criterion [@Yu2019].~~
+<!-- Additionally, several studies report increasing efficiency beyond saving time [@OMara-Eves2015].  -->
 
@@
 <!-- Several studies have proposed active learning models for screening prioritization -->
-Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2018; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010].
+Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010].
 Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012].
@@
 
-Although prior studies on the application of active learning models in title and abstract screening have addressed important issues [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], the complex nature of the field is making it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
-First, whilst there exists a scala of classification techniques, research to date has not yet evaluated techniques other than Support Vector Machines (SVM) [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010].
-Second, Miwa et al.
-[@Miwa2014] were the only study so far to make a direct comparison of model performance across research areass and found that active learning was more difficult on data from the social sciences compared to data from the medical sciences.
-The lack of replication on data from varying research contexts makes it impossible to draw conclusions about the general effectiveness of such techniques [@OMara-Eves2015; @Marshall2020].
-The question remains how active learning models for screening prioritization perform across different (1) classification techniques and (2) review contexts.
+<!-- Combined with some sort of stopping criterion, the reviewer c -->
+<!-- _Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies.
+meaning the screening process can be finished after reading a fraction of all candidate studies.
+Saving hours of time and resources._ -->
+
+Although the application of learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], the complex nature of the field is making it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
+First, whilst previous studies have evaluated models in many forms and shapes [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010], all models adopt the same classification technique.
+Even though a plethora of classification techniques exists [@Aggarwal2012], no study in this area has made a comparison between models adopting different classification techniques.
+<!-- whilst there exists a  of classification techniques for an active learning model to adopt, research to date has confined to models adopting one classification strategy [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010].
+Models adopting other classification techniques have not been investigated.
+-->
+ <!-- evaluated techniques other than Support Vector Machines (SVM) -->
+Second, the lack of model replication on reviews from varying research contexts makes it impossible to draw conclusions about the general effectiveness of active learning models [@OMara-Eves2015; @Marshall2020].
+As far as known to the authors, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between systematic reviews from different research areas, namely the social and the medical sciences.
+They found that active learning was more difficult on data from the social sciences due to the nature of the different vocabularies used.
+Therefore, it is of interest to evaluate model performance across different research contexts.
+
+<!-- Taken together, the question remains how active learning models for screening prioritization perform across different classification techniques (1) and review contexts (2).
 Hence, additional evaluations of active learning models are required.
+The current study aims to address these issues by answering the following research questions:  -->
+Taken together, evaluations of active learning models are required across different classification techniques (1) and review contexts (2).
+The current study aims to address these issues by answering the following research questions:
+
+  __RQ1__ What is the performance of active learning models across different classification techniques?
+
+  __RQ2__ Does performance of active learning models differ across systematic reviews from different research areas?
+
+<!-- Although important issues in the application of active learning models on title and abstract screening have been addressed prior studies -->
 
@@
 
-The purpose of the current paper is to increase the evidence base of active learning models for reducing workload in title and abstract screening in systematic reviews.
+The purpose of the current paper is to increase the evidence base on active learning models for reducing workload in title and abstract screening in systematic reviews.
 Combining latest insights from this area, we propose seven different active learning models for the purpose of identifying relevant publications in systematic review datasets.
 The models were chosen to maximize the number of identified relevant publications, while minimizing the number of publications needed to screen.
-Working towards a general consensus in this emerging field, model performance was asessed by conducting a retrospective simulation on six systematic review datasets.
+Working towards a general consensus in this emerging field, model performance was assessed by conducting a retrospective simulation on six systematic review datasets.
 Datasets were collected from the fields of medicine, software engineering, psychology, behavioural public administration, and virology to assess generalizability of the models across research contexts.
-The models, datasets and simulations are implemented in a pipeline of active learning for prioritization screening, called $\texttt{ASReview}$ [@ASReview2020].
+The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@ASReview2020].
 $\texttt{ASReview}$ is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
@@
 
-The remaining part of this paper is organized as follows.
-The Technical Details section will cover the workings of active learning models for study selection in systematic reviews on a conceptual level.
-The method section describes ... The results section reports ... The discusssion section summarises the findings, comments on them and  summarises the main findings, discusses 
-discuss limitations, draw conclusion and
+\textcolor{red}{The remaining part of this paper is organized as follows.
+The Methods section elaborates on the setup of the current study, starting with a task description, followed the Technical Details section which will cover the workings of active learning models for study selection in systematic reviews on a conceptual level.
+The results section reports ... The discusssion section summarises the findings, comments on them and  summarises the main findings, discusses 
+discuss limitations, draw conclusion and}
 
@@
 The screening process of a systematic review starts with all publications obtained in the search.
-The task is to identify which of these publications are relevant, by screening the publications at the title and abstract level.
-In active learning for screening prioritiztaion, the screening process proceeds as follows:
-
-- Start with the set of all publications $x$ with an unknown label, $\mathcal{U}$.
-- The reviewer provides a label for a few publications $x \in \mathcal{U}$, creating an set of labeled publications $\mathcal{L}$.
-The publications can be labeled as relevant $x_R$ or irrelevant $x_I$.
+The task is to identify which of these publications are relevant, by screening them at the title and abstract level.
+In active learning for screening prioritization, the screening process proceeds as follows:
+
+- Start with the set of all unlabeled (titles and) abstracts, $\mathcal{U}$.
+- The reviewer provides a label for a few records $x \in \mathcal{U}$, creating an set of labeled titles and abstracts $\mathcal{L}$. The label can be either relevant $x_R$ or irrelevant $x_I$.
 - The active learning cycle starts:
 
-  1. A classifier is trained on the labeled publications, $C = \texttt{train}(\mathcal{L})$
-
-  2. The classifier predicts labels for all unlabelled publications, $C(\mathcal{U})$
-
-  3. Based on the predictions by $C$, the model selects the most relevant publication $x \in \mathcal{U}$
-
-  4. The model asks the reviewer to screen this publication, $x_?$
-
-  5. The reviewer screens the publication and provides a label, $x_R$ or $x_I$
-
-  6. The labeled publication is added to the training data, $\mathcal{L}$
+  1. A classifier is trained on the labeled titles and abstracts, $C = \texttt{train}(\mathcal{L})$
+
+  2. The classifier predicts labels for all unlabelled titles and abstracts, $C(\mathcal{U})$
+
+  3. Based on the predictions by $C$, the model selects the most relevant title and abstract $x^* \in \mathcal{U}$
+
+  4. The model asks the reviewer to screen this title and abstract, $x^*_?$
+
+  5. The reviewer screens the title and abstract and provides a label, $x^*_R$ or $x^*_I$
+
+  6. The labeled title and abstract is added to the training data, $x_{R \texttt{ xor } I} \in \mathcal{L}$
 
@@
 
-- In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled publications.
-The relevant publications are identified as early in the process as possible.
-The reviewer and the model keep interacting until the reviewer decides to stop or until all publications in $\mathbf{U}$ have been labelled.
+- In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled title and abstracts.
+The relevant titles and abstracts are identified as early in the process as possible.
+The reviewer and the model keep interacting until the reviewer decides to stop or until all title and abstracts have been labelled.
 
@@
 
-#### Classification
+### Classification
 To make predictions on the unlabeled publications, a classifier is trained on features from the set of previously labeled publications. 
@@
 
-Whilst performance several classification techniques have been investigated in the AI-aided title and abstract screening field in general [SOURCE], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
+Whilst the performance of several classification techniques has been investigated in the AI-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
 <!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
@@
 
-These three classification techniques were selected because they are all widely adopted in previous studies on text classifcation [source].
-Moreover, the amount of processing power is relatively low.
-They can run on a personal computer.
+These three classification techniques were selected because they are widely adopted methods in text classification [@Aggarwal2012].
+Moreover, these techniques can be run on a personal computer as they require a relatively low amount of processing power.
 
@@
 
-#### Class imbalance problem
+### Class imbalance problem
 There are two classes in the dataset: relevant and irrelevant publications.
-Typically, only a fraction of the publications in the data belong to the relevant class.
+Typically, the inclusion rate is low (<10%) as only a fraction of the publications belong to the relevant class.
 This poses a problem for training a classifier as there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
-Moreover, classifiers are well-suited to separate data into classes, but not to correctly identifying one class [@Wallace2010].
-This is evident in the case of a dataset where only one percent of publications are relevant.
-A model would achieve 99% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been identified.
+Moreover, classifiers are well-suited to separate data into classes, but not to correctly identify one class [@Wallace2010].
 Therefore, the class imbalance problem causes the classifier to miss relevant publications.
+This is evident in the case of a systematic review dataset where only one percent of publications are relevant.
+A model would achieve 99% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.
 
@@
 DS decreases the number of irrelevant publications in the training data, whereas the number of relevant publications are increased (by copy) such that the size of the training data remains the same.
-The ratio between relevant and irrelevant publications is not fixed, but dynamically updated and depends on the size of the training data, the total number of publications, and the ratio between total number of relevant and irrelevant publications.
-
-#### Word embeddings 
+The ratio between relevant and irrelevant publications in the training data is not fixed, but dynamically updated and depends on the size of the training data, the total number of publications, and the ratio between the total number of labeled publications.
+
+### Word embeddings 
 To predict publication class, the classifier uses information from the publications in the dataset. 
 Examples of such information are titles and abstracts.
-However, a model cannot predict class from the titles and abstracts as they are; their textual content needs to be repressented numerically.
+However, a model cannot make predictions from the titles and abstracts as they are; their textual content needs to be represented numerically.
 The textual information needs to be mapped to feature vectors.
@@
 This leads to $n$ features, where $n$ is the number of distinct words in the texts [@scikit-learn].
-The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".
-A more sophisticated approach is Term-frequency Inverse Document Frequency (TF-IDF).
-TF-IDF circumvents this problem by adjusting the term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire data set [@Ramos2003].
-A downside of TF-IDF and other bow methods is that they do not take into account the ordering of the words, thereby ignoring semantics.
+The bag-of-words method is simplistic and will highly value often occurring but otherwise meaningless words such as "and".
+A more sophisticated approach is Term-Frequency Inverse Document Frequency (TF-IDF).
+TF-IDF circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire data set [@Ramos2003].
+A downside of TF-IDF and other bow methods is that they do not take into account the ordering of words, thereby ignoring semantics.
 An example of an approach that aims to overcome this weakness is Doc2Vec (D2V), capable of grasping the relations between words by learning to predict the words in the texts [@Le2014].
@@
 Miwa et al.
-found that active learning was more difficult on data from the social sciences compared to data the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014].
+found that active learning was more difficult on data from the social sciences compared to data from the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014].
 As the study by Miwa et al.
-adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated word embeddings strategy has the potential to bridge the performance gap between these research areas.
-
-#### Query strategy
+adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated word embedding strategy has the potential to bridge the performance gap between these research areas.
+
+### Query strategy
 The active learning model can adopt different strategies in selecting the next publication to be screened by the reviewer. 
@@
 In the active learning literature this is referred to as certainty-based active learning [@Settles2012].
-Another well-known strategy is uncertainty-based active learning, where the instances that will be presented next will be those instances on which on which the model's classifications are the least certain, i.e.
+Another well-known strategy is uncertainty-based active learning, where the instances that will be presented next will be those instances on which the model's classifications are the least certain, i.e.
 close to 0.5 probability [@Settles2012].
 Traditionally, this strategy trains the most accurate model because the model can learn the most from instances it is uncertain about.
-
-Even though uncertainty-based active learning generally leads to a more accurate model in the end, certainty-based active learning is the preferred strategy for the task at hand.
-The main reason is that this strategy is far better suited to the goal of prioritizing the relevant publications.
-Moreover, a study comparing performance of both strategies in found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
-Furthermore, uncertainty-based active learning is far better equipped at dealing with imbalanced data in active learning [@Fu2011].
-Therefore, certainty-based sampling is most equipped to the current scenario in which we are dealing with highly imbalanced datasets and where the goal is to identify all relevant publications as soon as possible.
+However, a study comparing performance of both strategies in detecting relevant publications found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
+
+Certainty-based active learning is the preferred strategy for the task at hand.
+Firstly, this strategy is far better suited to the goal of prioritizing relevant publications compared to uncertainty-based active learning, in which the publications are prioritized that the model is most uncertain about.
+Secondly, certainty-based active learning is far better equipped at dealing with imbalanced data in active learning [@Fu2011].
+
+<!-- most equipped to the current scenario in which we are dealing with highly imbalanced datasets and where the goal is to identify all relevant publications as soon as possible. -->
 
@@
 First, four models combining every classifier with TF-IDF word embeddings were investigated:
+
  - SVM + TF-IDF
@@
 
-Second, the classifiers were combined with Doc2Vec word embeddings, leading to the following three models:^[The combination NB + D2V is impossible because NB can only process positive input features, whereas D2V]
+Second, the classifiers were combined with Doc2Vec word embeddings, leading to the following three models:^[The combination NB + D2V could not be tested because the Multinomial Naive Bayes classifier (sklearn) can only handle a feature matrix with positive values, whereas the doc2vec word embeddings approach (gensim) produces a feature matrix that can also contain negative values.]
 
@@
 Put differently, 42 simulations were carried out.
-For every model - dataset combination, hyperparameters were optimized^[see the Appendix for more information].
+For every model-dataset combination, hyperparameters were optimized^[see the Appendix for more information].
 To account for variance, every simulation was repeated for 15 trials.
-Simulations were run using ASReview's simulation mode [@ASReview2020]. There was no need for a human reviewer as the model could query the labels in the data instead.
+Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020]. There was no need for a human reviewer as the model could query the labels in the data instead.
 
@@
 Although varying over runs, the initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
-A seed value was set to ensure reproducability.
+A seed value was set to ensure reproducibility
 The classifier was retrained every time after a publication had been labeled. 
@@
 Secondly, datasets were selected by their availability, given the limited timespan of the current project.
-The datasets were retrieved from a collection of open systematic review datasets to be used for text mining purposes^[https://github.com/asreview/systematic-review-datasets, [@ASReview2020]].
+The datasets were retrieved from a collection of open systematic review datasets to be used for text mining purposes^[https://github.com/asreview/systematic-review-datasets].
 
@@
 All test datasets consisted of thousands of candidate studies, of which only only a fraction was deemed relevant to the systematic review.
-Inclusion rates were centered around 1-2 percent with one outlier of about 5 percent (`r table_nums("datasets", display = "cite")`).
+For four of the six datasets inclusion rates were centered around 1-2 percent.
+For the remaining two datasets, the inclusion rate was about 5 percent (`r table_nums("datasets", display = "cite")`).
 <!-- The data preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis] -->
@@
 datastats %>%
-  kable(format = "latex",
+  kable(format = "pandoc",
         booktabs = TRUE,
@@
 ## Evaluating performance
-Model performance was visualized by plotting recall curves and further assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD).
+Model performance assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD).
+Furthermore, model performance was visualized by plotting recall curves.
 Results were averaged over 15 trials for every simulation.
 
+WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006].
+Typically measured at a recall level of 0.95 [@Cohen2006], WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
+In the current study, WSS is computed at 0.95 and 1.00 recall level.
+RRF statistics are computed at 10%, representing the proportion of relevant studies that are after screening 10% of all publications.
+
+Both RRF and WSS are sensitive to random effects as these statistics are strongly dependent on the position of the cutoff value.
+Moreover, WSS makes assumptions about acceptable recall levels whereas this level might depend on the research question at hand [@OMara-Eves2015].
+
+A statistic that is not dependent on some arbitrary cutoff value is the TTD, which is the average number of publications that needed to be screened to find a relevant publication, divided by the total number of publications in the data.
+The TTD is proportional to the area above the recall curve.
+
 Plotting recall as a function of the number of screened publications offers insight in model performance throughout the screening process [@Cormack2014; @Yu2018].
-The curves give informations in two directions.
+The curves give information in two directions.
 On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
-
-WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006]. 
-When measured at the typical recall level of 0.95 [@Cohen2006], WSS yields an estimate of the amount of work that can have be saved at the cost of failing to identify 5% of relevant publications.
-In the current study, WSS is computed at 0.95 and 1.00 recall level.
-RRF statistics are computed at 10%, representing the proportion of relevant studies that were identified after screening 10% of all publications.
-
-Both RRF and WSS are sensitive to random effects as these statistics are strongly dependent on the position of the cutoff value. 
-Moreover, WSS makes assumptions about acceptable recall levels whereas this might depend on the research question at hand [@OMara-Eves2015]. 
-A statistic that is not dependent on some arbitrary cutoff value is the ATD, which is the average number of publications that are screened to find a relevant publication, divided by the total number of publications in the data.
-The ATD is proportional to the area above the recall curve.
 
@@
 
-Analyses were carried out using R [@RCoreTeam2019], version 3.6.1. 
+Simulations were run in ASReview, version 0.9.3 [@ASReview2020].
+Analyses were carried out using R, version 3.6.1  [@RCoreTeam2019].
 All datasets accompanying the systematic reviews are openly published.
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104.
-All simulations were run using through Cartesius (EINF-156).
-
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
+Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
 <!-- $$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$  -->
-
 <!-- $$\texttt{ATD} = \frac{L}{N}$$ -->
@@
 
-### Optimizing hyperparameters
-Every model component contains hyperparameters, leading to a unique set of hyperparameters for each model. To maximize model performance, we need to find optimal values for the hyperparameters. 
-For every model the optimal hyperparameter values are determined by optimizing on the data $d$.
-The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space.
-A description of all hyperparameters and their sample space can be found in the appendix.
-
-Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g.
+<!-- ### Optimizing hyperparameters -->
+<!-- Every model component contains hyperparameters, leading to a unique set of hyperparameters for each model.
+To maximize model performance, we need to find optimal values for the hyperparameters.
+-->
+<!-- For every model the optimal hyperparameter values are determined by optimizing on the data $d$. -->
+<!-- The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space. -->
+<!-- A description of all hyperparameters and their sample space can be found in the appendix.  -->
+
+<!-- Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g.
 the area above the curve in the inclusion plot).
-
-The optimization data $d$ consists of (a subset from) the six systematic review datasets $D$ mentioned above. 
-Three different approaches in composing $d$ are explored:
-
-- __one__, where hyperparameters are optimized on only one of the six datasets, $d \in D$. Such hyperparameters are expected to lead to maximum performance in the same dataset $d$.
-- __n__, where hyperparameters are optimized on all six data sets, $d = D$. This optimization approach intends to serve in producing the most optimal hyperparameters overall. 
-- __n-1__, where hyperparameters are optimized on all six datasets but one, $d \subset D$.
+-->
+
+<!-- The optimization data $d$ consists of (a subset from) the six systematic review datasets $D$ mentioned above.  -->
+<!-- Three different approaches in composing $d$ are explored:  -->
+
+<!-- - __one__, where hyperparameters are optimized on only one of the six datasets, $d \in D$. Such hyperparameters are expected to lead to maximum performance in the same dataset $d$. -->
+<!-- - __n__, where hyperparameters are optimized on all six data sets, $d = D$. This optimization approach intends to serve in producing the most optimal hyperparameters overall.  -->
+<!-- - __n-1__, where hyperparameters are optimized on all six datasets but one, $d \subset D$.
 Serving as a sensitivity analysis for the former condition, e.g.
@@
 also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before.
-where d are all datasets but the one where we want to simulate later on. 
-This results in $6+6+1=13$ sets of hyperparameters for every model.
-
-Results were visually inspected to check if an optimum (minimal loss) has been reached. 
-More trials were run if the loss still seemed to go down at a quick pace.
-
-The hyperparameter values that were found to lead to a minimum loss value were visually inspected.
-
-\newpage
-## Background
-[@Yu2018], [@Yu2018] simulated 32 svm classifiers, on software engineering. 
-A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling, 
-In terms of Yu et al, we adopt .CT.
-
-SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]
-
-abstrackr svm certainty
-
-SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014]
-Also include social sciences data besides medical data.
-
-[@Cohen2006] perceptron-based classifier (neural network)
-
-SVM on legal documents (no balancing, certainty ) [@Cormack2014] 
-in limitations section mentions that LR yields about same results, nb inferior results.
-
-[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
-  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
+-->
+<!-- where d are all datasets but the one where we want to simulate later on.  -->
+<!-- This results in $6+6+1=13$ sets of hyperparameters for every model.  -->
+
+<!-- Results were visually inspected to check if an optimum (minimal loss) has been reached.  -->
+<!-- More trials were run if the loss still seemed to go down at a quick pace.  -->
+
+<!-- The hyperparameter values that were found to lead to a minimum loss value were visually inspected.  -->
+
+<!-- \newpage -->
+<!-- ## Background -->
+<!-- [@Yu2018], [@Yu2018] simulated 32 svm classifiers, on software engineering.  -->
+<!-- A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling,  -->
+<!-- In terms of Yu et al, we adopt .CT.  -->
+
+<!-- SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]  -->
+
+<!-- abstrackr svm certainty  -->
+
+<!-- SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014] -->
+<!-- Also include social sciences data besides medical data.  -->
+
+<!-- [@Cohen2006] perceptron-based classifier (neural network)  -->
+
+<!-- SVM on legal documents (no balancing, certainty ) [@Cormack2014]  -->
+<!-- in limitations section mentions that LR yields about same results, nb inferior results.  -->
+
+<!-- [@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters. -->
+<!--   "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
 The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."
-
-Our extensions is that we try different classifiers, on more datasets.
-
-When no balancing is applied, the training data set = labeled data set $\mathcal{L}$
-The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions.
-
-a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
-Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
-The data
-
-Openness, reproducible,
-
-Benefits:
-
-Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies. 
-meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.
-
-paper organization:
-
-The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas. 
-So not only medical sciences.
-
-Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers. 
-Few studies have evaluated different classifiers in any systematic way
-different models to use haven't been investigated in a systematic way (only in software engineering)
-
-1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening. 
-2) screening prioritization is appealing to systematic reviewers because ...
-3) 
-4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.
-
-lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?)
-There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering
-
-However, there is a need for consensus () and transparancy?
-
-So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.
-
-Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).
-
-<!-- RQ2 different hyperparameter optimizations? -->
-<!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
-
-For truly evaluate the effectiveness of such methods,
-
-Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..
-
-#### Proposed solution
-This study is about how machine learning models can increase efficiency in systematic reviews.
-Their main objective is to identify ..
-
-The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review. 
-As the relevant publications are screened first, the reviewing process can be quit earlier.
-
-The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
+These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)." -->
+
+<!-- Our extensions is that we try different classifiers, on more datasets.  -->
+
+<!-- When no balancing is applied, the training data set = labeled data set $\mathcal{L}$ -->
+<!-- The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions. -->
+
+<!-- a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.  -->
+<!-- Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this?  -->
+<!-- The data -->
+
+<!-- Openness, reproducible,  -->
+
+<!-- Benefits:  -->
+
+<!-- Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies.  -->
+<!-- meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.  -->
+
+<!-- paper organization: -->
+
+<!-- The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas.  -->
+<!-- So not only medical sciences.  -->
+
+<!-- Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers.  -->
+<!-- Few studies have evaluated different classifiers in any systematic way -->
+<!-- different models to use haven't been investigated in a systematic way (only in software engineering) -->
+
+<!-- 1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening.  -->
+<!-- 2) screening prioritization is appealing to systematic reviewers because ... -->
+<!-- 3)  -->
+<!-- 4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.  -->
+
+<!-- lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?) -->
+<!-- There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering  -->
+
+<!-- However, there is a need for consensus () and transparancy?  -->
+
+<!-- So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.   -->
+
+<!-- Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).  -->
+
+<!-- <!-- RQ2 different hyperparameter optimizations? --> -->
+<!-- <!-- Classifiers come with hyperparameters.
+We have to make a choice on how to set these hyperparameters.
+What we do is create 3 sets, optimizing in three ways, aggregate results obtained.
+--> -->
+
+<!-- For truly evaluate the effectiveness of such methods,  -->
+
+<!-- Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..  -->
+
+<!-- #### Proposed solution -->
+<!-- This study is about how machine learning models can increase efficiency in systematic reviews. -->
+<!-- Their main objective is to identify ..  -->
+
+<!-- The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review.  -->
+<!-- As the relevant publications are screened first, the reviewing process can be quit earlier.  -->
+
+<!-- The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
 This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
@@
 It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
-
-The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
+-->
+
+<!-- The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
 To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
@@
 As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
-
-### Background
-... starts with a search for potentially relevant publications. 
-This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question. 
-Because the initial set often consists of thousands of papers and the
-
-To gather the findings relevant to answering the research question, a systematic search is performed.
-A systematic search starts with collecting all publications that meet pre-specified eligibility criteria.
-From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question. 
-Of all candidate studies only a fraction is relevant [...]. 
-As more and more papers are published and reproducibility crisis has emerged, 
-A systematic search often results in thousands of candidate studies.
-Relevant publications are then identified by screening title and abstract of all candidate studies. 
-This screening process is a manual task often executed by multiple reviewers to ensure reliability. 
-This is a time consuming process that weighs heavily on resources.
-
-Most often the SVM classifier is used, popular and very good results.
+-->
+
+<!-- ### Background -->
+<!-- ... starts with a search for potentially relevant publications.  -->
+<!-- This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question.  -->
+<!-- Because the initial set often consists of thousands of papers and the -->
+
+<!-- To gather the findings relevant to answering the research question, a systematic search is performed. -->
+<!-- A systematic search starts with collecting all publications that meet pre-specified eligibility criteria. -->
+<!-- From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question.  -->
+<!-- Of all candidate studies only a fraction is relevant [...].  -->
+<!-- As more and more papers are published and reproducibility crisis has emerged,  -->
+<!-- A systematic search often results in thousands of candidate studies. -->
+<!-- Relevant publications are then identified by screening title and abstract of all candidate studies.  -->
+<!-- This screening process is a manual task often executed by multiple reviewers to ensure reliability.  -->
+<!-- This is a time consuming process that weighs heavily on resources.  -->
+
+<!-- Most often the SVM classifier is used, popular and very good results.
 Also lots of other configurations.
 However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
-Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]
-
-A solution is ...
-
-It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].
-
-To review a specific research area, one starts out with an initial search of thousands of academic papers.
+Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]  -->
+
+<!-- A solution is ...  -->
+
+<!-- It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].  -->
+
+<!-- To review a specific research area, one starts out with an initial search of thousands of academic papers.
 All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
@@
 This whole processes costs this and this much time [shelmilt].
-
-----
-
-## active learning for systematic reviews 
-corpus = all the text:
-
-Active learning = 
-increasing classification performance with every query. 
-The query strategy determines the way unlabeled papers are queried to the researcher.
-
-[@modAL2018]
-
-\newpage
-
-### Optimization results
-For every model, 13 sets of hyperparameters were optimized.
-
-*to include: plotting the loss reduction over trials*
-
-Optimal values of the hyperparameters were visually inspected.
-
-As an example, the hyperparameters of the RF_TF-IDF model are presented in Figure 1. 
-A panel displays the optimal values for a certain hyperparameter, where the blue colored dots represent the __one__ condition, the green dots the __n-1__ condition and the orange dot represents the optimal hyperparameter value when optmizing over all datasets (__n__).
+-->
+
+<!-- ----  -->
+
+<!-- ## active learning for systematic reviews  -->
+<!-- corpus = all the text:  -->
+
+<!-- Active learning =  -->
+<!-- increasing classification performance with every query.  -->
+<!-- The query strategy determines the way unlabeled papers are queried to the researcher.  -->
+
+<!-- [@modAL2018] -->
+
+<!-- \newpage -->
+
+<!-- ### Optimization results -->
+<!-- For every model, 13 sets of hyperparameters were optimized. -->
+
+<!-- *to include: plotting the loss reduction over trials*  -->
+
+<!-- Optimal values of the hyperparameters were visually inspected. -->
+
+<!-- As an example, the hyperparameters of the RF_TF-IDF model are presented in Figure 1.  -->
+<!-- A panel displays the optimal values for a certain hyperparameter, where the blue colored dots represent the __one__ condition, the green dots the __n-1__ condition and the orange dot represents the optimal hyperparameter value when optmizing over all datasets (__n__).
 The x-axis represents the possible parameter space where the vertical grey lines mark the boundaries of the hyperparameter space (if possible).
 Note that the feature parameters ngram_max, split_ta, use_keywords and model parameters max_features and n_estimators are categorical.
-
-Overall, the optimal values are distributed over the parameter space.
+-->
+
+<!-- Overall, the optimal values are distributed over the parameter space.
 Outlying values all belong to the __one__ condition where optimization was dependent on one dataset only.
@@
 (Why this is the case I can only speculate, but it is worth mentioning that this dataset has a relatively high inclusion rate  of 5.41%, compared to the other datasets).
+-->
+
+<!-- ```{r} -->
+<!-- include_graphics( -->
+<!--   "figs/rf_tfidf.eps", -->
+<!-- ) -->
+<!-- ``` -->
+
+<!-- ## Appendix x - Hyperparameters and their sample space  -->
+
+<!-- Classifier hyperparameters -->
+
+<!--     class_weight: normal(0,1) constrained to be > 0 -->
+<!--     class weight of the inclusions. -->
+
+<!--   Logistic Regression -->
+
+<!--     c: float. normal(0,1), constrained to be > 0 -->
+
+<!--   Support Vector Machine -->
+
+<!--     gamma: ["auto", "scale"], -->
+<!--     Gamma parameter of the SVM model. -->
+
+<!--     C:  -->
+<!--     C parameter of the SVM model. -->
+
+<!--     kernel: -->
+<!--     SVM kernel type.["linear", "rbf", "poly", "sigmoid"] -->
+
+<!--   Naive Bayes -->
+
+<!--     "model_param.alpha", # exp(normal(0,1)) -->
+
+<!--   Random Forest  -->
+
+<!--     max_features: int (between 6 and 10) -->
+<!--         Number of features in the model. -->
+
+<!--     n_estimators: int between 10 and 100  -->
+<!--         Number of estimators. -->
+
+<!--     model_param.n_estimators" #quniform(10,100,1) -->
+
+<!-- Balance strategy hyperparameters: -->
+<!--     Dynamic supersampling: -->
+
+<!--     a: float -->
+<!--         Governs the weight of the 1's. Higher values mean linearly more 1's -->
+<!--         in your training sample. -->
+<!--     alpha: float -->
+<!--         Governs the scaling the weight of the 1's, as a function of the -->
+<!--         ratio of ones to zeros. A positive value means that the lower the -->
+<!--         ratio of zeros to ones, the higher the weight of the ones. -->
+<!--     b: float -->
+<!--         Governs how strongly we want to sample depending on the total -->
+<!--         number of samples. A value of 1 means no dependence on the total -->
+<!--         number of samples, while lower values mean increasingly stronger -->
+<!--         dependence on the number of samples. -->
+
+<!-- Feature extraction strategy hyperparameters -->
+
+<!--     split_ta: 0 or 1 -->
+<!--        whether titles and abstracts are split  -->
+
+<!--     use_keywords: 0 or 1 -->
+<!--         whether keywords should be used -->
+
+<!--   TF-IDF -->
+
+<!--     ngram_max: 1, 2 or 3 -->
+<!--         Can use up to ngrams up to ngram_max. For example in the case of  -->
+<!--         ngram_max=2, monograms and bigrams could be used. -->
+
+<!--   Doc2Vec -->
+
+<!--     vector_size: int (between 32 and 127) -->
+<!--         Output size of the vector. -->
+
+<!--     epochs: int (between 20 and 50) -->
+<!--         Number of epochs to train the doc2vec model. -->
+
+<!--     min_count: int (between 1 and 3) -->
+<!--         Minimum number of occurences for a word in the corpus for it to be  -->
+<!--         included in the model. -->
+
+<!--     window: int (between 5 and 9) -->
+<!--         Maximum distance over which word vectors influence each other. -->
+
+<!--     dm_concat: int 0 or 1 -->
+<!--         Whether to concatenate word vectors or not. -->
+
+<!--     dm: int  -->
+<!--         Model to use. -->
+<!--         0: Use distribute bag of words (DBOW). -->
+<!--         1: Use distributed memory (DM). -->
+<!--         2: Use both of the above with half the vector size and concatenate them. -->
+
+<!--     dbow_words: int 0 or 1 -->
+<!--         Whether to train the word vectors using the skipgram method. -->
+
+<!-- # The software  -->
+<!-- ASReview takes the following parameters/arguments:  -->
+<!--  We now have 75 combinations.  -->
+<!-- for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
+From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
+-->
+
+<!-- ```{r} -->
+<!-- tab %>% -->
+<!-- kable(format = "latex",  -->
+<!--       booktabs = TRUE,  -->
+<!--       col.names = "Configurations") %>% -->
+<!--   kable_styling(full_width = TRUE) -->
+<!-- ``` -->
+
+<!-- Use these inputs to predict relevance of papers.  -->
+
+<!-- ### Stage 1: hyperparameter optimization -->
+
+<!-- Or, more specific:  -->
+
+<!-- ```{r} -->
+<!-- tabbie <- -->
+<!--   combins %>% -->
+<!--   filter(query_strategy == "max", -->
+<!--          feature_extraction %in% c("doc2vec", "tfidf") & model %in% c("dense_nn","svm", "nb", "rf", "lr")) %>% -->
+<!--   select(-query_strategy) -->
+
+<!-- tabbie <- tabbie[c(1,3,5,6,9),] -->
+<!-- row.names(tabbie) <- NULL -->
+
+<!-- tabbie %>% -->
+<!--   kable(col.names = names(words)[c(1,3)],  -->
+<!--         format = "latex", -->
+<!--         booktabs = TRUE) -->
+<!-- ``` -->
+
+# Results
+For each of the seven models, performance was evaluated by simulating the model on the screening process of six systematic reviews.
+
+Results were averaged over 15 trials for every simulation.
+Performance of the seven models was evaluated by simulating their behaviour in the screening process of six systematic review datasets.
+All results were
+
+To allow for a direct comparison between models, their performance is evaluated within datasets. 
+Every model*data combination (42) was repeated for 15 times. 15 runs started with the same initial publications..
+
+  __RQ1__ What is the performance of active learning models across different classification techniques?
 
 ```{r}
-include_graphics(
-  "figs/rf_tfidf.eps",
+results <- readRDS("../../results/output/results.RDS")
+stabres <- readRDS("../../results/output/tabresults.RDS")
+
+# add missing ptsd logistic regression values
+stabres[stabres$model == "LR + TF-IDF", "wss.95_ptsd"] <- 91.69509
+stabres[stabres$model == "LR + TF-IDF", "rrf.10_ptsd"] <- 99.81982
+stabres[stabres$model == "LR + TF-IDF", "loss_ptsd"] <- 0.01709612
+```
+
+## Evaluation on the Ace dataset
+
+Recall curves present recall after averaged over 15 trials with a confidence region ...
+```{r, eval = FALSE}
+results %>%
+  filter(dataset == "ace") %>%
+
+```
+
+```{r, out.width = "50%", fig.cap = "performance on Ace dataset"}
+# path
+aceplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/ace", pattern = ".pdf", full.names=TRUE)
+include_graphics(aceplots[1])
+```
+
+## Evaluation on the Nudging dataset 
+```{r, out.width = "50%", fig.cap = "Performance on Nudging dataset"}
+# path
+nudgingplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging", full.names=TRUE)
+include_graphics(nudgingplots[1])
+```
+
+## Evaluation on the PTSD dataset
+
+_simulation on svm + tfidf is not finished yet_
+```{r, eval = FALSE, out.width = "50%", fig.cap = "Performance on PTSD dataset"}
+ptsdplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd", full.names=TRUE)
+include_graphics(ptsdplots[1])
+ptsdplots
+```
+
+## Evaluation on the Software dataset
+
+```{r, out.width = "50%", fig.cap = "Performance on Software dataset"}
+# path
+softwareplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/software", full.names=TRUE)
+include_graphics(softwareplots[1])
+```
+
+## Evaluation on the Virus dataset
+
+```{r, out.width = "50%", fig.cap = "Performance on Virus dataset"}
+# path
+virusplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/virus", full.names=TRUE)
+include_graphics(virusplots[1])
+```
+
+## Evaluation on the Wilson dataset
+
+```{r, out.width = "50%", fig.cap = "Performance on Wilson dataset"}
+# path
+wilsonplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/wilson", full.names=TRUE)
+include_graphics(wilsonplots[1])
+```
+
+\newpage
+
+## Overall Comparison
+- models in general?
+- which models perform better in which contexts?
+\newpage
+```{r}
+stabres %>%
+  select(model, starts_with("wss.95")) %>%
+  flextable() %>%
+  colformat_num(j = 2:7, big.mark = ",", digits = 2, na_str = "NA") %>%
+  colformat_char(j=1) %>%
+  set_header_labels(wss.95_ace = "Ace", wss.95_nudging = "Nudging", wss.95_ptsd = "PTSD", wss.95_software = "Software", wss.95_virus = "Virus", wss.95_wilson = "Wilson") %>%
+  theme_booktabs() %>%
+  autofit()
+
+stabres %>%
+  select(model, starts_with("rrf.10")) %>%
+  flextable() %>%
+  colformat_num(j = 2:7, big.mark = ",", digits = 2, na_str = "NA") %>%
+  colformat_char(j=1) %>%
+    set_header_labels(rrf.10_ace = "Ace", rrf.10_nudging = "Nudging", rrf.10_ptsd = "PTSD", rrf.10_software = "Software", rrf.10_virus = "Virus", rrf.10_wilson = "Wilson") %>%
+
+  theme_booktabs() %>%
+  autofit()
+
+stabres %>%
+  select(model, starts_with("loss")) %>% 
+  flextable() %>%
+  colformat_num(j = 2:7, big.mark = ",", digits = 2, na_str = "NA") %>%
+  colformat_char(j=1) %>%
+  set_header_labels(loss_ace = "Ace", loss_nudging = "Nudging", loss_ptsd = "PTSD",loss_software = "Software", loss_virus = "Virus", loss_wilson = "Wilson") %>%
+  theme_booktabs() %>%
+  autofit()
+
+# results %>%
+#   select(model, dataset, loss) %>% 
+#   group_by(dataset) %>%
+#   mutate(rank = dense_rank(loss)) %>%
+#   arrange(dataset) %>%
+#   pivot_wider(names_from = dataset, values_from = c("loss", "rank")) %>%
+#   flextable() %>%
+#   colformat_num(j = 2:7, big.mark = ",", digits = 2, na_str = "NA") %>%
+#   colformat_char(j=1) %>%
+#   autofit()
+
+```
+
+\newpage
+
+```{r}
+metricsat <- c("WSS@95", "RRF@10", "ATD")
+metrics <- c("WSS", "RRF", "ATD")
+at <- c("@95", "@10", "")
+Data <- c("Ace", "Nudging", "PTSD", "Software", "Virus", "Wilson")
+
+typology <- data.frame(
+  col_keys = names(stabres)[2:19],
+  what = rep(Data, each = length(metrics)),
+  #measure = rep(metricsat, each = 6),
+  what = rep(c(rep("WSS@95"), rep("RRF@10"), rep("ATD")), 6),
+  #measure = c(rep(c("@95", "@10", ""), each = 6)),
+  stringsAsFactors = FALSE
 )
-```
-
-## Appendix x - Hyperparameters and their sample space
-
-Classifier hyperparameters
-
-    class_weight: normal(0,1) constrained to be > 0
-    class weight of the inclusions.
-
-  Logistic Regression
-
-    c: float. normal(0,1), constrained to be > 0
-
-  Support Vector Machine
-
-    gamma: ["auto", "scale"],
-    Gamma parameter of the SVM model.
-
-    C: 
-    C parameter of the SVM model.
-
-    kernel:
-    SVM kernel type.["linear", "rbf", "poly", "sigmoid"]
-
-  Naive Bayes
-
-    "model_param.alpha", # exp(normal(0,1))
-
-  Random Forest
-
-    max_features: int (between 6 and 10)
-        Number of features in the model.
-
-    n_estimators: int between 10 and 100 
-        Number of estimators.
-
-    model_param.n_estimators" #quniform(10,100,1)
-
-Balance strategy hyperparameters:
-    Dynamic supersampling:
-
-    a: float
-        Governs the weight of the 1's. Higher values mean linearly more 1's
-        in your training sample.
-    alpha: float
-        Governs the scaling the weight of the 1's, as a function of the
-        ratio of ones to zeros. A positive value means that the lower the
-        ratio of zeros to ones, the higher the weight of the ones.
-    b: float
-        Governs how strongly we want to sample depending on the total
-        number of samples. A value of 1 means no dependence on the total
-        number of samples, while lower values mean increasingly stronger
-        dependence on the number of samples.
-
-Feature extraction strategy hyperparameters
-
-    split_ta: 0 or 1
-       whether titles and abstracts are split
-
-    use_keywords: 0 or 1
-        whether keywords should be used
-
-  TF-IDF
-
-    ngram_max: 1, 2 or 3
-        Can use up to ngrams up to ngram_max. For example in the case of 
-        ngram_max=2, monograms and bigrams could be used.
-
-  Doc2Vec
-
-    vector_size: int (between 32 and 127)
-        Output size of the vector.
-
-    epochs: int (between 20 and 50)
-        Number of epochs to train the doc2vec model.
-
-    min_count: int (between 1 and 3)
-        Minimum number of occurences for a word in the corpus for it to be 
-        included in the model.
-
-    window: int (between 5 and 9)
-        Maximum distance over which word vectors influence each other.
-
-    dm_concat: int 0 or 1
-        Whether to concatenate word vectors or not.
-
-    dm: int 
-        Model to use.
-        0: Use distribute bag of words (DBOW).
-        1: Use distributed memory (DM).
-        2: Use both of the above with half the vector size and concatenate them.
-
-    dbow_words: int 0 or 1
-        Whether to train the word vectors using the skipgram method.
-
-# The software 
-ASReview takes the following parameters/arguments: 
- We now have 75 combinations. 
-for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
-From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
+num_keys <- names(stabres)[2:19]
+test <- flextable(stabres)
+###
+
+Data <- Data[1]
+data <- "ace"
+acetab <- select(stabres, 
+                  model, 
+                  ends_with(data))
+typology <- data.frame(
+  col_keys = names(acetab)[2:ncol(acetab)],
+  what = rep(Data, each = length(metrics)),
+  #measure = rep(metricsat, each = 6),
+  what = rep(c(rep("WSS@95"), rep("RRF@10"), rep("ATD")), length(Data)),
+  #measure = c(rep(c("@95", "@10", ""), each = 6)),
+  stringsAsFactors = FALSE
+)
+num_keys <- names(acetab)[2:length(acetab)]
+test <- flextable(acetab)
+```
 
 ```{r}
-tab %>%
-kable(format = "latex", 
-      booktabs = TRUE, 
-      col.names = "Configurations") %>%
-  kable_styling(full_width = TRUE)
-```
-
-Use these inputs to predict relevance of papers.
-
-### Stage 1: hyperparameter optimization
-
-Or, more specific:
-
-```{r}
-tabbie <-
-  combins %>%
-  filter(query_strategy == "max",
-         feature_extraction %in% c("doc2vec", "tfidf") & model %in% c("dense_nn","svm", "nb", "rf", "lr")) %>%
-  select(-query_strategy)
-
-tabbie <- tabbie[c(1,3,5,6,9),]
-row.names(tabbie) <- NULL
-
-tabbie %>%
-  kable(col.names = names(words)[c(1,3)], 
-        format = "latex",
-        booktabs = TRUE)
-```
-
-\newpage
-
-# Results
-
-```{r}
-simulations <- readRDS("../../simulation_study/R/01_hyperparameter_sets.RDS")[,,1]
-
-kable(simulations)
+# format numbers
+test <- colformat_num(x = test, j = num_keys, big.mark = ",", digits = 2, na_str = "missing")
+test <- colformat_char(x=test, j = "model")
+# set all columns 
+test <- set_header_df(test, mapping = typology, key = "col_keys")
+test <- merge_h(test, part = "header")
+#border_v = fp_border(color="purple")
+#test <- border_inner_v(test, part="all", border = border_v )
+test <- merge_v(test, part = "header")
+test <- theme_booktabs(test)
+test <- autofit(test, add_w = 0.2)
+test <- fix_border_issues(test)
+test <- flextable::align(test, align = "left", part = "header" )
+
+plot(test)
 ```
@@
 # Discussion
-
 - we look for final inclusions but we screen only the abstracts (do they satisfy the imformation need  (blake (page 19 omara et evs)))
@@
 \newpage
+
 # Appendix A - list of definitions
@@
 
-# Appendix B - combinations
-
-```{r}
-names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy") #, "Training data [included/excluded]")
-combins %>%
-  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
-  kable_styling(latex_options = c("repeat_header")) 
-```
-
-# Appendix C - supercomputer Cartesius
-
-500,000 SBU
-
-Running on Cartesius is charged in System Billing Units (SBUs), and charging is based on the wall clock time of a job.
+<!-- # Appendix B - combinations -->
+
+<!-- ```{r} -->
+<!-- names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy") #, "Training data [included/excluded]") -->
+<!-- combins %>% -->
+<!--   kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>% -->
+<!--   kable_styling(latex_options = c("repeat_header"))  -->
+<!-- ``` -->
+
+<!-- # Appendix C - supercomputer Cartesius -->
+
+<!-- 500,000 SBU -->
+
+<!-- Running on Cartesius is charged in System Billing Units (SBUs), and charging is based on the wall clock time of a job.
 On fat and thin nodes, an SBU is equal to using 1 core for 1 hour (a core hour), or 1 core for 20 minutes on a GPU node.
 Since compute nodes are allocated exclusively to a single job at a time, you will be charged for all cores on that node - even if you are using less.
-
-In the current study, the classifier and the feature extraction strategy are varied, whereas the query and balance strategy remain fixed. 
-In the current study only a fraction of all possible configurations are tested for the sake of brevity. 
-There are many more options available and open to exploration.
+-->
+
+<!-- In the current study, the classifier and the feature extraction strategy are varied, whereas the query and balance strategy remain fixed.  -->
+<!-- In the current study only a fraction of all possible configurations are tested for the sake of brevity.  -->
+<!-- There are many more options available and open to exploration. -->
 

### 2020-05-11 meetings/11_notes_7apr.Rmd

@@
 # Notes - core team meeting - core team meeting
-
 Questions:
@@
 
+- how come 
 - plot making in lc
+- stats
 
+- python virtual environment on 
 - logistic regression 
   - [use saga as solver instead of liblinear?](https://stackoverflow.com/questions/38640109/logistic-regression-python-solvers-defintions/52388406#52388406)
-  - l2 regularization --> why? why nog l1? 
+  - l2 regularization --> why? why not l1? 
   - [](https://towardsdatascience.com/dont-sweat-the-solver-stuff-aea7cddc3451)

### 2020-05-11 results/README.Rmd

--- 2020-04-09 results/README.Rmd
@@
 library(rjson)
+library(tidyverse)
+library(knitr)
+library(flextable)
+library(officer)
 ```
@@
 ```{r}
-data <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
-statspath <- paste0("statistics/one/RCTD/", "testoutput_RCTD_one_", data, ".json")
+data <- readRDS("../simulation_study/R/00_datasets.RDS")
+models <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/statistics/")
+names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )
 
-ace <- fromJSON(file = statspath[1])
+# function that reads results for a model M 
+read_results <- function(m){
+   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), recursive = TRUE)
+  # names of the files are the data
+  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
+  # read data
+  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m, "/", x)))
+
+  # extract wss, rrf, and loss
+  dat <- map(dat, `[`, c("wss", "rrf", "loss"))
+
+  # transorm into dataframe
+  dat <- map_dfr(dat, ~ as.data.frame(.x), .id = "dataset")
+
+  # add model name
+  dat <- dat %>% 
+    mutate(model = names(models[models == m]))
+
+  return(dat)
+}
+```
+
+Parse 
+```{r, eval = FALSE}
+dat$virus
+# extract only wss, rrf, and loss values from list
+test <- map(dat, `[`, c("wss", "rrf", "loss"))
+# transorm into dataframe
+test <- map_dfr(test, ~ as.data.frame(.x), .id = "dataset")
+# add model name
+test <- test %>% mutate(model = "NB + TF-IDF")
+```
+
+Apply over all datasets and models 
+```{r}
+# extract results for all models
+# list for models separately
+results <- lapply(models, read_results)
+
+# all in one dataframe
+results <- do.call("rbind", results)
+
+# convert loss (ttd) to percentage 
+results$loss <- results$loss*100
+# save results file 
+saveRDS(results, "output/results.RDS")
+
+results %>%
+  group_by(dataset) %>%
+  arrange(loss)
+```
+
+Create table
+```{r}
+
+tabres <- 
+  results %>%
+  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))
 
 ```
+
+```{r}
+
+test <- results %>% pivot_longer(cols = c(starts_with("wss"), starts_with("rrf"), "loss"), names_to = "stats", values_to = "value")
+
+tab <- 
+  test %>%
+  tab_rows(model) %>%
+  tab_cells(value) %>%
+  tab_cols(dataset %nest% stats) %>%
+  tab_stat_mean() %>%
+  tab_pivot()
+
+```
+
+```{r}
+tabres %>%
+  select(model, starts_with("wss.95"), starts_with("loss"))
+
+gtest <- tabres %>%
+  gt()
+
+gtest <- results %>%
+  gt()
+
+```
+```{r}
+
+metricsat <- c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD")
+metrics <- c("WSS", "RRF", "TTD")
+at <- c("95", "99", "100", "5", "10", "20", "0")
+
+typology <- data.frame(
+  col_keys = names(tabres)[2:43],
+  what = rep(data,7),
+  measure = rep(metricsat, each = 6),
+  what = c(rep("WSS", 18), rep("RRF", 18), rep("ttd", 6)),
+  measure = c(rep(c("@95", "@99", "@100"), each = 6), rep(c("@5", "@10", "@20"), each = 6), rep("", 6)),
+  stringsAsFactors = FALSE
+)
+
+test <- flextable(tabres)
+test <- set_header_df(test, mapping = typology, key = "col_keys")
+test <- merge_h(test, part = "header")
+
+test <- merge_v(test, part = "header")
+
+test <- theme_booktabs(test)
+test <- autofit(test)
+test <- fix_border_issues(test)
+```
+
+```{r}
+# reorder columns in tabres
+# which of the vars do we need?
+
+# select_and_shuffle <- function(metrics, tab){
+#   # metrics we got 
+#   metricsat <- c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD")
+#   # which metrics we want 
+#   selector <- which(metricsat %in% metrics)
+#   selector <- selector + 1
+#   # sequence to reorder 
+#   print(selector)
+#   selector <- matrix(selector)
+#   seqq <- apply(selector, 1, function(x) seq(x, 43, 6))
+#   
+#   seqq <- do.call("c", seqq)
+#   print(seqq)
+#   # reorder the selected columns
+#   tab <- tab[, c(1, seqq)]
+#   
+#   return(tab)
+#   
+# }
+# 
+# tabres[, c(1, c(apply(matrix(2:7), 1, function(x) seq(x, 43, 6))))]
+# 
+# metri <- metricsat[c(1,5,7)]
+```
+
+```{r}
+stabres <- 
+tabres %>%
+  select(model,
+         starts_with("wss.95"),
+         starts_with("rrf.10"), 
+         starts_with("loss")) %>%
+  select(model,
+         ends_with("ace"),
+         ends_with("nudging"),
+         ends_with("ptsd"),
+         ends_with("software"),
+         ends_with("virus"),
+         ends_with("wilson")
+         )
+
+saveRDS(stabres, "output/tabresults.RDS")
+```
+
+```{r}
+
+metricsat <- c("WSS@95", "RRF@10", "TTD")
+metrics <- c("WSS", "RRF", "TTD")
+at <- c("@95", "@10", "")
+
+Data <- c("Ace", "Nudging", "PTSD", "Software", "Virus", "Wilson")
+
+typology <- data.frame(
+  col_keys = names(stabres)[2:19],
+  what = rep(Data, each = length(metrics)),
+  #measure = rep(metricsat, each = 6),
+  what = rep(c(rep("WSS@95"), rep("RRF@10"), rep("TTD")), 6),
+  #measure = c(rep(c("@95", "@10", ""), each = 6)),
+  stringsAsFactors = FALSE
+)
+num_keys <- names(stabres)[2:19]
+test <- flextable(stabres)
+# format numbers
+test <- colformat_num(x = test, j = num_keys, big.mark = ",", digits = 2, na_str = "missing")
+test <- colformat_char(x=test, j = "model")
+# set all columns 
+test <- set_header_df(test, mapping = typology, key = "col_keys")
+
+test
+test <- merge_h(test, part = "header")
+test
+#border_v = fp_border(color="purple")
+#test <- border_inner_v(test, part="all", border = border_v )
+test <- merge_v(test, part = "header")
+
+test
+
+test <- theme_booktabs(test)
+test <- autofit(test, add_w = 0.2)
+test <- fix_border_issues(test)
+
+test
+test <- align(test, align = "left", part = "all" )
+test
+```
+
+```{r}
+# make table for only ace
+
+# add ptsd logistic + tf-idf 
+ptsd_lctd <- fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/LCTD/ptsd/seed_lctd_ptsd_.json"))
+ptsd_lctd <- ptsd_lctd$.
+ptsd_lctd$wss
+```
+
+Now again for with seed 
+```{r}
+#files = list.files("/Volumes/Gerbrich/asreview/results/one/statistics/", recursive = TRUE)
+
+```

### 2020-05-11 simulation_study/simulation/README.Rmd

@@
 # sctd later
-names(seed_software) <- c("8129589", "8129732", "8129588", ".", ".", ".", ".")
+seed_software
+names(seed_software) <- c("8129589", "8129732", "8129588", "8131305", "8133472", "8134718", "8149271")
 
 # ptsd sctd
-
+seed_ptsd # 8149296
 ```

### 2020-05-11 manuscript/drafts/manuscript.Rmd
last fixes

@@
 ---
-title: Manuscript drafts
+title: Active learning for efficient systematic reviews - 
+subtitle: Evaluating models across research areas 
 author: "Gerbrich Ferdinands"
+header-includes:
+    - \usepackage{setspace}\doublespacing
+    - \usepackage[left]{lineno}
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
   bookdown::pdf_document2:
+    extra_dependencies: subfig, algorithm2e, float
     number_sections: no
@@
 link-citations: yes
-csl: systematic-reviews.csl
+csl: elsevier-vancouver.csl
 ---
 
+<!-- Active learning for detecting relevant publications - evaluating models across systematic reviews from different research areas.  -->
+
+<!-- Evaluating active learning models across research contexts.  -->
+
+<!--  generalizability  -->
 <!-- --- -->
@@
 <!--   bookdown::pdf_document2: -->
-
+<!--     extra_dependencies: subfig, algorithm2e -->
 <!--     number_sections: no -->
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
 options(tinytex.verbose = TRUE)
@@
 # table  on datasets statistics
-table_nums(name = "datasets", caption = "Statistics on datasets from original systematic reviews.")
-```
-
-Keywords: Human-Machine interaction, active learning, systematic reviews, text classification
-
-#### Introduction 
+table_nums(name = "datasets", caption = "Statistics on the test datasets obtained from six original systematic reviews.")
+table_nums(name = "atd", caption = "ATD values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
+table_nums(name = "wss", caption = "WSS@95 values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
+table_nums(name = "rrf", caption = "RRF@10 values ($\\bar x, (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
+
+```
+\newpage
+
+\linenumbers
+# Abstract
+#### Background 
 <!-- This study aims to contribute to this growing area of research by exploring  -->
@@
 #### Results
-#### Discussion
-
-\newpage
-
-# Introduction
-Systematic reviews are top of the bill in building evidence in research.
-A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
-Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007].
-<!-- PRISMA definition:  -->
-<!-- > "A systematic review attempts to collate all relevant evidences that fits pre-specified eligibility criteria to answer a specific research -->
-<!-- question. 
-add that this is a systematic/rigorous process?-->
-
-However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.
-An experienced reviewer takes on average 30 seconds to screen one title and abstract, whereas an inexperienced reviewer takes even longer [@Wallace2010].
-Conducting a systematic review typically requires over a year of work by a team of researchers [@Borah2017].
+#### Conclusions
+#### Keywords
+Machine learning, Active learning, Systematic Review, Study Selection, Text classification, Text representation,
+
 <!-- Besides time-consuming, the process of title and abstract screening is prone to human error [@Wang2020]. -->
@@
 <!-- Need to be screened by multiple researchers.  -->
+
+# Background
+Systematic reviews are top of the bill in research.
+A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
+Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007].
+However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.
+
+<!-- An experienced reviewer takes on average 30 seconds to screen one title and abstract, whereas an inexperienced reviewer takes even longer [@Wallace2010].
+A typical review of 5000 publications would require over 40 hours of uninterrupted screening, while typically only a fraction of the publications is relevant (mean = 2.94%, IQR=2.5 @Borah2017]).
+-->
+Conducting a systematic review typically requires over a year of work by a team of researchers [@Borah2017].
 Nevertheless, systematic reviewers are often bound to a limited budget and timeframe.
@@
 Especially when the need for guidelines is urgent - such as in the context of the current COVID-19 crisis - it is almost impossible to provide a review that is both timely and comprehensive.
+
 To ensure a timely review, reducing workload in systematic reviews is essential.
-
-With advances in Artificial Intelligence (AI), there has been wide interest in tools to reduce workload in systematic reviews [@Harrison2020].
+With advances in Machine Learning (ML), there has been wide interest in tools to reduce workload in systematic reviews [@Harrison2020].
 Various learning models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
@@
 The model presents the reviewer with the publications which are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
-Such an approach allows for substantial time-savings in the screening process.
-Reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
-~~Additionally, although outside the scope of the current study, active learning models have the potential to reduce the number of publications needed to screen when combined with some sort of stopping criterion [@Yu2019].~~
+Such an approach allows for substantial time-savings in the screening process as the reviewer can decide to stop screening after a sufficient number of relevant publications have been retrieved [@Yu2019].
+Moreover, reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
 <!-- Additionally, several studies report increasing efficiency beyond saving time [@OMara-Eves2015].  -->
@@
 <!-- Several studies have proposed active learning models for screening prioritization -->
-Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010].
-Active learning is when the model can iteratively improve its predictions by allowing the model to choose the data from which it can learn [@Settles2012].
-Active learning has proven to be an efficient strategy in large datasets where labels are scarce, which makes title and abstract screening an ideal candidate for such models.
-When applied in screening prioritization, the reviewer screens publications that are presented by an active learning model.
-Subsequently, the active learning model learns from the reviewers' decision ('relevant', 'irrelevant') and uses this knowledge in selecting the next publication to be screened by the reviewer.
+Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Gates2018a].
+With active learning, the machine learning model can iteratively improve its predictions on unlabelled data by allowing the model to select the records from which it wants to learn [@Settles2012].
+The model queries these records to a human annotator who provides them with a label, from which the model then updates its predictions.
+The general assumption is that by letting the model select which records are labelled, the model can achieve higher accuracy while requiring the human annotator to label as few records as possible [@Settles2009].
+Active learning has proven to be an efficient strategy in large unlabelled datasets where labels are expensive to obtain [@Settles2009], which makes the screening phase in systematic reviewing an ideal candidate for such models because labelling the typical large number of publications is very costly.
+When active learning is applied in the screening phase, the reviewer screens publications that are selected by an active learning model.
+Subsequently, the active learning model learns from the reviewers' decision ('relevant', 'irrelevant') and uses this knowledge to update its predictions and to select the next publication to be screened by the reviewer.
 
@@
 
-Although the application of learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], the complex nature of the field is making it difficult to draw overarching conclusions about best practice [@OMara-Eves2015].
-First, whilst previous studies have evaluated models in many forms and shapes [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010], all models adopt the same classification technique.
-Even though a plethora of classification techniques exists [@Aggarwal2012], no study in this area has made a comparison between models adopting different classification techniques.
+<!-- , the complex nature of the field is making it difficult to draw overarching conclusions about best practice [@OMara-Eves2015]. -->
+
+The application of active learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
+Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique, namely Support Vector Machine.
+Findings from outside the field of active learning show that different classification techniques can serve different needs in the retrieval of relevant publications, for example recall versus precision [@Kilicoglu2009; @Aphinyanaphongs2004].
+Therefore, it is essential to evaluate different classification techniques in the context of active learning models.
+<!-- no study in this area has made a comparison between models adopting different classification techniques. -->
+<!-- Since a plethora of techniques exist [@Aggarwal2012], it would be of interest to incorporate such models to this area as well.  -->
+Moreover, another component known to influence performance of the models is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Le2014; @Zhang2011].
+Previous studies all adopt the widely used 'bag of words' strategy [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010].
+It is of interest to evaluate models using this effective but rather simplistic approach by comparing them to models adopting a more sophisticated strategy, called 'Doc2vec' [@Le2014].
+Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] and software engineering [@Yu2018, @Yu2019].
+Model replications on reviews from varying research contexts are essential to draw conclusions about the general effectiveness of active learning models [@OMara-Eves2015; @Marshall2020].
+As far as known to the authors, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between two systematic reviews from different research areas, namely the social and the medical sciences.
+They found that active learning was more difficult on data from the social sciences due to the nature of the different vocabularies used.
+Therefore, it is of interest to evaluate model performance across different research contexts.
+Taken together, evaluations of active learning models in the context of systematic reviewing are required (1) across different classification techniques, (2) feature extraction strategies, and (3) review contexts.
+The current study aims to address these issues by answering the following research questions:
+
+|    __RQ1__ What is the performance of several active learning models across different classification techniques?
+|    __RQ2__ What is the performance of several active learning models across different feature extraction strategies? 
+|    __RQ3__ Does the performance of active learning models differ across systematic reviews from different research areas?
+<!-- is effective but rather simplistic as it is solely based on the relative frequency of words in the texts, the ordering of words in the texts cannot be taken into account.  -->
+<!-- . yet rather simplistic as they cannot take into account the structure of the texts -->
+<!-- the effect of adopting a different, more sophisticated strategies has not been investigated t -->
+<!-- previous another model component worth exploring is the feature extraction strategy,  T It is worth evaluating strategies  -->
+<!-- It  rather simplistic. Paragraph vector. As various feature extraction strategies exist, it is worth evaluating the different strategies as well. as mentioned by [@Yu2018] -->
+<!-- many facets of models  -->
+<!-- Previous studies adopt ...  -->
+<!-- little attention has been paid to [@Yu2018] mention paragraph vector -->
+<!-- How to represent  -->
+<!-- the representation of the title an abstracts   -->
 <!-- whilst there exists a  of classification techniques for an active learning model to adopt, research to date has confined to models adopting one classification strategy [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010].
@@
  <!-- evaluated techniques other than Support Vector Machines (SVM) -->
-Second, the lack of model replication on reviews from varying research contexts makes it impossible to draw conclusions about the general effectiveness of active learning models [@OMara-Eves2015; @Marshall2020].
-As far as known to the authors, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between systematic reviews from different research areas, namely the social and the medical sciences.
-They found that active learning was more difficult on data from the social sciences due to the nature of the different vocabularies used.
-Therefore, it is of interest to evaluate model performance across different research contexts.
-
-<!-- Taken together, the question remains how active learning models for screening prioritization perform across different classification techniques (1) and review contexts (2).
-Hence, additional evaluations of active learning models are required.
-The current study aims to address these issues by answering the following research questions:  -->
-Taken together, evaluations of active learning models are required across different classification techniques (1) and review contexts (2).
-The current study aims to address these issues by answering the following research questions:
-
-  __RQ1__ What is the performance of active learning models across different classification techniques?
-
-  __RQ2__ Does performance of active learning models differ across systematic reviews from different research areas?
-
 <!-- Although important issues in the application of active learning models on title and abstract screening have been addressed prior studies -->
@@
 The purpose of the current paper is to increase the evidence base on active learning models for reducing workload in title and abstract screening in systematic reviews.
-Combining latest insights from this area, we propose seven different active learning models for the purpose of identifying relevant publications in systematic review datasets.
-The models were chosen to maximize the number of identified relevant publications, while minimizing the number of publications needed to screen.
-Working towards a general consensus in this emerging field, model performance was assessed by conducting a retrospective simulation on six systematic review datasets.
-Datasets were collected from the fields of medicine, software engineering, psychology, behavioural public administration, and virology to assess generalizability of the models across research contexts.
+We adopt four different classification techniques (Naive Bayes, Linear Regression, Support Vector Machine, and Random Forest) and two different feature extraction strategies (TF-IDF and Doc2vec) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
+Model performance was assessed by conducting a retrospective simulation on six systematic review datasets.
+Datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], software engineering [@Yu2018], psychology [@vandeSchoot2017], behavioural public administration [@Nagtegaal2019] and virology [@Kwok2020] to assess generalizability of the models across research contexts.
 The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@ASReview2020].
 $\texttt{ASReview}$ is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
-All scripts and data used are openly published to facilitate usability and acceptability of AI-assisted title and abstract screening in the field of systematic review.
-
-\textcolor{red}{The remaining part of this paper is organized as follows.
-The Methods section elaborates on the setup of the current study, starting with a task description, followed the Technical Details section which will cover the workings of active learning models for study selection in systematic reviews on a conceptual level.
-The results section reports ... The discusssion section summarises the findings, comments on them and  summarises the main findings, discusses 
-discuss limitations, draw conclusion and}
+All scripts and data used are openly published to facilitate usability and acceptability of ML-assisted title and abstract screening in the field of systematic review.
+
+<!-- . -->
+
+The remaining part of this paper is organized as follows.
+The Technical details section elaborates on the characteristics of active learning models for identifying relevant publications in the context of systematic reviews.
+The Simulation study section describes the study that was designed to answer the research questions.
+The findings of the simulation study are reported in the Results section.
+The implications of the findings in context of previous research are discussed in the Discussion section, followed by this study's main conclusions in the Conclusion section.
 
@@
 
-# Methods 
-## Task Description
+# Technical details 
+What follows is a more detailed account of the active learning models.
+The structure and functions of the key components of the models are introduced to clarify the choices made in the design of the current study.
+
+## Task description
 The screening process of a systematic review starts with all publications obtained in the search.
@@
 
-- Start with the set of all unlabeled (titles and) abstracts, $\mathcal{U}$.
-- The reviewer provides a label for a few records $x \in \mathcal{U}$, creating an set of labeled titles and abstracts $\mathcal{L}$. The label can be either relevant $x_R$ or irrelevant $x_I$.
-- The active learning cycle starts:
-
-  1. A classifier is trained on the labeled titles and abstracts, $C = \texttt{train}(\mathcal{L})$
-
-  2. The classifier predicts labels for all unlabelled titles and abstracts, $C(\mathcal{U})$
-
-  3. Based on the predictions by $C$, the model selects the most relevant title and abstract $x^* \in \mathcal{U}$
-
-  4. The model asks the reviewer to screen this title and abstract, $x^*_?$
-
-  5. The reviewer screens the title and abstract and provides a label, $x^*_R$ or $x^*_I$
-
-  6. The labeled title and abstract is added to the training data, $x_{R \texttt{ xor } I} \in \mathcal{L}$
-
-  7. Back to step 1.
-
-- In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled title and abstracts.
-The relevant titles and abstracts are identified as early in the process as possible.
-The reviewer and the model keep interacting until the reviewer decides to stop or until all title and abstracts have been labelled.
-
-<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
-The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
--->
-
-<!-- - then active learning cycle starts in which the user makes a decision after each iteration of the model which is then used to re-train the model. -->
-
-<!-- - instance $x$, label $y$ -->
-<!-- - utility measure $\phi_A(\cdot)$ -->
-<!-- - $x^*_A$ best query instance according to $\phi_A(\cdot)$ -->
-
-<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$. -->
-<!-- This is the starting point for the active learning model. -->
-<!-- The model trains a classifier who predicts ...  -->
-<!-- The reviewer and the are interacting in the active learning cycle. -->
-<!-- Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset. -->
-
-<!-- # Algorithm 1 -->
 <!-- Just a sample algorithmn -->
@@
 
+- Start with the set of all unlabeled records (titles and abstracts), $\mathcal{U}$.
+- The reviewer provides a label for a few, for example 5-10, records $x \in \mathcal{U}$, creating an set of labeled records $\mathcal{L}$.
+The label can be either Relevant $\langle x, \texttt{R}\rangle$ or Irrelevant $\langle x, \texttt{I}\rangle$.
+- The active learning cycle starts:
+
+  1. A classifier, $C$, is trained on the labeled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
+
+  2. The classifier predicts relevancy scores for all unlabelled records $\mathcal{U}$, $C(\mathcal{U})$
+
+  3. Based on the predictions by $C$, the model selects the most relevant record $x^* \in \mathcal{U}$
+
+  4. The model queries the reviewer to screen this record, $\langle x^*, \texttt{?}\rangle$
+
+  5. The reviewer screens the record and provides a label, $\langle x^*, \texttt{R}\rangle$ or $\langle x^*, \texttt{I}\rangle$
+
+  6. The newly labeled record is added to the training data, such that $x \in \mathcal{L}$ and $x \notin \mathcal{U}$
+
+  7. Back to step 1.
+
+In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled title and abstracts.
+The relevant titles and abstracts are identified as early in the process as possible.
+The reviewer and the model keep interacting until the reviewer decides to stop or until all records been labelled.
+
+<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
+The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
+-->
+
+<!-- - then active learning cycle starts in which the user makes a decision after each iteration of the model which is then used to re-train the model. -->
+
+<!-- - instance $x$, label $y$ -->
+<!-- - utility measure $\phi_A(\cdot)$ -->
+<!-- - $x^*_A$ best query instance according to $\phi_A(\cdot)$ -->
+
+<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$. -->
+<!-- This is the starting point for the active learning model. -->
+<!-- The model trains a classifier who predicts ...  -->
+<!-- The reviewer and the are interacting in the active learning cycle. -->
+<!-- Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset. -->
 <!-- meaning the reviewer the reviewer screens as little as possible while inclusion rate = high (not true but is nice statistic?) -->
@@
 -->
-
 <!-- #### Assumptions  -->
@@
 <!-- Selecting papers is a two-step process: abstract & fulltext screening -->
-
-<!-- x -->
-
-<!-- Now there are a few technical details.
-Many different versions of such algorithms exist.
-Many of such algorithms have been described in the active learning literature and have been applied in the systematic reviewing process.
-Not exhaustive, but the algorithm can apply many different strategies to arrive at its predictions, which can be divided in following parameters: classifier, feature extraction strategy, balancing, query strateg y.
--->
-
-<!-- The current section describes how common issues in identifying relevant publication can be dealt with.  -->
-<!-- key components  -->
-
-## Technical details
-A more detailed account of the active learning models is given in the following section.
-The structure and functions of the key components of the models will be introduced to clarify the choices made in the design of the current study.
-
-### Classification
+## Class imbalance problem
+There are two classes in the dataset: relevant and irrelevant publications.
+Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94% [@Borah2017]).
+The class imbalance causes the classifier to miss relevant publications, because there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
+Moreover, classifiers can achieve high accuracy but still fail to identify any of the relevant publications [@Wallace2010].
+This is evident in the case of a systematic review dataset where only three percent of publications are relevant.
+A model would achieve 97% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.
+
+Previous studies have addressed the class imbalance problem by rebalancing the training data in different ways [@OMara-Eves2015].
+To decrease the class imbalance in the training data, the models in the current study rebalances the training set by Dynamic Resampling (DR).
+DR undersamples the number of irrelevant publications in the training data, whereas the number of relevant publications are oversampled such that the size of the training data remains the same.
+The ratio between relevant and irrelevant publications in the rebalanced training data is not fixed, but dynamically updated depending on the number of publications in the available training data, the number of publications in the total data, and the ratio between relevant and irrelevant publications in the available training data.
+
+## Classification
 To make predictions on the unlabeled publications, a classifier is trained on features from the set of previously labeled publications. 
@@
 
-Whilst the performance of several classification techniques has been investigated in the AI-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
+Whilst the performance of several classification techniques has been investigated in the ML-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
 <!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
@@
 
-### Class imbalance problem
-There are two classes in the dataset: relevant and irrelevant publications.
-Typically, the inclusion rate is low (<10%) as only a fraction of the publications belong to the relevant class.
-This poses a problem for training a classifier as there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
-Moreover, classifiers are well-suited to separate data into classes, but not to correctly identify one class [@Wallace2010].
-Therefore, the class imbalance problem causes the classifier to miss relevant publications.
-This is evident in the case of a systematic review dataset where only one percent of publications are relevant.
-A model would achieve 99% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.
-
-Previous studies have addressed the class imbalance problem by rebalancing the training data in different ways [@OMara-Eves2015].
-To decrease the class imbalance in the training data, the models in the current study rebalance the training set by Dynamic Supersampling (DS).
-DS decreases the number of irrelevant publications in the training data, whereas the number of relevant publications are increased (by copy) such that the size of the training data remains the same.
-The ratio between relevant and irrelevant publications in the training data is not fixed, but dynamically updated and depends on the size of the training data, the total number of publications, and the ratio between the total number of labeled publications.
-
-### Word embeddings 
+## Feature extraction
 To predict publication class, the classifier uses information from the publications in the dataset.
@@
 The textual information needs to be mapped to feature vectors.
-This process of numerically representing textual content is called 'word embeddings'.
-
-A classical example of word embeddings is a 'bag of words' (bow) representation.
-For each text in the data set, the number of occurrences of each word is stored.
+This process of numerically representing textual content is referred to as 'feature extraction'.
+
+A classical example of feature extraction is a 'bag of words' (bow) representation.
+For each text in the data set, the term frequency - the number of occurrences of each word - is stored.
 This leads to $n$ features, where $n$ is the number of distinct words in the texts [@scikit-learn].
-The bag-of-words method is simplistic and will highly value often occurring but otherwise meaningless words such as "and".
-A more sophisticated approach is Term-Frequency Inverse Document Frequency (TF-IDF).
-TF-IDF circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire data set [@Ramos2003].
+A serious weakness of this method is that it highly values often occurring but otherwise meaningless words such as "the".
+A more sophisticated bow approach is Term-Frequency Inverse Document Frequency (TF-IDF), which circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire data set [@Ramos2003].
 A downside of TF-IDF and other bow methods is that they do not take into account the ordering of words, thereby ignoring semantics.
-An example of an approach that aims to overcome this weakness is Doc2Vec (D2V), capable of grasping the relations between words by learning to predict the words in the texts [@Le2014].
-
-Miwa et al.
+An example of an approach that aims to overcome this weakness is Doc2vec (D2V).
+Doc2vec represents texts by a neural network, capable of grasping semantics by learning to predict the words in the texts [@Le2014].
+
+<!-- Miwa et al.
 found that active learning was more difficult on data from the social sciences compared to data from the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014].
 As the study by Miwa et al.
-adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated word embedding strategy has the potential to bridge the performance gap between these research areas.
-
-### Query strategy
+adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated feature extraction strategy has the potential to bridge the performance gap between these research areas.
+-->
+
+## Query strategy
 The active learning model can adopt different strategies in selecting the next publication to be screened by the reviewer.
@@
 In the active learning literature this is referred to as certainty-based active learning [@Settles2012].
-Another well-known strategy is uncertainty-based active learning, where the instances that will be presented next will be those instances on which the model's classifications are the least certain, i.e.
+Another well-known strategy is uncertainty-based active learning, where the instances that are presented next are those instances on which the model's classifications are the least certain, i.e.
 close to 0.5 probability [@Settles2012].
@@
 
-## Models 
-The seven models consist of the components described in the Technical Details section, adopting four different classification techniques and two different word embeddings approaches:
-
-First, four models combining every classifier with TF-IDF word embeddings were investigated:
-
- - SVM + TF-IDF
- - NB + TF-IDF
- - RF + TF-IDF 
- - SVM + TF-IDF
-
-Second, the classifiers were combined with Doc2Vec word embeddings, leading to the following three models:^[The combination NB + D2V could not be tested because the Multinomial Naive Bayes classifier (sklearn) can only handle a feature matrix with positive values, whereas the doc2vec word embeddings approach (gensim) produces a feature matrix that can also contain negative values.]
-
- - SVM + Doc2Vec
- - RF + Doc2Vec
- - SVM + Doc2Vec
-
-## Simulation study
-For each of the seven models, performance was evaluated by simulating the model on the screening process of six systematic reviews. 
-Performance of the seven models was evaluated by simulating their behaviour in the screening process of six systematic review datasets.
-Put differently, 42 simulations were carried out.
-For every model-dataset combination, hyperparameters were optimized^[see the Appendix for more information].
+# Simulation study
+The section below describes the simulation study that was carried out to answer the research questions.
+
+## Set-up
+<!-- The seven models consist of the components described in the Technical Details section, adopting four different classification techniques and two different feature extraction strategies:  -->
+
+To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:
+
+ 1. SVM + TF-IDF
+ 2. NB + TF-IDF
+ 3. RF + TF-IDF 
+ 4. LR + TF-IDF
+
+To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:^[The combination NB + D2V could not be tested because the [Multinomial Naive Bayes classifier](https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB) can only handle a feature matrix with positive values, whereas the [Doc2vec feature extraction approach](https://radimrehurek.com/gensim/models/doc2vec.html) produces a feature matrix that can also contain negative values.]
+
+ 5. SVM + Doc2vec
+ 6. RF + Doc2vec
+ 7. LR + Doc2vec
+
+Performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing __RQ3__.
+Hence, 42 simulations were carried out, representing all model-dataset combinations.
+For every simulation, hyperparameters were optimized through a random search to arrive at maximum model performance.
 To account for variance, every simulation was repeated for 15 trials.
-Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020]. There was no need for a human reviewer as the model could query the labels in the data instead.
+Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020].
+There was no need for a human reviewer as the model could query the labels in the data instead.
 
 Every simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
-To account for bias, the initial training set was randomly sampled from the dataset for every of the 15 runs.
-Although varying over runs, the initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
-A seed value was set to ensure reproducibility
+To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for every of the 15 trials.
+Although varying over trials, the initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
+A seed value was set to ensure reproducibility.
 The classifier was retrained every time after a publication had been labeled.
@@
 
+Simulations were run in ASReview, version 0.9.3 [@ASReview2020].
+Analyses were carried out using R, version 3.6.1 [@RCoreTeam2019].
+All scripts and data are stored in the supplementary material.
+This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
+Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
+Access was granted by SURF via a grant (ID EINF-156).
+. 
 <!-- can retrieve the labels from the annotated dataset instead -->
@@
 
+<!-- Data are available via the $\texttt{ASReview}$ GitHub page^[https://github.com/asreview/systematic-review-datasets]. -->
+<!-- All datasets accompanying the systematic reviews are openly published.  -->
 ## Datasets 
@@
 Secondly, datasets were selected by their availability, given the limited timespan of the current project.
-The datasets were retrieved from a collection of open systematic review datasets to be used for text mining purposes^[https://github.com/asreview/systematic-review-datasets].
-
-Three out of six datasets originated from the _medical sciences_: Ace, Wilson, and Virus.
+Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).
+
+Datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
 The Wilson dataset [@Appenzeller-Herzog2020] is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
@@
 From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012].
-The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_,
+The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_.
 The PTSD dataset contains publications from the field of _psychology_.
 The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017].
-Of these six datasets, Ace, and Software have been used for model simulations in previous studies on AI-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].
+Of these six datasets, Ace, and Software have been used for model simulations in previous studies on ML-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].
 
@@
 Candidate studies with missing abstracts and duplicate instances were removed from the data.
+Preprocessing scripts and resulting datasets can be found in the supplementary material.
 Test datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
 All test datasets consisted of thousands of candidate studies, of which only only a fraction was deemed relevant to the systematic review.
-For four of the six datasets inclusion rates were centered around 1-2 percent.
-For the remaining two datasets, the inclusion rate was about 5 percent (`r table_nums("datasets", display = "cite")`).
+For the Virus and the Nudging dataset, the inclusion rate was about 5 percent.
+For the remaining six datasets, inclusion rates were centered around 1-2 percent.
+(`r table_nums("datasets", display = "cite")`).
 <!-- The data preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis] -->
@@
 
+\begin{center}
 `r table_nums("datasets")` 
-```{r}
-datastats %>%
-  kable(format = "pandoc",
-        booktabs = TRUE,
-        col.names = c("Dataset", rep(c("Candidate studies", 
+\end{center}
+```{r, results = 'asis'}
+datastats <- datastats %>%
+  select(Dataset, candidates_test, incl_test, inclrate_test) 
+colnames(datastats) <- c("Dataset", rep(c("Candidate publications", 
                                        #"Studies selected for fulltext screening", 
-                                       "Relevant studies", 
-                                       "Inclusion rate (%)"),2))) %>%
-  kable_styling(full_width = TRUE) %>%
-  add_header_above(c("", "Original study" = 3, "Test collection" = 3))
+                                       "Relevant publications", 
+                                       "Inclusion rate (%)"),1))
+
+print(xtable(datastats, digits = c(0,0,0,0,1)),
+      include.rownames=FALSE, comment = FALSE, booktabs = TRUE,
+      format.args = list(big.mark = ",", decimal.mark = "."))
 ```
@@
 ## Evaluating performance
-Model performance assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD).
-Furthermore, model performance was visualized by plotting recall curves.
-Results were averaged over 15 trials for every simulation.
+Model performance was assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD).
 
@@
 Typically measured at a recall level of 0.95 [@Cohen2006], WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
-In the current study, WSS is computed at 0.95 and 1.00 recall level.
-RRF statistics are computed at 10%, representing the proportion of relevant studies that are after screening 10% of all publications.
+In the current study, WSS is computed at 0.95 recall.
+RRF statistics are computed at 10%, representing the proportion of relevant publications that are found after screening 10% of all publications.
 
@@
 Moreover, WSS makes assumptions about acceptable recall levels whereas this level might depend on the research question at hand [@OMara-Eves2015].
-
-A statistic that is not dependent on some arbitrary cutoff value is the TTD, which is the average number of publications that needed to be screened to find a relevant publication, divided by the total number of publications in the data.
-The TTD is proportional to the area above the recall curve.
-
-Plotting recall as a function of the number of screened publications offers insight in model performance throughout the screening process [@Cormack2014; @Yu2018].
+A statistic that is not dependent on some arbitrary cutoff value is the ATD, which is the average number of publications needed to screen to find a relevant publication.
+
+Furthermore, model performance was visualized by plotting recall curves.
+Plotting recall as a function of the proportion of screened publications offers insight in model performance throughout the entire screening process [@Cormack2014; @Yu2018].
 The curves give information in two directions.
-On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
+On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (1-WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
+Moreover, the recall curves relate to the ATD in such a way that the area above the curve is equal to the ATD.
+
+For every simulation, the RRF@10, WSS@95, and ATD are reported as means over 15 trials.
+To indicate the spread of performance within simulations, the means are accompanied by an estimated^[The metrics for all individual 15 trials deviate slightly from the overal mean over 15 trials because of pre-averaging in the \texttt{ASReview} source code.
+As the analyses across all trials did not produce information on the 15 separate runs, the standard deviation of the mean, $\hat s$, was estimated by computing the standard deviation within the individual 15 trials.] standard devation $\hat s$.
+To compare overall performance across datasets, median performance is reported for every dataset, accompanied by the Median Absolute Deviation (MAD), indicating variability between models within a certain dataset.
+Recall curves are plot for every simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.
 
@@
 
-Simulations were run in ASReview, version 0.9.3 [@ASReview2020].
-Analyses were carried out using R, version 3.6.1  [@RCoreTeam2019].
-All datasets accompanying the systematic reviews are openly published.
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
-Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
 <!-- $$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$  -->
@@
 <!-- Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas. -->
-
----
-
 <!-- ### Optimizing hyperparameters -->
@@
 <!-- A description of all hyperparameters and their sample space can be found in the appendix.  -->
-
 <!-- Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g.
@@
 
-<!-- <!-- RQ2 different hyperparameter optimizations? --> -->
-<!-- <!-- Classifiers come with hyperparameters.
-We have to make a choice on how to set these hyperparameters.
-What we do is create 3 sets, optimizing in three ways, aggregate results obtained.
---> -->
+<!-- <!-- RQ2 different hyperparameter optimizations? --> 
+<!-- <!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
 
@@
 
-<!-- ```{r} -->
-<!-- tab %>% -->
-<!-- kable(format = "latex",  -->
-<!--       booktabs = TRUE,  -->
-<!--       col.names = "Configurations") %>% -->
-<!--   kable_styling(full_width = TRUE) -->
-<!-- ``` -->
-
-<!-- Use these inputs to predict relevance of papers.  -->
-
-<!-- ### Stage 1: hyperparameter optimization -->
-
-<!-- Or, more specific:  -->
-
-<!-- ```{r} -->
-<!-- tabbie <- -->
-<!--   combins %>% -->
-<!--   filter(query_strategy == "max", -->
-<!--          feature_extraction %in% c("doc2vec", "tfidf") & model %in% c("dense_nn","svm", "nb", "rf", "lr")) %>% -->
-<!--   select(-query_strategy) -->
-
-<!-- tabbie <- tabbie[c(1,3,5,6,9),] -->
-<!-- row.names(tabbie) <- NULL -->
-
-<!-- tabbie %>% -->
-<!--   kable(col.names = names(words)[c(1,3)],  -->
-<!--         format = "latex", -->
-<!--         booktabs = TRUE) -->
-<!-- ``` -->
-
 # Results 
-For each of the seven models, performance was evaluated by simulating the model on the screening process of six systematic reviews.
-
-Results were averaged over 15 trials for every simulation.
-Performance of the seven models was evaluated by simulating their behaviour in the screening process of six systematic review datasets.
-All results were
-
-To allow for a direct comparison between models, their performance is evaluated within datasets. 
-Every model*data combination (42) was repeated for 15 times. 15 runs started with the same initial publications..
-
-  __RQ1__ What is the performance of active learning models across different classification techniques?
-
-```{r}
+This section proceeds as follows.
+Firstly, the results of the Nudging dataset are discussed in detail to provide a basis for answering the research questions.
+Secondly, the results are presented for each research question over all datasets.
+
+```{r, eval = TRUE}
+# measures for averages over 15 runs 
 results <- readRDS("../../results/output/results.RDS")
 stabres <- readRDS("../../results/output/tabresults.RDS")
-
-# add missing ptsd logistic regression values
-stabres[stabres$model == "LR + TF-IDF", "wss.95_ptsd"] <- 91.69509
-stabres[stabres$model == "LR + TF-IDF", "rrf.10_ptsd"] <- 99.81982
-stabres[stabres$model == "LR + TF-IDF", "loss_ptsd"] <- 0.01709612
-```
-
-## Evaluation on the Ace dataset
-
-Recall curves present recall after averaged over 15 trials with a confidence region ...
+```
+
+```{r}
+# measures for variation within 15 runs 
+#sumruns <- readRDS("../../results/output/sumruns.RDS")
+# tabruns <- sumruns %>%
+#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95", "mean_wss99", "sd_wss99","mean_wss100","sd_wss100", "mean_rrf5","sd_rrf5", "mean_rrf10", "sd_rrf10", "mean_rrf20","sd_rrf20", "mean_loss", "sd_loss"))
+
+# tabruns <- sumruns %>%
+#   select(dataset, model, mean_wss95, sd_wss95, mean_rrf10, sd_rrf10, mean_loss, sd_loss) 
+#
+
+# wss95tab <- tabruns %>%
+#   select(dataset, model, mean_wss95, sd_wss95) %>%
+#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95"))
+
+# wss95tab <- stabres %>%
+#   select(model, starts_with("wss.95"))
+
+# table for in manuscript
+
+sdruns <- readRDS("../../results/output/sdruns.RDS")
+
+nicetab <- function(results, statistic){
+  test <- results %>% select(model, dataset, all_of(statistic))
+  sdname <- paste0("sd", statistic)
+
+  test <- left_join(test, sdruns[,c("model", "dataset", sdname)], by = c("model", "dataset"))
+
+  test[,statistic] <- sprintf("%.1f", round(test[,statistic],1)) 
+  test[,sdname] <-  sprintf("%.2f", round(test[,sdname],2)) 
+  test$tab <- with(test, paste0(test[,statistic], " (", test[,sdname], ")"))
+
+  tab <- test %>%
+      select(model, dataset, tab) %>%
+      pivot_wider(names_from = dataset, values_from = c("tab"))
+
+  tab <- tab %>%
+    select(model, nudging, ptsd, software, ace, virus, wilson)
+  names(tab) <- c("", "Nudging", "PTSD", "Software", "Ace", "Virus", "Wilson")
+  return(tab)
+}
+
+# rrf10tab <- tabruns %>%
+#   select(dataset, model, mean_rrf10, sd_rrf10) %>%
+#   pivot_wider(names_from = dataset, values_from = c("mean_rrf10","sd_rrf10"))
+# 
+# atdtab <- tabruns %>% 
+#   select(dataset, model, mean_loss, sd_loss) %>%
+#   pivot_wider(names_from = dataset, values_from = c("mean_loss","sd_loss"))
+# tabruns %>%
+#   select(model, starts_with(mean_wss95), starts_with(sd_wss95),
+#          starts_with(mean_rrf10), starts_with(sd_rrf10), 
+#          starts_with(mean_loss), starts_with(sd_loss))
+```
+
+## Evaluation on the Nudging dataset
+Figure 1a shows the recall curves for all simulations on the Nudging dataset.
+As desribed in the previous section, these curves plot recall as a function of the proportion of publications screened.
+The curves represent the average recall over 15 trials $\pm$ the standard error of the mean in the direction of the y-axis.
+The x-axis is cut off at 40% since all for simulations, the models reached 95% recall after screening 40% of the publications.
+The dashed horizontal lines indicate the RRF@10 values, the dashed vertical lines the WSS@95 values.
+The recall curves relate to the ATD such that ATD is equal to the area above the curve.
+The dashed grey diagonal line corresponds to the expected recall curve when publications are screened in a random order.
+Desirable model performance was defined as maximizing recall while minimizing the number of publications needed to screen.
+
+The recall curves were used to examine model performance throughout the entire screening process and to make a visual comparison between models within datasets.
+For example in Figure 1a, after screening about 30% of the publications all models had already found 95% of the relevant publications.
+Moreover, after screening 5% the green curve - representing the RF + TF-IDF model - splits away from the others and remains to be the lowest of all curves until about 30% of publications have been screened.
+Hence, from screening 5 to 30 percent of publications, the RF + TF- IDF model was the slowest in finding the relevant publications.
+The ordering of the remaining recall curves changes throughout the screening process, but maintain to show relatively similar performance at face value.
+
+<!-- although the RF + TF-IDF model performs seems to be the lowest performing model for the longest part of the screening process.   -->
+<!-- , buy the SVM + D2V model (pink) reaches this point of 95% recall earlier than the LR + TF-IDF model (yellow).  -->
+
+Figure 1b shows a subset of the recall curves in Figure 1a, namely the curves for the first four models only to allow for a visual comparison across classification techniques adopting the TF-IDF feature extraction strategy.
+Figure 1c shows recall curves for the remaining three models to compare the models using Doc2vec feature extraction.
+Figures 1d-f plot recall curves for models adopting the TF-IDF feature extraction strategy to recall curves for their Doc2vec-using counterparts to allow for a comparison between models adopting TF-IDF and models adopting Doc2vec feature extraction.
+
+```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves for the Nudging dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+# nudgingplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging", full.names=TRUE)
+f <- c("inclusion_all_nudging", "inclusion_tfidf_nudging", "inclusion_d2v_nudging", "inclusion_d2v_vs_tfidf_logistic_nudging", "inclusion_d2v_vs_tfidf_rf_nudging", "inclusion_d2v_vs_tfidf_svm_nudging")
+nudgingplots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging/", f, ".pdf")
+include_graphics(nudgingplots)
+```
+<!-- is apparent that models adopting the TF-IDF feature extraction strategy are outperformed by their Doc2Vec-using counterparts:  -->
+<!-- The best performing model in terms of ATD is NB + TF-IDF (9.25, 0.29), LR + TF-IDF (9.46, 0.19), SVM + TF-IDF (62.20),and RF + TF-IDF (11.6, 0.43).
+SVM + D2V (8.71, 0.33), LR + D2V (8.73, 0.47), RF + D2V (10.17, 0.88).
+-->
+
+<!-- provides the RRF@10 values for all model-dataset combinations.  -->
+It can be seen from the data in the first column of `r table_nums("atd", display = "cite")` that in terms of ATD, the best performing models on the Nudging dataset were SVM + D2V and LR + D2V, both with an ATD of 8.9%.
+This indicates that the average proportion of publications needed to screen to find a relevant publication was 8.9% for both models.
+In the SVM + D2V model, the standard deviation was 0.33 , whereas for the LR + D2V model $\hat s =$ 0.47.
+This indicates that for the SVM + D2V model, the ATD values of individual trials were closer to the overal mean compared to the LR + D2V model, meaning that the SVM + D2V model performed more stable across different initial training datasets.
+Median ATD for this dataset was 9.6% with an MAD of 1.06, indicating that for half of the models, the ATD was within 1.06 distance from the median ATD.
+
+\begin{center}
+`r table_nums("atd")`
+\end{center}
+```{r, results="asis"}
+tabatd <- nicetab(results, "loss") 
+tabatd <- tabatd[c(7, 1, 5, 3, 6, 4, 2),]
+# add range rows 
+mad <- results %>% group_by(dataset) %>% summarise(median = sprintf("%.1f", round(median(loss), 1)), mad = sprintf("%.2f", round(mad(loss), 2)))
+
+mad <- with(mad, paste0(median, " (", mad, ")"))
+
+tabatd <- rbind(tabatd, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
+
+print(xtable(tabatd, align = c("r", "r", rep("c", 6))), 
+      include.rownames=FALSE, comment = FALSE, booktabs = TRUE, hline.after = c(0,7))
+
+```
+
+As `r table_nums("wss", display = "cite")` shows, the highest WSS@95 value on the Nudging dataset was achieved by the NB + TF-IDF model with a mean of 71.7, meaning that this model reduced the number of publications needed to screen with 71.7% at the cost of losing 5% of relevant publications.
+The estimated standard deviation of 1.37 indicates that in terms of WSS@95, this model performed the most stable across trials.
+The model with the lowest WSS@95 value was RF + TF-IDF ($\bar x$ = 64.9, $\hat s =$ 2.50).
+Median WSS@95 of these models was 66.9%, with a MAD of 3.05%, indicating that WSS@95 values of models varied the most within this dataset.
+
+\begin{center}
+`r table_nums("wss")` 
+\end{center}
+```{r, eval = TRUE, results="asis"}
+tabwss95 <- nicetab(results, "wss.95") 
+tabwss95 <- tabwss95[c(7, 1, 5, 3, 6, 4, 2),]
+# add range rows 
+mad <- results %>% group_by(dataset) %>% summarise(median = sprintf("%.1f", round(median(wss.95), 1)), 
+                                                   mad = sprintf("%.2f", round(mad(wss.95), 2)))
+# insert mad 
+mad <- with(mad, paste0(median, " (", mad, ")"))
+
+tabwss95 <- rbind(tabwss95, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
+# insert N per dataset
+
+print(xtable(tabwss95, align = c("r", "r", rep("c", 6))), 
+      include.rownames=FALSE, comment = FALSE, booktabs = TRUE, hline.after = c(0,7))
+
+  # kable(format = "latex") %>%
+  # kableExtra()
+```
+
+As can be seen from the data in `r table_nums("rrf", display = "cite")`, LR + D2V was the best performing model in terms of RRF@10, with a mean of 67.5 indicating that after screening 10% of publications, on average 67.5% of all relevant publications had been identified, with a standard deviation of 2.59.
+The worst performing model was RF + TF-IDF ($\bar x =$ 53.6, $\hat s =$ 2.71).
+Median performance was 62.6, with an MAD of 3.89 indicating again that RRF@10 values were most dispersed for models within this dataset.
+
+\begin{center}
+`r table_nums("rrf")` 
+\end{center}
+```{r, results="asis"}
+tabrrf10 <- nicetab(results, "rrf.10")
+
+tabrrf10 <- tabrrf10[c(7, 1, 5, 3, 6, 4, 2),]
+# add range rows 
+mad <- results %>% group_by(dataset) %>% summarise(median = sprintf("%.1f", round(median(rrf.10), 1)), mad = sprintf("%.2f", round(mad(rrf.10), 2)))
+
+mad <- with(mad, paste0(median, " (", mad, ")"))
+
+tabrrf10 <- rbind(tabrrf10, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
+
+print(xtable(tabrrf10, align = c("r", "r", rep("c", 6))), 
+      include.rownames=FALSE, comment = FALSE, booktabs = TRUE, hline.after = c(0,7))
+
+```
+<!-- (67.74, 2.40), followed by SVM + D2V (67.61, 2.82), NB + TF-IDF (65.59, 2.57), RF + D2V (62.83, 5.54), LR + TF-IDF (62.22, 2.72), SVM + TF-IDF (60.40, 3.29), AND RF + TF-IDF (53.74, 2.71) . -->
+
 ```{r, eval = FALSE}
-results %>%
-  filter(dataset == "ace") %>%
-
-```
-
-```{r, out.width = "50%", fig.cap = "performance on Ace dataset"}
-# path
-aceplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/ace", pattern = ".pdf", full.names=TRUE)
-include_graphics(aceplots[1])
-```
-
-## Evaluation on the Nudging dataset 
-```{r, out.width = "50%", fig.cap = "Performance on Nudging dataset"}
-# path
-nudgingplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging", full.names=TRUE)
-include_graphics(nudgingplots[1])
-```
-
-## Evaluation on the PTSD dataset
-
-_simulation on svm + tfidf is not finished yet_
-```{r, eval = FALSE, out.width = "50%", fig.cap = "Performance on PTSD dataset"}
-ptsdplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd", full.names=TRUE)
-include_graphics(ptsdplots[1])
-ptsdplots
-```
-
-## Evaluation on the Software dataset
-
-```{r, out.width = "50%", fig.cap = "Performance on Software dataset"}
-# path
-softwareplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/software", full.names=TRUE)
-include_graphics(softwareplots[1])
-```
-
-## Evaluation on the Virus dataset
-
-```{r, out.width = "50%", fig.cap = "Performance on Virus dataset"}
-# path
-virusplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/virus", full.names=TRUE)
-include_graphics(virusplots[1])
-```
-
-## Evaluation on the Wilson dataset
-
-```{r, out.width = "50%", fig.cap = "Performance on Wilson dataset"}
-# path
-wilsonplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/wilson", full.names=TRUE)
-include_graphics(wilsonplots[1])
-```
-
-\newpage
-
-## Overall Comparison
-- models in general?
-- which models perform better in which contexts?
-\newpage
-```{r}
 stabres %>%
@@
   autofit() 
-
-# results %>%
-#   select(model, dataset, loss) %>% 
-#   group_by(dataset) %>%
-#   mutate(rank = dense_rank(loss)) %>%
-#   arrange(dataset) %>%
-#   pivot_wider(names_from = dataset, values_from = c("loss", "rank")) %>%
-#   flextable() %>%
-#   colformat_num(j = 2:7, big.mark = ",", digits = 2, na_str = "NA") %>%
-#   colformat_char(j=1) %>%
-#   autofit()
-
-```
-
-\newpage
-
-```{r}
+```
+
+```{r, eval = FALSE}
+atdrank <-
+  results %>%
+  group_by(dataset) %>%
+  mutate(atd_rank = dense_rank(loss)) %>%
+  select(dataset, model, loss, atd_rank)
+
+# %>%
+#   filter(model == "SVM + TF-IDF")
+
+wssrank <- 
+results %>%
+  group_by(dataset) %>%
+  mutate(wss95rank = dense_rank(-wss.95)) %>%
+  select(dataset, model, wss95rank)
+
+rrfrank <-
+results %>%
+  group_by(dataset) %>%
+  mutate(rrf10rank = dense_rank(-rrf.10)) %>%
+  select(dataset, model, rrf10rank)
+
+tabruns %>%
+  group_by(dataset) %>%
+  mutate(atd_rank = dense_rank(mean_loss)) %>%
+  filter(model == "RF + TF-IDF")
+
+tabruns %>%
+  mutate(wss95rank = dense_rank(-mean_wss95)) %>%
+  filter(model == "RF + TF-IDF")
+
+tabruns %>%
+  mutate(rrf10rank = dense_rank(-mean_rrf10)) %>%
+  filter(model == "RF + TF-IDF")
+
+```
+
+## Overall evaluation 
+Recall curves for the simulations on the five remaining datasets are presented in Figure 2.
+For the sake of brevity, recall curves are only plotted once per dataset, like in Figure 1a.
+Please refer to the supplementary material for figures presenting subsets of recall curves for the remaining datasets, like in Figure 1b-f.
+
+```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves for all seven models on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
+d <- c("ptsd", "software", "ace", "virus", "wilson")
+files <- c("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
+include_graphics(files)
+```
+
+First of all, for all datasets, the models were able to detect the relevant publications much faster compared to when screening publications at random order as the recall curves exceed the expected recall at screening at random order by far.
+Even the worst results outperform this reference condition.
+Across simulations, the ATD was at maximum 11.8% (in the Nudging dataset), the WSS@95 at least 63.9% (in the Virus dataset), and the lowest RRF@10 was 53.6% (in the Nudging dataset).
+Interestingly, all these values were achieved by the RF + TF-IDF model.
+
+Similar to the simulations on the Nudging dataset (Figure 1b), the ordering of recall curves changes throughout the screening process, indicating that model performance is dependent on the number of publications that have been screened.
+Moreover, the ordering of models in the Nudging dataset (Figure 1b) does not replicate on the remaining five datasets (Figure 2).
+
+### RQ1 - Comparison across classification techniques
+The first reserach question was aimed at evaluating the first four models adopting either the NB, SVM, LR or RF classification technique, combined with TF-IDF feature extraction.
+When comparing ATD-values of the models (Table 2), the NB + TF-IDF model ranked first in the Ace, Nudging, PTSD, Virus and Wilson dataset, and second in the PTSD and the Software dataset, in which the LR + TF-IDF model achieved the lowest ATD value.
+The RF + TF-IDF ranked last in all of the datasets except in the Ace dataset, where the SVM + TF-IDF model achieved the highest ATD-value.
+
+```{r, eval = FALSE}
+atdrank %>% 
+  filter(model %in% c("NB + TF-IDF", "RF + TF-IDF", "SVM + TF-IDF", "LR + TF-IDF")) %>% 
+  arrange(dataset, atd_rank)
+```
+
+```{r, eval = FALSE}
+wssrank %>% 
+  filter(model %in% c("NB + TF-IDF", "RF + TF-IDF", "SVM + TF-IDF", "LR + TF-IDF")) %>% 
+  arrange(dataset, wss95rank)
+```
+Additionally, in terms of WSS@95 (Table 3) the ranking of models was strikingly similar across all datasets.
+In the Ace, Nudging, Software, and Virus dataset, the highest WSS@95 value was always achieved by the NB + TF-IDF model, followed by LR + TF-IDF, SVM + TF-IDF, and RF + TF-IDF.
+In the PTSD dataset this ranking applied as well, except that the LR + TF-IDF and NB + TF-IDF showed equal WSS@95 values.
+The ordering of the models for the Wilson dataset was NB + TF-IDF, RF + TF-IDF, LR + TF-IDF and SVM + TF-IDF.
+
+```{r, eval = FALSE}
+rrfrank %>% 
+  filter(model %in% c("NB + TF-IDF", "RF + TF-IDF", "SVM + TF-IDF", "LR + TF-IDF")) %>% 
+  arrange(dataset, rrf10rank)
+```
+Moreover, in terms of RRF@10 (Table 4) the NB + TF-IDF model achieved the highest RRF@10 value in the Ace, Nudging, and Wilson dataset.
+LR + TF-IDF ranked first in the PTSD dataset, SVM + TF-IDF was the best performing model within the Wilson dataset.
+The RF + TF-IDF model was again the worst performing model within all datasets, with on exception for the Software dataset.
+In this dataset, NB + TF-IDF ranked fourth, the remaining three models achieved an equal RRF@10 score.
+
+Taken together, these results show that while all four models perform quite well, the NB + TF-IDF shows high performance on all measures across all datasets, whereas the RF + TF-IDF model never performd best on any of the measures across all datasets.
+<!-- The RF + TF-IDF model did not perform well on any of the datasets.
+This model was listed the lower half of the ranking across all datasets for both WSS@95, RRF@10^[With one exception for the RRF@10 in the Software dataset, however the range for this model-dataset combination is relatively small min(RRF@10) = 98.2, max(RRF@10) = 99.3.], and ATD, where the model ranked lowest within four datasets.
+-->
+
+<!-- all datasets. Interestingly this model held it position when comparing ATD-values of all seven models at once, except for the Wilson dataset, where it ranked second, outperformed by   -->
+
+<!-- the NB + TF-IDF belonged to the top four performing models in every dataset in terms of ATD, ranking first in the Wilson, Ace, and Virus dataset.  -->
+
+<!-- For the PTSD dataset, the top performing classifiers are SVM + D2V (1.36, 0.05) AND LR + D2V () -->
+<!-- For the Software dataset, models perform very similar with the -->
+
+<!-- On the PTSD dataset  classification strategies had good performance as WSS@95%.  -->
+<!-- No direct comparison between datasets can be made so we summarise model performance in terms of ranking. -->
+
+### RQ2 - Comparison across feature extraction techniques
+The following section is concerned with the question of how models using different feature extraction strategies relate to each other.
+The recall curves for the Nudging data (Figure 1d-f) show a clear trend of the models adopting Doc2vec feature extraction outperforming their TF-IDF counterparts.
+This trend also shows from the WSS@95 and RRF@10 values indicated by the vertical and horizontal lines in the figure.
+Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting Doc2vec feature extraction always achieved a smaller ATD-value than the model adoptin TF-IDF feature extraction.
+
+In contrast, this pattern of models adopting Doc2vec outperforming their TF-IDF counterparts in the Nudging dataset does not replicate across other datasets.
+Whether evaluated in terms of recall curves, WSS@95, RRF@10 or ATD, the findings were mixed.
+Neither one of the feature extraction strategies showed superior performance within certain datasets nor within certain classification techniques.
+
+```{r, eval = FALSE}
+wssrank %>% 
+  filter(model != "NB + TF-IDF") %>% 
+  arrange(dataset, wss95rank)
+
+atdrank %>% 
+  filter(model != "NB + TF-IDF") %>% 
+  arrange(dataset, atd_rank)
+
+atdrank %>% 
+  arrange(model, atd_rank)
+
+```
+
+```{r, eval = FALSE}
+wssrank %>% 
+  arrange(wss95rank, model, dataset)
+
+atdrank %>% 
+  arrange(atd_rank, model, dataset)
+
+rrfrank %>% 
+  arrange(rrf10rank, model, dataset)
+
+```
+
+### RQ3 - Comparison across research contexts 
+First of all, models showed much higher performance for some datasets than for others.
+While performance on the PTSD (Figure 2a) and the Software dataset (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.
+There does not seem to be a clear distinction between the datasets from the biomedical sciences (Ace, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, Software).
+This result also holds in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
+
+Secondly, variability of model performance differed across datasets.
+For the PTSD (Figure 2a), Software (Figure 2b), and the Virus (Figure 2d) datasets, recall curves form a tight group meaning that within these datasets, the models perform relatively similar.
+For the Nudging (Figure 1a), Ace (Figure 2c), and Wilson (Figure 2e) dataset, the recall curves are much further apart, indicating that model performace is much more dependent on the classification technique and feature extraction strategy.
+The MAD values of the ATD, WSS@95 and RRF@10 confirm that within the PTSD, Software and Virus datasets, model performance is less spread out than within the Nudging, Ace and Wilson dataset.
+
+Moreover, for some datasets the initial training data set seemed to have more impact on model performance than for others.
+the Ace and Wilson datasets model performance is more dependent on the initial training data, as these curves curves are wider compared to the other figures.
+
+<!-- For the PTSD dataset, WSS@95% ranges from 84.20% (RF + TF-IDF) to 93.75% (LR + TF-IDF).  -->
+
+Overall these results indicate that first of all, model performance was mostly data dependent, however, the ordering of models is fairly similar. 
+<!-- - the ordering of models is not the same in every dataset -->
+<!-- - the spread between models performance differs over datasets, (high in ) -->
+<!-- - social sciences vs medical sciences -->
+
+<!-- #### plot:  -->
+<!-- ## Overall Comparison -->
+<!-- - models in general? -->
+<!-- - which models perform better in which contexts? -->
+
+<!-- all models perform better  -->
+<!-- which models perform well overall.  -->
+
+<!-- ranges in value: some datasets is matters more which models you choose, for some it matters less!  -->
+
+<!-- #### across datasets  -->
+<!-- For the SVM + TF-IDF model, WSS@95 ranged from 71.11 - 92.76 for the NB + TF-IDF model, WSS@95 ranged from 71.69 - 93.52, for -->
+
+```{r, eval = FALSE}
 metricsat <- c("WSS@95", "RRF@10", "ATD")
@@
 
-```{r}
+```{r, eval = FALSE}
 # format numbers
@@
 
-\newpage
 # Discussion 
-- we look for final inclusions but we screen only the abstracts (do they satisfy the imformation need  (blake (page 19 omara et evs)))
-
-future research: 
-- stopping rule is not discussed
-- computation/retraining time
-
-strengths:
-
-- open data
-- different research areas
-- different models on same dataset
-- different datasets on same model
-
-limitations
-
-future research
-- all models save time, difficult to distinguish performance over datasets, especially when applied on a dataset of which no prior information is known (e.g.
-inclusions isn't known in practice).
-Perhaps go for other criteria like the fastest model, replicate study with computation time?
-
-Simulating the title and abstract screening process, models are evaluted on their capability/speed of detecting the final inclusions. 
-However, in a manual SR these final inclusions are selected after reading the fulltext. Information the text mining tool does not have. 
-To truly assess the added value of such a tool, models should be evaluated on their capability of detecting the abstract inclusions. 
-Call for systematic reviewers to openly publish need for open data containing abstract inclusions, not only final inclusions!
-
-\newpage
-
-# Appendix A - list of definitions
-
-### Feature Extraction Strategies 
-split_ta = overall hyperparameter
-
-#### TF-IDF
-
-##### hyperparameters 
-    ngram_max: int
-            Can use up to ngrams up to ngram_max. For example in the case of
-            ngram_max=2, monograms and bigrams could be used.
-
-#### Doc2Vec
-Predicts words from context. 
-Aims at capturing the relations between word (man-woman, king-queen).
-[@Le2014]. Using a neural network.
-
-using Continuous Bag-of-Words (CBOW), Skip-Gram model, ....
-Word vector _W_ and extra: document vector _D_, trained to predict words in the text.
-
-From gensim [@Rehurek2010].
-
-        Arguments
-        ---------
-        vector_size: int
-            Output size of the vector.
-        epochs: int
-            Number of epochs to train the doc2vec model.
-        min_count: int
-            Minimum number of occurences for a word in the corpus for it to
-            be included in the model.
-        workers: int
-            Number of threads to train the model with.
-        window: int
-            Maximum distance over which word vectors influence each other.
-        dm_concat: int
-            Whether to concatenate word vectors or not.
-            See paper for more detail.
-        dm: int
-            Model to use.
-            0: Use distribute bag of words (DBOW).
-            1: Use distributed memory (DM).
-            2: Use both of the above with half the vector size and concatenate
-            them.
-        dbow_words: int
-            Whether to train the word vectors using the skipgram metho
-
-#### SBERT
-
-BERT-base model with mean-tokens pooling [@Reimers2019]
-
-#### embeddingIdf 
-This model averages the weighted word vectors of all the words in the text,
-in order to get a single feature vector for each text. The weights are provided by the inverse document frequencies
-
-### Models 
-#### Naive Bayes 
-Naive Bayes assumes all features are independent given the class value. [@Zhang2004]
-
-ASReview uses the ` MultinomialNB` from the scikit-learn package [@scikit-learn], that implements the naive Bayes algorithm for multinomially distributed data. 
-` nb`
-
-Hyperparameters
-
-  * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations.
-
-#### Random Forests
-A number of decision trees are fit on bootstrapped samples of the original data, 
-[@Breiman2001]
-RandomForestClassifier from sklearn
-
-Arguments
-        ---------
-        n_estimators: int
-            Number of estimators.
-        max_features: int
-            Number of features in the model.
-        class_weight: float
-            Class weight of the inclusions.
-        random_state: int, RandomState
-            Set the random state of the RNG.
-        """
-
-#### Support Vector Machine
-
- Arguments
-        ---------
-        gamma: str
-            Gamma parameter of the SVM model.
-        class_weight:
-            class_weight of the inclusions.
-        C:
-            C parameter of the SVM model.
-        kernel:
-            SVM kernel type.
-        random_state:
-            State of the RNG.
-
-#### Logistic Regression
-
-#### __Dense Neural Network__
-
-### Query Strategies 
-* Max - Choose the most likely samples to be included according to the model
-* Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994] 
-* Random - randomly selects abstracts with no regard to model assigned probabilities. 
-* Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled
-
-The following combinations are simulated:
-
-* cluster
-* max
-* cluster * random 
-* cluster * uncertainty
-* max * cluster
-* max * random
-* max * uncertainty
-
-### Balance Strategies
-
-### amount of training data
-
-* n_instances = number of papers queried each query
-* n_queries = number of queries
-* n_prior_included: 5
-* n_prior_excluded:
-
-# Combinations
-
-This leads to  `r nrow(combins)` combinations of configurations.
-
-- Naive bayes only goes with tfidf feature extraction.
-- For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
-- This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.
-
-See appendix A for a table containing all 273 combinations.
-
-## Cross-validation
-Should give an accurate estimate of maximum performance / future systematic reviews to be performed.
+The current study set out to evaluate performance of active learning models for the purpose of identifying relevant publications in systematic review datasets. 
+<!-- This study adds to existing literature by evaluating models across four different classification techniques and two different feature extraction strategies.
+Moreover, as previous studies have paid little attention to the generalizability of active learning models across different research contexts, models were evaluated across six systematic review datasets from various research areas.
+-->
+This study has been one of the first attempts to examine different classification strategies and feature extraction strategies in active learning models for systematic reviews.
+Moreover, this study has provided a deeper insight into the perforance of active learning models across research contexts.
+
+Taken together, the findings confirm the great potential of active learning models in reducing workload for systematic reviewers. 
+In a previous study, the Ace dataset was used to simulate a model that did not use active learning, finding a WSS@95 value of 56.61% [@Cohen2006], whereas the models in the current study achieved far superior WSS@95 values varying from 68.6% to 82.9% in this dataset.
+Active learning models clearly outperformed a model who did not use active learning.
+In addition, the Software dataset was used to simulate an active learning model [@Yu2018] and reached WSS@95 of 91%, strikingly similar the WSS@95 values found in the current study which ranged from 90.5 to 92.3.
+
+### Classification techniques
+The first research question in this study sought to evaluate models adopting different classification techniques.
+The most obvious finding to emerge from these evaluations was that the NB + TF-IDF model consistently performed as one of the best models.
+The results suggest that albeit the widely used SVM-classifier performed fairly well, LR and NB classification strategies are interesting, if not superior alternatives to the standard in this field.
+<!-- Across simulations the NB + TF-IDF model demonstrated high performance on  -->
+
+### Feature extraction strategy 
+The overall results on models adopting Doc2vec versus TF-IDF feature extraction strategy remain inconclusive.
+According to these findings, adopting Doc2vec instead of the well-established TF-IDF feature extraction strategy does not lead to better performing models.
+Given these results, although preliminary, preference goes out to teh TF-IDF feature extraction technique as this relatively simplistic technique will lead to more interpretable model.
+
+### Research contexts 
+Simulating models on a heterogenous collection of systematic review datasets demonstrated that model performance was very data-dependent.
+Within some datasets, models achieved much higher overall performance than within other datasets.
+Moreover, for some datasets, differences between models were much larger than for other datasets.
+It has been suggested that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014].
+This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, Ace) was not in any way superior to performance within the datasets from other resesarch areas (PTSD, Software and Nudging).
+An issue that emerges from these findings is that difficulty of active learning was not confined to any particular research area.
+A possible explanation for this is that difficulty of active learning could be attributed to factors more directly related to the systematic review at hand, such as the inclusion rate and the complexity of inclusion criteria used to identify relevant publications [@Gates2018a; @Rathbone2015].
+Although the current study did not investigate the inclusion criteria of systematic reviews, interestingly, the datasets on which the active learning models performed worst, Nudging and Virus, were also the datasets with the highest inclusion rates, 5.4% and 5.0%, respectively.
+
+<!-- as differences in model performance could not be linked to non-biomedical datasets only from the biomedical areas (Nudging, Virus, and Wilson) did not perform did the datasets in which models pachieved highest performance  -->
+
+<!-- although the nature of this study was rather exploratory, the results yield important insights on the ...  -->
+
+<!-- Since models are more data dependent than model dependent (although for some datasets model performance varies more widely than for others).
+Maybe it doesn't really matter which model you pick although if you want to be save, the nb is a one size fits all model.
+
+## Strengths and limitations
+<!-- The findings from this study have extened our knowledge on performance of different classification strategies We added to this emerging field of research by expanding model evaluations across classification techniques and feature extraction strategies.
+The findings from this study has extended our knowledge on  -->
+
+<!-- what does this mean for reviewing?? save a lot of time ! -->
+<!-- and if you've limited screening time then why not use such an prioritization model.  -->
+
+<!-- This thesis adds to the existing knowledge on active learning models for sreening publications by evaluating  -->
+<!-- We evaluted active learning models using established methods (certainty sampling, rebalancing, threw some new methods in the mix and evaluated them on heterogenous   -->
+<!-- what did we add to other research  -->
+
+<!-- We were able to reach WSS@95 of 63.9-91.7% (instead of 30-70 as stated in [@OMara-Eves2015]). Depending on the model-dataset combination.  -->
+<!-- current study adds to this field by expanding -->
+<!-- Across all classification techniques, feature extraction strategies and review contexts, active learning models exceeded screening at random order by far.  -->
+
+## Limitations and future research
+When applied in systematic review practice, the succes of active learning models stands or falls down with the generalizability of model performance across unseen datasets.
+It is important to bear in mind that model hyperparameters were optimized for each model-dataset combination.
+Thus, the observed results reflect maximum model performance for the datasets at hand.
+The question remains whether model performance generalizes to datasets for which the hyperparameters were not optimized.
+Further research should be undertaken to determine the sensitivity of model performance to the hyperparameter values.
+
+<!-- When models are applied in a real world setting there is no way to know of optimal parameter. Future research will focus on a cross-validation  -->
+<!-- study did not seek to address results to differences in ... ?  -->
+
+<!-- The current study was designed to detecting the final inclusions in a systematic review.  -->
+<!-- It is interesting to note that studies use only abstract + title infor -->
+<!-- Since the active learning models base their predictions only on metadata... -->
+In systematic reviews, screening publications is typically a two-step process in which first, titles and abstracts are screened to identify potentially relevant publications, called abstract inclusions.
+Second, the fulltexts of these publications are read to identify the relevant publications.
+This implies that the relevant publications are selected based on information that the models do not have.
+To truly assess the added value of active learning models in title-and-abstract screening, models should be evaluated on their capability of detecting the abstract inclusions instead of relevant publications only.
+However, this data is typically not available.
+Hence, greater efforts are needed to provide information on the abstract inclusions in openly published systematic review datasets.
+
+<!-- just exploratory, no fancy statistical analysis, however the goal was not to look for the best model. -->
+<!-- strengths: -->
+
+<!-- - open data -->
+<!-- - different research areas -->
+<!-- - different models on same dataset -->
+<!-- - different datasets on same model -->
+
+One unanticipated finding was that the runtime of simulations varied widely across models, indicating that some models need more time to retrain after a publication has been labelled than other models.
+This finding has important implications for the practical application of such models, as an efficient model should be able to keep up with the decision-making speed of the reviewer.
+Further studies taking into account retraining time will need to be undertaken.
+
+<!-- Now that we know that the potential of models/that the models show good performance, the next step is to identify factors that drive performance.
+When the only information available is an unlabeled dataset and we only want to try one model,  When applied in practice, it is  -->
+<!-- - challenge is how to define BEFORE knowing the answers, what the model is..
+In practice, knowing what the best mdoel is after labelling has no value whatsoever, the model + hyperparameters need to be defined a priori.
+-->
+<!-- - difficult to distinguish performance over datasets, especially when applied on a dataset of which no prior information is known (e.g. inclusions isn't known in practice).  -->
+
+# Conclusions 
+Overall, the findings of this study confirm that active learning models show great potential of finding relevant publications in a systematic review dataset, while minimizing the number of publications needed to screen.
+The results shed new light on the performance of different classification techniques, indicating that the Naive Bayes classification technique is superior to the widely used SVM.
+As model performance differs vastly across datasets, this study raises the question what causes models to yield more workload savings for some systematic review datasets than for others.
+In order to gain a better understanding of the added value of active learning models in the screening process, it is essential to identify how dataset characteristics relate to model performance.
+
+<!-- This study shows that active learning models are   -->
+<!-- As all models exceeded screening at random order by far, they show great potential in reducing workload of systematic reviewers.  -->
+<!-- of more precise estimate of  -->
+
+# List of abbreviations
+ML - Machine learning
+
+# Declarations
+
+## Ethics approval and consent to participate
+
+## Consent for publication
+Not applicable.
+
+## Availability of data and materials 
+All systematic review datasets used during this study are
+
+## Competing interests
+The author declares that they has no competing interests" in this section.
+
+## Funding
+Computing hours on the Cartesius supercomputer were funded by SURFsara.
+SURFsara had no role whatsoever in the design of the current study, nor in the data collection, analysis and interpretation, nor in writing the manuscript.
+
+## Authors' contributions
+
+## Acknowledgements
+I am grateful for all researchers who have made great efforts to openly publish the data on their systematic reviews, special thanks go out to Rosanna Nagtegaal.
+I would also like to thank Caroline van Baal for supporting me in writing this thesis, and prof.
+dr.
+René Eijkemans, for being the second grader of this thesis.
+Finally, I would like to express my appreciation to my supervisors prof.
+dr.
+Rens van de Schoot, Jonathan de Bruin and dr.
+Raoul Schram.
+Your door was always open and your enthusiasm was contagious.
+<!-- \newpage -->
+
+<!-- # Appendix A - list of definitions -->
+
+<!-- ### Feature Extraction Strategies  -->
+<!-- split_ta = overall hyperparameter  -->
+
+<!-- #### TF-IDF -->
+
+<!-- ##### hyperparameters  -->
+<!--     ngram_max: int -->
+<!--             Can use up to ngrams up to ngram_max. For example in the case of -->
+<!--             ngram_max=2, monograms and bigrams could be used. -->
+
+<!-- #### Doc2vec -->
+<!-- Predicts words from context.  -->
+<!-- Aims at capturing the relations between word (man-woman, king-queen). -->
+<!-- [@Le2014]. Using a neural network.  -->
+
+<!-- using Continuous Bag-of-Words (CBOW), Skip-Gram model, .... -->
+<!-- Word vector _W_ and extra: document vector _D_, trained to predict words in the text. -->
+
+<!-- From gensim [@Rehurek2010]. -->
+
+<!--         Arguments -->
+<!--         --------- -->
+<!--         vector_size: int -->
+<!--             Output size of the vector. -->
+<!--         epochs: int -->
+<!--             Number of epochs to train the Doc2vec model. -->
+<!--         min_count: int -->
+<!--             Minimum number of occurences for a word in the corpus for it to -->
+<!--             be included in the model. -->
+<!--         workers: int -->
+<!--             Number of threads to train the model with. -->
+<!--         window: int -->
+<!--             Maximum distance over which word vectors influence each other. -->
+<!--         dm_concat: int -->
+<!--             Whether to concatenate word vectors or not. -->
+<!--             See paper for more detail. -->
+<!--         dm: int -->
+<!--             Model to use. -->
+<!--             0: Use distribute bag of words (DBOW). -->
+<!--             1: Use distributed memory (DM). -->
+<!--             2: Use both of the above with half the vector size and concatenate -->
+<!--             them. -->
+<!--         dbow_words: int -->
+<!--             Whether to train the word vectors using the skipgram metho -->
+
+<!-- #### SBERT -->
+
+<!-- BERT-base model with mean-tokens pooling [@Reimers2019] -->
+
+<!-- #### embeddingIdf  -->
+<!-- This model averages the weighted word vectors of all the words in the text, -->
+<!-- in order to get a single feature vector for each text. The weights are provided by the inverse document frequencies -->
+
+<!-- ### Models  -->
+<!-- #### Naive Bayes  -->
+<!-- Naive Bayes assumes all features are independent given the class value. [@Zhang2004]  -->
+
+<!-- ASReview uses the ` MultinomialNB` from the scikit-learn package [@scikit-learn], that implements the naive Bayes algorithm for multinomially distributed data.  -->
+<!-- ` nb` -->
+
+<!-- Hyperparameters -->
+
+<!--   * alpha - accounts for features not present in learning samples and prevents zero probabilities in further computations.  -->
+
+<!-- #### Random Forests -->
+<!-- A number of decision trees are fit on bootstrapped samples of the original data,  -->
+<!-- [@Breiman2001] -->
+<!-- RandomForestClassifier from sklearn  -->
+
+<!-- Arguments -->
+<!--         --------- -->
+<!--         n_estimators: int -->
+<!--             Number of estimators. -->
+<!--         max_features: int -->
+<!--             Number of features in the model. -->
+<!--         class_weight: float -->
+<!--             Class weight of the inclusions. -->
+<!--         random_state: int, RandomState -->
+<!--             Set the random state of the RNG. -->
+<!--         """ -->
+
+<!-- #### Support Vector Machine -->
+
+<!--  Arguments -->
+<!--         --------- -->
+<!--         gamma: str -->
+<!--             Gamma parameter of the SVM model. -->
+<!--         class_weight: -->
+<!--             class_weight of the inclusions. -->
+<!--         C: -->
+<!--             C parameter of the SVM model. -->
+<!--         kernel: -->
+<!--             SVM kernel type. -->
+<!--         random_state: -->
+<!--             State of the RNG. -->
+
+<!-- #### Logistic Regression  -->
+
+<!-- #### __Dense Neural Network__ -->
+
+<!-- ### Query Strategies  -->
+<!-- * Max - Choose the most likely samples to be included according to the model -->
+<!-- * Uncertainty - choose the most uncertain samples according to the model (i.e. closest to 0.5 probability) [@Lewis1994]  -->
+<!-- * Random - randomly selects abstracts with no regard to model assigned probabilities.  -->
+<!-- * Cluster - Use clustering after feature extraction on the dataset. Then the highest probabilities within random clusters are sampled -->
+
+<!-- The following combinations are simulated:  -->
+
+<!-- * cluster -->
+<!-- * max -->
+<!-- * cluster * random  -->
+<!-- * cluster * uncertainty -->
+<!-- * max * cluster -->
+<!-- * max * random -->
+<!-- * max * uncertainty -->
+
+<!-- ### Balance Strategies  -->
+
+<!-- ### amount of training data -->
+
+<!-- * n_instances = number of papers queried each query -->
+<!-- * n_queries = number of queries -->
+<!-- * n_prior_included: 5 -->
+<!-- * n_prior_excluded: -->
+
+<!-- # Combinations  -->
+
+<!-- This leads to  `r nrow(combins)` combinations of configurations.  -->
+
+<!-- - Naive bayes only goes with tfidf feature extraction. -->
+<!-- - For the feature extraction strategies we will focus on Doc2vec and tfidf. (but will compute all 4) -->
+<!-- - This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.  -->
+
+<!-- See appendix A for a table containing all 273 combinations.  -->
+
+<!-- ## Cross-validation -->
+<!-- Should give an accurate estimate of maximum performance / future systematic reviews to be performed.  -->
 
@@
 <!-- There are many more options available and open to exploration. -->
+\nolinenumbers
 
 # References
+
+<div id="refs"></div>
+
+# Additional file 1 - Remaining figures 
+## PTSD
+```{r, eval = TRUE, fig-sub-ptsd, fig.cap = "Recall curves for the PTSD dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+f <- c("inclusion_all_", "inclusion_tfidf_", "inclusion_d2v_", "inclusion_d2v_vs_tfidf_logistic_", "inclusion_d2v_vs_tfidf_rf_", "inclusion_d2v_vs_tfidf_svm_")
+
+plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/", f, "ptsd.pdf")
+include_graphics(plots)
+```
+
+## Software
+```{r, fig-sub-software, fig.cap = "Recall curves for the Software dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/software/", f, "software.pdf")
+include_graphics(plots)
+```
+
+## Ace
+```{r, fig-sub-ace, fig.cap = "Recall curves for the Ace dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/ace/", f, "ace.pdf")
+include_graphics(plots)
+```
+
+## Virus
+```{r, fig-sub-virus, fig.cap = "Recall curves for the Virus dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/virus/", f, "virus.pdf")
+include_graphics(plots)
+
+```
+
+## Wilson
+```{r, eval = TRUE, fig-sub-wilson, fig.cap = "Recall curves for the Wilson dataset.
+", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+# path
+plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/wilson/", f, "wilson.pdf")
+include_graphics(plots)
+```

### 2020-05-11 results/README.Rmd

@@
 read_results <- function(m){
-   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), recursive = TRUE)
+   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), pattern = "all.json", recursive = TRUE)
   # names of the files are the data
@@
 }
+
+read_trials <- function(m){
+   files <- list.files(paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
+  # names of the files are the data
+  names(files) <- str_split(files, "/", simplify = TRUE)[,9]
+  # read data
+
+  dat <- lapply(files, function(x) fromJSON(file = x))
+  # dat <- lapply(models, list)
+  # dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one_seed/statistics/", m, "/", x)))
+
+  # extract wss, rrf, and loss
+  dat <- map(dat, `[`, c("wss", "rrf", "loss"))
+
+  # transorm into dataframe
+  dat <- map_dfr(dat, ~ as.data.frame(.x), .id = "dataset")
+
+  # add model name
+  dat <- dat %>% 
+    mutate(model = names(models[models == m]))
+
+  return(dat)
+}
+
+datastats <- readRDS("datastats.RDS") %>%
+  select(Dataset, candidates_test, incl_test) %>%
+  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
+  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))
+# account for 1 prior exclusion
+
+datastats$dataset <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
+atdratio <- datastats %>%
+  select(dataset, ratio)
+
+```
+
+```{r}
+runs <- lapply(models, FUN = read_trials)
+
+# all in one dataframe
+runs <- do.call("rbind", runs)
+
+# convert loss (ttd) to percentage 
+runs$loss <- runs$loss*100
+# adjust loss to N_1 : N_1-1
+runs <- left_join(runs, atdratio, by = "dataset")
+
+runs <- runs %>%
+  mutate(loss = loss/ratio) %>%
+  select(-ratio)
+
+# save results file 
+saveRDS(runs, "output/runs.RDS")
+```
+
+```{r}
+# compute standard devaition (bootstrapped)
+test <- 
+  runs %>%
+  select(dataset, model, wss.95, rrf.10, loss)
+
+# compute bootstrap statistics 
+library(boot)
+
+bootmeans <- function(d,i){
+  d2 <- d[i,]
+
+  # result <- d2 %>%
+  #   group_by(model, dataset) %>%
+  #   summarise(meanwss = mean(wss.95),
+  #             meanrrf = mean(rrf.10), 
+  #             meanloss = mean(loss))
+  wss <- mean(d2[, "wss.95"])
+  rrf <- mean(d2[, "rrf.10"])
+  loss <- mean(d2[, "loss"])
+
+  return(c(wss,rrf,loss))
+}
+res <- boot(test, bootmeans, 1000)
+
+test <- 
+  runs %>%
+  select(dataset, model, wss.95, rrf.10, loss) %>% 
+  group_by(model, dataset) %>%
+  summarise(sdwss.95 = sd(wss.95),
+            sdrrf.10 = sd(rrf.10),
+            sdloss = sd(loss))
+
+saveRDS(test, "output/sdruns.RDS")
+```
+
+```{r}
+# sumruns <- runs %>%
+#   group_by(dataset, model) %>%
+#   summarise(mean_wss95 = mean(wss.95),
+#             sd_wss95 = sd(wss.95), 
+#             mean_wss99 = mean(wss.99),
+#             sd_wss99= sd(wss.99),
+#             mean_wss100 = mean(wss.100),
+#             sd_wss100 = sd(wss.100), 
+#             mean_rrf5 = mean(rrf.5),
+#             sd_rrf5 = sd(rrf.5),
+#             mean_rrf10 = mean(rrf.10),
+#             sd_rrf10 = sd(rrf.10), 
+#             mean_rrf20 = mean(rrf.20),
+#             sd_rrf20 = sd(rrf.20),
+#             mean_loss = mean(loss),
+#             sd_loss = sd(loss)) %>%
+#   arrange(mean_loss)
+
+# saveRDS(sumruns, "output/sumruns.RDS")
 ```
@@
 results$loss <- results$loss*100
+# adjust loss to N_1 : N_1-1
+results <- left_join(results, atdratio, by = "dataset")
+
+results <- results %>%
+  mutate(loss = loss/ratio) %>%
+  select(-ratio)
+
 # save results file 
@@
 
+library(expss)
 tab <- 
@@
   select(model,
-         ends_with("ace"),
          ends_with("nudging"),
@@
          ends_with("software"),
+         ends_with("ace"),
          ends_with("virus"),
@@
 ```{r}
-
 metricsat <- c("WSS@95", "RRF@10", "TTD")
@@
 
-test
 test <- merge_h(test, part = "header")
-test
+
 #border_v = fp_border(color="purple")
@@
 test <- merge_v(test, part = "header")
-
-test
-
 test <- theme_booktabs(test)
@@
 
-test
 test <- align(test, align = "left", part = "all" )
-test
+
 ```

### 2020-05-12 manuscript/drafts/manuscript.Rmd
Final version thesis

@@
 ---
-title: Active learning for efficient systematic reviews - 
+title: Active learning for efficient systematic reviews
 subtitle: Evaluating models across research areas 
 author: "Gerbrich Ferdinands"
+# keywords:
+#   - Machine learning
+#   - Active learning
+#   - Systematic Review
+#   - Study Selection
+#   - Text classification
+#   - Text representation
 header-includes:
@@
 output:
-  word_document: default
   bookdown::pdf_document2:
@@
     toc: no
+  word_document: default
 bibliography: asreview.bib
@@
 <!-- csl: systematic-reviews.csl -->
-<!-- --- -->
 
@@
 ```
+
 \newpage
@@
 \linenumbers
-# Abstract
-#### Background 
-<!-- This study aims to contribute to this growing area of research by exploring  -->
-
-#### Methods
-<!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->
-
-#### Results
-#### Conclusions
-#### Keywords
-Machine learning, Active learning, Systematic Review, Study Selection, Text classification, Text representation,
+<!-- # Abstract -->
+<!-- #### Background  -->
+<!-- <!-- This study aims to contribute to this growing area of research by exploring  -->
+
+<!-- #### Methods -->
+<!-- <!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->
+
+<!-- #### Results -->
+<!-- #### Conclusions -->
 
@@
 Various learning models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
-Findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications, i.e.
+Previous findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications, i.e.
 95% recall [@OMara-Eves2015].
@@
 A well-established approach in increasing efficiency in title and abstract screening is screening prioritization [@Cohen2009; @Shemilt2014].
-In screening prioritization, the learning model reorders publications to be screened by their likeliness to be relevant.
-The model presents the reviewer with the publications which are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
+In screening prioritization, the learning model presents the reviewer with the publications which are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
 Such an approach allows for substantial time-savings in the screening process as the reviewer can decide to stop screening after a sufficient number of relevant publications have been retrieved [@Yu2019].
@@
 The general assumption is that by letting the model select which records are labelled, the model can achieve higher accuracy while requiring the human annotator to label as few records as possible [@Settles2009].
-Active learning has proven to be an efficient strategy in large unlabelled datasets where labels are expensive to obtain [@Settles2009], which makes the screening phase in systematic reviewing an ideal candidate for such models because labelling the typical large number of publications is very costly.
+Active learning has proven to be an efficient strategy in large unlabelled datasets where labels are expensive to obtain [@Settles2009].
+This makes the screening phase in systematic reviewing an ideal candidate for such models because typically, labelling a large number of publications is very costly.
 When active learning is applied in the screening phase, the reviewer screens publications that are selected by an active learning model.
@@
 The application of active learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
-Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique, namely Support Vector Machine.
+Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique to predict relevanc of publications, namely Support Vector Machine.
 Findings from outside the field of active learning show that different classification techniques can serve different needs in the retrieval of relevant publications, for example recall versus precision [@Kilicoglu2009; @Aphinyanaphongs2004].
@@
 <!-- Since a plethora of techniques exist [@Aggarwal2012], it would be of interest to incorporate such models to this area as well.  -->
-Moreover, another component known to influence performance of the models is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Le2014; @Zhang2011].
-Previous studies all adopt the widely used 'bag of words' strategy [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010].
-It is of interest to evaluate models using this effective but rather simplistic approach by comparing them to models adopting a more sophisticated strategy, called 'Doc2vec' [@Le2014].
+Another component known to influence performance of the models is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Le2014; @Zhang2011].
+Previous studies all adopt an effective but rather simplistic 'bag of words' strategy [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010].
+It is of interest to evaluate models using this approach by comparing them to models adopting a more sophisticated strategy, called 'Doc2vec' [@Le2014].
 Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] and software engineering [@Yu2018, @Yu2019].
@@
 As far as known to the authors, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between two systematic reviews from different research areas, namely the social and the medical sciences.
-They found that active learning was more difficult on data from the social sciences due to the nature of the different vocabularies used.
+They found that active learning was more difficult on data from the social sciences due to the different nature of the vocabularies used.
 Therefore, it is of interest to evaluate model performance across different research contexts.
@@
 <!-- Active learning systems attempt to overcome the labeling bottleneck by asking -->
-<!-- queries in the form of unlabeled instances to be labeled by an oracle (e.g., a human -->
+<!-- queries in the form of unlabelled instances to be labelled by an oracle (e.g., a human -->
 <!-- annotator). -->
 <!--  that a machine learning algorithm can perform better with less training if it is allowed to choose the data from which it learns.
-An active learner may pose "queries," usually in the form of unlabeled data instances to be labeled by an "oracle" (e.g., a human annotator) that already understands the nature of the problem -->
+An active learner may pose "queries," usually in the form of unlabelled data instances to be labelled by an "oracle" (e.g., a human annotator) that already understands the nature of the problem -->
 <!-- in which a model can choose the data points it would like to learn from, thus allowing it to learn more efficiently -->
-<!-- its predictions by interactively querying the user to provide labels to unlabeled data .  -->
+<!-- its predictions by interactively querying the user to provide labels to unlabelled data .  -->
 <!-- In title and abstract screening this means that the active learning -->
@@
 We adopt four different classification techniques (Naive Bayes, Linear Regression, Support Vector Machine, and Random Forest) and two different feature extraction strategies (TF-IDF and Doc2vec) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
-Model performance was assessed by conducting a retrospective simulation on six systematic review datasets.
-Datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], software engineering [@Yu2018], psychology [@vandeSchoot2017], behavioural public administration [@Nagtegaal2019] and virology [@Kwok2020] to assess generalizability of the models across research contexts.
+Model performance was assessed by conducting a simulation on six systematic review datasets.
+Datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], virology [@Kwok2020], software engineering [@Yu2018], behavioural public administration [@Nagtegaal2019] and psychology [@vandeSchoot2017], to assess generalizability of the models across research contexts.
 The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@ASReview2020].
@@
 
-- Start with the set of all unlabeled records (titles and abstracts), $\mathcal{U}$.
-- The reviewer provides a label for a few, for example 5-10, records $x \in \mathcal{U}$, creating an set of labeled records $\mathcal{L}$.
+- Start with the set of all unlabelled records (titles and abstracts), $\mathcal{U}$.
+- The reviewer provides a label for a few, for example 5-10, records $x \in \mathcal{U}$, creating an set of labelled records $x \in \mathcal{L}$ such that $x \notin \mathcal{U}$.
 The label can be either Relevant $\langle x, \texttt{R}\rangle$ or Irrelevant $\langle x, \texttt{I}\rangle$.
@@
 
-  1. A classifier, $C$, is trained on the labeled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
+  1. A classifier, $C$, is trained on the labelled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
 
@@
 
-  6. The newly labeled record is added to the training data, such that $x \in \mathcal{L}$ and $x \notin \mathcal{U}$
+  6. The newly labelled record is added to the training data, such that $x \in \mathcal{L}$ and $x \notin \mathcal{U}$
 
@@
 
-In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabeled title and abstracts.
+In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabelled title and abstracts.
 The relevant titles and abstracts are identified as early in the process as possible.
@@
 
-<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labeled data set $\mathcal{L}$. -->
+<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labelled data set $\mathcal{L}$. -->
 <!-- This is the starting point for the active learning model. -->
@@
 There are two classes in the dataset: relevant and irrelevant publications.
-Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94% [@Borah2017]).
+Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94%, [@Borah2017]).
 The class imbalance causes the classifier to miss relevant publications, because there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
@@
 
-Previous studies have addressed the class imbalance problem by rebalancing the training data in different ways [@OMara-Eves2015].
-To decrease the class imbalance in the training data, the models in the current study rebalances the training set by Dynamic Resampling (DR).
+Previous studies have addressed the class imbalance problem by rebalancing the training data in various ways [@OMara-Eves2015].
+To decrease the class imbalance in the training data, the models in the current study rebalance the training set by Dynamic Resampling (DR).
 DR undersamples the number of irrelevant publications in the training data, whereas the number of relevant publications are oversampled such that the size of the training data remains the same.
@@
 ## Classification
-To make predictions on the unlabeled publications, a classifier is trained on features from the set of previously labeled publications. 
-<!-- The classifier predicts class of a given unlabeled publication.  -->
+To make predictions on the unlabelled publications, a classifier is trained on features from the training data. 
+<!-- The classifier predicts class of a given unlabelled publication.  -->
 A technique widely used in classification tasks is the Support Vector Machine (SVM).
 SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
-SVMs have been proven to be effective in active learning models for screening prioritization [@Yu2018; Miwa2014].
+SVMs have been proven to be effective in active learning models for screening prioritization [@Yu2018; @Miwa2014].
 Moreover, SVMs are the currently the only classifier implemented in ready-to-use software tools implementing active learning for screening prioritization (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]).
 
-Whilst the performance of several classification techniques has been investigated in the ML-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2018; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
+Whilst the performance of several classification techniques has been investigated in the ML-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2019; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
 <!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
@@
 <!-- To carry out classification of publications, a classifier takes given input features $\mathbf{X}$ -->
-<!-- The model utilizes features of previously labeled publications and  -->
+<!-- The model utilizes features of previously labelled publications and  -->
 <!-- The model utilizes L to predict labels for all abstracts (classifier). (training) -->
@@
 <!-- The cycle starts over again..  -->
-<!-- As the cycle repeats itselfs, labeled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s -->
+<!-- As the cycle repeats itselfs, labelled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s -->
 <!-- We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.  -->
@@
 An example of an approach that aims to overcome this weakness is Doc2vec (D2V).
-Doc2vec represents texts by a neural network, capable of grasping semantics by learning to predict the words in the texts [@Le2014].
+Doc2vec extracts features of the texts by a neural network, capable of grasping semantics by learning to predict the words in the texts [@Le2014].
 
@@
 Firstly, this strategy is far better suited to the goal of prioritizing relevant publications compared to uncertainty-based active learning, in which the publications are prioritized that the model is most uncertain about.
-Secondly, certainty-based active learning is far better equipped at dealing with imbalanced data in active learning [@Fu2011].
+Secondly, certainty-based active learning is far better equipped at dealing with imbalanced data in active learning, as it aims to present only records that belong to the relevant class [@Fu2011].
 
@@
 
-To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:^[The combination NB + D2V could not be tested because the [Multinomial Naive Bayes classifier](https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB) can only handle a feature matrix with positive values, whereas the [Doc2vec feature extraction approach](https://radimrehurek.com/gensim/models/doc2vec.html) produces a feature matrix that can also contain negative values.]
+To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:^[]
 
@@
 
+The combination NB + D2V could not be tested because the Multinomial Naive Bayes classifier^[https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB] can only handle a feature matrix with positive values, whereas the Doc2vec feature extraction approach^[https://radimrehurek.com/gensim/models/doc2vec.html] produces a feature matrix that can also contain negative values.
 Performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing __RQ3__.
 Hence, 42 simulations were carried out, representing all model-dataset combinations.
+To account for variance, every simulation was repeated for 15 trials.
 For every simulation, hyperparameters were optimized through a random search to arrive at maximum model performance.
-To account for variance, every simulation was repeated for 15 trials.
 Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020].
@@
 To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for every of the 15 trials.
-Although varying over trials, the initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
+Although varying over trials, the 15 initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
 A seed value was set to ensure reproducibility.
-The classifier was retrained every time after a publication had been labeled.
-The simulation ended after all publications in the dataset had been labeled.
-
+The classifier was retrained every time after a publication had been labelled.
+The simulation ended after all publications in the dataset had been labelled.
+
+This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
 Simulations were run in ASReview, version 0.9.3 [@ASReview2020].
-Analyses were carried out using R, version 3.6.1 [@RCoreTeam2019].
-All scripts and data are stored in the supplementary material.
-This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
+Analyses were carried out using \texttt{R}, version 3.6.1 [@RCoreTeam2019].
+Scripts and data are stored in the GitHub repository for this thesis^[https://github.com/GerbrichFerdinands/asreview-thesis].The output resulting from the simulation was stored on the Open Science Framework page of this thesis ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far.
 Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
 Access was granted by SURF via a grant (ID EINF-156).
-. 
 <!-- can retrieve the labels from the annotated dataset instead -->
@@
 The PTSD dataset contains publications from the field of _psychology_.
-The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017].
+The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
 Of these six datasets, Ace, and Software have been used for model simulations in previous studies on ML-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].
@@
 Candidate studies with missing abstracts and duplicate instances were removed from the data.
-Preprocessing scripts and resulting datasets can be found in the supplementary material.
+Preprocessing scripts and resulting datasets can be found on the GitHub repository for this thesis.
 Test datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
@@
                                        "Inclusion rate (%)"),1))
-
+datastats <- datastats[c(2,3,4,1,5,6), ]
 print(xtable(datastats, digits = c(0,0,0,0,1)),
@@
 Moreover, WSS makes assumptions about acceptable recall levels whereas this level might depend on the research question at hand [@OMara-Eves2015].
-A statistic that is not dependent on some arbitrary cutoff value is the ATD, which is the average number of publications needed to screen to find a relevant publication.
+A statistic that is not dependent on some arbitrary cutoff value is the ATD, which indicates the average proportion of publications needed to screen to find a relevant publication.
 
@@
 
-<!-- When no balancing is applied, the training data set = labeled data set $\mathcal{L}$ -->
+<!-- When no balancing is applied, the training data set = labelled data set $\mathcal{L}$ -->
 <!-- The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions. -->
@@
 <!-- increasing classification performance with every query.  -->
-<!-- The query strategy determines the way unlabeled papers are queried to the researcher.  -->
+<!-- The query strategy determines the way unlabelled papers are queried to the researcher.  -->
 
@@
 ```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves for the Nudging dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
 # path
@@
 Recall curves for the simulations on the five remaining datasets are presented in Figure 2.
-For the sake of brevity, recall curves are only plotted once per dataset, like in Figure 1a.
-Please refer to the supplementary material for figures presenting subsets of recall curves for the remaining datasets, like in Figure 1b-f.
+For the sake of conciseness, recall curves are only plotted once per dataset, like in Figure 1a.
+Please refer to Additional file 1 for figures presenting subsets of recall curves for the remaining datasets, like in Figure 1b-f.
+
+First of all, for all datasets, the models were able to detect the relevant publications much faster compared to when screening publications at random order as the recall curves exceed the expected recall at screening at random order by far.
+Even the worst results outperform this reference condition.
+Across simulations, the ATD was at maximum 11.8% (in the Nudging dataset), the WSS@95 at least 63.9% (in the Virus dataset), and the lowest RRF@10 was 53.6% (in the Nudging dataset).
+Interestingly, all these values were achieved by the RF + TF-IDF model.
+
+Similar to the simulations on the Nudging dataset (Figure 1b), the ordering of recall curves changes throughout the screening process, indicating that model performance is dependent on the number of publications that have been screened.
+Moreover, the ordering of models in the Nudging dataset (Figure 1b) does not replicate on the remaining five datasets (Figure 2).
 
@@
 
-First of all, for all datasets, the models were able to detect the relevant publications much faster compared to when screening publications at random order as the recall curves exceed the expected recall at screening at random order by far.
-Even the worst results outperform this reference condition.
-Across simulations, the ATD was at maximum 11.8% (in the Nudging dataset), the WSS@95 at least 63.9% (in the Virus dataset), and the lowest RRF@10 was 53.6% (in the Nudging dataset).
-Interestingly, all these values were achieved by the RF + TF-IDF model.
-
-Similar to the simulations on the Nudging dataset (Figure 1b), the ordering of recall curves changes throughout the screening process, indicating that model performance is dependent on the number of publications that have been screened.
-Moreover, the ordering of models in the Nudging dataset (Figure 1b) does not replicate on the remaining five datasets (Figure 2).
-
 ### RQ1 - Comparison across classification techniques
@@
 This trend also shows from the WSS@95 and RRF@10 values indicated by the vertical and horizontal lines in the figure.
-Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting Doc2vec feature extraction always achieved a smaller ATD-value than the model adoptin TF-IDF feature extraction.
+Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting Doc2vec feature extraction always achieved a smaller ATD-value than the model adopting TF-IDF feature extraction.
 
@@
 There does not seem to be a clear distinction between the datasets from the biomedical sciences (Ace, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, Software).
-This result also holds in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
+The PTSD, Software and Nudging dataset also demonstrated high performance in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
 
@@
 
-Moreover, for some datasets the initial training data set seemed to have more impact on model performance than for others.
-the Ace and Wilson datasets model performance is more dependent on the initial training data, as these curves curves are wider compared to the other figures.
+Moreover, the curves for the Ace (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared to other the other datasets.
+For these datasets, model performance seemed to be more dependent on the initial training data set compared to other datasets.
 
@@
 
-Overall these results indicate that first of all, model performance was mostly data dependent, however, the ordering of models is fairly similar. 
+<!-- Overall these results indicate that first of all, model performance was mostly data dependent, however, the ordering of models is fairly similar.  -->
 <!-- - the ordering of models is not the same in every dataset -->
@@
 -->
-This study has been one of the first attempts to examine different classification strategies and feature extraction strategies in active learning models for systematic reviews.
-Moreover, this study has provided a deeper insight into the perforance of active learning models across research contexts.
-
-Taken together, the findings confirm the great potential of active learning models in reducing workload for systematic reviewers. 
+It has been one of the first attempts to examine different classification strategies and feature extraction strategies in active learning models for systematic reviews.
+Moreover, this study has provided a deeper insight into the performance of active learning models across research contexts.
+
+Overall, the findings confirm the great potential of active learning models in reducing workload for systematic reviewers.
+All models were able to detect 95% of the relevant publications after screening less than 40% of the total number of publications, indicating that active learning models can save more than half of the workload in the screening process.
 In a previous study, the Ace dataset was used to simulate a model that did not use active learning, finding a WSS@95 value of 56.61% [@Cohen2006], whereas the models in the current study achieved far superior WSS@95 values varying from 68.6% to 82.9% in this dataset.
-Active learning models clearly outperformed a model who did not use active learning.
-In addition, the Software dataset was used to simulate an active learning model [@Yu2018] and reached WSS@95 of 91%, strikingly similar the WSS@95 values found in the current study which ranged from 90.5 to 92.3.
+Active learning models clearly outperformed a model which did not use active learning.
+In addition, the Software dataset was used to simulate an active learning model [@Yu2018] and reached WSS@95 of 91%, strikingly similar the WSS@95 values found in the current study which ranged from 90.5% to 92.3%.
 
@@
 The most obvious finding to emerge from these evaluations was that the NB + TF-IDF model consistently performed as one of the best models.
-The results suggest that albeit the widely used SVM-classifier performed fairly well, LR and NB classification strategies are interesting, if not superior alternatives to the standard in this field.
+The results suggest that whilst the widely used SVM-classifier performed fairly well, LR and NB classification strategies are interesting if not superior alternatives to the standard in this field.
 <!-- Across simulations the NB + TF-IDF model demonstrated high performance on  -->
@@
 ### Research contexts 
-Simulating models on a heterogenous collection of systematic review datasets demonstrated that model performance was very data-dependent.
+Simulating models on a heterogenous collection of systematic review datasets revealed that model performance is very data-dependent.
 Within some datasets, models achieved much higher overall performance than within other datasets.
@@
 It has been suggested that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014].
-This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, Ace) was not in any way superior to performance within the datasets from other resesarch areas (PTSD, Software and Nudging).
+This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, Ace) was not in any way superior to performance within the datasets from the social sciences (PTSD and Nudging).
 An issue that emerges from these findings is that difficulty of active learning was not confined to any particular research area.
 A possible explanation for this is that difficulty of active learning could be attributed to factors more directly related to the systematic review at hand, such as the inclusion rate and the complexity of inclusion criteria used to identify relevant publications [@Gates2018a; @Rathbone2015].
-Although the current study did not investigate the inclusion criteria of systematic reviews, interestingly, the datasets on which the active learning models performed worst, Nudging and Virus, were also the datasets with the highest inclusion rates, 5.4% and 5.0%, respectively.
+Although the current study did not investigate the inclusion criteria of systematic reviews, the datasets on which the active learning models performed worst, Nudging and Virus, were interestingly also the datasets with the highest inclusion rates, 5.4% and 5.0%, respectively.
 
@@
 <!-- Since the active learning models base their predictions only on metadata... -->
-In systematic reviews, screening publications is typically a two-step process in which first, titles and abstracts are screened to identify potentially relevant publications, called abstract inclusions.
+Screening publications in systematic reviews is typically a two-step process.
+First, titles and abstracts are screened to identify potentially relevant publications, called abstract inclusions.
 Second, the fulltexts of these publications are read to identify the relevant publications.
@@
 
-One unanticipated finding was that the runtime of simulations varied widely across models, indicating that some models need more time to retrain after a publication has been labelled than other models.
+An unanticipated finding was that the runtime of simulations varied widely across models, indicating that some models need more time to retrain after a publication has been labelled than other models.
 This finding has important implications for the practical application of such models, as an efficient model should be able to keep up with the decision-making speed of the reviewer.
@@
 <!-- Now that we know that the potential of models/that the models show good performance, the next step is to identify factors that drive performance.
-When the only information available is an unlabeled dataset and we only want to try one model,  When applied in practice, it is  -->
+When the only information available is an unlabelled dataset and we only want to try one model,  When applied in practice, it is  -->
 <!-- - challenge is how to define BEFORE knowing the answers, what the model is..
@@
 Overall, the findings of this study confirm that active learning models show great potential of finding relevant publications in a systematic review dataset, while minimizing the number of publications needed to screen.
-The results shed new light on the performance of different classification techniques, indicating that the Naive Bayes classification technique is superior to the widely used SVM.
+The results shed new light on the performance of different classification techniques, indicating that the Naive Bayes classification technique is superior to the widely used Support Vector Machine.
 As model performance differs vastly across datasets, this study raises the question what causes models to yield more workload savings for some systematic review datasets than for others.
-In order to gain a better understanding of the added value of active learning models in the screening process, it is essential to identify how dataset characteristics relate to model performance.
+In order to facilitate the applicability of active learning models in systematic review practice, it is essential to identify how dataset characteristics relate to model performance.
 
@@
 
-# List of abbreviations
-ML - Machine learning
-
 # Declarations
@@
 ## Ethics approval and consent to participate
+Was reported in the main text.
 
@@
 ## Availability of data and materials 
-All systematic review datasets used during this study are
+As reported in the main text, all data and materials are available through the GitHub repository for this thesis, https://github.com/GerbrichFerdinands/asreview-thesis.
+This repository contains all systematic review datasets used during this study and their preprocessing scripts, scripts and data on the hyperparamter optimization, scripts on the simulations, scripts for analyzing the results of the simulations, and the source files for this manuscript.
+All output files of the simulation study are stored on the Open Science Framework page of this thesis, https://osf.io/7mr2g/.
 
 ## Competing interests
-The author declares that they has no competing interests" in this section.
+The author declares that they has no competing interests.
 
@@
 SURFsara had no role whatsoever in the design of the current study, nor in the data collection, analysis and interpretation, nor in writing the manuscript.
-
-## Authors' contributions
 
@@
 dr.
-Rens van de Schoot, Jonathan de Bruin and dr.
+Rens van de Schoot, Jonathan de Bruin, and dr.
 Raoul Schram.
@@
 
-# Additional file 1 - Remaining figures 
+# Additional file 1 
+Recall curves plot separately for the PTSD, Software, Ace, Virus and Wilson datasets.
+
 ## PTSD
 ```{r, eval = TRUE, fig-sub-ptsd, fig.cap = "Recall curves for the PTSD dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
 # path
@@
 ```{r, fig-sub-software, fig.cap = "Recall curves for the Software dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
 # path
@@
 ```{r, fig-sub-ace, fig.cap = "Recall curves for the Ace dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
 # path
@@
 ```{r, fig-sub-virus, fig.cap = "Recall curves for the Virus dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
 # path
@@
 ```{r, eval = TRUE, fig-sub-wilson, fig.cap = "Recall curves for the Wilson dataset.
-", fig.subcap=c('All seven models',  "classifier only", "only D2V",'D2V vs TF-IDF for LR', 'D2V vs TF-IDF for RF', "D2V vs TF-IDF for SVM") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
 # path

### 2020-05-13 datasets/readme.Rmd
update research archive

--- 2020-05-11 datasets/data_preprocessing.nb.Rmd
@@
 ---
-title: "Dataset preprocessing"
+title: "Preprocessing datasets"
 output: github_document
 ---
-This notebook processes all systematic review datasets into datasets suitable testing ASReview.
+
+This notebook processes six systematic review datasets into datasets suitable for simulating the screening process.
+
+- Wilson - [@Appenzeller-Herzog2020] is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019]. 
+- Ace -  contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006]. 
+- Virus -  is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020]. 
+- Software - from the software engineering field, contains publications on fault prediction in source code [@Hall2012].
+- Nudging dataset - [@Nagtegaal2019a] on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of 
+- PTSD - on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
+
+Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search.
+Candidate studies with missing abstracts and duplicate instances were removed from the data.
+
+Every dataset has 2 versions: one for hyperparameter optimization `test_datasets` and one for simulation `sim_datasets`.
 
@@
   - keywords? (only for hyperparameter optimization, not for simulation).
-
-Entries with missing abstracts are removed
 

### 2020-05-13 R/datasets.R

@@ -1,115 +1,0 @@
-# this script is for checking all the raw vs preprocessed data, that are on datasets GH repo. 
-library(tidyverse)
-template <- data.frame(search = rep(0,3),
-                       ftext = rep(0, 3), 
-                       incl = rep(0,3),
-                       row.names = c("paper", "raw", "asreview"))
-
-################################################################################
-## Nagtegaal dataset ###########################################################
-################################################################################ 
-# original ---------------------------------------------------------------------
-nagtegaal <- data.frame(paper = c(2006, 377, 100), 
-                        raw = rep(0, 3), 
-                        asreview = rep(0,3),
-                        row.names = c("search", "ftext", "incl"))
-nagtegaal <- t(nagtegaal)
-
-# raw --------------------------------------------------------------------------
-# see nagtegaal.R file
-# asreview ---------------------------------------------------------------------
-abstracts <- readxl::read_xlsx("data/nagtegaal.xlsx")
-table(abstracts$included)
-# duplicated abstracts ?? 
-anyDuplicated(abstracts$abstract)
-abstracts[duplicated(abstracts$abstract),]
-
-nagtegaal["asreview",] <- c(length(abstracts$included),
-                            NA,
-                            sum(abstracts$included)
-                            )
-
-################################################################################
-## Wilson dataset ##############################################################
-################################################################################
-wilson <- template
-wilson["paper", ] <- c(3453, 174, 26)
-
-# raw --------------------------------------------------------------------------
-w_ftext <- read.csv("../datasets/raw/DOKU_All FT-Screening_20200116_cap.csv")
-w_incl <- read.csv("../datasets/raw/DOKU_All Included_20200116_cap.csv")
-w_all <- read.csv("../datasets/raw/DOKU_All TiAb-Screening_20200116_cap.csv")
-wilson["raw", ] <- c(nrow(w_all), nrow(w_ftext), nrow(w_incl))
-
-# asreview ---------------------------------------------------------------------
-w_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Appenzeller-Herzog_Wilson/output/output_csv_wilson.csv",
-                  header=T)
-
-wilson ["asreview",] <- c(nrow(w_asr), 
-                          sum(w_asr$label_abstract_screening, na.rm = TRUE),
-                          sum(w_asr$label_included))
-wilson
-# difference in asreview and raw data is because of 16 duplicates. 
-wilson[2,1] - wilson[3,1]
-
-################################################################################
[…]

### 2020-05-14 manuscript/manuscript/manuscript.Rmd
update research archive
update readme in root

--- 2020-05-12 manuscript/drafts/manuscript.Rmd
@@
 The models were simulated on a convenience sample of six systematic review datasets.
-The data selection process was driven by two factors.
+The data selection process was driven by three factors.
 Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas.
@@
 ```{r}
-# measures for variation within 15 runs 
-#sumruns <- readRDS("../../results/output/sumruns.RDS")
-# tabruns <- sumruns %>%
-#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95", "mean_wss99", "sd_wss99","mean_wss100","sd_wss100", "mean_rrf5","sd_rrf5", "mean_rrf10", "sd_rrf10", "mean_rrf20","sd_rrf20", "mean_loss", "sd_loss"))
-
-# tabruns <- sumruns %>%
-#   select(dataset, model, mean_wss95, sd_wss95, mean_rrf10, sd_rrf10, mean_loss, sd_loss) 
-#
-
-# wss95tab <- tabruns %>%
-#   select(dataset, model, mean_wss95, sd_wss95) %>%
-#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95"))
-
-# wss95tab <- stabres %>%
-#   select(model, starts_with("wss.95"))
 

### 2020-05-14 results/README.Rmd
update readme in root

--- 2020-05-01 results/README.Rmd
@@
 ---
-title: "Untitled"
+title: "Processing simulation output"
 output: github_document
@@
 library(knitr)
+library(flextable)
+library(officer)
 ```
 
-Script for reading simulation files
-```{python}
-# to be found on harddrive results folder
-```
+This directory stores all files used to extract figures and statistics from the simulation study output.
+The directory contains the following:
 
-Script for reading results 
+- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
+- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
+- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
+- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
+- `output` contains the abovementioned tables, stored as .RDS files.
+
+## Define functions for reading simulation output 
 ```{r}
 data <- readRDS("../simulation_study/R/00_datasets.RDS")
-models <- list.files("/Volumes/Gerbrich/asreview/results/one/statistics/")
+models <-c("BCTD", "LCDD", "LCTD", "RCDD", "RCTD", "SCDD", "SCTD")
 names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )
 
-# function that reads results for a model M 
+# function that reads results for all 15 runs
 read_results <- function(m){
-   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m), recursive = TRUE)
+   files = list.files(paste0("one_seed/statistics/", m), pattern = "all.json", recursive = TRUE)
   # names of the files are the data
@@
   # read data
-  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m, "/", x)))
+  dat <- lapply(files, function(x) fromJSON(file = paste0("one_seed/statistics/", m, "/", x)))
 
@@
 }
+
+# function for extracting all separate runs 
+read_trials <- function(m){
+   files <- list.files(paste0("one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
+  # names of the files are the data
+  names(files) <- str_split(files, "/", simplify = TRUE)[,9]
+
+  # read data
+  dat <- lapply(files, function(x) fromJSON(file = x))
+
+  # extract wss, rrf, and loss
+  dat <- map(dat, `[`, c("wss", "rrf", "loss"))
+
+  # transorm into dataframe
+  dat <- map_dfr(dat, ~ as.data.frame(.x), .id = "dataset")
+
+  # add model name
+  dat <- dat %>% 
+    mutate(model = names(models[models == m]))
+
+  return(dat)
+}
+
+# ATD needs to be adjusted for 1 prior inclusion and 1 prior exclusion! 
+# compute adjusted ATD to make it equal to the area above the curve
+datastats <- readRDS("datastats.RDS") %>%
+  select(Dataset, candidates_test, incl_test) %>%
+  # account for 1 prior exclusion and 1 prior inclusion
+  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
+  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))
+
+datastats$dataset <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
+atdratio <- datastats %>%
+  select(dataset, ratio)
 ```
 
-Parse 
-```{r, eval = FALSE}
-dat$virus
-# extract only wss, rrf, and loss values from list
-test <- map(dat, `[`, c("wss", "rrf", "loss"))
-# transorm into dataframe
-test <- map_dfr(test, ~ as.data.frame(.x), .id = "dataset")
-# add model name
-test <- test %>% mutate(model = "NB + TF-IDF")
+## Load results for 15 separate trials
+```{r}
+# read all 15 trials separately
+runs <- lapply(models, FUN = read_trials)
+
+# all in one dataframe
+runs <- do.call("rbind", runs)
+
+# convert loss (ttd) to percentage 
+runs$loss <- runs$loss*100
+# adjust loss to N_1 : N_1-1 (to the prior inclusions)
+runs <- left_join(runs, atdratio, by = "dataset")
+runs <- runs %>%
+  mutate(loss = loss/ratio) %>%
+  select(-ratio)
+
+# save results file 
+saveRDS(runs, "output/runs.RDS")
 ```
 
-Apply over all datasets and models 
+Compute standarad deviation from the 15 separate trials.
+```{r}
+# compute standard deviation (bootstrapped)
+sdruns <- 
+  runs %>%
+  select(dataset, model, wss.95, rrf.10, loss) %>% 
+  group_by(model, dataset) %>%
+  summarise(sdwss.95 = sd(wss.95),
+            sdrrf.10 = sd(rrf.10),
+            sdloss = sd(loss))
+
+saveRDS(sdruns, "output/sdruns.RDS")
+```
+
+## Load results as means over all 15 trials  
 ```{r}
@@
 results <- do.call("rbind", results)
-results %>%
-  group_by(dataset) %>%
-  arrange(loss)
+
+# convert loss (ttd) to percentage 
+results$loss <- results$loss*100
+# adjust loss to N_1 : N_1-1
+results <- left_join(results, atdratio, by = "dataset")
+
+results <- results %>%
+  mutate(loss = loss/ratio) %>%
+  select(-ratio)
+
+# save results file 
+saveRDS(results, "output/results.RDS")
 ```
 
-Create table
+Create table for manuscript (all means over 15 runs)
 ```{r}
-library(tables)
-library(data.table)
-library(gt)
-library(tidyr)
-library(tidyverse)
 tabres <- 
@@
 
-```
-
-```{r}
-library(expss)
-
-test <- results %>% pivot_longer(cols = c(starts_with("wss"), starts_with("rrf"), "loss"), names_to = "stats", values_to = "value")
-
-tab <- 
-  test %>%
-  tab_rows(model) %>%
-  tab_cells(value) %>%
-  tab_cols(dataset %nest% stats) %>%
-  tab_stat_mean() %>%
-  tab_pivot()
-
-```
-
-```{r}
+# table of mean statistics over all runs 
+stabres <- 
 tabres %>%
-  select(model, starts_with("wss.95"), starts_with("loss"))
-
-gtest <- tabres %>%
-  gt()
-
-gtest <- results %>%
-  gt() %>%
-
-```
-```{r}
-library(flextable)
-typology <- data.frame(
-  col_keys = names(results)[2:43],
-  what = rep(data,7),
-  measure = rep(c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD"), each = )
-  what = c(rep("WSS", 3), rep("RRF", 3), "loss"),
-  measure = c("95", "99", "100", "5", "10", "20", "0"),
-  stringsAsFactors = FALSE
+  # select statistics
+  select(model,
+         starts_with("wss.95"),
+         starts_with("rrf.10"), 
+         starts_with("loss")) %>%
+  # reorder datasets
+  select(model,
+         ends_with("nudging"),
+         ends_with("ptsd"),
+         ends_with("software"),
+         ends_with("ace"),
+         ends_with("virus"),
+         ends_with("wilson")
          )
 
-test <- flextable(tabres)
-test <- set_header_df(test, mapping = typology, key = "col_keys")
-merge_h(test, part = "header")
+saveRDS(stabres, "output/tabresults.RDS")
+
+knitr::kable(stabres, format = "markdown", digits = 1)
 ```
-
-Now again for with seed 
-```{r}
-#files = list.files("/Volumes/Gerbrich/asreview/results/one/statistics/", recursive = TRUE)
-
-```

### 2020-05-14 simulation_study/plot/saveplot.py

@@ -1,7 +1,0 @@
-with Plot.from_paths(["PATH_1", "PATH_2"]) as plot:
-	inc_plot = plot.new("inclusion")
-	inc_plot.set_grid()
-	inc_plot.set_xlim(0, 30)
-	inc_plot.set_ylim(0, 101)
-	inc_plot.set_legend()
-	inc_plot.save("SOME_FILE.png")

### 2020-05-14 datasets/readme.Rmd
update dataset preprocessing'

--- 2020-05-11 datasets/data_preprocessing.nb.Rmd
@@
 ---
-title: "Dataset preprocessing"
+title: "Preprocessing datasets"
 output: github_document
+bibliography: ../manuscript/manuscript/asreview.bib
 ---
-This notebook processes all systematic review datasets into datasets suitable testing ASReview.
 
-Every dataset is a .csv file with the following columns: 
-  - title
-  - abstract
-  - label_included
-  - keywords? (only for hyperparameter optimization, not for simulation).
+This notebook processes six systematic review datasets into datasets suitable for simulating the screening process.
 
-Entries with missing abstracts are removed
+- __Wilson__ - is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism.
+Dataset: [@Appenzeller-Herzog2020].
+Paper: [@Appenzeller-Herzog2019].
+- __Ace__ -  contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease Paper and dataset: [@Cohen2006]. 
+- __Virus__ -  is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020]. 
+- __Software__ - from the software engineering field, contains publications on fault prediction in source code [@Hall2012].
+- __Nudging__ dataset - [@Nagtegaal2019a] on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of 
+- __PTSD__ - on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
+
+Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search.
+Candidate studies with missing abstracts and duplicate instances were removed from the data.
+
+Every dataset has 2 versions: one for hyperparameter optimization (`test_datasets`), and one for simulation (`sim_datasets`).
+
+Every simulation dataset is a .csv file with the columns `title`, `abstract`, `label_included`, the last one indicating whether a publication was relevant or not.
+This is the label that is queried by the active learning model when simulating a systematic review.
+The reason for this sparse datasets (no keywords are included etc) is twofold.
+1) This is by PRISMA guidelines the only information that should be used to identify relevant publications from a search and 2) I wanted equal information for all datasets, and for some datasets this was the only information that was available.
+For hyperparameter optimization I used all information accessible to arrive at better hyperparameters, with future projects in mind.
 
@@
 
-### Set-up
+### Preprocessing datasets
+For every datasets, 3 numbers are given: total number of publications, abstract inclusions and final inclusions.
+For some datasets there are discrepancies between how these numbers are reported in the publication and how they actually are in the raw dataset.
+Therefore, these numbers are given for how they are reported in the manuscript, how they are found in the raw data, and how they are found in the test dataset, e.g.
+after removing duplicates and missing abstracts.
+Moreover, statistics on missingness and duplicates are given.
+
 ```{r, echo = FALSE}
@@
 
-## ACE
+## Ace dataset
 ```{r}
 ace <- template
-# paper ------------------------------------------------------------------------
+
+# information given in the paper -----------------------------------------------
 ace["paper", ] <- c(2544, NA, round(2544*0.0160))
@@
 
-# asreview ---------------------------------------------------------------------
+# asreview dataset -------------------------------------------------------------
 ace_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Cohen_EBM/output/ACEInhibitors.csv",
                      header=T)
+```
+
+### Create test dataset
+```{r}
 # replace empty abstracts by NA values. 
-
 ace_asr[ace_asr$abstract == "", "abstract"] <- NA
@@
                        sum(ace_asr$label_included))
-```
 
-### Create test dataset
-```{r}
 # drop missings and duplicates. 
@@
 ### Some statistics 
-```{r}
+On missingness (# and %) and duplicates (# and %): 
+```{r, echo = false}
 # missingness and duplicates in raw data on ASReview
-drops["ace",]
-ace
+drops["ace",] %>% knitr::kable(format = "markdown", digits = 2)
 ```
 
-## nudging dataset 
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+ace %>% knitr::kable(format = "markdown")
+```
+
+## Nudging dataset 
 ```{r}
@@
 
-### Create test dataset
+### Some statistics
+On missingness (# and %) and duplicates (# and %):
 
-### Some statistics
-```{r}
-
-drops["nudging",]
-nudging
+```{r, echo = FALSE}
+drops["nudging",]%>% knitr::kable(format = "markdown")
+```
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+nudging %>% knitr::kable(format = "markdown")
 ```
@@
 
-Derive statistics in final test set.
-```{r}
-drops["ptsd", ]
-ptsd
+### Some statistics
+On missingness (# and %) and duplicates (# and %):
+
+```{r, echo = FALSE}
+drops["ptsd",]%>% knitr::kable(format = "markdown")
+```
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+ptsd %>% knitr::kable(format = "markdown")
 ```
@@
 
-### Statistics 
 ```{r}
@@
 
-hall
+```
+
+### Some statistics
+On missingness (# and %) and duplicates (# and %):
+
+```{r, echo = FALSE}
+drops["hall",]%>% knitr::kable(format = "markdown")
+```
+
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+hall %>% knitr::kable(format = "markdown")
 ```
@@
 virus["test",] <- data_descr(v_test)
+```
+
+### Some statistics
+On missingness (# and %) and duplicates (# and %):
+
+```{r, echo = FALSE}
+drops["virus",]%>% knitr::kable(format = "markdown")
+```
+
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+virus %>% knitr::kable(format = "markdown")
 ```
@@
 
-Statistics
-```{r}
-drops["wilson",]
+### Some statistics
+On missingness (# and %) and duplicates (# and %):
 
-wilson
+```{r, echo = FALSE}
+drops["wilson",]%>% knitr::kable(format = "markdown")
+```
+
+On total number of publications, abstract inclusions (this information was not available for this dataset) and final inclusions. 
+```{r, echo = FALSE}
+wilson %>% knitr::kable(format = "markdown")
 ```
@@
 saveRDS(all, file = "data_statistics/all.RDS")
-
 saveRDS(drops, file = "data_statistics/drops.RDS")
@@
   t() %>% 
-  kable("markdown") 
+  kable("markdown", digits = 2) 
 # %>%
@@
         digits = 2)
-# %>%
-#   kable_styling(full_width = TRUE)
 
@@
 ```
+# refrences

### 2020-05-14 datasets/readme.Rmd
knit readme

@@
 On missingness (# and %) and duplicates (# and %): 
-```{r, echo = false}
+```{r, echo = FALSE}
 # missingness and duplicates in raw data on ASReview

### 2020-05-14 datasets/readme.Rmd
readme update

@@
 
-## software dataset
+## Software dataset
 ```{r}
@@
 # Statistics
-All candidate papers, paper selected for full text screening, papers included in final review and inclusion rate, over various versions of the dataset.  
-```{r, echo = FALSE}
+All candidate papers, paper selected for full text screening, papers included in final review and inclusion rate, for the test datasets. 
+```{r, echo = FALSE, eval = TRUE, warning = FALSE}
 tibble(Dataset = names(all), 
        # paper 
-       `candidates_paper` = nostudies(all, "paper", "search"), 
-       `fulltext_paper` = nostudies(all, "paper", "ftext"),
-       `incl_paper` = nostudies(all, "paper", "incl"),
-       `inclrate_paper` = inclrate(all, "paper"),
-
-       # raw data 
-       `candidates_raw` = nostudies(all, "raw", "search"), 
-       `fulltext_raw` = nostudies(all, "raw", "ftext"),
-       `incl_raw` = nostudies(all, "raw", "incl"),
-       `inclrate_raw` = inclrate(all, "raw"),
-
-       # asreview repository 
-       `candidates_asr` = nostudies(all, "asreview", "search"), 
-       `fulltext_asr` = nostudies(all, "asreview", "ftext"),
-       `incl_asr` = nostudies(all, "asreview", "incl"),
-       `inclrate_asr` = inclrate(all, "asreview"),
-
+       # `candidates_paper` = nostudies(all, "paper", "search"), 
+       # `fulltext_paper` = nostudies(all, "paper", "ftext"),
+       # `incl_paper` = nostudies(all, "paper", "incl"),
+       # `inclrate_paper` = inclrate(all, "paper"),
+       # 
+       # # raw data 
+       # `candidates_raw` = nostudies(all, "raw", "search"), 
+       # `fulltext_raw` = nostudies(all, "raw", "ftext"),
+       # `incl_raw` = nostudies(all, "raw", "incl"),
+       # `inclrate_raw` = inclrate(all, "raw"),
+       # 
+       # # asreview repository 
+       # `candidates_asr` = nostudies(all, "asreview", "search"), 
+       # `fulltext_asr` = nostudies(all, "asreview", "ftext"),
+       # `incl_asr` = nostudies(all, "asreview", "incl"),
+       # `inclrate_asr` = inclrate(all, "asreview"),
+       # 
        # test set 
@@
 
-Descriptives on missingness and duplicate abstracts in the ASReview test data set. 
+Descriptives on missingness and duplicate abstracts in the raw datasets: 
 ```{r, echo = FALSE}
@@
 
-To check:
-```{bash , eval = FALSE}
-asreview stat test_datasets/*
-```
-
-returns 
-```
-************  ace.csv  ************
-
-Number of papers:            2235
-Number of inclusions:        41 (1.83%)
-Number of exclusions:        2194 (98.17%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        123
-Average abstract length:     1623
-Average number of keywords:  15.0
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-************  nudging.csv  ************
-
-Number of papers:            1847
-Number of inclusions:        100 (5.41%)
-Number of exclusions:        1747 (94.59%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        109
-Average abstract length:     1831
-Average number of keywords:  None
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-************  ptsd.csv  ************
-
-Number of papers:            5031
-Number of inclusions:        38 (0.76%)
-Number of exclusions:        4993 (99.24%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        104
-Average abstract length:     1537
-Average number of keywords:  9.9
-Number of missing titles:    1 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-************  software.csv  ************
-
-Number of papers:            8896
-Number of inclusions:        104 (1.17%)
-Number of exclusions:        8792 (98.83%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        81
-Average abstract length:     896
-Average number of keywords:  None
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-************  virus.csv  ************
-
-Number of papers:            2304
-Number of inclusions:        114 (4.95%)
-Number of exclusions:        2190 (95.05%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        103
-Average abstract length:     1345
-Average number of keywords:  20.3
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-************  wilson.csv  ************
-
-Number of papers:            2333
-Number of inclusions:        23 (0.99%)
-Number of exclusions:        2310 (99.01%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        83
-Average abstract length:     1325
-Average number of keywords:  31.3
-Number of missing titles:    1 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-
-```
-# refrences
+# References

### 2020-05-14 results/README.Rmd
readme update

@@
 - `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
-- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
+- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
 - `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
@@
 - `output` contains the abovementioned tables, stored as .RDS files.
+
+# Requirements
+Extracing data from the simulation output requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020].
+All these requirements are listed in the `requirements.txt` file.
+If you've already installed this file in the `simulation_study` step, please skip this.
+If not, you can run the following in your terminal to install all requirements:
+```{bash, eval = FALSE}
+pip install -r ../simulation_study/requirements.txt
+```
+
+Additionally, to create the plots and statistics in the manuscript you will need to install a specific branch of the asreview visualization package. Run the following in your terminal: 
+```{bash, eval = FALSE}
+# clone visualization package from GitHub
+git clone https://github.com/GerbrichFerdinands/asreview-thesis-visualization.git
+```
+
+And then, within the newly created directory, the following:
+
+```{bash, eval = FALSE}
+# install visualization package 
+pip install . 
+```
 

### 2020-05-14 simulation_study/README.Rmd
readme update

@@
     variant: markdown_github
+bibliography: ../manuscript/manuscript/asreview.bib
 ---
 
-The log of the simulation study.
-
-- hpoptimization. 
-  - Sripts for hyperparameter optimization
-  - 
-- simulation 
-  - scripts for simulation studies
+This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.
 
@@
 
+# Models 
+We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
 ```{r, eval = FALSE}
 #  
-source("R/00_condition_grid.R")
-source("R/01_hyperparameter_sets.R")
+# source("R/00_condition_grid.R")
+# source("R/01_hyperparameter_sets.R")
+
+conditiongrid <- readRDS("R/00_conditiongrid.RDS")
+
+conditiongrid[c(1:4, 7:9),] %>%
+  mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
+  mutate(Abbreviation = condition) %>%
+  select(Model, Abbreviation)
+  kable(format = "markdown")
 ```
+The first letter denotes the classification strategy, NB, LR, RF, or SVM.
+The second letter stands for C of certainty sampling.
+The third letter denotes the feature extraction strategy, TF-IDF or Doc2vec.
+The fourth letter stands for D of Dynamic Resampling.
 
-## Hyperparameter optimization
-There are three stages, we start with the first 5 where we are comparing different classifiers.
-
-```{r}
-conditiongrid <- readRDS("R/00_conditiongrid.RDS")
-conditiongrid %>%
-  kable(format = "markdown")
+# Requirements 
+This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
+All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following to install all requirements: 
+```{bash, eval = FALSE}
+pip install -r requirements.txt
 ```
@@
 Personal device: macos catalina 10.15.2
-
 Cartesius supercomputer 
-asreview 0.7.2
 asreview simulation branch reorganization.
 
------
-
-# Stage 1 - Classifiers 
-Comparing five different classifiers
-```{r}
-emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
-todo <- emptytodo
-```
-
-R - 275 secs 119% - 5 datasets 
-```{r}
-275 / 5 * 1000 / 60 # 916 minutes
-```
-
-## 1.1 Optimizing (hyper)parameters per model, per dataset (1-1)
-```{r}
-lubridate::date("2020-03-17")
-# i am working on svm model for all datasets 
-todo <- busy(todo, "SCTW", "one", "ace")
-```
-
-Optimization run on Cartesius
-```{bash, eval = FALSE}
-# BCTW
-# RCTW
-# SCTW 
-./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
-# LCTW
-# NCTW
-```
-
-***
-
-```{r}
-lubridate::date("2020-03-18")
-todo <- check(todo, "BCTW", "one", datasets)
-todo <- check(todo, "SCTW", "one", "ace")
-```
-
-Store config files from job 7768402, SCTW model.
-
-```{bash, eval = FALSE}
-asreview create-config output/active/svm_max_double_tfidf/ace/trials.pkl -o config/SCTW_ace.ini
-```
-
-Transfer config files to my computer home directory 
-```{bash, eval = FALSE}
-# in own device. 
-scp gerbrich@cartesius.surfsara.nl:asreview/config/SCTW_ace.ini ~
-```
-
-```{bash, eval = FALSE}
-# BCTW
-./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ace -r 23 # 7772446
-./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d nudging -r 23 # 7772450
-./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ptsd -r 23 # 7772452
-./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d software -r 23 # 7772454
-./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d wilson -r 23 # 7772456
-# extract all trials.pkl files 
-scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ace/trials.pkl ~/hyperopt/trials/BCTW_ace.pkl 
-scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/nudging/trials.pkl ~/hyperopt/trials/BCTW_nudging.pkl 
-scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ptsd/trials.pkl ~/hyperopt/trials/BCTW_ptsd.pkl
-scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/software/trials.pkl ~/hyperopt/trials/BCTW_software.pkl 
-scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/wilson/trials.pkl ~/hyperopt/trials/BCTW_wilson.pkl 
-# create config files
-asreview create-config trials/BCTW_ace.pkl -o config/BCTW_ace.ini
-asreview create-config trials/BCTW_nudging.pkl -o config/BCTW_nudging.ini
-asreview create-config trials/BCTW_ptsd.pkl -o config/BCTW_ptsd.ini
-asreview create-config trials/BCTW_software.pkl -o config/BCTW_software.ini
-asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini
-# RCTW
-# SCTW 
-# LCTW
-# NCTW
-```
-
-***
-
-```{r}
-lubridate::date("2020-03-19")
-#todo <- check(todo, "BCTW", "one", datasets)
-```
-
-### simulations with nb 
-```{bash, eval = FALSE}
-# create config files within cartesius (scripts folder)
-asreview create-config output/active/nb_max_double_tfidf/ace/trials.pkl -o config/BCTW_ace.ini
-asreview create-config output/active/nb_max_double_tfidf/nudging/trials.pkl  -o config/BCTW_nudging.ini
-asreview create-config output/active/nb_max_double_tfidf/ptsd/trials.pkl  -o config/BCTW_ptsd.ini
-asreview create-config output/active/nb_max_double_tfidf/software/trials.pkl  -o config/BCTW_software.ini
-asreview create-config output/active/nb_max_double_tfidf/wilson/trials.pkl  -o config/BCTW_wilson.ini
-```
-
-```{bash, eval = FALSE}
-# run simulations within cartesius
-./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23 
-./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23 
-./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23 
-./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23 
-./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
-```
-
-### extract simulation results nb 
-```{bash, eval = FALSE}
-# transfer files to device 
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
-scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
-```
-
-```{bash, eval = FALSE}
-# on own device
-asreview plot asreview-thesis/simulation_output
-```
-
-***
-```{r}
-lubridate::date("2020-03-22")
-todo <- busy(todo, "SCTW", "one", datasets[2:5])
-todo <- busy(todo, c("LCTW", "RCTW", "NCDW"), "one", "ace")
-todo <- not(todo, "NCTW", "one", datasets)
-# do the remaining datasets of svm, and one test run for L and one for R. 
-```
-
-Sent hyperparameters for optimization
-```{bash, eval = FALSE}
-# SCTW
-./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d nudging -r 23 # 7805983
-./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ptsd -r 23 # 7805984
-./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d software -r 23 # 7805985
-./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986
-# LCTW 
-./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987
-# RCTW 
-./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989
-# NCTW does not work well with tfidf, save for second round with doc2vec: 
-# NCDW
-./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021
-```
-
-***
-```{r}
-lubridate::date("2020-03-23")
-todo <- check(todo, "SCTW", "one", datasets[3:5])
-```
-
-Checkout hyperopt SCTW
-Nudging dataset doesn't optimize well? 
-```{r}
-todo <- huh(todo, "SCTW", "one", "nudging")
-todo <- check(todo, "SCTW", "one", "nudging")
-```
-
-### Checkout results first hyperopt 
-LCTW - no output? 
-RCTW - only 'current'
-```{r}
-todo <- huh(todo, c("LCTW", "RCTW"), "one", "ace")
-```
-
-```{bash, eval = FALSE}
-# LCTW 
-# made a mistake in command, "logistic" instead of "lr", run again 
-./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
-# evaluated run, now other datasets
-./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
-./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
-./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
-./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
-./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157
-# RCTW, fixed a parameter bug in simulation package. 
-./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
-# evaluated run, now other datasets
-./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
-./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
-./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
-./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
-./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
-```
-
-```{r}
-todo <- busy(todo, c("LCTW", "RCTW"), "one", datasets)
-```
-
-NCDW - loss still going down, sent in for another 12 hours. 
-```{bash, eval = FALSE}
-# NCDW
-./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
-# error 
-# accidentally got killed while downgrading tensorflow at the same time. 
-# run again, 7815147
-# NCDW for remaining datasets 
-```
-
-Resimulate BCTW models.
- - create-config file from trials.pkl: n_instances 20, 1/1
- - how to overrule this parameters? (not possible through cli)
-
-```{bash, eval = FALSE}
-./cart_simulate.py data/ace.csv --config_file config/one/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 # 7814382
-./cart_simulate.py data/nudging.csv --config_file config/one/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 # 7814384
-./cart_simulate.py data/ptsd.csv --config_file config/one/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 # 7814391
-./cart_simulate.py data/software.csv --config_file config/one/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 # 7814392 
-./cart_simulate.py data/wilson.csv --config_file config/one/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 # 7814395
-```
-
-Optimize BCTW model 6 datasets (for paper)
-```{bash, eval = FALSE}
-./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
-./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
-# create config file (BMTW (M=mixed)) 
-asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
-# move config to device
-scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/
-# run simulations (on own device)
-# see script
-```
-
-***
-
-```{r}
-lubridate::date("2020-03-27")
-# todo <- busy(todo, "SCTW", "one", datasets[2:5])
-```
-
-Process BCTW models simulations into table
- - python script to extract statistics
-
-Create checklist table for simulations
-
-Checkout what happened with NCDW and other errors in hpcbatch 
-```{bash, eval = FALSE}
-# retest with hall dataset 
-./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d hall -r 23 # 7843185
-```
-
-Simulate SCTW models
-
-Process SCTW models into table
-
-Simulate LCTW, RCTW and NCTW models 
-   - create config files
-   - run simulation
-
-Create a nice plot
-
-Send first version of table
-
-Move all hyperopt results to harddrive
-
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active /Volumes/Gerbrich/asreview/archive/output
-
-scp -r gerbrich@cartesius.surfsara.nl:/output/active/nb_max_random_triple_tfidf ~
-
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf ~
-
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/best ~
-***
-
-```{r}
-# save the to-do grid in markdown style
-todo[todo==0] <- emo::ji("white square button")
-todo %>% kable(format = "markdown")
-saveRDS(todo %>% kable(format = "markdown"), 
-        file = "02_todo_hp.RDS")
-```
-
-## Stage 2 - Feature extraction 
-Comparing tfidf with doc2vec
-
-## Stage 3 - Balance strategy
-Redo all the analyses with a different balance strategy (aggressive undersampling?)
-Probably won't have time for this.
-
-# The data 
-On 17 march 2020:
-
-```
-************  ace.csv  ************
-Number of papers:            2235
-Number of inclusions:        41 (1.83%)
-Number of exclusions:        2194 (98.17%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        123
-Average abstract length:     1623
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-************  nudging.csv  ************
-Number of papers:            1847
-Number of inclusions:        100 (5.41%)
-Number of exclusions:        1747 (94.59%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        109
-Average abstract length:     1831
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-************  ptsd.csv  ************
-Number of papers:            5031
-Number of inclusions:        38 (0.76%)
-Number of exclusions:        4993 (99.24%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        104
-Average abstract length:     1537
-Number of missing titles:    1 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-************  software.csv  ************
-Number of papers:            8896
-Number of inclusions:        104 (1.17%)
-Number of exclusions:        8792 (98.83%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        81
-Average abstract length:     896
-Number of missing titles:    0 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-************  wilson.csv  ************
-Number of papers:            2333
-Number of inclusions:        23 (0.99%)
-Number of exclusions:        2310 (99.01%)
-Number of unlabeled:         0 (0.00%)
-Average title length:        83
-Average abstract length:     1325
-Number of missing titles:    1 (of which 0 included)
-Number of missing abstracts: 0 (of which 0 included)
-```
+# References

### 2020-05-14 results/README.Rmd
update readmes

@@
 - `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
-- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
-- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
-- `output` contains the abovementioned tables, stored as .RDS files.
+- `one_seed`, containing all plots and `.json` statistics files produced by the two jupyter notebooks above.
+The plots are used in the manuscript, the data are further processed by this readme into tables before they are manuscript-ready.
+- `README.Rmd` containing R-code to transform the `.json` files into readable tables for the manuscript.
+- `output` contains the abovementioned tables, stored as `.RDS` files.
 
@@
 If not, you can run the following in your terminal to install all requirements:
+
 ```{bash, eval = FALSE}
@@
 Additionally, to create the plots and statistics in the manuscript you will need to install a specific branch of the asreview visualization package. Run the following in your terminal:
+
 ```{bash, eval = FALSE}
@@
   # names of the files are the data
-  names(files) <- str_split(files, "/", simplify = TRUE)[,9]
+  names(files) <- str_split(files, "/", simplify = TRUE)[,4]
 

### 2020-05-14 simulation_study/README.Rmd
update readmes

@@
 ---
-title: "log"
-output:   
-  md_document:
-    variant: markdown_github
+title: "Simulation study scripts"
+output: github_document
 bibliography: ../manuscript/manuscript/asreview.bib
@@
 
-This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.
+This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews. The output
 
@@
 This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
-All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following to install all requirements: 
+All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following in your bash terminal to install all requirements:
+
 ```{bash, eval = FALSE}
 pip install -r requirements.txt
+```
+
+This automatically installs asreview version 0.9.3 and several dependencies.
+Moreover, a specific branch of the asreview simulation extension should be installed.
+Run the following in your bash terminal:
+```{bash, eval = FALSE}
+git clone https://github.com/GerbrichFerdinands/asreview-thesis-simulation.git
+```
+
+And then, within the newly created directory, the following:
+```{bash, eval = FALSE}
+# install visualization package 
+pip install . 
 ```

### 2020-05-14 simulation_study/README.Rmd
update

@@
 
-This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews. The output
+This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.
 
@@
 source("R/functions.R")
-knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 
+For every model, first the hyperparameters were optimized.
+The scripts and results for that can be found in the `hpoptimization` directory.
+The `simulation` directory contains scripts for simulating an automated systematic review, using the hyperparameters obtained in the optimization.
+
 # Requirements 
@@
 
-### Version information
-Personal device: macos catalina 10.15.2
-Cartesius supercomputer 
-asreview simulation branch reorganization.
-
 # References

### 2020-05-14 simulation_study/hpoptimization/README.Rmd
update

@@
 The hyperparameter sets that were found to lead to a minimum loss value were visually inspected.
+
+The __one__ hyperparameters are used in the simulations of the current thesis.
+The remaining sets of hyperparameters will be used in a future project.
+The `config` folder contains stores all sets of hyperparameters.
+
+## Content
+The `scripts` folder contains all scripts run on the Cartesius supercomputer.
+The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
+
+The `trials` folder transforms the hyperparameter output
+
+The `config` folder contains all sets of optimal hyperparameters.
+
+The current readme file preprocesses the optimal hyperparameters into an `.RDS` file for a visual inspection of the hyperparameters given below.
+
+If you have no access to Cartesius you can run optimization trials on your own device by running the following type of commands:
+
+```{bash, eval = FALSE}
+
+```
 

### 2020-05-14 simulation_study/simulation/README.Rmd
update

--- 2020-04-25 simulation_study/simulation/README.Rmd
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
+This directory contains all scripts used to simulate systematic reviews. 
+Note that the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub.
+Instead, those files are published on the Open Science Framework, divided over 2 ..
 
-createLines <- function(cond, d, hp, seed = FALSE){
-  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
-  files <- data.frame(c = condition, 
-                    f = c("nb_max_double_tfidf",
-                    "rf_max_double_tfidf",
-                    "svm_max_double_tfidf",
-                    "logistic_max_double_tfidf",
-                    "nn-2-layer_max_double_tfidf",
-                    "nb_max_double_doc2vec",
-                    "rf_max_double_doc2vec",
-                    "svm_max_double_doc2vec",
-                    "logistic_max_double_doc2vec",
-                    "nn-2-layer_max_double_doc2vec"))
+- `scripts` -  contains all scripts run on the Cartesius supercomputer.
+The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
+- `config` - contains the hyperparameters for every model-dataset combination. These files are called upon in the simulation command.
 
-  # create condition grid
-  cons <- expand.grid(d = d, hp = hp, c = cond, stringsAsFactors = FALSE)
-  cons <- left_join(cons, files)
+If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging run the following in your bash terminal:
 
-  # write 
-  script <- sprintf(comm, 
-        # input data
-        cons$d, 
-        # config file details
-        cons$hp, cons$c, cons$f, cons$d,
-        # output file details
-        cons$hp, cons$c, cons$d)
-
-  if(seed){
-    script <- paste0(script, " --init_seed 42")
-  }
-return(script)
-}
-transfer <- function(hp, c, seed = FALSE){
-    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)
-
-    if(seed){
-      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s_seed/%s"
-    } else {
-      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"
-    }
-    result <- sprintf(txt, hp, c, hp, c)
-    return(result)
-}
+```{bash, eval = FALSE}
 
@@
 
-```{r, include=FALSE}
-sims <- readRDS("../R/01_hyperparameter_sets.RDS")
-d <- colnames(sims)
-condition <- rownames(sims)
-classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
-names(classifier) <- c("B", "R", "S", "L", "N")
-```
-
-# create config files 
-#### 01.04.2020
-```{bash, eval = FALSE}
-# get config files from surfsara to hard drive 
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
-```
-
-Manually update config files to simulation 
-Push finished ones to GH repository
-Fetch github repo on surfsara
-
-ASReview version 0.8.1
-
-```{r}
-sims[condition[c(1,2,4)], d, "one"] <- 1 # simulation configs are up
-```
-
-# Run simulations
-
-## hp = one
-
-#### BCTD
-```{r}
-bctd <- createLines(condition[1], d=d, hp = "one")
-write.table(bctd, file = "scripts/one/bctd.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(bctd) <- c("7883184", "7883202", "7883207", "7883209", "7883213", "7883214")
-```
-
-#### RCTD, LCTD
-```{r}
-rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
-write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-#one_rctd_virus etc 
-names(rctd_lctd) <- c(rep("0", 6), "7949940", "7949952", "7949953", "7949954", "7949956", "7949959")
-```
-
-```{r}
-sims[condition[c(1,2,4)], d, "one"] <- 2 # simulations are running 
-```
-
-# transfer simulation files to harddrive
-
-```{bash, eval = FALSE}
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
-
-./cart_simulate.py simdata/wilson.csv --config_file simconfig/one/LCTD/logistic_max_double_tfidf-wilson.ini --state_file simoutput/one/LCTD/wilson/results.h5 -r 15
-```
-
-```{r}
-transfer("one", condition[c(1,2,4)])
-```
-
-```{r}
-# output is on harddrive
-sims[condition[1], , "one"] <- 3
-```
-
-#### 02.04.2020
-get config files 'all' BCTD, LCTD.
-
-scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
-
-```{r}
-# output is on harddrive
-sims[condition[2], , "one"] <- 3
-```
-
-#### 03.04.2020
-SCDD model
-
-```{r}
-# get config files
-# manually transform
-# push to github 
-sims[condition[8], d, "one"] <- 1 # simulation configs are up
-
-# run simulations 
-scdd <- createLines(condition[8], d, "one")
-write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
-           row.names = FALSE)
- names(scdd) <- c("7950186", "7950187", "7950188", "7950189", "7950190", "7950191")
- sims[condition[8], d, "one"] <- 2 # simulations are running 
-```
-
-```{r}
- sctd <- createLines(condition[3], d, "one")
- write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(sctd) <- c("7950483", "7950484", "7950485", "7950487", "7950489", "7950490")
-sims[condition[3], d, "one"] <- 2 # simulations are running
-```
-
-```{r}
-rcdd <- createLines(condition[7], d, "one")
-write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
-            row.names = FALSE)
-names(rcdd) <- c("7950491", "7950493", "7950495", "7950496", "7950497", "7950499")
-sims[condition[7], d, "one"] <- 2 # simulations are running
-```
-
-```{r}
-lcdd <- createLines(condition[9], d, "one")
-write.table(lcdd, file = "scripts/one/lcdd.txt", sep = "\t", quote = FALSE, row.names = FALSE)
-names(lcdd) <- c("7965136", "7965141", "7965143", "7965145", "7965146", "7965147")
-sims[condition[9], d, "one"] <- 2 # simulations are running
-```
-
-10.04.2020
-
-```{r}
-# LCTD and SCDD both failedsimulations both failed? 
-# ran again 
-# transfer to harddrive
-transfer("one", condition[c(4,7:9)])
-
-# sctd is not finished yet! 
-sims[condition[4],,"one"] <- 3 # output is on harddrive
-
-# sims[condition[7],,"one"] <- 3 # output is on harddrive 
-# sims[condition[8],,"one"] <- 3 # output is on harddrive 
-# too little space for 9, so run again
-
-sims[condition[9],,"one"] <- 3 # output is on harddrive 
-# but ace wasn't finished yet! 
-```
-
-Repeat all failed simulations
-
-```{r}
-# run again 
-# transfer to harddrive 
-transfer("one", condition[8])
-```
-
-15.04.2020 
-```{r}
-transfer("one", condition[3]) # SCTD 
-sims[condition[8], , "one"] <- 3 # output is on harddrive
-
-# BCTD run ace dataset again 
-createLines(condition[1], "ace", "one") # 8018165
-#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/BCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/BCTD
-sims[condition[1], "ace", "one"] <- 3 # output is on harddrive
-
-# RCDD needs to go all over again
-names(rcdd) <- c("8018262", "8018263", "8018264", "8018265", "8018267", "8018268")
-transfer("one", "RCDD")
-
-# SCDD need ace ptsd software virus again
-# ace 8019246
-# ptsd 8019247
-# software 8019250
-# virus 8019251
-transfer("one", "SCDD")
-
-# LCDD only ace 
-createLines(condition[9], "ace", "one") # 8019423
-#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCDD/ace /Volumes/Gerbrich/asreview/simoutput/one/LCDD
-
-# LCTD
-# software 
-createLines("LCTD", "software", "one") # 8020733
-# scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCTD/software /Volumes/Gerbrich/asreview/simoutput/one/LCTD
-
-# SCTD 
-# ace ptsd software
-sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
-names(sctd) <- c("8025808", "8025809", "8025810")
-#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
-createLines("SCTD", "ptsd", "one") # 8066095
-createLines("SCTD", "software", "one")
-```
-
----
-
-23.04.2020
-Simulations for ace dataset again but now with seed. 
-```{r, message = FALSE}
-seed_ace <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ace", "one", seed = TRUE) %>%
-  noquote()
-names(seed_ace) <- c(".", "8119459", "8119460", "8119461", "8119462", "8119463", "8119464")
-
-seed_nudging <- createLines(condition[c(1, 2, 3,4,7,8,9)], "nudging", "one", seed = TRUE) %>%
-  noquote()
-names(seed_nudging) <- c("8119472", "8119472", "8121720", "8121721", "8121722", "8121723", "8121725")
-
-# transfer sctd's later!(3)
-noquote(transfer("one", condition[c(1, 2,4,7,8,9)], seed = TRUE))
-# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD
-
-```
-
-```{r template, eval = FALSE}
-# get config files
-# manually transform
-# push to github 
-sims[condition[1], d, "one"] <- 1 # simulation configs are up
-# run simulations 
-createLines()
-sims[condition[1], d, "one"] <- 2 # simulations are running 
-# transfer to harddrive 
-transfer()
-sims[condition[1], , "one"] <- 3 # output is on harddrive
-```
+The simulation will output one or more `.h5` files (depending on the number of trials you choose).
+Please refer to the `results` folder in the root directory of this repository for a demonstration of how to analyze the resulting files.

### 2020-05-14 simulation_study/simulation/log.Rmd
update

---
title: "Simulations log"
author: "Gerbrich Ferdinands"
date: "5/14/2020"
output: github_document
---
This notebook contains all simulations run on the Cartesius supercomputer.

# Run simulations

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

createLines <- function(cond, d, hp, seed = FALSE){
  comm <- "./cart_simulate.py simdata/%s.csv --config_file simconfig/%s/%s/%s-%s.ini --state_file simoutput/%s/%s/%s/results.h5 -r 15"
  files <- data.frame(c = condition, 
                    f = c("nb_max_double_tfidf",
                    "rf_max_double_tfidf",
                    "svm_max_double_tfidf",
                    "logistic_max_double_tfidf",
                    "nn-2-layer_max_double_tfidf",
                    "nb_max_double_doc2vec",
                    "rf_max_double_doc2vec",
                    "svm_max_double_doc2vec",
                    "logistic_max_double_doc2vec",
                    "nn-2-layer_max_double_doc2vec"))

  # create condition grid
  cons <- expand.grid(d = d, hp = hp, c = cond, stringsAsFactors = FALSE)
  cons <- left_join(cons, files)

  # write 
  script <- sprintf(comm, 
        # input data
        cons$d, 
        # config file details
        cons$hp, cons$c, cons$f, cons$d,
        # output file details
        cons$hp, cons$c, cons$d)

  if(seed){
    script <- paste0(script, " --init_seed 42")
  }
return(script)
}
transfer <- function(hp, c, seed = FALSE){
    cons <- expand.grid(hp = hp, c = c, stringsAsFactors = FALSE)

    if(seed){
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s_seed/%s"
    } else {
      txt <- "scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/%s/%s /Volumes/Gerbrich/asreview/simoutput/%s/%s"
    }
    result <- sprintf(txt, hp, c, hp, c)
    return(result)
}

```

```{r, include=FALSE}
sims <- readRDS("../R/01_hyperparameter_sets.RDS")
d <- colnames(sims)
condition <- rownames(sims)
classifier <- c("nb", "rf", "svm", "logistic", "nn-2-layer")
names(classifier) <- c("B", "R", "S", "L", "N")
```

# create config files 
#### 01.04.2020
```{bash, eval = FALSE}
# get config files from surfsara to hard drive 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
```

Manually update config files to simulation 
Push finished ones to GH repository
Fetch github repo on surfsara

ASReview version 0.8.1

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 1 # simulation configs are up
```

## hp = one

#### BCTD
```{r}
bctd <- createLines(condition[1], d=d, hp = "one")
write.table(bctd, file = "scripts/one/bctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(bctd) <- c("7883184", "7883202", "7883207", "7883209", "7883213", "7883214")
```

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c(rep("0", 6), "7949940", "7949952", "7949953", "7949954", "7949956", "7949959")
```

```{r}
sims[condition[c(1,2,4)], d, "one"] <- 2 # simulations are running 
```

# transfer simulation files to harddrive

```{bash, eval = FALSE}
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

./cart_simulate.py simdata/wilson.csv --config_file simconfig/one/LCTD/logistic_max_double_tfidf-wilson.ini --state_file simoutput/one/LCTD/wilson/results.h5 -r 15
```

```{r}
transfer("one", condition[c(1,2,4)])
```

```{r}
# output is on harddrive
sims[condition[1], , "one"] <- 3
```

#### 02.04.2020
get config files 'all' BCTD, LCTD.

scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output

```{r}
# output is on harddrive
sims[condition[2], , "one"] <- 3
```

#### 03.04.2020
SCDD model

```{r}
# get config files
# manually transform
# push to github 
sims[condition[8], d, "one"] <- 1 # simulation configs are up

# run simulations 
scdd <- createLines(condition[8], d, "one")
write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
           row.names = FALSE)
 names(scdd) <- c("7950186", "7950187", "7950188", "7950189", "7950190", "7950191")
 sims[condition[8], d, "one"] <- 2 # simulations are running 
```

```{r}
 sctd <- createLines(condition[3], d, "one")
 write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(sctd) <- c("7950483", "7950484", "7950485", "7950487", "7950489", "7950490")
sims[condition[3], d, "one"] <- 2 # simulations are running
```

```{r}
rcdd <- createLines(condition[7], d, "one")
write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(rcdd) <- c("7950491", "7950493", "7950495", "7950496", "7950497", "7950499")
sims[condition[7], d, "one"] <- 2 # simulations are running
```

```{r}
lcdd <- createLines(condition[9], d, "one")
write.table(lcdd, file = "scripts/one/lcdd.txt", sep = "\t", quote = FALSE, row.names = FALSE)
names(lcdd) <- c("7965136", "7965141", "7965143", "7965145", "7965146", "7965147")
sims[condition[9], d, "one"] <- 2 # simulations are running
```

10.04.2020

```{r}
# LCTD and SCDD both failedsimulations both failed? 
# ran again 
# transfer to harddrive
transfer("one", condition[c(4,7:9)])

# sctd is not finished yet! 
sims[condition[4],,"one"] <- 3 # output is on harddrive

# sims[condition[7],,"one"] <- 3 # output is on harddrive 
# sims[condition[8],,"one"] <- 3 # output is on harddrive 
# too little space for 9, so run again

sims[condition[9],,"one"] <- 3 # output is on harddrive 
# but ace wasn't finished yet! 
```

Repeat all failed simulations

```{r}
# run again 
# transfer to harddrive 
transfer("one", condition[8])
```

15.04.2020 
```{r}
transfer("one", condition[3]) # SCTD 
sims[condition[8], , "one"] <- 3 # output is on harddrive

# BCTD run ace dataset again 
createLines(condition[1], "ace", "one") # 8018165
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/BCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/BCTD
sims[condition[1], "ace", "one"] <- 3 # output is on harddrive

# RCDD needs to go all over again
names(rcdd) <- c("8018262", "8018263", "8018264", "8018265", "8018267", "8018268")
transfer("one", "RCDD")

# SCDD need ace ptsd software virus again
# ace 8019246
# ptsd 8019247
# software 8019250
# virus 8019251
transfer("one", "SCDD")

# LCDD only ace 
createLines(condition[9], "ace", "one") # 8019423
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCDD/ace /Volumes/Gerbrich/asreview/simoutput/one/LCDD

# LCTD
# software 
createLines("LCTD", "software", "one") # 8020733
# scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/LCTD/software /Volumes/Gerbrich/asreview/simoutput/one/LCTD

# SCTD 
# ace ptsd software
sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
names(sctd) <- c("8025808", "8025809", "8025810")
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
createLines("SCTD", "ptsd", "one") # 8066095
createLines("SCTD", "software", "one")
```

---

23.04.2020
Simulations for ace dataset again but now with seed. 
```{r, message = FALSE}
seed_ace <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ace", "one", seed = TRUE) %>%
  noquote()
names(seed_ace) <- c(".", "8119459", "8119460", "8119461", "8119462", "8119463", "8119464")

seed_nudging <- createLines(condition[c(1, 2, 3,4,7,8,9)], "nudging", "one", seed = TRUE) %>%
  noquote()
names(seed_nudging) <- c("8119472", "8119472", "8121720", "8121721", "8121722", "8121723", "8121725")

# transfer sctd's later!(3)
noquote(transfer("one", condition[c(1,2,3,4,7,8,9)], seed = TRUE))
# ace: scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one_seed/SCTD

```

```{r}
seed_virus <- createLines(condition[c(1, 2, 3,4,7,8,9)], "virus", "one", seed = TRUE) %>%
  noquote()
names(seed_virus) <- c("8125572", "8125573", "8125574", "8125575", "8125581", "8125582", "8125583")

seed_wilson <- createLines(condition[c(1, 2, 3,4,7,8,9)], "wilson", "one", seed = TRUE) %>%
  noquote()
names(seed_wilson) <- c("8125584", "8125585", "8125586", "8125587", "8125588", "8125589", "8125590")
```

```{r}
seed_ptsd <- createLines(condition[c(1, 2, 3,4,7,8,9)], "ptsd", "one", seed = TRUE) %>%
  noquote()

# sctd later

seed_software <- createLines(condition[c(1, 2, 3,4,7,8,9)], "software", "one", seed = TRUE) %>%
  noquote()
# sctd later
seed_software
names(seed_software) <- c("8129589", "8129732", "8129588", "8131305", "8133472", "8134718", "8149271")

# ptsd sctd
seed_ptsd # 8149296
```

```{r template, eval = FALSE}
# get config files
# manually transform
# push to github 
sims[condition[1], d, "one"] <- 1 # simulation configs are up
# run simulations 
createLines()
sims[condition[1], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[1], , "one"] <- 3 # output is on harddrive
```

### 2020-05-14 simulation_study/README.Rmd
update table sims

@@
 source("R/functions.R")
+#source("R/00_condition_grid.R")
 ```
@@
 We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
-```{r, eval = FALSE}
-#  
-# source("R/00_condition_grid.R")
-# source("R/01_hyperparameter_sets.R")
-
+```{r, eval = TRUE}
 conditiongrid <- readRDS("R/00_conditiongrid.RDS")
-
-conditiongrid[c(1:4, 7:9),] %>%
+conditiongrid <- conditiongrid[c(1:4,7:9),]
+conditiongrid %>%
   mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
   mutate(Abbreviation = condition) %>%
-  select(Model, Abbreviation)
+  select(Model, Abbreviation) %>%
   kable(format = "markdown")

### 2020-05-14 simulation_study/hpoptimization/README.Rmd
update table sims

--- 2020-04-24 simulation_study/hpoptimization/README.Rmd
@@
 ---
+# Hyperparameter Optimization 
+To every model belongs a unique set of hyperparameters.
+To maximize model performance, we need to find optimal values for the hyperparameters.
+For every model the optimal hyperparameter values are determined by optimizing on data $d$.
+The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space.
+
+Maximum model performance is defined as the average time it takes to find an inclusion in the data, ATD, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (the area above the curve in the inclusion plot).
+
+### Content
+The `scripts` folder contains all scripts run on the Cartesius supercomputer.
+The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
+
+The `trials` folder transforms the raw data into smaller datafiles, containing the results of the hyperparameter optimization.
+As mentioned in the readme of the root directory, the raw files cannot be published on the OSF yet, however these raw datafiles should yield enough information for the time being.
+
+The `config` folder contains configuration files containing all sets of optimal hyperparameters. This file format is necessary for running simulations later on.
+
+The current readme file analyzes the hyperparameter optimization process (stored in `trials`), and creates the visual inspection of the hyperparameters given below.
+
+`README_files` stores the figures displayed in the current readme.
+
+### Running optimization trials
+If you have no access to Cartesius, you can still run optimization trials on your own device.
+For example, for optimizing the NB + TF-IDF model on the ace dataset for 12 hours, run the following command in your bash terminal:
+
+```{bash, eval = FALSE}
+asreview hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d ace
+```
+
+This will create a file structure `output/active/nb_max_double_tfidf/ace`. To create a configuration file from your optimized trials, run:
+```{bash, eval = FALSE}
+asreview create-config output/active/nb_max_double_tfidf/ace/trials.pkl
+```
+
+For more information, check out https://github.com/asreview/asreview-hyperopt.
+
 # Optimizing Hyperparameters
@@
 
-To every model belongs a unique set of hyperparameters.
-To maximize model performance, we need to find optimal values for the hyperparameters.
-For every model the optimal hyperparameter values are determined by optimizing on data $d$.
-The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space.
-
-Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (eg the area above the curve in the inclusion plot).
-
 The optimization data d consists of (a subset from) the six systematic review datasets D mentioned above. Three different approaches in composing d are explored:
@@
 - __n__, where hyperparameters are optimized on all six data sets. This optimization approach intends to serve in producing the most optimal hyperparameters overall. 
-- __n-1__, where hyperparameters are optimized on all six datasets but one. Serving as a sensitivity analysis for the former condition, eg how sensitive are the hyperparamters to different data sets.
+- __n-1__, where hyperparameters are optimized on all six datasets but one.
+Serving as a sensitivity analysis for the former condition, e.g.
+how sensitive are the hyperparamters to different data sets.
 
@@
 The hyperparameter sets that were found to lead to a minimum loss value were visually inspected.
+
+The __one__ hyperparameters are used in the simulations of the current thesis.
+The remaining sets of hyperparameters will be used in a future project.
+The `config` folder contains stores all sets of hyperparameters.
 
@@
 
-## Results
-Loss plots: Two times the same data, first plot is over trials, second sorted from highest to lowest loss.
+<!-- ## Results -->
+<!-- Loss plots: Two times the same data, first plot is over trials, second sorted from highest to lowest loss. -->
 
-Hyperparameters on a continuous scale are plotted as dots in a scatterplot. 
-Discrete hyperparameters are displayed in a barplot
+<!-- Hyperparameters on a continuous scale are plotted as dots in a scatterplot.  -->
+<!-- Discrete hyperparameters are displayed in a barplot -->
 
-Conclusions: 
-- loss is going down over trials 
-- some datasets go down faster
-- some datasets go down more
+<!-- Conclusions:  -->
+<!-- - loss is going down over trials  -->
+<!-- - some datasets go down faster -->
+<!-- - some datasets go down more  -->
 

### 2020-05-14 simulation_study/hpoptimization/scripts/cart_hyper_run.py

@@ -1,0 +1,116 @@
+#!/usr/bin/env python
+import os
+import subprocess
+import sys
+import shlex
+
+from asreviewcontrib.hyperopt.job_utils import get_data_names
+
+
+BATCH_TEMPLATE = """\
+#!/bin/bash
+
+#SBATCH -t {time}
+#SBATCH --tasks-per-node {tasks_per_node}
+#SBATCH -p {node_type}
+#SBATCH -N {num_nodes}
+#SBATCH -J hyper_{hyper_name}
+#SBATCH --output={batch_dir}/lisa.out
+#SBATCH --error={batch_dir}/lisa.err
+
+module load eb
+
+cd {cur_dir}
+source ~/py-env/asreview/bin/activate
+
+srun asreview {args} --n_iter 10000 --mpi
+
+date
+
+"""
+
+
+def main(cli_args):
+    mode = cli_args[0]
+    if mode == "hyper-cluster":
+        from asreviewcontrib.hyperopt.cluster import _parse_arguments  # noqa
+    elif mode == "hyper-active":
+        from asreviewcontrib.hyperopt.active import _parse_arguments  # noqa
+    elif mode == "hyper-passive":
+        from asreviewcontrib.hyperopt.passive import _parse_arguments  #noqa
+    else:
+        print("Error: need one of the following modes: ['hyper-cluster',"
+              "'hyper-active', 'hyper-inactive']")
+        sys.exit(192)
+
+    parser = _parse_arguments()
+    parser.add_argument("-t", "--time",
+                        type=str, default="120:00:00",
+                        help="Maximum clock wall time for the optimization"
+                        " to run.")
+    args = vars(parser.parse_args(cli_args[1:]))
+    cur_dir = os.getcwd()
+    time = args.pop("time")
+
+    split_time = time.split(":")
+    if len(split_time) == 1:
+        minutes = int(time)
+    elif len(split_time) == 2:
+        minutes = int(split_time[0]) + int(split_time[1])/60
+    elif len(split_time) == 3:
+        double_split = split_time[0].split("-")
+        if len(double_split) == 2:
+            hours = int(double_split[0])*24
+            hours += int(double_split[1])
+        else:
+            hours = int(split_time[0])
+        minutes = 60*hours + int(split_time[1]) + int(split_time[2])/60
+
+    if minutes > 60:
+        node_type = "normal"
+    else:
+        node_type = "short"
+
[…]

### 2020-05-14 simulation_study/hpoptimization/trials/load_trials.R

@@ -1,7 +1,9 @@
 library(tidyverse)
 # load data from trials.csv files and process into dataframe
 
+# This is the storage location of the raw hyperparameter output onmy personal harddrive, the raw data will be published on the OSF when university buildings open again (see the readme file in the root directory).
 losspath <- "/Volumes/Gerbrich/asreview/output/active/"
+
 models <- list.files(losspath)
 # get rid of neural network 2-layer models s
 models <- models[c(-4, -5)]

### 2020-05-14 results/README.Rmd
update simulations

@@
 - `output` contains the abovementioned tables, stored as `.RDS` files.  
+- the `datastats.RDS` is used in the analyses to compute adjusted ATD values (see code below)
 
@@
 ```
+
+# Reproduce data extraction
+To reproduce the results, follow the steps below. If you do not want to download the raw simulation output, start at step 3:
+
+1.
+Run all code in the `extract_plots.ipynb` notebook to create all plots.
+This requires having the raw simulation data, to be found on the OSF (https://osf.io/7mr2g/ and https://osf.io/ag2xp/).
+Note that you will need to adjust the paths to where you've stored the simulation output on your local computer.
+Also, note that creating figures can take quite some time, depending on your computer.
+Mine took from 30 minutes to 5 hours per figure The final figures can be found in the `one_seed/plots` directory.
+2.
+Run all code in the `extract_results.ipynb` to extract the metrics WSS, RRF and ATD from the raw simulation data.
+Note that you will need to adjust the paths to where you've stored the simulation output on your local computer.
+Also, note that extracting all results will take quite some time, depending on your computer.
+Mine took 48 hours.
+The results are stored in the `one_seed/plots` directory.
+3. Follow the preprocessing steps in the `README.Rmd` files to create tables for in the manuscript, stored in the `output` directory.
 
@@
 }
+```
 
+The ATD values need to be adjusted for prior inclusions and exclusions as the computation does not take into account that prior to the active learning cycle, already 1 inclusion and 1 exclusion have been labelled 'for free'.
+```{r}
 # ATD needs to be adjusted for 1 prior inclusion and 1 prior exclusion! 

### 2020-05-14 simulation_study/README.Rmd
update simulations

@@
 ```
+# Content 
+This repository contains:
+
+- `hpoptimization` documentation on how hyperparameters were optimized plus the resulting parameters.
+- `simulation` documentation on how the models were simulated on the systematic review datasets. 
+- `R` containing R-scripts called upon in the current readme, to structure the whole simulation process.
+
+To reproduce the research, first follow the steps in `hpoptimization`, then those in `simulation`.
+If you wish to skip the hyperparameter optimization step, this is possible since the results of the hyperparameter optimization are available in this repository.
 
@@
 We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
-```{r, eval = TRUE}
+```{r, eval = TRUE, echo = FALSE}
 conditiongrid <- readRDS("R/00_conditiongrid.RDS")
@@
 ```{bash, eval = FALSE}
-# install visualization package 
 pip install . 

### 2020-05-14 simulation_study/simulation/README.Rmd
update simulations

@@
 ---
-title: "Simulations log"
+title: "Simulations"
 output: github_document
@@
 
-This directory contains all scripts used to simulate systematic reviews. 
-Note that the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub.
-Instead, those files are published on the Open Science Framework, divided over 2 ..
+This directory contains all scripts used to simulate systematic reviews:
 
+- `config` - contains the hyperparameters for every model-dataset combination.
+These files are called upon in the simulation command.
+They are copies from the config files in the `hpoptimization/config` directory, except that the `n_instances` parameter has been set to 1, so that the model is retrained after labelling one publication instead of 20.
 - `scripts` -  contains all scripts run on the Cartesius supercomputer.
 The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
-- `config` - contains the hyperparameters for every model-dataset combination. These files are called upon in the simulation command.
+- `simoutput` - where the output of the simulation files is stored.
+As mentioned in the readme in the root directory, the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub and the `simoutput` directory remains empty.
+Instead, the simulation output files are published on the Open Science Framework: https://osf.io/7mr2g/ and https://osf.io/ag2xp/.
 
-If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging run the following in your bash terminal:
+## Running a simulation
+All simulations were run with seed value `42`.
+If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging dataset, for 15 trials, run the following in your bash terminal:
 
 ```{bash, eval = FALSE}
-
+asreview batch ../../datasets/sim_datasets/nudging.csv --config_file config/one/BCTD/nb_max_double_tfidf-nudging.ini --state_file simoutput/one/BCTD/nudging/results.h5 -r 15 --init_seed 42
 ```
 
-The simulation will output one or more `.h5` files (depending on the number of trials you choose).
+The simulation will output 15 `.h5` files.
 Please refer to the `results` folder in the root directory of this repository for a demonstration of how to analyze the resulting files.
+Code for processing these files can be found in the `results` directory, which also contains already A processed version of the simulation output files is available in the `results` directory.

### 2020-05-14 simulation_study/simulation/log.Rmd
update simulations

@@
 ```
-
 ---

### 2020-05-14 manuscript/manuscript/manuscript.Rmd
update paths

@@
 
-<!-- Active learning for detecting relevant publications - evaluating models across systematic reviews from different research areas.  -->
-
-<!-- Evaluating active learning models across research contexts.  -->
-
-<!--  generalizability  -->
 <!-- --- -->
@@
 \linenumbers
-<!-- # Abstract -->
-<!-- #### Background  -->
-<!-- <!-- This study aims to contribute to this growing area of research by exploring  -->
-
-<!-- #### Methods -->
-<!-- <!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->
-
-<!-- #### Results -->
-<!-- #### Conclusions -->
-
-<!-- Besides time-consuming, the process of title and abstract screening is prone to human error [@Wang2020]. -->
-<!-- (14 to 77,910, trimmed mean 1,286).  -->
-<!-- Need to be screened by multiple researchers.  -->
-
 # Background
@@
 |    __RQ3__ Does the performance of active learning models differ across systematic reviews from different research areas?
-<!-- is effective but rather simplistic as it is solely based on the relative frequency of words in the texts, the ordering of words in the texts cannot be taken into account.  -->
-<!-- . yet rather simplistic as they cannot take into account the structure of the texts -->
-<!-- the effect of adopting a different, more sophisticated strategies has not been investigated t -->
-<!-- previous another model component worth exploring is the feature extraction strategy,  T It is worth evaluating strategies  -->
-<!-- It  rather simplistic. Paragraph vector. As various feature extraction strategies exist, it is worth evaluating the different strategies as well. as mentioned by [@Yu2018] -->
-<!-- many facets of models  -->
-<!-- Previous studies adopt ...  -->
-<!-- little attention has been paid to [@Yu2018] mention paragraph vector -->
-<!-- How to represent  -->
-<!-- the representation of the title an abstracts   -->
-<!-- whilst there exists a  of classification techniques for an active learning model to adopt, research to date has confined to models adopting one classification strategy [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010].
-Models adopting other classification techniques have not been investigated.
--->
- <!-- evaluated techniques other than Support Vector Machines (SVM) -->
-<!-- Although important issues in the application of active learning models on title and abstract screening have been addressed prior studies -->
-
-<!-- on the reviewers screening decision ('relevant', 'irrelevant'), the model can incrementally improve its relevancy predictions on the remaining publications, and again select the next publication to be screened.
--->
-
-<!-- The latest state-of-the-art methods implement active learning, where the model improves  -->
-<!-- The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.  -->
-
-<!-- The algorithm aims to detect whether a given publication is relevant or irrelevant to the systematic review and reorders the publications by their likeliness of relevance; the reviewer sees most relevant papers first!
--->
-<!-- thereby its predictions can be  is allowed to choose the data points it would like to learn from, thus allowing it to learn more efficiently.  -->
-<!-- Active learning systems attempt to overcome the labeling bottleneck by asking -->
-<!-- queries in the form of unlabelled instances to be labelled by an oracle (e.g., a human -->
-<!-- annotator). -->
-<!--  that a machine learning algorithm can perform better with less training if it is allowed to choose the data from which it learns.
-An active learner may pose "queries," usually in the form of unlabelled data instances to be labelled by an "oracle" (e.g., a human annotator) that already understands the nature of the problem -->
-<!-- in which a model can choose the data points it would like to learn from, thus allowing it to learn more efficiently -->
-<!-- its predictions by interactively querying the user to provide labels to unlabelled data .  -->
-<!-- In title and abstract screening this means that the active learning -->
-<!-- is allowed to improve its predictions by choosing the data it wants to learn from.  -->
-
-<!-- Although the effectiveness of active learning models in reducing workload in title and abstract screening has been extensively studied,  -->
 
@@
 The implications of the findings in context of previous research are discussed in the Discussion section, followed by this study's main conclusions in the Conclusion section.
-
-<!-- We demonstrate effectiveness of a generic/flexible tool for assisting researchers in the screening phase..? -->
-<!-- To allow comparison of different models they need to be applied on the same dataset.  -->
-
-<!-- "Screening is performed in two steps, first preliminarily based on title and abstract, -->
-<!-- then based on full-text."  -->
-
-<!-- add: current consensus active learning are state of the art: how do they woroK; by prioritizatio (put in a picture)  -->
-
-<!-- #### identifying the niche  -->
-
-<!-- By evaluating different configurations of an active learning model on different review contexts.  -->
-<!-- status quo: prioritization + active learning? + certainty [@Miwa2014], but classifier  -->
-<!-- Although several studies attempt to evaluate such methods,  -->
-<!-- It makes  -->
-<!-- although  tackle issues in the (complex) area,  -->
-<!-- Furthermore, few studies have investigated the use of different classifiers in any systematic way -->
-<!-- AI-aided title and abstract screening has been proven succesful in reducing workload, but a lack of replication and  -->
-
-<!-- Furthermore, a comparison mode in public health and clinicial medicing [@Miwa2014] compared different classifier on different datasets and found differential performance on 'messier' social sciences datasets.
--->
-
-<!-- #### Occupying -->
-<!-- ##### (listing purpose of new research,  -->
-
-<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
- <!-- [@OConnor2019] -->
-
-<!-- ##### listing questions,  -->
-<!-- This study .  -->
-<!-- research questions:  -->
-<!-- RQ1 – how -->
-<!-- -	RQ1a – does classifier performance vary over different research areas? -->
-<!-- (in what terms does it perform best)  -->
-
-<!-- ASReview aims to reduce workload in the citation screening process by prioritizing the most relevant abstracts.  -->
-<!-- ASReview combines in text classification  -->
-
-<!-- Furthermore, this study makes a contribution to ...  by demonstrating a reproducible and flexible tool,  -->
-<!-- Furthermore, a generic and reproducible workflow is presented to facilitate, hopefully to increase acceptability and usability by researchers performing systematic reviews.  -->
 
@@
 
-<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
-The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
--->
-
-<!-- - then active learning cycle starts in which the user makes a decision after each iteration of the model which is then used to re-train the model. -->
-
-<!-- - instance $x$, label $y$ -->
-<!-- - utility measure $\phi_A(\cdot)$ -->
-<!-- - $x^*_A$ best query instance according to $\phi_A(\cdot)$ -->
-
-<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labelled data set $\mathcal{L}$. -->
-<!-- This is the starting point for the active learning model. -->
-<!-- The model trains a classifier who predicts ...  -->
-<!-- The reviewer and the are interacting in the active learning cycle. -->
-<!-- Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset. -->
-<!-- meaning the reviewer the reviewer screens as little as possible while inclusion rate = high (not true but is nice statistic?) -->
-<!-- The model is balancing two goals: obtain all relevant publications with as little as reviewing possible. -->
-<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model.
-The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer.
--->
-<!-- #### Assumptions  -->
-<!-- 1) decisions of the original SR are **ground truth** (benchmark) (oracle) -->
-<!-- study assumptions: -->
-<!-- - simulation mode  -->
-<!-- - assumptions (prior knowledge etc, oracle = reviewer). -->
-
-<!-- A SR can be divided into phases.  -->
-<!-- Everything starts with a **systematic search**, leading to -->
-<!-- then citation screening is performed, then full-text screening -->
-<!-- [@PRISMA-PGroup2015] -->
-
-<!-- Selecting papers is a two-step process: abstract & fulltext screening -->
 ## Class imbalance problem
@@
 Moreover, these techniques can be run on a personal computer as they require a relatively low amount of processing power.
-
- <!-- Logistic models the posterior directly, naive bayes has higher bias but lower variance,  -->
- <!-- logistic might perform better when trainign set increases. [@Ng2002] -->
-<!-- To carry out classification of publications, a classifier takes given input features $\mathbf{X}$ -->
-<!-- The model utilizes features of previously labelled publications and  -->
-<!-- The model utilizes L to predict labels for all abstracts (classifier). (training) -->
-<!-- a new paper is selected (query) the one that is most likely to be relevant. & queried  -->
-<!-- The reviewer is asked to label the query (relevant, irrelevant), which is then added to the training set.  -->
-<!-- Now the model can update in (retraining) its predictions based on the new training dataset. This is caled retraining.  -->
-<!-- The cycle starts over again..  -->
-<!-- As the cycle repeats itselfs, labelled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s -->
-<!-- We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.  -->
 
@@
 
-<!-- Miwa et al.
-found that active learning was more difficult on data from the social sciences compared to data from the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014].
-As the study by Miwa et al.
-adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated feature extraction strategy has the potential to bridge the performance gap between these research areas.
--->
-
 ## Query strategy
@@
 
-<!-- most equipped to the current scenario in which we are dealing with highly imbalanced datasets and where the goal is to identify all relevant publications as soon as possible. -->
-
 # Simulation study
@@
 ## Set-up
-<!-- The seven models consist of the components described in the Technical Details section, adopting four different classification techniques and two different feature extraction strategies:  -->
-
 To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:
@@
 Access was granted by SURF via a grant (ID EINF-156).
-<!-- can retrieve the labels from the annotated dataset instead -->
-<!-- The oracle is not the reviewer but the labels in the data.  -->
-<!-- The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.  -->
-
-<!-- Data are available via the $\texttt{ASReview}$ GitHub page^[https://github.com/asreview/systematic-review-datasets]. -->
-<!-- All datasets accompanying the systematic reviews are openly published.  -->
+
 ## Datasets 
@@
 
-<!-- FN are far more problematic/unwanted/detrimental than FP: a researcher can label the FP as irrelevant whereas the FN are possibly never seen thereby missing relevant studies running the risk of an invalid systematic review.
--->
-<!-- The goal is twofold: we want to identify all relevant papers, as fast as we can.  -->
-<!-- Tradeoff: identifying all relevant papers and reducing workload.  -->
-<!-- what about class imbalance.  -->
-
-<!-- $$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$  -->
-<!-- $$\texttt{ATD} = \frac{L}{N}$$ -->
-<!-- $$\texttt{ATD} = \frac{L(relevant) }{N}$$ -->
-
-<!-- Is performance related to some characteristic (n, inclusion rate, ...) -->
-
-<!-- ? How to compare outcomes of 3 different optimization strategies?  -->
-
-<!-- The cost of a false negative outweighs the cost of a false positive.  -->
-<!-- Note that we assume the oracle/original user to hold the truth.  -->
-<!-- This is of course not always the case.  -->
-<!-- There are two classes in the data: exlusions and inclusions. -->
-
-<!-- Datasets from the medical and social sciences, software engineering and public administration.  -->
-<!-- Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.  -->
-<!-- Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas. -->
-<!-- ### Optimizing hyperparameters -->
-<!-- Every model component contains hyperparameters, leading to a unique set of hyperparameters for each model.
-To maximize model performance, we need to find optimal values for the hyperparameters.
--->
-<!-- For every model the optimal hyperparameter values are determined by optimizing on the data $d$. -->
-<!-- The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space. -->
-<!-- A description of all hyperparameters and their sample space can be found in the appendix.  -->
-<!-- Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g.
-the area above the curve in the inclusion plot).
--->
-
-<!-- The optimization data $d$ consists of (a subset from) the six systematic review datasets $D$ mentioned above.  -->
-<!-- Three different approaches in composing $d$ are explored:  -->
-
-<!-- - __one__, where hyperparameters are optimized on only one of the six datasets, $d \in D$. Such hyperparameters are expected to lead to maximum performance in the same dataset $d$. -->
-<!-- - __n__, where hyperparameters are optimized on all six data sets, $d = D$. This optimization approach intends to serve in producing the most optimal hyperparameters overall.  -->
-<!-- - __n-1__, where hyperparameters are optimized on all six datasets but one, $d \subset D$.
-Serving as a sensitivity analysis for the former condition, e.g.
-how sensitive are the hyperparamters.
-also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before.
--->
-<!-- where d are all datasets but the one where we want to simulate later on.  -->
-<!-- This results in $6+6+1=13$ sets of hyperparameters for every model.  -->
-
-<!-- Results were visually inspected to check if an optimum (minimal loss) has been reached.  -->
-<!-- More trials were run if the loss still seemed to go down at a quick pace.  -->
-
-<!-- The hyperparameter values that were found to lead to a minimum loss value were visually inspected.  -->
-
-<!-- \newpage -->
-<!-- ## Background -->
-<!-- [@Yu2018], [@Yu2018] simulated 32 svm classifiers, on software engineering.  -->
-<!-- A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling,  -->
-<!-- In terms of Yu et al, we adopt .CT.  -->
-
-<!-- SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]  -->
-
-<!-- abstrackr svm certainty  -->
-
-<!-- SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014] -->
-<!-- Also include social sciences data besides medical data.  -->
-
-<!-- [@Cohen2006] perceptron-based classifier (neural network)  -->
-
-<!-- SVM on legal documents (no balancing, certainty ) [@Cormack2014]  -->
-<!-- in limitations section mentions that LR yields about same results, nb inferior results.  -->
-
-<!-- [@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters. -->
-<!--   "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision.
-The AUC results are mixed, although boosting has a slight edge overall.
-These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)." -->
-
-<!-- Our extensions is that we try different classifiers, on more datasets.  -->
-
-<!-- When no balancing is applied, the training data set = labelled data set $\mathcal{L}$ -->
-<!-- The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions. -->
-
-<!-- a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.  -->
-<!-- Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this?  -->
-<!-- The data -->
-
-<!-- Openness, reproducible,  -->
-
-<!-- Benefits:  -->
-
-<!-- Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies.  -->
-<!-- meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.  -->
-
-<!-- paper organization: -->
-
-<!-- The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas.  -->
-<!-- So not only medical sciences.  -->
-
-<!-- Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers.  -->
-<!-- Few studies have evaluated different classifiers in any systematic way -->
-<!-- different models to use haven't been investigated in a systematic way (only in software engineering) -->
-
-<!-- 1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening.  -->
-<!-- 2) screening prioritization is appealing to systematic reviewers because ... -->
-<!-- 3)  -->
-<!-- 4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.  -->
-
-<!-- lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?) -->
-<!-- There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering  -->
-
-<!-- However, there is a need for consensus () and transparancy?  -->
-
-<!-- So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.   -->
-
-<!-- Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).  -->
-
-<!-- <!-- RQ2 different hyperparameter optimizations? --> 
-<!-- <!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->
-
-<!-- For truly evaluate the effectiveness of such methods,  -->
-
-<!-- Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..  -->
-
-<!-- #### Proposed solution -->
-<!-- This study is about how machine learning models can increase efficiency in systematic reviews. -->
-<!-- Their main objective is to identify ..  -->
-
-<!-- The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review.  -->
-<!-- As the relevant publications are screened first, the reviewing process can be quit earlier.  -->
-
-<!-- The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained.
-This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers.
-Together with the reviewer /human machine interaction.
-The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.
-It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.
--->
-
-<!-- The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical).
-To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible.
-This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken).
-Also reviewing is now much more fun.
-As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.
--->
-
-<!-- ### Background -->
-<!-- ... starts with a search for potentially relevant publications.  -->
-<!-- This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question.  -->
-<!-- Because the initial set often consists of thousands of papers and the -->
-
-<!-- To gather the findings relevant to answering the research question, a systematic search is performed. -->
-<!-- A systematic search starts with collecting all publications that meet pre-specified eligibility criteria. -->
-<!-- From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question.  -->
-<!-- Of all candidate studies only a fraction is relevant [...].  -->
-<!-- As more and more papers are published and reproducibility crisis has emerged,  -->
-<!-- A systematic search often results in thousands of candidate studies. -->
-<!-- Relevant publications are then identified by screening title and abstract of all candidate studies.  -->
-<!-- This screening process is a manual task often executed by multiple reviewers to ensure reliability.  -->
-<!-- This is a time consuming process that weighs heavily on resources.  -->
-
-<!-- Most often the SVM classifier is used, popular and very good results.
-Also lots of other configurations.
-However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still.
-Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]  -->
-
-<!-- A solution is ...  -->
-
-<!-- It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].  -->
-
-<!-- To review a specific research area, one starts out with an initial search of thousands of academic papers.
-All these papers abstracts need to be screened to find an initial batch of possibly relevant papers.
-With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?].
-This whole processes costs this and this much time [shelmilt].
--->
-
-<!-- ----  -->
-
-<!-- ## active learning for systematic reviews  -->
-<!-- corpus = all the text:  -->
-
-<!-- Active learning =  -->
-<!-- increasing classification performance with every query.  -->
-<!-- The query strategy determines the way unlabelled papers are queried to the researcher.  -->
-
-<!-- [@modAL2018] -->
-
-<!-- \newpage -->
-
-<!-- ### Optimization results -->
-<!-- For every model, 13 sets of hyperparameters were optimized. -->
-
-<!-- *to include: plotting the loss reduction over trials*  -->
-
-<!-- Optimal values of the hyperparameters were visually inspected. -->
-
-<!-- As an example, the hyperparameters of the RF_TF-IDF model are presented in Figure 1.  -->
-<!-- A panel displays the optimal values for a certain hyperparameter, where the blue colored dots represent the __one__ condition, the green dots the __n-1__ condition and the orange dot represents the optimal hyperparameter value when optmizing over all datasets (__n__).
-The x-axis represents the possible parameter space where the vertical grey lines mark the boundaries of the hyperparameter space (if possible).
-Note that the feature parameters ngram_max, split_ta, use_keywords and model parameters max_features and n_estimators are categorical.
--->
-
-<!-- Overall, the optimal values are distributed over the parameter space.
-Outlying values all belong to the __one__ condition where optimization was dependent on one dataset only.
-Fore example, the class_weight parameter has an outlying value of 11.3 that belongs to the nudging dataset.
-(Why this is the case I can only speculate, but it is worth mentioning that this dataset has a relatively high inclusion rate  of 5.41%, compared to the other datasets).
--->
-
-<!-- ```{r} -->
-<!-- include_graphics( -->
-<!--   "figs/rf_tfidf.eps", -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- ## Appendix x - Hyperparameters and their sample space  -->
-
-<!-- Classifier hyperparameters -->
-
-<!--     class_weight: normal(0,1) constrained to be > 0 -->
-<!--     class weight of the inclusions. -->
-
-<!--   Logistic Regression -->
-
-<!--     c: float. normal(0,1), constrained to be > 0 -->
-
-<!--   Support Vector Machine -->
-
-<!--     gamma: ["auto", "scale"], -->
-<!--     Gamma parameter of the SVM model. -->
-
-<!--     C:  -->
-<!--     C parameter of the SVM model. -->
-
-<!--     kernel: -->
-<!--     SVM kernel type.["linear", "rbf", "poly", "sigmoid"] -->
-
-<!--   Naive Bayes -->
-
-<!--     "model_param.alpha", # exp(normal(0,1)) -->
-
-<!--   Random Forest  -->
-
-<!--     max_features: int (between 6 and 10) -->
-<!--         Number of features in the model. -->
-
-<!--     n_estimators: int between 10 and 100  -->
-<!--         Number of estimators. -->
-
-<!--     model_param.n_estimators" #quniform(10,100,1) -->
-
-<!-- Balance strategy hyperparameters: -->
-<!--     Dynamic supersampling: -->
-
-<!--     a: float -->
-<!--         Governs the weight of the 1's. Higher values mean linearly more 1's -->
-<!--         in your training sample. -->
-<!--     alpha: float -->
-<!--         Governs the scaling the weight of the 1's, as a function of the -->
-<!--         ratio of ones to zeros. A positive value means that the lower the -->
-<!--         ratio of zeros to ones, the higher the weight of the ones. -->
-<!--     b: float -->
-<!--         Governs how strongly we want to sample depending on the total -->
-<!--         number of samples. A value of 1 means no dependence on the total -->
-<!--         number of samples, while lower values mean increasingly stronger -->
-<!--         dependence on the number of samples. -->
-
-<!-- Feature extraction strategy hyperparameters -->
-
-<!--     split_ta: 0 or 1 -->
-<!--        whether titles and abstracts are split  -->
-
-<!--     use_keywords: 0 or 1 -->
-<!--         whether keywords should be used -->
-
-<!--   TF-IDF -->
-
-<!--     ngram_max: 1, 2 or 3 -->
-<!--         Can use up to ngrams up to ngram_max. For example in the case of  -->
-<!--         ngram_max=2, monograms and bigrams could be used. -->
-
-<!--   Doc2Vec -->
-
-<!--     vector_size: int (between 32 and 127) -->
-<!--         Output size of the vector. -->
-
-<!--     epochs: int (between 20 and 50) -->
-<!--         Number of epochs to train the doc2vec model. -->
-
-<!--     min_count: int (between 1 and 3) -->
-<!--         Minimum number of occurences for a word in the corpus for it to be  -->
-<!--         included in the model. -->
-
-<!--     window: int (between 5 and 9) -->
-<!--         Maximum distance over which word vectors influence each other. -->
-
-<!--     dm_concat: int 0 or 1 -->
-<!--         Whether to concatenate word vectors or not. -->
-
-<!--     dm: int  -->
-<!--         Model to use. -->
-<!--         0: Use distribute bag of words (DBOW). -->
-<!--         1: Use distributed memory (DM). -->
-<!--         2: Use both of the above with half the vector size and concatenate them. -->
-
-<!--     dbow_words: int 0 or 1 -->
-<!--         Whether to train the word vectors using the skipgram method. -->
-
-<!-- # The software  -->
-<!-- ASReview takes the following parameters/arguments:  -->
-<!--  We now have 75 combinations.  -->
-<!-- for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed.
-From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.
--->
-
 # Results 
@@
 
-<!-- although the RF + TF-IDF model performs seems to be the lowest performing model for the longest part of the screening process.   -->
-<!-- , buy the SVM + D2V model (pink) reaches this point of 95% recall earlier than the LR + TF-IDF model (yellow).  -->
-
 Figure 1b shows a subset of the recall curves in Figure 1a, namely the curves for the first four models only to allow for a visual comparison across classification techniques adopting the TF-IDF feature extraction strategy.
@@
 # path
-# nudgingplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging", full.names=TRUE)
+# nudgingplots <- list.files("../../results/one_seed/plots/nudging", full.names=TRUE)
 f <- c("inclusion_all_nudging", "inclusion_tfidf_nudging", "inclusion_d2v_nudging", "inclusion_d2v_vs_tfidf_logistic_nudging", "inclusion_d2v_vs_tfidf_rf_nudging", "inclusion_d2v_vs_tfidf_svm_nudging")
-nudgingplots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging/", f, ".pdf")
+nudgingplots <- paste0("../../results/one_seed/plots/nudging/", f, ".pdf")
 include_graphics(nudgingplots)
@@
 d <- c("ptsd", "software", "ace", "virus", "wilson")
-files <- c("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
+files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
 include_graphics(files)
@@
 
-plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/", f, "ptsd.pdf")
+plots <- paste0("../../results/one_seed/plots/ptsd/", f, "ptsd.pdf")
 include_graphics(plots)
@@
 # path
-plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/software/", f, "software.pdf")
+plots <- paste0("../../results/one_seed/plots/software/", f, "software.pdf")
 include_graphics(plots)
@@
 # path
-plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/ace/", f, "ace.pdf")
+plots <- paste0("../../results/one_seed/plots/ace/", f, "ace.pdf")
 include_graphics(plots)
@@
 # path
-plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/virus/", f, "virus.pdf")
+plots <- paste0("../../results/one_seed/plots/virus/", f, "virus.pdf")
 include_graphics(plots)
@@
 # path
-plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/wilson/", f, "wilson.pdf")
+plots <- paste0("../../results/one_seed/plots/wilson/", f, "wilson.pdf")
 include_graphics(plots)

### 2020-05-14 results/README.Rmd
update paths

@@
 output: github_document
+bibliography: ../manuscript/manuscript/asreview.bib
 ---
@@
 Create table for manuscript (all means over 15 runs)
-```{r}
+```{r, results = "asis"}
 tabres <- 

### 2020-05-14 results/README.Rmd
add r scripts results readme

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = TRUE)
 library(rjson)
@@
 Create table for manuscript (all means over 15 runs)
-```{r, results = "asis"}
+```{r, echo = FALSE, results = "asis"}
 tabres <- 

### 2020-06-18 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
update config file N
fix a few mistakes

--- 2020-05-14 manuscript/manuscript/manuscript.Rmd
@@
 # keywords:
-#   - Machine learning
-#   - Active learning
-#   - Systematic Review
-#   - Study Selection
-#   - Text classification
-#   - Text representation
 header-includes:
@@
 Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
-Especially when the need for guidelines is urgent - such as in the context of the current COVID-19 crisis - it is almost impossible to provide a review that is both timely and comprehensive.
+Especially when the need for guidelines is urgent it is almost impossible to provide a review that is both timely and comprehensive.
 
@@
 The application of active learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
-Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique to predict relevanc of publications, namely Support Vector Machine.
+Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique to predict relevance of publications, namely Support Vector Machine.
 Findings from outside the field of active learning show that different classification techniques can serve different needs in the retrieval of relevant publications, for example recall versus precision [@Kilicoglu2009; @Aphinyanaphongs2004].
@@
 Model performance was assessed by conducting a simulation on six systematic review datasets.
-Datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], virology [@Kwok2020], software engineering [@Yu2018], behavioural public administration [@Nagtegaal2019] and psychology [@vandeSchoot2017], to assess generalizability of the models across research contexts.
+datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], virology [@Kwok2020], software engineering [@Yu2018], behavioural public administration [@Nagtegaal2019] and psychology [@vandeSchoot2017], to assess generalizability of the models across research contexts.
 The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@ASReview2020].
@@
  - L2-regularized Logistic Regression (LR) models the probabilities describing the possible outcomes by a logistic function.
-The L2 penalty is imposed on the coefficients to reduce the number of features upon which the given solution is dependent [@scikit-learn].
+A penalty is imposed on the size of the coefficients, shrinking coefficients of features with a minor contribution to the solution towards zero.
+
  - Naive Bayes (NB) is a supervised learning algorithm often used in text classification.
@@
 A classical example of feature extraction is a 'bag of words' (bow) representation.
-For each text in the data set, the term frequency - the number of occurrences of each word - is stored.
+For each text in the dataset, the term frequency - the number of occurrences of each word - is stored.
 This leads to $n$ features, where $n$ is the number of distinct words in the texts [@scikit-learn].
 A serious weakness of this method is that it highly values often occurring but otherwise meaningless words such as "the".
-A more sophisticated bow approach is Term-Frequency Inverse Document Frequency (TF-IDF), which circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire data set [@Ramos2003].
+A more sophisticated bow approach is Term-Frequency Inverse Document Frequency (TF-IDF), which circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire dataset [@Ramos2003].
 A downside of TF-IDF and other bow methods is that they do not take into account the ordering of words, thereby ignoring semantics.
@@
 
-To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:^[]
-
- 5. SVM + Doc2vec
- 6. RF + Doc2vec
- 7. LR + Doc2vec
+To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:
+
+ 5. SVM + D2V
+ 6. RF + D2V
+ 7. LR + D2V
 
@@
 Hence, 42 simulations were carried out, representing all model-dataset combinations.
-To account for variance, every simulation was repeated for 15 trials.
-For every simulation, hyperparameters were optimized through a random search to arrive at maximum model performance.
+Every simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
+To account for sampling variance, every simulation was repeated for 15 trials, a reasonable number within the available computing power.
+To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for every of the 15 trials.
+Although varying over trials, the 15 initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
+A seed value was set to ensure reproducibility.For every simulation, hyperparameters were optimized through a random search to arrive at maximum model performance.
+The classifier was retrained every time after a publication had been labelled.
+The simulation ended after all publications in the dataset had been labelled.
 Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020].
 There was no need for a human reviewer as the model could query the labels in the data instead.
-
-Every simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
-To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for every of the 15 trials.
-Although varying over trials, the 15 initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
-A seed value was set to ensure reproducibility.
-The classifier was retrained every time after a publication had been labelled.
-The simulation ended after all publications in the dataset had been labelled.
 
@@
 
-Datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
-The Wilson dataset [@Appenzeller-Herzog2020] is on a review on effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
-The Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
-The Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
+datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
+The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
+From the same scientific field, the Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
+From _virology_, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
 From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012].
@@
 datastats <- 
-  tibble(Dataset = names(all), 
+  tibble(dataset = names(all), 
        #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
@@
 datastats <- datastats %>%
-  select(Dataset, candidates_test, incl_test, inclrate_test) 
-colnames(datastats) <- c("Dataset", rep(c("Candidate publications", 
+  select(dataset, candidates_test, incl_test, inclrate_test) 
+colnames(datastats) <- c("dataset", rep(c("Candidate publications", 
                                        #"Studies selected for fulltext screening", 
@@
 
-```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves for the Nudging dataset.
-", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
+```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves of different models for the Nudging dataset, indicating how fast the model finds relevant publications during the process of screening publications.
+Figure a displays curves for all seven models at once.
+The remaining figures display curves for several subsets of those models to allow for a more detailed inspection.", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
 # path
@@
 \end{center}
+
 ```{r, results="asis"}
@@
 
-```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves for all seven models on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
+```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for all  indicating how fast the model finds relevant publications during the process of screening publications.
+on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
 d <- c("ptsd", "software", "ace", "virus", "wilson")
@@
 Moreover, the curves for the Ace (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared to other the other datasets.
-For these datasets, model performance seemed to be more dependent on the initial training data set compared to other datasets.
+For these datasets, model performance seemed to be more dependent on the initial training dataset compared to other datasets.
 
@@
 
+Additionally, whilst the sample of datasets in the current study is diverse compared to previous studies, the sample size does not allow for investigating how characteristics of the data - such as inclusion rate - relate to model performance.
+To build confidence in active learning models for screening publications, it is essential to identify how characteristics of the data influence model performance.
+Such a study requires more data on systematic reviews.
+Therefore, we call systematic reviewers to make an effort to openly publish their datasets.
+
+<!-- the datasets are by no means representative of the current body of systematic reviews.  -->
+
 <!-- When models are applied in a real world setting there is no way to know of optimal parameter. Future research will focus on a cross-validation  -->
@@
 <!-- Since the active learning models base their predictions only on metadata... -->
-Screening publications in systematic reviews is typically a two-step process.
+<!-- Screening publications in systematic reviews is typically a two-step process.
 First, titles and abstracts are screened to identify potentially relevant publications, called abstract inclusions.
@@
 Hence, greater efforts are needed to provide information on the abstract inclusions in openly published systematic review datasets.
+-->
 
@@
 I am grateful for all researchers who have made great efforts to openly publish the data on their systematic reviews, special thanks go out to Rosanna Nagtegaal.
-I would also like to thank Caroline van Baal for supporting me in writing this thesis, and prof.
+I would also like to thank dr.
+Caroline van Baal for supporting me in writing this thesis, and prof.
 dr.

### 2020-06-18 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
first draft simulation study documentation

@@
 
-datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
+Datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
 The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
@@
 datastats <- datastats[c(2,3,4,1,5,6), ]
+saveRDS(datastats, "tables/tab1_data.RDS")
+
 print(xtable(datastats, digits = c(0,0,0,0,1)),
@@
 
+saveRDS(tabatd, file = "tables/tab2_atd.RDS")
+
 print(xtable(tabatd, align = c("r", "r", rep("c", 6))), 
@@
 # insert N per dataset 
+saveRDS(tabwss95, file = "tables/tab3_wss95.RDS")
 
@@
 tabrrf10 <- rbind(tabrrf10, (c("median (MAD)", mad[c(2:4, 1, 5,6)])))
+saveRDS(tabrrf10, file = "tables/tab4_rrf10.RDS")
 

### 2020-06-18 manuscript/manuscript/simulation_study_results.Rmd
first draft simulation study documentation

---
title: "Simulation studies"
output: github_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
options(tinytex.verbose = TRUE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(captioner)
library(glue)
library(rbbt)
library(officer)
library(flextable)
# load model parameters 
source("asr-parameters.R")

#pathRdata <- "data/"
pathRdata <- "../../datasets/data_statistics/"
```

_This document is currently a work in progress. The results documented here originate from Gerbrich Ferdinands' master's thesis which can be found [here](https://github.com/GerbrichFerdinands/asreview-thesis/blob/master/manuscript/manuscript/Ferdinands%2C-G---MSBBSS.pdf)._

To provide insight in how much screening effort ASReview could potentially save, seven ASReview models were simulated on six existing systematic review datasets. In short, for all six datasets ASReview could have saved at least 60% of screening effort (e.g. WSS95% was < 40%). For some datasets, ASReview was even able to detect 95% of relevant publiations after screening only 5% of relevant publications.

### Datasets 
Datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], virology [@Kwok2020], software engineering [@Yu2018], behavioural public administration [@Nagtegaal2019] and psychology [@vandeSchoot2017], to assess generalizability of the models across research contexts. Datasets are available in the [ASReview systematic review datasets repository](https://github.com/asreview/systematic-review-datasets).

Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search. Candidate studies with missing abstracts and duplicate instances were removed from the data. All test datasets consisted of thousands of candidate studies, of which only only a fraction was deemed relevant to the systematic review. For the Virus and the Nudging dataset, the inclusion rate was about 5 percent. For the remaining six datasets, inclusion rates were centered around 1-2 percent.
<!-- Preprocessing scripts and resulting datasets can be found on the [GitHub repository for this thesis](https://github.com/GerbrichFerdinands/asreview-thesis). Test datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.  -->

__Table 1 - Statistics on the systematic review datasets__
```{r}
tab1 <- readRDS("tables/tab1_data.RDS")
knitr::kable(tab1, format="markdown")
```

### Models
To assess effect of different ASReview models, seven models were evaluated differing in terms of the classification technique (Naive Bayes, Linear Regression, Support Vector Machine, and Random Forest) and the feature extraction strategy they adopt (TF-IDF and Doc2vec).  The Naive Bayes + TF-IDF model is the current default in ASReview. Note that the ASReview GUI currently only offers freedom of choice for a classification technique. However, the models presented here are not exhaustive as the ASReview backend implements various other configurations.

### Evaluation
Model performance was assessed by two different measures, Work Saved over Sampling (WSS), and Relevant References Found (RRF).

WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006]. Typically measured at a recall level of 0.95 [@Cohen2006], WSS95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications. In the current study, WSS is computed at 0.95 recall. RRF statistics are computed at 10%, representing the proportion of relevant publications that are found after screening 10% of all publications.

Furthermore, model performance was visualized by plotting recall curves. Plotting recall as a function of the proportion of screened publications offers insight in model performance throughout the entire screening process [@Cormack2014; @Yu2018]. The curves give information in two directions. On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (1-WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).

For every simulation, the RRF10 and WSS95, are reported as means over 15 trials. To indicate the spread of performance within simulations, the means are accompanied by an estimated standard error of the mean $\hat s$. To compare overall performance across datasets, median performance is reported for every dataset, accompanied by the Median Absolute Deviation (MAD), indicating variability between models within a certain dataset. Recall curves are plot for every simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.

## Results
First of all, models showed much higher performance for some datasets than for others. While performance on the PTSD (Figure 2a) and the Software dataset (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.

#### Recall curves 
__Nudging dataset__
```{r}
include_graphics("../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf")
```
<embed src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf" width="50%" style="display: block; margin: auto;" type="application/pdf" />

<img src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf"
     style="float: left; margin-right: 10px;" />
__PTSD dataset__

__Software dataset__

__Ace dataset__

__Virus dataset__

__Wilson dataset__

__Table 2 - WSS95 values (mean, standard error) for all model-dataset combinations, and median (MAD) for all datasets__
```{r}
tabwss <- readRDS("tables/tab3_WSS95.RDS")
knitr::kable(tabwss, format = "markdown", caption="WSS95 values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
```

__Table 3 - RRF10 values (mean, standard error) for all model-dataset combinations, and median (MAD) for all datasets__
```{r}
tabrrf <- readRDS("tables/tab4_RRF10.RDS")
knitr::kable(tabrrf, format = "markdown", caption="RRF10 values ($\\bar x, (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
```

# References

### 2020-06-18 manuscript/manuscript/simulation_study_results.Rmd
add figures

@@
 __Nudging dataset__
-```{r}
-include_graphics("../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf")
-```
-<embed src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf" width="50%" style="display: block; margin: auto;" type="application/pdf" />
 
-<img src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf"
-     style="float: left; margin-right: 10px;" />
 __PTSD dataset__

### 2020-07-20 Ferdinands,-G---MSBBSS.Rmd
corrctions July 20 2020

--- 2020-06-18 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
@@
 subtitle: Evaluating models across research areas 
-author: "Gerbrich Ferdinands"
+author: "G. Ferdinands, R.D. Schram, J. de Bruin, A. Bagheri, D. Oberski, L. Tummers, R. van de Schoot"
 # keywords:
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
+knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center",fig.path = "figures/", dev = "png", fig.pos = "H") 
 options(tinytex.verbose = TRUE)
@@
 files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
+
 include_graphics(files)

### 2020-07-20 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
corrctions July 20 2020

@@
     - \usepackage[left]{lineno}
+    - \usepackage{amssymb}
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 <!--   bookdown::pdf_document2: -->
-<!--     extra_dependencies: subfig, algorithm2e -->
+<!--     extra_dependencies: subfig, algorithm2e, float -->
 <!--     number_sections: no -->
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", fig.pos = "H") 
+knitr::opts_chunk$set(echo = FALSE, fig.ncol = 2, out.width = "50%", fig.align = "center", dev = "png", fig.pos = "H") 
 options(tinytex.verbose = TRUE)
@@
 # table  on datasets statistics
-table_nums(name = "datasets", caption = "Statistics on the test datasets obtained from six original systematic reviews.")
+table_nums(name = "datasets", caption = "Statistics on the datasets obtained from six original systematic reviews.")
 table_nums(name = "atd", caption = "ATD values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
@@
 \linenumbers
+# Abstract
+#### Background 
+the context and purpose of the study
+
+#### Methods
+how the study was performed and statistical tests used
+
+#### Results
+the main findings
+
+#### Conclusions
+brief summary and potential implications
+
+keywords:
+
 # Background
@@
 Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
-Especially when the need for guidelines is urgent it is almost impossible to provide a review that is both timely and comprehensive.
+Especially when the need for guidelines is urgent it is extremely challenging to provide a review that is both timely and comprehensive.
 
@@
 A well-established approach in increasing efficiency in title and abstract screening is screening prioritization [@Cohen2009; @Shemilt2014].
-In screening prioritization, the learning model presents the reviewer with the publications which are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
+In screening prioritization, the learning model presents the reviewer with the publications that are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
 Such an approach allows for substantial time-savings in the screening process as the reviewer can decide to stop screening after a sufficient number of relevant publications have been retrieved [@Yu2019].
-Moreover, reviewing relevant publications early facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
+Moreover, the early retrieval of relevant publications facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
 <!-- Additionally, several studies report increasing efficiency beyond saving time [@OMara-Eves2015].  -->
@@
 Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Gates2018a].
-With active learning, the machine learning model can iteratively improve its predictions on unlabelled data by allowing the model to select the records from which it wants to learn [@Settles2012].
+With active learning, the ML model can iteratively improve its predictions on unlabelled data by allowing the model to select the records from which it wants to learn [@Settles2012].
 The model queries these records to a human annotator who provides them with a label, from which the model then updates its predictions.
-The general assumption is that by letting the model select which records are labelled, the model can achieve higher accuracy while requiring the human annotator to label as few records as possible [@Settles2009].
+The general assumption is that by letting the model select which records are labelled, the model can achieve higher accuracy more quickly while requiring the human annotator to label as few records as possible [@Settles2009].
 Active learning has proven to be an efficient strategy in large unlabelled datasets where labels are expensive to obtain [@Settles2009].
-This makes the screening phase in systematic reviewing an ideal candidate for such models because typically, labelling a large number of publications is very costly.
-When active learning is applied in the screening phase, the reviewer screens publications that are selected by an active learning model.
+This makes the screening phase in systematic reviewing an ideal candidate solution for such models because typically, labelling a large number of publications is very costly.
+When active learning is applied in the screening phase, the reviewer screens publications that are suggested by an active learning model.
 Subsequently, the active learning model learns from the reviewers' decision ('relevant', 'irrelevant') and uses this knowledge to update its predictions and to select the next publication to be screened by the reviewer.
@@
 The application of active learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
-Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], all studies used the same classification technique to predict relevance of publications, namely Support Vector Machine.
-Findings from outside the field of active learning show that different classification techniques can serve different needs in the retrieval of relevant publications, for example recall versus precision [@Kilicoglu2009; @Aphinyanaphongs2004].
-Therefore, it is essential to evaluate different classification techniques in the context of active learning models.
+Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Singh2018; @Carvallo; @Yimin2007], ready-to-use software tools implementing such active learning models (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]) currently use the same classification technique to predict relevance of publications, namely Support Vector Machine (SVM).
+Findings show that different classification techniques can serve different needs in the retrieval of relevant publications, for example the desired balance between recall and precision [@Kilicoglu2009; @Aphinyanaphongs2004].
+Therefore, is essential to evaluate different classification techniques in the context of active learning models.
+The current study investigates active learning models adopting four classification techniques: Naive Bayes, Logistic Regression, Support Vector Machine, and Random Forest.
+These are widely adopted techniques in text classification [@Aggarwal2012] and are suitable for creating interpretable ML models [@Molnar2020].
+Moreover, due to their relatively short computation time they are fit for software tools to be used in scientific practice, as they allow the reviewer to be timely presented with the next publication.
+
+<!-- low computation time makes these techniques fit to practial use in a software tool when run on a personal computer, as retraining a model can be done in a timely manner.
+as default of asreview is on local computer to be applicable -->
+
+<!-- Whilst the performance of several classification techniques has been investigated in the ML-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2019; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
+-->
+
 <!-- no study in this area has made a comparison between models adopting different classification techniques. -->
 <!-- Since a plethora of techniques exist [@Aggarwal2012], it would be of interest to incorporate such models to this area as well.  -->
-Another component known to influence performance of the models is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Le2014; @Zhang2011].
-Previous studies all adopt an effective but rather simplistic 'bag of words' strategy [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010].
-It is of interest to evaluate models using this approach by comparing them to models adopting a more sophisticated strategy, called 'Doc2vec' [@Le2014].
-Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] and software engineering [@Yu2018, @Yu2019].
+Another component that influences model performance is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Zhang2011; @Carvallo; @Singh2018].
+One of the more sophisticated feature extraction strategies is called Doc2vec (D2V), also known as Paragraph vector [@Le2014].
+D2V learns continuous distributed vector representations for pieces of text.
+The idea of distributed representation is that every word can be known by its neighborhood.
+D2V can overcome problems with more simplistic feature extraction strategies such as TF-IDF, which ignores the the semantics and the ordering of the words [@Le2014].
+Therefore, it is of interest to compare models adopting D2V to models adopting TF-IDF.
+
+<!-- [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010], -->
+
+Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] and computer science [@Yu2018, @Yu2019].
 Model replications on reviews from varying research contexts are essential to draw conclusions about the general effectiveness of active learning models [@OMara-Eves2015; @Marshall2020].
@@
 They found that active learning was more difficult on data from the social sciences due to the different nature of the vocabularies used.
-Therefore, it is of interest to evaluate model performance across different research contexts.
-Taken together, evaluations of active learning models in the context of systematic reviewing are required (1) across different classification techniques, (2) feature extraction strategies, and (3) review contexts.
-The current study aims to address these issues by answering the following research questions:
-
-|    __RQ1__ What is the performance of several active learning models across different classification techniques?
-|    __RQ2__ What is the performance of several active learning models across different feature extraction strategies? 
-|    __RQ3__ Does the performance of active learning models differ across systematic reviews from different research areas?
+Thus, it is of interest to evaluate model performance across different research contexts, namely the social science, humanities, medical science and computer science.
+
+Taken together, for a more comprehensive understanding of active learning models in the context of systematic reviewing, a methodical evaluation of such models is required.
+The current study aims to address this issue by answering the following research questions:
+
+<!-- (1) across different classification techniques, (2) feature extraction strategies, and (3) review contexts.  -->
+
+<!-- Therefore, the current study aims to address these issues by answering the following research questions: -->
+
+|    __RQ1__ What is the performance of active learning models across four different classification techniques?
+|    __RQ2__ What is the performance of active learning models across two different feature extraction strategies? 
+|    __RQ3__ Does the performance of active learning models differ across six systematic reviews from four different research areas?
 
 The purpose of the current paper is to increase the evidence base on active learning models for reducing workload in title and abstract screening in systematic reviews.
-We adopt four different classification techniques (Naive Bayes, Linear Regression, Support Vector Machine, and Random Forest) and two different feature extraction strategies (TF-IDF and Doc2vec) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
-Model performance was assessed by conducting a simulation on six systematic review datasets.
-datasets were collected from the fields of medicine [@Cohen2006; @Appenzeller-Herzog2019], virology [@Kwok2020], software engineering [@Yu2018], behavioural public administration [@Nagtegaal2019] and psychology [@vandeSchoot2017], to assess generalizability of the models across research contexts.
-The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@ASReview2020].
-$\texttt{ASReview}$ is an open source and generic tool such that users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
+We adopt four different classification techniques (NB, LR, SVM, and RF) and two different feature extraction strategies (TF-IDF and D2V) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
+Models were assessed by conducting a simulation on six systematic review datasets.
+Datasets were collected from the fields of medical science [@Cohen2006; @Appenzeller-Herzog2019; @Kwok2020], computer science [@Yu2018], humanities [@Nagtegaal2019] and social science [@vandeSchoot2017], to assess generalizability of the models across research contexts.
+The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@vandeSchoot2020].
+$\texttt{ASReview}$ is an open source and generic tool in which users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
 All scripts and data used are openly published to facilitate usability and acceptability of ML-assisted title and abstract screening in the field of systematic review.
 
-<!-- . -->
-
 The remaining part of this paper is organized as follows.
-The Technical details section elaborates on the characteristics of active learning models for identifying relevant publications in the context of systematic reviews.
-The Simulation study section describes the study that was designed to answer the research questions.
-The findings of the simulation study are reported in the Results section.
-The implications of the findings in context of previous research are discussed in the Discussion section, followed by this study's main conclusions in the Conclusion section.
-
-# Technical details 
+The methods section describes the study that was designed to answer the research questions and elaborates on the technical details of active learning models for identifying relevant publications in the context of systematic reviews.
+The findings of the simulation study are reported in the results section.
+The implications of the findings in context of previous research are discussed in the discussion section, followed by this study's main conclusions in the conclusion section.
+
+# Methods
+
+## Technical details 
 What follows is a more detailed account of the active learning models.
@@
 
-## Task description
+### Task description
 The screening process of a systematic review starts with all publications obtained in the search.
-The task is to identify which of these publications are relevant, by screening them at the title and abstract level.
+The task is to identify which of these publications are relevant, by screening their titles and abstracts.
 In active learning for screening prioritization, the screening process proceeds as follows:
@@
 - Start with the set of all unlabelled records (titles and abstracts), $\mathcal{U}$.
-- The reviewer provides a label for a few, for example 5-10, records $x \in \mathcal{U}$, creating an set of labelled records $x \in \mathcal{L}$ such that $x \notin \mathcal{U}$.
+- The reviewer provides a label for a few, for example 5-10 records $x \in \mathcal{U}$, creating a set of labelled records $x \in \mathcal{L}$ such that $x \notin \mathcal{U}$.
 The label can be either Relevant $\langle x, \texttt{R}\rangle$ or Irrelevant $\langle x, \texttt{I}\rangle$.
@@
 
-  1. A classifier, $C$, is trained on the labelled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
+  1. A classifier $C$ is trained on the labelled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
 
@@
 
-  6. The newly labelled record is added to the training data, such that $x \in \mathcal{L}$ and $x \notin \mathcal{U}$
-
-  7. Back to step 1.
-
-In this active learning cycle, the model can incrementally improve its predictions on the remaining unlabelled title and abstracts.
-The relevant titles and abstracts are identified as early in the process as possible.
-The reviewer and the model keep interacting until the reviewer decides to stop or until all records been labelled.
-
-## Class imbalance problem
+  6. The newly labelled record is added to the training data, such that $x^* \in \mathcal{L}$ and $x^* \notin \mathcal{U}$
+
+  7. Back to step 1
+
+  8. Repeat this cycle until the reviewer decides to stop [@Yu2019] or until all records have been labelled, $\mathcal{U} = \varnothing$.
+
+In this active learning cycle, the model incrementally improves its predictions on the remaining unlabelled title and abstracts.
+Relevant titles and abstracts are identified as early in the process as possible.
+
+This case is an example of pool-based active learning, as the next record to be queried is selected by predicting relevancy for all records in a fixed pool [@Settles2012].
+Another form of active learning is stream-based active learning, in which data is regarded as a stream instead of a fixed pool, in which the model selects one record at a time and then decides whether or not to query this record.
+This approach of active learning is preferred when it is expensive or impossible to exhaustively search the data for selecting the next query.
+A possible application of stream-based active learning is living systematic reviews, as the review is continually updated as new evidence becomes available.
+For an example see the study by Wynants et al., @Wynants2020.
+
+### Class imbalance problem
 There are two classes in the dataset: relevant and irrelevant publications.
@@
 This is evident in the case of a systematic review dataset where only three percent of publications are relevant.
-A model would achieve 97% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.
+
+<!-- A model would achieve 97% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.  -->
 
 Previous studies have addressed the class imbalance problem by rebalancing the training data in various ways [@OMara-Eves2015].
-To decrease the class imbalance in the training data, the models in the current study rebalance the training set by Dynamic Resampling (DR).
+To decrease the class imbalance in the training data, the models in the current study rebalance the training set by a technique we propose to call Dynamic Resampling (DR).
 DR undersamples the number of irrelevant publications in the training data, whereas the number of relevant publications are oversampled such that the size of the training data remains the same.
-The ratio between relevant and irrelevant publications in the rebalanced training data is not fixed, but dynamically updated depending on the number of publications in the available training data, the number of publications in the total data, and the ratio between relevant and irrelevant publications in the available training data.
-
-## Classification
-To make predictions on the unlabelled publications, a classifier is trained on features from the training data. 
+The ratio between relevant and irrelevant publications in the rebalanced training data is not fixed, but dynamically updated depending on the number of publications in the available training data, the total number of publications in the dataset, and the ratio between relevant and irrelevant publications in the available training data.
+
+<!-- This works because..  -->
+<!-- This technique is related to aggressive undersampling in such a way that.  -->
+
+### Classification
+To make predictions on the unlabelled publications, a classifier is trained on features from the training data. The performance of the following four classifiers is explored:
 <!-- The classifier predicts class of a given unlabelled publication.  -->
-A technique widely used in classification tasks is the Support Vector Machine (SVM).
-SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
-SVMs have been proven to be effective in active learning models for screening prioritization [@Yu2018; @Miwa2014].
-Moreover, SVMs are the currently the only classifier implemented in ready-to-use software tools implementing active learning for screening prioritization (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]).
-
-Whilst the performance of several classification techniques has been investigated in the ML-aided title-and-abstract screening field in general [@Kilicoglu2009; @Aphinyanaphongs2004], the relatively new subfield of active learning for screening prioritization has not yet studied the performance of classifiers other than SVMs [@Yu2018; @Yu2019; @Cormack2014; @Cormack2015; @Miwa2014; @Wallace2010].
 <!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
 <!-- In fact, research in this area to date has not yet determined the performance of classifiers other than SVMs. -->
-The current study aims to address this gap by exploring performance of three classifiers besides SVM:
-
- - L2-regularized Logistic Regression (LR) models the probabilities describing the possible outcomes by a logistic function.
+
+ - Support Vector Machine (SVM) - SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
+
+ - L2-regularized Logistic Regression (LR) models the probabilities describing the possible outcomes by a logistic function. The coefficients are regularizes/model is regularized. 
  A penalty is imposed on the size of the coefficients, shrinking coefficients of features with a minor contribution to the solution towards zero.
@@
  - Naive Bayes (NB) is a supervised learning algorithm often used in text classification.
-Based on Bayes' Theorem, with the 'naive' assumption that all features are independent given the class value [@Zhang2004].
+Based on Bayes' theorem, with the 'naive' assumption that all features are independent given the class value [@Zhang2004].
+
 - Random Forests (RF) is a supervised learning algorithm where a large number of decision trees are fit on bootstrapped samples of the original data.
@@
 
-These three classification techniques were selected because they are widely adopted methods in text classification [@Aggarwal2012].
-Moreover, these techniques can be run on a personal computer as they require a relatively low amount of processing power.
-
-## Feature extraction
-To predict publication class, the classifier uses information from the publications in the dataset.
+### Feature extraction
+To predict relevance of a given publication, the classifier uses information from the publications in the dataset.
 Examples of such information are titles and abstracts.
@@
 
-A classical example of feature extraction is a 'bag of words' (bow) representation.
-For each text in the dataset, the term frequency - the number of occurrences of each word - is stored.
-This leads to $n$ features, where $n$ is the number of distinct words in the texts [@scikit-learn].
-A serious weakness of this method is that it highly values often occurring but otherwise meaningless words such as "the".
-A more sophisticated bow approach is Term-Frequency Inverse Document Frequency (TF-IDF), which circumvents this problem by adjusting the term frequency in a text with the inverse document frequency, the frequency of a given word in the entire dataset [@Ramos2003].
-A downside of TF-IDF and other bow methods is that they do not take into account the ordering of words, thereby ignoring semantics.
-An example of an approach that aims to overcome this weakness is Doc2vec (D2V).
-Doc2vec extracts features of the texts by a neural network, capable of grasping semantics by learning to predict the words in the texts [@Le2014].
-
-## Query strategy
+Term-Frequency Inverse Document Frequency (TF-IDF) stores the term frequency - the number of occurrences of each word - for each text in the dataset.
+The term frequency is adjusted with the inverse document frequency, the number of documents which contain the given word [@Ramos2003].
+A disadvantage of TF-IDF and other bag-of-words methods is that they do not take the ordering of words into account, thereby ignoring semantics.
+An example of an approach that aims to overcome this weakness is D2V.
+D2V learns continuous distributed vector representations for pieces of text capable of grasping semantics by learning to predict the words in the texts [@Le2014].
+
+### Query strategy
 The active learning model can adopt different strategies in selecting the next publication to be screened by the reviewer.
@@
 Traditionally, this strategy trains the most accurate model because the model can learn the most from instances it is uncertain about.
-However, a study comparing performance of both strategies in detecting relevant publications found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
+However, a study comparing the performance of both strategies in detecting relevant publications found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
 
 Certainty-based active learning is the preferred strategy for the task at hand.
-Firstly, this strategy is far better suited to the goal of prioritizing relevant publications compared to uncertainty-based active learning, in which the publications are prioritized that the model is most uncertain about.
+Firstly, the aim of the screening process is to find relevant publications, not to train a good model.
 Secondly, certainty-based active learning is far better equipped at dealing with imbalanced data in active learning, as it aims to present only records that belong to the relevant class [@Fu2011].
 
-# Simulation study
+## Simulation study
 The section below describes the simulation study that was carried out to answer the research questions.
 
-## Set-up
+### Set-up
 To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:
@@
 
-To address __RQ2__, the classifiers were combined with Doc2vec feature extraction, leading to the following three models:
+To address __RQ2__, the classifiers were combined with D2V feature extraction, leading to the following three models:
 
@@
 
-The combination NB + D2V could not be tested because the Multinomial Naive Bayes classifier^[https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB] can only handle a feature matrix with positive values, whereas the Doc2vec feature extraction approach^[https://radimrehurek.com/gensim/models/doc2vec.html] produces a feature matrix that can also contain negative values.
-Performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing __RQ3__.
+The combination NB + D2V could not be tested because the multinomial naive Bayes classifier^[https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB] can only handle a feature matrix with positive values, whereas the D2V feature extraction approach^[https://radimrehurek.com/gensim/models/doc2vec.html] produces a feature matrix that can also contain negative values.
+The performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing __RQ3__.
 Hence, 42 simulations were carried out, representing all model-dataset combinations.
-Every simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
-To account for sampling variance, every simulation was repeated for 15 trials, a reasonable number within the available computing power.
-To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for every of the 15 trials.
+
+Instead of having a human reviewer label publications manually, the screening process was simulated by retrieving the labels in the data.
+Each simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
+The model was retrained every time after a publication had been labelled.
+A simulation ended after all publications in the dataset had been labelled.
+To account for sampling variance, each simulation was repeated 15 times.
+To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for each of the 15 trials.
 Although varying over trials, the 15 initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
-A seed value was set to ensure reproducibility.For every simulation, hyperparameters were optimized through a random search to arrive at maximum model performance.
-The classifier was retrained every time after a publication had been labelled.
-The simulation ended after all publications in the dataset had been labelled.
-Simulations were run using \texttt{ASReview}'s simulation mode [@ASReview2020].
-There was no need for a human reviewer as the model could query the labels in the data instead.
-
-This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
-Simulations were run in ASReview, version 0.9.3 [@ASReview2020].
+A seed value was set to ensure reproducibility.
+The simulation study was carried out using the \texttt{ASReview} simulation extension [@ASReview2020].
+For each simulation, hyperparameters were optimized through a ...
+tpe to arrive at maximum model performance.
+todo
+<!-- About a 1000 runs, retraining after labelling 20, after visual inspection.  --> 
+Scripts for the hyperparaemter optimization and resulting hyperparameter values can be found at GitHub.
+
+Simulations were carried out in ASReview, version 0.9.3 [@ASReview2020].
 Analyses were carried out using \texttt{R}, version 3.6.1 [@RCoreTeam2019].
-Scripts and data are stored in the GitHub repository for this thesis^[https://github.com/GerbrichFerdinands/asreview-thesis].The output resulting from the simulation was stored on the Open Science Framework page of this thesis ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far.
+Scripts and data are stored in the GitHub repository for this paper^[https://github.com/asreview/paper-evaluating-models-across-research-areas].The output resulting from the simulation was stored on the Open Science Framework page of this paper ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far.
 Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
@@
 
-## Datasets 
+### Datasets 
 The models were simulated on a convenience sample of six systematic review datasets.
-The data selection process was driven by three factors.
-Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas.
-Secondly, datasets were selected by their availability, given the limited timespan of the current project.
-Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).
-
-Datasets were collected from the fields of medicine, virology, software engineering, behavioural public administration, and pyschology to assess generalizability of the models across research contexts.
+The data selection process was driven by two factors.
+Firstly, datasets were collected from various research areas to assess generalizability of the models across research contexts (RQ3).
+Secondly, all original data files should be openly published with a CC-BY license.
+
+todo to different section. and are available through the [ $\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).
+
+The models are simulated on a convenience sample of six systematic review datasets.
+The data selection process was driven by two factors.
+Firstly, datasets are collected from various research areas to assess generalizability of the models across research contexts (RQ3).
+Secondly, all original data files have to be openly published with a CC-BY license.
+Datasets are available through this paper’s GitHub page.
+
 The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
-From the same scientific field, the Ace dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
-From _virology_, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
-From the field of _software engineering_, the Software dataset contains publications from a review on fault prediction in source code [@Hall2012].
-The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the area of _behavioural public administration_.
-The PTSD dataset contains publications from the field of _psychology_.
-The corresponding systematic review is on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
-Of these six datasets, Ace, and Software have been used for model simulations in previous studies on ML-aided title and abstract screening, respectively [@Cohen2006] and [@Yu2018].
-
-Data were preprocessed from their original source into a test dataset, containing title and abstract of the publications obtained in the initial search.
+From the same scientific field, the ACE dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
+Additionally, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
+From the field of _computer science_, the Software dataset contains publications from a review on fault prediction in software engineering [@Hall2012].
+The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the _humanities_.
+From _social science_, the PTSD dataset contains publications on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
+Of these six datasets, ACE and Software have been used for model simulations in previous studies on ML-aided title and abstract screening [@Cohen2006; @Yu2018].
+
+Data were preprocessed from their original source into a dataset, containing title and abstract of the publications obtained in the initial search.
 Candidate studies with missing abstracts and duplicate instances were removed from the data.
-Preprocessing scripts and resulting datasets can be found on the GitHub repository for this thesis.
-Test datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
-All test datasets consisted of thousands of candidate studies, of which only only a fraction was deemed relevant to the systematic review.
+Preprocessing scripts and resulting datasets can be found at GitHub repository for this paper.
+Datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
+All datasets consisted of thousands of candidate studies, of which only a fraction was deemed relevant to the systematic review.
 For the Virus and the Nudging dataset, the inclusion rate was about 5 percent.
@@
 
-```{r}
+```{r, results = 'asis'}
 # datasets table
@@
        )
+
+test <- 
+datastats %>%
+  select(dataset, candidates_test, incl_test) %>%
+  mutate(excl = candidates_test - incl_test)
+
+test <- rbind(test,test) %>%
+  mutate(relevancy = c(rep("incl", 6), rep("excl", 6))) 
+a <- c(test[1:6,"incl_test"], test[7:12, "excl"])
+test[,"number"] <- c(a$incl_test, a$excl)
+```
+
+```{r, results = 'asis', caption = "Datasets obtained from six original systematic reviews.", eval = FALSE}
+test %>%
+  ggplot(aes(x=dataset, y = number, fill = relevancy)) +
+  geom_col(position = "stack") +
+  # scale_fill_brewer(palette="Set1") +
+  scale_fill_manual(values= c("#CC6666","#66CC99"))+
+  theme_bw() +
+  theme(legend.position = "none") +
+  labs(y="Candidate studies", x = "") +
+  coord_flip()
+
+#ggsave("datasets.png")
 ```
@@
 datastats <- datastats[c(2,3,4,1,5,6), ]
+datastats[datastats == "Ace"] <- "ACE"
 saveRDS(datastats, "tables/tab1_data.RDS")
@@
 
-## Evaluating performance
+### Evaluating performance
 Model performance was assessed by three different measures, Work Saved over Sampling (WSS), Relevant References Found (RRF), and Average Time to Discovery (ATD). 
-
 WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006].
-Typically measured at a recall level of 0.95 [@Cohen2006], WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
+Typically measured at a recall level of 0.95, WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
 In the current study, WSS is computed at 0.95 recall.
-RRF statistics are computed at 10%, representing the proportion of relevant publications that are found after screening 10% of all publications.
-
-Both RRF and WSS are sensitive to random effects as these statistics are strongly dependent on the position of the cutoff value.
+RRF@10 represents the proportion of relevant publications that are found after screening 10% of all publications.
+
+Both RRF and WSS are sensitive to the position of the cutoff value.
 Moreover, WSS makes assumptions about acceptable recall levels whereas this level might depend on the research question at hand [@OMara-Eves2015].
-A statistic that is not dependent on some arbitrary cutoff value is the ATD, which indicates the average proportion of publications needed to screen to find a relevant publication.
+Therefore, we introduce the ATD, the average proportion of publications needed to screen to find a relevant publication.
+The ATD is an indicator of performance throughout the entire screening process instead of performance at some arbitrary cutoff value.
 
@@
 The curves give information in two directions.
-On the one hand they display the number of publications that need to be screened to achieve a certain level of recall (1-WSS), but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
-Moreover, the recall curves relate to the ATD in such a way that the area above the curve is equal to the ATD.
-
-For every simulation, the RRF@10, WSS@95, and ATD are reported as means over 15 trials.
+On the one hand they display the number of publications that need to be screened to achieve a certain level of recall, but on the other hand they present how many relevant publications are identified after screening a certain proportion of all publications (RRF).
+
+For each simulation, the RRF@10, WSS@95, and ATD are reported as means over 15 trials.
 To indicate the spread of performance within simulations, the means are accompanied by an estimated^[The metrics for all individual 15 trials deviate slightly from the overal mean over 15 trials because of pre-averaging in the \texttt{ASReview} source code.
 As the analyses across all trials did not produce information on the 15 separate runs, the standard deviation of the mean, $\hat s$, was estimated by computing the standard deviation within the individual 15 trials.] standard devation $\hat s$.
-To compare overall performance across datasets, median performance is reported for every dataset, accompanied by the Median Absolute Deviation (MAD), indicating variability between models within a certain dataset.
-Recall curves are plot for every simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.
+To compare the overall performance across datasets, median performance is reported for every dataset, accompanied by the Median Absolute Deviation (MAD), indicating variability between models within a certain dataset.
+Recall curves are plot for each simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.
 
 # Results 
-This section proceeds as follows.
-Firstly, the results of the Nudging dataset are discussed in detail to provide a basis for answering the research questions.
+This section proceeds as follows: Firstly, the results of the Nudging dataset are discussed in detail to provide a basis for answering the research questions.
 Secondly, the results are presented for each research question over all datasets.
@@
     select(model, nudging, ptsd, software, ace, virus, wilson)
-  names(tab) <- c("", "Nudging", "PTSD", "Software", "Ace", "Virus", "Wilson")
+  names(tab) <- c("", "Nudging", "PTSD", "Software", "ACE", "Virus", "Wilson")
   return(tab)
@@
 The curves represent the average recall over 15 trials $\pm$ the standard error of the mean in the direction of the y-axis.
-The x-axis is cut off at 40% since all for simulations, the models reached 95% recall after screening 40% of the publications.
+The x-axis is cut off at 40% since at this point in screening all models had already reached 95% recall.
 The dashed horizontal lines indicate the RRF@10 values, the dashed vertical lines the WSS@95 values.
-The recall curves relate to the ATD such that ATD is equal to the area above the curve.
 The dashed grey diagonal line corresponds to the expected recall curve when publications are screened in a random order.
@@
 Figure 1b shows a subset of the recall curves in Figure 1a, namely the curves for the first four models only to allow for a visual comparison across classification techniques adopting the TF-IDF feature extraction strategy.
-Figure 1c shows recall curves for the remaining three models to compare the models using Doc2vec feature extraction.
-Figures 1d-f plot recall curves for models adopting the TF-IDF feature extraction strategy to recall curves for their Doc2vec-using counterparts to allow for a comparison between models adopting TF-IDF and models adopting Doc2vec feature extraction.
+Figure 1c shows recall curves for the remaining three models to compare the models using D2V feature extraction.
+Figures 1d to 1f plot recall curves for models adopting the TF-IDF feature extraction strategy to recall curves for their D2V-using counterparts to allow for a comparison between models adopting TF-IDF and models adopting D2V feature extraction.
 
@@
 <!-- provides the RRF@10 values for all model-dataset combinations.  -->
-It can be seen from the data in the first column of `r table_nums("atd", display = "cite")` that in terms of ATD, the best performing models on the Nudging dataset were SVM + D2V and LR + D2V, both with an ATD of 8.9%.
+It can be seen from `r table_nums("atd", display = "cite")` that in terms of ATD, the best performing models on the Nudging dataset were SVM + D2V and LR + D2V, both with an ATD of 8.9%.
 This indicates that the average proportion of publications needed to screen to find a relevant publication was 8.9% for both models.
@@
 
-As `r table_nums("wss", display = "cite")` shows, the highest WSS@95 value on the Nudging dataset was achieved by the NB + TF-IDF model with a mean of 71.7, meaning that this model reduced the number of publications needed to screen with 71.7% at the cost of losing 5% of relevant publications.
-The estimated standard deviation of 1.37 indicates that in terms of WSS@95, this model performed the most stable across trials.
+As `r table_nums("wss", display = "cite")` shows, the highest WSS@95 value on the Nudging dataset was achieved by the NB + TF-IDF model with a mean of 71.7%, meaning that this model reduced the number of publications needed to screen with 71.7% at the cost of losing 5% of relevant publications.
+The estimated standard deviation of 1.37% indicates that in terms of WSS@95, this model performed the most stable across trials.
 The model with the lowest WSS@95 value was RF + TF-IDF ($\bar x$ = 64.9, $\hat s =$ 2.50).
@@
   colformat_char(j=1) %>%
-  set_header_labels(wss.95_ace = "Ace", wss.95_nudging = "Nudging", wss.95_ptsd = "PTSD", wss.95_software = "Software", wss.95_virus = "Virus", wss.95_wilson = "Wilson") %>%
+  set_header_labels(wss.95_ace = "ACE", wss.95_nudging = "Nudging", wss.95_ptsd = "PTSD", wss.95_software = "Software", wss.95_virus = "Virus", wss.95_wilson = "Wilson") %>%
   theme_booktabs() %>%
@@
   colformat_char(j=1) %>%
-    set_header_labels(rrf.10_ace = "Ace", rrf.10_nudging = "Nudging", rrf.10_ptsd = "PTSD", rrf.10_software = "Software", rrf.10_virus = "Virus", rrf.10_wilson = "Wilson") %>%
+    set_header_labels(rrf.10_ace = "ACE", rrf.10_nudging = "Nudging", rrf.10_ptsd = "PTSD", rrf.10_software = "Software", rrf.10_virus = "Virus", rrf.10_wilson = "Wilson") %>%
 
@@
   colformat_char(j=1) %>%
-  set_header_labels(loss_ace = "Ace", loss_nudging = "Nudging", loss_ptsd = "PTSD",loss_software = "Software", loss_virus = "Virus", loss_wilson = "Wilson") %>%
+  set_header_labels(loss_ace = "ACE", loss_nudging = "Nudging", loss_ptsd = "PTSD",loss_software = "Software", loss_virus = "Virus", loss_wilson = "Wilson") %>%
   theme_booktabs() %>%
@@
 ```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for all  indicating how fast the model finds relevant publications during the process of screening publications.
-on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
+on (a) the PTSD, (b) Software, (c) ACE, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","ACE","Virus","Wilson")}
 d <- c("ptsd", "software", "ace", "virus", "wilson")
 files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
+
 include_graphics(files)
@@
 The first reserach question was aimed at evaluating the first four models adopting either the NB, SVM, LR or RF classification technique, combined with TF-IDF feature extraction.
-When comparing ATD-values of the models (Table 2), the NB + TF-IDF model ranked first in the Ace, Nudging, PTSD, Virus and Wilson dataset, and second in the PTSD and the Software dataset, in which the LR + TF-IDF model achieved the lowest ATD value.
-The RF + TF-IDF ranked last in all of the datasets except in the Ace dataset, where the SVM + TF-IDF model achieved the highest ATD-value.
+When comparing ATD-values of the models (Table 2), the NB + TF-IDF model ranked first in the ACE, Nudging, PTSD, Virus and Wilson dataset, and second in the PTSD and the Software dataset, in which the LR + TF-IDF model achieved the lowest ATD value.
+The RF + TF-IDF ranked last in all of the datasets except in the ACE dataset, where the SVM + TF-IDF model achieved the highest ATD-value.
 
@@
 Additionally, in terms of WSS@95 (Table 3) the ranking of models was strikingly similar across all datasets.
-In the Ace, Nudging, Software, and Virus dataset, the highest WSS@95 value was always achieved by the NB + TF-IDF model, followed by LR + TF-IDF, SVM + TF-IDF, and RF + TF-IDF.
+In the ACE, Nudging, Software, and Virus dataset, the highest WSS@95 value was always achieved by the NB + TF-IDF model, followed by LR + TF-IDF, SVM + TF-IDF, and RF + TF-IDF.
 In the PTSD dataset this ranking applied as well, except that the LR + TF-IDF and NB + TF-IDF showed equal WSS@95 values.
@@
 ```
-Moreover, in terms of RRF@10 (Table 4) the NB + TF-IDF model achieved the highest RRF@10 value in the Ace, Nudging, and Wilson dataset.
+Moreover, in terms of RRF@10 (Table 4) the NB + TF-IDF model achieved the highest RRF@10 value in the ACE, Nudging, and Wilson dataset.
 LR + TF-IDF ranked first in the PTSD dataset, SVM + TF-IDF was the best performing model within the Wilson dataset.
-The RF + TF-IDF model was again the worst performing model within all datasets, with on exception for the Software dataset.
+The RF + TF-IDF model was again the worst performing model within all datasets, with an exception for the Software dataset.
 In this dataset, NB + TF-IDF ranked fourth, the remaining three models achieved an equal RRF@10 score.
 
-Taken together, these results show that while all four models perform quite well, the NB + TF-IDF shows high performance on all measures across all datasets, whereas the RF + TF-IDF model never performd best on any of the measures across all datasets.
+Taken together, these results show that while all four models perform quite well, the NB + TF-IDF shows high performance on all measures across all datasets, whereas the RF + TF-IDF model never performed best on any of the measures across all datasets.
 <!-- The RF + TF-IDF model did not perform well on any of the datasets.
@@
 ### RQ2 - Comparison across feature extraction techniques
-The following section is concerned with the question of how models using different feature extraction strategies relate to each other.
-The recall curves for the Nudging data (Figure 1d-f) show a clear trend of the models adopting Doc2vec feature extraction outperforming their TF-IDF counterparts.
+This section is concerned with the question of how models using different feature extraction strategies relate to each other.
+The recall curves for the Nudging data (Figure 1d-f) show a clear trend of the models adopting D2V feature extraction outperforming their TF-IDF counterparts.
 This trend also shows from the WSS@95 and RRF@10 values indicated by the vertical and horizontal lines in the figure.
-Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting Doc2vec feature extraction always achieved a smaller ATD-value than the model adopting TF-IDF feature extraction.
-
-In contrast, this pattern of models adopting Doc2vec outperforming their TF-IDF counterparts in the Nudging dataset does not replicate across other datasets.
+Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting D2V feature extraction always achieved a smaller ATD-value than the model adopting TF-IDF feature extraction.
+
+In contrast, this pattern of models adopting D2V outperforming their TF-IDF counterparts in the Nudging dataset does not replicate across other datasets.
 Whether evaluated in terms of recall curves, WSS@95, RRF@10 or ATD, the findings were mixed.
@@
 First of all, models showed much higher performance for some datasets than for others.
-While performance on the PTSD (Figure 2a) and the Software dataset (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.
-There does not seem to be a clear distinction between the datasets from the biomedical sciences (Ace, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, Software).
-The PTSD, Software and Nudging dataset also demonstrated high performance in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
-
-Secondly, variability of model performance differed across datasets.
+Whilst performances on the PTSD (Figure 2a) and the Software dataset (Figure 2b) were quite high, performances were much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.
+There does not seem to be a clear distinction between the datasets from the biomedical sciences (ACE, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, Software).
+The PTSD, Software and Nudging dataset also demonstrated high performances in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
+
+Secondly, variability of between-model performance differed across datasets.
 For the PTSD (Figure 2a), Software (Figure 2b), and the Virus (Figure 2d) datasets, recall curves form a tight group meaning that within these datasets, the models perform relatively similar.
-For the Nudging (Figure 1a), Ace (Figure 2c), and Wilson (Figure 2e) dataset, the recall curves are much further apart, indicating that model performace is much more dependent on the classification technique and feature extraction strategy.
-The MAD values of the ATD, WSS@95 and RRF@10 confirm that within the PTSD, Software and Virus datasets, model performance is less spread out than within the Nudging, Ace and Wilson dataset.
-
-Moreover, the curves for the Ace (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared to other the other datasets.
-For these datasets, model performance seemed to be more dependent on the initial training dataset compared to other datasets.
+For the Nudging (Figure 1a), ACE (Figure 2c), and Wilson (Figure 2e) dataset, the recall curves are much further apart, indicating that model performance is much more dependent on the classification technique and feature extraction strategy.
+The MAD values of the ATD, WSS@95 and RRF@10 confirm that within the PTSD, Software and Virus datasets, model performance is less spread out than within the Nudging, ACE and Wilson dataset.
+
+Moreover, the curves for the ACE (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared to other the other datasets.
+For these datasets, model performance seemed to be more dependent on the initial training dataset compared to others.
 
@@
 at <- c("@95", "@10", "")
-Data <- c("Ace", "Nudging", "PTSD", "Software", "Virus", "Wilson")
+Data <- c("ACE", "Nudging", "PTSD", "Software", "Virus", "Wilson")
 
@@
 
+## Active learning-based screening prioritization
 Overall, the findings confirm the great potential of active learning models in reducing workload for systematic reviewers.
 All models were able to detect 95% of the relevant publications after screening less than 40% of the total number of publications, indicating that active learning models can save more than half of the workload in the screening process.
-In a previous study, the Ace dataset was used to simulate a model that did not use active learning, finding a WSS@95 value of 56.61% [@Cohen2006], whereas the models in the current study achieved far superior WSS@95 values varying from 68.6% to 82.9% in this dataset.
+In a previous study, the ACE dataset was used to simulate a model that did not use active learning, finding a WSS@95 value of 56.61% [@Cohen2006], whereas the models in the current study achieved far superior WSS@95 values varying from 68.6% to 82.9% in this dataset.
 Active learning models clearly outperformed a model which did not use active learning.
@@
 The most obvious finding to emerge from these evaluations was that the NB + TF-IDF model consistently performed as one of the best models.
-The results suggest that whilst the widely used SVM-classifier performed fairly well, LR and NB classification strategies are interesting if not superior alternatives to the standard in this field.
+The results suggest that whilst SVM - the classifier standardly used in software tools for active learning in systematic reviews - performed fairly well, the LR and NB classification techniques are good if not superior alternatives.
+Note that NB and LR were always good methods for text classifciation tasks [@Mitchell1997].
 <!-- Across simulations the NB + TF-IDF model demonstrated high performance on  -->
@@
 ### Feature extraction strategy 
-The overall results on models adopting Doc2vec versus TF-IDF feature extraction strategy remain inconclusive.
-According to these findings, adopting Doc2vec instead of the well-established TF-IDF feature extraction strategy does not lead to better performing models.
-Given these results, although preliminary, preference goes out to teh TF-IDF feature extraction technique as this relatively simplistic technique will lead to more interpretable model.
+The overall results on models adopting D2V versus TF-IDF feature extraction strategy remain inconclusive.
+According to these findings, adopting D2V instead of the well-established TF-IDF feature extraction strategy does not lead to better performing models.
+Given these results, although preliminary, preference goes out to the TF-IDF feature extraction technique as this relatively simplistic technique will lead to more interpretable model.
 
@@
 It has been suggested that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014].
-This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, Ace) was not in any way superior to performance within the datasets from the social sciences (PTSD and Nudging).
+This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, ACE) was not in any way superior to performance within the datasets from the social sciences (PTSD and Nudging).
 An issue that emerges from these findings is that difficulty of active learning was not confined to any particular research area.
@@
 # Conclusions 
-Overall, the findings of this study confirm that active learning models show great potential of finding relevant publications in a systematic review dataset, while minimizing the number of publications needed to screen.
-The results shed new light on the performance of different classification techniques, indicating that the Naive Bayes classification technique is superior to the widely used Support Vector Machine.
-As model performance differs vastly across datasets, this study raises the question what causes models to yield more workload savings for some systematic review datasets than for others.
+Overall, the findings of this study confirm that active learning models show great potential of retrieving relevant publications in a systematic review dataset, while minimizing the number of publications needed to screen.
+The results shed new light on the performance of different classification techniques, indicating that the NB classification technique is superior to the widely used SVM As model performance differs vastly across datasets, this study raises the question what causes models to yield more workload savings for some systematic review datasets than for others.
 In order to facilitate the applicability of active learning models in systematic review practice, it is essential to identify how dataset characteristics relate to model performance.
@@
 # Declarations
+## List of abbreviations
+
+ATD
+
+D2V
+LR
+MAD
+ML
+NB
+PTSD
+RF
+RRF
+SD
+SEM
+SVM
+TF-IDF
+WSS
 
 ## Ethics approval and consent to participate
-Was reported in the main text.
+This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
 
@@
 ## Availability of data and materials 
-As reported in the main text, all data and materials are available through the GitHub repository for this thesis, https://github.com/GerbrichFerdinands/asreview-thesis.
+As reported in the main text, all data and materials are available through the GitHub repository for this paper, https://github.com/asreview/paper-evaluating-models-across-research-areas.
 This repository contains all systematic review datasets used during this study and their preprocessing scripts, scripts and data on the hyperparamter optimization, scripts on the simulations, scripts for analyzing the results of the simulations, and the source files for this manuscript.
-All output files of the simulation study are stored on the Open Science Framework page of this thesis, https://osf.io/7mr2g/.
+All output files of the simulation study are stored on the Open Science Framework page of this paper, https://osf.io/7mr2g/.
 
@@
 
+## Author's contributions
+RS developed the DR balance strategy and ATD metric.
+
+All authors read and approved the final manuscript.
+
 ## Acknowledgements
@@
 I would also like to thank dr.
-Caroline van Baal for supporting me in writing this thesis, and prof.
+Caroline van Baal for supporting me in writing this paper, and prof.
 dr.
-René Eijkemans, for being the second grader of this thesis.
-Finally, I would like to express my appreciation to my supervisors prof.
+René Eijkemans, for being the second grader of this paper Finally, I would like to express my appreciation to my supervisors prof.
 dr.
@@
 # Additional file 1 
-Recall curves plot separately for the PTSD, Software, Ace, Virus and Wilson datasets.
+Recall curves plot separately for the PTSD, Software, ACE, Virus and Wilson datasets.
 
@@
 
-## Ace
-```{r, fig-sub-ace, fig.cap = "Recall curves for the Ace dataset.
+## ACE
+```{r, fig-sub-ace, fig.cap = "Recall curves for the ACE dataset.
 ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }

### 2020-07-20 manuscript/manuscript/simulation_study_results.Rmd
corrctions July 20 2020

@@
 bibliography: asreview.bib
+csl: elsevier-vancouver.csl
 ---
@@
 ## Results
+The figures below shows the recall curves of simulations for all model-dataset combinations.
+These curves plot recall as a function of the proportion of publications screened.
+The curves represent the average recall over 15 trials $\pm$ the standard error of the mean in the direction of the y-axis.
+The x-axis is cut off at 40% since all for simulations, the models reached 95% recall after screening 40% of the publications.
+The dashed horizontal lines indicate the RRF@10 values, the dashed vertical lines the WSS@95 values.
+The dashed grey diagonal line corresponds to the expected recall curve when publications are screened in a random order.
+
 First of all, models showed much higher performance for some datasets than for others.

### 2020-07-20 simulation_study/hpoptimization/README.Rmd
update simulations
corrctions July 20 2020

@@
 ```{bash, eval = FALSE}
-asreview hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d ace
+asreview hyper-active -t 12:00:00 -m nb -b double -e tfidf -q max -d ../../datasets/test_datasets/ace
 ```
@@
   labs(title = "Loss plot", x = "Trials sorted from high to low loss") +
-    theme_minimal()
+    theme_bw() + 
+    theme(legend.position = 'none')
+
 }
@@
     labs(title = "Loss plot", x = "Over trials") +
-    theme_minimal()
+    theme_bw() +
+    theme(legend.position = 'none')
+
 }
@@
   loss_t()
+```
+
+```{r}
+
+nbtfidftrials$group <-  relevel(nbtfidftrials$group , "one")
+
+nbtfidftrials %>%
+  filter(group == "one") %>%
+    ggplot(aes(x = trial, y = loss)) +
+    geom_line(aes(group = datasets, colour = datasets), lineend = "round", alpha = 0.8) + 
+    geom_dl(aes(label = datasets, size = 2), colour = "black", method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
+  #geom_label(aes(label = datasets, colour = datasets)) +
+  scale_colour_viridis_d() +
+    labs(title = "Optimizing hyperparameters through a random search", x = "Over trials") +
+  scale_x_continuous(limits = c(0,6000)) +
+    theme_bw() +
+    theme(legend.position = 'none')
+
+nbtfidftrials %>%
+  filter(group == "one") %>%
+  ggplot(aes(x = index, y = loss)) +
+  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
+ scale_fill_manual(values= c("#CC6666","#66CC99"))+
+  labs(title = "Optimizing hyperparameters through a random search", x = "Trials sorted from high to low loss") +
+    theme_bw() + 
+    theme(legend.position = 'none')
+
+nbtfidftrials %>%
+   filter(group != "n") %>%
+  ggplot(aes(x = index, y = loss)) +
+  geom_line(aes(group = datasets, colour = group), lineend = "round") + 
+  geom_dl(aes(label = datasets, colour = group), method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) + 
+ scale_fill_manual(values= c("#CC6666","#66CC99"))+
+  labs(title = "Optimizing hyperparameters through a random search", x = "Trials sorted from high to low loss") +
+  theme_bw() + 
+  theme(legend.position = 'none')
+
+nbtfidftrials %>%
+  filter(group == "n-1") %>%
+    ggplot(aes(x = trial, y = loss)) +
+    geom_line(aes(group = datasets, colour = datasets), lineend = "round", alpha = 0.8) + 
+    geom_dl(aes(label = datasets, size = 2), colour = "black", method = list(dl.trans(x = x + 0.2), dl.combine("last.points"), cex = 0.8)) +
+  #geom_label(aes(label = datasets, colour = datasets)) +
+  scale_colour_viridis_d() +
+    labs(title = "Optimizing hyperparameters through a random search", x = "Over trials") +
+  scale_x_continuous(limits = c(0,2000)) +
+    theme_bw() +
+    theme(legend.position = 'none')
+
 ```

### 2020-07-29 manuscript/manuscript/Ferdinands, G - MSBBSS.Rmd
update 29-07 corrections

@@
 ---
-title: Active learning for efficient systematic reviews
-subtitle: Evaluating models across research areas 
-author: "Gerbrich Ferdinands"
-# keywords:
+title: Active learning for screening prioritization in systematic reviews
+subtitle: A simulation study
+author: 
+    - Gerbrich Ferdinands
+    - Raoul Schram
+    - Jonathan de Bruin
+    - Ayoub Bagheri
+    - Daniel Oberski
+    - Lars Tummers
+    - Rens van de Schoot
+date: '`r format(Sys.time(), "%d %B, %Y")`'
 header-includes:
     - \usepackage{setspace}\doublespacing
-    - \usepackage[left]{lineno}
-    - \usepackage{amssymb}
-date: '`r format(Sys.time(), "%d %B, %Y")`'
+
 output:
   bookdown::pdf_document2:
-    extra_dependencies: subfig, algorithm2e, float
+    extra_dependencies: subfig, algorithm2e, float, lineno, setspace, amssymb
     number_sections: no
@@
 link-citations: yes
-csl: elsevier-vancouver.csl
+csl: systematic-reviews.csl
 ---
@@
 <!-- --- -->
-<!-- title: Manuscript drafts -->
-<!-- author: "Gerbrich Ferdinands" -->
+<!-- title: Interactive screening prioritization in systematic reviews by employing active learning -->
+<!-- subtitle: A comprehensive study -->
+<!-- author:  -->
+<!--     - Gerbrich Ferdinands -->
+<!--     - Raoul Schram -->
+<!--     - Jonathan de Bruin -->
+<!--     - Ayoub Bagheri -->
+<!--     - Daniel Oberski -->
+<!--     - Lars Tummers -->
+<!--     - Rens van de Schoot -->
 <!-- date: '`r format(Sys.time(), "%d %B, %Y")`' -->
+<!-- header-includes: -->
+<!--     - \usepackage{setspace}\doublespacing -->
 <!-- output: -->
-
+<!--   word_document: default -->
 <!--   bookdown::pdf_document2: -->
-<!--     extra_dependencies: subfig, algorithm2e, float -->
+<!--     extra_dependencies: subfig, algorithm2e, float, lineno, setspace, amssymb -->
 <!--     number_sections: no -->
 <!--     toc: no -->
-<!--   word_document: default -->
 <!-- bibliography: asreview.bib -->
@@
 <!-- csl: systematic-reviews.csl -->
+<!-- --- -->
 
@@
 table_nums(name = "datasets", caption = "Statistics on the datasets obtained from six original systematic reviews.")
-table_nums(name = "atd", caption = "ATD values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
-table_nums(name = "wss", caption = "WSS@95 values ($\\bar x (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
-table_nums(name = "rrf", caption = "RRF@10 values ($\\bar x, (\\hat s)$) for all model-dataset combinations, and median (MAD) for all datasets.")
-
-```
-
-\newpage
+table_nums(name = "atd", caption = "ATD values ($\\bar x (\\hat s)$) for all model-dataset combinations. For every dataset, the best results are in bold. Median (MAD) is given for all datasets.")
+table_nums(name = "wss", caption = "WSS@95 values ($\\bar x (\\hat s)$) for all model-dataset combinations. For every dataset, the best results are in bold. Median (MAD) is given for all datasets.")
+table_nums(name = "rrf", caption = "RRF@10 values ($\\bar x, (\\hat s)$) for all model-dataset combinations. For every dataset, the best results are in bold. Median (MAD) is given for all datasets.")
+
+```
 
@@
 #### Background
-the context and purpose of the study
+Conducting a systematic review requires great screening effort.
+Various tools have been proposed to speed up the process of screening thousands of titles and abstracts by engaging in active learning.
+In active learning, the reviewer interacts with machine learning software to identify relevant publications as early as possible.
+To gain a comprehensive understanding of active learning models for reducing workload in systematic reviews, the current study provides an methodical overview of such models.
+Active learning models were evaluated across four different classification techniques (naive Bayes, logistic regression, support vector machines, and random forest) and two different feature extraction strategies (TF-IDF and Doc2vec).
+Moreover, models were evaluated across six systematic review datasets from various research areas to assess generalizability of active learning models across different research contexts.
 
 #### Methods
-how the study was performed and statistical tests used
+Performance of the models were assessed by conducting simulations on six systematic review datasets.
+We defined desirable model performance as maximizing recall while minimizing the number of publications needed to screen.
+Model performance was evaluated by recall curves, WSS@95, RRF@10, and ATD.
 
 #### Results
-the main findings
+Within all datasets, the model performance exceeded screening at random order to a great degree, reducing the number of publications needed to screen by 91.7% to 63.9%.
+Overall, the Naive Bayes + TF-IDF model performed the best.
 
 #### Conclusions
-brief summary and potential implications
-
-keywords:
+Active learning models for screening prioritization show great potential in reducing the workload of systematic reviewers.
+<!-- Model performance differs vastly across datasets, and the naive Bayes classifier is a  -->
+<!-- The results shed new light on the performance of different classification techniques, indicating that the NB classification technique is superior to the widely used SVM.
+As model performance differs vastly across datasets,  -->
+<!-- To facilitate the usability of active learning models in systematic review practice, it is essential to identify how dataset characteristics relate to model performance. -->
+
+__keywords:__ systematic reviews, active learning, screening prioritization, researcher-in-the-loop, title-and-abstract screening
+
+<!-- #### Background  -->
+<!-- the context and purpose of the study -->
+
+<!-- context: -->
+<!-- active learning models for reducing workload in title and abstract screening in systematic reviews. -->
+
+<!-- This study adds to existing literature by evaluating models across four different classification techniques (Naive Bayes, Logistic Regression, Support Vector Machine, and Random Forest) and two different feature extraction strategies (TF-IDF and Doc2vec).
+Moreover, as previous studies have paid little attention to the generalizability of active learning models across different research contexts, models were evaluated across six systematic review datasets from various research areas.
+-->
+<!-- purpose  -->
+
+<!-- The purpose of the current paper is to increase the evidence base on active learning models for reducing workload in title and abstract screening in systematic reviews.  -->
+
+<!-- for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.  -->
+
+<!--  We adopt four different classification techniques (Naive Bayes, Logistic Regression, Support Vector Machine, and Random Forest) and two different feature extraction strategies (TF-IDF and Doc2vec) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
+-->
+
+<!-- #### Methods -->
+<!-- how the study was performed and statistical tests used -->
+
+<!-- Models were assessed by conducting a simulation on six systematic review datasets. -->
+<!-- To assess generalizability of the models across research contexts, datasets were collected from the fields of medical science, computer science, humanities and social science,  -->
+
+<!-- Desirable model performance was defined as maximizing recall while minimizing the number of publications needed to screen. (WSS@95 recall curves RRF@10 ATD) -->
+
+<!-- #### Results -->
+<!-- the main findings -->
+
+<!-- Across all classification techniques, feature extraction strategies and review contexts, active learning models exceeded screening at random order by far.  -->
+
+<!-- #### Conclusions -->
+<!-- brief summary and potential implications -->
+
+<!-- As all models exceeded screening at random order by far, they show great potential in reducing workload of systematic reviewers.  -->
+
+<!-- implications: researchers can use this  -->
+
+\newpage
 
@@
 Systematic reviews are top of the bill in research.
-A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015].
+A systematic review brings together all available studies relevant to answer a specific research question [@PRISMA-PGroup2015].
 Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007].
-However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.
+However, systematic reviews are costly because to identify publications relevant to answering the research question, they among else involve the manual screening of thousands of titles and abstracts.
 
@@
 Currently, the demand for systematic reviews exceeds the available time and resources by far [@Lau2019].
-Especially when the need for guidelines is urgent it is extremely challenging to provide a review that is both timely and comprehensive.
-
-To ensure a timely review, reducing workload in systematic reviews is essential.
-With advances in Machine Learning (ML), there has been wide interest in tools to reduce workload in systematic reviews [@Harrison2020].
-Various learning models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
-Previous findings suggest that such models potentially reduce workload with 30-70% at the cost of losing 5% of relevant publications, i.e.
-95% recall [@OMara-Eves2015].
+Especially when answering the research question at hand is urgent, it is extremely challenging to provide a review that is both timely and comprehensive.
+
+To ensure a timely review, reducing the workload in systematic reviews is essential.
+With advances in machine learning (ML), there has been wide interest in tools to reduce the workload in systematic reviews [@Harrison2020].
+Various ML models have been proposed, aiming to predict whether a given publication is relevant or irrelevant to the systematic review.
+Previous findings suggest that such models potentially reduce the workload with 30-70% at the cost of losing 5% of relevant publications, in else, a 95% recall [@OMara-Eves2015].
 <!-- To date, several studies have begun to examine the use of learning algorithms for screening prioritization. -->
 
-A well-established approach in increasing efficiency in title and abstract screening is screening prioritization [@Cohen2009; @Shemilt2014].
-In screening prioritization, the learning model presents the reviewer with the publications that are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
-Such an approach allows for substantial time-savings in the screening process as the reviewer can decide to stop screening after a sufficient number of relevant publications have been retrieved [@Yu2019].
+A well-established approach to increase the efficiency of title and abstract screening is screening prioritization [@Cohen2009; @Shemilt2014].
+In screening prioritization, the ML model presents the reviewer with the publications that are most likely to be relevant first, thereby expediting the process of finding all of the relevant publications.
+Such an approach allows for substantial time-savings in the screening process as the reviewer can decide to stop screening after a sufficient number of relevant publications have been found [@Yu2019].
 Moreover, the early retrieval of relevant publications facilitates a faster transition of those publications to the next steps in the review process [@Cohen2009].
@@
 Recent studies have demonstrated the effectiveness of screening prioritization by means of active learning models [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Gates2018a].
-With active learning, the ML model can iteratively improve its predictions on unlabelled data by allowing the model to select the records from which it wants to learn [@Settles2012].
-The model queries these records to a human annotator who provides them with a label, from which the model then updates its predictions.
+With active learning, the ML model can iteratively improve its predictions on unlabeled data by allowing the model to select the records from which it wants to learn [@Settles2012].
+The model proposes these records to a human annotator who provides the records with labels, which the model then uses to update its predictions.
 The general assumption is that by letting the model select which records are labelled, the model can achieve higher accuracy more quickly while requiring the human annotator to label as few records as possible [@Settles2009].
-Active learning has proven to be an efficient strategy in large unlabelled datasets where labels are expensive to obtain [@Settles2009].
-This makes the screening phase in systematic reviewing an ideal candidate solution for such models because typically, labelling a large number of publications is very costly.
+Active learning has proven to be an efficient strategy in large unlabeled datasets where labels are expensive to obtain [@Settles2009].
+This makes the screening phase in systematic reviewing an ideal candidate solution for such models, because typically labelling a large number of publications is very costly.
+
 When active learning is applied in the screening phase, the reviewer screens publications that are suggested by an active learning model.
@@
 <!-- Combined with some sort of stopping criterion, the reviewer c -->
-<!-- _Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies.
-meaning the screening process can be finished after reading a fraction of all candidate studies.
+<!-- _Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate publications.
+meaning the screening process can be finished after reading a fraction of all candidate publications.
 Saving hours of time and resources._ -->
@@
 
-The application of active learning models in reducing workload of systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
-Whilst previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Singh2018; @Carvallo; @Yimin2007], ready-to-use software tools implementing such active learning models (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]) currently use the same classification technique to predict relevance of publications, namely Support Vector Machine (SVM).
-Findings show that different classification techniques can serve different needs in the retrieval of relevant publications, for example the desired balance between recall and precision [@Kilicoglu2009; @Aphinyanaphongs2004].
-Therefore, is essential to evaluate different classification techniques in the context of active learning models.
-The current study investigates active learning models adopting four classification techniques: Naive Bayes, Logistic Regression, Support Vector Machine, and Random Forest.
+The application of active learning models in systematic reviews has been extensively studied [@Yu2018; @Yu2019; @Miwa2014; @Wallace2010; @Gates2018a].
+While previous studies have evaluated active learning models in many forms and shapes [@Yu2018; @Yu2019; @Miwa2014; @Cormack2014; @Cormack2015; @Wallace2010; @Singh2018; @Carvallo; @Yimin2007], ready-to-use software tools implementing such models (Abstrackr [@Wallace2012b], Colandr [@Cheng2018], FASTREAD [@Yu2018], Rayyan [@Ouzzani2016], and RobotAnalyst [@Przybyla2018]) currently use the same classification technique to predict relevance of publications, namely support vector machines (SVM).
+It was found [@Kilicoglu2009; @Aphinyanaphongs2004] that different classification techniques can serve different needs in the retrieval of relevant publications, for example the desired balance between recall and precision.
+Therefore, it is essential to evaluate different classification techniques in the context of active learning models.
+The current study investigates active learning models adopting four classification techniques: naive Bayes (NB), logistic regression (LR), SVM, and random forest (RF).
 These are widely adopted techniques in text classification [@Aggarwal2012] and are suitable for creating interpretable ML models [@Molnar2020].
-Moreover, due to their relatively short computation time they are fit for software tools to be used in scientific practice, as they allow the reviewer to be timely presented with the next publication.
+Moreover, due to their relatively short computation time they are fit for software tools to be used in scientific practice.
+
+<!-- as they allow the reviewer to be timely presented with the next publication.  -->
 
@@
 <!-- Since a plethora of techniques exist [@Aggarwal2012], it would be of interest to incorporate such models to this area as well.  -->
-Another component that influences model performance is the way how the textual content of titles and abstracts are represented in a model, called the feature extraction strategy [@Zhang2011; @Carvallo; @Singh2018].
-One of the more sophisticated feature extraction strategies is called Doc2vec (D2V), also known as Paragraph vector [@Le2014].
+Another component that influences model performance is how the textual content of titles and abstracts is represented in a model, called the feature extraction strategy [@Zhang2011; @Carvallo; @Singh2018].
+One of the more sophisticated feature extraction strategies is Doc2vec (D2V), also known as paragraph vectors [@Le2014].
 D2V learns continuous distributed vector representations for pieces of text.
-The idea of distributed representation is that every word can be known by its neighborhood.
-D2V can overcome problems with more simplistic feature extraction strategies such as TF-IDF, which ignores the the semantics and the ordering of the words [@Le2014].
-Therefore, it is of interest to compare models adopting D2V to models adopting TF-IDF.
+In distributed text representations, words are assumed to appear in the same context when they are similar in terms of a latent space, the “embedding”.
+A word embedding is simply a vector of scores estimated from a corpus for each word; D2V is an extension of this idea to document embeddings.
+Embeddings can sometimes outperform simpler feature extraction strategies such as term frequency-inverse document frequency (TF-IDF).
+They can be trained on large corpora to capture wider semantics and subsequently applied in a specific systematic reviewing application [@Le2014].
+Therefore, it is interesting to compare models adopting D2V to models adopting TF-IDF.
 
@@
 
-Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] and computer science [@Yu2018, @Yu2019].
-Model replications on reviews from varying research contexts are essential to draw conclusions about the general effectiveness of active learning models [@OMara-Eves2015; @Marshall2020].
-As far as known to the authors, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between two systematic reviews from different research areas, namely the social and the medical sciences.
-They found that active learning was more difficult on data from the social sciences due to the different nature of the vocabularies used.
-Thus, it is of interest to evaluate model performance across different research contexts, namely the social science, humanities, medical science and computer science.
+Lastly, previous studies have mainly focussed on reviews from a single scientific field, like medicine [@Wallace2010; @Gates2018a] or computer science [@Yu2018, @Yu2019].
+To draw conclusions about the general effectiveness of active learning models, it is essential to evaluate models on reviews from varying research contexts [@OMara-Eves2015; @Marshall2020].
+To our knowledge, Miwa et al [@Miwa2014] were the only researchers to make a direct comparison between systematic reviews from different research areas, such as the social and the medical sciences.
+They found that the application of active learning to systematic reviews was more difficult on a systematic review from the social sciences due to the different nature of the vocabularies used.
+Thus, it is of interest to evaluate model performance across different research contexts, namely social science, medical science and computer science.
 
@@
 
-|    __RQ1__ What is the performance of active learning models across four different classification techniques?
-|    __RQ2__ What is the performance of active learning models across two different feature extraction strategies? 
-|    __RQ3__ Does the performance of active learning models differ across six systematic reviews from four different research areas?
-
-The purpose of the current paper is to increase the evidence base on active learning models for reducing workload in title and abstract screening in systematic reviews.
+__RQ1__ What is the performance of active learning models across four classification techniques?
+__RQ2__ What is the performance of active learning models across two feature extraction strategies? 
+__RQ3__ Does the performance of active learning models differ across six systematic reviews from four research areas?
+
+The purpose of this paper is to show the usefulness of active learning models for reducing workload in title and abstract screening in systematic reviews.
 We adopt four different classification techniques (NB, LR, SVM, and RF) and two different feature extraction strategies (TF-IDF and D2V) for the purpose of maximizing the number of identified relevant publications, while minimizing the number of publications needed to screen.
 Models were assessed by conducting a simulation on six systematic review datasets.
-Datasets were collected from the fields of medical science [@Cohen2006; @Appenzeller-Herzog2019; @Kwok2020], computer science [@Yu2018], humanities [@Nagtegaal2019] and social science [@vandeSchoot2017], to assess generalizability of the models across research contexts.
+To assess generalizability of the models across research contexts, datasets containing previous systeamtic reviews were collected from the fields of medical science [@Cohen2006; @Appenzeller-Herzog2019; @Kwok2020], computer science [@Yu2018], and social science [@Nagtegaal2019; @vandeSchoot2017].
 The models, datasets and simulations are implemented in a pipeline of active learning for screening prioritization, called $\texttt{ASReview}$ [@vandeSchoot2020].
 $\texttt{ASReview}$ is an open source and generic tool in which users can adapt and add modules as they like, encouraging fellow researchers to replicate findings from previous studies.
-All scripts and data used are openly published to facilitate usability and acceptability of ML-assisted title and abstract screening in the field of systematic review.
-
-The remaining part of this paper is organized as follows.
+To facilitate usability and acceptability of ML-assisted title and abstract screening in the field of systematic review our scripts and data used are openly available.
+
+<!-- The remaining part of this paper is organized as follows.
 The methods section describes the study that was designed to answer the research questions and elaborates on the technical details of active learning models for identifying relevant publications in the context of systematic reviews.
@@
 The implications of the findings in context of previous research are discussed in the discussion section, followed by this study's main conclusions in the conclusion section.
+-->
 
@@
 ## Technical details 
-What follows is a more detailed account of the active learning models.
+<!-- What follows is a more detailed account of the active learning models.
 The structure and functions of the key components of the models are introduced to clarify the choices made in the design of the current study.
+-->
+What follows is a more detailed account of the active learning models to clarify the choices made in the design of the current study.
 
@@
 The task is to identify which of these publications are relevant, by screening their titles and abstracts.
-In active learning for screening prioritization, the screening process proceeds as follows:
+In _active learning_ for screening prioritization, the screening process proceeds as follows:
 
@@
 <!-- \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output} -->
-<!-- \Input{Write here the input} -->
-<!-- \Output{Write here the output} -->
+<!-- \Input{Record IDs in screening order} -->
+<!-- \Output{Average Time to Discovery} -->
 <!-- \BlankLine -->
+<!--  # inclusions -->
+<!--  one_labels = np.where(labels == 1)[0] -->
+<!--  # store discovery time -->
+<!--  time_results = {label: [] for label in one_labels} -->
+
 <!-- \While{While condition}{ -->
@@
 
-- Start with the set of all unlabelled records (titles and abstracts), $\mathcal{U}$.
-- The reviewer provides a label for a few, for example 5-10 records $x \in \mathcal{U}$, creating a set of labelled records $x \in \mathcal{L}$ such that $x \notin \mathcal{U}$.
+- Start with the set of all unlabeled records (titles and abstracts), $\mathcal{U}$.
+- The reviewer provides a label for a few, e.g.
+5-10 records $x \in \mathcal{U}$, creating a set of labelled records $x \in \mathcal{L}$ such that $x \notin \mathcal{U}$.
 The label can be either Relevant $\langle x, \texttt{R}\rangle$ or Irrelevant $\langle x, \texttt{I}\rangle$.
@@
 
-  1. A classifier $C$ is trained on the labelled records $\mathcal{L}$, $C = \texttt{train}(\mathcal{L})$
-
-  2. The classifier predicts relevancy scores for all unlabelled records $\mathcal{U}$, $C(\mathcal{U})$
+  1. A classifier $C$ is trained on the labelled records $\mathcal{L}$; $C = \texttt{train}(\mathcal{L})$
+
+  2. The classifier predicts relevancy scores for all unlabeled records $\mathcal{U}$, $C(\mathcal{U})$
 
@@
 
-  4. The model queries the reviewer to screen this record, $\langle x^*, \texttt{?}\rangle$
+  4. The model requests the reviewer to screen this record, $\langle x^*, \texttt{?}\rangle$
 
@@
 
-In this active learning cycle, the model incrementally improves its predictions on the remaining unlabelled title and abstracts.
+In this active learning cycle, the model incrementally improves its predictions on the remaining unlabeled title and abstracts.
 Relevant titles and abstracts are identified as early in the process as possible.
@@
 This case is an example of pool-based active learning, as the next record to be queried is selected by predicting relevancy for all records in a fixed pool [@Settles2012].
-Another form of active learning is stream-based active learning, in which data is regarded as a stream instead of a fixed pool, in which the model selects one record at a time and then decides whether or not to query this record.
+Another form of active learning is stream-based active learning, in which the data is regarded as a stream instead of a fixed pool, in which the model selects one record at a time and then decides whether or not to query this record.
 This approach of active learning is preferred when it is expensive or impossible to exhaustively search the data for selecting the next query.
 A possible application of stream-based active learning is living systematic reviews, as the review is continually updated as new evidence becomes available.
-For an example see the study by Wynants et al., @Wynants2020.
+For an example see the study by Wynants et al @Wynants2020.
 
 ### Class imbalance problem
-There are two classes in the dataset: relevant and irrelevant publications.
-Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94%, [@Borah2017]).
-The class imbalance causes the classifier to miss relevant publications, because there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015].
+<!-- There are two classes in the dataset: relevant and irrelevant publications.  -->
+Typically, only a fraction of the publications belong to the relevant class (2.94%, [@Borah2017]).
+To some extent, this fraction is under the control of the researcher through the search criteria: if the researcher narrows the search query, it will generally result in a higher proportion of relevant publications.
+However, in most applications this practice would yield an unacceptable number of false negatives (erroneously excluded papers) in the querying phase of the review process.
+For this reason, the query phase in most practical applications would typically yield a very low percentage of relevant publications.
+In the discussion, we will provide some further remarks on the interplay among query scope and subsequent active machine learning in the abstract screening phase.
+Because there are genearlly far fewer examples of relevant than irrelevant publications to train on, the class imbalance causes the classifier to miss relevant publications [@OMara-Eves2015].
 Moreover, classifiers can achieve high accuracy but still fail to identify any of the relevant publications [@Wallace2010].
-This is evident in the case of a systematic review dataset where only three percent of publications are relevant.
+
+<!-- This is evident in the case of a systematic review dataset where only three percent of publications are relevant.  -->
 
@@
 Previous studies have addressed the class imbalance problem by rebalancing the training data in various ways [@OMara-Eves2015].
-To decrease the class imbalance in the training data, the models in the current study rebalance the training set by a technique we propose to call Dynamic Resampling (DR).
+To decrease the class imbalance in the training data, we rebalance the training set by a technique we propose to call "dynamic resampling" (DR).
 DR undersamples the number of irrelevant publications in the training data, whereas the number of relevant publications are oversampled such that the size of the training data remains the same.
-The ratio between relevant and irrelevant publications in the rebalanced training data is not fixed, but dynamically updated depending on the number of publications in the available training data, the total number of publications in the dataset, and the ratio between relevant and irrelevant publications in the available training data.
+The ratio between relevant and irrelevant publications in the rebalanced training data is not fixed, but dynamically updated and depends on the number of publications in the available training data, the total number of publications in the dataset, and the ratio between relevant and irrelevant publications in the available training data.
+Additional file 1 provides a detailed script to perform DR.
 
@@
 ### Classification
-To make predictions on the unlabelled publications, a classifier is trained on features from the training data. The performance of the following four classifiers is explored:
-<!-- The classifier predicts class of a given unlabelled publication.  -->
+To make relevancy predictions on the unlabeled publications, a classifier is trained on features from the training data. The performance of the following four classifiers is explored:
+<!-- The classifier predicts class of a given unlabeled publication.  -->
 <!-- Whilst the SVM is a well-known technique, also classifiers have been employed in class prediction tasks in systematic reviews.  -->
@@
 
- - Support Vector Machine (SVM) - SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
-
- - L2-regularized Logistic Regression (LR) models the probabilities describing the possible outcomes by a logistic function. The coefficients are regularizes/model is regularized. 
- A penalty is imposed on the size of the coefficients, shrinking coefficients of features with a minor contribution to the solution towards zero.
+ - Support vector machines (SVM) - SVMs separate the data into classes by finding a multidimensional hyperplane [@Tong2001; @Kremer2014].
+
+ - L2-regularized logistic regression (LR) - models the probabilities describing the possible outcomes by a logistic function.
+The classifier uses regularization, shrinking coefficients of features with small contributions to the solution towards zero.
+
+<!-- A penalty is imposed on the size of the coefficients, shrinking coefficients of features with a minor contribution to the solution towards zero. -->
 
@@
 
-- Random Forests (RF) is a supervised learning algorithm where a large number of decision trees are fit on bootstrapped samples of the original data.
-All trees cast a vote on the class, which are aggregated into a class prediction for each instance [@Breiman2001].
+- Random forests (RF) is a supervised learning algorithm where a large number of decision trees are fit on samples obtained from the original data by sampling both rows (bootstrapped samples) and columns (feature samples).
+In prediction mode, each tree casts a vote on the class, and the final prediction is the class that received the most votes [@Breiman2001].
 
@@
 To predict relevance of a given publication, the classifier uses information from the publications in the dataset.
-Examples of such information are titles and abstracts.
-However, a model cannot make predictions from the titles and abstracts as they are; their textual content needs to be represented numerically.
-The textual information needs to be mapped to feature vectors.
+Examples of information are titles and abstracts.
+However, a model cannot make predictions from the titles and abstracts as they are; their textual content needs to be represented numerically as feature vectors.
 This process of numerically representing textual content is referred to as 'feature extraction'.
 
-Term-Frequency Inverse Document Frequency (TF-IDF) stores the term frequency - the number of occurrences of each word - for each text in the dataset.
-The term frequency is adjusted with the inverse document frequency, the number of documents which contain the given word [@Ramos2003].
-A disadvantage of TF-IDF and other bag-of-words methods is that they do not take the ordering of words into account, thereby ignoring semantics.
-An example of an approach that aims to overcome this weakness is D2V.
-D2V learns continuous distributed vector representations for pieces of text capable of grasping semantics by learning to predict the words in the texts [@Le2014].
+TF-IDF is a specific way of assigning scores to the cells of the “document-term matrix” used in all bag-of-words representations.
+That is, the rows of the document-term matrix represent the documents (titles and abstracts) and the columns represent all words in the dictionary.
+Instead of simply counting the number of times each word occurred in the given document, TF-IDF assigns a score to a word relative to the number of documents the word occurs in.
+<!-- assigns high scores only when a word occurs especially often, relative to its overall frequency across all documents.  -->
+The idea behind weighting words by their rarity is that surprising word choices should subsequently make for more discriminative features [@Ramos2003].
+A disadvantage of TF-IDF and other bag-of-words methods is that they do not take the ordering of words into account, thereby ignoring syntax.
+However, in practice, TF-IDF is often found to be a strong baseline [@Shahmirzadi2019].
+
+In recent years, a range of modern methods have been developed that often outperform bag-of-words approaches.
+Here, we consider doc2vec, an extension of the classic word2vec embedding [@Le2014].
+In word embedding models, whether a word did or did not happen to appear in a specific context is predicted by its similarity to that context in a latent space - the “embedding”.
+The context is usually a sliding window across training sentences.
+For example, if the window “child ate cookies” occurs in the training data, this might be compared with a random ‘negative’ window that did not occur, such as  “child lovely cookies”.
+In this example, the word “lovely” was chosen as a randomly sampled “negative” example with about the same word frequency as “ate”.
+The tokens “child” and “cookies” are then assigned scores (vectors) that give a higher inner product with the “child” vector, and a smaller product with “lovely”.
+The word vectors of “ate” and “lovely” are similarly updated.
+Typically the embedding dimension is a few hundred, i.e.
+each word vector contains some two hundred scores.
+Note that if “cookies” previously co-occurred frequently with “spinach”, then the above also indirectly makes “ate” more similar to “spinach”, even though these two words were not observed in the same context yet.
+Thus, the distributed representation learns something of the meaning of these words through their occurrence in similar contexts.
+D2V performs the above procedure while including a paragraph identifier, allowing for paragraph embeddings - or, in our case, embeddings for titles and abstracts.
+In short, D2V converts each abstract into a vector of a few hundred scores, which can be used to predict inclusion or exclusion.
 
@@
 close to 0.5 probability [@Settles2012].
-Traditionally, this strategy trains the most accurate model because the model can learn the most from instances it is uncertain about.
-However, a study comparing the performance of both strategies in detecting relevant publications found that the accuracy gain of uncertainty-based screening was not significant [@Miwa2014].
-
-Certainty-based active learning is the preferred strategy for the task at hand.
-Firstly, the aim of the screening process is to find relevant publications, not to train a good model.
-Secondly, certainty-based active learning is far better equipped at dealing with imbalanced data in active learning, as it aims to present only records that belong to the relevant class [@Fu2011].
+Further strategies include selecting the next instance to optimize for various criteria, including: model fit (MLI), model change (MMC), parameter estimate accuracy (EVR), and expected (EER) or worst-case (MER) prediction accuracy [@Yang2018].
+Although uncertainty sampling is not explicitly motivated by the optimization of any particular criterion, intuitively it can be seen as attempting to improve the model’s accuracy by reducing uncertainty about its parameter estimates.
+
+Simulation-based comparisons of these methods across different domains have yielded an equivocal picture of their relative strengths [@Miwa2014; @Yang2018].
+What has become clear from such studies is that the features of the task at hand determine the effectiveness of active learning strategies (“no free active lunch”).
+For example, if a linear classifier is used for a task that also happens to have a Bayes optimal linear decision boundary, a model-based approach such as Fisher information reduction can be expected to perform well, whereas the same technique can be disastrous when the model is misspecified - a fact that cannot be known in advance.
+Furthermore, the criteria mentioned above differ from the task of semi-automated abstract screening: here, the aim is not to obtain an accurate model, but rather to end up with a list of records belonging to the relevant class [@Fu2011].
+This is the criterion corresponding intuitively to certainty-based sampling.
+For this reason, we choose to focus on certainty-based sampling strategies as the baseline strategy for active learning in systematic reviewing.
+However, different strategies may outperform our baseline in specific applications.
 
 ## Simulation study
-The section below describes the simulation study that was carried out to answer the research questions.
+This section describes the simulation study that was carried out to answer the research questions.
 
 ### Set-up
-To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:
+To address RQ1, four models were investigated combining each classifier with TF-IDF feature extraction:
 
@@
 
-To address __RQ2__, the classifiers were combined with D2V feature extraction, leading to the following three models:
+To address RQ2, the classifiers were combined with D2V feature extraction, leading to the following three combinations:
 
@@
 
-The combination NB + D2V could not be tested because the multinomial naive Bayes classifier^[https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB] can only handle a feature matrix with positive values, whereas the D2V feature extraction approach^[https://radimrehurek.com/gensim/models/doc2vec.html] produces a feature matrix that can also contain negative values.
-The performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing __RQ3__.
+The combination NB + D2V could not be tested because the multinomial naive Bayes classifier
+^[https://scikit-learn.org/stable/modules/generated/sklearn.naive_bayes.MultinomialNB.html#sklearn.naive_bayes.MultinomialNB] requires a feature matrix with positive values, whereas the D2V feature extraction approach^[https://radimrehurek.com/gensim/models/doc2vec.html] produces a feature matrix that can contain negative values.
+The performance of the seven models was evaluated by simulating every model on six systematic review datasets, addressing RQ3.
 Hence, 42 simulations were carried out, representing all model-dataset combinations.
@@
 Instead of having a human reviewer label publications manually, the screening process was simulated by retrieving the labels in the data.
-Each simulation started with an initial training set of one relevant and one irrelevant publication to represent a 'worst case scenario' where the reviewer has minimal prior knowledge on the publications in the data.
-The model was retrained every time after a publication had been labelled.
+Each simulation started with an initial training set of one relevant and one irrelevant publication to represent a challenging scenario where the reviewer has very little prior knowledge on the publications in the data.
+The model was retrained each time after a publication had been labelled.
 A simulation ended after all publications in the dataset had been labelled.
-To account for sampling variance, each simulation was repeated 15 times.
+To account for sampling variance, every simulation was repeated 15 times.
 To account for bias due to the content of the initial publications, the initial training set was randomly sampled from the dataset for each of the 15 trials.
-Although varying over trials, the 15 initial training sets were kept constant over datasets to allow for a direct comparison of models within datasets.
+Although varying over trials, the 15 initial training sets were kept constant for each dataset to allow for a direct comparison of models within datasets.
 A seed value was set to ensure reproducibility.
-The simulation study was carried out using the \texttt{ASReview} simulation extension [@ASReview2020].
-For each simulation, hyperparameters were optimized through a ...
-tpe to arrive at maximum model performance.
-todo
+The simulation study was carried out using the ASReview simulation extension [@ASReview2020].
+For each simulation, hyperparameters were optimized through a Tree
+of Parzen Estimators (TPE) algorithm [@Bergstra2013] to arrive at maximum model performance.
 <!-- About a 1000 runs, retraining after labelling 20, after visual inspection.  --> 
-Scripts for the hyperparaemter optimization and resulting hyperparameter values can be found at GitHub.
-
-Simulations were carried out in ASReview, version 0.9.3 [@ASReview2020].
-Analyses were carried out using \texttt{R}, version 3.6.1 [@RCoreTeam2019].
-Scripts and data are stored in the GitHub repository for this paper^[https://github.com/asreview/paper-evaluating-models-across-research-areas].The output resulting from the simulation was stored on the Open Science Framework page of this paper ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far.
-Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer.
-Access was granted by SURF via a grant (ID EINF-156).
+<!-- Scripts for the hyperparaemter optimization and resulting hyperparameter values can be found at GitHub. -->
+
+Simulations were carried out in ASReview version 0.9.3 [@ASReview2020].
+Analyses were carried out using \texttt{R} version 3.6.1 [@RCoreTeam2019].
+The simulations were carried out on Cartesius, the Dutch national supercomputer.
 
@@
 The data selection process was driven by two factors.
-Firstly, datasets were collected from various research areas to assess generalizability of the models across research contexts (RQ3).
-Secondly, all original data files should be openly published with a CC-BY license.
-
-todo to different section. and are available through the [ $\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).
-
-The models are simulated on a convenience sample of six systematic review datasets.
-The data selection process was driven by two factors.
 Firstly, datasets are collected from various research areas to assess generalizability of the models across research contexts (RQ3).
 Secondly, all original data files have to be openly published with a CC-BY license.
-Datasets are available through this paper’s GitHub page.
-
-The Wilson dataset [@Appenzeller-Herzog2020] - from the field of _medicine_ - is on a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
-From the same scientific field, the ACE dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a drug treatment for heart disease [@Cohen2006].
+Datasets are available through ASReview's systematic review datasets GitHub^[https://github.com/asreview/systematic-review-datasets].
+
+The Wilson dataset [@Appenzeller-Herzog2020] - from the field of medicine - is from a review on the effectiveness and safety of treatments of Wilson Disease, a rare genetic disorder of copper metabolism [@Appenzeller-Herzog2019].
+From the same field, the ACE dataset contains publications on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors, a treatment drug for heart disease [@Cohen2006].
 Additionally, the Virus dataset is from a systematic review on studies that performed viral Metagenomic Next-Generation Sequencing (mNGS) in farm animals [@Kwok2020].
-From the field of _computer science_, the Software dataset contains publications from a review on fault prediction in software engineering [@Hall2012].
-The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the _humanities_.
-From _social science_, the PTSD dataset contains publications on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
+From the field of computer science, the Software dataset contains publications from a review on fault prediction in software engineering [@Hall2012].
+The Nudging dataset [@Nagtegaal2019a] belongs to a systematic review on nudging healthcare professionals [@Nagtegaal2019], stemming from the social sciences.
+From the same research area, the PTSD dataset contains publications on studies applying latent trajectory analyses on posttraumatic stress after exposure to traumatic events [@vandeSchoot2017].
 Of these six datasets, ACE and Software have been used for model simulations in previous studies on ML-aided title and abstract screening [@Cohen2006; @Yu2018].
@@
 Data were preprocessed from their original source into a dataset, containing title and abstract of the publications obtained in the initial search.
-Candidate studies with missing abstracts and duplicate instances were removed from the data.
-Preprocessing scripts and resulting datasets can be found at GitHub repository for this paper.
-Datasets were labelled to indicate which candidate studies were included in the systematic review, thereby indicating relevant publications.
-All datasets consisted of thousands of candidate studies, of which only a fraction was deemed relevant to the systematic review.
-For the Virus and the Nudging dataset, the inclusion rate was about 5 percent.
-For the remaining six datasets, inclusion rates were centered around 1-2 percent.
+Duplicates and publications with missing abstracts were removed from the data.
+<!-- Preprocessing scripts and resulting datasets can be found at GitHub repository for this paper.  -->
+Datasets were labelled to indicate which candidate publications were included in the systematic review, thereby denoting relevant publications.
+All datasets consisted of thousands of candidate publications, of which only a fraction was deemed relevant to the systematic review.
+For the Virus and the Nudging dataset, this proportion was about 5 percent.
+For the remaining six datasets, the proportions of relevant publications were centered around 1-2 percent.
 (`r table_nums("datasets", display = "cite")`).
@@
 test[,"number"] <- c(a$incl_test, a$excl)
+
 ```
@@
   theme(legend.position = "none") +
-  labs(y="Candidate studies", x = "") +
+  labs(y="candidate publications", x = "") +
   coord_flip()
@@
                                        "Relevant publications", 
-                                       "Inclusion rate (%)"),1))
+                                       "Proportion relevant (%)"),1))
 datastats <- datastats[c(2,3,4,1,5,6), ]
@@
       format.args = list(big.mark = ",", decimal.mark = "."))
+
+# 
+test <- xtable(datastats, digits = c(0,0,0,0,1))
+# 
+# library(pixiedust)
+# dust(test) %>%
+#    sprinkle(cols = 2, rows = 2, bold = TRUE) %>%
+#    sprinkle_print_method("latex") %>%
+#   print()
 ```
@@
 WSS indicates the reduction in publications needed to be screened, at a given level of recall [@Cohen2006].
-Typically measured at a recall level of 0.95, WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
-In the current study, WSS is computed at 0.95 recall.
+Typically measured at a recall level of 95%, WSS@95 yields an estimate of the amount of work that can be saved at the cost of failing to identify 5% of relevant publications.
+In the current study, WSS is computed at 95% recall.
 RRF@10 represents the proportion of relevant publications that are found after screening 10% of all publications.
 
-Both RRF and WSS are sensitive to the position of the cutoff value.
-Moreover, WSS makes assumptions about acceptable recall levels whereas this level might depend on the research question at hand [@OMara-Eves2015].
-Therefore, we introduce the ATD, the average proportion of publications needed to screen to find a relevant publication.
+Both RRF and WSS are sensitive to the position of the cutoff value and the distribution of the data.
+Moreover, WSS makes assumptions about the acceptable recall level whereas this level might depend on the research question at hand [@OMara-Eves2015].
+Therefore, we introduce the ATD, the average fraction of non-reviewed relevant publications during the review (except the relevant publications in the initial training set).
 The ATD is an indicator of performance throughout the entire screening process instead of performance at some arbitrary cutoff value.
+The ATD is computed by taking the average of the Time to Discovery (TD) of all relevant publications.
+The TD for a given relevant publication $i$ is computed as the fraction of publications needed to screen to detect $i$.
+Additional file 2 provides a detailed script to compute the ATD.
+<!-- proportion of publications needed to screen to find a relevant publication.  -->
 
@@
 For each simulation, the RRF@10, WSS@95, and ATD are reported as means over 15 trials.
-To indicate the spread of performance within simulations, the means are accompanied by an estimated^[The metrics for all individual 15 trials deviate slightly from the overal mean over 15 trials because of pre-averaging in the \texttt{ASReview} source code.
-As the analyses across all trials did not produce information on the 15 separate runs, the standard deviation of the mean, $\hat s$, was estimated by computing the standard deviation within the individual 15 trials.] standard devation $\hat s$.
+To indicate the spread of performance within simulations, the means are accompanied by a bootstrapped standard deviation $\hat s$.
 To compare the overall performance across datasets, median performance is reported for every dataset, accompanied by the Median Absolute Deviation (MAD), indicating variability between models within a certain dataset.
-Recall curves are plot for each simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.
+Recall curves are plotted for each simulation, representing the average recall over 15 trials $\pm$ the standard error of the mean.
+
+<!-- former footnote: -->
+ <!-- The metrics for individual trials of one simulation deviate slightly from the overall mean for one simulation because of pre-averaging in the source code.
+As the analyses across all trials did not produce information on the 15 separate trials, the standard deviation of the mean was estimated by bootstrapping the standard deviation of the 15 trials.
+-->
 
 # Results 
-This section proceeds as follows: Firstly, the results of the Nudging dataset are discussed in detail to provide a basis for answering the research questions.
+This section proceeds as follows: Firstly, as an example the results of the Nudging dataset are discussed in detail to provide a basis for answering the research questions.
 Secondly, the results are presented for each research question over all datasets.
@@
 Figure 1a shows the recall curves for all simulations on the Nudging dataset.
-As desribed in the previous section, these curves plot recall as a function of the proportion of publications screened.
+As described in the previous section, these curves plot recall as a function of the proportion of publications screened.
 The curves represent the average recall over 15 trials $\pm$ the standard error of the mean in the direction of the y-axis.
@@
 The dashed horizontal lines indicate the RRF@10 values, the dashed vertical lines the WSS@95 values.
-The dashed grey diagonal line corresponds to the expected recall curve when publications are screened in a random order.
-Desirable model performance was defined as maximizing recall while minimizing the number of publications needed to screen.
+The dashed black diagonal line corresponds to the expected recall curve when publications are screened in a random order.
+<!-- Desirable model performance was defined as maximizing recall while minimizing the number of publications needed to screen. -->
 
@@
 Hence, from screening 5 to 30 percent of publications, the RF + TF- IDF model was the slowest in finding the relevant publications.
-The ordering of the remaining recall curves changes throughout the screening process, but maintain to show relatively similar performance at face value.
-
-Figure 1b shows a subset of the recall curves in Figure 1a, namely the curves for the first four models only to allow for a visual comparison across classification techniques adopting the TF-IDF feature extraction strategy.
+The ordering of the remaining recall curves changes throughout the screening process, but maintain relatively similar performance at face value.
+
+Figure 1b shows a subset of the recall curves in Figure 1a, namely the curves of the first four models to allow for a visual comparison across classification techniques adopting the TF-IDF feature extraction strategy.
 Figure 1c shows recall curves for the remaining three models to compare the models using D2V feature extraction.
-Figures 1d to 1f plot recall curves for models adopting the TF-IDF feature extraction strategy to recall curves for their D2V-using counterparts to allow for a comparison between models adopting TF-IDF and models adopting D2V feature extraction.
+Figures 1d to 1f compare recall curves for models adopting the TF-IDF feature extraction strategy to recall curves for their D2V-using counterparts.
+
+<!-- to allow for a comparison between models adopting TF-IDF and models adopting D2V feature extraction.  -->
 
@@
 Figure a displays curves for all seven models at once.
-The remaining figures display curves for several subsets of those models to allow for a more detailed inspection.", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
+Figures b to f display curves for several subsets of those models to allow for a more detailed inspection of model performance.", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
 # path
@@
 This indicates that the average proportion of publications needed to screen to find a relevant publication was 8.9% for both models.
-In the SVM + D2V model, the standard deviation was 0.33 , whereas for the LR + D2V model $\hat s =$ 0.47.
-This indicates that for the SVM + D2V model, the ATD values of individual trials were closer to the overal mean compared to the LR + D2V model, meaning that the SVM + D2V model performed more stable across different initial training datasets.
-Median ATD for this dataset was 9.6% with an MAD of 1.06, indicating that for half of the models, the ATD was within 1.06 distance from the median ATD.
+In the SVM + D2V model, the standard deviation was 0.33, whereas for the LR + D2V model $\hat s =$ 0.47.
+This indicates that for the SVM + D2V model, the ATD values of individual trials were closer to the overall mean compared to the LR + D2V model, meaning that the SVM + D2V model performed more stable across different initial training datasets.
+Median ATD for this dataset was 9.6% with an MAD of 1.06, indicating that for half of the models, the ATD was within 1.06 percentage point distance from the median ATD.
 
@@
 
-print(xtable(tabatd, align = c("r", "r", rep("c", 6))), 
-      include.rownames=FALSE, comment = FALSE, booktabs = TRUE, hline.after = c(0,7))
-
-```
-
-As `r table_nums("wss", display = "cite")` shows, the highest WSS@95 value on the Nudging dataset was achieved by the NB + TF-IDF model with a mean of 71.7%, meaning that this model reduced the number of publications needed to screen with 71.7% at the cost of losing 5% of relevant publications.
-The estimated standard deviation of 1.37% indicates that in terms of WSS@95, this model performed the most stable across trials.
-The model with the lowest WSS@95 value was RF + TF-IDF ($\bar x$ = 64.9, $\hat s =$ 2.50).
-Median WSS@95 of these models was 66.9%, with a MAD of 3.05%, indicating that WSS@95 values of models varied the most within this dataset.
+# print(xtable(tabatd, align = c("r", "r", rep("c", 6))), 
+#       include.rownames=FALSE, comment = FALSE, booktabs = TRUE, hline.after = c(0,7))
+```
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rcccccc}
+  & Nudging & PTSD & Software & ACE & Virus & Wilson \\ 
+  \midrule
+SVM + TF-IDF & 10.2 (0.19) & 2.1 (0.13) & 1.9 (0.04) & 7.3 (1.18) & 8.5 (0.17) & 4.2 (0.33) \\ 
+  NB + TF-IDF & 9.4 (0.29) & 1.8 (0.11) & 1.5 (0.03) & \textbf{5.0 (0.53)} & \textbf{8.2 (0.22)} & \textbf{4.1 (0.37)} \\ 
+  RF + TF-IDF & 11.8 (0.44) & 3.4 (0.27) & 2.0 (0.09) & 7.0 (0.76) & 10.6 (0.42) & 5.9 (1.20) \\ 
+  LR + TF-IDF & 9.6 (0.19) & 1.7 (0.10) & \textbf{1.4 (0.02)} & 6.1 (1.20) & 8.4 (0.24) & 4.5 (0.34) \\ 
+  SVM + D2V & 8.9 (0.33) & 2.1 (0.15) & \textbf{1.4 (0.05)} & 6.2 (0.34) & 8.5 (0.21) & 4.7 (0.31) \\ 
+  RF + D2V & 10.4 (0.88) & 3.1 (0.34) & 1.6 (0.09) & 7.3 (1.29) & 9.3 (0.43) & 7.5 (1.56) \\ 
+  LR + D2V & \textbf{8.9 (0.47)} & 1.9 (0.17) & \textbf{1.4 (0.04)} & 5.6 (0.18) & 8.4 (0.41) & 4.9 (0.32) \\ 
+   \midrule
+median (MAD) & 9.6 (1.06) & 2.1 (0.49) & 1.5 (0.12) & 6.2 (1.14) & 8.5 (0.18) & 4.7 (0.66) \\ 
+  \end{tabular}
+\end{table}
+
+As `r table_nums("wss", display = "cite")` shows, the highest WSS@95 value on the Nudging dataset was achieved by the NB + TF-IDF model with a mean of 71.7%, meaning that this model reduced the number of publications needed to screen by 71.7% at the cost of losing 5% of relevant publications.
+The estimated standard deviation of 1.37 indicates that in terms of WSS@95, this model performed the most stable across trials.
+The model with the lowest WSS@95 value was RF + TF-IDF ($\bar x$ = 64.9%, $\hat s =$ 2.50).
+Median WSS@95 of these models was 66.9%, with a MAD of 3.05, indicating that of all datasets, the WSS@95 values of the models simulated on the Nudging dataset varied the most within the Nudging dataset.
 
@@
 `r table_nums("wss")`
-\end{center}
+
 ```{r, eval = TRUE, results="asis"}
@@
 ```
-
-As can be seen from the data in `r table_nums("rrf", display = "cite")`, LR + D2V was the best performing model in terms of RRF@10, with a mean of 67.5 indicating that after screening 10% of publications, on average 67.5% of all relevant publications had been identified, with a standard deviation of 2.59.
-The worst performing model was RF + TF-IDF ($\bar x =$ 53.6, $\hat s =$ 2.71).
-Median performance was 62.6, with an MAD of 3.89 indicating again that RRF@10 values were most dispersed for models within this dataset.
+\end{center}
+
+As can be seen from the data in `r table_nums("rrf", display = "cite")`, LR + D2V was the best performing model in terms of RRF@10, with a mean of 67.5% indicating that after screening 10% of publications, on average 67.5% of all relevant publications had been identified, with a standard deviation of 2.59.
+The worst performing model was RF + TF-IDF ($\bar x =$ 53.6%, $\hat s =$ 2.71).
+Median performance was 62.6%, with an MAD of 3.89 indicating again that of all datasets, the RRF@10 values were most dispersed for models simulated on the Nudging dataset.
 
@@
 Recall curves for the simulations on the five remaining datasets are presented in Figure 2.
-For the sake of conciseness, recall curves are only plotted once per dataset, like in Figure 1a.
-Please refer to Additional file 1 for figures presenting subsets of recall curves for the remaining datasets, like in Figure 1b-f.
-
-First of all, for all datasets, the models were able to detect the relevant publications much faster compared to when screening publications at random order as the recall curves exceed the expected recall at screening at random order by far.
+For the sake of conciseness, recall curves are only plotted once per dataset, like in Figure 1a for the Nudging dataset.
+Please refer to Additional file 3 for figures presenting subsets of recall curves for the remaining datasets, like in Figure 1b-f.
+
+First of all, as the recall curves exceed the expected recall at screening at random order by far for all datasets, the models were able to detect the relevant publications much faster compared to when screening publications at random order.
 Even the worst results outperform this reference condition.
@@
 
-Similar to the simulations on the Nudging dataset (Figure 1b), the ordering of recall curves changes throughout the screening process, indicating that model performance is dependent on the number of publications that have been screened.
-Moreover, the ordering of models in the Nudging dataset (Figure 1b) does not replicate on the remaining five datasets (Figure 2).
-
-```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for all  indicating how fast the model finds relevant publications during the process of screening publications.
-on (a) the PTSD, (b) Software, (c) ACE, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","ACE","Virus","Wilson")}
+Similar to the simulations on the Nudging dataset (Figure 1a), the ordering of recall curves changes throughout the screening process, indicating that some models perform better at the start of the screening phase whereas others models take the lead later on.
+<!-- model performance is dependent on the number of publications that have been screened.  -->
+Moreover, the ordering of models in the Nudging dataset (Figure 1a) is not replicated in the remaining five datasets (Figure 2).
+
+```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves of all seven models for (a) the PTSD, (b) Software, (c) ACE, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","ACE","Virus","Wilson")}
 d <- c("ptsd", "software", "ace", "virus", "wilson")
@@
 ### RQ1 - Comparison across classification techniques
-The first reserach question was aimed at evaluating the first four models adopting either the NB, SVM, LR or RF classification technique, combined with TF-IDF feature extraction.
-When comparing ATD-values of the models (Table 2), the NB + TF-IDF model ranked first in the ACE, Nudging, PTSD, Virus and Wilson dataset, and second in the PTSD and the Software dataset, in which the LR + TF-IDF model achieved the lowest ATD value.
-The RF + TF-IDF ranked last in all of the datasets except in the ACE dataset, where the SVM + TF-IDF model achieved the highest ATD-value.
+The first research question was aimed at evaluating the four models adopting either the NB, SVM, LR or RF classification technique combined with TF-IDF feature extraction.
+When comparing ATD-values of the models (Table 2), the NB + TF-IDF model ranked first in the ACE, Nudging, PTSD, Virus and Wilson dataset, and second in the PTSD and the Software dataset in which the LR + TF-IDF model achieved the lowest ATD value.
+The RF + TF-IDF ranked last in all of the datasets except for the ACE dataset, in which the SVM + TF-IDF model achieved the highest ATD-value.
 
@@
 ```
+
 Additionally, in terms of WSS@95 (Table 3) the ranking of models was strikingly similar across all datasets.
 In the ACE, Nudging, Software, and Virus dataset, the highest WSS@95 value was always achieved by the NB + TF-IDF model, followed by LR + TF-IDF, SVM + TF-IDF, and RF + TF-IDF.
-In the PTSD dataset this ranking applied as well, except that the LR + TF-IDF and NB + TF-IDF showed equal WSS@95 values.
+In the PTSD dataset this ranking applied as well, except that the LR + TF-IDF and NB + TF-IDF models showed the same WSS@95 value.
 The ordering of the models for the Wilson dataset was NB + TF-IDF, RF + TF-IDF, LR + TF-IDF and SVM + TF-IDF.
@@
 
-Taken together, these results show that while all four models perform quite well, the NB + TF-IDF shows high performance on all measures across all datasets, whereas the RF + TF-IDF model never performed best on any of the measures across all datasets.
+Taken together, these results show that while all four models perform quite well, the NB + TF-IDF model demonstrates high performance on all measures across all datasets, whereas the RF + TF-IDF model never performed best on any of the measures across all datasets.
 <!-- The RF + TF-IDF model did not perform well on any of the datasets.
@@
 This section is concerned with the question of how models using different feature extraction strategies relate to each other.
-The recall curves for the Nudging data (Figure 1d-f) show a clear trend of the models adopting D2V feature extraction outperforming their TF-IDF counterparts.
+The recall curves for the Nudging dataset (Figure 1d-f) show a clear trend of the models adopting D2V feature extraction outperforming their TF-IDF counterparts.
 This trend also shows from the WSS@95 and RRF@10 values indicated by the vertical and horizontal lines in the figure.
-Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the model adopting D2V feature extraction always achieved a smaller ATD-value than the model adopting TF-IDF feature extraction.
-
-In contrast, this pattern of models adopting D2V outperforming their TF-IDF counterparts in the Nudging dataset does not replicate across other datasets.
-Whether evaluated in terms of recall curves, WSS@95, RRF@10 or ATD, the findings were mixed.
+Likewise, the ATD values (Table 2) indicate that for the models adopting a particular classification technique, the models adopting D2V feature extraction always achieved a lower ATD-value than the model adopting TF-IDF feature extraction.
+
+In contrast, this pattern of models adopting D2V outperforming their TF-IDF counterparts in the Nudging dataset is not replicated across other datasets.
+Whether evaluated in terms of recall curves, WSS@95, RRF@10, or ATD, the findings were mixed.
 Neither one of the feature extraction strategies showed superior performance within certain datasets nor within certain classification techniques.
@@
 ### RQ3 - Comparison across research contexts 
-First of all, models showed much higher performance for some datasets than for others.
-Whilst performances on the PTSD (Figure 2a) and the Software dataset (Figure 2b) were quite high, performances were much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.
-There does not seem to be a clear distinction between the datasets from the biomedical sciences (ACE, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, Software).
-The PTSD, Software and Nudging dataset also demonstrated high performances in terms of the median ATD, WSS@95 and RRF@10 values for these models (Table 2, 3, and 4).
+First of all, models showed much higher recall curves for some datasets than for others.
+While performance of the PTSD (Figure 2a) and Software datasets (Figure 2b) was quite high, performance was much lower across models for the Nudging (Figure 1a) and Virus (Figure 2d) datasets.
+The models simulated on the PTSD and Software datasets also demonstrated high performances in terms of the median ATD, WSS@95, and RRF@10 values for these models (Table 2, 3, and 4).
 
 Secondly, variability of between-model performance differed across datasets.
-For the PTSD (Figure 2a), Software (Figure 2b), and the Virus (Figure 2d) datasets, recall curves form a tight group meaning that within these datasets, the models perform relatively similar.
-For the Nudging (Figure 1a), ACE (Figure 2c), and Wilson (Figure 2e) dataset, the recall curves are much further apart, indicating that model performance is much more dependent on the classification technique and feature extraction strategy.
-The MAD values of the ATD, WSS@95 and RRF@10 confirm that within the PTSD, Software and Virus datasets, model performance is less spread out than within the Nudging, ACE and Wilson dataset.
-
-Moreover, the curves for the ACE (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared to other the other datasets.
-For these datasets, model performance seemed to be more dependent on the initial training dataset compared to others.
+For the PTSD (Figure 2a), Software (Figure 2b), and the Virus (Figure 2d) datasets, recall curves form a tight group meaning that within these datasets, the models performed similarly In contrast, for the Nudging (Figure 1a), ACE (Figure 2c), and Wilson (Figure 2e) dataset, the recall curves are much further apart, indicating that model performance was more dependent on the adopted classification technique and feature extraction strategy.
+The MAD values of the ATD, WSS@95 and RRF@10 confirm that model performance is less spread out within the PTSD, Software, and Virus datasets than within the Nudging, ACE, and Wilson datasets.
+Moreover, the curves for the ACE (Figure 2c) and Wilson (Figure 2e) datasets show a larger standard error of the mean compared the other datasets.
+
+Taken together, although model performance is very data-dependent, there does not seem to be a distinction in performance between the datasets from the biomedical sciences (ACE, Virus, and Wilson) and datasets from other fields (Nudging, PTSD, and Software).
+<!-- Thus, for these datasets model performance was more dependent on the initial training dataset compared to others. -->
 
@@
 # Discussion 
-The current study set out to evaluate performance of active learning models for the purpose of identifying relevant publications in systematic review datasets. 
+The current study evaluates the performance of active learning models for the purpose of identifying relevant publications in systematic review datasets. 
 <!-- This study adds to existing literature by evaluating models across four different classification techniques and two different feature extraction strategies.
@@
 ## Active learning-based screening prioritization
-Overall, the findings confirm the great potential of active learning models in reducing workload for systematic reviewers.
+Overall, the findings confirm the great potential of active learning models to reduce the workload for systematic reviews.
 All models were able to detect 95% of the relevant publications after screening less than 40% of the total number of publications, indicating that active learning models can save more than half of the workload in the screening process.
 In a previous study, the ACE dataset was used to simulate a model that did not use active learning, finding a WSS@95 value of 56.61% [@Cohen2006], whereas the models in the current study achieved far superior WSS@95 values varying from 68.6% to 82.9% in this dataset.
-Active learning models clearly outperformed a model which did not use active learning.
-In addition, the Software dataset was used to simulate an active learning model [@Yu2018] and reached WSS@95 of 91%, strikingly similar the WSS@95 values found in the current study which ranged from 90.5% to 92.3%.
+<!-- Active learning models clearly outperformed this model that did not use active learning.  -->
+In another study [@Yu2018] that did use active learning, the Software dataset was used for simulation and a WSS@95 value of 91% was reached, strikingly similar to the values found in the current study which ranged from 90.5% to 92.3%.
 
@@
 The first research question in this study sought to evaluate models adopting different classification techniques.
-The most obvious finding to emerge from these evaluations was that the NB + TF-IDF model consistently performed as one of the best models.
-The results suggest that whilst SVM - the classifier standardly used in software tools for active learning in systematic reviews - performed fairly well, the LR and NB classification techniques are good if not superior alternatives.
-Note that NB and LR were always good methods for text classifciation tasks [@Mitchell1997].
+The most important finding to emerge from these evaluations was that the NB + TF-IDF model consistently performed as one of the best models.
+Our results suggest that while SVM performed fairly well, the LR and NB classification techniques are good if not superior alternatives to this default classifier in software tools.
+Note that LR and NB were always good methods for text classification tasks [@Mitchell1997].
 <!-- Across simulations the NB + TF-IDF model demonstrated high performance on  -->
@@
 The overall results on models adopting D2V versus TF-IDF feature extraction strategy remain inconclusive.
-According to these findings, adopting D2V instead of the well-established TF-IDF feature extraction strategy does not lead to better performing models.
-Given these results, although preliminary, preference goes out to the TF-IDF feature extraction technique as this relatively simplistic technique will lead to more interpretable model.
+According to our findings, models adopting D2V do not outperform models adopting the well-established TF-IDF feature extraction strategy.
+Given these results, preference goes out to the TF-IDF feature extraction technique as this relatively simple technique will lead to a model that is easier to interpret.
+Another advantage of this technique is its short computation time.
 
 ### Research contexts 
-Simulating models on a heterogenous collection of systematic review datasets revealed that model performance is very data-dependent.
-Within some datasets, models achieved much higher overall performance than within other datasets.
-Moreover, for some datasets, differences between models were much larger than for other datasets.
-It has been suggested that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014].
-This does not appear to be the case as performance within the biomedical datasets (Wilson, Virus, ACE) was not in any way superior to performance within the datasets from the social sciences (PTSD and Nudging).
-An issue that emerges from these findings is that difficulty of active learning was not confined to any particular research area.
-A possible explanation for this is that difficulty of active learning could be attributed to factors more directly related to the systematic review at hand, such as the inclusion rate and the complexity of inclusion criteria used to identify relevant publications [@Gates2018a; @Rathbone2015].
-Although the current study did not investigate the inclusion criteria of systematic reviews, the datasets on which the active learning models performed worst, Nudging and Virus, were interestingly also the datasets with the highest inclusion rates, 5.4% and 5.0%, respectively.
-
+Difficulty of applying active learning is not confined to any particular research area.
+The suggestion that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014] does not seem to be the case.
+<!-- Simulating models on a heterogenous collection of systematic review datasets revealed that model performance is very data-dependent. -->
+A possible explanation for this is that this difficulty has to be attributed to factors more directly related to the systematic review at hand, such as the proportion of relevant publications or the complexity of inclusion criteria used to identify relevant publications [@Gates2018a; @Rathbone2015].
+Although the current study did not investigate the inclusion criteria of systematic reviews, the datasets on which the active learning models performed worst, Nudging and Virus, were interestingly also the datasets with the highest proportion of relevant publications, 5.4% and 5.0%, respectively.
+<!-- For some datasets, models achieved much higher overall performance than for other datasets.
+Moreover, within some datasets, differences between models were much larger than within other datasets.
+-->
+<!-- It has been suggested that active learning is more difficult for datasets from the social sciences compared to data from the medical sciences [@Miwa2014].
+This does not appear to be the case as performance within the biomedical datasets was not in any way superior to performance within the datasets from the social sciences.
+-->
+<!-- An issue that emerges from our findings is that that difficulty of applying active learning is not confined to any particular research area.  -->
 <!-- as differences in model performance could not be linked to non-biomedical datasets only from the biomedical areas (Nudging, Virus, and Wilson) did not perform did the datasets in which models pachieved highest performance  -->
-
 <!-- although the nature of this study was rather exploratory, the results yield important insights on the ...  -->
-
 <!-- Since models are more data dependent than model dependent (although for some datasets model performance varies more widely than for others).
 Maybe it doesn't really matter which model you pick although if you want to be save, the nb is a one size fits all model.
-
 ## Strengths and limitations
@@
 The findings from this study has extended our knowledge on  -->
-
 <!-- what does this mean for reviewing?? save a lot of time ! -->
 <!-- and if you've limited screening time then why not use such an prioritization model.  -->
-
 <!-- This thesis adds to the existing knowledge on active learning models for sreening publications by evaluating  -->
@@
 <!-- what did we add to other research  -->
-
 <!-- We were able to reach WSS@95 of 63.9-91.7% (instead of 30-70 as stated in [@OMara-Eves2015]). Depending on the model-dataset combination.  -->
@@
 ## Limitations and future research
-When applied in systematic review practice, the succes of active learning models stands or falls down with the generalizability of model performance across unseen datasets.
-It is important to bear in mind that model hyperparameters were optimized for each model-dataset combination.
-Thus, the observed results reflect maximum model performance for the datasets at hand.
-The question remains whether model performance generalizes to datasets for which the hyperparameters were not optimized.
+When applied to systematic reviews, the success of active learning models stands or falls with the generalizability of model performance across unseen datasets.
+In our study, is important to bear in mind that model hyperparameters were optimized for each model-dataset combination.
+Thus, the observed results reflect the maximum model performance for each presented datasets.
+The question remains whether model performance generalizes to datasets for which the hyperparameters are not optimized.
 Further research should be undertaken to determine the sensitivity of model performance to the hyperparameter values.
 
-Additionally, whilst the sample of datasets in the current study is diverse compared to previous studies, the sample size does not allow for investigating how characteristics of the data - such as inclusion rate - relate to model performance.
-To build confidence in active learning models for screening publications, it is essential to identify how characteristics of the data influence model performance.
+Additionally, while the sample of datasets in the current study is diverse compared to previous studies, the sample size (n=6) does not allow for investigating how model performance relates to characteristics of the data, such as the proportion of relevant publications.
+To build more confidence in active learning models for screening publications, it is essential to identify how data characteristics affect model performance.
 Such a study requires more data on systematic reviews.
-Therefore, we call systematic reviewers to make an effort to openly publish their datasets.
+Thus, a more thorough study depends on researchers to openly publish their systematic review datasets.
 
@@
 
-An unanticipated finding was that the runtime of simulations varied widely across models, indicating that some models need more time to retrain after a publication has been labelled than other models.
-This finding has important implications for the practical application of such models, as an efficient model should be able to keep up with the decision-making speed of the reviewer.
-Further studies taking into account retraining time will need to be undertaken.
+Moreover, the runtime of simulations varied widely across models, indicating that some models take longer to retrain after a publication has been labelled than other models.
+This has important implications for the practical application of such models, as an efficient model should be able to keep up with the decision-making speed of the reviewer.
+Further studies should take into account the retraining time of models.
 
 <!-- Now that we know that the potential of models/that the models show good performance, the next step is to identify factors that drive performance.
-When the only information available is an unlabelled dataset and we only want to try one model,  When applied in practice, it is  -->
+When the only information available is an unlabeled dataset and we only want to try one model,  When applied in practice, it is  -->
 <!-- - challenge is how to define BEFORE knowing the answers, what the model is..
@@
 Overall, the findings of this study confirm that active learning models show great potential of retrieving relevant publications in a systematic review dataset, while minimizing the number of publications needed to screen.
-The results shed new light on the performance of different classification techniques, indicating that the NB classification technique is superior to the widely used SVM As model performance differs vastly across datasets, this study raises the question what causes models to yield more workload savings for some systematic review datasets than for others.
+The results shed new light on the performance of different classification techniques, indicating that the NB classification technique is superior to the widely used SVM.
+As model performance differs vastly across datasets, this study raises the question which factors cause models to yield more workload savings for some systematic review datasets than for others.
 In order to facilitate the applicability of active learning models in systematic review practice, it is essential to identify how dataset characteristics relate to model performance.
@@
 # Declarations
-## List of abbreviations
-
-ATD
-
-D2V
-LR
-MAD
-ML
-NB
-PTSD
-RF
-RRF
-SD
-SEM
-SVM
-TF-IDF
-WSS
-
-## Ethics approval and consent to participate
+
+### List of abbreviations
+ATD - Average Time to Discovery
+
+D2V - Doc2vec
+
+LR - Logistic regression
+
+MAD - Median Absolute Deviation
+
+ML - Machine Learning
+
+NB - Naive Bayes
+
+PTSD - Post Traumatic Stress Disorder
+
+RF - Random forest
+
+RRF - Relevant References Found
+
+SD - Standard Deviation
+
+SEM - Standard Error of the Mean
+
+SVM - Support vector machines
+
+TF-IDF - Term Frequency - Inverse Document Frequency
+
+TPE - Tree of Parzen Estimators
+
+TD - Time to Discovery
+
+WSS - Work Saved over Sampling
+
+### Ethics approval and consent to participate
 This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104.
 
-## Consent for publication
+### Consent for publication
 Not applicable.
 
-## Availability of data and materials 
-As reported in the main text, all data and materials are available through the GitHub repository for this paper, https://github.com/asreview/paper-evaluating-models-across-research-areas.
-This repository contains all systematic review datasets used during this study and their preprocessing scripts, scripts and data on the hyperparamter optimization, scripts on the simulations, scripts for analyzing the results of the simulations, and the source files for this manuscript.
-All output files of the simulation study are stored on the Open Science Framework page of this paper, https://osf.io/7mr2g/.
-
-## Competing interests
-The author declares that they has no competing interests.
-
-## Funding
-Computing hours on the Cartesius supercomputer were funded by SURFsara.
+### Availability of data and materials 
+All data and materials are stored in the GitHub repository for this paper^[https://github.com/asreview/paper-evaluating-models-across-research-areas].
+This repository contains all systematic review datasets used during this study and their preprocessing scripts, scripts for the hyperparameter optimization, the simulations, the processing and analysis of the results of the simulations, and for the figures and tables in this paper.
+The raw output files of the simulation study are stored on the Open Science Framework page of this paper, https://osf.io/7mr2g/ and https://osf.io/ag2xp/.
+
+### Competing interests
+The authors declare that they have no competing interests.
+
+### Funding
+Access to the Cartesius supercomputer was granted by SURFsara (ID EINF-156).
 SURFsara had no role whatsoever in the design of the current study, nor in the data collection, analysis and interpretation, nor in writing the manuscript.
 
-## Author's contributions
-RS developed the DR balance strategy and ATD metric.
-
+### Author's contributions
+RvdS, RS, JdB and GF designed the study. 
+GF extracted and analyzed the data and drafted the manuscript. 
+RvdS, AB, RS, and JdB assisted with writing the paper. 
+RS developed the DR balance strategy and ATD metric, and wrote the programs required for hyperparameter optimization and cloud computation.  
+RS, JdB, and DO designed the architecture required for the simulation study.  
+LT, AB, and RvdS provided domain knowledge. 
 All authors read and approved the final manuscript.
@@
 ## Acknowledgements
-I am grateful for all researchers who have made great efforts to openly publish the data on their systematic reviews, special thanks go out to Rosanna Nagtegaal.
-I would also like to thank dr.
-Caroline van Baal for supporting me in writing this paper, and prof.
-dr.
-René Eijkemans, for being the second grader of this paper Finally, I would like to express my appreciation to my supervisors prof.
-dr.
-Rens van de Schoot, Jonathan de Bruin, and dr.
-Raoul Schram.
-Your door was always open and your enthusiasm was contagious.
+We are grateful for all researchers who have made great efforts to openly publish the data on their systematic reviews, special thanks go out to Rosanna Nagtegaal.
 <!-- \newpage -->
@@
 <div id="refs"></div>
-
 # Additional file 1
+
+\newpage
+
+# Additional file 2
+
+\newpage
+
+# Additional file 3
 Recall curves plot separately for the PTSD, Software, ACE, Virus and Wilson datasets.
@@
 ```{r, fig-sub-virus, fig.cap = "Recall curves for the Virus dataset.
-", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
+", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifaier', "D2V vs TF-IDF for SVM classifier") }
 # path

### 2020-07-29 results/README.Rmd
update 29-07 corrections

@@
 library(officer)
+
+set.seed(42)
 ```
@@
             sdloss = sd(loss))
+library(boot)
+# but now boostrap
+sdruns <- 
+  runs %>%
+  select(dataset, model, wss.95, rrf.10, loss) %>% 
+  group_by(model, dataset)
+
+test <- sdruns %>% 
+  ungroup()%>%
+  filter(dataset == "ace", model == "NB + TF-IDF")
+
+samplemean <- function(x, d) {
+  result <- c(mean(x[1,d]), mean(x[2,d]), mean(x[3,d]))
+  return(result)
+}
+
+test <- tibble(test %>% select(wss.95, rrf.10, loss))
+
+bs <- boot(t(test),statistic = samplemean, R = 1000)
+
+bs# standard deviation 
+sd(bs$t[,1])
 

### 2020-07-29 manuscript/manuscript/appendices/atd.py

@@ -1,0 +1,56 @@
+
+    def avg_time_to_discovery(self, result_format="number"):
+        """Get the best/last estimate on how long it takes to find a paper.
+
+        Returns
+        -------
+        dict:
+            For each inclusion, key=paper_id, value=avg time.
+        """
+
+
+        labels = self.labels
+
+        # inclusions
+        one_labels = np.where(labels == 1)[0]
+        # store discovery time
+        time_results = {label: [] for label in one_labels}
+
+        # for every state file
+        for state in self.states.values():
+            # order of labeling
+            label_order, n = _get_labeled_order(state)
+            # ranking of papers at last query
+            proba_order = _get_last_proba_order(state)
+
+            # time_mult = ..
+            # n = n initial
+            if result_format == "percentage":
+                time_mult = 100 / (len(labels) - n)
+
+            elif result_format == "fraction":
+                time_mult = 1/(len(labels) - n)
+            else:
+                time_mult = 1
+
+            # for ... i_time, for all papers that are 1 (labels[idx])
+            for i_time, idx in enumerate(label_order[n:]):
+                # for all 1s
+                if labels[idx] == 1:
+                    # time results for inclusions idx = time_mult * the moment paper was detected + 1 (why +1?? )
+                    time_results[idx].append(time_mult*(i_time+1))
+
+            # for all inclusions that weren't labeled (prior inclusions!! )
+            for i_time, idx in enumerate(proba_order):
+                if labels[idx] == 1 and idx not in label_order[:n]:
+                    time_results[idx].append(
+                        time_mult*(i_time + len(label_order)))
+
+        results = {}
+
+        # average over all state_files
+        for label, trained_time in time_results.items():
+            if len(trained_time) > 0:
+                results[label] = np.average(trained_time)
+
+        return results

### 2020-07-29 manuscript/manuscript/tables/boldfunction.R

@@ -1,0 +1,73 @@
+printbold <-
+  function(x, which = NULL, each = c("column", "row"), max = TRUE,
+           NA.string = "", type = c("latex", "html"),
+           sanitize.text.function = force,
+           sanitize.rownames.function = NULL,
+           sanitize.colnames.function = NULL, ...){
+    stopifnot(inherits(x, "xtable"))
+    each <- match.arg(each)
+    type <- match.arg(type)
+    digits <- rep(digits(x), length = ncol(x)+1)
+    if (!is.null(which)) {
+      stopifnot(nrow(which) == nrow(x))
+      stopifnot(ncol(which) == ncol(x))
+      boldmatrix <- which
+    } else {
+      boldmatrix <- matrix(FALSE, ncol = ncol(x), nrow = nrow(x))
+      ## round values before calculating max/min to avoid trivial diffs
+      for (i in 1:ncol(x)) {
+        if (!is.numeric(x[,i])) next
+        x[,i] <- round(x[,i], digits = digits[i+1])
+      }
+      if (each == "column") {
+        max <- rep(max, length = ncol(x))
+        for (i in 1:ncol(x)) {
+          xi <- x[,i]
+          if (!is.numeric(xi)) next
+          if (is.na(max[i])) next
+          imax <- max(xi, na.rm = TRUE)
+          if (!max[i])
+            imax <- min(xi, na.rm = TRUE)
+          boldmatrix[xi == imax, i] <- TRUE
+        }
+      } else if (each == "row") {
+        max <- rep(max, length = nrow(x))
+        for (i in 1:nrow(x)) {
+          xi <- x[i,]
+          ok <- sapply(xi, is.numeric)
+          if (!any(ok)) next
+          if (is.na(max[i])) next
+          imax <- max(unlist(xi[ok]), na.rm = TRUE)
+          if (!max[i])
+            imax <- min(unlist(xi[ok]), na.rm = TRUE)
+          whichmax <- sapply(xi, identical, imax)
+          boldmatrix[i, whichmax] <- TRUE
+        }
+      }
+    }
+    ## need to convert to character
+    ## only support per-column formats, not cell formats
+    display <- rep(compose(x), length = ncol(x)+1)
+    for (i in 1:ncol(x)) {
+      if (!is.numeric(x[,i])) next
+      ina <- is.na(x[,i])
+      x[,i] <- formatC(x[,i], digits = digits[i+1],
+                       format = display[i+1])
[…]
